### 2020-03-05 Experiment_2/Bayesian_models_exp2.Rmd
changes to ToM models

---
title: "Bayesian_models_exp2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(dplyr)

dat <- read.csv("dat_exp2.csv")

####### test data 
dat <- subset(dat,human_id == "bZg1T3MNoItL6b7qAAAj")
#######

dat <- as_tibble(dat) %>% group_by(human_id,game)
dat <- dat %>%
  mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1))

```

```{r}
## the following computes probabilities of ai actions assuming
## strategy is always followed.

## level 0 predictions
dat <- dat %>% mutate(pred_a1_level0 = case_when(
  game == "rps" & ai_action_prev == "rock" ~ 1,
  game == "fwg" & ai_action_prev == "fire" ~ 1,
  game == "shootout" & ai_action_prev == "left" ~ 1,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level0 = case_when(
  game == "rps" & ai_action_prev == "paper" ~ 1,
  game == "fwg" & ai_action_prev == "water" ~ 1,
  game == "shootout" & ai_action_prev == "center" ~ 1,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level0 = case_when(
  game == "rps" & ai_action_prev == "scissors" ~ 1,
  game == "fwg" & ai_action_prev == "grass" ~ 1,
  game == "shootout" & ai_action_prev == "right" ~ 1,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))

## level 1 predictions
dat <- dat %>% mutate(pred_a1_level1 = case_when(
  game == "rps" & human_action_prev == "scissors" ~ 1,
  game == "fwg" & human_action_prev == "grass" ~ 1,
  game == "shootout" & human_action_prev == "left" ~ 1,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level1 = case_when(
  game == "rps" & human_action_prev == "rock" ~ 1,
  game == "fwg" & human_action_prev == "fire" ~ 1,
  game == "shootout" & human_action_prev == "center" ~ 1,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level1 = case_when(
  game == "rps" & human_action_prev == "paper" ~ 1,
  game == "fwg" & human_action_prev == "water" ~ 1,
  game == "shootout" & ai_action_prev == "right" ~ 1,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))

## level 2 predictions
dat <- dat %>% mutate(pred_a1_level2 = case_when(
  game == "rps" & ai_action_prev == "paper" ~ 1,
  game == "fwg" & ai_action_prev == "water" ~ 1,
  game == "shootout" & (ai_action_prev == "center" | ai_action_prev == "right") ~ .5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level2 = case_when(
  game == "rps" & ai_action_prev == "scissors" ~ 1,
  game == "fwg" & ai_action_prev == "grass" ~ 1,
  game == "shootout" & (ai_action_prev == "left" | ai_action_prev == "right") ~ .5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level2 = case_when(
  game == "rps" & ai_action_prev == "rock" ~ 1,
  game == "fwg" & ai_action_prev == "fire" ~ 1,
  game == "shootout" & (ai_action_prev == "left" | ai_action_prev == "center") ~ .5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))

dat$ai_action_num <- recode(dat$ai_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "left" = 1, "center" = 2, "right" = 3)
dat$human_action_num <- recode(dat$human_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "left" = 1, "center" = 2, "right" = 3)

```

```{r}
# group data by subjective component id

# if human does not distinguish between players, we can run with these predictions as is
# if human does distinguish between players, we need to set the predictions to uniform at the start of a round

# if human generalizes over games, we can run update the prior generally
# if human generalizes over rounds but not games, we need to reset the prior at the start of a game
# if human does not generalize, we need to reset the prior at the start of each round

Bayes_model_LL <- function(par,data,distinct_opponent = TRUE, generalize = c("game","stage","no")) {
  # data is a subset for a single participant
  generalize <- match.arg(generalize)
  alpha <- par[1] # probability that opponent plays according to strategy
  if(length(par) > 1) {
    beta <- par[2] # probability that human plays according to best response 
  } else{
    beta <- 1 # probability that human plays according to best response 
  }

  prior <- c(1,1,1) # prior alpha for dirichlet on p(level)
  prior <- prior/sum(prior)

  # use alpha to change the "deterministic" predictions
  make_probs <- function(x) {
    (1-alpha)*(1/3) + alpha*x
  }
  dat <- ungroup(data) %>%
    mutate_at(vars(starts_with("pred_")),make_probs)

  if(distinct_opponent) {
    # start of stage should not be predictable
    dat[dat$round == 1,paste0(paste0("pred_",c("a1_","a2_","a3_")),rep(c("level0","level1","level2"),each=3))] <- 1/3
    # group also by opponent
    dat <- group_by(dat,opp_type)
  }

  if(generalize == "stage") {
    # generalize over rounds but not game, so group by game
    dat <- group_by(dat,game,add=TRUE)
  } else if(generalize == "no") {
    # group by game and stage
    dat <- group_by(dat,game,stage,add=TRUE)
  }

  # compute likelihood of ai action
  dat <- dat %>%
    mutate(
      lik_level0 = case_when(
        ai_action_num == 1 ~ pred_a1_level0,
        ai_action_num == 2 ~ pred_a2_level0,
        ai_action_num == 3 ~ pred_a3_level0
      ),
      lik_level1 = case_when(
        ai_action_num == 1 ~ pred_a1_level1,
        ai_action_num == 2 ~ pred_a2_level1,
        ai_action_num == 3 ~ pred_a3_level1
      ),
      lik_level2 = case_when(
        ai_action_num == 1 ~ pred_a1_level2,
        ai_action_num == 2 ~ pred_a2_level2,
        ai_action_num == 3 ~ pred_a3_level2
      )
    )

  # use likelihood to compute the posterior predictive probability of each level
  dat <- dat %>%
    mutate(logpost_level0 = lag(log(prior[1]) + cumsum(log(lik_level0)),default=log(prior[1])),
           logpost_level1 = lag(log(prior[2]) + cumsum(log(lik_level1)),default=log(prior[2])),
           logpost_level2 = lag(log(prior[3]) + cumsum(log(lik_level2)),default=log(prior[3]))) %>%
    # you can add or subtract any constant from the log-likelihoods; this can aid in precision
    mutate(min = pmin(logpost_level0,logpost_level1, logpost_level2)) %>%
      mutate(normalize = exp(logpost_level0 - min) + exp(logpost_level1 - min) + exp(logpost_level2 - min)) %>%
        mutate(post_level0 = exp(logpost_level0 - min)/normalize,
               post_level1 = exp(logpost_level1 - min)/normalize,
               post_level2 = exp(logpost_level2 - min)/normalize)

  # use posterior predictive probability to predict probability of each ai and then human action
  dat <- dat %>%
    mutate(p_opp_a1 = post_level0*pred_a1_level0 + post_level1*pred_a1_level1 + post_level2*pred_a1_level2,
           p_opp_a2 = post_level0*pred_a2_level0 + post_level1*pred_a2_level1 + post_level2*pred_a2_level2,
           p_opp_a3 = post_level0*pred_a3_level0 + post_level1*pred_a3_level1 + post_level2*pred_a3_level2
    ) %>%
      mutate(p_self_a1 = case_when(
              game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a2 + .5*p_opp_a3),
              TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a3)
                ),
             p_self_a2 = case_when(
               game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a1 + .5*p_opp_a3),
               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a1)
             ),
             p_self_a3 = case_when(
               game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a1 + .5*p_opp_a2),
               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a2)
             )
        )

  # now finally compute the likelihood of human actions 
  dat <- dat %>% 
    mutate(
      loglik = case_when(
        human_action_num == 1 ~ log(p_self_a1),
        human_action_num == 2 ~ log(p_self_a2),
        human_action_num == 3 ~ log(p_self_a3))
    )

  ret <- -2*sum(dat$loglik)
  if(is.infinite(ret) || is.nan(ret)) {
    return(1e+300)
  } else {
    return(ret) 
  }
  # return(-2*sum(dat$loglik))
}

```

```{r}
Bayes_model_LL(0.1,data = dat,distinct_opponent = TRUE, generalize = "game")
```

```{r, ECHO = FALSE}

library(DEoptim)

Bayes_same_game <- Bayes_same_stage <- Bayes_same_no <- 
  Bayes_distinct_game <- Bayes_distinct_stage <- Bayes_distinct_no <- 
    list()

# USing DEOptim

# for(id in levels(dat$human_id)) {
#   tdat <- subset(dat,human_id == id)
#   ctrl <- DEoptim.control(NP = 20, itermax=50)
#   Bayes_same_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                    distinct_opponent = FALSE, generalize = "game",control=ctrl)
#   Bayes_same_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                    distinct_opponent = FALSE, generalize = "stage",control=ctrl)
#   Bayes_same_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                    distinct_opponent = FALSE, generalize = "no",control=ctrl)
#   Bayes_distinct_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                    distinct_opponent = TRUE, generalize = "game",control=ctrl)
#   Bayes_distinct_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                         distinct_opponent = TRUE, generalize = "stage",control=ctrl)
#   Bayes_distinct_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                  distinct_opponent = TRUE, generalize = "no",control=ctrl)
# }

# using optim

for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  # ctrl <- DEoptim.control(NP = 20, itermax=50)

  Bayes_same_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
                                 generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")

  Bayes_same_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
                                 generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")

  Bayes_same_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
                                 generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")

  Bayes_distinct_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
                                 generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")

  Bayes_distinct_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
                                 generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")

  Bayes_distinct_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
                                 generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
}
```

```{r}
# this will implement a pseudo-multinomial-dirichlet
pBayes_model_LL <- function(par,data,distinct_opponent = TRUE, generalize = c("game","stage","no")) {
  generalize <- match.arg(generalize)
  alpha <- par[1] # probability that opponent plays according to strategy
  if(length(par) > 1) {
    gamma <- par[2] # probability that human plays according to best response 
  } else{
    gamma <- 1 # probability that human plays according to best response 
  }
  if(length(par) > 2) {
    beta <- par[3] # probability that human plays according to best response 
  } else{
    beta <- 1 # probability that human plays according to best response 
  }

  prior <- c(gamma,gamma,gamma) # prior alpha for dirichlet on p(level)
  #prior <- prior/sum(prior)

  # use alpha to change the "deterministic" predictions
  make_probs <- function(x) {
    (1-alpha)*(1/3) + alpha*x
  }
  dat <- ungroup(data) %>%
    mutate_at(vars(starts_with("pred_")),make_probs)

  if(distinct_opponent) {
    # start of round should not be predictable
    dat[dat$round == 1,paste0(paste0("pred_",c("a1_","a2_","a3_")),rep(c("level0","level1","level2"),each=3))] <- 1/3
    # group also by opponent
    dat <- group_by(dat,opp_type)
  }

  if(generalize == "stage") {
    # generalize over rounds but not game, so group by game
    dat <- group_by(dat,game,add=TRUE)
  } else if(generalize == "no") {
    # group by game and stage
    dat <- group_by(dat,game,stage,add=TRUE)
  }

  # compute likelihood of ai action
  dat <- dat %>%
    mutate(
      lik_level0 = case_when(
        ai_action_num == 1 ~ pred_a1_level0,
        ai_action_num == 2 ~ pred_a2_level0,
        ai_action_num == 3 ~ pred_a3_level0
      ),
      lik_level1 = case_when(
        ai_action_num == 1 ~ pred_a1_level1,
        ai_action_num == 2 ~ pred_a2_level1,
        ai_action_num == 3 ~ pred_a3_level1
      ),
      lik_level2 = case_when(
        ai_action_num == 1 ~ pred_a1_level2,
        ai_action_num == 2 ~ pred_a2_level2,
        ai_action_num == 3 ~ pred_a3_level2
      )
    )

  # normalize the likeihoods to give a pseudo-observation of strategy
  dat <- dat %>%
    # compute normalizing factor
    mutate(normalize = lik_level0 + lik_level1 + lik_level2) %>%
    # avoid division by 0
    mutate(normalize = replace(normalize, normalize == 0, 1)) %>%
    # normalize
    mutate(pseudo_obs_level0 = lik_level0/normalize,
           pseudo_obs_level1 = lik_level1/normalize,
           pseudo_obs_level2 = lik_level2/normalize)

  # use pseudo observations to compute the posterior predictive probability of each level
  dat <- dat %>%
    mutate(post_level0 = lag(prior[1] + cumsum(pseudo_obs_level0),default=prior[1]),
           post_level1 = lag(prior[2] + cumsum(pseudo_obs_level1),default=prior[2]),
           post_level2 = lag(prior[3] + cumsum(pseudo_obs_level2),default=prior[3])) %>%
      mutate(normalize = post_level0 + post_level1 + post_level2) %>%
        mutate(post_level0 = post_level0/normalize,
               post_level1 = post_level1/normalize,
               post_level2 = post_level2/normalize)

  # use posterior predictive probability to predict probability of each ai and then human action
  dat <- dat %>%
    mutate(p_opp_a1 = post_level0*pred_a1_level0 + post_level1*pred_a1_level1 + post_level2*pred_a1_level2,
           p_opp_a2 = post_level0*pred_a2_level0 + post_level1*pred_a2_level1 + post_level2*pred_a2_level2,
           p_opp_a3 = post_level0*pred_a3_level0 + post_level1*pred_a3_level1 + post_level2*pred_a3_level2
    ) %>%
    mutate(p_self_a1 = case_when(
      game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a2 + .5*p_opp_a3),
      TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a3)
    ),
    p_self_a2 = case_when(
      game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a1 + .5*p_opp_a3),
      TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a1)
    ),
    p_self_a3 = case_when(
      game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a1 + .5*p_opp_a2),
      TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a2)
    )
    )

  # now finally compute the likelihood of human actions 
  dat <- dat %>% 
    mutate(
      loglik = case_when(
        human_action_num == 1 ~ log(p_self_a1),
        human_action_num == 2 ~ log(p_self_a2),
        human_action_num == 3 ~ log(p_self_a3))
    )

  return(-2*sum(dat$loglik))
}

```

```{r}
pBayes_same_game <- pBayes_same_stage <- pBayes_same_no <- 
  pBayes_distinct_game <- pBayes_distinct_stage <- pBayes_distinct_no <- 
  list()

for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  ctrl <- DEoptim.control(NP = 20, itermax=50)
  pBayes_same_game[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
                                   distinct_opponent = FALSE, generalize = "game",control=ctrl)
  pBayes_same_stage[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
                                    distinct_opponent = FALSE, generalize = "stage",control=ctrl)
  pBayes_same_no[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
                                 distinct_opponent = FALSE, generalize = "no",control=ctrl)
  pBayes_distinct_game[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
                                       distinct_opponent = TRUE, generalize = "game",control=ctrl)
  pBayes_distinct_stage[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
                                        distinct_opponent = TRUE, generalize = "stage",control=ctrl)
  pBayes_distinct_no[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
                                     distinct_opponent = TRUE, generalize = "no",control=ctrl)
}
```

### 2020-03-05 Experiment_2/Experiment_2_modelling.Rmd
changes to ToM models

---
title: "Experiment_2_modelling"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

```

```{r}
library(tidyr)
library(dplyr)
library(DEoptim)
library(optimParallel)
library(ggpubr)

# dat_exp2 <- read.csv("MyData.csv")
# 
# # transform 'winner' variable in numeric score
# dat_exp2$score <- recode(dat_exp2$winner, human = 1, tie = 0, AI = -1)
# 
# # Create a new variable stage.f as a factor for the stages 1,2 ,3 4 in game
# dat_exp2$stage.f <- factor(dat_exp2$stage, labels = c("Stage 1","Stage 2","Stage 3", "Stage 4"),levels=c(1,2,3,4))
# 
# # create a new variable "game.f" as a factor variable of games
# dat_exp2$game.f <- factor(dat_exp2$game, labels = c("RPS","FWG","SHOOT"),levels=c("rps","fwg","shootout"))
# 
# # recode actions to make them equal to the codes in these files
# dat_exp2$h_action <- recode(dat_exp2$human_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G")
# dat_exp2$a_action <- recode(dat_exp2$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G")
# 
# write.csv(dat_exp2, row.names=FALSE,file="data_exp2.csv")

```

```{r}
# Read in cleaned data file
dat_exp2 <- read.csv("data_exp2.csv")
test_data = subset(dat_exp2,human_id == "bZg1T3MNoItL6b7qAAAj")
```

```{r}
# Function to produce best reponse to ai_action in exp2
exp2_best_response <- function(game,ai_action){
  if (game == "rps"){
    if (ai_action == "R") {return("P")}
    else if (ai_action == "P") {return("S")}
    else if (ai_action == "S") {return("R")}

  } else if (game == "fwg"){ 
    if (ai_action == "F") {return("W")}
    else if (ai_action == "W") {return("G")}
    else if (ai_action == "G") {return("F")}

  } else if (game == "shootout") {
    if (ai_action == "left") {return("center/right")}
    else if (ai_action == "center") {return("left/right")}
    else if (ai_action == "right") {return("left/center")}
    else if (ai_action == "left/right") {return("center")}
    else if (ai_action == "left/center") {return("right")}
    else if (ai_action == "center/right") {return("left")}
  }
}
```

```{r}
# Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
# TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer) {
#   
#   # dat = data subset for one participant
#   # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
#   # return = -2logLik 
#   # or "likelihood_by_trial" vector  (for later plotting, etc)
#   # btwn_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise. 
#   
#   # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
#   # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
#   theta <- par[1]
#   eps <- par[2]
#   
#   num_strat = length(opp_strategy_vec) 
#   
#   # Load tables predicting oppponent movel
#   
#   rps_predict_opp <- read.csv("rps_predict_opp.csv")
#   fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
#   shootout_predict_opp <- read.csv("shootout_predict_opp.csv")
#   
# 
#   #lik_opp is a vector that holds and updates probability distribution of opp strategy given actions.
#   lik_opp <- matrix(0.0,num_strat, nrow(data))
#   
#   # Initiate prior vectors for each opponent as uniform
#   opp_prior_vec <- rep(1/num_strat, num_strat)
#   opp1_prior_vec <-rep(1/num_strat, num_strat)
#   opp2_prior_vec <-rep(1/num_strat, num_strat)
#   
#   lik_hum <- matrix(0.0,nrow(data))
#   # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
#   br_hum <- rep(NA,num_strat)
# 
#   
#   for(t in 1:nrow(data)) {
#     t_game <- data[t,"game"]
#     pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, shootout = shootout_predict_opp)
#     nopts <- 3
#     if(data[t,"round"] == 1) {
#       # first round is uniform prediction
#       pred_opp <- NA
#       lik_hum[t] <- 1/nopts
#       
#       ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer reset prior to uniform)#####
#       # Round 1 of stage 1 
#       if (data[t,"stage"] == 1) {
#         if (btwn_transfer){
#           # if there is between game transfer, then the opp_prior_vec should have stored what was learned about the SECOND opponent 
#           # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
#           opp2_prior_vec <- opp_prior_vec
#           # if between game transfer use stored opp1 prior vector from previous game (or uniform if first game  RPS) 
#           opp_prior_vec <- opp1_prior_vec
# 
#         } else { # <- No between game TRANSFER 
#           opp_prior_vec <- rep(1/num_strat, num_strat)
#         }
#         
#       # we are round 1 of stage 2, keep opp vector from round 20 of stage 1  for stage 3
#         } else if (data[t,"stage"] == 2) {
#           if (within_transfer){
#             # hold the probs vector of Opp type learned in stage 1 in memory and save to temp.
#             opp1_prior_temp <- opp_prior_vec
#           if (btwn_transfer){
#             # If  between games transfer get prior from opp2 prior saved from last stage of last game 
#             opp_prior_vec <- opp2_prior_vec
#           } else { # if no between transfer start of first interaction with secnd opp should be reset
#             opp_prior_vec <- rep(1/num_strat, num_strat)
#           }
#           
#         } else { # Assume no between game transfer if no within. reasonable. 
#           opp_prior_vec <- rep(1/num_strat, num_strat)    
#         }
#         
#       # we are round 1 of stage 3
#       } else if (data[t,"stage"] == 3) {
#         if (within_transfer) {
#           # if within_transfer keep opp vector from round 20 of stage 2 for stage 4
#           opp2_prior_temp <- opp_prior_vec
#           # if within_transfer, use what we learned about opp1 in stage 1 as new prior.  
#           opp_prior_vec <- opp1_prior_temp
#           
#         } else { # No within transfer, dont store anything and reset priors
#           opp_prior_vec <- rep(1/num_strat, num_strat)    
#         }
# 
#       
#       # We are in round 1 of stage 4,
#       }  else if (data[t,"stage"] == 4) {
#         if (within_transfer) {
#           if (btwn_transfer) {
#             # Store what was learned about opponent 1 for nxt game...
#            opp1_prior_vec <- opp_prior_vec
#           } 
#           # Use what was learned about opponent 2 from stage 2.
#           opp_prior_vec <- opp2_prior_temp
#           
#         } else {
#           opp_prior_vec <- rep(1/num_strat, num_strat)
#         }
#         
#       }
#       
#     # Rounds 2 to End of stage
#     } else {
#       cat("stage", data[t,"stage"], " opps ",  opp_prior_vec, "\n")
#       # get prediction of opponent action from CSV files
#       for (strategy in opp_strategy_vec) {
#         k = match(strategy,opp_strategy_vec)
#         pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])
#         
#         # Given opponent action predicted, what would be human action best response for each opp strat
#         br_hum[[k]] <- exp2_best_response(t_game,as.character(pred_opp))
#         
#         # First we deal with easy case of unique predicted action ( multiple possible preds in shoot are separated by "/" sign)
#         if (!grepl("/",pred_opp,fixed = TRUE)) {
#            # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
#           if(as.character(data[t,"a_action"]) == pred_opp) {
#             lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
#           } else {
#             lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
#           }
#         # Here we are in shootout and opponent predicted action is a vector of two possible moves (e.g "left/center")  
#         } else {
#           if(grepl(as.character(data[t,"a_action"]), pred_opp,fixed = TRUE)) {
#             # Assume each action has likelihood of 50%
#              lik_opp[k,t] <- 0.5*(theta + (1-theta)/nopts)*opp_prior_vec[k]
#           } else {
#             #the 2 is to standardise the theta dependent probs: P(ai plays pred | opp is level k)
#             lik_opp[k,t] <- 2*((1-theta)/nopts)*opp_prior_vec[k]
#           }
#         }
#         
#       # Get which opponent strategy human current actn maps to (i.e, if index = 0 then human current action is best response to level-0 comp_strat...)
#       indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))
# 
#       # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
#       # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
#       if(length(indices) == 0){
#         lik_hum[t] <- eps/nopts
#       # if same br action for multiple possible ai opponents, add probabilities 
#       } else {
#         lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
#       }
#     }  
#       # Standardising the probabilities and updating prior
#       lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
#       opp_prior_vec <- lik_opp[,t]
#     }
#   # for debugging uncomment the line below
#   #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"/n")
#   }
#   
#   if(return_value == "-2loglik") {
#     ret <- -2*sum(log(lik_hum))
#     if(is.infinite(ret) || is.nan(ret)) {
#       return(1e+300)
#     } else {
#       return(ret)
#     }
#   }
#   if(return_value == "likelihood_by_trial") return(lik_hum)
#   
# }

```

```{r}
# Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer, Naive = FALSE) {

  # dat = data subset for one participant
  # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
  # return = -2logLik 
  # or "likelihood_by_trial" vector  (for later plotting, etc)
  # btwn_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise.

  # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
  # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
  theta <- par[1]
  # eps <- par[2]

  num_strat = length(opp_strategy_vec)

  # Load tables predicting oppponent movel

  rps_predict_opp <- read.csv("rps_predict_opp.csv")
  fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
  shootout_predict_opp <- read.csv("shootout_predict_opp.csv")

  #lik_opp is a vector that holds and updates probability distribution of opp strategy given actions.
  lik_opp <- matrix(0.0,num_strat, nrow(data))

  # Initiate prior vectors for each opponent as uniform
  opp_prior_vec <- rep(1/num_strat, num_strat)
  opp1_prior_vec <-rep(1/num_strat, num_strat)
  opp2_prior_vec <-rep(1/num_strat, num_strat)

  lik_hum <- matrix(0.0,nrow(data))
  # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
  br_hum <- rep(NA,num_strat)

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, shootout = shootout_predict_opp)
    nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      pred_opp <- NA
      lik_hum[t] <- 1/nopts

      ## KEY CODE FOR LEARNING TRANSFER !! #####
      #Naive 
      if (Naive) {
        # pass. no update to prior vector throughout all stages and games
      } else {
        #abc
        #def
        # Round 1 of stage 1 
        if (data[t,"stage"] == 1) {
          if (btwn_transfer){
            # if there is between game transfer, then the opp_prior_vec should have stored what was learned about the SECOND opponent 
            # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
            opp2_prior_vec <- opp_prior_vec
            # if between game transfer use stored opp1 prior vector from previous game (or uniform if first game  RPS) 
            opp_prior_vec <- opp1_prior_vec
          } else { # <- No between game TRANSFER 
            opp_prior_vec <- rep(1/num_strat, num_strat)
          }

        # we are round 1 of stage 2, keep opp vector from round 20 of stage 1  for stage 3
        } else if (data[t,"stage"] == 2) {
            if (within_transfer){
              # hold the probs vector of Opp type learned in stage 1 in memory and save to temp.
              opp1_prior_temp <- opp_prior_vec
            if (btwn_transfer){
              # If  between games transfer get prior from opp2 prior saved from last stage of last game 
              opp_prior_vec <- opp2_prior_vec
            } else { # if no between transfer start of first interaction with secnd opp should be reset
              opp_prior_vec <- rep(1/num_strat, num_strat)
            }

          } else { # Assume no between game transfer if no within. reasonable. 
            opp_prior_vec <- rep(1/num_strat, num_strat)    
          }

        # we are round 1 of stage 3
        } else if (data[t,"stage"] == 3) {
          if (within_transfer) {
            # if within_transfer keep opp vector from round 20 of stage 2 for stage 4
            opp2_prior_temp <- opp_prior_vec
            # if within_transfer, use what we learned about opp1 in stage 1 as new prior.  
            opp_prior_vec <- opp1_prior_temp

          } else { # No within transfer, dont store anything and reset priors
            opp_prior_vec <- rep(1/num_strat, num_strat)    
          }

        # We are in round 1 of stage 4,
        }  else if (data[t,"stage"] == 4) {
          if (within_transfer) {
            if (btwn_transfer) {
              # Store what was learned about opponent 1 for nxt game...
             opp1_prior_vec <- opp_prior_vec
            } 
            # Use what was learned about opponent 2 from stage 2.
            opp_prior_vec <- opp2_prior_temp

          } else {
            opp_prior_vec <- rep(1/num_strat, num_strat)
          }

        }

      } #End of no naive condition

    # Rounds 2 to End of stage
    } else {
      #cat("stage", data[t,"stage"], " opps ",  opp_prior_vec, "\n")
      # get prediction of opponent action from CSV files
      for (strategy in opp_strategy_vec) {
        k = match(strategy,opp_strategy_vec)
        pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])

        # Given opponent action predicted, what would be human action best response for each opp strat
        br_hum[[k]] <- exp2_best_response(t_game,as.character(pred_opp))

        # First we deal with easy case of unique predicted action ( multiple possible preds in shoot are separated by "/" sign)
        if (!grepl("/",pred_opp,fixed = TRUE)) {
           # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
          if(as.character(data[t,"a_action"]) == pred_opp) {
            lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
          } else {
            lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
          }
        # Here we are in shootout and opponent predicted action is a vector of two possible moves (e.g "left/center")  
        } else {
          if(grepl(as.character(data[t,"a_action"]), pred_opp,fixed = TRUE)) {
            # Assume each action has likelihood of 50%
             lik_opp[k,t] <- 0.5*(theta + (1-theta)/nopts)*opp_prior_vec[k]
          } else {
            #the 2 is to standardise the theta dependent probs: P(ai plays pred | opp is level k)
            lik_opp[k,t] <- 2*((1-theta)/nopts)*opp_prior_vec[k]
          }
        }

      # Get which opponent strategy human current actn maps to (i.e, if index = 0 then human current action is best response to level-0 comp_strat...)
      indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))

      # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
      # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
      if(length(indices) == 0){
        #lik_hum[t] <- eps/nopts
        lik_hum[t] <- 1/nopts
      # if same br action for multiple possible ai opponents, add probabilities 
      } else {
        #lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
        lik_hum[t] <- sum(opp_prior_vec[indices])/length(indices)
      }
    }  
      # Standardising the probabilities and updating prior
      lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
      opp_prior_vec <- lik_opp[,t]
    }
  # for debugging uncomment the line below
  #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"/n")
  }

  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)

}

```

```{r}

TOM_model(c(0.00001),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = TRUE, btwn_transfer = TRUE, Naive = FALSE)
```
## Fitting Bayesian model with between game transfer (as well as within)  
```{r, cache=TRUE}
exp2_BT <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_BT[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

  # TR_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", btwn_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))

  exp2_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = TRUE, Naive = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}
save(exp2_BT, file="exp2_BT.RData")

```

## Fitting ToM model with NO Between transfer (but with transfer within games)
```{r, cache=TRUE}

exp2_NO_BT <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_NO_BT[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

  # exp2_NO_BT[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))

  exp2_NO_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = FALSE, Naive = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

save(exp2_NO_BT,file="exp2_NO_BT.RData")
```

## Fitting Bayesian model with NO Between or within transfer
```{r, cache=TRUE}

exp2_NO_Tr <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_NO_Tr[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

  # exp2_NO_Tr[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))

  exp2_NO_Tr[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, Naive =FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

save(exp2_NO_Tr,file="exp2_NO_Tr.RData")
```

#Fitting model where player does not distinguish between opponents 
```{r, cache=TRUE}

exp2_Naive <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_Naive[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

  # exp2_Naive[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))

  exp2_Naive[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, Naive = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

save(exp2_Naive,file="exp2_Naive.RData")
```

## Fitting Q_learning with state space of possible last round plays 
```{r, cache=TRUE}
exp2_QL_states <- function(par,data,return_value,gamma, within_transfer = FALSE){
  # Par[1] -> beta= inverse temperature parameter in softmax choice function
  # Par[2] -> lambda = learning rate (one per game?)
  # data : participant and ai choice data.
  # return_value=c("-2loglik","likelihood_by_trial")
  # Gamma is discount factor for future rewards 
  # Returns Q-values per trial and predicts choice using softmax
  beta <- par[1]
  alpha <- par[2]

  #gamma <- 0.9

  #Define matrix of state spaces for each game 
  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
  states_RPS <- paste0(G1$Var1,G1$Var2)

  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
  states_FWG <- paste0(G2$Var1,G2$Var2)

  G3 <- expand.grid(c("left","center","right"), c("left","center","right"))
  states_SHOOT <- paste0(G3$Var1,G3$Var2)

  Q_vals_RPS = matrix(-0.5,9,3)
  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))

  Q_vals_FWG = matrix(-0.5,9,3)
  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))

  Q_vals_SHOOT = matrix(-0.5,9,3)
  dimnames(Q_vals_SHOOT) = list(states_SHOOT, c("left","center","right"))

  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    nopts <- 3

    if(data[t,"round"] == 1) {

      # Within game transfer Code 
      if (!within_transfer){
              Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
      } else {
        if (data[t,"stage"] == 1){
          Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
        } else if (data[t,"stage"] == 2) {
          Q_vals_opp1 <- Q_vals
          Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
        } else if (data[t,"stage"] == 3) {
          Q_vals_opp2 <- Q_vals 
          Q_vals <- Q_vals_opp1
        } else if (data[t,"stage"] == 4) {
          Q_vals <- Q_vals_opp2
        }
      }

      #cat(Q_vals,"\n") 
      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, shootout = states_SHOOT)
      # first round is uniform prediction
      lik_hum[t] <- 1/nopts
      # Randomly select state and previous actions for first round
      curr_state <- sample(state_vec, size = 1)
      h_act <- sample(colnames(Q_vals), size =1)
      ai_act <- sample(colnames(Q_vals), size =1)
      reward <- 0

    } else {
      # Get past human action and associated reward 
      h_act <- as.character(data[t-1,"h_action"])
      ai_act <- as.character(data[t-1,"a_action"])
      reward <- as.numeric(data[t-1,"score"])
    }

    # cat(curr_state, " This is the previous state", "\n")
    new_state <- paste0(h_act,ai_act)
    # cat(new_state,"This is new state","\n")

    # Q_learning: update rule (time  = t-1)
    Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act] )

    # Assume human chooses action probabilistically using softmax on Q values
    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
    #if (data[t,"round"] == 1) { cat(probs,"\n") }

    # Get actual human action and compute likelihood
    h_act <- as.character(data[t,"h_action"])
    act_index <- match(h_act, colnames(Q_vals))
    lik_hum[t] <- probs[[act_index]]

    # Update state
    curr_state <- new_state 
    #}
  }
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)

}

```

```{r}
exp2_QL_states(c(5,0.4),test_data, "-2loglik", 0.0, TRUE)
```

```{r, cache=TRUE}
exp2_QLS_modelling <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_QLS_modelling[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)
  # QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")

   exp2_QLS_modelling[[id]] <- DEoptim(fn=exp2_QL_states,lower = c(0,0), upper = c(20,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE, parallelType=1))
}

save(exp2_QLS_modelling, file="exp2_QLS_modelling.RData")
```

```{r, cache=TRUE}
exp2_QLS_within_Tr <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_QLS_within_Tr[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)
  # QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")

   exp2_QLS_within_Tr[[id]] <- DEoptim(fn=exp2_QL_states,lower = c(0,0), upper = c(20,1), data=tdat,"-2loglik", gamma = 0, within_transfer =TRUE, control=list(trace = FALSE, parallelType=1))
}

save(exp2_QLS_within_Tr , file="exp2_QLS_within_Tr.RData")
```

##Self tuning EWA model

```{r}
exp2_EWA_self <- function(par,data,return_value){

  lambda <- par[1]
  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.

  # Define attraction vectors for each game 
  A_RPS = matrix(0.0,3)
  names(A_RPS) <- c("R","P","S")
  A_FWG = matrix(0.0,3)
  names(A_FWG) <- c("F","W","G")
  A_SHOOT = matrix(0.0,3)
  names(A_SHOOT) <- c("left","center","right")

  # # Define reward matrices from the prospective of the row player (human in our case)
  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))

  reward_SHOOT <- t(matrix(c(-1,1,1,1,-1,1,1,1,-1),nrow=3, ncol=3))
  dimnames(reward_SHOOT) = list(c("left","center","right"), c("left","center","right"))

  # Initiate likelihood by trial vector 
  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Att <- switch(as.character(t_game), rps=A_RPS, fwg = A_FWG, shootout = A_SHOOT)
      reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, shootout = reward_SHOOT)
      game_data <- subset(data, game == t_game)
      lik_hum[t] <- 1/nopts
      N <- 1.0

      R_t <- rep(0.0,nopts)
      H_t <- R_t

    } else {

      indx <- data[t,"round"]
      # Get reward and past human action
      h_act_prev <- as.character(game_data[indx-1,"h_action"])
      a_act_prev <- as.character(game_data[indx-1,"a_action"])

      # Estimate phi(t)
      R_t <- as.numeric(names(Att) == a_act_prev)
      # cat("This is R(t)",R_t,"\n")

      H_t <- (H_t*(indx-2) + R_t)/(indx-1)
      # cat("this is H(t)",H_t,"\n")

      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
      # cat("This is Phit(t)",Phi_t,"\t")

      # Estimate vector Delta(t)

      delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
      #cat("this is delta(t)",delta_t,"\n")

      for (i in 1:length(Att)) {
        action <- as.character(names(Att)[i])
        # cat("this is current strat",action,"\n")
        # cat("this is previous humna action",h_act_prev,"\n")

        # Attraction vector update rule 
        Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
      }
      #Update the value of N 
      N <- Phi_t*N + 1
      #cat(Att,'\n')

      # Assume human chooses action probabilistically using softmax on Attraction values
      probs <- exp(lambda*Att)/sum(exp(lambda*Att))

      # Get actual human action and compute likelihood
      h_act <- as.character(game_data[indx,"h_action"])
      act_index <- match(h_act, names(Att))
      lik_hum[t] <- probs[[act_index]]
    }
  }

 if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)
}

# exp2_EWA_self(1,test_data,"-2loglik")

```

## Fitting SEWA 
```{r, cache=TRUE}

exp2_SEWA_modelling <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_SEWA_modelling[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)
#   exp2_SEWA_modelling[[id]] <- optim(10.0,fn=exp2_EWA_self,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
# }
  exp2_SEWA_modelling[[id]] <- DEoptim(fn=exp2_EWA_self, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
}

save(exp2_SEWA_modelling,file="exp2_SEWA_modelling.RData")
```

## MBM in experiment 2  
```{r}
MBM_2 <- function(par,data,return_value,gamma){
  # Par[1] -> beta= inverse temperature parameter in softmax choice function
  # Par[2] -> lambda = learning rate (one per game?)
  # data : participant and ai choice data.
  # return_value=c("-2loglik","likelihood_by_trial")
  # Gamma is discount factor for future rewards 
  # Returns Q-values per trial and predicts choice using softmax
  beta <- par[1]
  alpha <- par[2]

  #gamma <- 0.9

  #Define matrix of state spaces for each game 
  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
  states_RPS <- paste0(G1$Var1,G1$Var2)

  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
  states_FWG <- paste0(G2$Var1,G2$Var2)

  G3 <- expand.grid(c("left","right","center"), c("left","right","center"))
  states_SHOOT <- paste0(G3$Var1,G3$Var2)

  # Matrices to store Q_values in each state 
  Q_vals_RPS = matrix(-0.5,9,3)
  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
  Q_vals_FWG = matrix(-0.5,9,3)
  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
  Q_vals_SHOOT = matrix(-0.5,9,3)
  dimnames(Q_vals_SHOOT) = list(states_SHOOT, c("left","right","center"))

  # Transition Matrices 
  Transit_RPS = matrix(0,9,9)
  dimnames(Transit_RPS) = list(states_RPS, states_RPS)
  Transit_FWG = matrix(0,9,9)
  dimnames(Transit_FWG) = list(states_FWG, states_FWG)
  Transit_SHOOT = matrix(0,9,9)
  dimnames(Transit_SHOOT) = list(states_SHOOT, states_SHOOT)

  lik_hum <- matrix(0.0,nrow(data))
  nopts <- 3

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, shootout = states_SHOOT)
      Transit <- switch(as.character(t_game),rps=Transit_RPS,fwg = Transit_FWG, shootout = Transit_SHOOT)
      lik_hum[t] <- 1/nopts

      # Randomly select prev_state and actions for first round
      curr_state <- sample(state_vec, size = 1)
      h_act <- sample(colnames(Q_vals), size =1)
      ai_act <- sample(colnames(Q_vals), size =1)
      reward <- 0

    } else {
      # Get past human action and associated reward 
      h_act <- as.character(data[t-1,"h_action"])
      ai_act <- as.character(data[t-1,"a_action"])
      reward <- as.numeric(data[t-1,"score"])
    }

    # cat(curr_state, " This is the previous state", "\n")
    new_state <- paste0(h_act,ai_act)
    # cat(new_state,"This is new state","\n")

    # Update Transit matrix ....first create hot vector = 1 if new state, 0 otherwise 
    hot_vector <- state_vec == new_state

    # Transit probs update: TD learning on transition matrix, learning rate fixed at 0.1
    Transit[curr_state,] <- Transit[curr_state,] + 0.1* (hot_vector - Transit[curr_state,])
    #cat(Transit[curr_state,], "\n")

    # Update Q-values as current reward + a weighted (by trasnsit probs) average of future Q-values.
    Q_Row_max <- apply(Q_vals, 1, max, na.rm = TRUE)
    #cat(Transit[curr_state,] * Q_Row_max, "\n")
    Q_vals[curr_state, h_act] <- reward +  gamma*( Transit[curr_state,] %*% Q_Row_max  )

    # Assume human chooses action probabilistically using softmax on Q values
    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
    #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }

    # Get actual human action and compute likelihood
    h_act <- as.character(data[t,"h_action"])
    act_index <- match(h_act, colnames(Q_vals))
    lik_hum[t] <- probs[[act_index]]

    # Update state
    curr_state<- new_state 
    #}
  }
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)

}

```

```{r, cache=TRUE}

#MBM_2(c(2, 0.1), test_data,"-2loglik", gamma = 0.9 )

MBM2_modelling <- list()
for(id in unique(dat_exp2$human_id)) {
  MBM2_modelling[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)
  # MBM_modelling[[id]] <- optim(c(1,0.1),fn=QMBM,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")

   MBM2_modelling[[id]] <- DEoptim(fn=MBM_2,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0.9, control=list(trace = FALSE,parallelType=1))
}

save(MBM2_modelling, file="MBM2_modelling.RData")

```

## Putting all results together 
```{r}

exp2_results <- data.frame()
for(id in unique(dat_exp2$human_id)) {
exp2_results <- rbind(exp2_results,
                       data.frame(
                         "ID" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Random_BIC" = -2*(180*log(1/3)),

                         # Bayesian updating with/without transfer
                         "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
                         "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
                         "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
                         "Naive_BIC" = exp2_Naive[[id]]$value+ 2*log(180),

                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
                         "theta_transfer" = exp2_BT[[id]]$par[1],
                         "theta_no_btw_tr" = exp2_NO_BT[[id]]$par[1],
                         "theta_no_tr" =  exp2_NO_Tr[[id]]$par[1],
                         "theta_naive" = exp2_Naive[[id]]$par[1],
                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
                         "eps_transfer" = exp2_BT[[id]]$par[2],
                         "eps_no_btwn_tr" = exp2_NO_BT[[id]]$par[2],
                         "eps_no_tr" = exp2_NO_Tr[[id]]$par[2],
                         "eps_naive" = exp2_Naive[[id]]$par[2],

                         # Q-learning with last round states (No within transfer)
                         "QL_states_BIC" = exp2_QLS_modelling[[id]]$optim$bestval + 2*log(180),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QL_states_Beta" = exp2_QLS_modelling[[id]]$optim$bestmem[1],
                         # alpha -> learning rate in QL update
                         "QL_states_alpha" = exp2_QLS_modelling[[id]]$optim$bestmem[2],

                         # QLS assuming within game transfer
                         "QLS_within_Tr_BIC" = exp2_QLS_within_Tr[[id]]$optim$bestval + 2*log(180),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QLS_within_Tr_Beta" = exp2_QLS_within_Tr[[id]]$optim$bestmem[1],
                         # alpha -> learning rate in QL update
                         "QLS_within_Tr_alpha" = exp2_QLS_within_Tr[[id]]$optim$bestmem[2],

                         # Self-Tuning EWA (only 1 parameter)
                          # BIC
                         "EWA_self_2LL" = exp2_SEWA_modelling[[id]]$optim$bestval,
                         "EWA_self_BIC" = exp2_SEWA_modelling[[id]]$optim$bestval + 1*log(180),
                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
                         "EWA_self_Lambda" = exp2_SEWA_modelling[[id]]$optim$bestmem[1],

                         # Model Based Model
                          # BIC
                         "MBM_2LL" = MBM2_modelling[[id]]$optim$bestval,
                         "MBM2_BIC" = MBM2_modelling[[id]]$optim$bestval + 2*log(180),
                          # Alpha is learning rate, beta is temperature in softmax
                         "MBM2_alpha" = MBM2_modelling[[id]]$optim$bestmem[1],
                         "MBM2_beta" = MBM2_modelling[[id]]$optim$bestmem[2]

                         ))
}

write.csv(exp2_results,file="exp2_results.csv",row.names = FALSE)

```

```{r}
exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

 write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
 kable(exp2_table_results)
```

```{r}
exp2_model_comp <- data.frame()
for(id in unique(dat_exp2$human_id)) {
  tdat <- subset(dat_exp2,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(exp2_results, ID == id)
  min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)

  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
  # 
  exp2_model_comp <- rbind(exp2_model_comp ,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model_2" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         "BT_minus_NBT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

                       ))
}

write.csv(exp2_model_comp,file="exp2_model_comp.csv",row.names = FALSE)
```

# Correlate difference between BICs of Bayes transfer and no transfer with early rounds score (evidence for transfer) 
```{r}

cor.test(exp2_model_comp$BT_minus_NBT_BIC, exp2_model_comp$Early_game_score, method="spearman")

```

#Correlation between early game score and difference between best model and random BIC
```{r}
cor.test(exp2_model_comp$Rand_minus_best_BIC, exp2_model_comp$Early_game_score, method="spearman")

```

# Histogram of best fitting models 
```{r}
barplot(table(exp2_model_comp$Best_model))
```

## Let's compare total scores of each participant by the model of best fit, see if Bayes+transfer total scores are higher than Bayes + no transfer

```{r}

# ggboxplot(exp2_model_comp, x = "model", y = "Total_score",
#           color = "model", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
#           order = c("Random", "No Transfer", "Transfer"),
#           ylab = "Total Score", xlab = "Model with best fit")

exp2_model_comp$model <- recode(exp2_model_comp$Best_model,"ToM_BT" = "btwn Tranfer","ToM_NBT" = "No btwn Transfer", "ToM_NT" = "No within or btwn Tr","QL_states" = "Q_Learning",  .default = "Random")
model <- factor(exp2_model_comp$model)
condition <- factor(exp2_model_comp$condition)

# Total score by best predictive model 
tapply(exp2_model_comp$Total_score, model, mean)

# Compute the analysis of variance
res.aov <- aov(Total_score ~ model + condition, data = exp2_model_comp)
# Summary of the analysis
summary(res.aov)
TukeyHSD(res.aov)
```

# Total time by best predictive model
```{r}
tapply(exp2_model_comp$Total_time, model, mean)

time.aov <- aov(Total_time ~ model, data = exp2_model_comp)
# Summary of the analysis
summary(time.aov)
TukeyHSD(time.aov)

```

### 2020-03-05 Experiment_2/pool_ig_ms_results.Rmd
changes to ToM models

---
title: "comparing models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### fit MS models using DEoptim and compre to IG models using optim  
```{r}

pool_de_optim <- data.frame()
for(id in unique(dat_exp2$human_id)) {
pool_de_optim <- rbind(pool_de_optim,
                       data.frame(
                         "ID" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Random_BIC" = -2*(180*log(1/3)),

                         # Bayesian updating with between and within game transfer
                         "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$optim$bestval + 2*log(180),

                         # # Bayesian updating with within but no btwn game transfer
                         "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
                         "Distinct_stage_BIC" = Bayes_distinct_stage[[id]]$optim$bestval + 2*log(180),
                         # 
                         # # No within or between game transfer
                         "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
                         "Bayes_distinct_no" = Bayes_distinct_no[[id]]$optim$bestval + 2*log(180),
                         # 
                         # # No distinction between players, transfer within and between
                         "Naive_BIC" = exp2_Naive[[id]]$value+ 2*log(180),
                         "Bayes_same_game" = Bayes_same_game[[id]]$optim$bestval + 2*log(180)
                       ))
}

write.csv(pool_de_optim,file="pool_de_optim.csv",row.names = FALSE)

```

# Fit both MS and IG models using optim 
```{r}
pool_optim <- data.frame()
for(id in unique(dat_exp2$human_id)) {
pool_optim <- rbind(pool_optim,
                       data.frame(
                         "ID" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Random_BIC" = -2*(180*log(1/3)),

                         # Bayesian updating with between and within game transfer
                         "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$value + 2*log(180),

                         # # Bayesian updating with within but no btwn game transfer
                         "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
                         "Distinct_stage_BIC" = Bayes_distinct_stage[[id]]$value + 2*log(180),
                         # 
                         # # No within or between game transfer
                         "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
                         "Bayes_distinct_no" = Bayes_distinct_no[[id]]$value + 2*log(180),
                         # 
                         # # No distinction between players, transfer within and between
                         "Naive_BIC" = exp2_Naive[[id]]$value+ 2*log(180),
                         "Bayes_same_game" = Bayes_same_game[[id]]$value + 2*log(180)
                       ))
}

write.csv(pool_optim,file="pool_optim.csv",row.names = FALSE)
```

### 2020-08-12 Bayesian_models_exp1.Rmd
added BIC weights and new Bayes model

---
title: "Bayesian_models_exp2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(dplyr)

dat <- read.csv("data20180719.csv")

####### test data

# dat <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")

#######

dat <- as_tibble(dat) %>% group_by(human_id,game)
dat <- dat %>%
  mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1))

```

```{r}
## the following computes probabilities of ai actions assuming
## strategy is always followed. (level refers to ai level)

## level 0 predictions
dat <- dat %>% mutate(pred_a1_level0 = case_when(
  game == "rps" & ai_action_prev == "rock" ~ 1,
  game == "fwg" & ai_action_prev == "fire" ~ 1,
  game == "numbers" & ai_action_prev == "one" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level0 = case_when(
  game == "rps" & ai_action_prev == "paper" ~ 1,
  game == "fwg" & ai_action_prev == "water" ~ 1,
  game == "numbers" & ai_action_prev == "two" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level0 = case_when(
  game == "rps" & ai_action_prev == "scissors" ~ 1,
  game == "fwg" & ai_action_prev == "grass" ~ 1,
  game == "numbers" & ai_action_prev == "three" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a4_level0 = case_when(
  game == "numbers" & ai_action_prev == "four" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))
dat <- dat %>% mutate(pred_a5_level0 = case_when(
  game == "numbers" & ai_action_prev == "five" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))

## level 1 predictions
dat <- dat %>% mutate(pred_a1_level1 = case_when(
  game == "rps" & human_action_prev == "scissors" ~ 1,
  game == "fwg" & human_action_prev == "grass" ~ 1,
  game == "numbers" & human_action_prev == "five" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level1 = case_when(
  game == "rps" & human_action_prev == "rock" ~ 1,
  game == "fwg" & human_action_prev == "fire" ~ 1,
  game == "numbers" & human_action_prev == "one" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level1 = case_when(
  game == "rps" & human_action_prev == "paper" ~ 1,
  game == "fwg" & human_action_prev == "water" ~ 1,
  game == "numbers" & ai_action_prev == "two" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a4_level1 = case_when(
  game == "numbers" & ai_action_prev == "three" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))
dat <- dat %>% mutate(pred_a5_level1 = case_when(
  game == "numbers" & ai_action_prev == "four" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))

## level 2 predictions
dat <- dat %>% mutate(pred_a1_level2 = case_when(
  game == "rps" & ai_action_prev == "paper" ~ 1,
  game == "fwg" & ai_action_prev == "water" ~ 1,
  game == "numbers" & ai_action_prev == "four" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level2 = case_when(
  game == "rps" & ai_action_prev == "scissors" ~ 1,
  game == "fwg" & ai_action_prev == "grass" ~ 1,
  game == "numbers" & ai_action_prev == "five" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level2 = case_when(
  game == "rps" & ai_action_prev == "rock" ~ 1,
  game == "fwg" & ai_action_prev == "fire" ~ 1,
  game == "numbers" & ai_action_prev == "one" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a4_level2 = case_when(
  game == "numbers" & ai_action_prev == "two" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))
dat <- dat %>% mutate(pred_a5_level2 = case_when(
  game == "numbers" & ai_action_prev == "three" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))

dat$ai_action_num <- recode(dat$ai_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "one" = 1, "two" = 2, "three" = 3, "four" = 4 , "five" = 5)
dat$human_action_num <- recode(dat$human_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "one" = 1, "two" = 2, "three" = 3, "four" = 4 , "five" = 5)

```

```{r}
# group data by subjective component id

# if human generalizes over games, we can run update the prior generally
# if human does not generalize, we need to reset the prior at the start of each ?stage?
exp1_Bayes_model_LL <- function(par,data, generalize = c("game","no")) {
  # data is a subset for a single participant
  generalize <- match.arg(generalize)
  alpha <- par[1] # probability that ai opponent plays according to strategy
  if(length(par) > 1) {
    beta <- par[2] # probability that human plays according to best response 
  } else{
    beta <- 1 # probability that human plays according to best response 
  }

  prior <- c(1,1,1) # prior alpha for dirichlet on p(level)
  prior <- prior/sum(prior)

  # use alpha to change the "deterministic" prediction

  dat <- ungroup(data) %>%
     mutate_at(.vars = vars(c(starts_with("pred_a1"),starts_with("pred_a2"),starts_with("pred_a3"))), 
                            funs (case_when(
      game == "numbers" ~  alpha*. + (1-alpha)/5,
                  TRUE ~ alpha*. + (1-alpha)/3))) %>%
     mutate_at(.vars = vars(c(starts_with("pred_a4"),starts_with("pred_a5"))), 
                            funs (case_when(
      game == "numbers" ~  alpha*. + (1-alpha)/5,
                  TRUE ~ 0)))

  if(generalize == "no") {
    # group by game and stage
    dat <- group_by(dat,game,add=TRUE)
  }

  # compute likelihood of ai action
  dat <- dat %>%
    mutate(
      lik_level0 = case_when(
        ai_action_num == 1 ~ pred_a1_level0,
        ai_action_num == 2 ~ pred_a2_level0,
        ai_action_num == 3 ~ pred_a3_level0,
        ai_action_num == 4 ~ pred_a4_level0,
        ai_action_num == 5 ~ pred_a5_level0
      ),
      lik_level1 = case_when(
        ai_action_num == 1 ~ pred_a1_level1,
        ai_action_num == 2 ~ pred_a2_level1,
        ai_action_num == 3 ~ pred_a3_level1,
        ai_action_num == 4 ~ pred_a4_level1,
        ai_action_num == 5 ~ pred_a5_level1
      ),
      lik_level2 = case_when(
        ai_action_num == 1 ~ pred_a1_level2,
        ai_action_num == 2 ~ pred_a2_level2,
        ai_action_num == 3 ~ pred_a3_level2,
        ai_action_num == 4 ~ pred_a4_level2,
        ai_action_num == 5 ~ pred_a5_level2
      )
    )

  # use likelihood to compute the posterior predictive probability of each level
  dat <- dat %>%
    mutate(logpost_level0 = lag(log(prior[1]) + cumsum(log(lik_level0)),default=log(prior[1])),
           logpost_level1 = lag(log(prior[2]) + cumsum(log(lik_level1)),default=log(prior[2])),
           logpost_level2 = lag(log(prior[3]) + cumsum(log(lik_level2)),default=log(prior[3]))) %>%
    # you can add or subtract any constant from the log-likelihoods; this can aid in precision
    mutate(min = pmin(logpost_level0,logpost_level1, logpost_level2)) %>%
      mutate(normalize = exp(logpost_level0 - min) + exp(logpost_level1 - min) + exp(logpost_level2 - min)) %>%
        mutate(post_level0 = exp(logpost_level0 - min)/normalize,
               post_level1 = exp(logpost_level1 - min)/normalize,
               post_level2 = exp(logpost_level2 - min)/normalize)

   #cat(as.character(c(round(dat$post_level0,2), round(dat$post_level1,2), round(dat$post_level2,2)), "\n", "\n"))

  # use posterior predictive probability to predict probability of each ai and then human action
  # opp is ai and self is human player here
  dat <- dat %>%
    mutate(p_opp_a1 = post_level0*pred_a1_level0 + post_level1*pred_a1_level1 + post_level2*pred_a1_level2,
           p_opp_a2 = post_level0*pred_a2_level0 + post_level1*pred_a2_level1 + post_level2*pred_a2_level2,
           p_opp_a3 = post_level0*pred_a3_level0 + post_level1*pred_a3_level1 + post_level2*pred_a3_level2,
           p_opp_a4 = post_level0*pred_a4_level0 + post_level1*pred_a4_level1 + post_level2*pred_a4_level2,
           p_opp_a5 = post_level0*pred_a5_level0 + post_level1*pred_a5_level1 + post_level2*pred_a5_level2
    ) %>%
      mutate(p_self_a1 = case_when(
              game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a5,
              TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a3)
                ),
             p_self_a2 = case_when(
               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a1,
               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a1)
             ),
             p_self_a3 = case_when(
               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a2,
               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a2)
             ),
             p_self_a4 = case_when(
               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a3,
               TRUE ~ 0
             ),
             p_self_a5 = case_when(
               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a4,
               TRUE ~ 0
             )
        )

  # now finally compute the likelihood of human actions 
  dat <- dat %>% 
    mutate(
      loglik = case_when(
        human_action_num == 1 ~ log(p_self_a1),
        human_action_num == 2 ~ log(p_self_a2),
        human_action_num == 3 ~ log(p_self_a3),
        human_action_num == 4 ~ log(p_self_a4),
        human_action_num == 5 ~ log(p_self_a5))
    )

  #cat(as.character(exp(dat$loglik)), "\n", "\n")

  ret <- -2*sum(dat$loglik)
  if(is.infinite(ret) || is.nan(ret)) {
    return(1e+300)
  } else {
    return(ret)
  }
  # return(-2*sum(dat$loglik))
}

```

```{r}
# exp1_Bayes_model_LL(0.4,data = dat, generalize = "game")
```

```{r}
#PLot likelihood for first participant as function of parameter

dat <- subset(dat, human_id == "QSuzBXpbyRc370HsAACW")
likelihoods <- list()
for (t in 1:95) {
  likelihoods[t] <- exp1_Bayes_model_LL(t/100,data = dat, generalize = "game")
}

jpeg(file="QSuzBXpbyRc370HsAACW.jpeg")
plot(unlist(likelihoods))
dev.off()

```

```{r, ECHO = FALSE}

library(DEoptim)

exp1_Bayes_game_Tr <- exp1_Bayes_no_Tr <- list()

# # USing DEOptim 
for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))
  exp1_Bayes_game_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                  generalize = "game",control=ctrl)
  exp1_Bayes_no_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                  generalize = "no",control=ctrl)
}

# using optim

# for(id in levels(dat$human_id)) {
#   tdat <- subset(dat,human_id == id)
#   # ctrl <- DEoptim.control(NP = 20, itermax=50)
#   
#   Bayes_same_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
#   
#   
#   Bayes_same_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_same_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_distinct_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_distinct_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_distinct_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
# }
```
```{r}

exp1_Bayes_game_Tr[["QSuzBXpbyRc370HsAACW"]]$optim$bestval
exp1_Bayes_game_Tr[["QSuzBXpbyRc370HsAACW"]]$optim$bestmem[[1]]
```

### 2020-08-12 Experiment_2/Bayesian_models_exp2.Rmd
added BIC weights and new Bayes model

@@
 ####### test data
-dat <- subset(dat,human_id == "bZg1T3MNoItL6b7qAAAj")
+
+# dat <- subset(dat,human_id == "bZg1T3MNoItL6b7qAAAj")
+# dat <- subset(dat,human_id == "J3SqvTcFUwXtSC6wAAB0")
+# dat <- subset(dat,human_id == "gRRZ0rUagyVejWTOAAFl")
+dat <- subset(dat,human_id == "vGnDPRowetREQVmwAADL")
+# dat <- subset(dat,human_id == "wi_zWhftr9MdqTmCAAHs")
+
 #######
@@
 ## the following computes probabilities of ai actions assuming
-## strategy is always followed.
+## strategy is always followed. (level refers to ai level)
 
@@
 # if human does not distinguish between players, we can run with these predictions as is
-# if human does distinguish between players, we need to set the predictions to uniform at the start of a round
+# if human does distinguish between players, we need to set the predictions to uniform at the start of a stage
 
@@
 # if human generalizes over rounds but not games, we need to reset the prior at the start of a game
-# if human does not generalize, we need to reset the prior at the start of each round
+# if human does not generalize, we need to reset the prior at the start of each ?stage?
 
@@
   generalize <- match.arg(generalize)
-  alpha <- par[1] # probability that opponent plays according to strategy
+  alpha <- par[1] # probability that ai opponent plays according to strategy
   if(length(par) > 1) {
@@
 
+    # cat(as.character(c(dat$post_level0, dat$post_level1, dat$post_level2)), "\n")
+
   # use posterior predictive probability to predict probability of each ai and then human action
+  # opp is ai and self is human player here
   dat <- dat %>%
@@
 
+  #cat(as.character(exp(dat$loglik)), "\n", "\n")
+
   ret <- -2*sum(dat$loglik)
@@
 ```{r}
-Bayes_model_LL(0.1,data = dat,distinct_opponent = TRUE, generalize = "game")
+#Bayes_model_LL(0.5,data = dat,distinct_opponent = TRUE, generalize = "game")
+
+#PLot likelihood for first participant as function of parameter 
+likelihoods <- list()
+for (t in 1:99) {
+  likelihoods[t] <- Bayes_model_LL(t/100,data = dat,distinct_opponent = TRUE, generalize = "game")
+}
+
+jpeg(file="vGnDPRowetREQVmwAADL.jpeg")
+plot(unlist(likelihoods))
+dev.off()
+
 ```
@@
 
-# for(id in levels(dat$human_id)) {
-#   tdat <- subset(dat,human_id == id)
-#   ctrl <- DEoptim.control(NP = 20, itermax=50)
-#   Bayes_same_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                    distinct_opponent = FALSE, generalize = "game",control=ctrl)
-#   Bayes_same_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                    distinct_opponent = FALSE, generalize = "stage",control=ctrl)
-#   Bayes_same_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                    distinct_opponent = FALSE, generalize = "no",control=ctrl)
-#   Bayes_distinct_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                    distinct_opponent = TRUE, generalize = "game",control=ctrl)
-#   Bayes_distinct_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                         distinct_opponent = TRUE, generalize = "stage",control=ctrl)
-#   Bayes_distinct_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                  distinct_opponent = TRUE, generalize = "no",control=ctrl)
-# }
+for(id in levels(dat$human_id)) {
+  tdat <- subset(dat,human_id == id)
+  ctrl <- DEoptim.control(NP = 20, itermax=50)
+  Bayes_same_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
+                                   distinct_opponent = FALSE, generalize = "game",control=ctrl)
+  Bayes_same_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
+                                   distinct_opponent = FALSE, generalize = "stage",control=ctrl)
+  Bayes_same_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
+                                   distinct_opponent = FALSE, generalize = "no",control=ctrl)
+  Bayes_distinct_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
+                                   distinct_opponent = TRUE, generalize = "game",control=ctrl)
+  Bayes_distinct_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
+                                        distinct_opponent = TRUE, generalize = "stage",control=ctrl)
+  Bayes_distinct_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
+                                 distinct_opponent = TRUE, generalize = "no",control=ctrl)
+}
 
@@
 
-for(id in levels(dat$human_id)) {
-  tdat <- subset(dat,human_id == id)
-  # ctrl <- DEoptim.control(NP = 20, itermax=50)
-
-  Bayes_same_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-                                 generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
-
-  Bayes_same_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-                                 generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
-
-  Bayes_same_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-                                 generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
-
-  Bayes_distinct_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-                                 generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
-
-  Bayes_distinct_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-                                 generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
-
-  Bayes_distinct_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-                                 generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
-}
+# for(id in levels(dat$human_id)) {
+#   tdat <- subset(dat,human_id == id)
+#   # ctrl <- DEoptim.control(NP = 20, itermax=50)
+#   
+#   Bayes_same_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
+#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
+#   
+#   
+#   Bayes_same_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
+#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
+# 
+#   Bayes_same_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
+#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
+# 
+#   Bayes_distinct_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
+#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
+# 
+#   Bayes_distinct_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
+#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
+# 
+#   Bayes_distinct_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
+#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
+# }
 ```

### 2020-08-12 Experiment_2/Experiment_2_modelling.Rmd
added BIC weights and new Bayes model

@@
   # dat = data subset for one participant
-  # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
+  # opp_strategy_vec = vector of possible opponent strategies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
   # return = -2logLik 
@@
   # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
-  # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
   theta <- par[1]
-  # eps <- par[2]
 
@@
 
-  # Load tables predicting oppponent movel
+  # Load tables predicting oppponent model
 
@@
             if (within_transfer){
-              # hold the probs vector of Opp type learned in stage 1 in memory and save to temp.
+              # hold the probs vector of opponent type learned in stage 1 in memory and save to temp.
               opp1_prior_temp <- opp_prior_vec
+
               if (btwn_transfer){
@@
 
+      lik_opp[,t] <- opp_prior_vec
+
       } #End of no naive condition
@@
         # Given opponent action predicted, what would be human action best response for each opp strat
-        br_hum[[k]] <- exp2_best_response(t_game,as.character(pred_opp))
-
-        # First we deal with easy case of unique predicted action ( multiple possible preds in shoot are separated by "/" sign)
+        br_hum[[k]] <- as.character(exp2_best_response(t_game,as.character(pred_opp)))
+
+        # First we deal with easy case of unique predicted action ( multiple preds in shoot are separated by "/" sign)
         if (!grepl("/",pred_opp,fixed = TRUE)) {
@@
             # Assume each action has likelihood of 50% 
-             lik_opp[k,t] <- 0.5*(theta + (1-theta)/nopts)*opp_prior_vec[k]
-          } else {
-            #the 2 is to standardise the theta dependent probs: P(ai plays pred | opp is level k)
-            lik_opp[k,t] <- 2*((1-theta)/nopts)*opp_prior_vec[k]
-          }
-        }
-
+             lik_opp[k,t] <- (0.5*(theta + (1-theta)/nopts) + 0.5*((1-theta)/nopts)) *opp_prior_vec[k]
+          } else { 
+            lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
+          }
+        }
+      }  
       # Get which opponent strategy human current actn maps to (i.e, if index = 0 then human current action is best response to level-0 comp_strat...)
       indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))
-
-      # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
-      # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
-      if(length(indices) == 0){
-        #lik_hum[t] <- eps/nopts
-        lik_hum[t] <- 1/nopts
-      # if same br action for multiple possible ai opponents, add probabilities 
-      } else {
-        #lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
-        lik_hum[t] <- sum(opp_prior_vec[indices])/length(indices)
-      }
-    }  
+      not_pred_indx <- setdiff(c(1,2,3),indices)
+      # cat(as.character(indices), "\n")
+
+      # THEN likelihood of current human action is just sumproduct of priors and likelihood of each oppoennt action
+      if (!grepl("/",br_hum,fixed = TRUE)) {
+        lik_hum[t] <- sum(opp_prior_vec[indices])* (theta + (1-theta)/nopts) +    sum(opp_prior_vec[not_pred_indx])*(1-theta)/nopts
+      } else {
+        for (i in 1:3) {
+          temp <- 0
+          if (grepl("/",br_hum[i],fixed = TRUE)) {
+            temp <- temp + 0.5*(theta + (1-theta)/nopts)*opp_prior_vec[i]
+          } else{
+            temp <- temp + 
+          }
+        }
+        lik_hum[t] <- sum(opp_prior_vec[indices])* (theta + (1-theta)/nopts) +    sum(opp_prior_vec[not_pred_indx])*(1-theta)/nopts
+      }
+
       # Standardising the probabilities and updating prior
@@
       opp_prior_vec <- lik_opp[,t]
-    }
+    } # End of else ( from round 2 onwards)
+
   # for debugging uncomment the line below
-  #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"/n")
+  # cat(as.character(data[t,"a_action"]),lik_opp[,t],"\n")
+  cat(as.character(br_hum),as.character(data[t,"h_action"]),lik_hum[t],"\n","\n")
+
   }
@@
 
-TOM_model(c(0.00001),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = TRUE, btwn_transfer = TRUE, Naive = FALSE)
+TOM_model(c(0.5),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = TRUE, btwn_transfer = TRUE, Naive = FALSE)
+
 ```
@@
 ```{r}
-
 exp2_results <- data.frame()
@@
                          "Random_BIC" = -2*(180*log(1/3)),
-
-                         # Bayesian updating with/without transfer
-                         "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
-                         "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
-                         "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
-                         "Naive_BIC" = exp2_Naive[[id]]$value+ 2*log(180),
+# 
+# #                          # Bayesian updating with/without transfer
+#                          "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
+#                          "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
+#                          "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
+#                          "Naive_BIC" = exp2_Naive[[id]]$value+ 2*log(180),
+
+                         # MS results for Bayesian models
+                         #  # Bayesian updating with between and within game transfer
+                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$value + 2*log(180),
+                          # Bayesian updating with within but no btwn game transfer
+                         "Distinct_stage_BIC" = Bayes_distinct_stage[[id]]$value + 2*log(180),
+                          #  No within or between game transfer
+                         "Bayes_distinct_no" = Bayes_distinct_no[[id]]$value + 2*log(180),
+                          # No distinction between players, transfer within and between
+                         "Bayes_same_game" = Bayes_same_game[[id]]$value + 2*log(180),
 
@@
 ```{r}
-exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+# WIth IG results for Bayesian models
+# exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+
+# WIth MS results for Bayesian models
+exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
 
@@
  kable(exp2_table_results)
+```
+
+```{r}
+# WITH MS results for bayesian models 
+# exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+# 
+#  write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
+#  kable(exp2_table_results)
 ```
@@
   id_results <- subset(exp2_results, ID == id)
-  min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
-
-  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
+
+  # IG BAYES MODELS 
+  # min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
+  # 
+  # best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
+
+  # MS BAYES MODELS
+  min_BIC <- apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
+
+  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
+
   # 
@@
                          "Total_time" = sum(tdat$human_rt),
-                         "BT_minus_NBT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
+                         # "BT_minus_NBT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
+                         "BT_minus_NBT_BIC" = id_results[,"Distinct_game_BIC"] - id_results[,"Distinct_stage_BIC"],
                          "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
@@
 
+# exp2_model_comp$model <- recode(exp2_model_comp$Best_model,"ToM_BT" = "btwn Tranfer","ToM_NBT" = "No btwn Transfer", "ToM_NT" = "No within or btwn Tr","QL_states" = "Q_Learning",  .default = "Random")
+
 exp2_model_comp$model <- recode(exp2_model_comp$Best_model,"ToM_BT" = "btwn Tranfer","ToM_NBT" = "No btwn Transfer", "ToM_NT" = "No within or btwn Tr","QL_states" = "Q_Learning",  .default = "Random")
+
 model <- factor(exp2_model_comp$model)

### 2020-08-12 Experiment_2/score_plots_exp2.Rmd
added BIC weights and new Bayes model

---
title: "Score_plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggpubr)

```

```{r}

exp2_dat = read.csv("data_exp2.csv")
exp2_model_comp = read.csv("exp2_model_comp.csv")

datalist = list()
i = 0
new_dat <- setNames(data.frame(matrix(ncol = ncol(exp2_dat), nrow = 0)), colnames(exp2_dat))
for(id in unique(exp2_dat$human_id)) {
  i <- i+1
  tdat <- subset(exp2_dat,human_id == id)
  tdat$part_num <- i
  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
  datalist[[i]] <- tdat
}

# Merge all datasets into one 
new_dat <- dplyr::bind_rows(datalist)
# or new_dat <- data.table::rbindlist(datalist)

# Add column for time t
new_dat <- new_dat %>% group_by(exp2_dat$human_id) %>% mutate(t = row_number())

# Participant number as a factor 
# tdat$part_num <- as.factor(tdat$part_num)

# Add best fitting model per participant
new_dat <- merge(new_dat, exp2_model_comp[, c("human_id", "Best_model_2")], by="human_id")
```

```{r}
ggplot(data = new_dat, aes(x = t, y=acc_sum, group = part_num)) + 
  geom_line(aes(color= Best_model_2))
```

```{r}
temp <- new_dat[,c("t","acc_sum","Best_model_2","condition","part_num")]
dat_by_model <- temp %>% group_by(Best_model_2,t) %>% 
  summarize(model_acc_sum = mean(acc_sum))

ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model_2)) + 
   geom_line(aes(color= Best_model_2))
```

### 2020-08-12 Report/draft_report_v1.Rmd
added BIC weights and new Bayes model

---
title             : "Transfer of Learned Opponent Models in Zero Sum Games"
shorttitle        : "Draft-1"

author: 
  - name          : "Ismail Guennouni"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
    email         : "i.guennouni.17@ucl.ac.uk"
  - name          : "Maarten Speekenbrink"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Experimental Psychology, University College London"

author_note: |
  <!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

# keywords          : "keywords"
# wordcount         : "X"

bibliography      : ["Mendeley.bib"]
# csl               : "apa-6th-edition.csl"

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
linkcolor         : "blue"
mask              : no
draft             : no
fig_caption       : yes

documentclass     : "apa6"
# classoption       : a4paper
classoption       : man
output            : papaja::apa6_pdf
---

```{r load-packages, include = FALSE}
library(papaja)
require(knitr)
require(citr)
require(bookdown)
# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
library(tidyr)
library(dplyr)
library(MASS)
library(ggpubr)
library(afex)
library(PairedData)
library(multcompView)
library(lsmeans)
library(magick)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
```

```{r, include=FALSE} 
options(tinytex.verbose = TRUE)
```

# Introduction
Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence. Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge. More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation. This typically human skill has so far eluded modern AI agents. Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games. Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains. @Lake2017 argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.

One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next. Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations. This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction. There is evidence that people learn models of their opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher]. In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations. These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities [@Woodruff] play a role in determining human behaviour.  In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions. More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards. Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to the task of opponent modelling.

Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously. For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games. They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players. @knez2000increasing test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones. They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings. They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity. If the games were only strategically similar, then the transfer was much weaker.

@Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer. However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games. In a series of experiments using economic signalling games [@cooper2003lessons; @Cooper2008] the researchers found that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.  They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.

Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games. A notable exception is the effort by @Haruvy2012 to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game. Participants played ten games, presented as 4x4 normal form (matrix payoffs). Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant. They also showed that players learn abstract aspects of the game that are then transferred to new settings. Their rule-learning model, based on @stahl1995players, was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.

Still, one of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules. The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints. It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning. @simon1972theories explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria. Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one. This concept finds its natural application in 'level-k' theory, first adopted by @stahl1995players. It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication. At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment @arad201211. Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption. Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below, and so on.

In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning. The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit @goodie2012levels.

Our choice of using computer oponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs. When playing against other human opponents, players are learning about the game and the strategy of the opponent simultaneously. Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent. The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.  For instance, @spiliopoulos2013strategic made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing. @shachat2004we made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game. They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.

We chose to use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors. We avoid social dilemma and coordination games that crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome. Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion. Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors. As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transferred. By contrast, purely competitive settings and zero sum games in particular would be more appropriate. They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building. Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learning. Games with unique mixed strategy Nash equilibrium leading to nil average rewards facilitate inferring whether participants have learned to exploit the non-random play of the opponent.

We measure transfer of learning about the opponent strategy between games with varying degrees of similarity. The first two games we use are identical except for action labels. In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with a fixed expected reward against a Nash player.

Hence, we ran a total of two experiments where human participants played 3 different games against either 1 (first experiment ) or 2 (second experiment) computer opponents. In the following sections, we will describe each experiment's methodology and results separately, then discuss the findings before using computational modelling to shed light on some of the results.

\newpage

# Experiment 1

## Methods

## Participants

A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform. The mean age of participants was 31.2 years. Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06. The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.

## Procedure

In the first experiment, participants played 3 games sequentially against the same computer opponent. The computer opponent either used a level-1 or level-2 strategy. The three games were rock-paper-scissors, fire-water-grass and the numbers game. A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper. If one player choses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1). Otherwise it is a draw and both players receive a reward of 0. It has a unique MSNE consisting of randomly playing one of the three options each time.

The second game is identical to Rock-Paper-Scissors in all but action labels. We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water. We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.  Finally, the numbers game is a generalization of rock-paper-scissors. In the variant we use, 2 participants concurrently pick a number between 1 and 5. To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent. For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round. To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1. This game has a structure similar to RPS in which every action is dominated by exactly one choice. All other possible combination of choices that are not consecutive are considered ties. A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score. Similar to RPS, the MSNE is to play each action with equal probability in a random way.

Participants were informed they would play three different games against the same computer opponent. Each participant plays all three games consecutively and in the same order described above. Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice. A total of 50 rounds of each game was played with the player's score displayed at the end of each game. The score was calculated as the number of wins minus the number of losses. Ties did not affect the score. In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score. The overall score of the players was translated into the bonus by making each point worth £0.02. This bonus is significant as players could increase the total payoff from the experiment by up to 60% assuming they'd won all rounds against the computer opponent.  An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps).

```{r feedback-rps, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align='center'}

knitr::include_graphics("images/feedback_rps.png")

```

## Results

```{r load-exp1-data, include=FALSE}

dat1 <- read.csv("../data20180719.csv")

# transform 'winner' variable in numeric score
dat1$score <- recode(dat1$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat1$block <- factor(as.numeric(cut(dat1$round,2)),labels =c("first half", "second half"))

# create a new variable "game.f" as a factor variable of games
dat1$game.f <- factor(dat1$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))

#Group data by human_id and calculate mean score per block of each game.
dat2 <- dat1 %>% 
  group_by(human_id,condition,game,block,game.f) %>% 
      summarize(block_score = mean(score))

# Group data by game and ID
dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
# head(dat3,6)

# Subsetting scores data by game
rps <- subset(dat3,  game.f == "RPS",game_score)
fwg <- subset(dat3,  game.f == "FWG",game_score)
num <- subset(dat3,  game.f == "NUM",game_score)
# head(rps,6)
```

```{r exp1-avg-scores-game, fig.cap = "Average scores per game across conditions", fig.align="center"}
# Plot average  scores per game 
ggboxplot(dat3, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games") 
```

Looking at the aggregate scores (See Figure\ \@ref(fig:exp1-avg-scores-game) ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).  Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value < 0.001 ;  FWG:  t(51) = 10.04 , p-value < 0.001 ; NUMBERS: t(51) = 7.17, p-value < 0.001).

To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants. There was a main effect of Game ( F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games. Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024). The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65). The main effect of Block ( F(1,50) = 22.51 , p < .001, $\eta^{2}$ = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning. As players interact more with the agent, they learn how to win more often. The main effect of Condition (F(1,50) = 5.44, p = .024, $\eta^{2}$ = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27). This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).

```{r exp1-3factor-plot, fig.cap = "Average scores by game, block and condition", fig.align = "center"}

# Plot results by game and block (for all 3 games, learning is happening) 
p <- ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")

p + facet_grid(. ~ condition)

```

Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, $\eta^{2}$ = 0.02), indicating that within-game learning differed between the games. Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p <.0001), while there was no significant difference between block scores for the other two games. This is indicative of the significant within game transfer within the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.  There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent. For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than agaisnt level-1 opponent. The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.

### Learning transfer

As a measure for learning transfer, we focus on participants’ scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response. A group of players with no experience of the game are expected to have scores not significantly different from 0. Any significantly positive group average scores would therefore reflect prior learning from past experiences.

We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests. As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89). In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001). This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).

Next, we explore whether learning transfer is moderated by the type of opponent and game similarity. Figure\ \@ref(fig: exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players. Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent. To test these hypotheses, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).

```{r exp1-early-rounds, include=FALSE}
dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
exp1_dat2_6 <- dat_26 %>% 
  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
      summarise(early_score = mean(score))

# Check group means and SDs by game and condition
group_by(exp1_dat2_6, game.f,condition) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )

```

```{r exp1-score-by-opp, fig.cap = "Average early scores by game and type of opponent faced", fig.align='center'}

p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Average Score rounds 2-6", xlab = "Games")

p2 + facet_grid(. ~ condition)

```

<!-- Table\ \@ref(tab:table-early-scores) shows the scores on rounds 2-6 for both type of opponents in each game. We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.  Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.  -->

For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p < 0.001) and NUMBERS (t(150) = 3.74, p < 0.001) . For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.

```{r ANOVA early exp1, include = FALSE, warning=FALSE}

exp1_early_anova <- afex :: aov_car(
  early_score ~ game.f*condition + Error(human_id/(game.f))
  , data=exp1_dat2_6
  , type = 3)

apa_lm1 <- apa_print(exp1_early_anova)

means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","NUM"))

```

```{r table-early-scores, include = FALSE, results = "asis"}
# apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
```

Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS). We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game. Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.

\newpage

# Second Experiment

## Methods

### Participants 
A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment. This was a new set of participants unrelated to those taking part in Experiment 1. The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes. Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.

### Procedure

The participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment. The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game. The first two games were identical to the ones used in the first experiment. In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper. Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal. If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses. Otherwise, the goalkeeper catches the ball and the player loses the round. There is no possibility of ties in this game. Figure XXXXXXXXX shows a snapshot of play in the shootout game. What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''. A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round. As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.

Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game. Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game. Participants start by facing one of the opponents in stage one, then face the other in stage two. This is repeated in the same order in stages 3 and 4. Which opponent they faced first was counterbalanced. All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.

In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round. During those 3 seconds, participants could not choose an option and had to wait for the timer to run out. A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent. After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round. Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction. The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.

Like games used in the first experiment, all the games used in this seeting have a unique MSNE consisting of randomising across actions. If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players. Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.

## Results

```{r load_exp2_data , include=FALSE}
dat_int <- read.csv(file = "../Experiment_2/dat_int_exp2.csv")
```

The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had the highest average score (M = 0.622, SD = 0.326).  The higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG. Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game. To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33). Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value < 0.0001 ;  FWG:  t(49) = 7.25 , p-value < 0.0001 ; Shootout: t(49) = 13.61, p-value < 0.0001 ).

Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.  We perform a two (condition: level-1 first, level-2 first) by two ( opponne type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.

```{r Anova exp 2, include= FALSE}
exp2_anova <- afex::aov_car(
  int_score ~ (game.f*interaction_lvl*condition.f*opp_type) + Error(human_id/(game.f*interaction_lvl*opp_type))
  , data = dat_int
  , type = 3
)

(ls0 <- lsmeans(exp2_anova, "game.f", by = "opp_type"))
(ls0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
apa_lm <- apa_print(exp2_anova)

```

```{r exp2-score-by-opp, fig.cap="Average scores per game by opponent type", fig.align="center"}
# p3 <- ggerrorplot(dat_int, x = "game.f", y = "int_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Scores per game", xlab = "Games")
# 
# p3 + facet_grid(. ~ opp_type)

p4 <- ggboxplot(dat_int, x = "game.f", y = "int_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","SHOOT"), fill="interaction_lvl",ylab = "Percentage score", xlab = "Games")

p4 + facet_grid(. ~ opp_type)

```

```{r exp2-anova, results = "asis", echo=FALSE, warning=FALSE}
# apa_table( apa_lm$table, caption = "ANOVA results for experiment 2", escape = FALSE)
```

There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, $\eta^{2}$ = 0.04,  p < .0001). To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).  We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the Shootout game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ). There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first). This means that neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance. There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,$\eta^{2}$ = 0.02,  p = .01). As can be seen in Figure\ \@ref(fig:exp2-score-by-opp), when facing level-1 agents, scores increase steadily after each game, with FWG score sgnificantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG  ( t(191) = 3.05, p = 0.01). There was no significant difference between average scores on any two games when facing level-2 agents however.

### Learning transfer

```{r , include=FALSE}
dat <- read.csv(file = "../Experiment_2/dat_exp2.csv")
```

As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random. Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.

```{r, include = FALSE}

#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########

dat_26 <- subset(dat,(round >1 & round < 7) & (interaction_lvl == "first interaction" ), drop =TRUE)

exp2_dat2_6 <- dat_26 %>% 
  group_by(human_id,condition.f,game.f,opp_type,confidence,difficulty) %>% 
      summarise(early_score = mean(adj_score))

# Check group means and SDs
group_by(exp2_dat2_6, game.f) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
group_by(exp2_dat2_6, game.f,opp_type) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
```

```{r exp2-early-scores, fig.cap="Average early round scores by game for experiment 2", fig.align="center"}
# plot scores per game 
p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Score rounds 2-6", xlab = "Games")

p2 + facet_grid(. ~ opp_type)
```

In Figure\ \@ref(fig:exp2-early-scores), we show the average score across participants in rounds 2-6 of the first interaction with the opponent for each game. These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first). For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types. (Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; Shootout:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; Shootout:  t(270) = 3.21, p =0.004 ). Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent. Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01). These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.

\newpage

# Computational modelling

To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent.  As a base model, we assume play is random, and each potential action is chosen with equal probability. Note that this corresponds to the Nash equilibrium strategy. In this section, we will go through the various models we have used and explain how they update what they learn about the game or the opponent

## Reinforcement Learning

We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state. We will use a simple temporal difference learning update rule:

$$ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) $$

Where $V_{t}(a)$ is the value associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t. Actions are chosen based on action values using a softmax choice rule.

We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm [@watkins1992q]. The update rule becomes:

$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$

Where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\gamma$ is the discount rate applied to future rewards. For instance, $Q(RS,P)$ denotes the value of taking action "Paper" this round if the player's last action was "Rock" and the opponent played "Scissors". This is a much richer model allowing the players to compute the values of actions conditional on past play.

In experiment 2, we allow this richer model to have a memory of the interaction. In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used. In another instance, we fit a model in which what was learned about an opponent in the first interaction is transfered to the first round of the second interaction, so there is a within-game trasnfer of Q-values allowed (QLS-within). We fit both models to all participant's data in the second experiment where both opponents are faced.

### EWA Models 
Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics]. EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning. Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that. In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward. The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.

Let's define some notation in order to write the update rule of the self-tuning EWA model. For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j). Strategies actually played by i in period t, are denoted $s_{i}(t)$, while the opponent's strategy at time t is denoted $s_{-i}(t)$. After playing  $s_{i}^{j}$ at time $t$, player i payoff is denoted $\pi_{i}(s_{i}^{j},s_{-i}(t))$, and the actual payoff the player received is $\pi_{i}(t)$.

The EWA model is based on updating "Attractions" for each action over time. For instance, the attraction of strategy $j$ to player $i$ at time $t$ is written $A_{i}^{j}(t)$. Future action choice probabilities are based on these attractions using the softmax playing rule:

$$P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} $$

The attractions are updated over every time step $t$ using the followng update rule :

$$ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} $$

Here, I(x,y) is the indicator function equal to 1 if $ x = y$ and 0 otherwise. A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince ($N(t-1)$) which is itself decaying by a wight $\phi$. The result is added to either the payoff received (when the indicator function is 0), or to $\delta$ times the foregone payoff (when indicator function is 1).   We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play [@cheung1994learning]. 
While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].

### ToM models

In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k. We use values of k  in ${0,1,2}$. We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer. In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability. In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between trasnfer)

Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game. In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).

We fit the above two models to experiment 1 data. In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive). And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.

In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive). In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood. Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.

## Experiment 1 modelling :

```{r load-comp-mod-distrib, include=FALSE}

All_comp_results <- read.csv(file="../All_results.csv")
exp1_comp_table <- table(All_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(All_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])

 #write.csv(exp1_comp_table ,file="exp1_comp_table ",row.names = TRUE)
 kable(exp1_comp_table)
```

```{r exp1-cum-score-plots, include=FALSE}

exp1_dat = read.csv("../exp1_data.csv")
# exp1_model_comp = read.csv("../exp1_model_comp.csv")

exp1_model_comp <- data.frame()
for(id in unique(exp1_dat$human_id)) {
  tdat <- subset(exp1_dat,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(All_comp_results, ID == id)
  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)

  best_model <- c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
  # 
  exp1_model_comp <- rbind(exp1_model_comp,
                       data.frame(
                         "human_id" = id,
                         "condition" = exp1_dat[exp1_dat$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

                       ))
}

datalist = list()
i = 0
new_dat <- setNames(data.frame(matrix(ncol = ncol(exp1_dat), nrow = 0)), colnames(exp1_dat))
for(id in unique(exp1_dat$human_id)) {
  i <- i+1
  tdat <- subset(exp1_dat,human_id == id)
  tdat$part_num <- i
  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
  datalist[[i]] <- tdat
}

# Merge all datasets into one 
new_dat <- dplyr::bind_rows(datalist)
# or new_dat <- data.table::rbindlist(datalist)

# Add column for time t
new_dat <- new_dat %>% group_by(exp1_dat$human_id) %>% mutate(t = row_number())

# Add best fitting model per participant
new_dat <- merge(new_dat, exp1_model_comp[, c("human_id", "Best_model")], by="human_id")

temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
dat_by_model <- temp %>% group_by(Best_model,t) %>% 
  summarize(model_acc_sum = mean(acc_sum))

```

Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.

```{r exp1-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 1", fig.align='center'}

#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
par(las=2) # make label text perpendicular to axis
par(mar=c(5,8,4,2)) # increase y-axis margin.
barplot(exp1_comp_table,
        horiz =TRUE, # rotate barplot for better visibility 
        las=1, # change orientation x axis labels 
        cex.names=0.8, # text label size
        legend = rownames(exp1_comp_table),
        beside =TRUE,
        xlab="Number of participants",
        args.legend=list( # positioning of legend box 
        x=ncol(exp1_comp_table) + 4,
        y=max(colSums(exp1_comp_table)) + 4,
        bty = "n")
 )

```

Next we compared the performance of players whose actions are consistent with each of our hypothesized models. Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1. We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play. EWA, QL and random players had, understandably the lowest performance.

```{r exp1-cumScores, fig.cap = "Average cumulative scores of participants in experiment 1 by best fitting model", fig.align='center'}
p5 <- ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
   geom_line(aes(color= Best_model))

p5+ labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
```

## Experiment 2

```{r, include = FALSE}

exp2_comp_results <- read.csv(file="../Experiment_2/exp2_results.csv")
# exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

 # write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
 kable(exp2_comp_table)
```

```{r exp2-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 2", fig.align='center'}

#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
par(las=2) # make label text perpendicular to axis
par(mar=c(5,8,4,2)) # increase y-axis margin.
barplot(exp2_comp_table,
        horiz =TRUE, # rotate barplot for better visibility 
        las=1, # change orientation x axis labels 
        cex.names=0.8, # text label size
        beside =TRUE,
        xlab="Number of participants",
        # legend = c("level-1 opp first","level-2 opp first"),
        legend = paste0(rownames(exp2_comp_table) , " faced first"),
        args.legend=list( # positioning of legend box 
        x=ncol(exp2_comp_table) + 6,
        y=max(colSums(exp2_comp_table)) +1,
        bty = "n")
 )

```

In experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that Q-learning with the aforementioned state-space was again more successful than the bayesian models in fitting player's action choices. In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) did not fit players observed data as well.

```{r, include=FALSE}

dat_exp2 = read.csv("../Experiment_2/data_exp2.csv")

#Adjust shootout score tor eflect easier game
dat_exp2$adj_score <- ifelse(as.character(dat_exp2$game) == "shootout", dat_exp2$score - 0.333, dat_exp2$score)

# Load data comparing models BIC for each participant 
model_comp_2 = read.csv("../Experiment_2/exp2_model_comp.csv")

datalist2 = list()
i = 0

#Build empty dataframe with same names as original data
exp2_cum_score <- setNames(data.frame(matrix(ncol = ncol(dat_exp2), nrow = 0)), colnames(dat_exp2))
for(id in unique(dat_exp2$human_id)) {
  i <- i+1
  tdat <- subset(dat_exp2,human_id == id)
  tdat$part_num <- i
  # NB : USE ADJUSTED SCORE IN SHOOTOUT
  tdat <- within(tdat, acc_sum <- cumsum(tdat$adj_score))
  datalist2[[i]] <- tdat
}

# Merge all datasets into one 
exp2_cum_score <- dplyr::bind_rows(datalist2)
# or exp2_cum_score <- data.table::rbindlist(datalist)

# Add column for time t
exp2_cum_score <- exp2_cum_score %>% group_by(human_id) %>% mutate(t = row_number())

# Participant number as a factor 
# tdat$part_num <- as.factor(tdat$part_num)

# Add best fitting model per participant
exp2_cum_score <- merge(exp2_cum_score, model_comp_2[, c("human_id", "Best_model_2")], by="human_id")

temp2 <- exp2_cum_score[,c("t","acc_sum","Best_model_2","condition","part_num")]
dat_by_model_2 <- temp2 %>% group_by(Best_model_2,t) %>% 
  summarize(avg_acc_sum = mean(acc_sum))

```

```{r exp2-cumScores, fig.cap = "Average cumulative scores of participants in experiment 2 by best fitting model", fig.align='center'}

 p8 <- ggplot(data = dat_by_model_2, aes(x = t, y=avg_acc_sum, group = Best_model_2)) + 
   geom_line(aes(color= Best_model_2)) +
  scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))

p8 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")

```

Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance. Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance, folowed by a model in which both within and between trasnfer of opponent models is allowed (BT). The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive). As expected, random play as well as self-tuning EWA were at the bottom of cumulative performance.

\newpage

# Discussion

In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies. We were interested in uncovering evidence for transfer and exploring whether it is modulated by the degree of similarity between games and the sophistication of the agent.

The results of our first online experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game. We found that using results on very early rounds is a better proxy for measuring transfer as it is not tainted by any within game learning. Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.

In the second online experiment, the paradigm was better suited to explore our main research question, related to learning transfer rather than within-game learning. Indeed, when facing two opponents sequentially, there are many more opportunities to test transfer than before. Indeed, there are 2 opportunities to transfer knowledge within each game, and a total of three games, which means 6 opportunities to test transfer. When we made players face only one type of opponent each, we only had two possible learning transfers to test. In that regard, the results on learning transfer confirmed prior findings from the first experiment. While there was no evidence of learning transfer across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed. We also found that learning transfer is modulated by the type of opponent faced. When the players faced the level-1 opponent, they were able to transfer learning. However, when they faced the level-2 opponent, there was weaker evidence for transfer. The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with. A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.

Coming back to evidence for learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis. The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout? what did the players learn exactly about the opponent strategy and what form did this learning take?

We will proceed by considering multiple potential answers to this question. First, maybe players simply learn spatial heuristics that allow them to perform better than chance. An example is a spatial heuristic that consists of choosing "weapons" in a particular order (for instance left to right). This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds. We took this into account in designing experiment two by randomly shuffling the spatial order of action choices in each round. Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.

A second possible hypothesis for learning the opponent’s strategy is the use of simple rules based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...). Our Q-learning with states as prior-round play model is a good proxy for this type of strategies. While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed. Indeed, learning the best action in a particular state cannot easily transfer to a new game since the state space is different and there is no simgle mapping between the state spaces of the initial and latter games. These rules would thereofre need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.

Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, would require many rounds of practice. Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents. After all, if players were using some type of associative learning or spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant. The fact that the degree of sophisitication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.

We are left with two possible explanations: First, it is possible that the players have uncovered a heuristic that allows them to beat the opponent without explicitly modelling their strategy, and is robust to transfer. Indeed, because of the cyclicality in action choices (e.g : Rock beats Scissors beats Paper beats Rock), it is possible to beat level-2 opponents most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round. This is a rule that wins and is also robust to transfer as it does not depend on action labels and even works in the dissimilar game.

The second explanation of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is. A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model. For instance, the player may think “My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be”. This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy. This type of learning would be deemed “explicit” in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them. It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004). Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).

Our second experimental design allows us to test whether the first explanation holds. Since there is a simple transferable heuristic that works agaisnt level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents. Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.

Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first intractions across games and using early rounds analysis. Based on our assumptions, we conclude that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the ourse of learning.

\newpage

# Conclusion

Our online experiments confirm behavioural game theory results, stating that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium. Moreover, we showed that participants do transfer their learning to new games with varying degrees of similarity. The most likely explanation as we saw is that players build a mental representation of their opponent strategy, rather than rely on associative learning or action-based heuristics. The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.

Having said that, there remains a high degree of heterogeneity between players. There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them. Moreover, the computational modelling shows that a significant number of players are still using random strategies in the games. Whether this ability depends on engagement with the experiment or on other characteristics of the learner is an open question that more research in the area would hope to answer.

\newpage

# References

```{r create_r-references}
r_refs(file = "Mendeley.bib")

```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2020-08-12 Report/draft_report_v1.tex
added BIC weights and new Bayes model

--- 2020-08-12 Report/draft_report_v1.Rmd
@@
----
-title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-shorttitle        : "Draft-1"
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
+%
+\documentclass[man,floatsintext]{apa6}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provides euro and other symbols
+\else % if luatex or xelatex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage[]{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\usepackage{xcolor}
+\usepackage{hyperref}
+\hypersetup{
+            pdftitle={Transfer of Learned Opponent Models in Zero Sum Games},
+            pdfauthor={Ismail Guennouni~\& Maarten Speekenbrink},
+            colorlinks=true,
+            linkcolor=blue,
+            filecolor=Maroon,
+            citecolor=Blue,
+            urlcolor=Blue,
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-author: 
-  - name          : "Ismail Guennouni"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
-    email         : "i.guennouni.17@ucl.ac.uk"
-  - name          : "Maarten Speekenbrink"
-    affiliation   : "1"
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 
-affiliation:
-  - id            : "1"
-    institution   : "Department of Experimental Psychology, University College London"
+\shorttitle{Draft-1}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Department of Experimental Psychology, University College London}
+\usepackage{csquotes}
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
 
-author_note: |
-  <!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+\usepackage{lineno}
+
+\linenumbers
+
+\title{Transfer of Learned Opponent Models in Zero Sum Games}
+\author{Ismail Guennouni\textsuperscript{1}~\& Maarten Speekenbrink\textsuperscript{1}}
+\date{}
+
+\authornote{
 
@@
 
-abstract: |
+Correspondence concerning this article should be addressed to Ismail Guennouni, Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom.
+E-mail: \href{mailto:i.guennouni.17@ucl.ac.uk}{\nolinkurl{i.guennouni.17@ucl.ac.uk}}}
+
+\abstract{
 Enter abstract here. Each new line herein must be indented, like this line.
 
-# keywords          : "keywords"
-# wordcount         : "X"
+}
 
-bibliography      : ["Mendeley.bib"]
-# csl               : "apa-6th-edition.csl"
+\begin{document}
+\maketitle
 
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-linkcolor         : "blue"
-mask              : no
-draft             : no
-fig_caption       : yes
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-documentclass     : "apa6"
-# classoption       : a4paper
-classoption       : man
-output            : papaja::apa6_pdf
----
-
-```{r load-packages, include = FALSE}
-library(papaja)
-require(knitr)
-require(citr)
-require(bookdown)
-# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
-library(tidyr)
-library(dplyr)
-library(MASS)
-library(ggpubr)
-library(afex)
-library(PairedData)
-library(multcompView)
-library(lsmeans)
-library(magick)
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-```
-
-```{r, include=FALSE} 
-options(tinytex.verbose = TRUE)
-```
-
-# Introduction
 Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
@@
 Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-@Lake2017 argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
+Lake, Ullman, Tenenbaum, \& Gershman (2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
-There is evidence that people learn models of their opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
+There is evidence that people learn models of their opponents when they play repeated economic games (Stahl \& Wilson, 1995), engage in bilateral negotiations (Baarslag, Hendrikx, Hindriks, \& Jonker, 2016), or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors (Weerd, Verbrugge, \& Verheij, 2012).
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities [@Woodruff] play a role in determining human behaviour.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Woodruff, Sciences, Brain, \& 1978, n.d.) play a role in determining human behaviour.
 In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
 More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to the task of opponent modelling.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to the task of opponent modelling.
 
 Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
-For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
+For instance, Ho, Camerer, \& Weigelt (1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
 They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-@knez2000increasing test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+Knez \& Camerer (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
 They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
@@
 
-@Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
+Juvina, Saleem, Martin, Gonzalez, \& Lebiere (2013) made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
 However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games [@cooper2003lessons; @Cooper2008] the researchers found that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+In a series of experiments using economic signalling games (Cooper \& Kagel, 2003, 2008) the researchers found that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
 They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
@@
 Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
-A notable exception is the effort by @Haruvy2012 to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
+A notable exception is the effort by Haruvy \& Stahl (2012) to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
 Participants played ten games, presented as 4x4 normal form (matrix payoffs).
@@
 They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on @stahl1995players, was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
+Their rule-learning model, based on Stahl \& Wilson (1995), was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
 
 Still, one of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
-@simon1972theories explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
-Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in 'level-k' theory, first adopted by @stahl1995players.
+The strategies implemented by the computer opponents had a style of play that was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+It is therefore important to have agents that \enquote{play like humans}, and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
+Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
+Instead, they will try to \enquote{satisfice} by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
+This concept finds its natural application in \enquote{level-k} theory, first adopted by Stahl \& Wilson (1995).
 It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment @arad201211.
+At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment Arad \& Rubinstein (2012).
 Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
@@
 In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit @goodie2012levels.
+The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit Goodie, Doshi, \& Young (2012).
 
@@
 The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
-For instance, @spiliopoulos2013strategic made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
-@shachat2004we made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
+For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
+Shachat \& Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
 They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
@@
 
-# Experiment 1
+\hypertarget{experiment-1}{%
+\section{Experiment 1}\label{experiment-1}}
 
-## Methods
+\hypertarget{methods}{%
+\subsection{Methods}\label{methods}}
 
-## Participants
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
@@
 
-## Procedure
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
@@
 The overall score of the players was translated into the bonus by making each point worth £0.02.
-This bonus is significant as players could increase the total payoff from the experiment by up to 60% assuming they'd won all rounds against the computer opponent.
-An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps).
+This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they'd won all rounds against the computer opponent.
+An example of the interface for the rock-paper-scissors game is provided in Figure~\ref{fig:feedback-rps}.
 
-```{r feedback-rps, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align='center'}
+\begin{figure}
 
-knitr::include_graphics("images/feedback_rps.png")
+{\centering \includegraphics{images/feedback_rps}
 
-```
+}
 
-## Results
+\caption{Screenshot of the feedback at the end of a round of Rock-Paper-Scissors}\label{fig:feedback-rps}
+\end{figure}
 
-```{r load-exp1-data, include=FALSE}
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
-dat1 <- read.csv("../data20180719.csv")
+\begin{figure}
 
-# transform 'winner' variable in numeric score
-dat1$score <- recode(dat1$winner, human = 1, tie = 0, ai = -1)
-# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
-dat1$block <- factor(as.numeric(cut(dat1$round,2)),labels =c("first half", "second half"))
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-avg-scores-game-1}
 
-# create a new variable "game.f" as a factor variable of games
-dat1$game.f <- factor(dat1$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))
+}
 
-#Group data by human_id and calculate mean score per block of each game.
-dat2 <- dat1 %>% 
-  group_by(human_id,condition,game,block,game.f) %>% 
-      summarize(block_score = mean(score))
+\caption{Average scores per game across conditions}\label{fig:exp1-avg-scores-game}
+\end{figure}
 
-# Group data by game and ID
-dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
-# head(dat3,6)
-
-# Subsetting scores data by game
-rps <- subset(dat3,  game.f == "RPS",game_score)
-fwg <- subset(dat3,  game.f == "FWG",game_score)
-num <- subset(dat3,  game.f == "NUM",game_score)
-# head(rps,6)
-```
-
-```{r exp1-avg-scores-game, fig.cap = "Average scores per game across conditions", fig.align="center"}
-# Plot average  scores per game 
-ggboxplot(dat3, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
-```
-
-Looking at the aggregate scores (See Figure\ \@ref(fig:exp1-avg-scores-game) ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
-Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value < 0.001 ;  FWG:  t(51) = 10.04 , p-value < 0.001 ; NUMBERS: t(51) = 7.17, p-value < 0.001).
+Looking at the aggregate scores (See Figure~\ref{fig:exp1-avg-scores-game} ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
+Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value \textless{} 0.001 ; FWG: t(51) = 10.04 , p-value \textless{} 0.001 ; NUMBERS: t(51) = 7.17, p-value \textless{} 0.001).
 
 To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game ( F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games.
+There was a main effect of Game ( F(2,100) = 8.54, \(\eta^{2}\) = 0.05, p \textless{} 0.001), showing that average scores varied significantly over the games.
 Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
 The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
-The main effect of Block ( F(1,50) = 22.51 , p < .001, $\eta^{2}$ = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning.
+The main effect of Block ( F(1,50) = 22.51 , p \textless{} .001, \(\eta^{2}\) = 0.03) shows that the average score in the first half of games (M = 0.29) was significantly lower than in the second half of the games played (M = 0.40), which translates to within-game learning.
 As players interact more with the agent, they learn how to win more often.
-The main effect of Condition (F(1,50) = 5.44, p = .024, $\eta^{2}$ = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
+The main effect of Condition (F(1,50) = 5.44, p = .024, \(\eta^{2}\) = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
 This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
 
-```{r exp1-3factor-plot, fig.cap = "Average scores by game, block and condition", fig.align = "center"}
+\begin{figure}
 
-# Plot results by game and block (for all 3 games, learning is happening) 
-p <- ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-3factor-plot-1}
 
-p + facet_grid(. ~ condition)
+}
 
-```
+\caption{Average scores by game, block and condition}\label{fig:exp1-3factor-plot}
+\end{figure}
 
-Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, $\eta^{2}$ = 0.02), indicating that within-game learning differed between the games.
-Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p <.0001), while there was no significant difference between block scores for the other two games.
+Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, \(\eta^{2}\) = 0.02), indicating that within-game learning differed between the games.
+Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p \textless{}.0001), while there was no significant difference between block scores for the other two games.
 This is indicative of the significant within game transfer within the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
-There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent.
+There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, \(\eta^{2}\) = 0.01), which indicates, as seen in Figure~\ref{fig:exp1-3factor-plot} that within-game learning changes across games also depend on the sophistication of the opponent.
 For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than agaisnt level-1 opponent.
@@
 
-### Learning transfer
+\hypertarget{learning-transfer}{%
+\subsubsection{Learning transfer}\label{learning-transfer}}
 
-As a measure for learning transfer, we focus on participants’ scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
+As a measure for learning transfer, we focus on participants' scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
 A group of players with no experience of the game are expected to have scores not significantly different from 0.
@@
 As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
-In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
+In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p \textless{} 0.0001).
 This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
@@
 Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-Figure\ \@ref(fig: exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players.
+Figure~@ref(fig: exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players.
 Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
@@
 
-```{r exp1-early-rounds, include=FALSE}
-dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
-exp1_dat2_6 <- dat_26 %>% 
-  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
-      summarise(early_score = mean(score))
+\begin{figure}
 
-# Check group means and SDs by game and condition
-group_by(exp1_dat2_6, game.f,condition) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-score-by-opp-1}
 
-```
+}
 
-```{r exp1-score-by-opp, fig.cap = "Average early scores by game and type of opponent faced", fig.align='center'}
+\caption{Average early scores by game and type of opponent faced}\label{fig:exp1-score-by-opp}
+\end{figure}
 
-p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Average Score rounds 2-6", xlab = "Games")
-
-p2 + facet_grid(. ~ condition)
-
-```
-
-<!-- Table\ \@ref(tab:table-early-scores) shows the scores on rounds 2-6 for both type of opponents in each game.
-We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
-Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
--->
-
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p < 0.001) and NUMBERS (t(150) = 3.74, p < 0.001) .
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p \textless{} 0.001) and NUMBERS (t(150) = 3.74, p \textless{} 0.001) .
 For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
-
-```{r ANOVA early exp1, include = FALSE, warning=FALSE}
-
-exp1_early_anova <- afex :: aov_car(
-  early_score ~ game.f*condition + Error(human_id/(game.f))
-  , data=exp1_dat2_6
-  , type = 3)
-
-apa_lm1 <- apa_print(exp1_early_anova)
-
-means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
-trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","NUM"))
-
-```
-
-```{r table-early-scores, include = FALSE, results = "asis"}
-# apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
-```
 
@@
 
-# Second Experiment
+\hypertarget{second-experiment}{%
+\section{Second Experiment}\label{second-experiment}}
 
-## Methods
+\hypertarget{methods-1}{%
+\subsection{Methods}\label{methods-1}}
 
-### Participants 
+\hypertarget{participants-1}{%
+\subsubsection{Participants}\label{participants-1}}
+
 A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
@@
 
-### Procedure
+\hypertarget{procedure-1}{%
+\subsubsection{Procedure}\label{procedure-1}}
 
@@
 Figure XXXXXXXXX shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
+What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose \enquote{'right}' in the next round, we can win by both choosing \enquote{'left}' and \enquote{'center}'.
 A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
@@
 
-## Results
-
-```{r load_exp2_data , include=FALSE}
-dat_int <- read.csv(file = "../Experiment_2/dat_int_exp2.csv")
-```
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
 
@@
 The higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
-Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value < 0.0001 ;  FWG:  t(49) = 7.25 , p-value < 0.0001 ; Shootout: t(49) = 13.61, p-value < 0.0001 ).
+Indeed, a player not aiming to uncover the opponent's strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
+To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
+Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value \textless{} 0.0001 ; FWG: t(49) = 7.25 , p-value \textless{} 0.0001 ; Shootout: t(49) = 13.61, p-value \textless{} 0.0001 ).
 
@@
 
-```{r Anova exp 2, include= FALSE}
-exp2_anova <- afex::aov_car(
-  int_score ~ (game.f*interaction_lvl*condition.f*opp_type) + Error(human_id/(game.f*interaction_lvl*opp_type))
-  , data = dat_int
-  , type = 3
-)
+\begin{figure}
 
-(ls0 <- lsmeans(exp2_anova, "game.f", by = "opp_type"))
-(ls0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
-apa_lm <- apa_print(exp2_anova)
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-score-by-opp-1}
 
-```
+}
 
-```{r exp2-score-by-opp, fig.cap="Average scores per game by opponent type", fig.align="center"}
-# p3 <- ggerrorplot(dat_int, x = "game.f", y = "int_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Scores per game", xlab = "Games")
-# 
-# p3 + facet_grid(. ~ opp_type)
+\caption{Average scores per game by opponent type}\label{fig:exp2-score-by-opp}
+\end{figure}
 
-p4 <- ggboxplot(dat_int, x = "game.f", y = "int_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","SHOOT"), fill="interaction_lvl",ylab = "Percentage score", xlab = "Games")
-
-p4 + facet_grid(. ~ opp_type)
-
-```
-
-```{r exp2-anova, results = "asis", echo=FALSE, warning=FALSE}
-# apa_table( apa_lm$table, caption = "ANOVA results for experiment 2", escape = FALSE)
-```
-
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, $\eta^{2}$ = 0.04,  p < .0001).
+There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, \(\eta^{2}\) = 0.04, p \textless{} .0001).
 To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
@@
 This means that neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
-There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,$\eta^{2}$ = 0.02,  p = .01).
-As can be seen in Figure\ \@ref(fig:exp2-score-by-opp), when facing level-1 agents, scores increase steadily after each game, with FWG score sgnificantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG  ( t(191) = 3.05, p = 0.01).
+There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,\(\eta^{2}\) = 0.02, p = .01).
+As can be seen in Figure~\ref{fig:exp2-score-by-opp}, when facing level-1 agents, scores increase steadily after each game, with FWG score sgnificantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG ( t(191) = 3.05, p = 0.01).
 There was no significant difference between average scores on any two games when facing level-2 agents however.
 
-### Learning transfer
-
-```{r , include=FALSE}
-dat <- read.csv(file = "../Experiment_2/dat_exp2.csv")
-```
+\hypertarget{learning-transfer-1}{%
+\subsubsection{Learning transfer}\label{learning-transfer-1}}
 
@@
 
-```{r, include = FALSE}
+\begin{figure}
 
-#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-early-scores-1}
 
-dat_26 <- subset(dat,(round >1 & round < 7) & (interaction_lvl == "first interaction" ), drop =TRUE)
+}
 
-exp2_dat2_6 <- dat_26 %>% 
-  group_by(human_id,condition.f,game.f,opp_type,confidence,difficulty) %>% 
-      summarise(early_score = mean(adj_score))
+\caption{Average early round scores by game for experiment 2}\label{fig:exp2-early-scores}
+\end{figure}
 
-# Check group means and SDs
-group_by(exp2_dat2_6, game.f) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-group_by(exp2_dat2_6, game.f,opp_type) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-```
-
-```{r exp2-early-scores, fig.cap="Average early round scores by game for experiment 2", fig.align="center"}
-# plot scores per game 
-p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Score rounds 2-6", xlab = "Games")
-
-p2 + facet_grid(. ~ opp_type)
-```
-
-In Figure\ \@ref(fig:exp2-early-scores), we show the average score across participants in rounds 2-6 of the first interaction with the opponent for each game.
+In Figure~\ref{fig:exp2-early-scores}, we show the average score across participants in rounds 2-6 of the first interaction with the opponent for each game.
 These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
 For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
-(Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; Shootout:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; Shootout:  t(270) = 3.21, p =0.004 ).
+(Level-1 opponent: FWG: t(270) = 4.99, p \textless{} 0.0001; Shootout: t(270) = 6.66, p \textless{} 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p \textless{} 0.0001; Shootout: t(270) = 3.21, p =0.004 ).
 Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
@@
 
-# Computational modelling
+\hypertarget{computational-modelling}{%
+\section{Computational modelling}\label{computational-modelling}}
 
@@
 
-## Reinforcement Learning
+\hypertarget{reinforcement-learning}{%
+\subsection{Reinforcement Learning}\label{reinforcement-learning}}
 
@@
 
-$$ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) $$
+\[ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) \]
 
-Where $V_{t}(a)$ is the value associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
+Where \(V_{t}(a)\) is the value associated with action \(a\) at time \(t\), \(\alpha\) is the learning rate and \(R_{t}\) the reward at time t.
 Actions are chosen based on action values using a softmax choice rule.
 
-We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm [@watkins1992q]. The update rule becomes:
+We extend this very simple model by adding a state space that consists of last round human and agent play.
+This is akin to using a Q-learning algorithm (Watkins \& Dayan, 1992).
+The update rule becomes:
 
-$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$
+\[ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) \]
 
-Where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\gamma$ is the discount rate applied to future rewards.
-For instance, $Q(RS,P)$ denotes the value of taking action "Paper" this round if the player's last action was "Rock" and the opponent played "Scissors".
+Where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), \(\gamma\) is the discount rate applied to future rewards.
+For instance, \(Q(RS,P)\) denotes the value of taking action \enquote{Paper} this round if the player's last action was \enquote{Rock} and the opponent played \enquote{Scissors}.
 This is a much richer model allowing the players to compute the values of actions conditional on past play.
@@
 
-### EWA Models 
-Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics].
+\hypertarget{ewa-models}{%
+\subsubsection{EWA Models}\label{ewa-models}}
+
+Next, we use a self-tuning Experience Weighted attraction model (Ho, Camerer, \& Chong, 2004).
 EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning.
@@
 Let's define some notation in order to write the update rule of the self-tuning EWA model.
-For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j).
-Strategies actually played by i in period t, are denoted $s_{i}(t)$, while the opponent's strategy at time t is denoted $s_{-i}(t)$.
-After playing  $s_{i}^{j}$ at time $t$, player i payoff is denoted $\pi_{i}(s_{i}^{j},s_{-i}(t))$, and the actual payoff the player received is $\pi_{i}(t)$.
+For player i, there are \(m_{i}\) strategies, denoted \(s_{i}^{j}\) (i.e player i's strategy number j).
+Strategies actually played by i in period t, are denoted \(s_{i}(t)\), while the opponent's strategy at time t is denoted \(s_{-i}(t)\).
+After playing \(s_{i}^{j}\) at time \(t\), player i payoff is denoted \(\pi_{i}(s_{i}^{j},s_{-i}(t))\), and the actual payoff the player received is \(\pi_{i}(t)\).
 
-The EWA model is based on updating "Attractions" for each action over time.
-For instance, the attraction of strategy $j$ to player $i$ at time $t$ is written $A_{i}^{j}(t)$.
+The EWA model is based on updating \enquote{Attractions} for each action over time.
+For instance, the attraction of strategy \(j\) to player \(i\) at time \(t\) is written \(A_{i}^{j}(t)\).
 Future action choice probabilities are based on these attractions using the softmax playing rule:
 
-$$P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} $$
+\[P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} \]
 
-The attractions are updated over every time step $t$ using the followng update rule :
+The attractions are updated over every time step \(t\) using the followng update rule :
 
-$$ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} $$
+\[ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} \]
 
-Here, I(x,y) is the indicator function equal to 1 if $ x = y$ and 0 otherwise.
-A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince ($N(t-1)$) which is itself decaying by a wight $\phi$.
-The result is added to either the payoff received (when the indicator function is 0), or to $\delta$ times the foregone payoff (when indicator function is 1).
-We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play [@cheung1994learning].
-While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].
+Here, I(x,y) is the indicator function equal to 1 if \$ x = y\$ and 0 otherwise.
+A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince (\(N(t-1)\)) which is itself decaying by a wight \(\phi\).
+The result is added to either the payoff received (when the indicator function is 0), or to \(\delta\) times the foregone payoff (when indicator function is 1).
+We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play (Cheung \& Friedman, 1994).
+While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Ho et al., 2004).
 
-### ToM models
+\hypertarget{tom-models}{%
+\subsubsection{ToM models}\label{tom-models}}
 
 In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
-We use values of k  in ${0,1,2}$.
+We use values of k in \({0,1,2}\).
 We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
@@
 
-## Experiment 1 modelling :
+\hypertarget{experiment-1-modelling}{%
+\subsection{Experiment 1 modelling :}\label{experiment-1-modelling}}
 
-```{r load-comp-mod-distrib, include=FALSE}
+Figure~\ref{fig:exp1-comp-models} shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
 
-All_comp_results <- read.csv(file="../All_results.csv")
-exp1_comp_table <- table(All_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(All_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])
+\begin{figure}
 
- #write.csv(exp1_comp_table ,file="exp1_comp_table ",row.names = TRUE)
- kable(exp1_comp_table)
-```
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-comp-models-1}
 
-```{r exp1-cum-score-plots, include=FALSE}
-
-exp1_dat = read.csv("../exp1_data.csv")
-# exp1_model_comp = read.csv("../exp1_model_comp.csv")
-
-exp1_model_comp <- data.frame()
-for(id in unique(exp1_dat$human_id)) {
-  tdat <- subset(exp1_dat,human_id == id)
-  tot_score <- sum(tdat$score)
-  tot_time <- sum(tdat$human_rt)
-  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
-  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
-  tr_score <- sum(early_dat$score)
-  id_results <- subset(All_comp_results, ID == id)
-  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)
-
-  best_model <- c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
-  # 
-  exp1_model_comp <- rbind(exp1_model_comp,
-                       data.frame(
-                         "human_id" = id,
-                         "condition" = exp1_dat[exp1_dat$human_id==id,"condition"][1],
-                         "Early_game_score" = tr_score,
-                         "Total_score" = tot_score,
-                         "Best_model" = best_model,
-                         "Total_time" = sum(tdat$human_rt),
-                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
-                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
-
-                       ))
 }
 
-datalist = list()
-i = 0
-new_dat <- setNames(data.frame(matrix(ncol = ncol(exp1_dat), nrow = 0)), colnames(exp1_dat))
-for(id in unique(exp1_dat$human_id)) {
-  i <- i+1
-  tdat <- subset(exp1_dat,human_id == id)
-  tdat$part_num <- i
-  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
-  datalist[[i]] <- tdat
-}
-
-# Merge all datasets into one 
-new_dat <- dplyr::bind_rows(datalist)
-# or new_dat <- data.table::rbindlist(datalist)
-
-# Add column for time t
-new_dat <- new_dat %>% group_by(exp1_dat$human_id) %>% mutate(t = row_number())
-
-# Add best fitting model per participant
-new_dat <- merge(new_dat, exp1_model_comp[, c("human_id", "Best_model")], by="human_id")
-
-temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
-dat_by_model <- temp %>% group_by(Best_model,t) %>% 
-  summarize(model_acc_sum = mean(acc_sum))
-
-```
-
-Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
-
-```{r exp1-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 1", fig.align='center'}
-
-#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
-par(las=2) # make label text perpendicular to axis
-par(mar=c(5,8,4,2)) # increase y-axis margin.
-barplot(exp1_comp_table,
-        horiz =TRUE, # rotate barplot for better visibility 
-        las=1, # change orientation x axis labels 
-        cex.names=0.8, # text label size
-        legend = rownames(exp1_comp_table),
-        beside =TRUE,
-        xlab="Number of participants",
-        args.legend=list( # positioning of legend box 
-        x=ncol(exp1_comp_table) + 4,
-        y=max(colSums(exp1_comp_table)) + 4,
-        bty = "n")
- )
-
-```
+\caption{Histogram of best fitting computational models by condition for experiment 1}\label{fig:exp1-comp-models}
+\end{figure}
 
 Next we compared the performance of players whose actions are consistent with each of our hypothesized models.
-Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
+Figure~\ref{fig:exp1-cumScores} shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
 We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play.
@@
 
-```{r exp1-cumScores, fig.cap = "Average cumulative scores of participants in experiment 1 by best fitting model", fig.align='center'}
-p5 <- ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
-   geom_line(aes(color= Best_model))
+\begin{figure}
 
-p5+ labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
-```
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-cumScores-1}
 
-## Experiment 2
+}
 
-```{r, include = FALSE}
+\caption{Average cumulative scores of participants in experiment 1 by best fitting model}\label{fig:exp1-cumScores}
+\end{figure}
 
-exp2_comp_results <- read.csv(file="../Experiment_2/exp2_results.csv")
-# exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+\hypertarget{experiment-2}{%
+\subsection{Experiment 2}\label{experiment-2}}
 
-exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+\begin{figure}
 
- # write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
- kable(exp2_comp_table)
-```
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-comp-models-1}
 
-```{r exp2-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 2", fig.align='center'}
+}
 
-#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
-par(las=2) # make label text perpendicular to axis
-par(mar=c(5,8,4,2)) # increase y-axis margin.
-barplot(exp2_comp_table,
-        horiz =TRUE, # rotate barplot for better visibility 
-        las=1, # change orientation x axis labels 
-        cex.names=0.8, # text label size
-        beside =TRUE,
-        xlab="Number of participants",
-        # legend = c("level-1 opp first","level-2 opp first"),
-        legend = paste0(rownames(exp2_comp_table) , " faced first"),
-        args.legend=list( # positioning of legend box 
-        x=ncol(exp2_comp_table) + 6,
-        y=max(colSums(exp2_comp_table)) +1,
-        bty = "n")
- )
+\caption{Histogram of best fitting computational models by condition for experiment 2}\label{fig:exp2-comp-models}
+\end{figure}
 
-```
-
-In experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that Q-learning with the aforementioned state-space was again more successful than the bayesian models in fitting player's action choices.
+In experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that Q-learning with the aforementioned state-space was again more successful than the bayesian models in fitting player's action choices.
 In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) did not fit players observed data as well.
 
-```{r, include=FALSE}
+\begin{figure}
 
-dat_exp2 = read.csv("../Experiment_2/data_exp2.csv")
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-cumScores-1}
 
-#Adjust shootout score tor eflect easier game
-dat_exp2$adj_score <- ifelse(as.character(dat_exp2$game) == "shootout", dat_exp2$score - 0.333, dat_exp2$score)
-
-# Load data comparing models BIC for each participant 
-model_comp_2 = read.csv("../Experiment_2/exp2_model_comp.csv")
-
-datalist2 = list()
-i = 0
-
-#Build empty dataframe with same names as original data
-exp2_cum_score <- setNames(data.frame(matrix(ncol = ncol(dat_exp2), nrow = 0)), colnames(dat_exp2))
-for(id in unique(dat_exp2$human_id)) {
-  i <- i+1
-  tdat <- subset(dat_exp2,human_id == id)
-  tdat$part_num <- i
-  # NB : USE ADJUSTED SCORE IN SHOOTOUT
-  tdat <- within(tdat, acc_sum <- cumsum(tdat$adj_score))
-  datalist2[[i]] <- tdat
 }
 
-# Merge all datasets into one 
-exp2_cum_score <- dplyr::bind_rows(datalist2)
-# or exp2_cum_score <- data.table::rbindlist(datalist)
+\caption{Average cumulative scores of participants in experiment 2 by best fitting model}\label{fig:exp2-cumScores}
+\end{figure}
 
-# Add column for time t
-exp2_cum_score <- exp2_cum_score %>% group_by(human_id) %>% mutate(t = row_number())
-
-# Participant number as a factor 
-# tdat$part_num <- as.factor(tdat$part_num)
-
-# Add best fitting model per participant
-exp2_cum_score <- merge(exp2_cum_score, model_comp_2[, c("human_id", "Best_model_2")], by="human_id")
-
-temp2 <- exp2_cum_score[,c("t","acc_sum","Best_model_2","condition","part_num")]
-dat_by_model_2 <- temp2 %>% group_by(Best_model_2,t) %>% 
-  summarize(avg_acc_sum = mean(acc_sum))
-
-```
-
-```{r exp2-cumScores, fig.cap = "Average cumulative scores of participants in experiment 2 by best fitting model", fig.align='center'}
-
- p8 <- ggplot(data = dat_by_model_2, aes(x = t, y=avg_acc_sum, group = Best_model_2)) + 
-   geom_line(aes(color= Best_model_2)) +
-  scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))
-
-p8 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
-
-```
-
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
 Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance, folowed by a model in which both within and between trasnfer of opponent models is allowed (BT).
@@
 
-# Discussion
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
-An example is a spatial heuristic that consists of choosing "weapons" in a particular order (for instance left to right).
+An example is a spatial heuristic that consists of choosing \enquote{weapons} in a particular order (for instance left to right).
 This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
@@
 
-A second possible hypothesis for learning the opponent’s strategy is the use of simple rules based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
+A second possible hypothesis for learning the opponent's strategy is the use of simple rules based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc\ldots{}).
 Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
@@
 A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
-For instance, the player may think “My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be”.
+For instance, the player may think \enquote{My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be}.
 This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
-This type of learning would be deemed “explicit” in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
+This type of learning would be deemed \enquote{explicit} in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
 It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
@@
 
-# Conclusion
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
@@
 
-# References
-
-```{r create_r-references}
-r_refs(file = "Mendeley.bib")
-
-```
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 
-<div id = "refs"></div>
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-arad201211}{}%
+Arad, A., \& Rubinstein, A. (2012). The 11-20 money request game: A level-k reasoning study. \emph{American Economic Review}, \emph{102}(7), 3561--3573.
+
+\leavevmode\hypertarget{ref-baarslag2016learning}{}%
+Baarslag, T., Hendrikx, M.
+J.
+C., Hindriks, K.
+V., \& Jonker, C.
+M.
+(2016).
+Learning about the opponent in automated bilateral negotiation: a comprehensive survey of opponent modeling techniques.
+\emph{Autonomous Agents and Multi-Agent Systems}, \emph{30}(5), 849--898.
+
+\leavevmode\hypertarget{ref-camerer1997experience}{}%
+Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
+
+\leavevmode\hypertarget{ref-cheung1994learning}{}%
+Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
+
+\leavevmode\hypertarget{ref-cooper2003lessons}{}%
+Cooper, D. J., \& Kagel, J. H. (2003). Lessons learned: generalizing learning across games. \emph{American Economic Review}, \emph{93}(2), 202--207.
+
+\leavevmode\hypertarget{ref-Cooper2008}{}%
+Cooper, D.
+J., \& Kagel, J.
+H.
+(2008).
+Learning and transfer in signaling games.
+\emph{Economic Theory}, \emph{34}(3), 415--439.
+doi:\href{https://doi.org/10.1007/s00199-006-0192-5}{10.1007/s00199-006-0192-5}
+
+\leavevmode\hypertarget{ref-goodie2012levels}{}%
+Goodie, A. S., Doshi, P., \& Young, D. L. (2012). Levels of theory-of-mind reasoning in competitive games. \emph{Journal of Behavioral Decision Making}, \emph{25}(1), 95--108.
+
+\leavevmode\hypertarget{ref-Haruvy2012}{}%
+Haruvy, E., \& Stahl, D.
+O.
+(2012).
+Between-game rule learning in dissimilar symmetric normal-form games.
+\emph{Games and Economic Behavior}, \emph{74}(1), 208--221.
+doi:\href{https://doi.org/10.1016/j.geb.2011.06.001}{10.1016/j.geb.2011.06.001}
+
+\leavevmode\hypertarget{ref-ho2004economics}{}%
+Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). The economics of learning models: A self-tuning theory of learning in games.
+
+\leavevmode\hypertarget{ref-ho1998iterated}{}%
+Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
+
+\leavevmode\hypertarget{ref-Juvina2013}{}%
+Juvina, I., Saleem, M., Martin, J.
+M., Gonzalez, C., \& Lebiere, C.
+(2013).
+Reciprocal trust mediates deep transfer of learning between games of strategic interaction.
+\emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215.
+doi:\href{https://doi.org/10.1016/j.obhdp.2012.09.004}{10.1016/j.obhdp.2012.09.004}
+
+\leavevmode\hypertarget{ref-knez2000increasing}{}%
+Knez, M., \& Camerer, C.
+(2000).
+Increasing cooperation in prisoner's dilemmas by establishing a precedent of efficiency in coordination games.
+\emph{Organizational Behavior and Human Decision Processes}, \emph{82}(2), 194--216.
+
+\leavevmode\hypertarget{ref-Lake2017}{}%
+Lake, B.
+M., Ullman, T.
+D., Tenenbaum, J.
+B., \& Gershman, S.
+J.
+(2017).
+Building machines that learn and think like people.
+\emph{Behavioral and Brain Sciences}, \emph{40}.
+doi:\href{https://doi.org/10.1017/S0140525X16001837}{10.1017/S0140525X16001837}
+
+\leavevmode\hypertarget{ref-mertens1990repeated}{}%
+Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+
+\leavevmode\hypertarget{ref-shachat2004we}{}%
+Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
+
+\leavevmode\hypertarget{ref-simon1972theories}{}%
+Simon, H. A. (1972). Theories of bounded rationality. \emph{Decision and Organization}, \emph{1}(1), 161--176.
+
+\leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
+Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
+
+\leavevmode\hypertarget{ref-stahl1995players}{}%
+Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
+
+\leavevmode\hypertarget{ref-watkins1992q}{}%
+Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
+
+\leavevmode\hypertarget{ref-de2012higher}{}%
+Weerd, H.
+de, Verbrugge, R., \& Verheij, B.
+(2012).
+Higher-order social cognition in rock-paper-scissors: A simulation study.
+In \emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3} (pp.
+1195--1196).
+
+\leavevmode\hypertarget{ref-Woodruff}{}%
+Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). Does the chimpanzee have a theory of mind.
+
+\leavevmode\hypertarget{ref-arad201211}{}%
+Arad, A., \& Rubinstein, A. (2012). The 11-20 money request game: A level-k reasoning study. \emph{American Economic Review}, \emph{102}(7), 3561--3573.
+
+\leavevmode\hypertarget{ref-baarslag2016learning}{}%
+Baarslag, T., Hendrikx, M.
+J.
+C., Hindriks, K.
+V., \& Jonker, C.
+M.
+(2016).
+Learning about the opponent in automated bilateral negotiation: a comprehensive survey of opponent modeling techniques.
+\emph{Autonomous Agents and Multi-Agent Systems}, \emph{30}(5), 849--898.
+
+\leavevmode\hypertarget{ref-camerer1997experience}{}%
+Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
+
+\leavevmode\hypertarget{ref-cheung1994learning}{}%
+Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
+
+\leavevmode\hypertarget{ref-cooper2003lessons}{}%
+Cooper, D. J., \& Kagel, J. H. (2003). Lessons learned: generalizing learning across games. \emph{American Economic Review}, \emph{93}(2), 202--207.
+
+\leavevmode\hypertarget{ref-Cooper2008}{}%
+Cooper, D.
+J., \& Kagel, J.
+H.
+(2008).
+Learning and transfer in signaling games.
+\emph{Economic Theory}, \emph{34}(3), 415--439.
+doi:\href{https://doi.org/10.1007/s00199-006-0192-5}{10.1007/s00199-006-0192-5}
+
+\leavevmode\hypertarget{ref-goodie2012levels}{}%
+Goodie, A. S., Doshi, P., \& Young, D. L. (2012). Levels of theory-of-mind reasoning in competitive games. \emph{Journal of Behavioral Decision Making}, \emph{25}(1), 95--108.
+
+\leavevmode\hypertarget{ref-Haruvy2012}{}%
+Haruvy, E., \& Stahl, D.
+O.
+(2012).
+Between-game rule learning in dissimilar symmetric normal-form games.
+\emph{Games and Economic Behavior}, \emph{74}(1), 208--221.
+doi:\href{https://doi.org/10.1016/j.geb.2011.06.001}{10.1016/j.geb.2011.06.001}
+
+\leavevmode\hypertarget{ref-ho2004economics}{}%
+Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). The economics of learning models: A self-tuning theory of learning in games.
+
+\leavevmode\hypertarget{ref-ho1998iterated}{}%
+Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
+
+\leavevmode\hypertarget{ref-Juvina2013}{}%
+Juvina, I., Saleem, M., Martin, J.
+M., Gonzalez, C., \& Lebiere, C.
+(2013).
+Reciprocal trust mediates deep transfer of learning between games of strategic interaction.
+\emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215.
+doi:\href{https://doi.org/10.1016/j.obhdp.2012.09.004}{10.1016/j.obhdp.2012.09.004}
+
+\leavevmode\hypertarget{ref-knez2000increasing}{}%
+Knez, M., \& Camerer, C.
+(2000).
+Increasing cooperation in prisoner's dilemmas by establishing a precedent of efficiency in coordination games.
+\emph{Organizational Behavior and Human Decision Processes}, \emph{82}(2), 194--216.
+
+\leavevmode\hypertarget{ref-Lake2017}{}%
+Lake, B.
+M., Ullman, T.
+D., Tenenbaum, J.
+B., \& Gershman, S.
+J.
+(2017).
+Building machines that learn and think like people.
+\emph{Behavioral and Brain Sciences}, \emph{40}.
+doi:\href{https://doi.org/10.1017/S0140525X16001837}{10.1017/S0140525X16001837}
+
+\leavevmode\hypertarget{ref-mertens1990repeated}{}%
+Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+
+\leavevmode\hypertarget{ref-shachat2004we}{}%
+Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
+
+\leavevmode\hypertarget{ref-simon1972theories}{}%
+Simon, H. A. (1972). Theories of bounded rationality. \emph{Decision and Organization}, \emph{1}(1), 161--176.
+
+\leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
+Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
+
+\leavevmode\hypertarget{ref-stahl1995players}{}%
+Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
+
+\leavevmode\hypertarget{ref-watkins1992q}{}%
+Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
+
+\leavevmode\hypertarget{ref-de2012higher}{}%
+Weerd, H.
+de, Verbrugge, R., \& Verheij, B.
+(2012).
+Higher-order social cognition in rock-paper-scissors: A simulation study.
+In \emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3} (pp.
+1195--1196).
+
+\leavevmode\hypertarget{ref-Woodruff}{}%
+Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). Does the chimpanzee have a theory of mind.
+
 \endgroup
+
+\end{document}

### 2020-08-12 comp_model_1019.Rmd
added BIC weights and new Bayes model

---
title: "opponent modelling"
author: "Ismail Guennouni & Maarten Speekenbrink"
date: "1 November 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

## Reading data

```{r}
dat <- read.csv("data20180719.csv")
#dat <- read.csv("test_data.csv")
```

## Preprosessing and transforming data

```{r}
# using some functions from the 'tidyverse' (also for me to get use to them ;-)
library(tidyr)
library(dplyr)
library(DEoptim)
library(optimParallel)
library(ggpubr)

# create a new data.frame in a 'wide format'
# widedata <- dat %>%
#   unite(game_block,game,block) %>% # this creates a new variable which combines game and block
#     group_by(human_id,condition,game_block) %>% # let the functions know you want to separate things by ID, condition, and game_block
#       summarize(mean_score = mean(score)) %>% # compute average score (i.e wins - losses)
#         spread(game_block,mean_score) # reformat in the 'wide' format
# # save the data file as a .csv to use in e.g. SPSS
# write.csv(widedata,row.names=FALSE,file="scores_wide.csv")

```

```{r estimate-models, cache=TRUE}
# read in the various files which 
rps_predict_opp <- read.csv("rps_predict_opp.csv")
fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
numbers_predict_opp <- read.csv("numbers_predict_opp.csv")

# transform 'winner' variable in numeric score
dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat$block <- as.numeric(cut(dat$round,2))

# recode actions to make them equal to the codes in these files
dat$h_action <- recode(dat$human_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
dat$a_action <- recode(dat$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")

write.csv(dat,file = "exp1_data.csv", row.names = FALSE)

# logit tranformation
my_logit <- function(x) {
  ret <- log(x/(1-x))
  ret[x==0] <- -Inf
  ret[x==1] <- Inf 
  return(ret)
}

# inverse logit transformation
my_logistic <- function(x) {
  ret <- 1/(1+exp(-x))
  ret[x == -Inf] <- 0.0
  ret[x == Inf] <- 1.0
  return(ret)
}

```

#### New work

## Fitting simple Bayesian learning model with flat prior

#Fit a bayesian model to observed human play. Prior is vector of possible level-k opponent strategies.
```{r}
# Function to produce best reponse to ai_action 
best_response <- function(game,ai_action){
  if (game == "rps"){
    if (ai_action == "R") {return("P")}
    else if (ai_action == "P") {return("S")}
    else if (ai_action == "S") {return("R")}
  } else if (game == "fwg"){ 
    if (ai_action == "F") {return("W")}
    else if (ai_action == "W") {return("G")}
    else if (ai_action == "G") {return("F")}
  } else if (game == "numbers") {
    if (ai_action == "1") {return("2")}
    else if (ai_action == "2") {return("3")}
    else if (ai_action == "3") {return("4")}
    else if (ai_action == "4") {return("5")}
    else if (ai_action == "5") {return("1")}
  }
}

exp1_ToM <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {

  # dat = data subset for one participant
  # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
  # return = -2logLik 
  # or "likelihood_by_trial" vector  (for later plotting, etc)
  # opp_mod_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise.

  # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
  # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
  theta <- par[1]
  eps <- par[2]

  num_strat = length(opp_strategy_vec)

  # Load tables predicting oppponent move
  rps_predict_opp <- read.csv("rps_predict_opp.csv")
  fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
  numbers_predict_opp <- read.csv("numbers_predict_opp.csv")

  #lik_opp is a vector that holds and update probability distribution of opp strategy given actions.
  lik_opp <- matrix(0.0,num_strat, nrow(data))
  # Initiate prior vector as uniform
  opp_prior_vec <-rep(1/num_strat, num_strat)

  lik_hum <- matrix(0.0,nrow(data))
  # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
  br_hum <- rep(NA,num_strat)

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)

    if(t_game == "numbers") nopts <- 5 else nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      pred_opp <- NA
      lik_hum[t] <- 1/nopts
      ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer, reset prior to uniform)
      if (!(opp_mod_transfer)) {
        opp_prior_vec <- rep(1/num_strat, num_strat)
        lik_opp[,t] <- opp_prior_vec
        }

    # Rounds after first
    } else {
      # get prediction of opponent action from CSV files
      for (strategy in opp_strategy_vec) {
        k = match(strategy,opp_strategy_vec)
        pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])

        # Given opponent action predicted, what would be human action best response for each opp strat
        br_hum[[k]] <- best_response(t_game,as.character(pred_opp))

        # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
        if(as.character(data[t,"a_action"]) == pred_opp) {
          lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
        } else {
          lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
        }
      }
      # Get which opponent strategy human current actn maps to (if index = 0 then human current action is br to level-0 comp_strat...)
      indices <- which(br_hum %in% as.character(data[t,"h_action"]))

      # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
      # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
      if(length(indices) == 0){
        lik_hum[t] <- eps/nopts
      # if same br action for multiple possible ai opponents, add probabilities 
      } else {
        lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
      }
      # Standardising the probabilities and updating prior
      lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
      opp_prior_vec <- lik_opp[,t]
    }
    # for debugging uncomment the line below
    #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"\n")
  }
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)
}

# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
# exp1_ToM(c(0.9,0.99),data,c("level0","level1","level2"),"-2loglik",FALSE)
```

```{r}
# rps_predict_opp <- read.csv("rps_predict_opp.csv")
# red_opp <- filter(rps_predict_opp, rps_predict_opp$human_previous == "R" & rps_predict_opp$computer_previous == "S")
# 
# as.character(red_opp[["level0"]])
```

# Fitting a bayesian model WITH BETWEEN GAME TRANSFER of opp strat distribution between games 
```{r, cache=TRUE}
exp1_ToM_TR <- list()
for(id in unique(dat$human_id)) {
  exp1_ToM_TR[[id]] <- list()
  tdat <- subset(dat,human_id == id)

  # exp1_ToM_TR[[id]] <- DEoptim(fn=exp1_ToM, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))

  exp1_ToM_TR[[id]] <- optim(c(0.1,0.1),fn=exp1_ToM,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}
save(exp1_ToM_TR,file="exp1_ToM_TR.RData")

```

# Fitting a bayesian model with NO BETWEEN GAME TRANSFER of opp strat distribution between games 
```{r, cache =TRUE}
exp1_ToM_NT <- list()
for(id in unique(dat$human_id)) {
  exp1_ToM_NT[[id]] <- list()
  tdat <- subset(dat,human_id == id)

  # exp1_ToM_NT[[id]] <- DEoptim(fn=exp1_ToM, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))

  exp1_ToM_NT[[id]] <- optim(c(0.1,0.1),fn=exp1_ToM,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE ,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

save(exp1_ToM_NT,file="exp1_ToM_NT.RData")

```

# Summarise results in dataframe for both transfer and no transfer models 
```{r}
Nbayes_par_results <- data.frame()
for(id in unique(dat$human_id)) {
Nbayes_par_results <- rbind(Nbayes_par_results,
                       data.frame(
                         "id" = id,
                         "condition" = dat[dat$human_id==id,"condition"][1],
                         # BICs 
                         "BIC_transfer" = exp1_ToM_TR[[id]]$value + 2*log(150),
                         "BIC_no_transfer" = exp1_ToM_NT[[id]]$value+ 2*log(150),
                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
                         "theta_transfer" = exp1_ToM_TR[[id]]$par[1],
                         "theta_no_transfer" = exp1_ToM_NT[[id]]$par[1],
                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
                         "eps_transfer" = exp1_ToM_TR[[id]]$par[2],
                         "eps_no_transfer" = exp1_ToM_NT[[id]]$par[2]))
}

#Plotting the theta/eps scatter for all participants...
plot(Nbayes_par_results$theta_transfer,Nbayes_par_results$eps_transfer, xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
# 
write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
```

## Q-learning (Basic)
```{r}
Q_learn <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
  # actions
  # beta= inverse temperature parameter in softmax choice function
  # lambda = learning rate (one per game?)
  # data : participant and ai choice data.
  # Returns Q-values per trial and predicts choice using softmax
  beta <- par[1]
  alpha <- par[2]
  Q_vals_RPS = matrix(0.0,3)
  names(Q_vals_RPS) <- c("R","P","S")
  Q_vals_FWG = matrix(0.0,3)
  names(Q_vals_FWG) <- c("F","W","G")
  Q_vals_NUM = matrix(0.0,5)
  names(Q_vals_NUM) <- c("1","2","3","4","5")

  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
      lik_hum[t] <- 1/nopts
    } else {
      # Get reward and past human action
      reward <- as.numeric(data[t-1,"score"])
      h_act_prev <- as.character(data[t-1,"h_action"])
      Q_vals[h_act_prev] <- Q_vals[[h_act_prev]] + as.numeric(alpha)*( reward - Q_vals[[h_act_prev]])

      # cat(Q_vals,"\n")

      # Assume human chooses action probabilistically using softmax on Q values
      probs <- exp(Q_vals/beta)/sum(exp(Q_vals/beta))

      # Get actual human action and compute likelihood
      h_act <- as.character(data[t,"h_action"])
      act_index <- match(h_act, names(Q_vals))
      lik_hum[t] <- probs[[act_index]]
    }
  }
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)

}

```

## Q-learning fit
```{r, cache=TRUE}
QL_modelling <- list()
for(id in unique(dat$human_id)) {
  QL_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
  QL_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
}
save(QL_modelling,file="QL_modelling.RData")

```

## Q-Learning with state space consisting of last round play
```{r}

Q_learn_states <- function(par,data,return_value,gamma){
  # Par[1] -> beta= inverse temperature parameter in softmax choice function
  # Par[2] -> lambda = learning rate (one per game?)
  # data : participant and ai choice data.
  # return_value=c("-2loglik","likelihood_by_trial")
  # Gamma is discount factor for future rewards 
  # Returns Q-values per trial and predicts choice using softmax
  beta <- par[1]
  alpha <- par[2]

  #gamma <- 0.9

  #Define matrix of state spaces for each game 
  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
  states_RPS <- paste0(G1$Var1,G1$Var2)

  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
  states_FWG <- paste0(G2$Var1,G2$Var2)

  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
  states_NUM <- paste0(G3$Var1,G3$Var2)

  Q_vals_RPS = matrix(-0.5,9,3)
  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))

  Q_vals_FWG = matrix(-0.5,9,3)
  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))

  Q_vals_NUM = matrix(-0.5,25,5)
  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))

  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3

    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
      lik_hum[t] <- 1/nopts
      # Randomly select prev_state and actions for first round
      curr_state <- sample(state_vec, size = 1)
      h_act <- sample(colnames(Q_vals), size =1)
      ai_act <- sample(colnames(Q_vals), size =1)
      reward <- 0

    } else {
      # Get past human action and associated reward 
      h_act <- as.character(data[t-1,"h_action"])
      ai_act <- as.character(data[t-1,"a_action"])
      reward <- as.numeric(data[t-1,"score"])
    }

    # cat(curr_state, " This is the previous state", "\n")
    new_state <- paste0(h_act,ai_act)
    # cat(new_state,"This is new state","\n")

    # Q_learning: update rule (time  = t-1)
    Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])

    # Assume human chooses action probabilistically using softmax on Q values
    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
    #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }

    # Get actual human action and compute likelihood
    h_act <- as.character(data[t,"h_action"])
    act_index <- match(h_act, colnames(Q_vals))
    lik_hum[t] <- probs[[act_index]]

    # Update state
    curr_state <- new_state 
    #}
  }
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)

}

```

## Fitting Q_learning with states
```{r , cache =TRUE}
# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
# Q_learn_states(c(0.1,0.1), data, "-2loglik")

QL_states_modelling <- list()
for(id in unique(dat$human_id)) {
  QL_states_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
  # QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")

   QL_states_modelling[[id]] <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))
}

save(QL_states_modelling, file="QL_states_modelling.RData")

# QL_states_gamma <- list()
# for(id in unique(dat$human_id)) {
#   QL_states_gamma[[id]] <- list()
#   tdat <- subset(dat,human_id == id)
#   QL_states_gamma[[id]] <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0.9, control=list(trace = FALSE,parallelType=1))
# }
# save(QL_states_gamma,file="QL_states_gamma.RData")

```

```{r}
# OK, let's compare BICs and parameters for Gamma = 0 and Gamma = 0.9 (both for initial Q-values of -0.5)

compare_QL_states <- data.frame()
for(id in unique(dat$human_id)) {
compare_QL_states  <- rbind(compare_QL_states ,
                       data.frame(
                         "id" = id,
                         "condition" = dat[dat$human_id==id,"condition"][1],
                         "Zero_Gamma_BIC" = QL_states_modelling[[id]]$optim$bestval + 2*log(150),
                         "High_gamma_BIC" = QL_states_gamma[[id]]$optim$bestval + 2*log(150),
                         "diff" = QL_states_modelling[[id]]$optim$bestval - QL_states_gamma[[id]]$optim$bestval
                       ))
}

```
#Notes: Q-Learning as done above is far from optimal. The reason is that most states are never visited during play ( anecdotal evidence, about 40-60% in RPS/FWG and 10-20% in NUM). This method needs a lot more rounds to start modelling players behavior correctly.

## Parametric Experience Weighted Attraction model (Camerer & Ho 1997)
```{r}
EWA_par <- function(par,data,return_value){
  # par: vector of parameters to the EWA model
  # Data :choice data by trial for each participant
  # Returns sum of loglikelihoods or likelihood per trial
  phi <- par[1]
  delta <- par[2]
  rho <- par[3]
  lambda <- par[4]

  # Define attraction vectors for each game
  A_RPS = matrix(0.0,3)
  names(A_RPS) <- c("R","P","S")
  A_FWG = matrix(0.0,3)
  names(A_FWG) <- c("F","W","G")
  A_NUM = matrix(0.0,5)
  names(A_NUM) <- c("1","2","3","4","5")

  # # Define reward matrices from the prospective of the row player (human in our case)
  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))

  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))

  # Initiate likelihood by trial vector
  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
      reward <- switch(as.character(t_game),rps=reward_RPS,fwg = reward_FWG, numbers = reward_NUM)
      lik_hum[t] <- 1/nopts
      # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.
      N <- 1

    } else {
      # Get reward and past human action
      h_act_prev <- as.character(data[t-1,"h_action"])
      a_act_prev <- as.character(data[t-1,"a_action"])
      for (i in 1:length(Att)) {
        action <- as.character(names(Att)[i])
        # cat("this is current strat",action,"\n")
        # cat("this is previous human action",h_act_prev,"\n")

        # Attraction vector update rule
        Att[[i]] <- (phi*N*Att[[i]]  + ( delta + (1- delta)*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (rho*N + 1)
      }
      #Update the value of N
      N <- rho*N + 1

      # Assume human chooses action probabilistically using softmax on Attraction values
      probs <- exp(lambda*Att)/sum(exp(lambda*Att))

      # Get actual human action and compute likelihood
      h_act <- as.character(data[t,"h_action"])
      act_index <- match(h_act, names(Att))
      lik_hum[t] <- probs[[act_index]]
    }
  }

 if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret) ) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)
}
```

## Fitting Parametric EWA to data 
```{r, cache =TRUE}

EWA_modelling <- list()
for(id in unique(dat$human_id)) {
  EWA_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
  # EWA_modelling[[id]] <- optim(c(0.5,0.5,0.5,0.5),fn=EWA_par,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.001,0.001,0.001), upper = c(1,0.99,0.99,1), method="L-BFGS-B")
  EWA_modelling[[id]] <- DEoptim(fn=EWA_par,lower = c(0.01,0.01,0.01,0.01), upper = c(10,1,1,10), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))
}

save(EWA_modelling,file="EWA_modelling.RData")

```

##  Self-Tuning EWA (Camerer & Ho 2007) 
```{r}

EWA_self <- function(par,data,return_value){

  lambda <- par[1]
  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.

  # Define attraction vectors for each game 
  A_RPS = matrix(0.0,3)
  names(A_RPS) <- c("R","P","S")
  A_FWG = matrix(0.0,3)
  names(A_FWG) <- c("F","W","G")
  A_NUM = matrix(0.0,5)
  names(A_NUM) <- c("1","2","3","4","5")

  # # Define reward matrices from the prospective of the row player (human in our case)
  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))

  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))

  # Initiate likelihood by trial vector 
  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
      reward <- switch(as.character(t_game),rps=reward_RPS,fwg = reward_FWG, numbers = reward_NUM)
      game_data <- subset(data, game == t_game)
      lik_hum[t] <- 1/nopts
      N <- 1.0

      R_t <- rep(0.0,nopts)
      H_t <- R_t

    } else {

      indx <- data[t,"round"]
      # Get reward and past human action
      h_act_prev <- as.character(game_data[indx-1,"h_action"])
      a_act_prev <- as.character(game_data[indx-1,"a_action"])

      # Estimate phi(t)
      R_t <- as.numeric(names(Att) == a_act_prev)
      # cat("This is R(t)",R_t,"\n")

      H_t <- (H_t*(indx-2) + R_t)/(indx-1)
      # cat("this is H(t)",H_t,"\n")

      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
      # cat("This is Phit(t)",Phi_t,"\t")

      # Estimate vector Delta(t)

      delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
      #cat("this is delta(t)",delta_t,"\n")

      for (i in 1:length(Att)) {
        action <- as.character(names(Att)[i])
        # cat("this is current strat",action,"\n")
        # cat("this is previous humna action",h_act_prev,"\n")

        # Attraction vector update rule 
        Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
      }
      #Update the value of N 
      N <- Phi_t*N + 1
      #cat(Att,'\n')

      # Assume human chooses action probabilistically using softmax on Attraction values
      probs <- exp(lambda*Att)/sum(exp(lambda*Att))

      # Get actual human action and compute likelihood
      h_act <- as.character(game_data[indx,"h_action"])
      act_index <- match(h_act, names(Att))
      lik_hum[t] <- probs[[act_index]]
    }
  }

 if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)
}

```

```{r}
##Plotting self_tuning EWA likelihood function for lambda from 0 to 100 
# 
# lambdas <- seq(1,10,0.01)
# count = 0.0
# 
# 
# 
# for(id in unique(dat$human_id)) {
#   if (count <= 15) {
#       tdat <- subset(dat,human_id == id)
#       likelihoods <- sapply(lambdas, EWA_self, tdat, "-2loglik")
#       plot(lambdas,likelihoods)
#       count <- count + 1
#   }
# }

```

## Fitting Self-Tuning EWA to data 
```{r, cache=TRUE}

EWA_self_modelling <- list()
for(id in unique(dat$human_id)) {
  EWA_self_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
#   EWA_self_modelling[[id]] <- optim(10.0,fn=EWA_self,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
# }
  EWA_self_modelling[[id]] <- DEoptim(fn=EWA_self, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
}

save(EWA_self_modelling,file="EWA_self_modelling.RData")

```

```{r}
# cat(EWA_self_modelling[["38VxtUSv_h6RR5-tAAA2"]]$optim$bestmem)
```

##  Self-Tuning EWA with prior round play as state (Camerer & Ho 2007) 
```{r}

EWA_states <- function(par,data,return_value){

  lambda <- par[1]
  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.

  #Define matrix of state spaces for each game 
  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
  states_RPS <- paste0(G1$Var1,G1$Var2)

  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
  states_FWG <- paste0(G2$Var1,G2$Var2)

  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
  states_NUM <- paste0(G3$Var1,G3$Var2)

  A_RPS = matrix(-0.5,9,3)
  dimnames(A_RPS) = list(states_RPS, c("R", "P", "S"))

  A_FWG = matrix(-0.5,9,3)
  dimnames(A_FWG) = list(states_FWG, c("F", "W", "G"))

  A_NUM = matrix(-0.5,25,5)
  dimnames(A_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))

  # # Define reward matrices from the perspective of the row player (human in our case)
  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))

  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))

  # Initiate likelihood by trial vector 
  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3
    if(data[t,"round"] == 1) {
      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
      state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, numbers = states_NUM)
      reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, numbers = reward_NUM)
      game_data <- subset(data, game == t_game)
      # first round is uniform prediction
      lik_hum[t] <- 1/nopts
      N <- 1.0

      R_t <- rep(0.0,nopts)
      H_t <- R_t

      # Randomly select prev_state and actions for first round
      curr_state <- sample(state_vec, size = 1)
      h_act_prev <- sample(colnames(Att), size =1)
      a_act_prev <- sample(colnames(Att), size =1)
      #reward <- 0

    } else {

      indx <- data[t,"round"]
      state_indx <- match(curr_state,state_vec)
      #cat("this is the current state index", state_indx, "\n")

      # Get reward and past human action
      h_act_prev <- as.character(game_data[indx-1,"h_action"])
      a_act_prev <- as.character(game_data[indx-1,"a_action"])
      new_state <- paste0(h_act_prev,a_act_prev)

      # Estimate phi(t)
      R_t <- as.numeric(colnames(Att) == a_act_prev)
      #cat("This is R(t)",R_t,"\n")

      H_t <- (H_t*(indx-2) + R_t)/(indx-1)
      #cat("this is H(t)",H_t,"\n")

      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
      #cat("This is Phit(t)",Phi_t,"\t")

      # Estimate vector Delta(t)

      delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
      #cat("this is delta(t)",delta_t,"\n")

      for (i in 1:nopts) {
        action <- as.character(colnames(Att)[i])

        #cat("this is current indexed action",action,"\n")
        #cat("this is previous human action",h_act_prev,"\n")

        # Attraction vector update rule
        Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
      }

      #Update the value of N 
      N <- Phi_t*N + 1

      # Assume human chooses action probabilistically using softmax on Attraction values
      probs <- exp(lambda*Att[new_state,])/sum(exp(lambda*Att[new_state,]))

      # Get actual human action and compute likelihood
      h_act <- as.character(game_data[indx,"h_action"])
      act_index <- match(h_act, colnames(Att))
      lik_hum[t] <- probs[[act_index]]

      curr_state <- new_state

      # if (indx == 50) {
      #   cat("this is the attraction matrix at last round of", "\n")
      #   print(Att)
      # }
    }
  }

 if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)
}

```

```{r, cache=TRUE}
# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
# EWA_states(0.1, data, "-2loglik")
# optim(10.0,fn=EWA_states,gr = NULL, data=data,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")

EWA_states_modelling <- list()
for(id in unique(dat$human_id)) {
  EWA_states_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
#   EWA_states_modelling[[id]] <- optim(10.0,fn=EWA_states,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
# }
  EWA_states_modelling[[id]] <- DEoptim(fn=EWA_states, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
}

save(EWA_states_modelling,file="EWA_states_modelling.RData")

```

## What next?: Fitting models that explicitly take into account opponent strategy. LOLA? Won't work, it suffers from same issues as normal QL in that most states are not visited during game play. Influence model? Like belief lerning. it still has no sequential memory, still computes distribution on beliefs. We need to incorporate models that can mimic human memory by looking at history of play and leverage sequence prediction capabilities.

### Model based model: learn transition probabilities to new states. Weigh the value of an action by the conditional probability of ending up in a future state times the value of the new state.... once you take an action in current round, you can only end up in 3 states, with probabilities p, q and 1-p-q. You are learning these probabilities by updating priors (initial prior is dirichlet). 
```{r}
MBM <- function(par,data,return_value,gamma){
  # Par[1] -> beta= inverse temperature parameter in softmax choice function
  # Par[2] -> lambda = learning rate (one per game?)
  # data : participant and ai choice data.
  # return_value=c("-2loglik","likelihood_by_trial")
  # Gamma is discount factor for future rewards 
  # Returns Q-values per trial and predicts choice using softmax
  beta <- par[1]
  alpha <- par[2]

  #gamma <- 0.9

  #Define matrix of state spaces for each game 
  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
  states_RPS <- paste0(G1$Var1,G1$Var2)

  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
  states_FWG <- paste0(G2$Var1,G2$Var2)

  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
  states_NUM <- paste0(G3$Var1,G3$Var2)

  # Matrices to store Q_values in each state 
  Q_vals_RPS = matrix(-0.5,9,3)
  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
  Q_vals_FWG = matrix(-0.5,9,3)
  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
  Q_vals_NUM = matrix(-0.5,25,5)
  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))

  # Transition Matrices 
  Transit_RPS = matrix(1/9,9,9)
  dimnames(Transit_RPS) = list(states_RPS, states_RPS)
  Transit_FWG = matrix(1/9,9,9)
  dimnames(Transit_FWG) = list(states_FWG, states_FWG)
  Transit_NUM = matrix(1/25,25,25)
  dimnames(Transit_NUM) = list(states_NUM, states_NUM)

  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3

    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
      Transit <- switch(as.character(t_game),rps=Transit_RPS,fwg = Transit_FWG, numbers = Transit_NUM)
      lik_hum[t] <- 1/nopts
      # Randomly select prev_state and actions for first round
      curr_state <- sample(state_vec, size = 1)
      h_act <- sample(colnames(Q_vals), size =1)
      ai_act <- sample(colnames(Q_vals), size =1)
      reward <- 0

    } else {
      # Get past human action and associated reward 
      h_act <- as.character(data[t-1,"h_action"])
      ai_act <- as.character(data[t-1,"a_action"])
      reward <- as.numeric(data[t-1,"score"])
    }

    # cat(curr_state, " This is the previous state", "\n")
    new_state <- paste0(h_act,ai_act)
    # cat(new_state,"This is new state","\n")

    # Update Transit matrix ....first create hot vector = 1 if new state, 0 otherwise 
    hot_vector <- state_vec == new_state

    # Transit probs update: TD learning on transition matrix, learning rate fixed at 0.1
    Transit[curr_state,] <- Transit[curr_state,] + 0.1* (hot_vector - Transit[curr_state,])
    #cat(Transit[curr_state,], "\n")

    # Update Q-values as current reward + a weighted (by trasnsit probs) average of future Q-values.
    Q_Row_max <- apply(Q_vals, 1, max, na.rm = TRUE)
    #cat(Transit[curr_state,] * Q_Row_max, "\n")
    Q_vals[curr_state, h_act] <- reward +  gamma*( Transit[curr_state,] %*% Q_Row_max  )

    # Assume human chooses action probabilistically using softmax on Q values
    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
    #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }

    # Get actual human action and compute likelihood
    h_act <- as.character(data[t,"h_action"])
    act_index <- match(h_act, colnames(Q_vals))
    lik_hum[t] <- probs[[act_index]]

    # Update state
    curr_state<- new_state 
    #}
  }
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)

}

```

```{r, cache=TRUE}
MBM_modelling <- list()
for(id in unique(dat$human_id)) {
  MBM_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
  # MBM_modelling[[id]] <- optim(c(1,0.1),fn=QMBM,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")

   MBM_modelling[[id]] <- DEoptim(fn=MBM,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0.9, control=list(trace = FALSE,parallelType=1))
}

save(MBM_modelling, file="MBM_modelling.RData")

```

## Putting results together 
```{r}
load("QL_modelling.RData")
load("QL_states_modelling.RData")
load("EWA_modelling.RData")
load("EWA_self_modelling.RData")
load("MBM_modelling.RData")
load("EWA_states_modelling.RData")

All_results <- data.frame()
for(id in unique(dat$human_id)) {
  All_results <- rbind(All_results,
                       data.frame(
                         "ID" = id,
                         "condition" = dat[dat$human_id==id,"condition"][1],
                         "Random_BIC" = -2*(100*log(1/3) + 50*log(1/5)),

                         # Bayesian updating with/without transfer
                         "Bayes_Tr_BIC" = exp1_Bayes_game_Tr[[id]]$optim$bestval+ 1*log(150),
                         "Bayes_No_Tr_BIC" = exp1_Bayes_no_Tr[[id]]$optim$bestval + 1*log(150),
                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
                         "theta_transfer" = exp1_Bayes_game_Tr[[id]]$optim$bestmem[[1]],
                         "theta_no_transfer" = exp1_Bayes_no_Tr[[id]]$optim$bestmem[[1]],

                         # Q-Learning
                         "QL_BIC" = QL_modelling[[id]]$value + 2*log(150),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QL_Beta" = QL_modelling[[id]]$par[1],
                         # alpha -> learning rate in QL update
                         "QL_alpha" = QL_modelling[[id]]$par[2],

                         # Q-learning with last round states
                         "QL_states_BIC" = QL_states_modelling[[id]]$optim$bestval + 2*log(150),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QL_states_Beta" = QL_states_modelling[[id]]$optim$bestmem[1],
                         # alpha -> learning rate in QL update
                         "QL_states_alpha" = QL_states_modelling[[id]]$optim$bestmem[2],

                         # Parametric EWA
                         # Parametric EWA BIC
                         "EWA_BIC" = EWA_modelling[[id]]$optim$bestval + 4*log(150),
                         "EWA_2LL" = EWA_modelling[[id]]$optim$bestval,
                         # Phi is depreciation of past attractions
                         "EWA_Phi" = EWA_modelling[[id]]$optim$bestmem[1],
                         # Delta is weight of foregone payoffs vs actual payoffs
                         "EWA_Delta" = EWA_modelling[[id]]$optim$bestmem[2],
                         # Rho is depreciation of the experience measure N(t)
                         "EWA_Rho" = EWA_modelling[[id]]$optim$bestmem[3],
                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
                         "EWA_Lambda" = EWA_modelling[[id]]$optim$bestmem[4],

                         # Self-Tuning EWA (only 1 parameter)
                          # Parametric EWA BIC
                         "EWA_self_2LL" = EWA_self_modelling[[id]]$optim$bestval,
                         "EWA_self_BIC" = EWA_self_modelling[[id]]$optim$bestval + 1*log(150),
                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
                         "EWA_self_Lambda" = EWA_self_modelling[[id]]$optim$bestmem[1],

                         # EWA with states

                         "EWA_states_BIC" = EWA_states_modelling[[id]]$optim$bestval + 1*log(150),
                         "EWA_states_Lambda" = EWA_states_modelling[[id]]$optim$bestmem[1]

                         ))
}

write.csv(All_results,file="All_results.csv",row.names = FALSE)

```

## Calucalting BIC weights
```{r}

comp_BICs <- All_results[c("ID","Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")]

BIC_weights <- comp_BICs["ID"]
BIC_weights[,2:ncol(comp_BICs)] <- t(apply(comp_BICs[,2:ncol(comp_BICs)], 1, function(i) exp(-0.5*(i-min(i)) )))
colnames(BIC_weights) <-colnames(comp_BICs)

BIC_weights[,2:ncol(BIC_weights)] <- t(apply(BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))

```

## Building table of best model per participant
```{r}

Table_results <- table(All_results[, "condition"],c("random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])

 write.csv(Table_results,file="Table_results.csv",row.names = TRUE)
 kable(Table_results)
 #barplot(Table_results)

```
##### Looks like most participants behavior can be explained by QL_states. Bayesian models best explain a few more behaviors, while the others are consistent with random behavior, and only 1 with QL and 1 with S_EWA.

###### Question: Can we see evidence for transfer by looking at difference in BICS btwn Bayes with and without transfer. Let's test correlation between difference in BICs  with early rounds score (evidence for transfer) 
```{r}
# id_results_tst <- subset(All_results, ID == "38VxtUSv_h6RR5-tAAA2")
```

```{r}

exp1_model_comp <- data.frame()
for(id in unique(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(All_results, ID == id)
  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)

  best_model <- c("random","ToM_Game_Tr","ToM_No_Tr","QL", "QL_states","EWA","S_EWA", "EWA_states")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)]
  # 
  exp1_model_comp <- rbind(exp1_model_comp,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat[dat$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

                       ))
}

write.csv(exp1_model_comp,file = "exp1_model_comp.csv", row.names = FALSE)

```

### Correlate difference between BICs of Bayes transfer and no transfer with early rounds score (evidence for transfer) 
```{r}

cor.test(exp1_model_comp$TR_minus_NT_BIC,exp1_model_comp$Early_game_score, method="spearman")

```

### Correlation between early game score and difference between best model and random BIC
```{r}
cor.test(exp1_model_comp$Rand_minus_best_BIC, exp1_model_comp$Early_game_score, method="spearman")

```
### Histogram of best fitting models 
```{r}
barplot(table(exp1_model_comp$Best_model))
```
# Notes : There is positive and stat significant correlation between the difference between the best model BIC and random BIC on one hand, and the early scores from the target games ( FWG and NUM). What does this mean? It can be interpreted as a validation of early game score as good measure of how non-random play is....

## Let's compare total scores of each participant by the model of best fit, see if Bayes+transfer total scores are higher than Bayes + no transfer

```{r}

# ggboxplot(exp1_model_comp, x = "model", y = "Total_score",
#           color = "model", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
#           order = c("Random", "No Transfer", "Transfer"),
#           ylab = "Total Score", xlab = "Model with best fit")

exp1_model_comp$model <- recode(exp1_model_comp$Best_model,"Bayes Tr" = "Tranfer","Bayes No Tr" = "No Transfer", "QL_states" = "Q_Learning",  .default = "Random")
model <- factor(exp1_model_comp$model)
condition <- factor(exp1_model_comp$condition)

# Total score by best predictive model 
tapply(exp1_model_comp$Total_score, model, mean)

# Compute the analysis of variance
res.aov <- aov(Total_score ~ model + condition, data = exp1_model_comp)
# Summary of the analysis
summary(res.aov)
TukeyHSD(res.aov)
```

## What if we remove from data people who play randomly and then compare Transfer v No Transfer? 
```{r}

Non_Random_Only <- subset(exp1_model_comp, model != "Random" )

group_by(Non_Random_Only, model) %>%
  summarise(
    count = n(),
    mean = mean(Early_game_score, na.rm = TRUE),
    sd = sd(Early_game_score, na.rm = TRUE)
  )

res2 <- aov(Early_game_score ~ model, data = Non_Random_Only) 
summary(res2)
TukeyHSD(res2)
```

# Total time by best predictive model
```{r}
tapply(exp1_model_comp$Total_time, model, mean)

time.aov <- aov(Total_time ~ model, data = exp1_model_comp)
# Summary of the analysis
summary(time.aov)
TukeyHSD(time.aov)

``` 
#Early game scores for people best modelled with a Bayesian model with transfer are indeed higher than those best modelled without transfer but difference is not statistically significant.

### 2020-08-13 Bayesian_models_exp1.Rmd
added plots lik by trial

@@
 
-library(dplyr)
-
 dat <- read.csv("data20180719.csv")
@@
 
-# dat <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")
+dat <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")
 
@@
 # if human does not generalize, we need to reset the prior at the start of each ?stage?
-exp1_Bayes_model_LL <- function(par,data, generalize = c("game","no")) {
+exp1_Bayes_model_LL <- function(par,data, generalize = c("game","no"), return_value = "-2loglik") {
+   # return_value=c("-2loglik","likelihood_by_trial")
   # data is a subset for a single participant
@@
   ret <- -2*sum(dat$loglik)
+  if(return_value == "-2loglik") {
     if(is.infinite(ret) || is.nan(ret)) {
@@
     } 
-  # return(-2*sum(dat$loglik))
+  } else if ((return_value == "likelihood_by_trial")) {
+    return(exp(dat$loglik))
+  }
+
 }
@@
 ```{r}
-# exp1_Bayes_model_LL(0.4,data = dat, generalize = "game")
+exp1_Bayes_model_LL(0.4,data = dat, generalize = "no", "likelihood_by_trial")
 ```

### 2020-08-13 Report/draft_report_v1.Rmd
added plots lik by trial

@@
 
-Next we compared the performance of players whose actions are consistent with each of our hypothesized models.
+Next we compared the performance of players whose actions are best fit by each of our hypothesized models.
 Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play.
+We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (witout transfer), followed by Q-learning conditional on last round play.
 EWA, QL and random players had, understandably the lowest performance.

### 2020-08-13 comp_model_1019.Rmd
added plots lik by trial

@@
 
-BIC_weights <- comp_BICs["ID"]
-BIC_weights[,2:ncol(comp_BICs)] <- t(apply(comp_BICs[,2:ncol(comp_BICs)], 1, function(i) exp(-0.5*(i-min(i)) )))
-colnames(BIC_weights) <-colnames(comp_BICs)
-
-BIC_weights[,2:ncol(BIC_weights)] <- t(apply(BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
+exp1_BIC_weights <- comp_BICs["ID"]
+exp1_BIC_weights[,2:ncol(comp_BICs)] <- t(apply(comp_BICs[,2:ncol(comp_BICs)], 1, function(i) exp(-0.5*(i-min(i)) )))
+colnames(exp1_BIC_weights) <-colnames(comp_BICs)
+
+exp1_BIC_weights[,2:ncol(exp1_BIC_weights)] <- t(apply(exp1_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
 

### 2020-08-13 exp1_lik_by_trial.Rmd
added plots lik by trial

--- 2020-08-12 Bayesian_models_exp1.Rmd
@@
 ---
-title: "Bayesian_models_exp2"
+title: "exp1_lik_by_trial"
 output: html_document
@@
 knitr::opts_chunk$set(echo = TRUE)
+
+library(dplyr)
+```
+
+```{r}
+# Get Data for experiment 1, remove unecessary columns
+
+dat <- read.csv("exp1_data.csv")
+#####
+# dat <- subset(dat, human_id == "38VxtUSv_h6RR5-tAAA2")
+####
+
+optim_results <- read.csv("All_results.csv")
+
 ```
@@
 
-library(dplyr)
+#preparing data for functions to claculate likelihood
 
-dat <- read.csv("data20180719.csv")
-
-####### test data
-
-# dat <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")
-
-#######
-
-dat <- as_tibble(dat) %>% group_by(human_id,game)
+# dat <- as_tibble(dat) %>% group_by(human_id,game)
 dat <- dat %>%
   mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1))
-
-```
-
-```{r}
-## the following computes probabilities of ai actions assuming
-## strategy is always followed. (level refers to ai level)
 
@@
 ```{r}
-# group data by subjective component id
+# All_results <- data.frame()
+# for(id in unique(dat$human_id)) {
+#   All_results <- rbind(All_results,
+#                        data.frame(
+#                          "ID" = id,
+#                          "condition" = dat[dat$human_id==id,"condition"][1],
+#                          "Random_BIC" = -2*(100*log(1/3) + 50*log(1/5)),
 
-# if human generalizes over games, we can run update the prior generally
-# if human does not generalize, we need to reset the prior at the start of each ?stage?
-exp1_Bayes_model_LL <- function(par,data, generalize = c("game","no")) {
-  # data is a subset for a single participant
-  generalize <- match.arg(generalize)
-  alpha <- par[1] # probability that ai opponent plays according to strategy
-  if(length(par) > 1) {
-    beta <- par[2] # probability that human plays according to best response 
-  } else{
-    beta <- 1 # probability that human plays according to best response 
+lik_by_trial <- data.frame()
+
+for(id in unique(dat$human_id)) {
+
+  tdat <- dat %>% subset(human_id == id)
+
+  # QLS likelihoods 
+  pars_QLS <- unlist(filter(optim_results, ID == id)%>%select(QL_states_alpha,QL_states_Beta))
+  tdat$QLS_lik <- Q_learn_states(pars_QLS,tdat,"likelihood_by_trial",gamma = 0)
+
+  # Bayes model no transfer likelihoods
+  theta_NT <- unlist(filter(optim_results, ID == id)%>%select(theta_no_transfer))
+  tdat$Bayes_NT_lik <- exp1_Bayes_model_LL(theta_NT ,data = tdat, generalize = "no", "likelihood_by_trial")
+
+  # Bayes model with Transfer likelihood
+  theta_Tr <- unlist(filter(optim_results, ID == id)%>%select(theta_transfer))
+  tdat$Bayes_Tr_lik <- exp1_Bayes_model_LL(theta_Tr ,data = tdat, generalize = "game", "likelihood_by_trial")
+
+  lik_by_trial <- rbind(lik_by_trial,tdat)
 }
-
-  prior <- c(1,1,1) # prior alpha for dirichlet on p(level)
-  prior <- prior/sum(prior)
-
-  # use alpha to change the "deterministic" prediction
-
-  dat <- ungroup(data) %>%
-     mutate_at(.vars = vars(c(starts_with("pred_a1"),starts_with("pred_a2"),starts_with("pred_a3"))), 
-                            funs (case_when(
-      game == "numbers" ~  alpha*. + (1-alpha)/5,
-                  TRUE ~ alpha*. + (1-alpha)/3))) %>%
-     mutate_at(.vars = vars(c(starts_with("pred_a4"),starts_with("pred_a5"))), 
-                            funs (case_when(
-      game == "numbers" ~  alpha*. + (1-alpha)/5,
-                  TRUE ~ 0)))
-
-  if(generalize == "no") {
-    # group by game and stage
-    dat <- group_by(dat,game,add=TRUE)
-  }
-
-  # compute likelihood of ai action
-  dat <- dat %>%
-    mutate(
-      lik_level0 = case_when(
-        ai_action_num == 1 ~ pred_a1_level0,
-        ai_action_num == 2 ~ pred_a2_level0,
-        ai_action_num == 3 ~ pred_a3_level0,
-        ai_action_num == 4 ~ pred_a4_level0,
-        ai_action_num == 5 ~ pred_a5_level0
-      ),
-      lik_level1 = case_when(
-        ai_action_num == 1 ~ pred_a1_level1,
-        ai_action_num == 2 ~ pred_a2_level1,
-        ai_action_num == 3 ~ pred_a3_level1,
-        ai_action_num == 4 ~ pred_a4_level1,
-        ai_action_num == 5 ~ pred_a5_level1
-      ),
-      lik_level2 = case_when(
-        ai_action_num == 1 ~ pred_a1_level2,
-        ai_action_num == 2 ~ pred_a2_level2,
-        ai_action_num == 3 ~ pred_a3_level2,
-        ai_action_num == 4 ~ pred_a4_level2,
-        ai_action_num == 5 ~ pred_a5_level2
-      )
-    )
-
-  # use likelihood to compute the posterior predictive probability of each level
-  dat <- dat %>%
-    mutate(logpost_level0 = lag(log(prior[1]) + cumsum(log(lik_level0)),default=log(prior[1])),
-           logpost_level1 = lag(log(prior[2]) + cumsum(log(lik_level1)),default=log(prior[2])),
-           logpost_level2 = lag(log(prior[3]) + cumsum(log(lik_level2)),default=log(prior[3]))) %>%
-    # you can add or subtract any constant from the log-likelihoods; this can aid in precision
-    mutate(min = pmin(logpost_level0,logpost_level1, logpost_level2)) %>%
-      mutate(normalize = exp(logpost_level0 - min) + exp(logpost_level1 - min) + exp(logpost_level2 - min)) %>%
-        mutate(post_level0 = exp(logpost_level0 - min)/normalize,
-               post_level1 = exp(logpost_level1 - min)/normalize,
-               post_level2 = exp(logpost_level2 - min)/normalize)
-
-   #cat(as.character(c(round(dat$post_level0,2), round(dat$post_level1,2), round(dat$post_level2,2)), "\n", "\n"))
-
-  # use posterior predictive probability to predict probability of each ai and then human action
-  # opp is ai and self is human player here
-  dat <- dat %>%
-    mutate(p_opp_a1 = post_level0*pred_a1_level0 + post_level1*pred_a1_level1 + post_level2*pred_a1_level2,
-           p_opp_a2 = post_level0*pred_a2_level0 + post_level1*pred_a2_level1 + post_level2*pred_a2_level2,
-           p_opp_a3 = post_level0*pred_a3_level0 + post_level1*pred_a3_level1 + post_level2*pred_a3_level2,
-           p_opp_a4 = post_level0*pred_a4_level0 + post_level1*pred_a4_level1 + post_level2*pred_a4_level2,
-           p_opp_a5 = post_level0*pred_a5_level0 + post_level1*pred_a5_level1 + post_level2*pred_a5_level2
-    ) %>%
-      mutate(p_self_a1 = case_when(
-              game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a5,
-              TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a3)
-                ),
-             p_self_a2 = case_when(
-               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a1,
-               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a1)
-             ),
-             p_self_a3 = case_when(
-               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a2,
-               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a2)
-             ),
-             p_self_a4 = case_when(
-               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a3,
-               TRUE ~ 0
-             ),
-             p_self_a5 = case_when(
-               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a4,
-               TRUE ~ 0
-             )
-        )
-
-  # now finally compute the likelihood of human actions 
-  dat <- dat %>% 
-    mutate(
-      loglik = case_when(
-        human_action_num == 1 ~ log(p_self_a1),
-        human_action_num == 2 ~ log(p_self_a2),
-        human_action_num == 3 ~ log(p_self_a3),
-        human_action_num == 4 ~ log(p_self_a4),
-        human_action_num == 5 ~ log(p_self_a5))
-    )
-
-  #cat(as.character(exp(dat$loglik)), "\n", "\n")
-
-  ret <- -2*sum(dat$loglik)
-  if(is.infinite(ret) || is.nan(ret)) {
-    return(1e+300)
-  } else {
-    return(ret)
-  }
-  # return(-2*sum(dat$loglik))
-}
-
 ```
@@
 ```{r}
-# exp1_Bayes_model_LL(0.4,data = dat, generalize = "game")
-```
+library(ggplot2)
 
-```{r}
-#PLot likelihood for first participant as function of parameter
+mean_lik <- lik_by_trial %>%
+  select(human_id,condition,game, round,QLS_lik,Bayes_NT_lik,Bayes_Tr_lik) %>%
+  group_by(condition,game,round) %>%
+  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
+            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
+            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
 
-dat <- subset(dat, human_id == "QSuzBXpbyRc370HsAACW")
-likelihoods <- list()
-for (t in 1:95) {
-  likelihoods[t] <- exp1_Bayes_model_LL(t/100,data = dat, generalize = "game")
-}
+mean_lik$game <- factor(mean_lik$game,levels=c("rps","fwg","numbers"))
 
-jpeg(file="QSuzBXpbyRc370HsAACW.jpeg")
-plot(unlist(likelihoods))
-dev.off()
+data_long <- gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
+
+# make sure the different games are ordered in the way they were played
+data_long$game <- factor(data_long$game,levels=c("rps","fwg","numbers"))
+ggplot(data_long,aes(x=round,y=probability,colour=strategy)) + geom_line() + facet_grid(game~condition)
 
 ```
-
-```{r, ECHO = FALSE}
-
-library(DEoptim)
-
-exp1_Bayes_game_Tr <- exp1_Bayes_no_Tr <- list()
-
-# # USing DEOptim 
-for(id in levels(dat$human_id)) {
-  tdat <- subset(dat,human_id == id)
-  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))
-  exp1_Bayes_game_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-                                  generalize = "game",control=ctrl)
-  exp1_Bayes_no_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-                                  generalize = "no",control=ctrl)
-}
-
-# using optim
-
-# for(id in levels(dat$human_id)) {
-#   tdat <- subset(dat,human_id == id)
-#   # ctrl <- DEoptim.control(NP = 20, itermax=50)
-#   
-#   Bayes_same_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
-#   
-#   
-#   Bayes_same_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
-# 
-#   Bayes_same_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
-# 
-#   Bayes_distinct_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
-# 
-#   Bayes_distinct_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
-# 
-#   Bayes_distinct_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
-# }
-```
-```{r}
-
-exp1_Bayes_game_Tr[["QSuzBXpbyRc370HsAACW"]]$optim$bestval
-exp1_Bayes_game_Tr[["QSuzBXpbyRc370HsAACW"]]$optim$bestmem[[1]]
-```

### 2020-08-26 Experiment_2/Bayesian_models_exp2.Rmd
added lik by trial exp 2

@@
 
-dat <- read.csv("dat_exp2.csv")
+dat <- read.csv("data_exp2.csv")
 
@@
 
-Bayes_model_LL <- function(par,data,distinct_opponent = TRUE, generalize = c("game","stage","no")) {
+Bayes_model_LL <- function(par,data,distinct_opponent = TRUE, generalize = c("game","stage","no"), return = "-2loglik"){
+
   # data is a subset for a single participant
@@
     # group also by opponent
-    dat <- group_by(dat,opp_type)
+    dat <- group_by(dat,round_condition)
   }
@@
   #cat(as.character(exp(dat$loglik)), "\n", "\n")
-
+  if (return == "-2loglik") {
     ret <- -2*sum(dat$loglik)
@@
     } 
-  # return(-2*sum(dat$loglik))
+  } else if (return == "likelihood_by_trial") {
+    return(exp(dat$loglik))
+  }
 }
@@
 ```{r}
-#Bayes_model_LL(0.5,data = dat,distinct_opponent = TRUE, generalize = "game")
+Bayes_model_LL(0.5,data = dat,distinct_opponent = TRUE, generalize = "game", return = "likelihood_by_trial")
 
 #PLot likelihood for first participant as function of parameter 
-likelihoods <- list()
-for (t in 1:99) {
-  likelihoods[t] <- Bayes_model_LL(t/100,data = dat,distinct_opponent = TRUE, generalize = "game")
-}
-
-jpeg(file="vGnDPRowetREQVmwAADL.jpeg")
-plot(unlist(likelihoods))
-dev.off()
+# likelihoods <- list()
+# for (t in 1:99) {
+#   likelihoods[t] <- Bayes_model_LL(t/100,data = dat,distinct_opponent = TRUE, generalize = "game")
+# }
+# 
+# jpeg(file="vGnDPRowetREQVmwAADL.jpeg")
+# plot(unlist(likelihoods))
+# dev.off()
 

### 2020-08-26 Experiment_2/Experiment_2_modelling.Rmd
added lik by trial exp 2

@@
 }
-```
-
-```{r}
-# Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
-# TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer) {
-#   
-#   # dat = data subset for one participant
-#   # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
-#   # return = -2logLik 
-#   # or "likelihood_by_trial" vector  (for later plotting, etc)
-#   # btwn_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise. 
-#   
-#   # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
-#   # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
-#   theta <- par[1]
-#   eps <- par[2]
-#   
-#   num_strat = length(opp_strategy_vec) 
-#   
-#   # Load tables predicting oppponent movel
-#   
-#   rps_predict_opp <- read.csv("rps_predict_opp.csv")
-#   fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
-#   shootout_predict_opp <- read.csv("shootout_predict_opp.csv")
-#   
-# 
-#   #lik_opp is a vector that holds and updates probability distribution of opp strategy given actions.
-#   lik_opp <- matrix(0.0,num_strat, nrow(data))
-#   
-#   # Initiate prior vectors for each opponent as uniform
-#   opp_prior_vec <- rep(1/num_strat, num_strat)
-#   opp1_prior_vec <-rep(1/num_strat, num_strat)
-#   opp2_prior_vec <-rep(1/num_strat, num_strat)
-#   
-#   lik_hum <- matrix(0.0,nrow(data))
-#   # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
-#   br_hum <- rep(NA,num_strat)
-# 
-#   
-#   for(t in 1:nrow(data)) {
-#     t_game <- data[t,"game"]
-#     pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, shootout = shootout_predict_opp)
-#     nopts <- 3
-#     if(data[t,"round"] == 1) {
-#       # first round is uniform prediction
-#       pred_opp <- NA
-#       lik_hum[t] <- 1/nopts
-#       
-#       ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer reset prior to uniform)#####
-#       # Round 1 of stage 1 
-#       if (data[t,"stage"] == 1) {
-#         if (btwn_transfer){
-#           # if there is between game transfer, then the opp_prior_vec should have stored what was learned about the SECOND opponent 
-#           # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
-#           opp2_prior_vec <- opp_prior_vec
-#           # if between game transfer use stored opp1 prior vector from previous game (or uniform if first game  RPS) 
-#           opp_prior_vec <- opp1_prior_vec
-# 
-#         } else { # <- No between game TRANSFER 
-#           opp_prior_vec <- rep(1/num_strat, num_strat)
-#         }
-#         
-#       # we are round 1 of stage 2, keep opp vector from round 20 of stage 1  for stage 3
-#         } else if (data[t,"stage"] == 2) {
-#           if (within_transfer){
-#             # hold the probs vector of Opp type learned in stage 1 in memory and save to temp.
-#             opp1_prior_temp <- opp_prior_vec
-#           if (btwn_transfer){
-#             # If  between games transfer get prior from opp2 prior saved from last stage of last game 
-#             opp_prior_vec <- opp2_prior_vec
-#           } else { # if no between transfer start of first interaction with secnd opp should be reset
-#             opp_prior_vec <- rep(1/num_strat, num_strat)
-#           }
-#           
-#         } else { # Assume no between game transfer if no within. reasonable. 
-#           opp_prior_vec <- rep(1/num_strat, num_strat)    
-#         }
-#         
-#       # we are round 1 of stage 3
-#       } else if (data[t,"stage"] == 3) {
-#         if (within_transfer) {
-#           # if within_transfer keep opp vector from round 20 of stage 2 for stage 4
-#           opp2_prior_temp <- opp_prior_vec
-#           # if within_transfer, use what we learned about opp1 in stage 1 as new prior.  
-#           opp_prior_vec <- opp1_prior_temp
-#           
-#         } else { # No within transfer, dont store anything and reset priors
-#           opp_prior_vec <- rep(1/num_strat, num_strat)    
-#         }
-# 
-#       
-#       # We are in round 1 of stage 4,
-#       }  else if (data[t,"stage"] == 4) {
-#         if (within_transfer) {
-#           if (btwn_transfer) {
-#             # Store what was learned about opponent 1 for nxt game...
-#            opp1_prior_vec <- opp_prior_vec
-#           } 
-#           # Use what was learned about opponent 2 from stage 2.
-#           opp_prior_vec <- opp2_prior_temp
-#           
-#         } else {
-#           opp_prior_vec <- rep(1/num_strat, num_strat)
-#         }
-#         
-#       }
-#       
-#     # Rounds 2 to End of stage
-#     } else {
-#       cat("stage", data[t,"stage"], " opps ",  opp_prior_vec, "\n")
-#       # get prediction of opponent action from CSV files
-#       for (strategy in opp_strategy_vec) {
-#         k = match(strategy,opp_strategy_vec)
-#         pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])
-#         
-#         # Given opponent action predicted, what would be human action best response for each opp strat
-#         br_hum[[k]] <- exp2_best_response(t_game,as.character(pred_opp))
-#         
-#         # First we deal with easy case of unique predicted action ( multiple possible preds in shoot are separated by "/" sign)
-#         if (!grepl("/",pred_opp,fixed = TRUE)) {
-#            # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
-#           if(as.character(data[t,"a_action"]) == pred_opp) {
-#             lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
-#           } else {
-#             lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
-#           }
-#         # Here we are in shootout and opponent predicted action is a vector of two possible moves (e.g "left/center")  
-#         } else {
-#           if(grepl(as.character(data[t,"a_action"]), pred_opp,fixed = TRUE)) {
-#             # Assume each action has likelihood of 50%
-#              lik_opp[k,t] <- 0.5*(theta + (1-theta)/nopts)*opp_prior_vec[k]
-#           } else {
-#             #the 2 is to standardise the theta dependent probs: P(ai plays pred | opp is level k)
-#             lik_opp[k,t] <- 2*((1-theta)/nopts)*opp_prior_vec[k]
-#           }
-#         }
-#         
-#       # Get which opponent strategy human current actn maps to (i.e, if index = 0 then human current action is best response to level-0 comp_strat...)
-#       indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))
-# 
-#       # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
-#       # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
-#       if(length(indices) == 0){
-#         lik_hum[t] <- eps/nopts
-#       # if same br action for multiple possible ai opponents, add probabilities 
-#       } else {
-#         lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
-#       }
-#     }  
-#       # Standardising the probabilities and updating prior
-#       lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
-#       opp_prior_vec <- lik_opp[,t]
-#     }
-#   # for debugging uncomment the line below
-#   #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"/n")
-#   }
-#   
-#   if(return_value == "-2loglik") {
-#     ret <- -2*sum(log(lik_hum))
-#     if(is.infinite(ret) || is.nan(ret)) {
-#       return(1e+300)
-#     } else {
-#       return(ret)
-#     }
-#   }
-#   if(return_value == "likelihood_by_trial") return(lik_hum)
-#   
-# }
-
-```
-
-```{r}
-# Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
-TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer, Naive = FALSE) {
-
-  # dat = data subset for one participant
-  # opp_strategy_vec = vector of possible opponent strategies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
-  # return = -2logLik 
-  # or "likelihood_by_trial" vector  (for later plotting, etc)
-  # btwn_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise.
-
-  # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
-  theta <- par[1]
-
-  num_strat = length(opp_strategy_vec)
-
-  # Load tables predicting oppponent model
-
-  rps_predict_opp <- read.csv("rps_predict_opp.csv")
-  fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
-  shootout_predict_opp <- read.csv("shootout_predict_opp.csv")
-
-  #lik_opp is a vector that holds and updates probability distribution of opp strategy given actions.
-  lik_opp <- matrix(0.0,num_strat, nrow(data))
-
-  # Initiate prior vectors for each opponent as uniform
-  opp_prior_vec <- rep(1/num_strat, num_strat)
-  opp1_prior_vec <-rep(1/num_strat, num_strat)
-  opp2_prior_vec <-rep(1/num_strat, num_strat)
-
-  lik_hum <- matrix(0.0,nrow(data))
-  # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
-  br_hum <- rep(NA,num_strat)
-
-  for(t in 1:nrow(data)) {
-    t_game <- data[t,"game"]
-    pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, shootout = shootout_predict_opp)
-    nopts <- 3
-    if(data[t,"round"] == 1) {
-      # first round is uniform prediction
-      pred_opp <- NA
-      lik_hum[t] <- 1/nopts
-
-      ## KEY CODE FOR LEARNING TRANSFER !! #####
-      #Naive 
-      if (Naive) {
-        # pass. no update to prior vector throughout all stages and games
-      } else {
-        #abc
-        #def
-        # Round 1 of stage 1 
-        if (data[t,"stage"] == 1) {
-          if (btwn_transfer){
-            # if there is between game transfer, then the opp_prior_vec should have stored what was learned about the SECOND opponent 
-            # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
-            opp2_prior_vec <- opp_prior_vec
-            # if between game transfer use stored opp1 prior vector from previous game (or uniform if first game  RPS) 
-            opp_prior_vec <- opp1_prior_vec
-          } else { # <- No between game TRANSFER 
-            opp_prior_vec <- rep(1/num_strat, num_strat)
-          }
-
-        # we are round 1 of stage 2, keep opp vector from round 20 of stage 1  for stage 3
-        } else if (data[t,"stage"] == 2) {
-            if (within_transfer){
-              # hold the probs vector of opponent type learned in stage 1 in memory and save to temp.
-              opp1_prior_temp <- opp_prior_vec
-
-              if (btwn_transfer){
-              # If  between games transfer get prior from opp2 prior saved from last stage of last game 
-                opp_prior_vec <- opp2_prior_vec
-              } else { # if no between transfer start of first interaction with secnd opp should be reset
-              opp_prior_vec <- rep(1/num_strat, num_strat)
-              }
-
-            } else { # Assume no between game transfer if no within. reasonable. 
-            opp_prior_vec <- rep(1/num_strat, num_strat)    
-            }
-
-        # we are round 1 of stage 3
-        } else if (data[t,"stage"] == 3) {
-          if (within_transfer) {
-            # if within_transfer keep opp vector from round 20 of stage 2 for stage 4
-            opp2_prior_temp <- opp_prior_vec
-            # if within_transfer, use what we learned about opp1 in stage 1 as new prior.  
-            opp_prior_vec <- opp1_prior_temp
-
-          } else { # No within transfer, dont store anything and reset priors
-            opp_prior_vec <- rep(1/num_strat, num_strat)    
-          }
-
-        # We are in round 1 of stage 4,
-        }  else if (data[t,"stage"] == 4) {
-          if (within_transfer) {
-            if (btwn_transfer) {
-              # Store what was learned about opponent 1 for nxt game...
-              opp1_prior_vec <- opp_prior_vec
-            } 
-            # Use what was learned about opponent 2 from stage 2.
-            opp_prior_vec <- opp2_prior_temp
-
-          } else {
-            opp_prior_vec <- rep(1/num_strat, num_strat)
-          }
-
-        }
-
-      lik_opp[,t] <- opp_prior_vec
-
-      } #End of no naive condition
-
-    # Rounds 2 to End of stage
-    } else {
-      #cat("stage", data[t,"stage"], " opps ",  opp_prior_vec, "\n")
-      # get prediction of opponent action from CSV files
-      for (strategy in opp_strategy_vec) {
-        k = match(strategy,opp_strategy_vec)
-        pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])
-
-        # Given opponent action predicted, what would be human action best response for each opp strat
-        br_hum[[k]] <- as.character(exp2_best_response(t_game,as.character(pred_opp)))
-
-        # First we deal with easy case of unique predicted action ( multiple preds in shoot are separated by "/" sign)
-        if (!grepl("/",pred_opp,fixed = TRUE)) {
-           # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
-          if(as.character(data[t,"a_action"]) == pred_opp) {
-            lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
-          } else {
-            lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
-          }
-        # Here we are in shootout and opponent predicted action is a vector of two possible moves (e.g "left/center")  
-        } else {
-          if(grepl(as.character(data[t,"a_action"]), pred_opp,fixed = TRUE)) {
-            # Assume each action has likelihood of 50% 
-             lik_opp[k,t] <- (0.5*(theta + (1-theta)/nopts) + 0.5*((1-theta)/nopts)) *opp_prior_vec[k]
-          } else { 
-            lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
-          }
-        }
-      }  
-      # Get which opponent strategy human current actn maps to (i.e, if index = 0 then human current action is best response to level-0 comp_strat...)
-      indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))
-      not_pred_indx <- setdiff(c(1,2,3),indices)
-      # cat(as.character(indices), "\n")
-
-      # THEN likelihood of current human action is just sumproduct of priors and likelihood of each oppoennt action
-      if (!grepl("/",br_hum,fixed = TRUE)) {
-        lik_hum[t] <- sum(opp_prior_vec[indices])* (theta + (1-theta)/nopts) +    sum(opp_prior_vec[not_pred_indx])*(1-theta)/nopts
-      } else {
-        for (i in 1:3) {
-          temp <- 0
-          if (grepl("/",br_hum[i],fixed = TRUE)) {
-            temp <- temp + 0.5*(theta + (1-theta)/nopts)*opp_prior_vec[i]
-          } else{
-            temp <- temp + 
-          }
-        }
-        lik_hum[t] <- sum(opp_prior_vec[indices])* (theta + (1-theta)/nopts) +    sum(opp_prior_vec[not_pred_indx])*(1-theta)/nopts
-      }
-
-      # Standardising the probabilities and updating prior
-      lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
-      opp_prior_vec <- lik_opp[,t]
-    } # End of else ( from round 2 onwards)
-
-  # for debugging uncomment the line below
-  # cat(as.character(data[t,"a_action"]),lik_opp[,t],"\n")
-  cat(as.character(br_hum),as.character(data[t,"h_action"]),lik_hum[t],"\n","\n")
-
-  }
-
-  if(return_value == "-2loglik") {
-    ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret) || is.nan(ret)) {
-      return(1e+300)
-    } else {
-      return(ret)
-    }
-  }
-  if(return_value == "likelihood_by_trial") return(lik_hum)
-
-}
-
-```
-
-```{r}
-
-TOM_model(c(0.5),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = TRUE, btwn_transfer = TRUE, Naive = FALSE)
-
-```
-## Fitting Bayesian model with between game transfer (as well as within)  
-```{r, cache=TRUE}
-exp2_BT <- list()
-for(id in unique(dat_exp2$human_id)) {
-  exp2_BT[[id]] <- list()
-  tdat <- subset(dat_exp2,human_id == id)
-
-  # TR_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", btwn_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))
-
-  exp2_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = TRUE, Naive = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-}
-save(exp2_BT, file="exp2_BT.RData")
-
-```
-
-## Fitting ToM model with NO Between transfer (but with transfer within games)
-```{r, cache=TRUE}
-
-exp2_NO_BT <- list()
-for(id in unique(dat_exp2$human_id)) {
-  exp2_NO_BT[[id]] <- list()
-  tdat <- subset(dat_exp2,human_id == id)
-
-  # exp2_NO_BT[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
-
-  exp2_NO_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = FALSE, Naive = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-}
-
-save(exp2_NO_BT,file="exp2_NO_BT.RData")
-```
-
-## Fitting Bayesian model with NO Between or within transfer
-```{r, cache=TRUE}
-
-exp2_NO_Tr <- list()
-for(id in unique(dat_exp2$human_id)) {
-  exp2_NO_Tr[[id]] <- list()
-  tdat <- subset(dat_exp2,human_id == id)
-
-  # exp2_NO_Tr[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
-
-  exp2_NO_Tr[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, Naive =FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-}
-
-save(exp2_NO_Tr,file="exp2_NO_Tr.RData")
-```
-
-#Fitting model where player does not distinguish between opponents 
-```{r, cache=TRUE}
-
-exp2_Naive <- list()
-for(id in unique(dat_exp2$human_id)) {
-  exp2_Naive[[id]] <- list()
-  tdat <- subset(dat_exp2,human_id == id)
-
-  # exp2_Naive[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
-
-  exp2_Naive[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, Naive = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-}
-
-save(exp2_Naive,file="exp2_Naive.RData")
 ```
@@
 ```{r}
-exp2_QL_states(c(5,0.4),test_data, "-2loglik", 0.0, TRUE)
+exp2_QL_states(c(5,0.4),test_data, "likelihood_by_trial", 0.0, FALSE)
 ```
@@
 exp2_results <- data.frame()
+
 for(id in unique(dat_exp2$human_id)) {
@@
 
-                         # MS results for Bayesian models
-                         #  # Bayesian updating with between and within game transfer
-                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$value + 2*log(180),
+                         #MS results for Bayesian models
+                          # Bayesian updating with between and within game transfer
+                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$optim$bestval + 1*log(180),
+                         "theta_transfer" = Bayes_distinct_game[[id]]$optim$bestmem[1],
+
                           # Bayesian updating with within but no btwn game transfer
-                         "Distinct_stage_BIC" = Bayes_distinct_stage[[id]]$value + 2*log(180),
+                         "Distinct_stage_BIC" = Bayes_distinct_stage[[id]]$optim$bestval + 1*log(180),
+                         "theta_no_btw_tr" = Bayes_distinct_stage[[id]]$optim$bestmem[1],
+
                           #  No within or between game transfer
-                         "Bayes_distinct_no" = Bayes_distinct_no[[id]]$value + 2*log(180),
+                         "Bayes_distinct_no" = Bayes_distinct_no[[id]]$optim$bestval + 1*log(180),
+                         "theta_no_tr" =  Bayes_distinct_no[[id]]$optim$bestmem[1],
+
                           # No distinction between players, transfer within and between
-                         "Bayes_same_game" = Bayes_same_game[[id]]$value + 2*log(180),
+                         "Bayes_same_game" = Bayes_same_game[[id]]$optim$bestval + 1*log(180),
+                         "theta_naive" = Bayes_same_game[[id]]$optim$bestmem[1],
+                         #
 
-                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
-                         "theta_transfer" = exp2_BT[[id]]$par[1],
-                         "theta_no_btw_tr" = exp2_NO_BT[[id]]$par[1],
-                         "theta_no_tr" =  exp2_NO_Tr[[id]]$par[1],
-                         "theta_naive" = exp2_Naive[[id]]$par[1],
-                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
-                         "eps_transfer" = exp2_BT[[id]]$par[2],
-                         "eps_no_btwn_tr" = exp2_NO_BT[[id]]$par[2],
-                         "eps_no_tr" = exp2_NO_Tr[[id]]$par[2],
-                         "eps_naive" = exp2_Naive[[id]]$par[2],
+                         # # Theta is the parameter governing AI stochasticity. Truth is 0.9
+                         # "theta_transfer" = exp2_BT[[id]]$par[1],
+                         # "theta_no_btw_tr" = exp2_NO_BT[[id]]$par[1],
+                         # "theta_no_tr" =  exp2_NO_Tr[[id]]$par[1],
+                         # "theta_naive" = exp2_Naive[[id]]$par[1],
+                         # # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
+                         # "eps_transfer" = exp2_BT[[id]]$par[2],
+                         # "eps_no_btwn_tr" = exp2_NO_BT[[id]]$par[2],
+                         # "eps_no_tr" = exp2_NO_Tr[[id]]$par[2],
+                         # "eps_naive" = exp2_Naive[[id]]$par[2],
 

### 2020-08-26 Experiment_2/exp2_lik_by_trial.Rmd
added lik by trial exp 2

--- 2020-03-05 Experiment_2/Bayesian_models_exp2.Rmd
@@
 ---
-title: "Bayesian_models_exp2"
+title: "exp2_lik_by_trial"
 output: html_document
@@
 ```{r}
+library(dplyr)
+library(tidyr)
 
-library(dplyr)
+dat <- read.csv("data_exp2.csv")
 
-dat <- read.csv("dat_exp2.csv")
-
-####### test data 
-dat <- subset(dat,human_id == "bZg1T3MNoItL6b7qAAAj")
-#######
-
-dat <- as_tibble(dat) %>% group_by(human_id,game)
-dat <- dat %>%
-  mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1))
+exp2_optim_results <- read.csv("exp2_results.csv")
 
@@
 ```{r}
-## the following computes probabilities of ai actions assuming
-## strategy is always followed.
+
+# Preparing data for running functions to calculate likelihoods
+
+# dat <- as_tibble(dat) %>% group_by(human_id,game)
+  dat <- dat %>%
+   mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1))
 
@@
 ```{r}
-# group data by subjective component id
 
-# if human does not distinguish between players, we can run with these predictions as is
-# if human does distinguish between players, we need to set the predictions to uniform at the start of a round
+lik_by_trial_2 <- data.frame()
 
-# if human generalizes over games, we can run update the prior generally
-# if human generalizes over rounds but not games, we need to reset the prior at the start of a game
-# if human does not generalize, we need to reset the prior at the start of each round
+for(id in unique(dat$human_id)) {
 
-Bayes_model_LL <- function(par,data,distinct_opponent = TRUE, generalize = c("game","stage","no")) {
-  # data is a subset for a single participant
-  generalize <- match.arg(generalize)
-  alpha <- par[1] # probability that opponent plays according to strategy
-  if(length(par) > 1) {
-    beta <- par[2] # probability that human plays according to best response 
-  } else{
-    beta <- 1 # probability that human plays according to best response 
-  }
+  tdat <- dat %>% subset(human_id == id)
 
-  prior <- c(1,1,1) # prior alpha for dirichlet on p(level)
-  prior <- prior/sum(prior)
+  # QLS likelihoods 
+  pars_QLS <- unlist(filter(exp2_optim_results, ID == id)%>%select(QL_states_alpha,QL_states_Beta))
+  tdat$QLS_lik <-  exp2_QL_states(pars_QLS,tdat,"likelihood_by_trial",0.0, FALSE)
 
-  # use alpha to change the "deterministic" predictions
-  make_probs <- function(x) {
-    (1-alpha)*(1/3) + alpha*x
-  }
-  dat <- ungroup(data) %>%
-    mutate_at(vars(starts_with("pred_")),make_probs)
+  # QLS within Transfer likelihoods 
+  pars_QLS_within <- unlist(filter(exp2_optim_results, ID == id)%>%select(QLS_within_Tr_alpha,QLS_within_Tr_Beta))
+  tdat$QLS_lik_within <-  exp2_QL_states(pars_QLS_within,tdat,"likelihood_by_trial",gamma = 0, TRUE)
+  #                
+  # 
+  # Bayes model no transfer likelihoods
+  theta_NT <- unlist(filter(exp2_optim_results, ID == id)%>%select(theta_no_tr))
+  tdat$Bayes_NT_lik <- Bayes_model_LL(theta_NT, tdat, distinct_opponent = TRUE, generalize = "no",return = "likelihood_by_trial")
 
-  if(distinct_opponent) {
-    # start of stage should not be predictable
-    dat[dat$round == 1,paste0(paste0("pred_",c("a1_","a2_","a3_")),rep(c("level0","level1","level2"),each=3))] <- 1/3
-    # group also by opponent
-    dat <- group_by(dat,opp_type)
-  }
+  # Bayes model with Transfer likelihood
+  theta_Tr <- unlist(filter(exp2_optim_results, ID == id)%>%select(theta_transfer))
+  tdat$Bayes_Tr_lik <- Bayes_model_LL(theta_Tr, tdat, distinct_opponent = TRUE, generalize = "game",return = "likelihood_by_trial")
 
-  if(generalize == "stage") {
-    # generalize over rounds but not game, so group by game
-    dat <- group_by(dat,game,add=TRUE)
-  } else if(generalize == "no") {
-    # group by game and stage
-    dat <- group_by(dat,game,stage,add=TRUE)
-  }
-
-  # compute likelihood of ai action
-  dat <- dat %>%
-    mutate(
-      lik_level0 = case_when(
-        ai_action_num == 1 ~ pred_a1_level0,
-        ai_action_num == 2 ~ pred_a2_level0,
-        ai_action_num == 3 ~ pred_a3_level0
-      ),
-      lik_level1 = case_when(
-        ai_action_num == 1 ~ pred_a1_level1,
-        ai_action_num == 2 ~ pred_a2_level1,
-        ai_action_num == 3 ~ pred_a3_level1
-      ),
-      lik_level2 = case_when(
-        ai_action_num == 1 ~ pred_a1_level2,
-        ai_action_num == 2 ~ pred_a2_level2,
-        ai_action_num == 3 ~ pred_a3_level2
-      )
-    )
-
-  # use likelihood to compute the posterior predictive probability of each level
-  dat <- dat %>%
-    mutate(logpost_level0 = lag(log(prior[1]) + cumsum(log(lik_level0)),default=log(prior[1])),
-           logpost_level1 = lag(log(prior[2]) + cumsum(log(lik_level1)),default=log(prior[2])),
-           logpost_level2 = lag(log(prior[3]) + cumsum(log(lik_level2)),default=log(prior[3]))) %>%
-    # you can add or subtract any constant from the log-likelihoods; this can aid in precision
-    mutate(min = pmin(logpost_level0,logpost_level1, logpost_level2)) %>%
-      mutate(normalize = exp(logpost_level0 - min) + exp(logpost_level1 - min) + exp(logpost_level2 - min)) %>%
-        mutate(post_level0 = exp(logpost_level0 - min)/normalize,
-               post_level1 = exp(logpost_level1 - min)/normalize,
-               post_level2 = exp(logpost_level2 - min)/normalize)
-
-  # use posterior predictive probability to predict probability of each ai and then human action
-  dat <- dat %>%
-    mutate(p_opp_a1 = post_level0*pred_a1_level0 + post_level1*pred_a1_level1 + post_level2*pred_a1_level2,
-           p_opp_a2 = post_level0*pred_a2_level0 + post_level1*pred_a2_level1 + post_level2*pred_a2_level2,
-           p_opp_a3 = post_level0*pred_a3_level0 + post_level1*pred_a3_level1 + post_level2*pred_a3_level2
-    ) %>%
-      mutate(p_self_a1 = case_when(
-              game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a2 + .5*p_opp_a3),
-              TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a3)
-                ),
-             p_self_a2 = case_when(
-               game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a1 + .5*p_opp_a3),
-               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a1)
-             ),
-             p_self_a3 = case_when(
-               game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a1 + .5*p_opp_a2),
-               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a2)
-             )
-        )
-
-  # now finally compute the likelihood of human actions 
-  dat <- dat %>% 
-    mutate(
-      loglik = case_when(
-        human_action_num == 1 ~ log(p_self_a1),
-        human_action_num == 2 ~ log(p_self_a2),
-        human_action_num == 3 ~ log(p_self_a3))
-    )
-
-  ret <- -2*sum(dat$loglik)
-  if(is.infinite(ret) || is.nan(ret)) {
-    return(1e+300)
-  } else {
-    return(ret) 
-  }
-  # return(-2*sum(dat$loglik))
-}
-
-```
-
-```{r}
-Bayes_model_LL(0.1,data = dat,distinct_opponent = TRUE, generalize = "game")
-```
-
-```{r, ECHO = FALSE}
-
-library(DEoptim)
-
-Bayes_same_game <- Bayes_same_stage <- Bayes_same_no <- 
-  Bayes_distinct_game <- Bayes_distinct_stage <- Bayes_distinct_no <- 
-    list()
-
-# USing DEOptim
-
-# for(id in levels(dat$human_id)) {
-#   tdat <- subset(dat,human_id == id)
-#   ctrl <- DEoptim.control(NP = 20, itermax=50)
-#   Bayes_same_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                    distinct_opponent = FALSE, generalize = "game",control=ctrl)
-#   Bayes_same_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                    distinct_opponent = FALSE, generalize = "stage",control=ctrl)
-#   Bayes_same_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                    distinct_opponent = FALSE, generalize = "no",control=ctrl)
-#   Bayes_distinct_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                    distinct_opponent = TRUE, generalize = "game",control=ctrl)
-#   Bayes_distinct_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                         distinct_opponent = TRUE, generalize = "stage",control=ctrl)
-#   Bayes_distinct_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-#                                  distinct_opponent = TRUE, generalize = "no",control=ctrl)
-# }
-
-# using optim
-
-for(id in levels(dat$human_id)) {
-  tdat <- subset(dat,human_id == id)
-  # ctrl <- DEoptim.control(NP = 20, itermax=50)
-
-  Bayes_same_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-                                 generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
-
-  Bayes_same_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-                                 generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
-
-  Bayes_same_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-                                 generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
-
-  Bayes_distinct_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-                                 generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
-
-  Bayes_distinct_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-                                 generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
-
-  Bayes_distinct_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-                                 generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
+  lik_by_trial_2 <- rbind(lik_by_trial_2,tdat)
 }
@@
 ```{r}
-# this will implement a pseudo-multinomial-dirichlet
-pBayes_model_LL <- function(par,data,distinct_opponent = TRUE, generalize = c("game","stage","no")) {
-  generalize <- match.arg(generalize)
-  alpha <- par[1] # probability that opponent plays according to strategy
-  if(length(par) > 1) {
-    gamma <- par[2] # probability that human plays according to best response 
-  } else{
-    gamma <- 1 # probability that human plays according to best response 
-  }
-  if(length(par) > 2) {
-    beta <- par[3] # probability that human plays according to best response 
-  } else{
-    beta <- 1 # probability that human plays according to best response 
-  }
+library(ggplot2)
+library(dplyr)
+library(tidyr)
 
-  prior <- c(gamma,gamma,gamma) # prior alpha for dirichlet on p(level)
-  #prior <- prior/sum(prior)
+mean_lik_2 <- lik_by_trial_2 %>%
+  select(human_id,game,stage,round_condition, round, QLS_lik, QLS_lik_within, Bayes_NT_lik, Bayes_Tr_lik) %>%
+  group_by(game,stage,round) %>%
+  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
+            mean_QLS_within_lik = mean(QLS_lik_within, na.rm = TRUE),
+            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
+            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
 
-  # use alpha to change the "deterministic" predictions
-  make_probs <- function(x) {
-    (1-alpha)*(1/3) + alpha*x
-  }
-  dat <- ungroup(data) %>%
-    mutate_at(vars(starts_with("pred_")),make_probs)
+mean_lik$game <- factor(mean_lik$game,levels=c("rps","fwg","shootout"))
 
-  if(distinct_opponent) {
-    # start of round should not be predictable
-    dat[dat$round == 1,paste0(paste0("pred_",c("a1_","a2_","a3_")),rep(c("level0","level1","level2"),each=3))] <- 1/3
-    # group also by opponent
-    dat <- group_by(dat,opp_type)
-  }
+data_long <- gather(mean_lik_2, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
 
-  if(generalize == "stage") {
-    # generalize over rounds but not game, so group by game
-    dat <- group_by(dat,game,add=TRUE)
-  } else if(generalize == "no") {
-    # group by game and stage
-    dat <- group_by(dat,game,stage,add=TRUE)
-  }
-
-  # compute likelihood of ai action
-  dat <- dat %>%
-    mutate(
-      lik_level0 = case_when(
-        ai_action_num == 1 ~ pred_a1_level0,
-        ai_action_num == 2 ~ pred_a2_level0,
-        ai_action_num == 3 ~ pred_a3_level0
-      ),
-      lik_level1 = case_when(
-        ai_action_num == 1 ~ pred_a1_level1,
-        ai_action_num == 2 ~ pred_a2_level1,
-        ai_action_num == 3 ~ pred_a3_level1
-      ),
-      lik_level2 = case_when(
-        ai_action_num == 1 ~ pred_a1_level2,
-        ai_action_num == 2 ~ pred_a2_level2,
-        ai_action_num == 3 ~ pred_a3_level2
-      )
-    )
-
-  # normalize the likeihoods to give a pseudo-observation of strategy
-  dat <- dat %>%
-    # compute normalizing factor
-    mutate(normalize = lik_level0 + lik_level1 + lik_level2) %>%
-    # avoid division by 0
-    mutate(normalize = replace(normalize, normalize == 0, 1)) %>%
-    # normalize
-    mutate(pseudo_obs_level0 = lik_level0/normalize,
-           pseudo_obs_level1 = lik_level1/normalize,
-           pseudo_obs_level2 = lik_level2/normalize)
-
-  # use pseudo observations to compute the posterior predictive probability of each level
-  dat <- dat %>%
-    mutate(post_level0 = lag(prior[1] + cumsum(pseudo_obs_level0),default=prior[1]),
-           post_level1 = lag(prior[2] + cumsum(pseudo_obs_level1),default=prior[2]),
-           post_level2 = lag(prior[3] + cumsum(pseudo_obs_level2),default=prior[3])) %>%
-      mutate(normalize = post_level0 + post_level1 + post_level2) %>%
-        mutate(post_level0 = post_level0/normalize,
-               post_level1 = post_level1/normalize,
-               post_level2 = post_level2/normalize)
-
-  # use posterior predictive probability to predict probability of each ai and then human action
-  dat <- dat %>%
-    mutate(p_opp_a1 = post_level0*pred_a1_level0 + post_level1*pred_a1_level1 + post_level2*pred_a1_level2,
-           p_opp_a2 = post_level0*pred_a2_level0 + post_level1*pred_a2_level1 + post_level2*pred_a2_level2,
-           p_opp_a3 = post_level0*pred_a3_level0 + post_level1*pred_a3_level1 + post_level2*pred_a3_level2
-    ) %>%
-    mutate(p_self_a1 = case_when(
-      game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a2 + .5*p_opp_a3),
-      TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a3)
-    ),
-    p_self_a2 = case_when(
-      game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a1 + .5*p_opp_a3),
-      TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a1)
-    ),
-    p_self_a3 = case_when(
-      game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a1 + .5*p_opp_a2),
-      TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a2)
-    )
-    )
-
-  # now finally compute the likelihood of human actions 
-  dat <- dat %>% 
-    mutate(
-      loglik = case_when(
-        human_action_num == 1 ~ log(p_self_a1),
-        human_action_num == 2 ~ log(p_self_a2),
-        human_action_num == 3 ~ log(p_self_a3))
-    )
-
-  return(-2*sum(dat$loglik))
-}
+# make sure the different games are ordered in the way they were played
+data_long$game <- factor(data_long$game,levels=c("rps","fwg","shootout"))
+ggplot(data_long,aes(x=round,y=probability,colour=strategy)) + geom_line() + facet_grid(game~stage)
 
 ```
-
-```{r}
-pBayes_same_game <- pBayes_same_stage <- pBayes_same_no <- 
-  pBayes_distinct_game <- pBayes_distinct_stage <- pBayes_distinct_no <- 
-  list()
-
-for(id in levels(dat$human_id)) {
-  tdat <- subset(dat,human_id == id)
-  ctrl <- DEoptim.control(NP = 20, itermax=50)
-  pBayes_same_game[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
-                                   distinct_opponent = FALSE, generalize = "game",control=ctrl)
-  pBayes_same_stage[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
-                                    distinct_opponent = FALSE, generalize = "stage",control=ctrl)
-  pBayes_same_no[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
-                                 distinct_opponent = FALSE, generalize = "no",control=ctrl)
-  pBayes_distinct_game[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
-                                       distinct_opponent = TRUE, generalize = "game",control=ctrl)
-  pBayes_distinct_stage[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
-                                        distinct_opponent = TRUE, generalize = "stage",control=ctrl)
-  pBayes_distinct_no[[id]] <- DEoptim(pBayes_model_LL, lower=c(0.1,1), upper = c(1,100), data = tdat,
-                                     distinct_opponent = TRUE, generalize = "no",control=ctrl)
-}
-```

### 2020-09-04 Experiment_2/Experiment_2_modelling.Rmd
fixed Q learning bugs

@@
 ```{r, cache=TRUE}
+# exp2_QL_states <- function(par,data,return_value,gamma, within_transfer = FALSE){
+#   # Par[1] -> beta= inverse temperature parameter in softmax choice function
+#   # Par[2] -> lambda = learning rate (one per game?)
+#   # data : participant and ai choice data.
+#   # return_value=c("-2loglik","likelihood_by_trial")
+#   # Gamma is discount factor for future rewards 
+#   # Returns Q-values per trial and predicts choice using softmax
+#   beta <- par[1]
+#   alpha <- par[2]
+# 
+#   #gamma <- 0.9 
+# 
+#   #Define matrix of state spaces for each game 
+#   G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+#   states_RPS <- paste0(G1$Var1,G1$Var2)
+# 
+#   G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+#   states_FWG <- paste0(G2$Var1,G2$Var2)
+# 
+#   G3 <- expand.grid(c("left","center","right"), c("left","center","right"))
+#   states_SHOOT <- paste0(G3$Var1,G3$Var2)
+#   
+#   Q_vals_RPS = matrix(-0.5,9,3)
+#   dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
+# 
+#   Q_vals_FWG = matrix(-0.5,9,3)
+#   dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
+#   
+#   Q_vals_SHOOT = matrix(-0.5,9,3)
+#   dimnames(Q_vals_SHOOT) = list(states_SHOOT, c("left","center","right"))
+#  
+#   lik_hum <- matrix(0.0,nrow(data))
+# 
+#   for(t in 1:nrow(data)) {
+#     t_game <- data[t,"game"]
+#     nopts <- 3
+#     
+#     if(data[t,"round"] == 1) {
+#       
+#       # Within game transfer Code 
+#       if (!within_transfer){
+#               Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
+#       } else {
+#         if (data[t,"stage"] == 1){
+#           Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
+#         } else if (data[t,"stage"] == 2) {
+#           Q_vals_opp1 <- Q_vals
+#           Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
+#         } else if (data[t,"stage"] == 3) {
+#           Q_vals_opp2 <- Q_vals 
+#           Q_vals <- Q_vals_opp1
+#         } else if (data[t,"stage"] == 4) {
+#           Q_vals <- Q_vals_opp2
+#         }
+#       }
+#    
+# 
+#       #cat(Q_vals,"\n") 
+#       state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, shootout = states_SHOOT)
+#       # first round is uniform prediction
+#       lik_hum[t] <- 1/nopts
+#       # Randomly select state and previous actions for first round
+#       curr_state <- sample(state_vec, size = 1)
+#       h_act <- sample(colnames(Q_vals), size =1)
+#       ai_act <- sample(colnames(Q_vals), size =1)
+#       reward <- 0 
+#       
+#     } else {
+#       # Get past human action and associated reward 
+#       h_act <- as.character(data[t-1,"h_action"])
+#       ai_act <- as.character(data[t-1,"a_action"])
+#       reward <- as.numeric(data[t-1,"score"])
+#     }
+#     
+#     
+#     # cat(curr_state, " This is the previous state", "\n")
+#     new_state <- paste0(h_act,ai_act)
+#     # cat(new_state,"This is new state","\n")
+#     
+#     # Q_learning: update rule (time  = t-1)
+#     Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act] )
+#     
+#     # Assume human chooses action probabilistically using softmax on Q values
+#     probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
+#     #if (data[t,"round"] == 1) { cat(probs,"\n") }
+#     
+#     # Get actual human action and compute likelihood
+#     h_act <- as.character(data[t,"h_action"])
+#     act_index <- match(h_act, colnames(Q_vals))
+#     lik_hum[t] <- probs[[act_index]]
+#       
+#     # Update state
+#     curr_state <- new_state 
+#     #}
+#   }
+#   if(return_value == "-2loglik") {
+#     ret <- -2*sum(log(lik_hum))
+#     if(is.infinite(ret) || is.nan(ret)) {
+#       return(1e+300)
+#     } else {
+#       return(ret)
+#     }
+#   }
+#   if(return_value == "likelihood_by_trial") return(lik_hum)
+#   
+# }
+
+```
+## Attempt 2 : QL with states and option to activate transfer 
+```{r, cache=TRUE}
 exp2_QL_states <- function(par,data,return_value,gamma, within_transfer = FALSE){
@@
   alpha <- par[2]
-
-  #gamma <- 0.9
+  nopts <- 3
 
@@
     t_game <- data[t,"game"]
-    nopts <- 3
-
     if(data[t,"round"] == 1) {
@@
       lik_hum[t] <- 1/nopts
-      # Randomly select state and previous actions for first round
-      curr_state <- sample(state_vec, size = 1)
-      h_act <- sample(colnames(Q_vals), size =1)
-      ai_act <- sample(colnames(Q_vals), size =1)
-      reward <- 0
 
@@
       # Get past human action and associated reward 
-      h_act <- as.character(data[t-1,"h_action"])
-      ai_act <- as.character(data[t-1,"a_action"])
-      reward <- as.numeric(data[t-1,"score"])
-    }
+      h_act_prev <- as.character(data[t-1,"h_action"])
+      ai_act_prev <- as.character(data[t-1,"a_action"])
+      curr_state <- paste0(h_act_prev,ai_act_prev)
 
-    # cat(curr_state, " This is the previous state", "\n")
+      h_act <- as.character(data[t,"h_action"])
+      ai_act <- as.character(data[t,"a_action"])
+      reward <- as.numeric(data[t,"score"])
       new_state <- paste0(h_act,ai_act)
-    # cat(new_state,"This is new state","\n")
-
-    # Q_learning: update rule (time  = t-1)
-    Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act] )
 
       # Assume human chooses action probabilistically using softmax on Q values
-    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
-    #if (data[t,"round"] == 1) { cat(probs,"\n") }
-
-    # Get actual human action and compute likelihood
-    h_act <- as.character(data[t,"h_action"])
+      probs <- exp(Q_vals[curr_state,]/beta)/sum(exp(Q_vals[curr_state,]/beta))
+      # Get actual human next action and compute likelihood
       act_index <- match(h_act, colnames(Q_vals))
@@
 
-    # Update state
-    curr_state <- new_state 
-    #}
+      # Q_learning: update rule (time = t)
+      Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
+    }
+
   }

### 2020-09-04 Experiment_2/exp2_lik_by_trial.Rmd
fixed Q learning bugs

@@
 
-# dat <- as_tibble(dat) %>% group_by(human_id,game)
+dat <- as_tibble(dat) %>% group_by(human_id,game)
 dat <- dat %>%
@@
 
+dat <- as.data.frame(dat)   
 lik_by_trial_2 <- data.frame()
@@
   # QLS likelihoods 
-  pars_QLS <- unlist(filter(exp2_optim_results, ID == id)%>%select(QL_states_alpha,QL_states_Beta))
+  pars_QLS <- unlist(filter(exp2_optim_results, ID == id)%>%select(QL_states_Beta, QL_states_alpha))
   tdat$QLS_lik <-  exp2_QL_states(pars_QLS,tdat,"likelihood_by_trial",0.0, FALSE)
@@
   # QLS within Transfer likelihoods 
-  pars_QLS_within <- unlist(filter(exp2_optim_results, ID == id)%>%select(QLS_within_Tr_alpha,QLS_within_Tr_Beta))
+  pars_QLS_within <- unlist(filter(exp2_optim_results, ID == id)%>%select(QLS_within_Tr_Beta,QLS_within_Tr_alpha))
   tdat$QLS_lik_within <-  exp2_QL_states(pars_QLS_within,tdat,"likelihood_by_trial",gamma = 0, TRUE)

### 2020-09-04 Report/draft_report_v1.tex
fixed Q learning bugs

@@
 
-Next we compared the performance of players whose actions are consistent with each of our hypothesized models.
+Next we compared the performance of players whose actions are best fit by each of our hypothesized models.
 Figure~\ref{fig:exp1-cumScores} shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play.
+We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (witout transfer), followed by Q-learning conditional on last round play.
 EWA, QL and random players had, understandably the lowest performance.

### 2020-09-04 comp_model_1019.Rmd
fixed Q learning bugs

@@
 
-#Fit a bayesian model to observed human play. Prior is vector of possible level-k opponent strategies.
-```{r}
-# Function to produce best reponse to ai_action 
-best_response <- function(game,ai_action){
-  if (game == "rps"){
-    if (ai_action == "R") {return("P")}
-    else if (ai_action == "P") {return("S")}
-    else if (ai_action == "S") {return("R")}
-  } else if (game == "fwg"){ 
-    if (ai_action == "F") {return("W")}
-    else if (ai_action == "W") {return("G")}
-    else if (ai_action == "G") {return("F")}
-  } else if (game == "numbers") {
-    if (ai_action == "1") {return("2")}
-    else if (ai_action == "2") {return("3")}
-    else if (ai_action == "3") {return("4")}
-    else if (ai_action == "4") {return("5")}
-    else if (ai_action == "5") {return("1")}
-  }
-}
-
-exp1_ToM <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {
-
-  # dat = data subset for one participant
-  # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
-  # return = -2logLik 
-  # or "likelihood_by_trial" vector  (for later plotting, etc)
-  # opp_mod_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise.
-
-  # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
-  # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
-  theta <- par[1]
-  eps <- par[2]
-
-  num_strat = length(opp_strategy_vec)
-
-  # Load tables predicting oppponent move
-  rps_predict_opp <- read.csv("rps_predict_opp.csv")
-  fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
-  numbers_predict_opp <- read.csv("numbers_predict_opp.csv")
-
-  #lik_opp is a vector that holds and update probability distribution of opp strategy given actions.
-  lik_opp <- matrix(0.0,num_strat, nrow(data))
-  # Initiate prior vector as uniform
-  opp_prior_vec <-rep(1/num_strat, num_strat)
-
-  lik_hum <- matrix(0.0,nrow(data))
-  # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
-  br_hum <- rep(NA,num_strat)
-
-  for(t in 1:nrow(data)) {
-    t_game <- data[t,"game"]
-    pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)
-
-    if(t_game == "numbers") nopts <- 5 else nopts <- 3
-    if(data[t,"round"] == 1) {
-      # first round is uniform prediction
-      pred_opp <- NA
-      lik_hum[t] <- 1/nopts
-      ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer, reset prior to uniform)
-      if (!(opp_mod_transfer)) {
-        opp_prior_vec <- rep(1/num_strat, num_strat)
-        lik_opp[,t] <- opp_prior_vec
-        }
-
-    # Rounds after first
-    } else {
-      # get prediction of opponent action from CSV files
-      for (strategy in opp_strategy_vec) {
-        k = match(strategy,opp_strategy_vec)
-        pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])
-
-        # Given opponent action predicted, what would be human action best response for each opp strat
-        br_hum[[k]] <- best_response(t_game,as.character(pred_opp))
-
-        # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
-        if(as.character(data[t,"a_action"]) == pred_opp) {
-          lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
-        } else {
-          lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
-        }
-      }
-      # Get which opponent strategy human current actn maps to (if index = 0 then human current action is br to level-0 comp_strat...)
-      indices <- which(br_hum %in% as.character(data[t,"h_action"]))
-
-      # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
-      # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
-      if(length(indices) == 0){
-        lik_hum[t] <- eps/nopts
-      # if same br action for multiple possible ai opponents, add probabilities 
-      } else {
-        lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
-      }
-      # Standardising the probabilities and updating prior
-      lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
-      opp_prior_vec <- lik_opp[,t]
-    }
-    # for debugging uncomment the line below
-    #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"\n")
-  }
-  if(return_value == "-2loglik") {
-    ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret) || is.nan(ret)) {
-      return(1e+300)
-    } else {
-      return(ret)
-    }
-  }
-  if(return_value == "likelihood_by_trial") return(lik_hum)
-}
-
-# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
-# exp1_ToM(c(0.9,0.99),data,c("level0","level1","level2"),"-2loglik",FALSE)
-```
-
-```{r}
+## Fit a bayesian model to observed human play. Prior is vector of possible level-k opponent strategies.
+```{r}
+# # Function to produce best reponse to ai_action 
+# best_response <- function(game,ai_action){
+#   if (game == "rps"){
+#     if (ai_action == "R") {return("P")}
+#     else if (ai_action == "P") {return("S")}
+#     else if (ai_action == "S") {return("R")}
+#   } else if (game == "fwg"){ 
+#     if (ai_action == "F") {return("W")}
+#     else if (ai_action == "W") {return("G")}
+#     else if (ai_action == "G") {return("F")}
+#   } else if (game == "numbers") {
+#     if (ai_action == "1") {return("2")}
+#     else if (ai_action == "2") {return("3")}
+#     else if (ai_action == "3") {return("4")}
+#     else if (ai_action == "4") {return("5")}
+#     else if (ai_action == "5") {return("1")}
+#   }
+# }
+# 
+# exp1_ToM <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {
+#   
+#   # dat = data subset for one participant
+#   # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
+#   # return = -2logLik 
+#   # or "likelihood_by_trial" vector  (for later plotting, etc)
+#   # opp_mod_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise. 
+#   
+#   # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
+#   # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
+#   theta <- par[1]
+#   eps <- par[2]
+#   
+#   num_strat = length(opp_strategy_vec) 
+#   
+#   # Load tables predicting oppponent move
 #   rps_predict_opp <- read.csv("rps_predict_opp.csv")
-# red_opp <- filter(rps_predict_opp, rps_predict_opp$human_previous == "R" & rps_predict_opp$computer_previous == "S")
-# 
-# as.character(red_opp[["level0"]])
-```
-
-# Fitting a bayesian model WITH BETWEEN GAME TRANSFER of opp strat distribution between games 
-```{r, cache=TRUE}
-exp1_ToM_TR <- list()
-for(id in unique(dat$human_id)) {
-  exp1_ToM_TR[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
-
-  # exp1_ToM_TR[[id]] <- DEoptim(fn=exp1_ToM, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))
-
-  exp1_ToM_TR[[id]] <- optim(c(0.1,0.1),fn=exp1_ToM,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-}
-save(exp1_ToM_TR,file="exp1_ToM_TR.RData")
-
-```
-
-# Fitting a bayesian model with NO BETWEEN GAME TRANSFER of opp strat distribution between games 
-```{r, cache =TRUE}
-exp1_ToM_NT <- list()
-for(id in unique(dat$human_id)) {
-  exp1_ToM_NT[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
-
-  # exp1_ToM_NT[[id]] <- DEoptim(fn=exp1_ToM, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
-
-  exp1_ToM_NT[[id]] <- optim(c(0.1,0.1),fn=exp1_ToM,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE ,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-}
-
-save(exp1_ToM_NT,file="exp1_ToM_NT.RData")
-
-```
-
-# Summarise results in dataframe for both transfer and no transfer models 
-```{r}
-Nbayes_par_results <- data.frame()
-for(id in unique(dat$human_id)) {
-Nbayes_par_results <- rbind(Nbayes_par_results,
-                       data.frame(
-                         "id" = id,
-                         "condition" = dat[dat$human_id==id,"condition"][1],
-                         # BICs 
-                         "BIC_transfer" = exp1_ToM_TR[[id]]$value + 2*log(150),
-                         "BIC_no_transfer" = exp1_ToM_NT[[id]]$value+ 2*log(150),
-                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
-                         "theta_transfer" = exp1_ToM_TR[[id]]$par[1],
-                         "theta_no_transfer" = exp1_ToM_NT[[id]]$par[1],
-                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
-                         "eps_transfer" = exp1_ToM_TR[[id]]$par[2],
-                         "eps_no_transfer" = exp1_ToM_NT[[id]]$par[2]))
-}
-
-#Plotting the theta/eps scatter for all participants...
-plot(Nbayes_par_results$theta_transfer,Nbayes_par_results$eps_transfer, xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
-# 
-write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
+#   fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
+#   numbers_predict_opp <- read.csv("numbers_predict_opp.csv")
+# 
+#   #lik_opp is a vector that holds and update probability distribution of opp strategy given actions.
+#   lik_opp <- matrix(0.0,num_strat, nrow(data))
+#   # Initiate prior vector as uniform
+#   opp_prior_vec <-rep(1/num_strat, num_strat)
+#   
+#   lik_hum <- matrix(0.0,nrow(data))
+#   # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
+#   br_hum <- rep(NA,num_strat)
+# 
+#   
+#   for(t in 1:nrow(data)) {
+#     t_game <- data[t,"game"]
+#     pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)
+#     
+#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
+#     if(data[t,"round"] == 1) {
+#       # first round is uniform prediction
+#       pred_opp <- NA
+#       lik_hum[t] <- 1/nopts
+#       ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer, reset prior to uniform)
+#       if (!(opp_mod_transfer)) {
+#         opp_prior_vec <- rep(1/num_strat, num_strat)
+#         lik_opp[,t] <- opp_prior_vec
+#         }
+#       
+#     # Rounds after first
+#     } else {
+#       # get prediction of opponent action from CSV files
+#       for (strategy in opp_strategy_vec) {
+#         k = match(strategy,opp_strategy_vec)
+#         pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])
+#         
+#         # Given opponent action predicted, what would be human action best response for each opp strat
+#         br_hum[[k]] <- best_response(t_game,as.character(pred_opp))
+#         
+#         # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
+#         if(as.character(data[t,"a_action"]) == pred_opp) {
+#           lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
+#         } else {
+#           lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
+#         }
+#       }
+#       # Get which opponent strategy human current actn maps to (if index = 0 then human current action is br to level-0 comp_strat...)
+#       indices <- which(br_hum %in% as.character(data[t,"h_action"]))
+# 
+#       # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
+#       # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
+#       if(length(indices) == 0){
+#         lik_hum[t] <- eps/nopts
+#       # if same br action for multiple possible ai opponents, add probabilities 
+#       } else {
+#         lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
+#       }
+#       # Standardising the probabilities and updating prior
+#       lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
+#       opp_prior_vec <- lik_opp[,t]
+#     }
+#     # for debugging uncomment the line below
+#     #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"\n")
+#   }
+#   if(return_value == "-2loglik") {
+#     ret <- -2*sum(log(lik_hum))
+#     if(is.infinite(ret) || is.nan(ret)) {
+#       return(1e+300)
+#     } else {
+#       return(ret)
+#     }
+#   }
+#   if(return_value == "likelihood_by_trial") return(lik_hum)
+# }
+# 
+# # data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
+# # exp1_ToM(c(0.9,0.99),data,c("level0","level1","level2"),"-2loglik",FALSE)
+# ```
+# 
+# ```{r}
+# # rps_predict_opp <- read.csv("rps_predict_opp.csv")
+# # red_opp <- filter(rps_predict_opp, rps_predict_opp$human_previous == "R" & rps_predict_opp$computer_previous == "S")
+# # 
+# # as.character(red_opp[["level0"]])
+# ```
+# 
+# 
+# 
+# # Fitting a bayesian model WITH BETWEEN GAME TRANSFER of opp strat distribution between games 
+# ```{r, cache=TRUE}
+# exp1_ToM_TR <- list()
+# for(id in unique(dat$human_id)) {
+#   exp1_ToM_TR[[id]] <- list()
+#   tdat <- subset(dat,human_id == id)
+#   
+#   # exp1_ToM_TR[[id]] <- DEoptim(fn=exp1_ToM, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))
+# 
+#   exp1_ToM_TR[[id]] <- optim(c(0.1,0.1),fn=exp1_ToM,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+# }
+# save(exp1_ToM_TR,file="exp1_ToM_TR.RData")
+# 
+# ```
+# 
+# 
+# # Fitting a bayesian model with NO BETWEEN GAME TRANSFER of opp strat distribution between games 
+# ```{r, cache =TRUE}
+# exp1_ToM_NT <- list()
+# for(id in unique(dat$human_id)) {
+#   exp1_ToM_NT[[id]] <- list()
+#   tdat <- subset(dat,human_id == id)
+#   
+#   # exp1_ToM_NT[[id]] <- DEoptim(fn=exp1_ToM, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
+# 
+#   exp1_ToM_NT[[id]] <- optim(c(0.1,0.1),fn=exp1_ToM,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE ,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+# }
+# 
+# save(exp1_ToM_NT,file="exp1_ToM_NT.RData")
+# 
+# ```
+# 
+# 
+# # Summarise results in dataframe for both transfer and no transfer models 
+# ```{r}
+# Nbayes_par_results <- data.frame()
+# for(id in unique(dat$human_id)) {
+# Nbayes_par_results <- rbind(Nbayes_par_results,
+#                        data.frame(
+#                          "id" = id,
+#                          "condition" = dat[dat$human_id==id,"condition"][1],
+#                          # BICs 
+#                          "BIC_transfer" = exp1_ToM_TR[[id]]$value + 2*log(150),
+#                          "BIC_no_transfer" = exp1_ToM_NT[[id]]$value+ 2*log(150),
+#                          # Theta is the parameter governing AI stochasticity. Truth is 0.9
+#                          "theta_transfer" = exp1_ToM_TR[[id]]$par[1],
+#                          "theta_no_transfer" = exp1_ToM_NT[[id]]$par[1],
+#                          # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
+#                          "eps_transfer" = exp1_ToM_TR[[id]]$par[2],
+#                          "eps_no_transfer" = exp1_ToM_NT[[id]]$par[2]))
+# }
+# 
+# #Plotting the theta/eps scatter for all participants...
+# plot(Nbayes_par_results$theta_transfer,Nbayes_par_results$eps_transfer, xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
+# # 
+# write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
 ```
@@
 
-## Q-Learning with state space consisting of last round play
-```{r}
-
+## First attempt : Q-Learning with state space consisting of last round play (deprecated) 
+```{r}
+
+# Q_learn_states <- function(par,data,return_value,gamma){
+#   # Par[1] -> beta= inverse temperature parameter in softmax choice function
+#   # Par[2] -> lambda = learning rate (one per game?)
+#   # data : participant and ai choice data.
+#   # return_value=c("-2loglik","likelihood_by_trial")
+#   # Gamma is discount factor for future rewards 
+#   # Returns Q-values per trial and predicts choice using softmax
+#   beta <- par[1]
+#   alpha <- par[2]
+# 
+#   #gamma <- 0.9 
+# 
+#   #Define matrix of state spaces for each game 
+#   G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+#   states_RPS <- paste0(G1$Var1,G1$Var2)
+# 
+#   G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+#   states_FWG <- paste0(G2$Var1,G2$Var2)
+# 
+#   G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+#   states_NUM <- paste0(G3$Var1,G3$Var2)
+#   
+#   Q_vals_RPS = matrix(-0.5,9,3)
+#   dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
+# 
+#   Q_vals_FWG = matrix(-0.5,9,3)
+#   dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
+#   
+#   Q_vals_NUM = matrix(-0.5,25,5)
+#   dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
+#  
+#   lik_hum <- matrix(0.0,nrow(data))
+# 
+#   for(t in 1:nrow(data)) {
+#     t_game <- data[t,"game"]
+#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
+#     
+#     if(data[t,"round"] == 1) {
+#       # first round is uniform prediction
+#       Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
+#       state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
+#       lik_hum[t] <- 1/nopts
+#       # Randomly select prev_state and actions for first round
+#       curr_state <- sample(state_vec, size = 1)
+#       h_act <- sample(colnames(Q_vals), size =1)
+#       ai_act <- sample(colnames(Q_vals), size =1)
+#       reward <- 0 
+#       
+#     } else {
+#       # Get past human action and associated reward 
+#       h_act <- as.character(data[t-1,"h_action"])
+#       ai_act <- as.character(data[t-1,"a_action"])
+#       reward <- as.numeric(data[t-1,"score"])
+#     }
+#     
+#     
+#     # cat(curr_state, " This is the previous state", "\n")
+#     new_state <- paste0(h_act,ai_act)
+#     # cat(new_state,"This is new state","\n")
+#     
+#     # Q_learning: update rule (time  = t-1)
+#     Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
+#     
+#     # Assume human chooses action probabilistically using softmax on Q values
+#     probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
+#     #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }
+#     
+#     # Get actual human action and compute likelihood
+#     h_act <- as.character(data[t,"h_action"])
+#     act_index <- match(h_act, colnames(Q_vals))
+#     lik_hum[t] <- probs[[act_index]]
+#       
+#     # Update state
+#     curr_state <- new_state 
+#     #}
+#   }
+#   if(return_value == "-2loglik") {
+#     ret <- -2*sum(log(lik_hum))
+#     if(is.infinite(ret) || is.nan(ret)) {
+#       return(1e+300)
+#     } else {
+#       return(ret)
+#     }
+#   }
+#   if(return_value == "likelihood_by_trial") return(lik_hum)
+#   
+# }
+
+```
+
+#Second attempt at QL algorithm with states: No guessing of initial states
+```{r}
 Q_learn_states <- function(par,data,return_value,gamma){
@@
 
-  #gamma <- 0.9
-
   #Define matrix of state spaces for each game 
@@
   for(t in 1:nrow(data)) {
+
     t_game <- data[t,"game"]
@@
       lik_hum[t] <- 1/nopts
-      # Randomly select prev_state and actions for first round
-      curr_state <- sample(state_vec, size = 1)
-      h_act <- sample(colnames(Q_vals), size =1)
-      ai_act <- sample(colnames(Q_vals), size =1)
-      reward <- 0
 
@@
       # Get past human action and associated reward 
-      h_act <- as.character(data[t-1,"h_action"])
-      ai_act <- as.character(data[t-1,"a_action"])
-      reward <- as.numeric(data[t-1,"score"])
-    }
-
-    # cat(curr_state, " This is the previous state", "\n")
+      h_act_prev <- as.character(data[t-1,"h_action"])
+      ai_act_prev <- as.character(data[t-1,"a_action"])
+      curr_state <- paste0(h_act_prev,ai_act_prev)
+
+      h_act <- as.character(data[t,"h_action"])
+      ai_act <- as.character(data[t,"a_action"])
+      reward <- as.numeric(data[t,"score"])
+
       new_state <- paste0(h_act,ai_act)
-    # cat(new_state,"This is new state","\n")
-
-    # Q_learning: update rule (time  = t-1)
+
+      # Assume human chooses action probabilistically using softmax on Q values
+      probs <- exp(Q_vals[curr_state,]/beta)/sum(exp(Q_vals[curr_state,]/beta))
+      # Get actual human next action and compute likelihood
+      act_index <- match(h_act, colnames(Q_vals))
+
+      lik_hum[t] <- probs[[act_index]]
+
+       # Q_learning: update rule (time = t)
       Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
-
-    # Assume human chooses action probabilistically using softmax on Q values
-    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
-    #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }
-
-    # Get actual human action and compute likelihood
-    h_act <- as.character(data[t,"h_action"])
-    act_index <- match(h_act, colnames(Q_vals))
-    lik_hum[t] <- probs[[act_index]]
 
@@
       curr_state <- new_state
-    #}
+
+    }
+
   }
@@
 }
+
+```
+
+```{r}
+# data34 <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")
+# Q_learn_states(c(5, 0.5),data34 ,return_value = "likelihood_by_trial",gamma = 0 )
 
@@
 
-write.csv(All_results,file="All_results.csv",row.names = FALSE)
+write.csv(All_results,file="exp1_all_results.csv",row.names = FALSE)
 

### 2020-09-04 exp1_hmm_strategies.Rmd
fixed Q learning bugs

---
title: "Hidden Markov strategy model"
author: "Maarten Speekenbrink"
date: "25/08/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(depmixS4)
```

```{r define-dummy-response}
setClass("dummyResponse", contains="response")

setGeneric("dummyResponse", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("dummyResponse"))

setMethod("dummyResponse", 
    signature(y="ANY"), 
    function(y,pstart=NULL,fixed=NULL, ...) {
      y <- matrix(y,length(y))
  		x <- matrix(1)
  		parameters <- list()
  		npar <- 0
      mod <- new("dummyResponse",parameters=parameters,fixed=logical(0),x=x,y=y,npar=npar)
      mod
	}
)

setMethod("show","dummyResponse",
    function(object) {
        cat("Dummy for fixed likelihood Model \n")
    }
)

setMethod("dens","dummyResponse",
  function(object,log=FALSE) {
   if(log) log(as.numeric(object@y)) else as.numeric(object@y)
  }
)

setMethod("getpars","dummyResponse",
    function(object,which="pars",...) {
        switch(which,
            "pars" = {
                pars <- numeric(0)
            },
            "fixed" = {
                pars <- logical(0)
            }
        )
        return(pars)
    }
)

setMethod("setpars","dummyResponse",
    function(object, values, which="pars", ...) {
        npar <- npar(object)
        if(length(values)!=npar) stop("length of 'values' must be",npar)
        # determine whether parameters or fixed constraints are being set
		nms <- ""
		switch(which,
		  "pars"= {
		      },
		  "fixed" = {
		    }
		  )
      names(object@parameters) <- nms
      return(object)
    }
)

setMethod("fit","dummyResponse",
    function(object,w) {
		  return(object)
	}
)

setMethod("predict","dummyResponse", 
    function(object) {
        ret <- object@y
        return(ret)
    }
)
```

```{r}
# we need to have "dat" available and lik_by_trial
QLS_lik <- lik_by_trial$QLS_lik
QLS_lik[which(QLS_lik == 0)] <- .001
QLS_lik[is.na(QLS_lik)] <- .33 # this is a hack; there shouldn't be any missing values
Bayes_NT_lik <- lik_by_trial$Bayes_NT_lik
Bayes_Tr_lik <- lik_by_trial$Bayes_Tr_lik

nsubject <- length(unique(dat$human_id)) # number of participants
ngame <- 3 # number of games
ntrial <- c(50,50,50) # numer of trials in each game

rModels <- list(
  list(
	  dummyResponse(QLS_lik)
	),
	list(
		dummyResponse(Bayes_NT_lik)
	),
  list(
    dummyResponse(Bayes_Tr_lik)
  )
)

trstart <- matrix(c(0.8,0.1,0.1,0.1,0.8,0.1,.1,.1,.8),ncol=3)
transition <- list()
transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))

instart <- c(1/3,1/3,1/3)
inMod <- transInit(~1,nstates=3,pstart=instart,family=multinomial("identity"),data=data.frame(rep(1,nsubject*ngame)))

mod <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))

fmod <- fit(mod, emcontrol=em.control(random.start=FALSE))

# No switching. Force off diagonal initial elements of transtion matrix to 0
trstart <- matrix(c(1,0,0,0,1,0,0,0,1),ncol=3)
transition <- list()
transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))

mod_noswitch <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))

fmod_noswitch <- fit(mod_noswitch, emcontrol=em.control(random.start=FALSE))

# p-value for comparison between a model with strategy switches and one without:

1-pchisq(-2*as.numeric(logLik(fmod_noswitch)) - (-2*as.numeric(logLik(fmod))),df=6)

```

### 2020-09-04 exp1_lik_by_trial.Rmd
added lik by trial exp 2
fixed Q learning bugs

@@
 
-dat <- read.csv("exp1_data.csv")
+dat <- read.csv("data20180719.csv")
 #####
@@
 
-optim_results <- read.csv("All_results.csv")
+optim_results <- read.csv("exp1_all_results.csv")
 
@@
 
-# dat <- as_tibble(dat) %>% group_by(human_id,game)
+# transform 'winner' variable in numeric score
+dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
+# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
+dat$block <- as.numeric(cut(dat$round,2))
+
+# recode actions to make them equal to the codes in these files
+dat$h_action <- recode(dat$human_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
+dat$a_action <- recode(dat$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
+
+# Prepping data for Bayesian code
+dat <- as_tibble(dat) %>% group_by(human_id,game)
 dat <- dat %>%
@@
 ```{r}
-# All_results <- data.frame()
-# for(id in unique(dat$human_id)) {
-#   All_results <- rbind(All_results,
-#                        data.frame(
-#                          "ID" = id,
-#                          "condition" = dat[dat$human_id==id,"condition"][1],
-#                          "Random_BIC" = -2*(100*log(1/3) + 50*log(1/5)),
 
-lik_by_trial <- data.frame()
+dat <- as.data.frame(dat)                       
+exp1_lik_by_trial <- data.frame()
 
@@
   # QLS likelihoods 
-  pars_QLS <- unlist(filter(optim_results, ID == id)%>%select(QL_states_alpha,QL_states_Beta))
-  tdat$QLS_lik <- Q_learn_states(pars_QLS,tdat,"likelihood_by_trial",gamma = 0)
+  pars_QLS <- unlist(filter(optim_results, ID == id)%>%select(QL_states_Beta,QL_states_alpha))
+  QLS_lik <- Q_learn_states(pars_QLS ,tdat,"likelihood_by_trial",gamma = 0)
 
@@
   theta_NT <- unlist(filter(optim_results, ID == id)%>%select(theta_no_transfer))
-  tdat$Bayes_NT_lik <- exp1_Bayes_model_LL(theta_NT ,data = tdat, generalize = "no", "likelihood_by_trial")
+  Bayes_NT_lik <- exp1_Bayes_model_LL(theta_NT ,tdat, generalize = "no", "likelihood_by_trial")
 
@@
   theta_Tr <- unlist(filter(optim_results, ID == id)%>%select(theta_transfer))
-  tdat$Bayes_Tr_lik <- exp1_Bayes_model_LL(theta_Tr ,data = tdat, generalize = "game", "likelihood_by_trial")
+  Bayes_Tr_lik <- exp1_Bayes_model_LL(theta_Tr ,data = tdat, generalize = "game", "likelihood_by_trial")
 
-  lik_by_trial <- rbind(lik_by_trial,tdat)
+  exp1_lik_by_trial <- rbind(exp1_lik_by_trial,
+                        data.frame(
+                          "human_id" = id,
+                          "condition" = dat$condition,
+                          "game" = dat$game,
+                          "round" = dat$round,
+                          "QLS_lik" = QLS_lik,
+                          "Bayes_NT_lik" = Bayes_NT_lik,
+                          "Bayes_Tr_lik" = Bayes_Tr_lik
+
+                        ))
 }
+
+```
+
+```{r}
+
+which(exp1_lik_by_trial$QLS_lik == 1.0 )
+
 ```
@@
 library(ggplot2)
+library(dplyr)
+library(tidyr)
 
-mean_lik <- lik_by_trial %>%
+mean_lik <- exp1_lik_by_trial %>%
   select(human_id,condition,game, round,QLS_lik,Bayes_NT_lik,Bayes_Tr_lik) %>%

### 2020-09-08 Experiment_2/exp2_hmm_strategies.Rmd
fixed bugs in report

--- 2020-09-04 exp1_hmm_strategies.Rmd
@@
 # we need to have "dat" available and lik_by_trial
-QLS_lik <- lik_by_trial$QLS_lik
-QLS_lik[which(QLS_lik == 0)] <- .001
-QLS_lik[is.na(QLS_lik)] <- .33 # this is a hack; there shouldn't be any missing values
-Bayes_NT_lik <- lik_by_trial$Bayes_NT_lik
-Bayes_Tr_lik <- lik_by_trial$Bayes_Tr_lik
+QLS_lik <- lik_by_trial_2$QLS_lik
+Bayes_NT_lik <- lik_by_trial_2$Bayes_NT_lik
+Bayes_Tr_lik <- lik_by_trial_2$Bayes_Tr_lik
 
-nsubject <- length(unique(dat$human_id)) # number of participants
-ngame <- 3 # number of games
-ntrial <- c(50,50,50) # numer of trials in each game
+nsubject <- length(unique(lik_by_trial_2$human_id)) # number of participants
+ngame <- 12 # number of games
+#ntrial <- c(60,60,60)
+
+ntrial <- c(20,20,10,10,20,20,10,10,20,20,10,10) # number of trials in each game
 
@@
 
-fmod <- fit(mod, emcontrol=em.control(random.start=FALSE))
+fmod <- fit(mod, emcontrol=em.control(random.start=TRUE))
+
+summary(fmod,compact=FALSE)
+```
+
+```{r}
+
+# Create table for each trial and calc proportions of states 
+# Check book draft for weather prediction data 
+# p <- posterior(fmod)[60:66,1]
+# p
+
+forwardbackward(fmod)$gamma
+#check section called decoding
+
+```
+
+```{r}
 
@@
 
+# Use bootstrapped likeihood ratio test....(see chapter 2)
+
 ```

### 2020-09-08 Report/draft_report_v2.Rmd
fixed bugs in report

--- 2020-08-13 Report/draft_report_v1.Rmd
@@
 title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-shorttitle        : "Draft-1"
+shorttitle        : "Draft-2"
 
@@
 library(magick)
+library(depmixS4)
 ```
@@
 Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p <.0001), while there was no significant difference between block scores for the other two games.
-This is indicative of the significant within game transfer within the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
+This is indicative of the significant within game learning happening in the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
 There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent.
@@
 
-As a measure for learning transfer, we focus on participants’ scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
-A group of players with no experience of the game are expected to have scores not significantly different from 0.
+As a measure for learning transfer, we focus on participants’ scores in the first 5 rounds excluding the initial round (rounds 2-6).
+We exclude the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response, and therefore we cannot expect the participants to exhibit any learned best responses either.
+A group of players with no experience of the game are expected to have scores not significantly different from 0 over the early rounds of a new game, as was the case in RPS.
 Any significantly positive group average scores would therefore reflect prior learning from past experiences.
@@
 
-apa_lm1 <- apa_print(exp1_early_anova)
+#apa_lm1 <- apa_print(exp1_early_anova)
 
@@
 
-All_comp_results <- read.csv(file="../All_results.csv")
-exp1_comp_table <- table(All_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(All_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])
+exp1_comp_results <- read.csv(file="../exp1_all_results.csv")
+exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])
 
@@
   tr_score <- sum(early_dat$score)
-  id_results <- subset(All_comp_results, ID == id)
+  id_results <- subset(exp1_comp_results, ID == id)
   min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)
@@
 
-```{r exp1-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 1", fig.align='center'}
+```{r exp1-comp-models, fig.cap = "Experiment 1 - Histogram of best fitting computational models by condition", fig.align='center'}
 
@@
 
-```{r exp1-cumScores, fig.cap = "Average cumulative scores of participants in experiment 1 by best fitting model", fig.align='center'}
+```{r exp1-cumScores, fig.cap = "Experiment 1 - Average cumulative scores of participants by best fitting model", fig.align='center'}
 p5 <- ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
@@
 
-p5+ labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
+p5 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
+```
+
+However, this is at odds with the findings from the previous section regarding learning transfer: If indeed most participants use Q-learning with states to choose their actions, then they should not be able to transfer learning to the early rounds of the new game.
+In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Theory of Mind models with and without the possibility of across game transfer.
+
+Figure\ \@ref(fig:exp1-lik-by-tr) shows that in the later games, the likelihood for the ToM models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of ToM models.
+
+```{r, include= FALSE}
+
+exp1_lik_by_trial  <- read.csv("../exp1_lik_by_trial.csv")
+
+mean_lik <- exp1_lik_by_trial %>%
+  dplyr::select(human_id,condition,game, round, QLS_lik, Bayes_NT_lik, Bayes_Tr_lik) %>%
+  group_by(condition,game,round) %>%
+  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
+            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
+            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
+
+mean_lik$game <- factor(mean_lik$game,levels=c("rps","fwg","numbers"))
+
+data_long <- gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
+
+```
+
+```{r exp1-lik-by-tr, fig.cap = "Experiment 1 Likelihood by trial by game and opponent faced", fig.align='center'}
+# make sure the different games are ordered in the way they were played
+# data_long$game <- factor(data_long$game,levels=c("rps","fwg","numbers"))
+ggplot(data_long,aes(x=round,y=probability,colour=strategy)) +
+  geom_line() +
+  facet_grid(game~condition)
+
 ```
@@
 
-```{r exp2-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 2", fig.align='center'}
+```{r exp2-comp-models, fig.cap = "Experiment 2 Histogram of best fitting computational models by condition", fig.align='center'}
 
-#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
 par(las=2) # make label text perpendicular to axis
@@
 
-```{r exp2-cumScores, fig.cap = "Average cumulative scores of participants in experiment 2 by best fitting model", fig.align='center'}
+```{r exp2-cumScores, fig.cap = "Experiment 2 Average cumulative scores of participants by best fitting model", fig.align='center'}
 
@@
 Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
-Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance, folowed by a model in which both within and between trasnfer of opponent models is allowed (BT).
+Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance (although it only fit 2 participants best), followed by a model in which both within and between trasnfer of opponent models is allowed (BT).
 The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive).
-As expected, random play as well as self-tuning EWA were at the bottom of cumulative performance.
+As expected, random play was at the bottom of cumulative performance.
+
+As in experiment 1, we want to understand the dynamic of strategy choice by plotting the likelihood by trial for each strategy, using the optimal parameters found when fitting the model.
+Figure\ \@ref(fig:exp2-lik-by-tr) shows that, as in experiment 1, ToM models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
+In the third and mosre dissimilar game, we get a result that is different from experiment 1.
+In this instance, the likelihoods of the ToM models stay constant and close to their initial values.
+
+```{r, include = FALSE }
+
+exp2_lik_by_trial <- read.csv("../Experiment_2/exp2_lik_by_trial.csv")
+
+mean_lik_2 <- exp2_lik_by_trial %>%
+  dplyr::select(human_id,game,stage,round_condition, round, QLS_lik, QLS_lik_within, Bayes_NT_lik, Bayes_Tr_lik) %>%
+  group_by(game,stage,round) %>%
+  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
+            mean_QLS_within_lik = mean(QLS_lik_within, na.rm = TRUE),
+            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
+            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
+
+mean_lik_2$game <- factor(mean_lik_2$game,levels=c("rps","fwg","shootout"))
+
+data_long2 <- gather(mean_lik_2, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
+```
+
+```{r exp2-lik-by-tr, fig.cap = "Experiment2 likelihood by trial by game and opponent faced", fig.align ='center'}
+# make sure the different games are ordered in the way they were played
+# data_long2$game <- factor(data_long$game,levels=c("rps","fwg","shootout"))
+ggplot(data_long2,aes(x=round,y=probability,colour=strategy)) +
+  geom_line() +
+  facet_grid(game~stage)
+
+```
+
+## Using Hidden Markov Model to explore strategy switching
+
+The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative of participants switching between strategies as the games progressed.
+Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the ToM based strategies fit observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
+
+In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q learning with state space consisting of previous round play, ToM based model with and without opponent model transfer).
+Hidden Markov models are useful tools to explore structure in observed time series.
+They are named because of two properties: First, they make the assumption that any observable action at time t results from a process whose state at time t , named $S_{t}$ is "hidden" from the observer.
+Second, it also assumes that this hidden process has a Markov property, meaning that given state $S_{t-1}$, the value of $S_{t}$ is independent of all states occuring before time $t-1$.
+We also assume that $S_{t}$ has a discrete probability distribution in that it take one of K discrete values.
+The model is therefore specified by initial probabilities of being in each state ${1,2,...,K}$ and transition probabilities for moving from state $i$ to state $j$.
+These probabilities are fit using obsserved actiosn generated from these hidden states.
+
+Using the R DepmixS4 package, we fit a total of two HMMs.
+In the first model, we allow for a non-nil probability of players transitioning from one state (strategy) to another.
+In the second model, we assume that such switching does not happen, and as such assume implicitly that when players start with a particular strategy, they continue using it throughout the game.
+We then compare the likleihoods of each HMM model using a likelihood ration test.
+In experiment 1, the HMM model with swithcing has a significantly higher likelihood than the non-swithcing one (p-value = 0.00).
+The switching model in experiment two has also significantly higher likelihood (p-value = 0.00).
+On top of indications from looking at the liklihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
 

### 2020-09-08 Report/draft_report_v2.tex
fixed bugs in report

--- 2020-09-04 Report/draft_report_v1.tex
@@
 
-\shorttitle{Draft-1}
+\shorttitle{Draft-2}
 \affiliation{
@@
 
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-avg-scores-game-1}
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-avg-scores-game-1}
 
@@
 
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-3factor-plot-1}
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-3factor-plot-1}
 
@@
 Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p \textless{}.0001), while there was no significant difference between block scores for the other two games.
-This is indicative of the significant within game transfer within the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
+This is indicative of the significant within game learning happening in the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
 There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, \(\eta^{2}\) = 0.01), which indicates, as seen in Figure~\ref{fig:exp1-3factor-plot} that within-game learning changes across games also depend on the sophistication of the opponent.
@@
 
-As a measure for learning transfer, we focus on participants' scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
-A group of players with no experience of the game are expected to have scores not significantly different from 0.
+As a measure for learning transfer, we focus on participants' scores in the first 5 rounds excluding the initial round (rounds 2-6).
+We exclude the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response, and therefore we cannot expect the participants to exhibit any learned best responses either.
+A group of players with no experience of the game are expected to have scores not significantly different from 0 over the early rounds of a new game, as was the case in RPS.
 Any significantly positive group average scores would therefore reflect prior learning from past experiences.
@@
 
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-score-by-opp-1}
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-score-by-opp-1}
 
@@
 
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-score-by-opp-1}
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-score-by-opp-1}
 
@@
 
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-early-scores-1}
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-early-scores-1}
 
@@
 
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-comp-models-1}
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-comp-models-1}
 
@@
 
-\caption{Histogram of best fitting computational models by condition for experiment 1}\label{fig:exp1-comp-models}
+\caption{Experiment 1 - Histogram of best fitting computational models by condition}\label{fig:exp1-comp-models}
 \end{figure}
@@
 
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-cumScores-1}
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-cumScores-1}
 
@@
 
-\caption{Average cumulative scores of participants in experiment 1 by best fitting model}\label{fig:exp1-cumScores}
+\caption{Experiment 1 - Average cumulative scores of participants by best fitting model}\label{fig:exp1-cumScores}
+\end{figure}
+
+However, this is at odds with the findings from the previous section regarding learning transfer: If indeed most participants use Q-learning with states to choose their actions, then they should not be able to transfer learning to the early rounds of the new game.
+In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Theory of Mind models with and without the possibility of across game transfer.
+
+Figure~\ref{fig:exp1-lik-by-tr} shows that in the later games, the likelihood for the ToM models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of ToM models.
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-lik-by-tr-1}
+
+}
+
+\caption{Experiment 1 Likelihood by trial by game and opponent faced}\label{fig:exp1-lik-by-tr}
 \end{figure}
@@
 
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-comp-models-1}
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-comp-models-1}
 
@@
 
-\caption{Histogram of best fitting computational models by condition for experiment 2}\label{fig:exp2-comp-models}
+\caption{Experiment 2 Histogram of best fitting computational models by condition}\label{fig:exp2-comp-models}
 \end{figure}
@@
 
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-cumScores-1}
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-cumScores-1}
 
@@
 
-\caption{Average cumulative scores of participants in experiment 2 by best fitting model}\label{fig:exp2-cumScores}
+\caption{Experiment 2 Average cumulative scores of participants by best fitting model}\label{fig:exp2-cumScores}
 \end{figure}
@@
 Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
-Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance, folowed by a model in which both within and between trasnfer of opponent models is allowed (BT).
+Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance (although it only fit 2 participants best), followed by a model in which both within and between trasnfer of opponent models is allowed (BT).
 The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive).
-As expected, random play as well as self-tuning EWA were at the bottom of cumulative performance.
+As expected, random play was at the bottom of cumulative performance.
+
+As in experiment 1, we want to understand the dynamic of strategy choice by plotting the likelihood by trial for each strategy, using the optimal parameters found when fitting the model.
+Figure~\ref{fig:exp2-lik-by-tr} shows that, as in experiment 1, ToM models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
+In the third and mosre dissimilar game, we get a result that is different from experiment 1.
+In this instance, the likelihoods of the ToM models stay constant and close to their initial values.
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-lik-by-tr-1}
+
+}
+
+\caption{Experiment2 likelihood by trial by game and opponent faced}\label{fig:exp2-lik-by-tr}
+\end{figure}
+
+\hypertarget{using-hidden-markov-model-to-explore-strategy-switching}{%
+\subsection{Using Hidden Markov Model to explore strategy switching}\label{using-hidden-markov-model-to-explore-strategy-switching}}
+
+The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative of participants switching between strategies as the games progressed.
+Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the ToM based strategies fit observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
+
+In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q learning with state space consisting of previous round play, ToM based model with and without opponent model transfer).
+Hidden Markov models are useful tools to explore structure in observed time series.
+They are named because of two properties: First, they make the assumption that any observable action at time t results from a process whose state at time t , named \(S_{t}\) is \enquote{hidden} from the observer.
+Second, it also assumes that this hidden process has a Markov property, meaning that given state \(S_{t-1}\), the value of \(S_{t}\) is independent of all states occuring before time \(t-1\).
+We also assume that \(S_{t}\) has a discrete probability distribution in that it take one of K discrete values.
+The model is therefore specified by initial probabilities of being in each state \({1,2,...,K}\) and transition probabilities for moving from state \(i\) to state \(j\).
+These probabilities are fit using obsserved actiosn generated from these hidden states.
+
+Using the R DepmixS4 package, we fit a total of two HMMs.
+In the first model, we allow for a non-nil probability of players transitioning from one state (strategy) to another.
+In the second model, we assume that such switching does not happen, and as such assume implicitly that when players start with a particular strategy, they continue using it throughout the game.
+We then compare the likleihoods of each HMM model using a likelihood ration test.
+In experiment 1, the HMM model with swithcing has a significantly higher likelihood than the non-swithcing one (p-value = 0.00).
+The switching model in experiment two has also significantly higher likelihood (p-value = 0.00).
+On top of indications from looking at the liklihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
 

### 2020-09-08 comp_model_1019.Rmd
fixed bugs in report

@@
 ```{r}
-load("QL_modelling.RData")
-load("QL_states_modelling.RData")
-load("EWA_modelling.RData")
-load("EWA_self_modelling.RData")
-load("MBM_modelling.RData")
-load("EWA_states_modelling.RData")
+# load("QL_modelling.RData")
+# load("QL_states_modelling.RData")
+# load("EWA_modelling.RData")
+# load("EWA_self_modelling.RData")
+# load("MBM_modelling.RData")
+# load("EWA_states_modelling.RData")
 

### 2020-09-08 exp1_lik_by_trial.Rmd
fixed bugs in report

@@
                           "Bayes_Tr_lik" = Bayes_Tr_lik
+                        ))
+  #cat(as.character(Bayes_Tr_lik[c(1,51,101)]))
+}
 
-                        ))
-}
+write.csv(exp1_lik_by_trial,file="exp1_lik_by_trial.csv",row.names = FALSE)
 
@@
 
-which(exp1_lik_by_trial$QLS_lik == 1.0 )
+summary(exp1_lik_by_trial$QLS_lik == 1.0 )
+summary(exp1_lik_by_trial$QLS_lik == 0.0 )
+summary(is.na(exp1_lik_by_trial$QLS_lik))
+
+For
 

### 2020-09-09 Experiment_2/exp2_hmm_strategies.Rmd
added posterior plots

@@
 
-# Create table for each trial and calc proportions of states 
+# Adding posterior probabilities to original data for each state 
 # Check book draft for weather prediction data 
@@
 
-forwardbackward(fmod)$gamma
+lik_by_trial_2["post_QLS"] <- forwardbackward(fmod)$gamma[,1]
+lik_by_trial_2["post_Bayes_NT"] <- forwardbackward(fmod)$gamma[,2]
+lik_by_trial_2["post_Bayes_Tr"] <- forwardbackward(fmod)$gamma[,3]
+
 #check section called decoding

### 2020-09-09 Report/draft_report_v2.Rmd
added posterior plots

@@
 
-bibliography      : ["Mendeley.bib"]
+bibliography      : ["Mendeley2.bib"]
 # csl               : "apa-6th-edition.csl"
@@
 There is no possibility of ties in this game.
-Figure XXXXXXXXX shows a snapshot of play in the shootout game.
+Figure\ \@ref(fig:screenshot-shootout)  shows a snapshot of play in the shootout game.
 What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
@@
 As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
+
+```{r screenshot-shootout, fig.cap = "Screenshot of the shootout game", fig.align='center'}
+
+knitr::include_graphics("images/shootout.png")
+```
 
@@
   group_by(condition,game,round) %>%
-  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
+  dplyr::summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
             mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
@@
 
-data_long <- gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
+data_long <- tidyr::gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
 
@@
 
-Using the R DepmixS4 package, we fit a total of two HMMs.
+sing the R DepmixS4 package, we fit a total of two HMMs.
 In the first model, we allow for a non-nil probability of players transitioning from one state (strategy) to another.
@@
 We then compare the likleihoods of each HMM model using a likelihood ration test.
-In experiment 1, the HMM model with swithcing has a significantly higher likelihood than the non-swithcing one (p-value = 0.00).
+
+### Experiment 1:
+```{r define-dummy-response, include=FALSE}
+setClass("dummyResponse", contains="response")
+
+setGeneric("dummyResponse", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("dummyResponse"))
+
+setMethod("dummyResponse", 
+    signature(y="ANY"), 
+    function(y,pstart=NULL,fixed=NULL, ...) {
+      y <- matrix(y,length(y))
+  		x <- matrix(1)
+  		parameters <- list()
+  		npar <- 0
+      mod <- new("dummyResponse",parameters=parameters,fixed=logical(0),x=x,y=y,npar=npar)
+      mod
+	}
+)
+
+setMethod("show","dummyResponse",
+    function(object) {
+        cat("Dummy for fixed likelihood Model \n")
+    }
+)
+
+setMethod("dens","dummyResponse",
+  function(object,log=FALSE) {
+   if(log) log(as.numeric(object@y)) else as.numeric(object@y)
+  }
+)
+
+setMethod("getpars","dummyResponse",
+    function(object,which="pars",...) {
+        switch(which,
+            "pars" = {
+                pars <- numeric(0)
+            },
+            "fixed" = {
+                pars <- logical(0)
+            }
+        )
+        return(pars)
+    }
+)
+
+setMethod("setpars","dummyResponse",
+    function(object, values, which="pars", ...) {
+        npar <- npar(object)
+        if(length(values)!=npar) stop("length of 'values' must be",npar)
+        # determine whether parameters or fixed constraints are being set
+		nms <- ""
+		switch(which,
+		  "pars"= {
+		      },
+		  "fixed" = {
+		    }
+		  )
+      names(object@parameters) <- nms
+      return(object)
+    }
+)
+
+setMethod("fit","dummyResponse",
+    function(object,w) {
+		  return(object)
+	}
+)
+
+setMethod("predict","dummyResponse", 
+    function(object) {
+        ret <- object@y
+        return(ret)
+    }
+)
+```
+
+```{r, include=FALSE}
+
+## EXPERIMENT 1 Data
+
+QLS_lik <- exp1_lik_by_trial$QLS_lik
+# QLS_lik[which(QLS_lik == 0)] <- .001
+# QLS_lik[is.na(QLS_lik)] <- .33 # this is a hack; there shouldn't be any missing values
+Bayes_NT_lik <- exp1_lik_by_trial$Bayes_NT_lik
+Bayes_Tr_lik <- exp1_lik_by_trial$Bayes_Tr_lik
+
+nsubject <- length(unique(exp1_lik_by_trial$human_id)) # number of participants
+ngame <- 3 # number of games
+ntrial <- c(50,50,50) # numer of trials in each game
+
+rModels <- list(
+  list(
+	  dummyResponse(QLS_lik)
+	),
+	list(
+		dummyResponse(Bayes_NT_lik)
+	),
+  list(
+    dummyResponse(Bayes_Tr_lik)
+  )
+)
+
+trstart <- matrix(c(0.8,0.1,0.1,0.1,0.8,0.1,.1,.1,.8),ncol=3)
+transition <- list()
+transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
+transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
+transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
+
+instart <- c(1/3,1/3,1/3)
+inMod <- transInit(~1,nstates=3,pstart=instart,family=multinomial("identity"),data=data.frame(rep(1,nsubject*ngame)))
+
+mod1 <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
+
+fmod1 <- fit(mod1, emcontrol=em.control(random.start=FALSE))
+```
+
+```{r no-switch, include =FALSE}
+
+# No switching. Force off diagonal initial elements of transtion matrix to 0
+trstart <- matrix(c(1,0,0,0,1,0,0,0,1),ncol=3)
+transition <- list()
+transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
+transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
+transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
+
+mod1_noswitch <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
+
+fmod1_noswitch <- fit(mod1_noswitch, emcontrol=em.control(random.start=FALSE))
+
+# p-value for comparison between a model with strategy switches and one without:
+
+1-pchisq(-2*as.numeric(logLik(fmod1_noswitch)) - (-2*as.numeric(logLik(fmod1))),df=6)
+```
+```{r, include = FALSE}
+
+exp1_lik_by_trial["post_QLS"] <- forwardbackward(fmod1)$gamma[,1]
+exp1_lik_by_trial["post_Bayes_NT"] <- forwardbackward(fmod1)$gamma[,2]
+exp1_lik_by_trial["post_Bayes_Tr"] <- forwardbackward(fmod1)$gamma[,3]
+
+mean_post_1 <- exp1_lik_by_trial %>%
+  dplyr::select(human_id,game,condition, round, post_QLS, post_Bayes_Tr) %>%
+  group_by(game,condition, round) %>%
+  summarise(QLS_posterior = mean(post_QLS, na.rm = TRUE),
+            Bayes_Transfer_posterior = mean(post_Bayes_Tr, na.rm = TRUE))
+
+mean_post_1$game <- factor(mean_post_1$game,levels=c("rps","fwg","numbers"))
+
+data_long_post1 <- gather(mean_post_1, strategy, probability, QLS_posterior,Bayes_Transfer_posterior, factor_key=TRUE)
+
+```
+
+```{r exp1-posteriors-plot, fig.cap = "Experiment1 posterior probability of strategies by game and opponent faced", fig.align ='center'}
+
+ggplot(data_long_post1,aes(x=round,y=probability,colour=strategy)) +
+  geom_line() +
+  facet_grid(game~condition)
+
+```
+
+In experiment 1, the HMM model with swithcing has a significantly higher likelihood than the non-switching one (p-value = 0.00).
+This is further statistical evidence in favour of the hypothesis that participants switch between strategies.
+In order to understand at which stage of the games the switching might happen, and whether there are any differences between games and type of opponents faced, we plot in Figure\ \@ref(fig:exp1-posteriors-plot) the average (across participants) posterior probabilities given our HMM trial by trial for each game and opponent faced.
+Th eposterior probability is the probability that an observation comes from a component distribution a posteriori, i.e.
+given the value of the observation.
+In the first experiment, we can see from the plots of fwg and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the QLS model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
+
+### Experiment 2:
+
+```{r, include =FALSE}
+## EXPERIMENT 2 DATA 
+# we need to have "dat" available and lik_by_trial
+QLS_lik <- exp2_lik_by_trial$QLS_lik
+Bayes_NT_lik <- exp2_lik_by_trial$Bayes_NT_lik
+Bayes_Tr_lik <- exp2_lik_by_trial$Bayes_Tr_lik
+
+nsubject <- length(unique(exp2_lik_by_trial$human_id)) # number of participants
+ngame <- 12 # number of games
+#ntrial <- c(60,60,60)
+
+ntrial <- c(20,20,10,10,20,20,10,10,20,20,10,10) # number of trials in each game
+
+rModels <- list(
+  list(
+	  dummyResponse(QLS_lik)
+	),
+	list(
+		dummyResponse(Bayes_NT_lik)
+	),
+  list(
+    dummyResponse(Bayes_Tr_lik)
+  )
+)
+
+trstart <- matrix(c(0.8,0.1,0.1,0.1,0.8,0.1,.1,.1,.8),ncol=3)
+transition <- list()
+transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
+transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
+transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
+
+instart <- c(1/3,1/3,1/3)
+inMod <- transInit(~1,nstates=3,pstart=instart,family=multinomial("identity"),data=data.frame(rep(1,nsubject*ngame)))
+
+mod <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
+
+fmod <- fit(mod, emcontrol=em.control(random.start=TRUE))
+```
+
+```{r}
+
+exp2_lik_by_trial["post_QLSw"] <- forwardbackward(fmod)$gamma[,1]
+exp2_lik_by_trial["post_Bayes_NT"] <- forwardbackward(fmod)$gamma[,2]
+exp2_lik_by_trial["post_Bayes_Tr"] <- forwardbackward(fmod)$gamma[,3]
+
+mean_post_2 <- exp2_lik_by_trial %>%
+  dplyr::select(human_id,game,stage,round_condition, round, post_QLSw, post_Bayes_Tr) %>%
+  group_by(game,stage, round) %>%
+  summarise(mean_post_QLSw = mean(post_QLSw, na.rm = TRUE),
+            mean_post_Tr = mean(post_Bayes_Tr, na.rm = TRUE))
+
+mean_post_2$game <- factor(mean_post_2$game,levels=c("rps","fwg","shootout"))
+
+data_long_post2 <- gather(mean_post_2, strategy, probability, mean_post_QLSw,mean_post_Tr, factor_key=TRUE)
+
+```
+
+```{r exp2-posteriors-plot, fig.cap = "Experiment2 likelihood by trial by game and opponent faced", fig.align ='center'}
+
+ggplot(data_long_post2,aes(x=round,y=probability,colour=strategy)) +
+  geom_line() +
+  facet_grid(game~stage)
+
+```
+
 The switching model in experiment two has also significantly higher likelihood (p-value = 0.00).
 On top of indications from looking at the liklihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
+The posterior probability plot in Figure\ \@ref(fig:exp2-posteriors-plot) shows switching much more clearly across games ans stages, indicating a robust process.
+The switchign also seems to happen very early one at the beginning of each game and stage, and is also consistently in the same direction: The probability of Bayesian models with transfer being initially high, then decreasing rapidly while the posterior probability of QL-Learning with states and within transfer learning increases rapidly.
 
@@
 
+Our computational modelling allowed us to delve deeper into what might be driving the observed learning transfer.
+Initial modelling of observations using all available data seems to indicated that the most likely model was a Q-learning type model.
+However, as we argued above, that would be inconsistent with the evidence for learning transfer.
+Breaking down likelihoods by trial and fitting a hidden markov model to the data with states being the various strategies that participants are assumes to be using, we showed evidence for within game switching of strategies.
+Participants start the early rounds of a new game acting in a way consistent with a Bayesian Theory of mind level, which would be accurate and generalisable but computationally expensive.
+However, as trials continue, participants seem to switch to a habitual type of learning (QL-models).
+
+Why is this switching happening?
+We believe that participants show flexibility in their use of learning strategies.
+When a new game is started that is similar to a previously played game with the same opponent, participants need a way to transfer prior knowledge of the opponent and apply it to the new game in order to best respond.
+Adopting a Bayesian model based on ToM achieves the goal of trasnfering the opponent model and thus coming up with best responses in the early trials.
+However, Bayesian ToM models are computationally expensive and require a lot of higher order thinking (I think that you think that I think...).
+As such, as the games progresses, they become burdensome and the higher amount of historical interaction in the new game allows participants to have enough data to start using the cognitively cheaper model-free learning strategies such as Q-learning.
+The bias towards less computationally demanding strategies is well established @Kool_2011.
+Moreover, the ability to flexibly switch is also consistent with evidence from the literature on learning strategies in humans, showing that they indeed shift between model-based and model-free learning when the environment requires it @Simon_Daw_11.
+
 \newpage
@@
 Moreover, we showed that participants do transfer their learning to new games with varying degrees of similarity.
-The most likely explanation as we saw is that players build a mental representation of their opponent strategy, rather than rely on associative learning or action-based heuristics.
 The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.
@@
 There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
-Moreover, the computational modelling shows that a significant number of players are still using random strategies in the games.
-Whether this ability depends on engagement with the experiment or on other characteristics of the learner is an open question that more research in the area would hope to answer.
-
+Moreover, the computational modelling shows that it is likely that players start each game using a model-based learning strategy that facilitates generalisation and opponent model transfer, but then switch to behvior that is consistent with a  model-free learning strategy as the experiment goes on.
+This is likely driven by a trade-off between computational complexity and accuracy between model based and model free strategies.
 \newpage
@@
 ```{r create_r-references}
-r_refs(file = "Mendeley.bib")
+r_refs(file = "Mendeley2.bib")
 

### 2020-09-09 Report/draft_report_v2.tex
added posterior plots

@@
 They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-Knez \& Camerer (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+({\textbf{???}}) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
 They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
@@
 There is no possibility of ties in this game.
-Figure XXXXXXXXX shows a snapshot of play in the shootout game.
+Figure~\ref{fig:screenshot-shootout} shows a snapshot of play in the shootout game.
 What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose \enquote{'right}' in the next round, we can win by both choosing \enquote{'left}' and \enquote{'center}'.
@@
 As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
+
+\begin{figure}
+
+{\centering \includegraphics{images/shootout}
+
+}
+
+\caption{Screenshot of the shootout game}\label{fig:screenshot-shootout}
+\end{figure}
 
@@
 We then compare the likleihoods of each HMM model using a likelihood ration test.
-In experiment 1, the HMM model with swithcing has a significantly higher likelihood than the non-swithcing one (p-value = 0.00).
+
+\hypertarget{experiment-1-1}{%
+\subsubsection{Experiment 1:}\label{experiment-1-1}}
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-posteriors-plot-1}
+
+}
+
+\caption{Experiment1 posterior probability of strategies by game and opponent faced}\label{fig:exp1-posteriors-plot}
+\end{figure}
+
+In experiment 1, the HMM model with swithcing has a significantly higher likelihood than the non-switching one (p-value = 0.00).
+This is further statistical evidence in favour of the hypothesis that participants switch between strategies.
+In order to understand at which stage of the games the switching might happen, and whether there are any differences between games and type of opponents faced, we plot in Figure~\ref{fig:exp1-posteriors-plot} the average (across participants) posterior probabilities given our HMM trial by trial for each game and opponent faced.
+Th eposterior probability is the probability that an observation comes from a component distribution a posteriori, i.e.~given the value of the observation.
+In the first experiment, we can see from the plots of fwg and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the QLS model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
+
+\hypertarget{experiment-2-1}{%
+\subsubsection{Experiment 2:}\label{experiment-2-1}}
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-posteriors-plot-1}
+
+}
+
+\caption{Experiment2 likelihood by trial by game and opponent faced}\label{fig:exp2-posteriors-plot}
+\end{figure}
+
 The switching model in experiment two has also significantly higher likelihood (p-value = 0.00).
 On top of indications from looking at the liklihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
+The posterior probability plot in Figure~\ref{fig:exp2-posteriors-plot} shows switching much more clearly across games ans stages, indicating a robust process.
+The switchign also seems to happen very early one at the beginning of each game and stage, and is also consistently in the same direction: The probability of Bayesian models with transfer being initially high, then decreasing rapidly while the posterior probability of QL-Learning with states and within transfer learning increases rapidly.
 
@@
 
+Our computational modelling allowed us to delve deeper into what might be driving the observed learning transfer.
+Initial modelling of observations using all available data seems to indicated that the most likely model was a Q-learning type model.
+However, as we argued above, that would be inconsistent with the evidence for learning transfer.
+Breaking down likelihoods by trial and fitting a hidden markov model to the data with states being the various strategies that participants are assumes to be using, we showed evidence for within game switching of strategies.
+Participants start the early rounds of a new game acting in a way consistent with a Bayesian Theory of mind level, which would be accurate and generalisable but computationally expensive.
+However, as trials continue, participants seem to switch to a habitual type of learning (QL-models).
+
+Why is this switching happening?
+We believe that participants show flexibility in their use of learning strategies.
+When a new game is started that is similar to a previously played game with the same opponent, participants need a way to transfer prior knowledge of the opponent and apply it to the new game in order to best respond.
+Adopting a Bayesian model based on ToM achieves the goal of trasnfering the opponent model and thus coming up with best responses in the early trials.
+However, Bayesian ToM models are computationally expensive and require a lot of higher order thinking (I think that you think that I think\ldots{}).
+As such, as the games progresses, they become burdensome and the higher amount of historical interaction in the new game allows participants to have enough data to start using the cognitively cheaper model-free learning strategies such as Q-learning.
+The bias towards less computationally demanding strategies is well established Wouter Kool, Joseph T.
+McGuire, Zev B.
+Rosen, Matthew M.
+Bovinick (2011).
+Moreover, the ability to flexibly switch is also consistent with evidence from the literature on learning strategies in humans, showing that they indeed shift between model-based and model-free learning when the environment requires it Simon \& Daw (2011).
+
 \newpage
@@
 There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
-Moreover, the computational modelling shows that a significant number of players are still using random strategies in the games.
-Whether this ability depends on engagement with the experiment or on other characteristics of the learner is an open question that more research in the area would hope to answer.
-
+Moreover, the computational modelling shows that it is likely that players start each game using a model-based learning strategy that facilitates generalisation and opponent model transfer, but then switch to behvior that is consistent with a model-free learning strategy as the experiment goes on.
+This is likely driven by a trade-off between computational complexity and accuracy between model based and model free strategies.
 \newpage
@@
 
-\leavevmode\hypertarget{ref-knez2000increasing}{}%
-Knez, M., \& Camerer, C.
-(2000).
-Increasing cooperation in prisoner's dilemmas by establishing a precedent of efficiency in coordination games.
-\emph{Organizational Behavior and Human Decision Processes}, \emph{82}(2), 194--216.
-
 \leavevmode\hypertarget{ref-Lake2017}{}%
@@
 Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
+
+\leavevmode\hypertarget{ref-Simon_Daw_11}{}%
+Simon, D.
+A., \& Daw, N.
+D.
+(2011).
+Environmental statistics and the trade-off between model-based and TD learning in humans.
+\emph{Advances in Neural Information Processing Systems 24: 25th Annual Conference on Neural Information Processing Systems 2011, NIPS 2011}, 1--9.
 
@@
 Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). Does the chimpanzee have a theory of mind.
+
+\leavevmode\hypertarget{ref-Kool_2011}{}%
+Wouter Kool, Joseph T.
+McGuire, Zev B.
+Rosen, Matthew M.
+Bovinick.
+(2011).
+Decision Making and the Avoidance of Cognitive Demand.
+\emph{Experimental Psychology}.
+doi:\href{https://doi.org/10.2996/kmj/1138846322}{10.2996/kmj/1138846322}
 
@@
 
+\leavevmode\hypertarget{ref-Kool_2011}{}%
+Wouter Kool, Joseph T.
+McGuire, Zev B.
+Rosen, Matthew M.
+Bovinick.
+(2011).
+Decision Making and the Avoidance of Cognitive Demand.
+\emph{Experimental Psychology}.
+doi:\href{https://doi.org/10.2996/kmj/1138846322}{10.2996/kmj/1138846322}
+
 \endgroup

### 2020-09-09 comp_model_1019.Rmd
added posterior plots

@@
       act_index <- match(h_act, names(Q_vals))
+      #cat(as.character(act_index))
       lik_hum[t] <- probs[[act_index]]
@@
   # Returns Q-values per trial and predicts choice using softmax
-  beta <- par[1]
-  alpha <- par[2]
+  beta <- par[[1]]
+  alpha <- par[[2]]
 

### 2020-09-09 exp1_lik_by_trial.Rmd
added posterior plots

@@
 library(dplyr)
+library(ggplot2)
 ```
@@
 
-# transform 'winner' variable in numeric score
-dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
-# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
-dat$block <- as.numeric(cut(dat$round,2))
-
-# recode actions to make them equal to the codes in these files
-dat$h_action <- recode(dat$human_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
-dat$a_action <- recode(dat$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
-
-# Prepping data for Bayesian code
+#Prepping data for Bayesian code
 dat <- as_tibble(dat) %>% group_by(human_id,game)
@@
 
+# transform 'winner' variable in numeric score
+dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
+# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
+dat$block <- as.numeric(cut(dat$round,2))
+
+# recode actions to make them equal to the codes in these files
+dat$h_action <- recode(dat$human_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
+dat$a_action <- recode(dat$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
+
 ```
@@
 ```{r}
+dat <-as.data.frame(dat)
+exp1_lik_by_trial <- data.frame()
 
-dat <- as.data.frame(dat)                       
-exp1_lik_by_trial <- data.frame()
+# dat%>% group_by(human_id) %>%
+#   mutate(pars_QLS = as.vector(optim_results%>% dplyr::select(QL_states_Beta,QL_states_alpha))) %>%
+#   mutate(QLS_lik = Q_learn_states(pars_QLS[1,] ,tdat,"likelihood_by_trial",gamma = 0))
 
@@
   # QLS likelihoods 
-  pars_QLS <- unlist(filter(optim_results, ID == id)%>%select(QL_states_Beta,QL_states_alpha))
-  QLS_lik <- Q_learn_states(pars_QLS ,tdat,"likelihood_by_trial",gamma = 0)
+  pars_QLS <- as.vector(filter(optim_results, ID == id)%>% dplyr::select(QL_states_Beta,QL_states_alpha))
+  tdat$QLS_lik <- Q_learn_states(pars_QLS ,tdat,"likelihood_by_trial",gamma = 0)
 
-  # Bayes model no transfer likelihoods
-  theta_NT <- unlist(filter(optim_results, ID == id)%>%select(theta_no_transfer))
-  Bayes_NT_lik <- exp1_Bayes_model_LL(theta_NT ,tdat, generalize = "no", "likelihood_by_trial")
+  #Bayes model no transfer likelihoods
+  theta_NT <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_no_transfer))
+  tdat$Bayes_NT_lik <- exp1_Bayes_model_LL(theta_NT ,data = tdat, generalize = "no", "likelihood_by_trial")
 
   # Bayes model with Transfer likelihood
-  theta_Tr <- unlist(filter(optim_results, ID == id)%>%select(theta_transfer))
-  Bayes_Tr_lik <- exp1_Bayes_model_LL(theta_Tr ,data = tdat, generalize = "game", "likelihood_by_trial")
+  theta_Tr <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_transfer))
+  tdat$Bayes_Tr_lik <- exp1_Bayes_model_LL(theta_Tr ,data = tdat, generalize = "game", "likelihood_by_trial")
 
-  exp1_lik_by_trial <- rbind(exp1_lik_by_trial,
-                        data.frame(
-                          "human_id" = id,
-                          "condition" = dat$condition,
-                          "game" = dat$game,
-                          "round" = dat$round,
-                          "QLS_lik" = QLS_lik,
-                          "Bayes_NT_lik" = Bayes_NT_lik,
-                          "Bayes_Tr_lik" = Bayes_Tr_lik
-                        ))
+  exp1_lik_by_trial <- dplyr::bind_rows(exp1_lik_by_trial,tdat)
+
+  # 
+  # exp1_lik_by_trial <- rbind(exp1_lik_by_trial,
+  #                       data.frame(
+  #                         "human_id" = id,
+  #                         "condition" = dat$condition,
+  #                         "game" = dat$game,
+  #                         "round" = dat$round,
+  #                         "QLS_lik" = QLS_lik,
+  #                         "Bayes_NT_lik" = Bayes_NT_lik,
+  #                         "Bayes_Tr_lik" = Bayes_Tr_lik
+  #                       ))
   #cat(as.character(Bayes_Tr_lik[c(1,51,101)]))
@@
 
-For
-
 ```
@@
 ```{r}
-library(ggplot2)
-library(dplyr)
-library(tidyr)
 
@@
   select(human_id,condition,game, round,QLS_lik,Bayes_NT_lik,Bayes_Tr_lik) %>%
-  group_by(condition,game,round) %>%
-  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
+  group_by(game, condition, round)  %>%
+  dplyr::summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
             mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
@@
 
-mean_lik$game <- factor(mean_lik$game,levels=c("rps","fwg","numbers"))
-
-data_long <- gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
+data_long <- tidyr::gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
 

### 2020-10-30 Experiment_2/Experiment_2_modelling.Rmd
draft3

@@
 
-##Self tuning EWA model
+##Self tuning EWA model (simple, no states)
 
@@
     nopts <- 3
+    # Resets at the beginning of each game and stage
     if(data[t,"round"] == 1) {
@@
 
-      R_t <- rep(0.0,nopts)
-      H_t <- R_t
+      # initialize H_t by looking at first action 
+      a_act <- as.character(game_data[1,"a_action"])
+      H_t <- as.numeric(colnames(Att) == a_act)
 
@@
 
+      # rounds gets initialised at beginning of eahc stage so we can treat them as separate games and use
+      # round as index 
       indx <- data[t,"round"]
+
       # Get reward and past human action
@@
       a_act_prev <- as.character(game_data[indx-1,"a_action"])
+      curr_state <- paste0(h_act_prev,a_act_prev)
 
-      # Estimate phi(t)
-      R_t <- as.numeric(names(Att) == a_act_prev)
-      # cat("This is R(t)",R_t,"\n")
+      h_act <- as.character(game_data[indx,"h_action"])
+      a_act <- as.character(game_data[indx,"a_action"])
+      new_state <- paste0(h_act,a_act)
 
-      H_t <- (H_t*(indx-2) + R_t)/(indx-1)
-      # cat("this is H(t)",H_t,"\n")
+      # Assume human chooses action probabilistically using softmax on Attraction values
+      probs <- exp(lambda*Att[curr_state,])/sum(exp(lambda*Att[curr_state,]))
+
+      # Get actual human action and compute likelihood
+      act_index <- match(h_act, colnames(Att))
+      lik_hum[t] <- probs[[act_index]]
+
+      # Update rule:
+      # Estimate R(t) (recent history) then H(t) (history) then phi(t) (change detector)
+      R_t <- as.numeric(colnames(Att) == a_act)
+      #cat("This is R(t)",R_t,"\n")
+
+      H_t <- (H_t*(indx-1) + R_t)/(indx)
+      #cat("this is H(t)",H_t,"\n")
 
       Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
-      # cat("This is Phit(t)",Phi_t,"\t")
+      #cat("This is Phit(t)",Phi_t,"\t")
 
       # Estimate vector Delta(t)
-
-      delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
+      delta_t <- as.numeric(reward[,a_act] >= as.numeric(game_data[indx,"score"]))
       #cat("this is delta(t)",delta_t,"\n")
 
-      for (i in 1:length(Att)) {
-        action <- as.character(names(Att)[i])
-        # cat("this is current strat",action,"\n")
-        # cat("this is previous humna action",h_act_prev,"\n")
+      # This is a vectorised ST_EWA update rule, easier to follow the loop below in comments
+      state_indx <- match(curr_state,state_vec)
+      Att[state_indx,] <- (Phi_t*N*Att[state_indx,]  + ( delta_t + (1- delta_t)*(colnames(Att) == h_act))*as.numeric(reward[colnames(Att),a_act])) / (Phi_t*N + 1)
 
-        # Attraction vector update rule 
-        Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
-      }
+      ##############
+      # for (i in 1:nopts) {
+      #   action <- as.character(colnames(Att)[i])
+      #   state_indx <- match(curr_state,state_vec)
+      #   #cat("this is the current state index", state_indx, "\n")
+      # 
+      #   # Attraction vector update rule
+      #   Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act))*as.numeric(reward[action,a_act])) / (Phi_t*N + 1)
+      # 
+      # }
+      # 
+      #cat("this is the current Att vector", Att, "\n")
+      ###################
+
       #Update the value of N 
       N <- Phi_t*N + 1
-      #cat(Att,'\n')
 
-      # Assume human chooses action probabilistically using softmax on Attraction values
-      probs <- exp(lambda*Att)/sum(exp(lambda*Att))
-
-      # Get actual human action and compute likelihood
-      h_act <- as.character(game_data[indx,"h_action"])
-      act_index <- match(h_act, names(Att))
-      lik_hum[t] <- probs[[act_index]]
+      #Update the state 
+      curr_state <- new_state 
     }
@@
 }
-
-# exp2_EWA_self(1,test_data,"-2loglik")
-
 ```
@@
 save(exp2_SEWA_modelling,file="exp2_SEWA_modelling.RData")
+```
+
+# Self-Tuning EWA model with states ( and possibly transfer)
+
+```{r}
+
+exp2_STEWA_STATES <- function(par,data,return_value, transfer = TRUE){
+
+  lambda <- par[1]
+  nopts <- 3
+
+  #Define matrix of state spaces for each game 
+  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+  states_RPS <- paste0(G1$Var1,G1$Var2)
+
+  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+  states_FWG <- paste0(G2$Var1,G2$Var2)
+
+  G3 <- expand.grid(c("left","center","right"), c("left","center","right"))    # Left, Center, Right 
+  states_SHOOT <- paste0(G3$Var1,G3$Var2)
+
+  A_RPS = matrix(-0.5,9,3)
+  dimnames(A_RPS) = list(states_RPS, c("R", "P", "S"))
+
+  A_FWG = matrix(-0.5,9,3)
+  dimnames(A_FWG) = list(states_FWG, c("F", "W", "G"))
+
+  A_SHOOT = matrix(-0.5,9,3)
+  dimnames(A_SHOOT) = list(states_SHOOT, c("left","center","right"))
+
+  # # Define reward matrices from the perspective of the row player (human in our case)
+  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
+
+  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
+
+  reward_SHOOT <- t(matrix(c(-1,1,1,1,-1,1,1,1,-1),nrow=3, ncol=3))
+  dimnames(reward_SHOOT) = list(c("left","center","right"), c("left","center","right"))
+
+  # Initiate likelihood by trial vector 
+  lik_hum <- matrix(0.0,nrow(data))
+
+   for(t in 1:nrow(data)) {
+     # Get which game we are playing
+     t_game <- data[t,"game"]
+
+    if (data[t,"round"] == 1)  {
+
+      # chance likelihood :we have no data on previous round.
+      lik_hum[t] <- 1/nopts
+
+      if (!transfer) {
+        # switch and Reset attractions and reward matrices
+        Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, shootout = A_SHOOT)
+        state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, shootout = states_SHOOT)
+        reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, shootout = reward_SHOOT)
+
+        # Get first ai action 
+        a_act <- as.character(data[t,"a_action"])
+        # initialize H_t by looking at first action
+        H_t <- as.numeric(colnames(Att) == a_act)
+
+        # Asumme N(0) = 1 for now...see discussion in paper
+        N_t <- 1.0
+        indx <- 1
+
+      #Code for transfer , we're still in round 1 if loop  
+      } else {
+
+        if (data[t,"stage"] == 1) {
+
+          # switch and Reset attractions and reward matrices
+          Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, shootout = A_SHOOT)
+          state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, shootout = states_SHOOT)
+          reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, shootout = reward_SHOOT)
+          # Get first ai action 
+          a_act <- as.character(data[t,"a_action"])
+          # initialize H_t by looking at first action
+          H_t <- as.numeric(colnames(Att) == a_act)
+          #initialize N_t and index
+          N_t <- 1.0
+          indx <- 1
+
+        #round 1 stage 2
+        } else if (data[t,"stage"] == 2) {
+          Att_opp_1 <- Att
+          H_opp_1 <- H_t
+          N_opp_1 <- N_t
+          indx  <- 1
+          #reset Attractions
+          Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, shootout = A_SHOOT)
+
+        # round 1 stage 3  
+        } else if (data[t,"stage"] == 3) {
+          # we're in end of stage 2, so keep attractions and counts for stage 4
+          Att_opp_2 <- Att
+          H_opp_2 <- H_t
+          N_opp_2 <- N_t
+          indx <- 20
+          # Get attractions and counts from stage 1
+          Att <- Att_opp_1
+          H_t <- H_opp_1
+          N_t <- N_opp_1
+
+        } else if (data[t,"stage"] == 4) {
+          # get attractions and counts from end of stage 2
+          Att <- Att_opp_2
+          H_t <- H_opp_2
+          N_t <- N_opp_2
+          indx <- 20
+        }
+      }
+
+      # Rounds 2 to end 
+    } else {
+
+      #cat("Attraction matrix", Att, "\n")
+
+      # Get reward and past human action
+      h_act_prev <- as.character(data[t-1,"h_action"])
+      a_act_prev <- as.character(data[t-1,"a_action"])
+      curr_state <- paste0(h_act_prev,a_act_prev)
+
+      h_act <- as.character(data[t,"h_action"])
+      a_act <- as.character(data[t,"a_action"])
+      new_state <- paste0(h_act,a_act)
+
+      # Assume human chooses action probabilistically using softmax on Attraction values
+      probs <- exp(lambda*Att[curr_state,])/sum(exp(lambda*Att[curr_state,]))
+
+      # Get actual human action and compute likelihood
+      act_index <- match(h_act, colnames(Att))
+      lik_hum[t] <- probs[[act_index]]
+
+      # Update rule:
+      # Estimate R(t) (recent history) then H(t) (history) then phi(t) (change detector)
+      R_t <- as.numeric(colnames(Att) == a_act)
+      #cat("This is R(t)",R_t,"\n")
+
+      H_t <- (H_t*(indx-1) + R_t)/(indx)
+      #cat("this is H(t)",H_t,"\n")
+
+      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
+      #cat("This is Phit(t)",Phi_t,"\t")
+
+      # Estimate vector Delta(t)
+      delta_t <- as.numeric(reward[,a_act] >= as.numeric(data[t,"score"]))
+      #cat("this is delta(t)",delta_t,"\n")
+
+      # This is a vectorised ST_EWA update rule, easier to follow the loop below in comments
+      state_indx <- match(curr_state,state_vec)
+      Att[state_indx,] <- (Phi_t*N_t*Att[state_indx,]  + ( delta_t + (1- delta_t)*(colnames(Att) == h_act))*as.numeric(reward[colnames(Att),a_act])) / (Phi_t*N_t + 1)
+
+      ##############
+      # for (i in 1:nopts) {
+      #   action <- as.character(colnames(Att)[i])
+      #   state_indx <- match(curr_state,state_vec)
+      #   #cat("this is the current state index", state_indx, "\n")
+      # 
+      #   # Attraction vector update rule
+      #   Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act))*as.numeric(reward[action,a_act])) / (Phi_t*N + 1)
+      # 
+      # }
+      # 
+      #cat("this is the current Att vector", Att, "\n")
+      ###################
+
+      #Update the value of N 
+      N_t <- Phi_t*N_t + 1
+
+      #Update the state 
+      curr_state <- new_state
+
+    }
+   }  
+  if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret) || is.nan(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+
+}
+
+```
+
+```{r}
+exp2_STEWA_STATES(1,test_data,"-2loglik", TRUE)
+
+```
+## Fitting ST_EWA_states WITHOUT transfer 
+```{r, cache=TRUE}
+
+exp2_STEWA_NT <- list()
+for(id in unique(dat_exp2$human_id)) {
+  exp2_STEWA_NT[[id]] <- list()
+  tdat <- subset(dat_exp2,human_id == id)
+#   exp2_STEWA_NT[[id]] <- optim(10.0,fn=exp2_STEWA_STATES,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
+# }
+  exp2_STEWA_NT[[id]] <- DEoptim(fn=exp2_STEWA_STATES, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", FALSE, control=list(trace = FALSE,parallelType=1))
+}
+
+save(exp2_STEWA_NT,file="exp2_STEWA_NT.RData")
+```
+
+## Fitting ST_EWA_states WITH transfer 
+```{r, cache=TRUE}
+
+exp2_STEWA_Tr <- list()
+for(id in unique(dat_exp2$human_id)) {
+  exp2_STEWA_Tr[[id]] <- list()
+  tdat <- subset(dat_exp2,human_id == id)
+#   exp2_STEWA_Tr[[id]] <- optim(10.0,fn=exp2_STEWA_STATES,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
+# }
+  exp2_STEWA_Tr[[id]] <- DEoptim(fn=exp2_STEWA_STATES, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", TRUE, control=list(trace = FALSE,parallelType=1))
+}
+
+save(exp2_STEWA_Tr,file="exp2_STEWA_Tr.RData")
 ```
@@
                          "Random_BIC" = -2*(180*log(1/3)),
-# 
-# #                          # Bayesian updating with/without transfer
-#                          "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
-#                          "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
-#                          "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
-#                          "Naive_BIC" = exp2_Naive[[id]]$value+ 2*log(180),
 
-                         #MS results for Bayesian models
+                         ########## MS results for Bayesian models
                           # Bayesian updating with between and within game transfer
@@
                          "theta_naive" = Bayes_same_game[[id]]$optim$bestmem[1],
-                         #
+                          ###########
 
-                         # # Theta is the parameter governing AI stochasticity. Truth is 0.9
-                         # "theta_transfer" = exp2_BT[[id]]$par[1],
-                         # "theta_no_btw_tr" = exp2_NO_BT[[id]]$par[1],
-                         # "theta_no_tr" =  exp2_NO_Tr[[id]]$par[1],
-                         # "theta_naive" = exp2_Naive[[id]]$par[1],
-                         # # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
-                         # "eps_transfer" = exp2_BT[[id]]$par[2],
-                         # "eps_no_btwn_tr" = exp2_NO_BT[[id]]$par[2],
-                         # "eps_no_tr" = exp2_NO_Tr[[id]]$par[2],
-                         # "eps_naive" = exp2_Naive[[id]]$par[2],
-
-                         # Q-learning with last round states (No within transfer)
+                         ########### Q-learning with last round states (No within transfer)
                          "QL_states_BIC" = exp2_QLS_modelling[[id]]$optim$bestval + 2*log(180),
@@
                          "QL_states_alpha" = exp2_QLS_modelling[[id]]$optim$bestmem[2],
+                         ############
 
-                         # QLS assuming within game transfer
+                         ############# QLS assuming within game transfer
                          "QLS_within_Tr_BIC" = exp2_QLS_within_Tr[[id]]$optim$bestval + 2*log(180),
@@
                          "QLS_within_Tr_alpha" = exp2_QLS_within_Tr[[id]]$optim$bestmem[2],
+                         #############
 
-                         # Self-Tuning EWA (only 1 parameter)
+                         ########## Self-Tuning EWA states NO transfer(only 1 parameter)
                           # BIC
-                         "EWA_self_2LL" = exp2_SEWA_modelling[[id]]$optim$bestval,
-                         "EWA_self_BIC" = exp2_SEWA_modelling[[id]]$optim$bestval + 1*log(180),
+                         "STEWA_NT_2LL" = exp2_STEWA_NT[[id]]$optim$bestval,
+                         "STEWA_NT_BIC" = exp2_STEWA_NT[[id]]$optim$bestval + 1*log(180),
                          #Lambda is a parameter of the softmax choice function (inverse Temperature)
-                         "EWA_self_Lambda" = exp2_SEWA_modelling[[id]]$optim$bestmem[1],
+                         "STEWA_NT_Lambda" = exp2_STEWA_NT[[id]]$optim$bestmem[1],
+                         ###########
 
-                         # Model Based Model
+                          ########## Self-Tuning EWA states WITH transfer (only 1 parameter)
+                          # BIC
+                         "STEWA_Tr_2LL" = exp2_STEWA_Tr[[id]]$optim$bestval,
+                         "STEWA_Tr_BIC" = exp2_STEWA_Tr[[id]]$optim$bestval + 1*log(180),
+                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
+                         "STEWA_Tr_Lambda" = exp2_STEWA_Tr[[id]]$optim$bestmem[1],
+                         #############
+
+                         ########### Model Based Model
                           # BIC
@@
 ```{r}
-# WIth IG results for Bayesian models
-# exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
 
 # WIth MS results for Bayesian models
-exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT", "QL_states","QLS_within","STEWA_NT","STEWA_Tr")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])
 
@@
 ```{r}
-# WITH MS results for bayesian models 
-# exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
-# 
-#  write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
-#  kable(exp2_table_results)
+
 ```
@@
   tot_score <- sum(tdat$score)
-  tot_time <- sum(tdat$human_rt)
-  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
-  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
+  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
   tr_score <- sum(early_dat$score)
@@
 
-  # IG BAYES MODELS 
-  # min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
-  # 
-  # best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
+  # MS BAYES MODELS
+  min_BIC <- apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,min)
 
-  # MS BAYES MODELS
-  min_BIC <- apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
+  best_model <- c("random","TOM_BT","TOM_NBT", "TOM_NT", "QL_states","QLS_within","STEWA_NT","STEWA_Tr")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)]
 
-  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
-
-  # 
   exp2_model_comp <- rbind(exp2_model_comp ,

### 2020-10-30 Report/_main.Rmd
draft3

--- 2020-09-09 Report/draft_report_v2.Rmd
@@
+---
+title             : "Learning to learn in a changing environment"
+shorttitle        : "Learning to learn"
+
+author: 
+  - name          : "Maarten Speekenbrink"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
+    email         : "m.speekenbrink@ucl.ac.uk"
+  - name          : "Akhat Rakishev"
+    affiliation   : "1"
+
+affiliation:
+  - id            : "1"
+    institution   : "Department of Experimental Psychology, University College London"
+
+author_note: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+  Enter author note here.
+
+abstract: |
+  Enter abstract here. Each new line herein must be indented, like this line.
+
+keywords          : "keywords"
+wordcount         : "X"
+
+bibliography      : ["r-references.bib"]
+
+figsintext        : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+lineno            : yes
+mask              : no
+
+class             : "man"
+output            : papaja::apa6_pdf
+---
+
+```{r load-packages, include = FALSE}
+library("papaja")
+require(knitr)
+```
+
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+```
+
+```{r texreport}
+texreport <- function(object,effect.name,...) UseMethod("texreport")
+texreport.default <- function(object,effect.name,...) return(NULL)
+
+texreport.summary.merMod <- function(object,effect.name,print.estimate=TRUE) {
+  if(effect.name %in% rownames(object$coefficients)) {
+    tab <- object$coefficients
+    estimate <- tab[effect.name,"Estimate"]
+    se <- tab[effect.name,"Std. Error"]
+    Tval <- tab[effect.name,"t value"]
+    df <- tab[effect.name,"df"]
+    pval <- tab[effect.name,"Pr(>|t|)"]
+    if(pval < .001) ptext <- "$p < .001$" else {
+      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+      }
+    }
+    txt <- paste("$b = ",round(estimate,2),"$, $SE = ",round(se,2),"$, $t(",round(df,2),") = ",round(Tval,2),"$, ",sep="")
+    txt <- paste(txt,ptext,sep="")
+  } else {
+    txt <- "error"
+  }
+  txt
+}
+
+texreport.summary.Anova.mlm <- function(object,effect.name,effect.size=TRUE,sphericity.correction=TRUE) {
+  if(effect.name %in% rownames(object$sphericity.tests) && sphericity.correction && object$sphericity.test[effect.name,"p-value"] < .05) {
+    epsilon <- object$pval.adjustments[effect.name,"HF eps"]
+    pval <- object$pval.adjustments[effect.name,"Pr(>F[HF])"]
+  } else {
+    epsilon <- 1
+    pval <- object$univariate.tests[effect.name,"Pr(>F)"]
+  }
+  df1 <- object$univariate.tests[effect.name,"num Df"]*epsilon
+  df2 <- object$univariate.tests[effect.name,"den Df"]*epsilon
+  Fval <- object$univariate.tests[effect.name,"F"]
+  etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
+  # generate latex output
+  if(pval < .001) ptext <- "$p < .001$" else {
+    if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+      ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+    }
+  }
+  txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+  if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+  txt <- paste(txt,ptext,sep="")
+  txt
+}
+
+texreport.linearHypothesis.mlm <- function(object,effect.size=TRUE) {
+  if(ncol(object$SSPH) == 1 & nrow(object$SSPH) == 1 & ncol(object$SSPE) == 1 & nrow(object$SSPE) == 1) {
+    df1 <- object$df
+    df2 <- object$df.residual
+    Fval <- (object$SSPH/df1)/(object$SSPE/df2)
+    pval <- 1-pf(Fval,object$df,object$df.residual)
+    etasq <- object$SSPH/(object$SSPH + object$SSPE)
+    # generate latex output
+    if(pval < .001) ptext <- "$p < .001$" else {
+      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+      }
+    }
+    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+    if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+    txt <- paste(txt,ptext,sep="")
+  } else {
+    txt <- "error"
+  }
+  txt
+}
+
+texreport.anova.lme <- function(object,effect.name,effect.size=FALSE) {
+  if(effect.name %in% rownames(object)) {
+    pval <- object[effect.name,"p-value"]
+    if(is.null(pval)) pval <- object[effect.name,"Pr(>F)"]
+    df1 <- object[effect.name,"numDF"]
+    df2 <- object[effect.name,"denDF"]
+    Fval <- object[effect.name,"F-value"]
+    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
+    # generate latex output
+    if(pval < .001) ptext <- "$p < .001$" else {
+      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+      }
+    }
+    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+    txt <- paste(txt,ptext,sep="")
+    txt
+  }
+}
+
+texreport.anova <- function(object,effect.name,effect.size=FALSE) {
+  if(effect.name %in% rownames(object)) {
+    pval <- object[effect.name,"Pr(>F)"]
+    df1 <- object[effect.name,"NumDF"]
+    df2 <- object[effect.name,"DenDF"]
+    Fval <- object[effect.name,"F.value"]
+    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
+    # generate latex output
+    if(pval < .001) ptext <- "$p < .001$" else {
+      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+      }
+    }
+    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+    txt <- paste(txt,ptext,sep="")
+    txt
+  }
+}
+
+```
+
+```{r read-data,warning=FALSE}
+source("R/readData.R")
+demo_exit <- read.csv("data/demographics_and_exit_clean.csv")
+trial_data <- read.csv("data/trial_data_clean.csv")
+trial_data$trial <- 1:100
+```
+
+# Introduction
+
+## Optimal learning
+
+If the volatility $\sigma_{\xi}(t)$ and noise $\sigma_\epsilon$ are know, optimal Bayesian learning is implemented by the Kalman filter
+$$\hat{\mu}_{t+1} = \hat{\mu}_t + k_t (y_t - \hat{\mu}_{t})$$
+where the "Kalman gain" is $$k_t = \frac{s_t + \sigma^2_{\xi}(t)}{s_t + \sigma^2_\xi(t) + \sigma^2_\epsilon}$$ and $s_t$ is the prior uncertainty about the mean $\mu_t$, computed recursively as $$s_t = (1-k_t)(s_{t-1} + \sigma^2_\xi(t))$$.
+Note that the updating of estimates $\hat{\mu}_t$ takes the same form as the well-known delta-rule, where each update is proportional to the prediction error ($y_t - \hat{\mu}_t$), with the proportionality constant $k_t$ is the learning rate, which is usually constant in the delta-rule, but time-varying in the Kalman filter and dependent on the prior uncertainty ($s_t$), and the level of volatility ($\sigma_\xi$) and environmental noise ($\sigma_\epsilon$).
+If both latter parameters are constant, then as $t \rightarrow \infty$, the Kalman gain converges to a constant and thus becomes equal to the constant-learning rate delta-rule.
+This is the steady-state Kalman filter, and provides a means to determine the optimal (constant) learning rate.
+The steady state is
+\begin{equation}k(t)^* = \frac{1}{2} \left(\sqrt{\frac{\sigma^4_\xi}{\sigma^4_\epsilon} + 4 \frac{\sigma^2_\xi}{\sigma^2_\epsilon}} - \frac{\sigma^2_\xi}{\sigma^2_\epsilon} \right)\end{equation}
+
+## A particle filter
+
+When the parameters are unknown, the optimal learning rule becomes intractible.
+Bayesian scheme's for estimating the parameters on-line need to rely on approximations, such as Monte Carlo Markov Chain estimation, which are impractible for on-line estimation, as for each time point, estimation would have to be started fresh.
+When the parameters are time-varying,
+
+# Methods
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+
+## Participants and design
+
+One hundred participants (`r  sum(dat$gender[dat$trial == 1] == "Female",na.rm=TRUE)` females, `r  sum(dat$gender[dat$trial == 1] == "Male",na.rm=TRUE)` males, `r sum(is.na(dat$gender[dat$trial == 1]))` other or preferred not to say), aged between `r min(dat$age)` and `r max(dat$age)` ($M = `r round(mean(dat$age[dat$trial==1]),2)`$, $SD = `r round(sd(dat$age[dat$trial==1]),2)`$), voluntarily participated in the study.
+The participants were recruited from the UCL Psychology and Language Sciences subject pool or by personal invitation from the researchers.
+Eligible university students ($n=`r sum(dat$version[dat$trial==1] == "sona")`$) received course credit for their participation.
+In addition, all participants were invited to enter a draw to win one of two gift vouchers (worth £50 and £20).
+Participants were informed that the chance of winning the prizes was dependent on their performance during the experiment.
+The study was approved by the UCL ethics committe and all participants provided informed consent before participating in the experiment.
+
+Participants were randomly allocated to either the Gradual change and Abrupt change condition.
+In the gradual condition, the level of volatility changed according to a sinusoid function, smoothly increasing and decreasing over time.
+In the abrupt condition, the level of volatility changed in a stepwise manner, being low in some blocks of trials and abruptly increasing in others.
+
+## The Fisher Game
+
+All participants played "The Fisher Game", an online browser-based game programmed in HTML and javascript.
+In the game, particpants controlled the position of a fisherman's boat in order to catch as many fish as possible.
+They could maximise the number of fish caught by placing the horizontal position of the boat such that the fishing rod was located at the centre of a school of fish.
+The further away the rod was from the centre of the school of fish, the less fish they could catch.
+The horizontal position of the school of fish moved from trial to trial, with the level of movement dependent on the level of volatility.
+On each of 100 trials participants were asked to choose a position for their boat, effectively predicting were the school of fish would be on that trial.
+After making their prediction, participants received information about the actual location of the school of fish and how many fish they caught.
+The game then proceeded to the next trial.
+
+More formally, on each trial $t$ the location of fish $y_t$ was equal to mean fish location $\mu_t$ plus random noise $\epsilon_t$.
+The mean fish location $\mu_t$ was in turn equal to of the mean fish location on a previous trial, $\mu_{t-1}$,  plus random change $\zeta_t$ representing the effect of volatility:
+
+$$\begin{aligned}
+y_t &= \mu_t + \epsilon_t && & \epsilon_t &\sim \mathcal{N}(0,\sigma_\epsilon) \\
+\mu_t &= \mu_{t-1} + \xi_t && & \zeta_t &\sim \mathcal{N}(0,\sigma_\xi(t))
+\end{aligned}$$
+
+The standard deviation of the noise was set to $\sigma_\epsilon = 4$ in all conditions and did not vary over time.
+The level of volatility, $\sigma_\xi(t)$ (the standard deviation of the changes in mean fish location) varied over time in a way that was specific to each condition.
+In the Gradual change condition, the volatility varied according to a sinus function:
+
+$$ \sigma_\xi(t) = 16.5 + 13.5 \times \sin \left( -2.5 + \frac{5 \times (t - 1)}{99} \right)$$
+
+In the Abrupt change condition, volatility varied in stepwise way:
+
+$$\sigma_\xi(t) = \begin{cases} 3 & \text{if } t \in [1;25] \text{ or } [51;75] \\ 30 & \text{if } t \in [26;50] \text{ or } [76,;100] \end{cases} $$
+In both conditions lowest volatility was equal to $\sigma_\xi(t) = 3$ and the highest volatility was equal to $\sigma_\xi(t) = 30$.
+Overall, in both conditions there were two low and two high volatility periods.
+
+```{r task-structure, out.width = "85%", fig.cap = "Data generating process used in the experiment.
+a) schematic representation of data generation process; b) example of generated data: graphs in the top row show variation of volatility by trial, graphs in the middle row show mean fish location, graphs in the bottom row show observed fish locations."}
+include_graphics("img/task_structure.eps")
+```
+
+We generated ten different random sequences of fish location per condition in advance according to the data generating process described above.
+This allowed to let each player observe a randomly generated set of locations, making it unlikely that the results would be dependent on the particulars of a single random sequence or that players would be able to help each other by discussing known fish locations.
+
+The number of fish caught each trial  was then determined by dividing 0.1 by absolute prediction error (difference between response  and actual location , see the formula below).
+As generated data and participants’ responses were transformed to fit a 0-1 scale, the reward formula allowed players to catch very high amounts of fish in case of very accurate predictions (capped at 300).
+At the same time, they were still able to catch few fish even in case of very inaccurate predictions.
+We used this scoring method to keep players motivated, as due to the randomness in the data generating process it was impossible to exactly predict the next fish location.
+The scores were not used in actual analysis.
+
+## Procedure
+
+Participants completed the game at their own pace in a single session.
+After providing informed consent, participants provided demographic information (age, gender, and nationality).
+They then read instructions, in which they were informed about the game interface, the goal of the game, and the conditions of the prize draw.
+
+Following the instructions the game started.
+On each trial, participants could see the location of the school of fish on the previous trial on the game viewport.
+They were also able to see all past locations of the school of fish in the "location graph" on the right of the game viewport.
+They then chose the horizontal position of the fishing boat through a mouseclick at any position on the game viewport.
+After making their choice, the boat smoothly moved to the chosen location, and the school of fish moved to the new location.
+Participants were then informed about the number of fish they caught on that trial.
+
+```{r game-screen, out.width = "85%", fig.cap = "Illustration of online game interface. Yellow and blue text labels point on to respective interface elements."}
+include_graphics("img/game_screen.eps")
+```
+
+Upon completion of the game participants were redirected to a post-game questionnaire were they were asked to answer the following three questions about the study: "How do you think fish locations were determined from day to day?", "What was your strategy to determine where to fish next?", and "What do you think was the aim of this study?".
+The answers were given in a free format and were not mandatory.
+
+# Results
+
+## Exclusions
+
+Four of the 100 participants were excluded from further analysis because both the mean squared error of their choices and the mean reaction time further than two standard deviations removed from the sample mean.
+Of the remaining `r with(subset(trial_data,trial == 1),length(condition))` participants `r with(subset(trial_data,trial == 1),{tab <- table(condition); tab[names(tab) == "abrupt"]})` were in the abrupt and `r with(subset(trial_data,trial == 1),{tab <- table(condition); tab[names(tab) == "gradual"]})` in the gradual condition.
+
+## Performance
+
+Participants' average mean squared error was equal to 0.012 (SD = 0.006) and average mean reaction time to 2207.43 (SD = 949.815) milliseconds.
+Mean reaction times did not differ between conditions (t(72.37) = 1.17, p = .248).
+Mean squared error was significantly higher (t(78.09) = -4.23, p < .001) in the gradual condition (M = .015) than in the abrupt condition (M = .010).
+
+## Empirical learning rates
+
+According to the "delta-rule", fish locations are learned as
+
+$$\hat{y}_{t+1} = \hat{y}_{t} + \eta(t) \left( y_{t} - \hat{y}_{t} \right)$$
+where we allow the learning-rate $\eta(t) > 0$ to vary from trial to trial. Assuming that participants location choices $r_t$ are a noisy reflection of their location predictions:
+$$\begin{aligned} r_t = \hat{y}_t + e_t && e_t \sim \mathcal{N}(0,\sigma_e)\end{aligned}$$
+we substitute $r_t = \hat{y}_t$ and re-arrange this equation to
+
+$$\begin{aligned} r_{t+1} - r_{t} &= \eta(t) \left( y_{t} - r_{t} \right) \\ u_t &= \eta(t) d_t \end{aligned}$$
+with $u_{i,t} = (r_{i,t+1} - r_{i,t})$ representing the update in location choice from trial $t$ to trial $t+1$ and $d_{i,t}= (y_{i,t} - r_{i,t})$ the deviation between location choice and true location on trial $t$.
+To assess the relation between $\eta(t)$ and the optimal learning rate $\omega_t = \frac{\sigma_\xi^2(t)}{\sigma_\xi^2(t) + \sigma^2_\epsilon}$, we estimated a linear mixed-effects model
+
+<!-- with $u_{i,t} = (r_{i,t+1} - r_{i,t})$ (the update in location choice from trial $t$ to trial $t+1$ for participant $i$) as dependent variable and $d_{i,t}= (y_{i,t} - r_{i,t})$ (the deviation between location choice and true location on trial $t$ for participant $i$) as predictor: -->
+
+$$u_{i,t} = \left(\beta_d + b_{di} + \beta_{dC} C_i + \beta_{d\omega} \omega_{it} + b_{d\omega i} \omega_{it} \right) d_{it} + e_{t,i}$$
+where $C$ is a contrast-coded predictor for condition ($C = 1$ for the abrupt, and $C = -1$ for the gradual condition), each $\beta$ term is a fixed effect, and each $b$ term a participant-wise random effect.
+Random intercepts and slopes were allowed to correlate.
+The model was estimated with the lme4 package for R [@R-lme4], and $p$-values were computed with the lmerTest package [@R-lmerTest].
+```{r mixed-effects,cache=TRUE,echo=FALSE}
+require(lmerTest)
+dat <- subset(trial_data,trial < 100)
+dat$omega <- .5*(sqrt(dat$volatility^4/4^4 + 4*dat$volatility^2/4^2) - dat$volatility^2/4^2) # (2*dat$volatility^2)/(2*dat$volatility^2 + 4^2)
+
+mod0 <- lmer(update ~ condition_as_number*omega*error + (scale(omega)*error|id),data=dat)
+mod1 <- lmer(update ~ error + condition_as_number:error + omega:error + condition_as_number:omega:error - 1 + (0 + error + scale(omega):error|id),data=dat)
+mod1_summ <- summary(mod1)
+mod0_summ <- summary(mod0)
+aov_full_reduced <- anova(mod0,mod1)
+```
+There was a significant main effect of deviation, `r texreport(mod1_summ,"error")`.
+This effect of error was moderated by the steady-state learning rate, `r texreport(mod1_summ,"error:omega")` and condition, `r texreport(mod1_summ,"error:condition_as_number")`.
+There was also a three-way interaction between deviation, optimal learning rate, and condition, `r texreport(mod1_summ,"error:condition_as_number:omega")`.
+
+We also estimated a linear-mixed effects model which, in addition to these effects, included fixed effects of condition ($C$), optimal learning rate ($\omega$), as well as all two-way and three-way interactions between these variables and deviation ($d$).
+This model also included an additional random effect for optimal learning rate ($\omega$).
+Comparing these two models indicated that the latter, more complex model fitted the data significantly better than the first, simpler model, $\chi^2(`r aov_full_reduced$'Chi Df'[2]`) = `r printnum(aov_full_reduced$'Chisq'[2])`$, $p = `r round(aov_full_reduced$'Pr(>Chisq)'[2],3)`$.
+Hence, we report the results from the full model.
+There was a significant main effect of deviation, `r texreport(mod0_summ,"error")`.
+This effect of error was moderated by the optimal learning rate, `r texreport(mod0_summ,"omega:error")` and condition, `r texreport(mod0_summ,"condition_as_number:error")`.
+There was also a three-way interaction between deviation, optimal learning rate, and condition, `r texreport(mod0_summ,"condition_as_number:omega:error")`.
+Finally, there was a significant main effect of condition, `r texreport(mod0_summ,"condition_as_number")`, which is difficult to interpret, but indicates a small bias where ...
+
+These effects are more easily interpreted when inspecting the model-predicted learning rate (Figure \@ref(fig:learning-rate-plot)).
+As can be seen there, while on average, people adapt their learning rate to the changes in volatility, the adaptation is more marked in the gradual compared to the abrupt change condition.
+Also, the predicted learning rates are mostly higher than the optimal steady-state learning rates.
+```{r learning-rate-plot,echo=FALSE,out.width = "85%", fig.width=6, fig.height=3, fig.cap="Predicted learning rates from the linear mixed-effects model as a function of the optimal learning rate."}
+require(ggplot2)
+require(lmerTest)
+coef <- fixef(mod0)
+
+# newdata <- expand.grid(condition=c("abrupt","gradual"),omega = seq(min(dat$omega),max(dat$omega),length=100))
+# newdata$condition_as_number <- 1
+# newdata$condition_as_number[newdata$condition == "abrupt"] <- -1
+# coeff <-  fixef(mod0)
+# 
+# newdata$pred_eta <- coeff["error"] + coeff["condition_as_number:error"]*newdata$condition_as_number + coeff["omega:error"]*newdata$omega + coeff["condition_as_number:omega:error"]*newdata$condition_as_number*newdata$omega
+# ggplot(newdata,aes(x=omega,y=pred_eta,colour=condition)) + geom_line() + ylab("predicted learning rate") + xlab("optimal learning rate") + ylim(c(min(newdata$omega),max(newdata$pred_eta))) + xlim(c(min(newdata$omega),max(newdata$pred_eta))) + geom_abline(slope=1,intercept=0,lty=2,colour=grey(.5))
+
+newdata <- data.frame(condition=rep(c("abrupt","gradual"),each=100),volatility = c(subset(trial_data,condition=="abrupt")$volatility[1:100],subset(trial_data,condition=="gradual")$volatility[1:100]),trial=1:100)
+newdata$omega <- .5*(sqrt(newdata$volatility^4/4^4 + 4*newdata$volatility^2/4^2) - newdata$volatility^2/4^2) # (2*newdata$volatility^2)/(2*newdata$volatility^2 + 4^2)
+newdata$condition_as_number <- 1
+newdata$condition_as_number[newdata$condition == "abrupt"] <- -1
+newdata$type = "optimal"
+
+newdata <- rbind(newdata,cbind(newdata[,1:5],type="estimated"))
+
+coeff <-  fixef(mod1)
+newdata$omega[newdata$type=="estimated"] <- coeff["error"] + coeff["error:condition_as_number"]*newdata$condition_as_number[newdata$type=="estimated"] + coeff["error:omega"]*newdata$omega[newdata$type=="estimated"] + coeff["error:condition_as_number:omega"]*newdata$condition_as_number[newdata$type=="estimated"]*newdata$omega[newdata$type=="estimated"]
+
+# coeff <-  fixef(mod0)
+# newdata$omega[newdata$type=="estimated"] <- coeff["error"] + coeff["condition_as_number:error"]*newdata$condition_as_number[newdata$type=="estimated"] + coeff["omega:error"]*newdata$omega[newdata$type=="estimated"] + coeff["condition_as_number:omega:error"]*newdata$condition_as_number[newdata$type=="estimated"]*newdata$omega[newdata$type=="estimated"]
+
+ggplot(newdata,aes(x=trial,y=omega,colour=type)) + geom_line() + ylab("(predicted) learning rate") + xlab("trial") + facet_wrap(~condition) + theme(legend.position="bottom") #+ ylim(c(min(newdata$omega),max(newdata$pred_eta))) + xlim(c(min(newdata$omega),max(newdata$pred_eta))) + geom_abline(slope=1,intercept=0,lty=2,colour=grey(.5))
+
+```
+
+<!--
+. However, as the comparison just fails significance, we also report the results of the more complex model in the appendix.
+
+provides us with a trial-by-trial estimate of the learning rate
+$$\hat{\eta}(t) = \frac{r_{t + 1} - r_{t}}{y_t - r_t}$$
+Under the assumption that $r_t$ is Normal distributed, this empricial learning rate follows a general Cauchy distribution.
+-->
+
+# Discussion
+
+\newpage
+
+# References
+```{r create_r-references}
+r_refs(file = "r-references.bib")
+```
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id = "refs"></div>
+\endgroup
+
+<!--chapter:end:article.Rmd-->
+
+---
+title             : "brouillon"
+shorttitle        : "Draft-3"
+
+author: 
+  - name          : "Ismail Guennouni"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
+    email         : "i.guennouni.17@ucl.ac.uk"
+  - name          : "Maarten Speekenbrink"
+    affiliation   : "1"
+
+affiliation:
+  - id            : "1"
+    institution   : "Department of Experimental Psychology, University College London"
+
+author_note: |
+  <!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->
+
+  Enter author note here.
+
+abstract: |
+  Enter abstract here. Each new line herein must be indented, like this line.
+
+# keywords          : "keywords"
+# wordcount         : "X"
+
+bibliography      : ["Mendeley2.bib"]
+csl               : "apa-6th-edition.csl"
+
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+linkcolor         : "blue"
+mask              : no
+draft             : no
+fig_caption       : yes
+
+documentclass     : "apa6"
+# classoption       : a4paper
+classoption       : man
+output            : papaja::apa6_pdf
+citation_package  : natbib
+---
+
+```{r load-packages, include = FALSE}
+library(papaja)
+require(knitr)
+require(citr)
+require(bookdown)
+
+# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
+library(plyr)
+library(tidyr)
+library(dplyr)
+library(MASS)
+library(ggpubr)
+library(afex)
+library(PairedData)
+library(multcompView)
+library(lsmeans)
+library(magick)
+library(depmixS4)
+```
+
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+```
+
+```{r, include=FALSE} 
+options(tinytex.verbose = TRUE)
+```
+
+# Introduction
+Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
+Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
+More formally, @perkins1992transfer defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
+This typically human skill has so far eluded modern AI agents.
+Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
+Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
+[@Lake2017] argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
+
+One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
+Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations.
+This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
+There is evidence that people learn models of their opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
+In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities [@Woodruff] play a role in determining human behaviour.
+In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
+More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to the task of opponent modelling.
+
+Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
+For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
+They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
+@knez2000increasing test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
+They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity.
+If the games were only strategically similar, then the transfer was much weaker.
+
+@Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
+However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
+In a series of experiments using economic signalling games [@cooper2003lessons; @Cooper2008] the researchers found that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
+
+# References
+
+```{r create_r-references}
+r_refs(file = "Mendeley2.bib")
+
+```
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id = "refs"></div>
+\endgroup
+
+<!--chapter:end:brouillon.Rmd-->
+
+---
+title             : "Transfer of Learned Opponent Models in Zero Sum Games"
+shorttitle        : "Draft-1"
+
+author: 
+  - name          : "Ismail Guennouni"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
+    email         : "i.guennouni.17@ucl.ac.uk"
+  - name          : "Maarten Speekenbrink"
+    affiliation   : "1"
+
+affiliation:
+  - id            : "1"
+    institution   : "Department of Experimental Psychology, University College London"
+
+author_note: |
+  <!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->
+
+  Enter author note here.
+
+abstract: |
+  Enter abstract here. Each new line herein must be indented, like this line.
+
+# keywords          : "keywords"
+# wordcount         : "X"
+
+bibliography      : ["Mendeley.bib"]
+# csl               : "apa-6th-edition.csl"
+
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+linkcolor         : "blue"
+mask              : no
+draft             : no
+fig_caption       : yes
+
+documentclass     : "apa6"
+# classoption       : a4paper
+classoption       : man
+output            : papaja::apa6_pdf
+---
+
+```{r load-packages, include = FALSE}
+library(papaja)
+require(knitr)
+require(citr)
+require(bookdown)
+# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
+library(tidyr)
+library(dplyr)
+library(MASS)
+library(ggpubr)
+library(afex)
+library(PairedData)
+library(multcompView)
+library(lsmeans)
+library(magick)
+```
+
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+```
+
+```{r, include=FALSE} 
+options(tinytex.verbose = TRUE)
+```
+
+# Introduction
+Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
+Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
+More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
+This typically human skill has so far eluded modern AI agents.
+Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
+Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
+@Lake2017 argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
+
+One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
+Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations.
+This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
+There is evidence that people learn models of their opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
+In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities [@Woodruff] play a role in determining human behaviour.
+In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
+More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to the task of opponent modelling.
+
+Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
+For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
+They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
+@knez2000increasing test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
+They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity.
+If the games were only strategically similar, then the transfer was much weaker.
+
+@Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
+However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
+In a series of experiments using economic signalling games [@cooper2003lessons; @Cooper2008] the researchers found that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
+
+Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
+A notable exception is the effort by @Haruvy2012 to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
+Participants played ten games, presented as 4x4 normal form (matrix payoffs).
+Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
+They also showed that players learn abstract aspects of the game that are then transferred to new settings.
+Their rule-learning model, based on @stahl1995players, was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
+
+Still, one of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
+The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
+@simon1972theories explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
+Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
+This concept finds its natural application in 'level-k' theory, first adopted by @stahl1995players.
+It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
+At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment @arad201211.
+Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
+Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below, and so on.
+
+In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
+The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit @goodie2012levels.
+
+Our choice of using computer oponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
+When playing against other human opponents, players are learning about the game and the strategy of the opponent simultaneously.
+Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
+The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
+For instance, @spiliopoulos2013strategic made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
+@shachat2004we made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
+They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
+
+We chose to use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
+We avoid social dilemma and coordination games that crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
+Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
+Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
+As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transferred.
+By contrast, purely competitive settings and zero sum games in particular would be more appropriate.
+They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building.
+Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learning.
+Games with unique mixed strategy Nash equilibrium leading to nil average rewards facilitate inferring whether participants have learned to exploit the non-random play of the opponent.
+
+We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
+The first two games we use are identical except for action labels.
+In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with a fixed expected reward against a Nash player.
+
+Hence, we ran a total of two experiments where human participants played 3 different games against either 1 (first experiment ) or 2 (second experiment) computer opponents.
+In the following sections, we will describe each experiment's methodology and results separately, then discuss the findings before using computational modelling to shed light on some of the results.
+
+\newpage
+
+# Experiment 1
+
+## Methods
+
+## Participants
+
+A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
+The mean age of participants was 31.2 years.
+Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
+The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
+
+## Procedure
+
+In the first experiment, participants played 3 games sequentially against the same computer opponent.
+The computer opponent either used a level-1 or level-2 strategy.
+The three games were rock-paper-scissors, fire-water-grass and the numbers game.
+A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
+If one player choses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
+Otherwise it is a draw and both players receive a reward of 0.
+It has a unique MSNE consisting of randomly playing one of the three options each time.
+
+The second game is identical to Rock-Paper-Scissors in all but action labels.
+We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
+We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
+Finally, the numbers game is a generalization of rock-paper-scissors.
+In the variant we use, 2 participants concurrently pick a number between 1 and 5.
+To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent.
+For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
+To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
+This game has a structure similar to RPS in which every action is dominated by exactly one choice.
+All other possible combination of choices that are not consecutive are considered ties.
+A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score.
+Similar to RPS, the MSNE is to play each action with equal probability in a random way.
+
+Participants were informed they would play three different games against the same computer opponent.
+Each participant plays all three games consecutively and in the same order described above.
+Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
+A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
+The score was calculated as the number of wins minus the number of losses.
+Ties did not affect the score.
+In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
+The overall score of the players was translated into the bonus by making each point worth £0.02.
+This bonus is significant as players could increase the total payoff from the experiment by up to 60% assuming they'd won all rounds against the computer opponent.
+An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps).
+
+```{r feedback-rps, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align='center'}
+
+knitr::include_graphics("images/feedback_rps.png")
+
+```
+
+## Results
+
+```{r load-exp1-data, include=FALSE}
+
+dat1 <- read.csv("../data20180719.csv")
+
+# transform 'winner' variable in numeric score
+dat1$score <- recode(dat1$winner, human = 1, tie = 0, ai = -1)
+# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
+dat1$block <- factor(as.numeric(cut(dat1$round,2)),labels =c("first half", "second half"))
+
+# create a new variable "game.f" as a factor variable of games
+dat1$game.f <- factor(dat1$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))
+
+#Group data by human_id and calculate mean score per block of each game.
+dat2 <- dat1 %>% 
+  group_by(human_id,condition,game,block,game.f) %>% 
+      summarize(block_score = mean(score))
+
+# Group data by game and ID
+dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
+# head(dat3,6)
+
+# Subsetting scores data by game
+rps <- subset(dat3,  game.f == "RPS",game_score)
+fwg <- subset(dat3,  game.f == "FWG",game_score)
+num <- subset(dat3,  game.f == "NUM",game_score)
+# head(rps,6)
+```
+
+```{r exp1-avg-scores-game, fig.cap = "Average scores per game across conditions", fig.align="center"}
+# Plot average  scores per game 
+ggboxplot(dat3, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
+```
+
+Looking at the aggregate scores (See Figure\ \@ref(fig:exp1-avg-scores-game) ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
+Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value < 0.001 ;  FWG:  t(51) = 10.04 , p-value < 0.001 ; NUMBERS: t(51) = 7.17, p-value < 0.001).
+
+To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
+There was a main effect of Game ( F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games.
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
+The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
+The main effect of Block ( F(1,50) = 22.51 , p < .001, $\eta^{2}$ = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning.
+As players interact more with the agent, they learn how to win more often.
+The main effect of Condition (F(1,50) = 5.44, p = .024, $\eta^{2}$ = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
+This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
+
+```{r exp1-3factor-plot, fig.cap = "Average scores by game, block and condition", fig.align = "center"}
+
+# Plot results by game and block (for all 3 games, learning is happening) 
+p <- ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")
+
+p + facet_grid(. ~ condition)
+
+```
+
+Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, $\eta^{2}$ = 0.02), indicating that within-game learning differed between the games.
+Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p <.0001), while there was no significant difference between block scores for the other two games.
+This is indicative of the significant within game transfer within the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
+There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent.
+For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than agaisnt level-1 opponent.
+The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
+
+### Learning transfer
+
+As a measure for learning transfer, we focus on participants’ scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
+A group of players with no experience of the game are expected to have scores not significantly different from 0.
+Any significantly positive group average scores would therefore reflect prior learning from past experiences.
+
+We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
+As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
+In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
+This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
+
+Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
+Figure\ \@ref(fig: exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players.
+Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
+To test these hypotheses, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
+
+```{r exp1-early-rounds, include=FALSE}
+dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
+exp1_dat2_6 <- dat_26 %>% 
+  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
+      summarise(early_score = mean(score))
+
+# Check group means and SDs by game and condition
+group_by(exp1_dat2_6, game.f,condition) %>%
+  summarise(
+    count = n(),
+    mean = mean(early_score, na.rm = TRUE),
+    sd = sd(early_score, na.rm = TRUE)
+    )
+
+```
+
+```{r exp1-score-by-opp, fig.cap = "Average early scores by game and type of opponent faced", fig.align='center'}
+
+p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Average Score rounds 2-6", xlab = "Games")
+
+p2 + facet_grid(. ~ condition)
+
+```
+
+<!-- Table\ \@ref(tab:table-early-scores) shows the scores on rounds 2-6 for both type of opponents in each game.
+We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
+Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
+-->
+
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p < 0.001) and NUMBERS (t(150) = 3.74, p < 0.001) .
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
+
+```{r ANOVA early exp1, include = FALSE, warning=FALSE}
+
+exp1_early_anova <- afex :: aov_car(
+  early_score ~ game.f*condition + Error(human_id/(game.f))
+  , data=exp1_dat2_6
+  , type = 3)
+
+apa_lm1 <- apa_print(exp1_early_anova)
+
+means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
+trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","NUM"))
+
+```
+
+```{r table-early-scores, include = FALSE, results = "asis"}
+# apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
+```
+
+Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
+We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game.
+Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
+
+\newpage
+
+# Second Experiment
+
+## Methods
+
+### Participants 
+A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
+This was a new set of participants unrelated to those taking part in Experiment 1.
+The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
+Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
+
+### Procedure
+
+The participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
+The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
+The first two games were identical to the ones used in the first experiment.
+In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper.
+Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
+If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
+Otherwise, the goalkeeper catches the ball and the player loses the round.
+There is no possibility of ties in this game.
+Figure XXXXXXXXX shows a snapshot of play in the shootout game.
+What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
+A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
+As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
+
+Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
+Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
+Participants start by facing one of the opponents in stage one, then face the other in stage two.
+This is repeated in the same order in stages 3 and 4.
+Which opponent they faced first was counterbalanced.
+All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
+
+In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
+During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
+A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent.
+After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
+Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction.
+The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
+
+Like games used in the first experiment, all the games used in this seeting have a unique MSNE consisting of randomising across actions.
+If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
+Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
+
+## Results
+
+```{r load_exp2_data , include=FALSE}
+dat_int <- read.csv(file = "../Experiment_2/dat_int_exp2.csv")
+```
+
+The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had the highest average score (M = 0.622, SD = 0.326).
+The higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
+Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
+To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
+Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value < 0.0001 ;  FWG:  t(49) = 7.25 , p-value < 0.0001 ; Shootout: t(49) = 13.61, p-value < 0.0001 ).
+
+Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
+We perform a two (condition: level-1 first, level-2 first) by two ( opponne type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
+
+```{r Anova exp 2, include= FALSE}
+exp2_anova <- afex::aov_car(
+  int_score ~ (game.f*interaction_lvl*condition.f*opp_type) + Error(human_id/(game.f*interaction_lvl*opp_type))
+  , data = dat_int
+  , type = 3
+)
+
+(ls0 <- lsmeans(exp2_anova, "game.f", by = "opp_type"))
+(ls0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
+apa_lm <- apa_print(exp2_anova)
+
+```
+
+```{r exp2-score-by-opp, fig.cap="Average scores per game by opponent type", fig.align="center"}
+# p3 <- ggerrorplot(dat_int, x = "game.f", y = "int_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Scores per game", xlab = "Games")
+# 
+# p3 + facet_grid(. ~ opp_type)
+
+p4 <- ggboxplot(dat_int, x = "game.f", y = "int_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","SHOOT"), fill="interaction_lvl",ylab = "Percentage score", xlab = "Games")
+
+p4 + facet_grid(. ~ opp_type)
+
+```
+
+```{r exp2-anova, results = "asis", echo=FALSE, warning=FALSE}
+# apa_table( apa_lm$table, caption = "ANOVA results for experiment 2", escape = FALSE)
+```
+
+There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, $\eta^{2}$ = 0.04,  p < .0001).
+To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
+We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the Shootout game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
+There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
+This means that neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
+There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,$\eta^{2}$ = 0.02,  p = .01).
+As can be seen in Figure\ \@ref(fig:exp2-score-by-opp), when facing level-1 agents, scores increase steadily after each game, with FWG score sgnificantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG  ( t(191) = 3.05, p = 0.01).
+There was no significant difference between average scores on any two games when facing level-2 agents however.
+
+### Learning transfer
+
+```{r , include=FALSE}
+dat <- read.csv(file = "../Experiment_2/dat_exp2.csv")
+```
+
+As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random.
+Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
+
+```{r, include = FALSE}
+
+#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########
+
+dat_26 <- subset(dat,(round >1 & round < 7) & (interaction_lvl == "first interaction" ), drop =TRUE)
+
+exp2_dat2_6 <- dat_26 %>% 
+  group_by(human_id,condition.f,game.f,opp_type,confidence,difficulty) %>% 
+      summarise(early_score = mean(adj_score))
+
+# Check group means and SDs
+group_by(exp2_dat2_6, game.f) %>%
+  summarise(
+    count = n(),
+    mean = mean(early_score, na.rm = TRUE),
+    sd = sd(early_score, na.rm = TRUE)
+    )
+group_by(exp2_dat2_6, game.f,opp_type) %>%
+  summarise(
+    count = n(),
+    mean = mean(early_score, na.rm = TRUE),
+    sd = sd(early_score, na.rm = TRUE)
+    )
+```
+
+```{r exp2-early-scores, fig.cap="Average early round scores by game for experiment 2", fig.align="center"}
+# plot scores per game 
+p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Score rounds 2-6", xlab = "Games")
+
+p2 + facet_grid(. ~ opp_type)
+```
+
+In Figure\ \@ref(fig:exp2-early-scores), we show the average score across participants in rounds 2-6 of the first interaction with the opponent for each game.
+These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
+For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
+(Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; Shootout:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; Shootout:  t(270) = 3.21, p =0.004 ).
+Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
+Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
+These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
+
+\newpage
+
+# Computational modelling
+
+To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent.
+As a base model, we assume play is random, and each potential action is chosen with equal probability.
+Note that this corresponds to the Nash equilibrium strategy.
+In this section, we will go through the various models we have used and explain how they update what they learn about the game or the opponent
+
+## Reinforcement Learning
+
+We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
+We will use a simple temporal difference learning update rule:
+
+$$ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) $$
+
+Where $V_{t}(a)$ is the value associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
+Actions are chosen based on action values using a softmax choice rule.
+
+We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm [@watkins1992q]. The update rule becomes:
+
+$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$
+
+Where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\gamma$ is the discount rate applied to future rewards.
+For instance, $Q(RS,P)$ denotes the value of taking action "Paper" this round if the player's last action was "Rock" and the opponent played "Scissors".
+This is a much richer model allowing the players to compute the values of actions conditional on past play.
+
+In experiment 2, we allow this richer model to have a memory of the interaction.
+In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used.
+In another instance, we fit a model in which what was learned about an opponent in the first interaction is transfered to the first round of the second interaction, so there is a within-game trasnfer of Q-values allowed (QLS-within).
+We fit both models to all participant's data in the second experiment where both opponents are faced.
+
+### EWA Models 
+Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics].
+EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning.
+Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
+In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
+The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
+
+Let's define some notation in order to write the update rule of the self-tuning EWA model.
+For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j).
+Strategies actually played by i in period t, are denoted $s_{i}(t)$, while the opponent's strategy at time t is denoted $s_{-i}(t)$.
+After playing  $s_{i}^{j}$ at time $t$, player i payoff is denoted $\pi_{i}(s_{i}^{j},s_{-i}(t))$, and the actual payoff the player received is $\pi_{i}(t)$.
+
+The EWA model is based on updating "Attractions" for each action over time.
+For instance, the attraction of strategy $j$ to player $i$ at time $t$ is written $A_{i}^{j}(t)$.
+Future action choice probabilities are based on these attractions using the softmax playing rule:
+
+$$P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} $$
+
+The attractions are updated over every time step $t$ using the followng update rule :
+
+$$ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} $$
+
+Here, I(x,y) is the indicator function equal to 1 if $ x = y$ and 0 otherwise.
+A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince ($N(t-1)$) which is itself decaying by a wight $\phi$.
+The result is added to either the payoff received (when the indicator function is 0), or to $\delta$ times the foregone payoff (when indicator function is 1).
+We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play [@cheung1994learning].
+While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].
+
+### ToM models
+
+In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
+We use values of k  in ${0,1,2}$.
+We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
+In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
+In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between trasnfer)
+
+Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
+In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
+
+We fit the above two models to experiment 1 data.
+In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive).
+And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
+
+In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).
+In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
+Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
+
+## Experiment 1 modelling :
+
+```{r load-comp-mod-distrib, include=FALSE}
+
+All_comp_results <- read.csv(file="../All_results.csv")
+exp1_comp_table <- table(All_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(All_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])
+
+ #write.csv(exp1_comp_table ,file="exp1_comp_table ",row.names = TRUE)
+ kable(exp1_comp_table)
+```
+
+```{r exp1-cum-score-plots, include=FALSE}
+
+exp1_dat = read.csv("../exp1_data.csv")
+# exp1_model_comp = read.csv("../exp1_model_comp.csv")
+
+exp1_model_comp <- data.frame()
+for(id in unique(exp1_dat$human_id)) {
+  tdat <- subset(exp1_dat,human_id == id)
+  tot_score <- sum(tdat$score)
+  tot_time <- sum(tdat$human_rt)
+  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
+  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
+  tr_score <- sum(early_dat$score)
+  id_results <- subset(All_comp_results, ID == id)
+  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)
+
+  best_model <- c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
+  # 
+  exp1_model_comp <- rbind(exp1_model_comp,
+                       data.frame(
+                         "human_id" = id,
+                         "condition" = exp1_dat[exp1_dat$human_id==id,"condition"][1],
+                         "Early_game_score" = tr_score,
+                         "Total_score" = tot_score,
+                         "Best_model" = best_model,
+                         "Total_time" = sum(tdat$human_rt),
+                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
+                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
+
+                       ))
+}
+
+datalist = list()
+i = 0
+new_dat <- setNames(data.frame(matrix(ncol = ncol(exp1_dat), nrow = 0)), colnames(exp1_dat))
+for(id in unique(exp1_dat$human_id)) {
+  i <- i+1
+  tdat <- subset(exp1_dat,human_id == id)
+  tdat$part_num <- i
+  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
+  datalist[[i]] <- tdat
+}
+
+# Merge all datasets into one 
+new_dat <- dplyr::bind_rows(datalist)
+# or new_dat <- data.table::rbindlist(datalist)
+
+# Add column for time t
+new_dat <- new_dat %>% group_by(exp1_dat$human_id) %>% mutate(t = row_number())
+
+# Add best fitting model per participant
+new_dat <- merge(new_dat, exp1_model_comp[, c("human_id", "Best_model")], by="human_id")
+
+temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
+dat_by_model <- temp %>% group_by(Best_model,t) %>% 
+  summarize(model_acc_sum = mean(acc_sum))
+
+```
+
+Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
+
+```{r exp1-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 1", fig.align='center'}
+
+#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
+par(las=2) # make label text perpendicular to axis
+par(mar=c(5,8,4,2)) # increase y-axis margin.
+barplot(exp1_comp_table,
+        horiz =TRUE, # rotate barplot for better visibility 
+        las=1, # change orientation x axis labels 
+        cex.names=0.8, # text label size
+        legend = rownames(exp1_comp_table),
+        beside =TRUE,
+        xlab="Number of participants",
+        args.legend=list( # positioning of legend box 
+        x=ncol(exp1_comp_table) + 4,
+        y=max(colSums(exp1_comp_table)) + 4,
+        bty = "n")
+ )
+
+```
+
+Next we compared the performance of players whose actions are best fit by each of our hypothesized models.
+Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
+We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (witout transfer), followed by Q-learning conditional on last round play.
+EWA, QL and random players had, understandably the lowest performance.
+
+```{r exp1-cumScores, fig.cap = "Average cumulative scores of participants in experiment 1 by best fitting model", fig.align='center'}
+p5 <- ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
+   geom_line(aes(color= Best_model))
+
+p5+ labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
+```
+
+## Experiment 2
+
+```{r, include = FALSE}
+
+exp2_comp_results <- read.csv(file="../Experiment_2/exp2_results.csv")
+# exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+
+exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+
+ # write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
+ kable(exp2_comp_table)
+```
+
+```{r exp2-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 2", fig.align='center'}
+
+#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
+par(las=2) # make label text perpendicular to axis
+par(mar=c(5,8,4,2)) # increase y-axis margin.
+barplot(exp2_comp_table,
+        horiz =TRUE, # rotate barplot for better visibility 
+        las=1, # change orientation x axis labels 
+        cex.names=0.8, # text label size
+        beside =TRUE,
+        xlab="Number of participants",
+        # legend = c("level-1 opp first","level-2 opp first"),
+        legend = paste0(rownames(exp2_comp_table) , " faced first"),
+        args.legend=list( # positioning of legend box 
+        x=ncol(exp2_comp_table) + 6,
+        y=max(colSums(exp2_comp_table)) +1,
+        bty = "n")
+ )
+
+```
+
+In experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that Q-learning with the aforementioned state-space was again more successful than the bayesian models in fitting player's action choices.
+In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) did not fit players observed data as well.
+
+```{r, include=FALSE}
+
+dat_exp2 = read.csv("../Experiment_2/data_exp2.csv")
+
+#Adjust shootout score tor eflect easier game
+dat_exp2$adj_score <- ifelse(as.character(dat_exp2$game) == "shootout", dat_exp2$score - 0.333, dat_exp2$score)
+
+# Load data comparing models BIC for each participant 
+model_comp_2 = read.csv("../Experiment_2/exp2_model_comp.csv")
+
+datalist2 = list()
+i = 0
+
+#Build empty dataframe with same names as original data
+exp2_cum_score <- setNames(data.frame(matrix(ncol = ncol(dat_exp2), nrow = 0)), colnames(dat_exp2))
+for(id in unique(dat_exp2$human_id)) {
+  i <- i+1
+  tdat <- subset(dat_exp2,human_id == id)
+  tdat$part_num <- i
+  # NB : USE ADJUSTED SCORE IN SHOOTOUT
+  tdat <- within(tdat, acc_sum <- cumsum(tdat$adj_score))
+  datalist2[[i]] <- tdat
+}
+
+# Merge all datasets into one 
+exp2_cum_score <- dplyr::bind_rows(datalist2)
+# or exp2_cum_score <- data.table::rbindlist(datalist)
+
+# Add column for time t
+exp2_cum_score <- exp2_cum_score %>% group_by(human_id) %>% mutate(t = row_number())
+
+# Participant number as a factor 
+# tdat$part_num <- as.factor(tdat$part_num)
+
+# Add best fitting model per participant
+exp2_cum_score <- merge(exp2_cum_score, model_comp_2[, c("human_id", "Best_model_2")], by="human_id")
+
+temp2 <- exp2_cum_score[,c("t","acc_sum","Best_model_2","condition","part_num")]
+dat_by_model_2 <- temp2 %>% group_by(Best_model_2,t) %>% 
+  summarize(avg_acc_sum = mean(acc_sum))
+
+```
+
+```{r exp2-cumScores, fig.cap = "Average cumulative scores of participants in experiment 2 by best fitting model", fig.align='center'}
+
+ p8 <- ggplot(data = dat_by_model_2, aes(x = t, y=avg_acc_sum, group = Best_model_2)) + 
+   geom_line(aes(color= Best_model_2)) +
+  scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))
+
+p8 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
+
+```
+
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
+Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance, folowed by a model in which both within and between trasnfer of opponent models is allowed (BT).
+The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive).
+As expected, random play as well as self-tuning EWA were at the bottom of cumulative performance.
+
+\newpage
+
+# Discussion
+
+In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies.
+We were interested in uncovering evidence for transfer and exploring whether it is modulated by the degree of similarity between games and the sophistication of the agent.
+
+The results of our first online experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
+We found that using results on very early rounds is a better proxy for measuring transfer as it is not tainted by any within game learning.
+Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
+
+In the second online experiment, the paradigm was better suited to explore our main research question, related to learning transfer rather than within-game learning.
+Indeed, when facing two opponents sequentially, there are many more opportunities to test transfer than before.
+Indeed, there are 2 opportunities to transfer knowledge within each game, and a total of three games, which means 6 opportunities to test transfer.
+When we made players face only one type of opponent each, we only had two possible learning transfers to test.
+In that regard, the results on learning transfer confirmed prior findings from the first experiment.
+While there was no evidence of learning transfer across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
+We also found that learning transfer is modulated by the type of opponent faced.
+When the players faced the level-1 opponent, they were able to transfer learning.
+However, when they faced the level-2 opponent, there was weaker evidence for transfer.
+The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with.
+A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
+
+Coming back to evidence for learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
+The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
+what did the players learn exactly about the opponent strategy and what form did this learning take?
+
+We will proceed by considering multiple potential answers to this question.
+First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
+An example is a spatial heuristic that consists of choosing "weapons" in a particular order (for instance left to right).
+This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
+We took this into account in designing experiment two by randomly shuffling the spatial order of action choices in each round.
+Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.
+
+A second possible hypothesis for learning the opponent’s strategy is the use of simple rules based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
+Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
+While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
+Indeed, learning the best action in a particular state cannot easily transfer to a new game since the state space is different and there is no simgle mapping between the state spaces of the initial and latter games.
+These rules would thereofre need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
+
+Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, would require many rounds of practice.
+Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
+After all, if players were using some type of associative learning or spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
+The fact that the degree of sophisitication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
+
+We are left with two possible explanations: First, it is possible that the players have uncovered a heuristic that allows them to beat the opponent without explicitly modelling their strategy, and is robust to transfer.
+Indeed, because of the cyclicality in action choices (e.g : Rock beats Scissors beats Paper beats Rock), it is possible to beat level-2 opponents most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
+This is a rule that wins and is also robust to transfer as it does not depend on action labels and even works in the dissimilar game.
+
+The second explanation of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
+A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
+For instance, the player may think “My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be”.
+This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
+This type of learning would be deemed “explicit” in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
+It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
+Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
+
+Our second experimental design allows us to test whether the first explanation holds.
+Since there is a simple transferable heuristic that works agaisnt level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
+Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.
+
+Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first intractions across games and using early rounds analysis.
+Based on our assumptions, we conclude that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the ourse of learning.
+
+\newpage
+
+# Conclusion
+
+Our online experiments confirm behavioural game theory results, stating that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
+Moreover, we showed that participants do transfer their learning to new games with varying degrees of similarity.
+The most likely explanation as we saw is that players build a mental representation of their opponent strategy, rather than rely on associative learning or action-based heuristics.
+The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.
+
+Having said that, there remains a high degree of heterogeneity between players.
+There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
+Moreover, the computational modelling shows that a significant number of players are still using random strategies in the games.
+Whether this ability depends on engagement with the experiment or on other characteristics of the learner is an open question that more research in the area would hope to answer.
+
+\newpage
+
+# References
+
+```{r create_r-references}
+r_refs(file = "Mendeley.bib")
+
+```
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id = "refs"></div>
+\endgroup
+
+<!--chapter:end:draft_report_v1.Rmd-->
+
 ---
@@
 \endgroup
+
+<!--chapter:end:draft_report_v2.Rmd-->
+
+---
+title             : "Transfer of Learned Opponent Models in Zero Sum Games"
+shorttitle        : "Draft-3"
+
+author: 
+  - name          : "Ismail Guennouni"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
+    email         : "i.guennouni.17@ucl.ac.uk"
+  - name          : "Maarten Speekenbrink"
+    affiliation   : "1"
+
+affiliation:
+  - id            : "1"
+    institution   : "Department of Experimental Psychology, University College London"
+
+# author_note: |
+  #<!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->
+
+  #Enter author note here.
+
+abstract: |
+  Enter abstract here. Each new line herein must be indented, like this line.
+
+# keywords          : "keywords"
+# wordcount         : "X"
+
+bibliography      : ["Mendeley2.bib"]
+csl               : "apa-6th-edition.csl"
+
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+linkcolor         : "blue"
+mask              : no
+draft             : no
+fig_caption       : yes
+
+documentclass     : "apa6"
+# classoption       : a4paper
+classoption       : man
+output            : papaja::apa6_pdf
+      pandoc_args : !expr rmdfiltr::add_wordcount_filter()
+#citation_package  : natbib
+---
+
+```{r load-packages, include = FALSE}
+library(papaja)
+library(kableExtra)
+require(knitr)
+require(citr)
+require(bookdown)
+
+# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
+library(plyr)
+library(tidyr)
+library(dplyr)
+library(MASS)
+library(ggpubr)
+library(afex)
+library(PairedData)
+library(multcompView)
+library(lsmeans)
+library(magick)
+library(depmixS4)
+library(rmdfiltr)
+```
+
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+
+```
+
+```{r, include=FALSE} 
+options(tinytex.verbose = TRUE)
+add_wordcount_filter(NULL, error = FALSE)
+```
+
+# Introduction
+Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
+Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
+More formally, @perkins1992transfer defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
+This typically human skill has so far eluded modern AI agents.
+Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
+Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
+@Lake2017 argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
+
+One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
+Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations.
+This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
+There is evidence that people learn models of their opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
+In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind @premack1978does abilities play a role in determining human behaviour.
+In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
+More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to the task of opponent modelling.
+
+Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
+For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
+They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
+@knez2000 test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
+They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity.
+If the games were only strategically similar, then the transfer was much weaker.
+
+@Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
+However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
+In a series of experiments using economic signalling games Cooper & Kagel [-@cooper2003lessons; -@Cooper2008] found that participants who have learned to play according to a Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of a different payoff structure on an opponent's actions.
+
+Most studies fail to offer a formal explanation of transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
+A notable exception is the effort by @Haruvy2012 to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
+Participants played ten games, presented in 4x4 normal form (matrix payoffs).
+Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
+They also showed that players learn abstract aspects of the game that are then transferred to new settings.
+Their rule-learning model, based on @stahl1995players, was able to capture participants' dynamic behavior and shows that the propensity to select particular rules is perfectly transferred across games.
+
+This literature adopted two types of opponents in the experimental setting: either human participants or computer algorithms.
+One of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
+The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities.
+@simon1972theories explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally complex problems such as finding Nash equilibria.
+Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
+This concept finds its natural application in 'level-k' theory, first adopted by @stahl1995players.
+It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogeneous degree of strategic sophistication.
+At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment @arad201211.
+Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
+Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below, and so on.
+
+In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
+The agents will either be a level-1 or level-2 player, mimicking human theory of mind abilities and the limited recursion depth they exhibit [@goodie2012levels].
+
+Our choice of using computer opponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
+When playing against other human opponents, players are learning about the game as well as trying to infer the potential dynamic strategy of the opponent simultaneously.
+Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
+The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
+For instance, @spiliopoulos2013strategic made humans play constant sum games against 3 computer opponents, designed to take advantage of known patterns in human play such as imperfect randomization and heuristics use.
+He found that human participants do adapt to the opponent they are facing.
+@shachat2004we made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
+They found that the players changed their strategies towards exploiting the deviations of the opponent from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
+
+We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
+The first two games we use are structurally identical except for action labels.
+In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure.
+In the first experiment, participants face the same opponent throughout the three games, and the opponents are randomised to be either level-1 or level-2 players.
+In the second experiment, participants faced both level-1 and level-2 opponent sequentially, with the order in which they are faced randomised across participants.
+
+\newpage
+
+# Experiment 1
+
+## Methods
+
+### Participants and Design
+
+A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
+The mean age of participants was 31.2 years.
+Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
+The study used a 2 (computer opponent: level 1 or  level 2) by 3 (games: rock-paper-scissors, fire-water-grass, numbers) design, with repeated measures on the second factor.
+
+### Tasks
+
+In the first experiment,  The three games were rock-paper-scissors, fire-water-grass and the numbers game.
+A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
+If one player chooses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
+Otherwise it is a draw and both players receive a reward of 0.
+It has a unique MSNE consisting of randomly playing one of the three options each time.The second game is identical to Rock-Paper-Scissors in all but action labels.
+We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
+We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
+Finally, the numbers game is a generalization of rock-paper-scissors.
+In the variant we use, 2 participants concurrently pick a number between 1 and 5.
+To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent.
+For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
+To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
+This game has a structure similar to RPS in which every action is dominated by exactly one choice.
+All other possible combination of choices that are not consecutive are considered ties.
+A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score.
+Similar to RPS, the MSNE is to play each action with equal probability in a random way.
+
+### Procedure
+
+Participants played 3 games sequentially against the same computer opponent.
+The computer opponent either used a level-1 or level-2 strategy.
+Participants were informed they would play three different games against the same computer opponent.
+Each participant plays all three games consecutively and in the same order described above.
+Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
+A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
+The score was calculated as the number of wins minus the number of losses.
+Ties did not affect the score.
+In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
+Each point worth £0.02.
+An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps-exp2).
+
+```{r feedback-rps-exp2, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align='center'}
+
+knitr::include_graphics("images/feedback_rps.png")
+
+```
+
+### Results
+
+```{r load-exp1-data, include=FALSE}
+
+dat1 <- read.csv("../data20180719.csv")
+
+# transform 'winner' variable in numeric score
+dat1$score <- recode(dat1$winner, human = 1, tie = 0, ai = -1)
+# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
+dat1$block <- factor(as.numeric(cut(dat1$round,2)),labels =c("first half", "second half"))
+
+# create a new variable "game.f" as a factor variable of games
+dat1$game.f <- factor(dat1$game, labels = c("RPS","FWG","Numbers"),levels=c("rps","fwg","numbers"))
+
+#Group data by human_id and calculate mean score per block of each game.
+dat2 <- dat1 %>% 
+  group_by(human_id,condition,game,block,game.f) %>% 
+      summarize(block_score = mean(score))
+
+# Group data by game and ID
+dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
+# head(dat3,6)
+
+# Subsetting scores data by game
+rps <- subset(dat3,  game.f == "RPS",game_score)
+fwg <- subset(dat3,  game.f == "FWG",game_score)
+num <- subset(dat3,  game.f == "Numbers",game_score)
+# head(rps,6)
+```
+
+```{r exp1-avg-scores-game, fig.cap = "Boxplot of scores per game across conditions", fig.align="center"}
+# Plot average  scores per game 
+ggboxplot(dat3, x = "game", y = "game_score",group = 1, add =c("mean_ci"), color="game", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("rps", "fwg","numbers"), ylab = "Score", xlab = "Game", legend.title = "Game") + geom_jitter( aes(color = game), width = 0.2, alpha = 0.3 )
+
+```
+
+Looking at the aggregate scores (See Figure\ \@ref(fig:exp1-avg-scores-game) ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
+Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, $p$ < 0.001 ;  FWG:  t(51) = 10.04 , $p$ < 0.001 ; NUMBERS: t(51) = 7.17, $p$ < 0.001).
+To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
+There was a main effect of Game ( F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games.
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in the NUMBERS game was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
+The score in RPS was not significantly different from the score in NUMBERS ( t(100) = 0.45 , p = 0.65).
+The main effect of Block ( F(1,50) = 22.51 , p < .001, $\eta^{2}$ = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning.
+The main effect of Condition (F(1,50) = 5.44, p = .024, $\eta^{2}$ = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
+This indicates that it was harder for participants, on average, to exploit the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
+
+```{r exp1-3factor-plot, fig.cap = "Average scores by game, block and condition", fig.align = "center"}
+
+# Plot results by game and block (for all 3 games, learning is happening) 
+p <- ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")
+
+p + facet_grid(. ~ condition)
+
+```
+
+Finally, the analysis showed a significant block by game interaction ( F(2,100) = 6.92 , p = .002, $\eta^{2}$ = 0.02), indicating that within-game learning differed between the games.
+Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p <.0001), while there was no significant difference between block scores for the other two games.
+This is indicative of the significant within-game learning happening in the first game when players have no experience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some experience playing against the opponent and start with higher scores indicative of transfer.
+There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent.
+For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than against level-1 opponent.
+The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
+
+### Learning transfer
+
+As a measure for learning transfer, we focus on participants’ scores in the first 5 rounds excluding the initial round (rounds 2-6).
+We exclude the very first round as the computer opponent plays randomly here and there is no opportunity yet for the human player to exploit their opponent's strategy.
+A group of players with no experience of the game are expected to perform at chance level over the early rounds of a new game, as was the case in RPS.
+Positive scores in the early rounds would therefore reflect generalization of prior experience.
+For the FWG game, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
+This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
+For the RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
+
+```{r exp1-early-rounds, include=FALSE}
+dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
+exp1_dat2_6 <- dat_26 %>% 
+  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
+      summarise(early_score = mean(score))
+
+# Check group means and SDs by game and condition
+group_by(exp1_dat2_6, game.f,condition) %>%
+  summarise(
+    count = n(),
+    mean = mean(early_score, na.rm = TRUE),
+    sd = sd(early_score, na.rm = TRUE)
+    )
+
+```
+
+```{r exp1-score-by-opp, fig.cap = "Mean and CI of early scores by game and opponent", fig.align ='center'}
+
+p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","Numbers"), ylab = "Early rounds score", xlab = "Games", legend.title = "Games")
+
+p2 + facet_grid(. ~ condition)
+
+```
+
+Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
+Figure\ \@ref(fig:exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players as well as the $95$ percent confidence interval for the mean.
+Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
+To explore this, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p < 0.001) and NUMBERS (t(150) = 3.74, p < 0.001) .
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
+
+```{r ANOVA early exp1, include = FALSE, warning=FALSE}
+
+exp1_early_anova <- afex :: aov_car(
+  early_score ~ game.f*condition + Error(human_id/(game.f))
+  , data=exp1_dat2_6
+  , type = 3)
+
+#apa_lm1 <- apa_print(exp1_early_anova)
+
+means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
+trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","Numbers"))
+
+```
+
+```{r table-early-scores, include = FALSE, results = "asis"}
+# apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
+```
+
+### Discussion Experiment 1
+
+Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
+We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game.
+Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
+
+\newpage
+
+# Second Experiment
+
+We ran a second experiment with various differentiated features to improve the opportunity to measure learning transfer.
+Instead of making participants face either the level-1 or level-2 player throughout, we made them face both opponent sequentially.
+Because there were two distinct opponents, requiring potentially holding two opponent models in memory, we also made it easier to recall the results of past rounds by providing participants with the opportunity to see the history of the game since the beginning of each interaction.
+Figure\ \@ref(fig:feedback-rps-exp2) shows an example of showing interaction history in the RPS game.
+Finally, we changed the third game to a penalty shootout game, which has the same number of actions as the first two.
+If we see evidence for differential play against opponents, it would show participants adapting their strategies to the opponent they are facing, which is indicative of opponent modelling.
+
+## Methods
+
+### Participants & Design
+
+A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
+This was a new set of participants unrelated to those taking part in Experiment 1.
+The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
+Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
+
+### Tasks
+
+The three games the participants played were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
+The first two games were identical to the ones used in the first experiment.
+In the final game (shootout) the participants took the role of the player shooting a football (soccer) penalty, with the AI opponent being the goalkeeper.
+Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
+If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
+Otherwise, the goalkeeper catches the ball and the player loses the round.
+There is no possibility of ties in this game.
+Figure\ \@ref(fig:screenshot-shootout)  shows a snapshot of play in the shootout game.
+What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
+A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
+As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
+
+```{r screenshot-shootout, fig.cap = "Screenshot of the shootout game", fig.align='center'}
+
+knitr::include_graphics("images/shootout.png")
+```
+
+### Procedure
+
+The participants played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
+Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
+Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
+Participants start by facing one of the opponents in stage one, then face the other in stage two.
+This is repeated in the same order in stages 3 and 4.
+Which opponent they faced first was counterbalanced.
+All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
+In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
+During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
+A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response, as a way of simulating a real human opponent thinking time.
+After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
+Further information about the outcome of previous rounds was also visible on the game screen below the feedback area.
+Throughout each stage, participants could scroll down to recall the history of interaction.
+The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
+As in the first experiment, all the games have a unique MSNE consisting of randomising across actions.
+If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
+Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
+
+## Results
+
+```{r load_exp2_data , include=FALSE}
+dat_int <- read.csv(file = "../Experiment_2/dat_int_exp2.csv")
+```
+
+The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had an adjusted average score in between the two (M = 0.289, SD = 0.326).^[ A higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
+Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
+To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33)].
+Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, $p$ < 0.0001 ;  FWG:  t(49) = 7.25 , $p$ < 0.0001 ; Shootout: t(49) = 13.61, $p$ < 0.0001 ).
+Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
+We perform a two (condition: level-1 first, level-2 first) by two ( opponent type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
+
+```{r Anova exp 2, include= FALSE}
+exp2_anova <- afex::aov_car(
+  int_score ~ (game.f*interaction_lvl*condition.f*opp_type) + Error(human_id/(game.f*interaction_lvl*opp_type))
+  , data = dat_int
+  , type = 3
+)
+
+(ls0 <- lsmeans(exp2_anova, "game.f", by = "opp_type"))
+(ls0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
+apa_lm <- apa_print(exp2_anova)
+
+```
+
+```{r exp2-score-by-opp, fig.cap="Boxplot of scores per game and interaction by opponent type", fig.align="center"}
+# p3 <- ggerrorplot(dat_int, x = "game.f", y = "int_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Scores per game", xlab = "Games")
+# 
+# p3 + facet_grid(. ~ opp_type)
+
+p4 <- ggboxplot(dat_int, x = "game.f", y = "int_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","SHOOT"), fill="interaction_lvl",ylab = "Percentage score", xlab = "Games", legend.title = "interaction level")
+
+p4 + facet_grid(. ~ opp_type)
+
+```
+
+```{r exp2-anova, results = "asis", echo=FALSE, warning=FALSE}
+# apa_table( apa_lm$table, caption = "ANOVA results for experiment 2", escape = FALSE)
+```
+
+There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, $\eta^{2}$ = 0.04,  p < .0001).
+To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
+We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the Shootout game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
+There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
+There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,$\eta^{2}$ = 0.02,  p = .01).
+Figure\ \@ref(fig:exp2-score-by-opp) shows boxplots of game scores, averaged across participants, by game and opponent type.
+We also distinguish between scores from the first time the players faced the opponent (first interaction) and the second time they did (second interaction).
+We see that when facing level-1 agents, scores increase steadily after each game, with FWG score significantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG  ( t(191) = 3.05, p = 0.01).
+There was no significant difference between average scores on any two games when facing level-2 agents however.
+
+### Learning transfer
+
+```{r, include=FALSE}
+dat <- read.csv(file = "../Experiment_2/dat_exp2.csv")
+```
+
+As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random.
+
+```{r, include = FALSE}
+
+#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########
+
+dat_26 <- subset(dat,(round >1 & round < 7) & (interaction_lvl == "first interaction" ), drop =TRUE)
+
+exp2_dat2_6 <- dat_26 %>% 
+  group_by(human_id,condition.f,game.f,opp_type,confidence,difficulty) %>% 
+      summarise(early_score = mean(adj_score))
+
+# Check group means and SDs
+group_by(exp2_dat2_6, game.f) %>%
+  summarise(
+    count = n(),
+    mean = mean(early_score, na.rm = TRUE),
+    sd = sd(early_score, na.rm = TRUE)
+    )
+group_by(exp2_dat2_6, game.f,opp_type) %>%
+  summarise(
+    count = n(),
+    mean = mean(early_score, na.rm = TRUE),
+    sd = sd(early_score, na.rm = TRUE)
+    )
+```
+
+```{r exp2-early-scores, fig.cap="Average early round scores and confidence intervals by game and opponent for experiment 2", fig.align="center"}
+# plot scores per game 
+p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Score rounds 2-6", xlab = "Games")
+
+p2 + facet_grid(. ~ opp_type)
+```
+
+In Figure\ \@ref(fig:exp2-early-scores), we show the average score across participants and its $95$ percent confidence interval in rounds 2-6 of the first interaction with the opponent for each game.
+These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
+For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
+(Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; Shootout:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; Shootout:  t(270) = 3.21, p =0.004 ).
+
+### Experiment 2 discussion:
+
+Looking at learning transfer by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
+Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
+These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
+
+\newpage
+
+# Computational modelling
+
+To gain more insight into how participants played the games against the computer opponents, we estimated and compared different computational models of strategies the players may have been using to learn how to beat the opponent.
+The baseline model assumes play is random, and each potential action is chosen with equal probability.
+Note that this corresponds to the Nash equilibrium strategy.
+In this section, we will go through the various models we have used and explain how they update what they learn about the game or the opponent
+
+## Reinforcement Learning
+
+We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
+We will use a simple delta learning update rule:
+
+$$ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) $$
+
+Where $V_{t}(a)$ is the value associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
+The probability of player $i$ choosing action $j$ at time $t+1$ denoted by $P_{i}^{j}(t+1)$ is based on action values using a softmax choice rule:
+
+$$P_{i}^{j}(t+1) = \frac{e^{\lambda . V_{t}^{j}(a)}}{\sum_{k=1}^{m_{i}}e^{\lambda . V_{t}^{k}(a)}} $$
+
+We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm [@watkins1992q]. The update rule becomes:
+
+$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$
+
+Where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\gamma$ is the discount rate applied to future rewards.
+For instance, $Q(RS,P)$ denotes the value of taking action "Paper" this round if the player's last action was "Rock" and the opponent played "Scissors".
+This is a much richer model allowing the players to compute the values of actions conditional on past play.
+
+<!-- In experiment 2, we allow this richer model to have a memory of the interaction.
+In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used.
+In another instance, we fit a model in which what was learned about an opponent in the first interaction is transferred to the first round of the second interaction, so there is a within-game transfer of Q-values allowed (QLS-within).
+We fit both models to all participant's data in the second experiment where both opponents are faced.
+-->
+
+### EWA Models 
+Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics].
+EWA models particularity is that they nest two seemingly different approaches, namely reinforcement learning and belief learning.
+Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
+In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
+The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
+
+Let's define some notation in order to write the update rule of the self-tuning EWA model.
+For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j).
+Strategies actually played by i in period t, are denoted $s_{i}(t)$, while the opponent's strategy at time t is denoted $s_{-i}(t)$.
+After playing  $s_{i}^{j}$ at time $t$, player i pay-off is denoted $\pi_{i}(s_{i}^{j},s_{-i}(t))$, and the actual pay-off the player received is $\pi_{i}(t)$.
+
+The EWA model is based on updating "Attractions" for each action over time.
+For instance, the attraction of strategy $j$ to player $i$ at time $t$ is written $A_{i}^{j}(t)$.
+Future action choice probabilities are based on these attractions using the softmax playing rule:
+
+$$P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} $$
+
+The attractions are updated over every time step $t$ using the following update rule :
+
+$$ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} $$
+
+Here, I(x,y) is the indicator function equal to 1 if $x = y$ and 0 otherwise.
+A simple way to think about this update rule is that attractions are multiplied by a parameter that represents experience ($N(t-1)$) which is itself decaying by a weight $\phi$.
+The result is added to either the pay-off received (when the indicator function is 0), or to $\delta$ times the foregone pay-off (when indicator function is 1).
+We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play [@cheung1994learning].
+While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].
+
+### ToM models
+
+In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
+We use values of k  in ${0,1,2}$.
+These models also assume the opponent can deviate from these level-k strategies and play randomly with probability $\theta$, a parameter to be fit.
+We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
+In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
+In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between transfer)
+
+Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
+In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
+
+We fit the above two models to experiment 1 data.
+In experiment two, on top of these two models, we fit another model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
+
+### Estimation and model comparison
+In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
+Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
+
+## Experiment 1 modelling :
+
+```{r load-comp-mod-distrib, include=FALSE}
+
+exp1_comp_results <- read.csv(file="../exp1_all_results.csv")
+exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Nash","ToM_BT","ToM_NBT", "QL_states","ST_EWA_states")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])
+
+ #write.csv(exp1_comp_table ,file="exp1_comp_table ",row.names = TRUE)
+ kable(exp1_comp_table)
+```
+
+```{r exp1-cum-score-plots, include=FALSE}
+
+exp1_dat = read.csv("../exp1_data.csv")
+
+exp1_model_comp <- data.frame()
+for(id in unique(exp1_dat$human_id)) {
+  tdat <- subset(exp1_dat,human_id == id)
+  tot_score <- sum(tdat$score)
+  tot_time <- sum(tdat$human_rt)
+  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
+  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
+  tr_score <- sum(early_dat$score)
+  id_results <- subset(exp1_comp_results, ID == id)
+  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,min)
+
+  best_model <- c("Nash","ToM_BT","ToM_NBT", "QL_states","STEWA_States")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)]
+  # 
+  exp1_model_comp <- rbind(exp1_model_comp,
+                       data.frame(
+                         "human_id" = id,
+                         "condition" = exp1_dat[exp1_dat$human_id==id,"condition"][1],
+                         "Early_game_score" = tr_score,
+                         "Total_score" = tot_score,
+                         "Best_model" = best_model,
+                         "Total_time" = sum(tdat$human_rt),
+                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
+                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
+
+                       ))
+}
+
+datalist = list()
+i = 0
+new_dat <- setNames(data.frame(matrix(ncol = ncol(exp1_dat), nrow = 0)), colnames(exp1_dat))
+for(id in unique(exp1_dat$human_id)) {
+  i <- i+1
+  tdat <- subset(exp1_dat,human_id == id)
+  tdat$part_num <- i
+  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
+  datalist[[i]] <- tdat
+}
+
+# Merge all datasets into one 
+new_dat <- dplyr::bind_rows(datalist)
+# or new_dat <- data.table::rbindlist(datalist)
+
+# Add column for time t
+new_dat <- new_dat %>% dplyr::group_by(exp1_dat$human_id) %>% dplyr::mutate(t = row_number())
+
+# Add best fitting model per participant
+new_dat <- merge(new_dat, exp1_model_comp[, c("human_id", "Best_model")], by="human_id")
+
+temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
+dat_by_model <- temp %>% group_by(Best_model,t) %>% 
+  summarize(model_acc_sum = mean(acc_sum))
+
+```
+
+Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning with states defined by last round play.
+
+```{r, include=FALSE}
+
+#Only select models we're interested in 
+exp1_comp_BICs <- exp1_comp_results[c("ID","Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")]
+
+exp1_BIC_weights <- exp1_comp_BICs["ID"]
+exp1_BIC_weights[,2:ncol(exp1_comp_BICs)] <- t(apply(exp1_comp_BICs[,-1], 1, function(i) exp(-0.5*(i-min(i)) )))
+colnames(exp1_BIC_weights) <- c("ID","Nash","ToM_BT","ToM_NBT","QL_states","STEWA_States")
+exp1_BIC_weights[,-1] <- t(apply(exp1_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
+
+Average_BIC_weights <- as.data.frame(t(round(apply(exp1_BIC_weights[,-1],2,mean),2)))
+row.names(Average_BIC_weights) <- c("Model BIC weights")
+Average_BIC_weights
+
+#Count_Best_fit <- table(exp1_model_comp$Best_model)
+temp <- plyr::count(exp1_model_comp,"Best_model")
+Count_Best_fit <- tidyr::spread(temp,Best_model, freq)
+row.names(Count_Best_fit) <- c("Count best fit")
+Count_Best_fit
+
+table_exp_1 <- rbind.fill(Average_BIC_weights,Count_Best_fit)
+row.names(table_exp_1) <- c("Model BIC weights","Count best fit")
+table_exp_1
+
+```
+
+```{r exp1weightstable, results="asis", echo=FALSE, warning=FALSE}
+
+######apa_table breaks knitr....not sure why.
+#######
+papaja::apa_table(table_exp_1, caption = "Experiment one Average BIC weights and number of participants best fit by model")
+
+#knitr::kable(table_exp_1, caption = "Experiment 1 - Average BIC weights and number of participants best fit by model")
+
+```
+
+Table \ \@ref(tab:exp1weightstable) shows the model BIC weights  as well as the number of participants best fit by each model.
+
+```{r exp1-comp-models, fig.cap = "Experiment 1 - Histogram of best fitting computational models by condition", fig.align='center'}
+
+#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
+par(las=2) # make label text perpendicular to axis
+par(mar=c(5,8,4,2)) # increase y-axis margin.
+barplot(exp1_comp_table,
+        horiz =TRUE, # rotate barplot for better visibility 
+        las=1, # change orientation x axis labels 
+        cex.names=0.8, # text label size
+        legend = rownames(exp1_comp_table),
+        beside =TRUE,
+        xlab="Number of participants",
+        args.legend=list( # positioning of legend box 
+        x=ncol(exp1_comp_table) + 4,
+        y=max(colSums(exp1_comp_table)) + 4,
+        bty = "n")
+ )
+
+```
+
+Next we compared the performance of players whose actions are best fit by each of our hypothesized models.
+Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
+We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (without transfer), followed by Q-learning conditional on last round play.
+EWA, QL and random players had, understandably the lowest performance.
+
+```{r exp1-cumScores, fig.cap = "Experiment 1 - Average cumulative scores of participants by best fitting model", fig.align='center'}
+p5 <- ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
+   geom_line(aes(color= Best_model))
+
+p5 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
+```
+
+## Experiment 2
+
+```{r, include = FALSE}
+
+exp2_comp_results <- read.csv(file="../Experiment_2/exp2_results.csv")
+
+exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Nash","TOM BT","TOM NBT", "TOM NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])
+
+ # write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
+exp2_comp_table
+```
+
+```{r exp2-comp-models, fig.cap = "Experiment 2 Histogram of best fitting computational models by condition", fig.align='center'}
+
+par(las=2) # make label text perpendicular to axis
+par(mar=c(5,8,4,2)) # increase y-axis margin.
+barplot(exp2_comp_table,
+        horiz =TRUE, # rotate barplot for better visibility 
+        las=1, # change orientation x axis labels 
+        cex.names=0.8, # text label size
+        beside =TRUE,
+        xlab="Number of participants",
+        # legend = c("level-1 opp first","level-2 opp first"),
+        legend = paste0(rownames(exp2_comp_table) , " faced first"),
+        args.legend=list( # positioning of legend box 
+        x=ncol(exp2_comp_table) + 6,
+        y=max(colSums(exp2_comp_table)) +1,
+        bty = "n")
+ )
+
+```
+
+```{r, include=FALSE}
+
+dat_exp2 = read.csv("../Experiment_2/data_exp2.csv")
+
+#Adjust shootout score tor eflect easier game
+dat_exp2$adj_score <- ifelse(as.character(dat_exp2$game) == "shootout", dat_exp2$score - 0.333, dat_exp2$score)
+
+# Build dataframe comparing models BIC for each participant 
+exp2_model_comp <- data.frame()
+for(id in unique(dat_exp2$human_id)) {
+  tdat <- subset(dat_exp2,human_id == id)
+  tot_score <- sum(tdat$score)
+  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
+  tr_score <- sum(early_dat$score)
+  id_results <- subset(exp2_comp_results, ID == id)
+
+  # MS BAYES MODELS
+  min_BIC <- apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,min)
+
+  best_model <- c("Nash","TOM BT","TOM NBT", "TOM NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)]
+
+  exp2_model_comp <- rbind(exp2_model_comp ,
+                       data.frame(
+                         "human_id" = id,
+                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
+                         "Early_game_score" = tr_score,
+                         "Total_score" = tot_score,
+                         "Best_model_2" = best_model,
+                         "Total_time" = sum(tdat$human_rt),
+                         # "BT_minus_NBT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
+                         "BT_minus_NBT_BIC" = id_results[,"Distinct_game_BIC"] - id_results[,"Distinct_stage_BIC"],
+                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
+
+                       ))
+}
+
+datalist2 = list()
+i = 0
+
+#Build empty dataframe with same names as original data
+exp2_cum_score <- setNames(data.frame(matrix(ncol = ncol(dat_exp2), nrow = 0)), colnames(dat_exp2))
+for(id in unique(dat_exp2$human_id)) {
+  i <- i+1
+  tdat <- subset(dat_exp2,human_id == id)
+  tdat$part_num <- i
+  # NB : USE ADJUSTED SCORE IN SHOOTOUT
+  tdat <- within(tdat, acc_sum <- cumsum(tdat$adj_score))
+  datalist2[[i]] <- tdat
+}
+
+# Merge all datasets into one 
+exp2_cum_score <- dplyr::bind_rows(datalist2)
+# or exp2_cum_score <- data.table::rbindlist(datalist)
+
+# Add column for time t
+exp2_cum_score <- exp2_cum_score %>% group_by(human_id) %>% mutate(t = row_number())
+
+# Participant number as a factor 
+# tdat$part_num <- as.factor(tdat$part_num)
+
+# Add best fitting model per participant
+exp2_cum_score <- merge(exp2_cum_score, exp2_model_comp[, c("human_id", "Best_model_2")], by="human_id")
+
+temp2 <- exp2_cum_score[,c("t","acc_sum","Best_model_2","condition","part_num")]
+
+dat_by_model_2 <- temp2 %>% group_by(Best_model_2,t) %>% 
+  summarize(avg_acc_sum = mean(acc_sum))
+
+```
+
+```{r, include=TRUE}
+
+#Only select models we're interested in 
+exp2_comp_BICs <- exp2_comp_results[c("ID","Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")]
+
+exp2_BIC_weights <- exp2_comp_BICs["ID"]
+exp2_BIC_weights[,2:ncol(exp2_comp_BICs)] <- t(apply(exp2_comp_BICs[,-1], 1, function(i) exp(-0.5*(i-min(i)) )))
+colnames(exp2_BIC_weights) <- c("ID","Nash","TOM BT","TOM NBT", "TOM NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")
+exp2_BIC_weights[,-1] <- t(apply(exp2_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
+
+# Get dataframe of average BIC weights by model 
+Average_BIC_weights_2 <- as.data.frame(t(round(apply(exp2_BIC_weights[,-1],2,mean),2)))
+row.names(Average_BIC_weights_2) <- c("Model BIC weights")
+
+# Get dataframe of counts of participants fit by each model
+temp <- plyr::count(exp2_model_comp,"Best_model_2")
+Count_Best_fit_2 <- tidyr::spread(temp,Best_model_2, freq)
+#Count_Best_fit_2
+
+#Combine in one table
+table_exp_2 <- rbind.fill(Average_BIC_weights_2,Count_Best_fit_2)
+table_exp_2[is.na(table_exp_2)] <- 0
+rownames(table_exp_2) <- c("BIC weights","Count best fit")
+
+table_exp_2[2,] <- round(table_exp_2[2,],0)
+table_exp_2
+
+```
+
+(ref:my-table2-caption) Experiment 2 BIC weights and number of participants best fit by model.
+```{r exp2-weights-table, results="asis", echo=FALSE}
+
+# papaja::apa_table(
+#   table_exp_2
+#   , caption = "(ref:my-table2-caption)"
+#   , escape = FALSE)
+
+knitr::kable(table_exp_2, caption = "Experiment 2 - Average BIC weights and number of participants best fit by model")  %>% 
+  kable_styling(latex_options = c("scale_down"))
+```
+
+In experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that Q-learning with the aforementioned state-space was again more successful than the Bayesian models in fitting player's action choices.
+In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
+This is also reflected in BIC weights in Table \ \@ref(tab:exp2-weights-table)
+
+```{r exp2-cumScores, fig.cap = "Experiment 2 Average cumulative scores of participants by best fitting model", fig.align='center'}
+
+ p8 <- ggplot(data = dat_by_model_2, aes(x = t, y=avg_acc_sum, group = Best_model_2)) + 
+   geom_line(aes(color= Best_model_2)) +
+  scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))
+
+p8 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
+
+```
+
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the opponent strategy had the highest cumulative performance.
+Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance (although it only fit 2 participants best), followed by a model in which both within and between transfer of opponent models is allowed (BT).
+The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where players reset opponent models at each stage of each game (NT).
+As expected, random play was at the bottom of cumulative performance.
+
+## Using Hidden Markov Model to explore strategy switching
+
+The computational modelling indicates that most players are best fit by Q-learning type models with states defined by last round play.
+This is at odds with the findings from the section regarding learning transfer: If indeed most participants use Q-learning with states to choose their actions, then they should not be able to transfer learning to the early rounds of the new game.
+In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Theory of Mind models with and without the possibility of across game transfer.
+
+We start with experiment 1 data.
+Figure\ \@ref(fig:exp1-lik-by-tr) shows that in the later games, the likelihood for the ToM models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of ToM models.
+
+```{r, include= FALSE}
+
+exp1_lik_by_trial  <- read.csv("../exp1_lik_by_trial.csv")
+
+exp1_lik_by_trial <- exp1_lik_by_trial %>%
+    dplyr::mutate(Nash_lik = ifelse( (game == "rps" | game == "fwg"),1/3, 1/5))
+
+mean_lik <- exp1_lik_by_trial %>%
+  dplyr::select(human_id,condition,game, round, Nash_lik, QLS_lik, Bayes_Tr_lik) %>%
+  group_by(condition,game,round) %>%
+  dplyr::summarise(mean_Nash_lik = mean(Nash_lik, na.rm = TRUE),
+                   mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
+                   mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
+
+mean_lik$game <- factor(mean_lik$game,levels=c("rps","fwg","numbers"))
+
+data_long <- tidyr::gather(mean_lik, strategy, probability, mean_Nash_lik:mean_Tr_lik, factor_key=TRUE)
+
+```
+
+```{r exp1-lik-by-tr, fig.cap = "Experiment 1 Likelihood by trial by game and opponent faced", fig.align='center'}
+# make sure the different games are ordered in the way they were played
+# data_long$game <- factor(data_long$game,levels=c("rps","fwg","numbers"))
+ggplot(data_long,aes(x=round,y=probability,colour=strategy)) +
+  geom_line() +
+  facet_grid(game~condition) +
+  scale_colour_discrete(name = "Strategy", labels = c("Nash", "Q_learning", "ToM + Tr"))
+
+```
+
+Likewise, in experiment 2,  we want to understand the dynamic of strategy choice by plotting the likelihood by trial for each strategy, using the optimal parameters found when fitting the model.
+Figure\ \@ref(fig:exp2-lik-by-tr) shows that, as in experiment 1, ToM models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
+In the third and more dissimilar game, we get a result that is different from experiment 1.
+In this instance, the likelihoods of the ToM models stay constant and close to their initial values.
+
+```{r, include = FALSE }
+
+exp2_lik_by_trial <- read.csv("../Experiment_2/exp2_lik_by_trial.csv")
+
+exp2_lik_by_trial <-  exp2_lik_by_trial %>% dplyr::mutate(Nash_lik = 1/3)
+
+mean_lik_2 <- exp2_lik_by_trial %>%
+  dplyr::select(human_id,game,stage,round_condition, round, Nash_lik, QLS_lik_within, Bayes_Tr_lik) %>%
+  dplyr::group_by(game,stage,round) %>%
+  dplyr::summarise(mean_Nash_lik = mean(Nash_lik, na.rm = TRUE),
+             mean_QLS_within_lik = mean(QLS_lik_within, na.rm = TRUE),
+             mean_ToM_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
+
+mean_lik_2$game <- factor(mean_lik_2$game,levels=c("rps","fwg","shootout"))
+
+data_long2 <- gather(mean_lik_2, strategy, probability, mean_Nash_lik:mean_ToM_Tr_lik, factor_key=TRUE)
+```
+
+```{r exp2-lik-by-tr, fig.cap = "Experiment2 likelihood by trial by game and opponent faced", fig.align ='center'}
+# make sure the different games are ordered in the way they were played
+# data_long2$game <- factor(data_long$game,levels=c("rps","fwg","shootout"))
+ggplot(data_long2,aes(x=round,y=probability,colour=strategy)) +
+  geom_line() +
+  facet_grid(game~stage) +
+  scale_colour_discrete(name = "Strategy", labels = c( "Nash", "Q_Learning + within Tr", "ToM + Tr"))
+
+```
+
+The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative of participants switching between strategies as the games progressed.
+Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the ToM based strategies fitted observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
+
+In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q-learning with state space consisting of previous round play, ToM based model with opponent model transfer, and a base model consisting of random play consistent with a Nash equilibrium strategy).
+Hidden Markov models are useful tools to explore structure in observed time series.
+They are named as such because of two properties: First, they make the assumption that any observable action at time t results from a process whose state at time t , named $S_{t}$ is "hidden" from the observer.
+Second, it also assumes that this hidden process has a Markov property, meaning that given state $S_{t-1}$, the value of $S_{t}$ is independent of all states occurring before time $t-1$.
+We also assume that $S_{t}$ has a discrete probability distribution in that it take one of K discrete values.
+The model is therefore specified by initial probabilities of being in each state ${1,2,...,K}$ and transition probabilities for moving from state $i$ to state $j$.
+These probabilities are fit using observed actions generated from these hidden states.
+
+To investigate the possibility of strategy switching, we fit two different hidden Markov models with the depmixS4 R package.
+In the first model, we allow for a non-nil probability of players transitioning from one state (strategy) to another.
+In the second model, we assume that such switching does not happen, and as such assume implicitly that when players start with a particular strategy, they continue using it throughout the experiment.
+We then compare the likelihoods of each HMM model using a likelihood ratio test.
+
+### Experiment 1:
+```{r define-dummy-response, include=FALSE}
+setClass("dummyResponse", contains="response")
+
+setGeneric("dummyResponse", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("dummyResponse"))
+
+setMethod("dummyResponse", 
+    signature(y="ANY"), 
+    function(y,pstart=NULL,fixed=NULL, ...) {
+      y <- matrix(y,length(y))
+  		x <- matrix(1)
+  		parameters <- list()
+  		npar <- 0
+      mod <- new("dummyResponse",parameters=parameters,fixed=logical(0),x=x,y=y,npar=npar)
+      mod
+	}
+)
+
+setMethod("show","dummyResponse",
+    function(object) {
+        cat("Dummy for fixed likelihood Model \n")
+    }
+)
+
+setMethod("dens","dummyResponse",
+  function(object,log=FALSE) {
+   if(log) log(as.numeric(object@y)) else as.numeric(object@y)
+  }
+)
+
+setMethod("getpars","dummyResponse",
+    function(object,which="pars",...) {
+        switch(which,
+            "pars" = {
+                pars <- numeric(0)
+            },
+            "fixed" = {
+                pars <- logical(0)
+            }
+        )
+        return(pars)
+    }
+)
+
+setMethod("setpars","dummyResponse",
+    function(object, values, which="pars", ...) {
+        npar <- npar(object)
+        if(length(values)!=npar) stop("length of 'values' must be",npar)
+        # determine whether parameters or fixed constraints are being set
+		nms <- ""
+		switch(which,
+		  "pars"= {
+		      },
+		  "fixed" = {
+		    }
+		  )
+      names(object@parameters) <- nms
+      return(object)
+    }
+)
+
+setMethod("fit","dummyResponse",
+    function(object,w) {
+		  return(object)
+	}
+)
+
+setMethod("predict","dummyResponse", 
+    function(object) {
+        ret <- object@y
+        return(ret)
+    }
+)
+```
+
+```{r, include=FALSE}
+
+## EXPERIMENT 1 Data
+
+Nash_lik <- exp1_lik_by_trial$Nash_lik
+QLS_lik <- exp1_lik_by_trial$QLS_lik
+Bayes_Tr_lik <- exp1_lik_by_trial$Bayes_Tr_lik
+# QLS_lik[which(QLS_lik == 0)] <- .001
+# QLS_lik[is.na(QLS_lik)] <- .33 # this is a hack; there shouldn't be any missing values
+
+nsubject <- length(unique(exp1_lik_by_trial$human_id)) # number of participants
+ngame <- 3 # number of games
+ntrial <- c(50,50,50) # numer of trials in each game
+
+rModels <- list(
+  list(
+	  dummyResponse(QLS_lik)
+	),
+	list(
+		dummyResponse(Nash_lik)
+	),
+  list(
+    dummyResponse(Bayes_Tr_lik)
+  )
+)
+
+trstart <- matrix(c(0.8,0.1,0.1,0.1,0.8,0.1,.1,.1,.8),ncol=3)
+transition <- list()
+transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
+transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
+transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
+
+instart <- c(1/3,1/3,1/3)
+inMod <- transInit(~1,nstates=3,pstart=instart,family=multinomial("identity"),data=data.frame(rep(1,nsubject*ngame)))
+
+mod1 <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
+
+fmod1 <- fit(mod1, emcontrol=em.control(random.start=FALSE))
+```
+
+```{r no-switch, include=FALSE}
+
+# No switching. Force off diagonal initial elements of transtion matrix to 0
+trstart <- matrix(c(1,0,0,0,1,0,0,0,1),ncol=3)
+transition <- list()
+transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
+transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
+transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
+
+mod1_noswitch <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
+
+fmod1_noswitch <- fit(mod1_noswitch, emcontrol=em.control(random.start=FALSE))
+
+# p-value for comparison between a model with strategy switches and one without:
+
+1-pchisq(-2*as.numeric(logLik(fmod1_noswitch)) - (-2*as.numeric(logLik(fmod1))),df=6)
+```
+
+```{r, include = FALSE}
+
+exp1_lik_by_trial["post_QLS"] <- forwardbackward(fmod1)$gamma[,1]
+exp1_lik_by_trial["post_Nash"] <- forwardbackward(fmod1)$gamma[,2]
+exp1_lik_by_trial["post_Bayes_Tr"] <- forwardbackward(fmod1)$gamma[,3]
+
+mean_post_1 <- exp1_lik_by_trial %>%
+  dplyr::select(human_id,game,condition, round, post_QLS, post_Bayes_Tr) %>%
+  dplyr::group_by(game,condition, round) %>%
+  dplyr::summarise(QLS_posterior = mean(post_QLS, na.rm = TRUE),
+            Bayes_Transfer_posterior = mean(post_Bayes_Tr, na.rm = TRUE))
+
+mean_post_1$game <- factor(mean_post_1$game,levels=c("rps","fwg","numbers"))
+
+data_long_post1 <- gather(mean_post_1, strategy, probability, QLS_posterior,Bayes_Transfer_posterior, factor_key=TRUE)
+
+```
+
+```{r exp1-posteriors-plot, fig.cap = "Experiment1 posterior probability of strategies by game and opponent faced", fig.align ='center'}
+
+ggplot(data_long_post1,aes(x=round,y=probability,colour=strategy)) +
+  geom_line() +
+  facet_grid(game~condition)
+
+```
+
+In experiment 1, the HMM model with switching fits significantly better than the non-switching one ($p < .001$).
+This is further statistical evidence in favour of the hypothesis that participants switch between strategies.
+In order to understand at which stage of the games the switching might happen, and whether there are any differences between games and type of opponents faced, we plot in Figure\ \@ref(fig:exp1-posteriors-plot) the average (across participants) posterior probabilities of each state (strategy), as a function of trial and opponent faced.
+The posterior probability is the probability that an observation comes from a component distribution a posteriori, i.e.
+given the value of the observation.
+In the first experiment, we can see from the plots of fwg and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the QLS model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
+
+### Experiment 2:
+
+```{r, include =FALSE}
+## EXPERIMENT 2 DATA 
+# we need to have "dat" available and lik_by_trial
+QLS_lik <- exp2_lik_by_trial$QLS_lik
+Nash_lik <- exp2_lik_by_trial$Nash_lik
+Bayes_Tr_lik <- exp2_lik_by_trial$Bayes_Tr_lik
+
+nsubject <- length(unique(exp2_lik_by_trial$human_id)) # number of participants
+ngame <- 12 # number of games
+#ntrial <- c(60,60,60)
+
+ntrial <- c(20,20,10,10,20,20,10,10,20,20,10,10) # number of trials in each game
+
+rModels <- list(
+  list(
+	  dummyResponse(QLS_lik)
+	),
+	list(
+		dummyResponse(Nash_lik)
+	),
+  list(
+    dummyResponse(Bayes_Tr_lik)
+  )
+)
+
+trstart <- matrix(c(0.8,0.1,0.1,0.1,0.8,0.1,.1,.1,.8),ncol=3)
+transition <- list()
+transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
+transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
+transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
+
+instart <- c(1/3,1/3,1/3)
+inMod <- transInit(~1,nstates=3,pstart=instart,family=multinomial("identity"),data=data.frame(rep(1,nsubject*ngame)))
+
+mod <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
+
+fmod <- fit(mod, emcontrol=em.control(random.start=TRUE))
+```
+
+```{r}
+
+exp2_lik_by_trial["post_QLSw"] <- forwardbackward(fmod)$gamma[,1]
+exp2_lik_by_trial["post_Nash"] <- forwardbackward(fmod)$gamma[,2]
+exp2_lik_by_trial["post_Bayes_Tr"] <- forwardbackward(fmod)$gamma[,3]
+
+mean_post_2 <- exp2_lik_by_trial %>%
+  dplyr::select(human_id,game,stage,round_condition, round, post_QLSw, post_Bayes_Tr) %>%
+  dplyr::group_by(game,stage, round) %>%
+  dplyr::summarise(mean_post_QLSw = mean(post_QLSw, na.rm = TRUE),
+            mean_post_Tr = mean(post_Bayes_Tr, na.rm = TRUE))
+
+mean_post_2$game <- factor(mean_post_2$game,levels=c("rps","fwg","shootout"))
+
+data_long_post2 <- gather(mean_post_2, strategy, probability, mean_post_QLSw,mean_post_Tr, factor_key=TRUE)
+
+```
+
+```{r exp2-posteriors-plot, fig.cap = "Experiment2 likelihood by trial by game and opponent faced", fig.align ='center'}
+
+ggplot(data_long_post2,aes(x=round,y=probability,colour=strategy)) +
+  geom_line() +
+  facet_grid(game~stage)
+
+```
+
+The switching model in experiment two has also significantly higher likelihood ($p$ = 0.00).
+On top of indications from looking at the likelihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
+The posterior probability plot in Figure\ \@ref(fig:exp2-posteriors-plot) shows switching much more clearly across games and stages.
+The switching also seems to happen very early on at the beginning of each game and stage, and is also consistently in the same direction: The probability of Bayesian models with transfer being initially high, then decreasing rapidly while the posterior probability of QL-Learning with states and within transfer learning increases rapidly.
+
+Therefore, HMM modelling shows clear evidence in favour of strategy switching by participants, specifically after a few rounds of play.
+The strategy switching is consistently from ToM models towards Q-learning with states models in both experiments.
+
+\newpage
+
+# Discussion
+
+In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies.
+We were interested in exploring whether participants learn about the strategy of their opponent and transfer such knowledge between games, and whether this is modulated by the similarity between games and the sophistication of the agent.
+
+The results of our first online experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
+We used results on very early rounds for measuring transfer as they are unlikely to be tainted by any within game learning.
+Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
+
+In the second online experiment, there were many more opportunities to test transfer than before: 2 opportunities to transfer opponent models within each game, and a total of three games, which means 6 opportunities to test transfer.
+The results on learning transfer confirmed prior findings from the first experiment.
+While there was no evidence of higher scores across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
+We also found that learning transfer is modulated by the type of opponent faced.
+When the players faced the level-1 opponent, they were able to transfer learning.
+However, when they faced the level-2 opponent, there was weaker evidence for transfer.
+The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with.
+A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
+
+Coming back to learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are significantly higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
+The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
+what did the players learn specifically about the opponent strategy and what form did this learning take?
+
+We will proceed by considering multiple potential answers to this question.
+First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
+An example is a spatial heuristic that consists of choosing "weapons" in a particular order.
+For instance, it is possible to keep winning against a level-k opponent by choosing actions in a particular spatial order such as cycling through them from left to right.
+This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
+We took this into account in designing experiment two by randomly shuffling the spatial order of action choices in each round.
+Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.
+
+A second possible hypothesis for learning the opponent’s strategy is the use of simple rules based on last round play (for instance, I play scissors whenever opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
+Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
+While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
+Indeed, learning the best action in a particular state is not transferable to a new game since the state space is different and there is no single mapping between the state spaces of the initial and latter games.
+These rules would therefore need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
+
+Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, would require many rounds of practice.
+Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
+More specifically, if we assume that participants were using some type of associative learning or relying on spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
+To be sure, if a participant learns to pick say "scissors" whenever the opponent last picked "rock", then the degree of strategic sophistication of the opponent (its level k) should not impact this learning, and we would expect in this case there would be no difference between scores when facing level-1 and level-2 opponents, which is not the case here.
+The fact that the degree of sophistication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
+
+We are left with two possible explanations: First, it is possible that the players have uncovered a heuristic that allows them to beat the opponent without explicitly modelling their strategy, and is robust to transfer.
+Indeed, because of the cyclicality in action choices (e.g : Rock beats Scissors beats Paper beats Rock), it is possible to beat level-2 opponents most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
+This is a rule that wins and is also robust to transfer as it does not depend on action labels and even works in the dissimilar game.
+
+The second explanation of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
+A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
+For instance, the player may think “My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be”.
+This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
+This type of learning would be deemed “explicit” in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
+It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
+Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
+
+Our second experimental design allows us to test whether the first explanation holds.
+Since there is a simple transferable heuristic that works against level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
+Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.
+
+Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first interactions across games and using early rounds analysis.
+Based on our assumptions, we conclude therefore that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the course of learning.
+
+Our computational modelling allowed us to delve deeper into what might be driving the observed learning transfer.
+Initial modelling of observations using all available data seems to indicate that the most likely model was a Q-learning type model.
+However, as we argued above, that would be inconsistent with the evidence for learning transfer.
+Breaking down likelihoods by trial and fitting a hidden markov model to the data with states being the various strategies that participants are assumed to be using, we showed evidence for within game switching of strategies.
+Participants start the early rounds of a new game acting in a way consistent with a Bayesian Theory of mind level, which would be accurate and generalisable but computationally expensive.
+However, as trials continue, participants seem to switch to a habitual type of learning (QL-models).
+
+Why is this switching happening?
+We believe that participants show flexibility in their use of learning strategies.
+When a new game is started that is similar to a previously played game with the same opponent, participants need a way to transfer prior knowledge of the opponent and apply it to the new game in order to best respond.
+Adopting a Bayesian model based on ToM achieves the goal of transferring the opponent model and thus coming up with best responses in the early trials.
+However, Bayesian ToM models are computationally expensive and require higher order thinking (I think that you think that I think...).
+As such, as the games progresses, they may become burdensome and the higher amount of historical interaction in the new game allows participants to have enough data to start using the cognitively cheaper model-free learning strategies such as Q-learning.
+The preference for less computationally demanding strategies is well established [@Kool_2011].
+Moreover, the ability to flexibly switch is also consistent with evidence from the literature on learning strategies in humans, showing that they indeed shift between model-based and model-free learning when the environment requires it [@Simon_Daw_11].
+
+\newpage
+
+# Conclusion
+
+Our online experiments results are consistent with behavioural game theory findings, in that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
+Moreover, we showed that participants transfer their learning to new games with varying degrees of similarity.
+The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.
+
+Having said that, there remains a high degree of heterogeneity between players.
+There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
+Moreover, the computational modelling shows that it is likely that players start each game using a model-based learning strategy that facilitates generalisation and opponent model transfer, but then switch to behaviour that is consistent with a  model-free learning strategy as the experiment goes on.
+This is likely driven by a trade-off between computational complexity and accuracy between model based and model free strategies.
+\newpage
+
+# References
+
+```{r create_r-references}
+r_refs(file = "Mendeley2.bib")
+
+```
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id = "refs"></div>
+\endgroup
+
+<!--chapter:end:draft_report_v3.Rmd-->

### 2020-10-30 Report/brouillon.Rmd
draft3

--- 2020-09-08 Report/draft_report_v2.Rmd
@@
 ---
-title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-shorttitle        : "Draft-2"
+title             : "brouillon"
+shorttitle        : "Draft-3"
 
@@
 
-bibliography      : ["Mendeley.bib"]
-# csl               : "apa-6th-edition.csl"
+bibliography      : ["Mendeley2.bib"]
+csl               : "apa-6th-edition.csl"
 
@@
 output            : papaja::apa6_pdf
+citation_package  : natbib
 ---
@@
 require(bookdown)
+
 # using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
+library(plyr)
 library(tidyr)
@@
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
-More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
+More formally, @perkins1992transfer defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
 This typically human skill has so far eluded modern AI agents.
@@
 Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-@Lake2017 argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
+[@Lake2017] argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 
-Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
-A notable exception is the effort by @Haruvy2012 to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
-Participants played ten games, presented as 4x4 normal form (matrix payoffs).
-Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
-They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on @stahl1995players, was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
-
-Still, one of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
-@simon1972theories explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
-Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in 'level-k' theory, first adopted by @stahl1995players.
-It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment @arad201211.
-Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
-Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below, and so on.
-
-In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit @goodie2012levels.
-
-Our choice of using computer oponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-When playing against other human opponents, players are learning about the game and the strategy of the opponent simultaneously.
-Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
-The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
-For instance, @spiliopoulos2013strategic made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
-@shachat2004we made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
-
-We chose to use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
-We avoid social dilemma and coordination games that crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
-Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
-Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
-As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transferred.
-By contrast, purely competitive settings and zero sum games in particular would be more appropriate.
-They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building.
-Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learning.
-Games with unique mixed strategy Nash equilibrium leading to nil average rewards facilitate inferring whether participants have learned to exploit the non-random play of the opponent.
-
-We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
-The first two games we use are identical except for action labels.
-In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with a fixed expected reward against a Nash player.
-
-Hence, we ran a total of two experiments where human participants played 3 different games against either 1 (first experiment ) or 2 (second experiment) computer opponents.
-In the following sections, we will describe each experiment's methodology and results separately, then discuss the findings before using computational modelling to shed light on some of the results.
-
-\newpage
-
-# Experiment 1
-
-## Methods
-
-## Participants
-
-A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
-The mean age of participants was 31.2 years.
-Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
-
-## Procedure
-
-In the first experiment, participants played 3 games sequentially against the same computer opponent.
-The computer opponent either used a level-1 or level-2 strategy.
-The three games were rock-paper-scissors, fire-water-grass and the numbers game.
-A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
-If one player choses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
-Otherwise it is a draw and both players receive a reward of 0.
-It has a unique MSNE consisting of randomly playing one of the three options each time.
-
-The second game is identical to Rock-Paper-Scissors in all but action labels.
-We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
-We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
-Finally, the numbers game is a generalization of rock-paper-scissors.
-In the variant we use, 2 participants concurrently pick a number between 1 and 5.
-To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent.
-For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
-To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
-This game has a structure similar to RPS in which every action is dominated by exactly one choice.
-All other possible combination of choices that are not consecutive are considered ties.
-A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score.
-Similar to RPS, the MSNE is to play each action with equal probability in a random way.
-
-Participants were informed they would play three different games against the same computer opponent.
-Each participant plays all three games consecutively and in the same order described above.
-Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
-A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
-The score was calculated as the number of wins minus the number of losses.
-Ties did not affect the score.
-In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-The overall score of the players was translated into the bonus by making each point worth £0.02.
-This bonus is significant as players could increase the total payoff from the experiment by up to 60% assuming they'd won all rounds against the computer opponent.
-An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps).
-
-```{r feedback-rps, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align='center'}
-
-knitr::include_graphics("images/feedback_rps.png")
-
-```
-
-## Results
-
-```{r load-exp1-data, include=FALSE}
-
-dat1 <- read.csv("../data20180719.csv")
-
-# transform 'winner' variable in numeric score
-dat1$score <- recode(dat1$winner, human = 1, tie = 0, ai = -1)
-# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
-dat1$block <- factor(as.numeric(cut(dat1$round,2)),labels =c("first half", "second half"))
-
-# create a new variable "game.f" as a factor variable of games
-dat1$game.f <- factor(dat1$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))
-
-#Group data by human_id and calculate mean score per block of each game.
-dat2 <- dat1 %>% 
-  group_by(human_id,condition,game,block,game.f) %>% 
-      summarize(block_score = mean(score))
-
-# Group data by game and ID
-dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
-# head(dat3,6)
-
-# Subsetting scores data by game
-rps <- subset(dat3,  game.f == "RPS",game_score)
-fwg <- subset(dat3,  game.f == "FWG",game_score)
-num <- subset(dat3,  game.f == "NUM",game_score)
-# head(rps,6)
-```
-
-```{r exp1-avg-scores-game, fig.cap = "Average scores per game across conditions", fig.align="center"}
-# Plot average  scores per game 
-ggboxplot(dat3, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
-```
-
-Looking at the aggregate scores (See Figure\ \@ref(fig:exp1-avg-scores-game) ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
-Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value < 0.001 ;  FWG:  t(51) = 10.04 , p-value < 0.001 ; NUMBERS: t(51) = 7.17, p-value < 0.001).
-
-To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game ( F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
-The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
-The main effect of Block ( F(1,50) = 22.51 , p < .001, $\eta^{2}$ = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning.
-As players interact more with the agent, they learn how to win more often.
-The main effect of Condition (F(1,50) = 5.44, p = .024, $\eta^{2}$ = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
-This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
-
-```{r exp1-3factor-plot, fig.cap = "Average scores by game, block and condition", fig.align = "center"}
-
-# Plot results by game and block (for all 3 games, learning is happening) 
-p <- ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")
-
-p + facet_grid(. ~ condition)
-
-```
-
-Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, $\eta^{2}$ = 0.02), indicating that within-game learning differed between the games.
-Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p <.0001), while there was no significant difference between block scores for the other two games.
-This is indicative of the significant within game learning happening in the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
-There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent.
-For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than agaisnt level-1 opponent.
-The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
-
-### Learning transfer
-
-As a measure for learning transfer, we focus on participants’ scores in the first 5 rounds excluding the initial round (rounds 2-6).
-We exclude the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response, and therefore we cannot expect the participants to exhibit any learned best responses either.
-A group of players with no experience of the game are expected to have scores not significantly different from 0 over the early rounds of a new game, as was the case in RPS.
-Any significantly positive group average scores would therefore reflect prior learning from past experiences.
-
-We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
-As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
-In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
-This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
-
-Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-Figure\ \@ref(fig: exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players.
-Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
-To test these hypotheses, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
-
-```{r exp1-early-rounds, include=FALSE}
-dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
-exp1_dat2_6 <- dat_26 %>% 
-  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
-      summarise(early_score = mean(score))
-
-# Check group means and SDs by game and condition
-group_by(exp1_dat2_6, game.f,condition) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-
-```
-
-```{r exp1-score-by-opp, fig.cap = "Average early scores by game and type of opponent faced", fig.align='center'}
-
-p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Average Score rounds 2-6", xlab = "Games")
-
-p2 + facet_grid(. ~ condition)
-
-```
-
-<!-- Table\ \@ref(tab:table-early-scores) shows the scores on rounds 2-6 for both type of opponents in each game.
-We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
-Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
--->
-
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p < 0.001) and NUMBERS (t(150) = 3.74, p < 0.001) .
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
-
-```{r ANOVA early exp1, include = FALSE, warning=FALSE}
-
-exp1_early_anova <- afex :: aov_car(
-  early_score ~ game.f*condition + Error(human_id/(game.f))
-  , data=exp1_dat2_6
-  , type = 3)
-
-#apa_lm1 <- apa_print(exp1_early_anova)
-
-means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
-trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","NUM"))
-
-```
-
-```{r table-early-scores, include = FALSE, results = "asis"}
-# apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
-```
-
-Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game.
-Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
-
-\newpage
-
-# Second Experiment
-
-## Methods
-
-### Participants 
-A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
-This was a new set of participants unrelated to those taking part in Experiment 1.
-The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
-Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
-
-### Procedure
-
-The participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
-The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
-The first two games were identical to the ones used in the first experiment.
-In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper.
-Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
-If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
-Otherwise, the goalkeeper catches the ball and the player loses the round.
-There is no possibility of ties in this game.
-Figure XXXXXXXXX shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
-A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
-As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
-
-Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
-Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
-Participants start by facing one of the opponents in stage one, then face the other in stage two.
-This is repeated in the same order in stages 3 and 4.
-Which opponent they faced first was counterbalanced.
-All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
-
-In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
-During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
-A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent.
-After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
-Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction.
-The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-
-Like games used in the first experiment, all the games used in this seeting have a unique MSNE consisting of randomising across actions.
-If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
-Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
-
-## Results
-
-```{r load_exp2_data , include=FALSE}
-dat_int <- read.csv(file = "../Experiment_2/dat_int_exp2.csv")
-```
-
-The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had the highest average score (M = 0.622, SD = 0.326).
-The higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
-Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value < 0.0001 ;  FWG:  t(49) = 7.25 , p-value < 0.0001 ; Shootout: t(49) = 13.61, p-value < 0.0001 ).
-
-Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
-We perform a two (condition: level-1 first, level-2 first) by two ( opponne type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
-
-```{r Anova exp 2, include= FALSE}
-exp2_anova <- afex::aov_car(
-  int_score ~ (game.f*interaction_lvl*condition.f*opp_type) + Error(human_id/(game.f*interaction_lvl*opp_type))
-  , data = dat_int
-  , type = 3
-)
-
-(ls0 <- lsmeans(exp2_anova, "game.f", by = "opp_type"))
-(ls0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
-apa_lm <- apa_print(exp2_anova)
-
-```
-
-```{r exp2-score-by-opp, fig.cap="Average scores per game by opponent type", fig.align="center"}
-# p3 <- ggerrorplot(dat_int, x = "game.f", y = "int_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Scores per game", xlab = "Games")
-# 
-# p3 + facet_grid(. ~ opp_type)
-
-p4 <- ggboxplot(dat_int, x = "game.f", y = "int_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","SHOOT"), fill="interaction_lvl",ylab = "Percentage score", xlab = "Games")
-
-p4 + facet_grid(. ~ opp_type)
-
-```
-
-```{r exp2-anova, results = "asis", echo=FALSE, warning=FALSE}
-# apa_table( apa_lm$table, caption = "ANOVA results for experiment 2", escape = FALSE)
-```
-
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, $\eta^{2}$ = 0.04,  p < .0001).
-To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
-We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the Shootout game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
-There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
-This means that neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
-There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,$\eta^{2}$ = 0.02,  p = .01).
-As can be seen in Figure\ \@ref(fig:exp2-score-by-opp), when facing level-1 agents, scores increase steadily after each game, with FWG score sgnificantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG  ( t(191) = 3.05, p = 0.01).
-There was no significant difference between average scores on any two games when facing level-2 agents however.
-
-### Learning transfer
-
-```{r , include=FALSE}
-dat <- read.csv(file = "../Experiment_2/dat_exp2.csv")
-```
-
-As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random.
-Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
-
-```{r, include = FALSE}
-
-#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########
-
-dat_26 <- subset(dat,(round >1 & round < 7) & (interaction_lvl == "first interaction" ), drop =TRUE)
-
-exp2_dat2_6 <- dat_26 %>% 
-  group_by(human_id,condition.f,game.f,opp_type,confidence,difficulty) %>% 
-      summarise(early_score = mean(adj_score))
-
-# Check group means and SDs
-group_by(exp2_dat2_6, game.f) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-group_by(exp2_dat2_6, game.f,opp_type) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-```
-
-```{r exp2-early-scores, fig.cap="Average early round scores by game for experiment 2", fig.align="center"}
-# plot scores per game 
-p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Score rounds 2-6", xlab = "Games")
-
-p2 + facet_grid(. ~ opp_type)
-```
-
-In Figure\ \@ref(fig:exp2-early-scores), we show the average score across participants in rounds 2-6 of the first interaction with the opponent for each game.
-These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
-For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
-(Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; Shootout:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; Shootout:  t(270) = 3.21, p =0.004 ).
-Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
-Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
-These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
-
-\newpage
-
-# Computational modelling
-
-To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent.
-As a base model, we assume play is random, and each potential action is chosen with equal probability.
-Note that this corresponds to the Nash equilibrium strategy.
-In this section, we will go through the various models we have used and explain how they update what they learn about the game or the opponent
-
-## Reinforcement Learning
-
-We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
-We will use a simple temporal difference learning update rule:
-
-$$ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) $$
-
-Where $V_{t}(a)$ is the value associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
-Actions are chosen based on action values using a softmax choice rule.
-
-We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm [@watkins1992q]. The update rule becomes:
-
-$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$
-
-Where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\gamma$ is the discount rate applied to future rewards.
-For instance, $Q(RS,P)$ denotes the value of taking action "Paper" this round if the player's last action was "Rock" and the opponent played "Scissors".
-This is a much richer model allowing the players to compute the values of actions conditional on past play.
-
-In experiment 2, we allow this richer model to have a memory of the interaction.
-In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used.
-In another instance, we fit a model in which what was learned about an opponent in the first interaction is transfered to the first round of the second interaction, so there is a within-game trasnfer of Q-values allowed (QLS-within).
-We fit both models to all participant's data in the second experiment where both opponents are faced.
-
-### EWA Models 
-Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics].
-EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning.
-Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
-In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
-The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
-
-Let's define some notation in order to write the update rule of the self-tuning EWA model.
-For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j).
-Strategies actually played by i in period t, are denoted $s_{i}(t)$, while the opponent's strategy at time t is denoted $s_{-i}(t)$.
-After playing  $s_{i}^{j}$ at time $t$, player i payoff is denoted $\pi_{i}(s_{i}^{j},s_{-i}(t))$, and the actual payoff the player received is $\pi_{i}(t)$.
-
-The EWA model is based on updating "Attractions" for each action over time.
-For instance, the attraction of strategy $j$ to player $i$ at time $t$ is written $A_{i}^{j}(t)$.
-Future action choice probabilities are based on these attractions using the softmax playing rule:
-
-$$P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} $$
-
-The attractions are updated over every time step $t$ using the followng update rule :
-
-$$ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} $$
-
-Here, I(x,y) is the indicator function equal to 1 if $ x = y$ and 0 otherwise.
-A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince ($N(t-1)$) which is itself decaying by a wight $\phi$.
-The result is added to either the payoff received (when the indicator function is 0), or to $\delta$ times the foregone payoff (when indicator function is 1).
-We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play [@cheung1994learning].
-While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].
-
-### ToM models
-
-In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
-We use values of k  in ${0,1,2}$.
-We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
-In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between trasnfer)
-
-Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
-In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
-
-We fit the above two models to experiment 1 data.
-In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive).
-And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
-
-In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).
-In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
-Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
-
-## Experiment 1 modelling :
-
-```{r load-comp-mod-distrib, include=FALSE}
-
-exp1_comp_results <- read.csv(file="../exp1_all_results.csv")
-exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])
-
- #write.csv(exp1_comp_table ,file="exp1_comp_table ",row.names = TRUE)
- kable(exp1_comp_table)
-```
-
-```{r exp1-cum-score-plots, include=FALSE}
-
-exp1_dat = read.csv("../exp1_data.csv")
-# exp1_model_comp = read.csv("../exp1_model_comp.csv")
-
-exp1_model_comp <- data.frame()
-for(id in unique(exp1_dat$human_id)) {
-  tdat <- subset(exp1_dat,human_id == id)
-  tot_score <- sum(tdat$score)
-  tot_time <- sum(tdat$human_rt)
-  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
-  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
-  tr_score <- sum(early_dat$score)
-  id_results <- subset(exp1_comp_results, ID == id)
-  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)
-
-  best_model <- c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
-  # 
-  exp1_model_comp <- rbind(exp1_model_comp,
-                       data.frame(
-                         "human_id" = id,
-                         "condition" = exp1_dat[exp1_dat$human_id==id,"condition"][1],
-                         "Early_game_score" = tr_score,
-                         "Total_score" = tot_score,
-                         "Best_model" = best_model,
-                         "Total_time" = sum(tdat$human_rt),
-                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
-                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
-
-                       ))
-}
-
-datalist = list()
-i = 0
-new_dat <- setNames(data.frame(matrix(ncol = ncol(exp1_dat), nrow = 0)), colnames(exp1_dat))
-for(id in unique(exp1_dat$human_id)) {
-  i <- i+1
-  tdat <- subset(exp1_dat,human_id == id)
-  tdat$part_num <- i
-  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
-  datalist[[i]] <- tdat
-}
-
-# Merge all datasets into one 
-new_dat <- dplyr::bind_rows(datalist)
-# or new_dat <- data.table::rbindlist(datalist)
-
-# Add column for time t
-new_dat <- new_dat %>% group_by(exp1_dat$human_id) %>% mutate(t = row_number())
-
-# Add best fitting model per participant
-new_dat <- merge(new_dat, exp1_model_comp[, c("human_id", "Best_model")], by="human_id")
-
-temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
-dat_by_model <- temp %>% group_by(Best_model,t) %>% 
-  summarize(model_acc_sum = mean(acc_sum))
-
-```
-
-Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
-
-```{r exp1-comp-models, fig.cap = "Experiment 1 - Histogram of best fitting computational models by condition", fig.align='center'}
-
-#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
-par(las=2) # make label text perpendicular to axis
-par(mar=c(5,8,4,2)) # increase y-axis margin.
-barplot(exp1_comp_table,
-        horiz =TRUE, # rotate barplot for better visibility 
-        las=1, # change orientation x axis labels 
-        cex.names=0.8, # text label size
-        legend = rownames(exp1_comp_table),
-        beside =TRUE,
-        xlab="Number of participants",
-        args.legend=list( # positioning of legend box 
-        x=ncol(exp1_comp_table) + 4,
-        y=max(colSums(exp1_comp_table)) + 4,
-        bty = "n")
- )
-
-```
-
-Next we compared the performance of players whose actions are best fit by each of our hypothesized models.
-Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (witout transfer), followed by Q-learning conditional on last round play.
-EWA, QL and random players had, understandably the lowest performance.
-
-```{r exp1-cumScores, fig.cap = "Experiment 1 - Average cumulative scores of participants by best fitting model", fig.align='center'}
-p5 <- ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
-   geom_line(aes(color= Best_model))
-
-p5 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
-```
-
-However, this is at odds with the findings from the previous section regarding learning transfer: If indeed most participants use Q-learning with states to choose their actions, then they should not be able to transfer learning to the early rounds of the new game.
-In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Theory of Mind models with and without the possibility of across game transfer.
-
-Figure\ \@ref(fig:exp1-lik-by-tr) shows that in the later games, the likelihood for the ToM models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of ToM models.
-
-```{r, include= FALSE}
-
-exp1_lik_by_trial  <- read.csv("../exp1_lik_by_trial.csv")
-
-mean_lik <- exp1_lik_by_trial %>%
-  dplyr::select(human_id,condition,game, round, QLS_lik, Bayes_NT_lik, Bayes_Tr_lik) %>%
-  group_by(condition,game,round) %>%
-  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
-            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
-            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
-
-mean_lik$game <- factor(mean_lik$game,levels=c("rps","fwg","numbers"))
-
-data_long <- gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
-
-```
-
-```{r exp1-lik-by-tr, fig.cap = "Experiment 1 Likelihood by trial by game and opponent faced", fig.align='center'}
-# make sure the different games are ordered in the way they were played
-# data_long$game <- factor(data_long$game,levels=c("rps","fwg","numbers"))
-ggplot(data_long,aes(x=round,y=probability,colour=strategy)) +
-  geom_line() +
-  facet_grid(game~condition)
-
-```
-
-## Experiment 2
-
-```{r, include = FALSE}
-
-exp2_comp_results <- read.csv(file="../Experiment_2/exp2_results.csv")
-# exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
-
-exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
-
- # write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
- kable(exp2_comp_table)
-```
-
-```{r exp2-comp-models, fig.cap = "Experiment 2 Histogram of best fitting computational models by condition", fig.align='center'}
-
-par(las=2) # make label text perpendicular to axis
-par(mar=c(5,8,4,2)) # increase y-axis margin.
-barplot(exp2_comp_table,
-        horiz =TRUE, # rotate barplot for better visibility 
-        las=1, # change orientation x axis labels 
-        cex.names=0.8, # text label size
-        beside =TRUE,
-        xlab="Number of participants",
-        # legend = c("level-1 opp first","level-2 opp first"),
-        legend = paste0(rownames(exp2_comp_table) , " faced first"),
-        args.legend=list( # positioning of legend box 
-        x=ncol(exp2_comp_table) + 6,
-        y=max(colSums(exp2_comp_table)) +1,
-        bty = "n")
- )
-
-```
-
-In experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that Q-learning with the aforementioned state-space was again more successful than the bayesian models in fitting player's action choices.
-In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) did not fit players observed data as well.
-
-```{r, include=FALSE}
-
-dat_exp2 = read.csv("../Experiment_2/data_exp2.csv")
-
-#Adjust shootout score tor eflect easier game
-dat_exp2$adj_score <- ifelse(as.character(dat_exp2$game) == "shootout", dat_exp2$score - 0.333, dat_exp2$score)
-
-# Load data comparing models BIC for each participant 
-model_comp_2 = read.csv("../Experiment_2/exp2_model_comp.csv")
-
-datalist2 = list()
-i = 0
-
-#Build empty dataframe with same names as original data
-exp2_cum_score <- setNames(data.frame(matrix(ncol = ncol(dat_exp2), nrow = 0)), colnames(dat_exp2))
-for(id in unique(dat_exp2$human_id)) {
-  i <- i+1
-  tdat <- subset(dat_exp2,human_id == id)
-  tdat$part_num <- i
-  # NB : USE ADJUSTED SCORE IN SHOOTOUT
-  tdat <- within(tdat, acc_sum <- cumsum(tdat$adj_score))
-  datalist2[[i]] <- tdat
-}
-
-# Merge all datasets into one 
-exp2_cum_score <- dplyr::bind_rows(datalist2)
-# or exp2_cum_score <- data.table::rbindlist(datalist)
-
-# Add column for time t
-exp2_cum_score <- exp2_cum_score %>% group_by(human_id) %>% mutate(t = row_number())
-
-# Participant number as a factor 
-# tdat$part_num <- as.factor(tdat$part_num)
-
-# Add best fitting model per participant
-exp2_cum_score <- merge(exp2_cum_score, model_comp_2[, c("human_id", "Best_model_2")], by="human_id")
-
-temp2 <- exp2_cum_score[,c("t","acc_sum","Best_model_2","condition","part_num")]
-dat_by_model_2 <- temp2 %>% group_by(Best_model_2,t) %>% 
-  summarize(avg_acc_sum = mean(acc_sum))
-
-```
-
-```{r exp2-cumScores, fig.cap = "Experiment 2 Average cumulative scores of participants by best fitting model", fig.align='center'}
-
- p8 <- ggplot(data = dat_by_model_2, aes(x = t, y=avg_acc_sum, group = Best_model_2)) + 
-   geom_line(aes(color= Best_model_2)) +
-  scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))
-
-p8 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
-
-```
-
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
-Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance (although it only fit 2 participants best), followed by a model in which both within and between trasnfer of opponent models is allowed (BT).
-The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive).
-As expected, random play was at the bottom of cumulative performance.
-
-As in experiment 1, we want to understand the dynamic of strategy choice by plotting the likelihood by trial for each strategy, using the optimal parameters found when fitting the model.
-Figure\ \@ref(fig:exp2-lik-by-tr) shows that, as in experiment 1, ToM models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
-In the third and mosre dissimilar game, we get a result that is different from experiment 1.
-In this instance, the likelihoods of the ToM models stay constant and close to their initial values.
-
-```{r, include = FALSE }
-
-exp2_lik_by_trial <- read.csv("../Experiment_2/exp2_lik_by_trial.csv")
-
-mean_lik_2 <- exp2_lik_by_trial %>%
-  dplyr::select(human_id,game,stage,round_condition, round, QLS_lik, QLS_lik_within, Bayes_NT_lik, Bayes_Tr_lik) %>%
-  group_by(game,stage,round) %>%
-  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
-            mean_QLS_within_lik = mean(QLS_lik_within, na.rm = TRUE),
-            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
-            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
-
-mean_lik_2$game <- factor(mean_lik_2$game,levels=c("rps","fwg","shootout"))
-
-data_long2 <- gather(mean_lik_2, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
-```
-
-```{r exp2-lik-by-tr, fig.cap = "Experiment2 likelihood by trial by game and opponent faced", fig.align ='center'}
-# make sure the different games are ordered in the way they were played
-# data_long2$game <- factor(data_long$game,levels=c("rps","fwg","shootout"))
-ggplot(data_long2,aes(x=round,y=probability,colour=strategy)) +
-  geom_line() +
-  facet_grid(game~stage)
-
-```
-
-## Using Hidden Markov Model to explore strategy switching
-
-The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative of participants switching between strategies as the games progressed.
-Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the ToM based strategies fit observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
-
-In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q learning with state space consisting of previous round play, ToM based model with and without opponent model transfer).
-Hidden Markov models are useful tools to explore structure in observed time series.
-They are named because of two properties: First, they make the assumption that any observable action at time t results from a process whose state at time t , named $S_{t}$ is "hidden" from the observer.
-Second, it also assumes that this hidden process has a Markov property, meaning that given state $S_{t-1}$, the value of $S_{t}$ is independent of all states occuring before time $t-1$.
-We also assume that $S_{t}$ has a discrete probability distribution in that it take one of K discrete values.
-The model is therefore specified by initial probabilities of being in each state ${1,2,...,K}$ and transition probabilities for moving from state $i$ to state $j$.
-These probabilities are fit using obsserved actiosn generated from these hidden states.
-
-Using the R DepmixS4 package, we fit a total of two HMMs.
-In the first model, we allow for a non-nil probability of players transitioning from one state (strategy) to another.
-In the second model, we assume that such switching does not happen, and as such assume implicitly that when players start with a particular strategy, they continue using it throughout the game.
-We then compare the likleihoods of each HMM model using a likelihood ration test.
-In experiment 1, the HMM model with swithcing has a significantly higher likelihood than the non-swithcing one (p-value = 0.00).
-The switching model in experiment two has also significantly higher likelihood (p-value = 0.00).
-On top of indications from looking at the liklihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
-
-\newpage
-
-# Discussion
-
-In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies.
-We were interested in uncovering evidence for transfer and exploring whether it is modulated by the degree of similarity between games and the sophistication of the agent.
-
-The results of our first online experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
-We found that using results on very early rounds is a better proxy for measuring transfer as it is not tainted by any within game learning.
-Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
-
-In the second online experiment, the paradigm was better suited to explore our main research question, related to learning transfer rather than within-game learning.
-Indeed, when facing two opponents sequentially, there are many more opportunities to test transfer than before.
-Indeed, there are 2 opportunities to transfer knowledge within each game, and a total of three games, which means 6 opportunities to test transfer.
-When we made players face only one type of opponent each, we only had two possible learning transfers to test.
-In that regard, the results on learning transfer confirmed prior findings from the first experiment.
-While there was no evidence of learning transfer across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
-We also found that learning transfer is modulated by the type of opponent faced.
-When the players faced the level-1 opponent, they were able to transfer learning.
-However, when they faced the level-2 opponent, there was weaker evidence for transfer.
-The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with.
-A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
-
-Coming back to evidence for learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
-The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
-what did the players learn exactly about the opponent strategy and what form did this learning take?
-
-We will proceed by considering multiple potential answers to this question.
-First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
-An example is a spatial heuristic that consists of choosing "weapons" in a particular order (for instance left to right).
-This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
-We took this into account in designing experiment two by randomly shuffling the spatial order of action choices in each round.
-Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.
-
-A second possible hypothesis for learning the opponent’s strategy is the use of simple rules based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
-Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
-While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
-Indeed, learning the best action in a particular state cannot easily transfer to a new game since the state space is different and there is no simgle mapping between the state spaces of the initial and latter games.
-These rules would thereofre need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
-
-Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, would require many rounds of practice.
-Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
-After all, if players were using some type of associative learning or spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
-The fact that the degree of sophisitication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
-
-We are left with two possible explanations: First, it is possible that the players have uncovered a heuristic that allows them to beat the opponent without explicitly modelling their strategy, and is robust to transfer.
-Indeed, because of the cyclicality in action choices (e.g : Rock beats Scissors beats Paper beats Rock), it is possible to beat level-2 opponents most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
-This is a rule that wins and is also robust to transfer as it does not depend on action labels and even works in the dissimilar game.
-
-The second explanation of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
-A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
-For instance, the player may think “My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be”.
-This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
-This type of learning would be deemed “explicit” in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
-It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
-Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
-
-Our second experimental design allows us to test whether the first explanation holds.
-Since there is a simple transferable heuristic that works agaisnt level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
-Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.
-
-Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first intractions across games and using early rounds analysis.
-Based on our assumptions, we conclude that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the ourse of learning.
-
-\newpage
-
-# Conclusion
-
-Our online experiments confirm behavioural game theory results, stating that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
-Moreover, we showed that participants do transfer their learning to new games with varying degrees of similarity.
-The most likely explanation as we saw is that players build a mental representation of their opponent strategy, rather than rely on associative learning or action-based heuristics.
-The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.
-
-Having said that, there remains a high degree of heterogeneity between players.
-There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
-Moreover, the computational modelling shows that a significant number of players are still using random strategies in the games.
-Whether this ability depends on engagement with the experiment or on other characteristics of the learner is an open question that more research in the area would hope to answer.
-
-\newpage
-
 # References

### 2020-10-30 Report/brouillon.tex
draft3

--- 2020-09-04 Report/draft_report_v1.tex
@@
 \hypersetup{
-            pdftitle={Transfer of Learned Opponent Models in Zero Sum Games},
+            pdftitle={brouillon},
             pdfauthor={Ismail Guennouni~\& Maarten Speekenbrink},
@@
 
-\shorttitle{Draft-1}
+\shorttitle{Draft-3}
 \affiliation{
@@
 
-\title{Transfer of Learned Opponent Models in Zero Sum Games}
+\title{brouillon}
 \author{Ismail Guennouni\textsuperscript{1}~\& Maarten Speekenbrink\textsuperscript{1}}
@@
 Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-Lake, Ullman, Tenenbaum, \& Gershman (2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
+(Lake, Ullman, Tenenbaum, \& Gershman, 2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 
-Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
-A notable exception is the effort by Haruvy \& Stahl (2012) to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
-Participants played ten games, presented as 4x4 normal form (matrix payoffs).
-Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
-They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on Stahl \& Wilson (1995), was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
-
-Still, one of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-The strategies implemented by the computer opponents had a style of play that was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that \enquote{play like humans}, and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
-Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
-Instead, they will try to \enquote{satisfice} by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in \enquote{level-k} theory, first adopted by Stahl \& Wilson (1995).
-It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment Arad \& Rubinstein (2012).
-Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
-Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below, and so on.
-
-In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit Goodie, Doshi, \& Young (2012).
-
-Our choice of using computer oponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-When playing against other human opponents, players are learning about the game and the strategy of the opponent simultaneously.
-Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
-The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
-For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
-Shachat \& Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
-
-We chose to use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
-We avoid social dilemma and coordination games that crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
-Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
-Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
-As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transferred.
-By contrast, purely competitive settings and zero sum games in particular would be more appropriate.
-They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building.
-Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learning.
-Games with unique mixed strategy Nash equilibrium leading to nil average rewards facilitate inferring whether participants have learned to exploit the non-random play of the opponent.
-
-We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
-The first two games we use are identical except for action labels.
-In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with a fixed expected reward against a Nash player.
-
-Hence, we ran a total of two experiments where human participants played 3 different games against either 1 (first experiment ) or 2 (second experiment) computer opponents.
-In the following sections, we will describe each experiment's methodology and results separately, then discuss the findings before using computational modelling to shed light on some of the results.
-
-\newpage
-
-\hypertarget{experiment-1}{%
-\section{Experiment 1}\label{experiment-1}}
-
-\hypertarget{methods}{%
-\subsection{Methods}\label{methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
-The mean age of participants was 31.2 years.
-Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-In the first experiment, participants played 3 games sequentially against the same computer opponent.
-The computer opponent either used a level-1 or level-2 strategy.
-The three games were rock-paper-scissors, fire-water-grass and the numbers game.
-A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
-If one player choses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
-Otherwise it is a draw and both players receive a reward of 0.
-It has a unique MSNE consisting of randomly playing one of the three options each time.
-
-The second game is identical to Rock-Paper-Scissors in all but action labels.
-We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
-We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
-Finally, the numbers game is a generalization of rock-paper-scissors.
-In the variant we use, 2 participants concurrently pick a number between 1 and 5.
-To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent.
-For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
-To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
-This game has a structure similar to RPS in which every action is dominated by exactly one choice.
-All other possible combination of choices that are not consecutive are considered ties.
-A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score.
-Similar to RPS, the MSNE is to play each action with equal probability in a random way.
-
-Participants were informed they would play three different games against the same computer opponent.
-Each participant plays all three games consecutively and in the same order described above.
-Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
-A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
-The score was calculated as the number of wins minus the number of losses.
-Ties did not affect the score.
-In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-The overall score of the players was translated into the bonus by making each point worth £0.02.
-This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they'd won all rounds against the computer opponent.
-An example of the interface for the rock-paper-scissors game is provided in Figure~\ref{fig:feedback-rps}.
-
-\begin{figure}
-
-{\centering \includegraphics{images/feedback_rps}
-
-}
-
-\caption{Screenshot of the feedback at the end of a round of Rock-Paper-Scissors}\label{fig:feedback-rps}
-\end{figure}
-
-\hypertarget{results}{%
-\subsection{Results}\label{results}}
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-avg-scores-game-1}
-
-}
-
-\caption{Average scores per game across conditions}\label{fig:exp1-avg-scores-game}
-\end{figure}
-
-Looking at the aggregate scores (See Figure~\ref{fig:exp1-avg-scores-game} ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
-Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value \textless{} 0.001 ; FWG: t(51) = 10.04 , p-value \textless{} 0.001 ; NUMBERS: t(51) = 7.17, p-value \textless{} 0.001).
-
-To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game ( F(2,100) = 8.54, \(\eta^{2}\) = 0.05, p \textless{} 0.001), showing that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
-The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
-The main effect of Block ( F(1,50) = 22.51 , p \textless{} .001, \(\eta^{2}\) = 0.03) shows that the average score in the first half of games (M = 0.29) was significantly lower than in the second half of the games played (M = 0.40), which translates to within-game learning.
-As players interact more with the agent, they learn how to win more often.
-The main effect of Condition (F(1,50) = 5.44, p = .024, \(\eta^{2}\) = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
-This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-3factor-plot-1}
-
-}
-
-\caption{Average scores by game, block and condition}\label{fig:exp1-3factor-plot}
-\end{figure}
-
-Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, \(\eta^{2}\) = 0.02), indicating that within-game learning differed between the games.
-Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p \textless{}.0001), while there was no significant difference between block scores for the other two games.
-This is indicative of the significant within game transfer within the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
-There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, \(\eta^{2}\) = 0.01), which indicates, as seen in Figure~\ref{fig:exp1-3factor-plot} that within-game learning changes across games also depend on the sophistication of the opponent.
-For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than agaisnt level-1 opponent.
-The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
-
-\hypertarget{learning-transfer}{%
-\subsubsection{Learning transfer}\label{learning-transfer}}
-
-As a measure for learning transfer, we focus on participants' scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
-A group of players with no experience of the game are expected to have scores not significantly different from 0.
-Any significantly positive group average scores would therefore reflect prior learning from past experiences.
-
-We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
-As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
-In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p \textless{} 0.0001).
-This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
-
-Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-Figure~@ref(fig: exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players.
-Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
-To test these hypotheses, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-score-by-opp-1}
-
-}
-
-\caption{Average early scores by game and type of opponent faced}\label{fig:exp1-score-by-opp}
-\end{figure}
-
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p \textless{} 0.001) and NUMBERS (t(150) = 3.74, p \textless{} 0.001) .
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
-
-Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game.
-Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
-
-\newpage
-
-\hypertarget{second-experiment}{%
-\section{Second Experiment}\label{second-experiment}}
-
-\hypertarget{methods-1}{%
-\subsection{Methods}\label{methods-1}}
-
-\hypertarget{participants-1}{%
-\subsubsection{Participants}\label{participants-1}}
-
-A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
-This was a new set of participants unrelated to those taking part in Experiment 1.
-The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
-Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
-
-\hypertarget{procedure-1}{%
-\subsubsection{Procedure}\label{procedure-1}}
-
-The participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
-The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
-The first two games were identical to the ones used in the first experiment.
-In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper.
-Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
-If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
-Otherwise, the goalkeeper catches the ball and the player loses the round.
-There is no possibility of ties in this game.
-Figure XXXXXXXXX shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose \enquote{'right}' in the next round, we can win by both choosing \enquote{'left}' and \enquote{'center}'.
-A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
-As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
-
-Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
-Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
-Participants start by facing one of the opponents in stage one, then face the other in stage two.
-This is repeated in the same order in stages 3 and 4.
-Which opponent they faced first was counterbalanced.
-All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
-
-In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
-During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
-A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent.
-After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
-Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction.
-The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-
-Like games used in the first experiment, all the games used in this seeting have a unique MSNE consisting of randomising across actions.
-If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
-Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
-
-\hypertarget{results-1}{%
-\subsection{Results}\label{results-1}}
-
-The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had the highest average score (M = 0.622, SD = 0.326).
-The higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
-Indeed, a player not aiming to uncover the opponent's strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value \textless{} 0.0001 ; FWG: t(49) = 7.25 , p-value \textless{} 0.0001 ; Shootout: t(49) = 13.61, p-value \textless{} 0.0001 ).
-
-Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
-We perform a two (condition: level-1 first, level-2 first) by two ( opponne type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-score-by-opp-1}
-
-}
-
-\caption{Average scores per game by opponent type}\label{fig:exp2-score-by-opp}
-\end{figure}
-
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, \(\eta^{2}\) = 0.04, p \textless{} .0001).
-To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
-We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the Shootout game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
-There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
-This means that neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
-There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,\(\eta^{2}\) = 0.02, p = .01).
-As can be seen in Figure~\ref{fig:exp2-score-by-opp}, when facing level-1 agents, scores increase steadily after each game, with FWG score sgnificantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG ( t(191) = 3.05, p = 0.01).
-There was no significant difference between average scores on any two games when facing level-2 agents however.
-
-\hypertarget{learning-transfer-1}{%
-\subsubsection{Learning transfer}\label{learning-transfer-1}}
-
-As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random.
-Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-early-scores-1}
-
-}
-
-\caption{Average early round scores by game for experiment 2}\label{fig:exp2-early-scores}
-\end{figure}
-
-In Figure~\ref{fig:exp2-early-scores}, we show the average score across participants in rounds 2-6 of the first interaction with the opponent for each game.
-These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
-For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
-(Level-1 opponent: FWG: t(270) = 4.99, p \textless{} 0.0001; Shootout: t(270) = 6.66, p \textless{} 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p \textless{} 0.0001; Shootout: t(270) = 3.21, p =0.004 ).
-Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
-Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
-These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
-
-\newpage
-
-\hypertarget{computational-modelling}{%
-\section{Computational modelling}\label{computational-modelling}}
-
-To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent.
-As a base model, we assume play is random, and each potential action is chosen with equal probability.
-Note that this corresponds to the Nash equilibrium strategy.
-In this section, we will go through the various models we have used and explain how they update what they learn about the game or the opponent
-
-\hypertarget{reinforcement-learning}{%
-\subsection{Reinforcement Learning}\label{reinforcement-learning}}
-
-We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
-We will use a simple temporal difference learning update rule:
-
-\[ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) \]
-
-Where \(V_{t}(a)\) is the value associated with action \(a\) at time \(t\), \(\alpha\) is the learning rate and \(R_{t}\) the reward at time t.
-Actions are chosen based on action values using a softmax choice rule.
-
-We extend this very simple model by adding a state space that consists of last round human and agent play.
-This is akin to using a Q-learning algorithm (Watkins \& Dayan, 1992).
-The update rule becomes:
-
-\[ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) \]
-
-Where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), \(\gamma\) is the discount rate applied to future rewards.
-For instance, \(Q(RS,P)\) denotes the value of taking action \enquote{Paper} this round if the player's last action was \enquote{Rock} and the opponent played \enquote{Scissors}.
-This is a much richer model allowing the players to compute the values of actions conditional on past play.
-
-In experiment 2, we allow this richer model to have a memory of the interaction.
-In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used.
-In another instance, we fit a model in which what was learned about an opponent in the first interaction is transfered to the first round of the second interaction, so there is a within-game trasnfer of Q-values allowed (QLS-within).
-We fit both models to all participant's data in the second experiment where both opponents are faced.
-
-\hypertarget{ewa-models}{%
-\subsubsection{EWA Models}\label{ewa-models}}
-
-Next, we use a self-tuning Experience Weighted attraction model (Ho, Camerer, \& Chong, 2004).
-EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning.
-Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
-In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
-The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
-
-Let's define some notation in order to write the update rule of the self-tuning EWA model.
-For player i, there are \(m_{i}\) strategies, denoted \(s_{i}^{j}\) (i.e player i's strategy number j).
-Strategies actually played by i in period t, are denoted \(s_{i}(t)\), while the opponent's strategy at time t is denoted \(s_{-i}(t)\).
-After playing \(s_{i}^{j}\) at time \(t\), player i payoff is denoted \(\pi_{i}(s_{i}^{j},s_{-i}(t))\), and the actual payoff the player received is \(\pi_{i}(t)\).
-
-The EWA model is based on updating \enquote{Attractions} for each action over time.
-For instance, the attraction of strategy \(j\) to player \(i\) at time \(t\) is written \(A_{i}^{j}(t)\).
-Future action choice probabilities are based on these attractions using the softmax playing rule:
-
-\[P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} \]
-
-The attractions are updated over every time step \(t\) using the followng update rule :
-
-\[ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} \]
-
-Here, I(x,y) is the indicator function equal to 1 if \$ x = y\$ and 0 otherwise.
-A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince (\(N(t-1)\)) which is itself decaying by a wight \(\phi\).
-The result is added to either the payoff received (when the indicator function is 0), or to \(\delta\) times the foregone payoff (when indicator function is 1).
-We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play (Cheung \& Friedman, 1994).
-While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Ho et al., 2004).
-
-\hypertarget{tom-models}{%
-\subsubsection{ToM models}\label{tom-models}}
-
-In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
-We use values of k in \({0,1,2}\).
-We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
-In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between trasnfer)
-
-Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
-In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
-
-We fit the above two models to experiment 1 data.
-In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive).
-And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
-
-In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).
-In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
-Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
-
-\hypertarget{experiment-1-modelling}{%
-\subsection{Experiment 1 modelling :}\label{experiment-1-modelling}}
-
-Figure~\ref{fig:exp1-comp-models} shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-comp-models-1}
-
-}
-
-\caption{Histogram of best fitting computational models by condition for experiment 1}\label{fig:exp1-comp-models}
-\end{figure}
-
-Next we compared the performance of players whose actions are best fit by each of our hypothesized models.
-Figure~\ref{fig:exp1-cumScores} shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (witout transfer), followed by Q-learning conditional on last round play.
-EWA, QL and random players had, understandably the lowest performance.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-cumScores-1}
-
-}
-
-\caption{Average cumulative scores of participants in experiment 1 by best fitting model}\label{fig:exp1-cumScores}
-\end{figure}
-
-\hypertarget{experiment-2}{%
-\subsection{Experiment 2}\label{experiment-2}}
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-comp-models-1}
-
-}
-
-\caption{Histogram of best fitting computational models by condition for experiment 2}\label{fig:exp2-comp-models}
-\end{figure}
-
-In experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that Q-learning with the aforementioned state-space was again more successful than the bayesian models in fitting player's action choices.
-In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) did not fit players observed data as well.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-cumScores-1}
-
-}
-
-\caption{Average cumulative scores of participants in experiment 2 by best fitting model}\label{fig:exp2-cumScores}
-\end{figure}
-
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
-Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance, folowed by a model in which both within and between trasnfer of opponent models is allowed (BT).
-The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive).
-As expected, random play as well as self-tuning EWA were at the bottom of cumulative performance.
-
-\newpage
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies.
-We were interested in uncovering evidence for transfer and exploring whether it is modulated by the degree of similarity between games and the sophistication of the agent.
-
-The results of our first online experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
-We found that using results on very early rounds is a better proxy for measuring transfer as it is not tainted by any within game learning.
-Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
-
-In the second online experiment, the paradigm was better suited to explore our main research question, related to learning transfer rather than within-game learning.
-Indeed, when facing two opponents sequentially, there are many more opportunities to test transfer than before.
-Indeed, there are 2 opportunities to transfer knowledge within each game, and a total of three games, which means 6 opportunities to test transfer.
-When we made players face only one type of opponent each, we only had two possible learning transfers to test.
-In that regard, the results on learning transfer confirmed prior findings from the first experiment.
-While there was no evidence of learning transfer across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
-We also found that learning transfer is modulated by the type of opponent faced.
-When the players faced the level-1 opponent, they were able to transfer learning.
-However, when they faced the level-2 opponent, there was weaker evidence for transfer.
-The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with.
-A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
-
-Coming back to evidence for learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
-The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
-what did the players learn exactly about the opponent strategy and what form did this learning take?
-
-We will proceed by considering multiple potential answers to this question.
-First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
-An example is a spatial heuristic that consists of choosing \enquote{weapons} in a particular order (for instance left to right).
-This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
-We took this into account in designing experiment two by randomly shuffling the spatial order of action choices in each round.
-Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.
-
-A second possible hypothesis for learning the opponent's strategy is the use of simple rules based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc\ldots{}).
-Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
-While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
-Indeed, learning the best action in a particular state cannot easily transfer to a new game since the state space is different and there is no simgle mapping between the state spaces of the initial and latter games.
-These rules would thereofre need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
-
-Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, would require many rounds of practice.
-Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
-After all, if players were using some type of associative learning or spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
-The fact that the degree of sophisitication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
-
-We are left with two possible explanations: First, it is possible that the players have uncovered a heuristic that allows them to beat the opponent without explicitly modelling their strategy, and is robust to transfer.
-Indeed, because of the cyclicality in action choices (e.g : Rock beats Scissors beats Paper beats Rock), it is possible to beat level-2 opponents most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
-This is a rule that wins and is also robust to transfer as it does not depend on action labels and even works in the dissimilar game.
-
-The second explanation of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
-A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
-For instance, the player may think \enquote{My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be}.
-This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
-This type of learning would be deemed \enquote{explicit} in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
-It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
-Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
-
-Our second experimental design allows us to test whether the first explanation holds.
-Since there is a simple transferable heuristic that works agaisnt level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
-Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.
-
-Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first intractions across games and using early rounds analysis.
-Based on our assumptions, we conclude that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the ourse of learning.
-
-\newpage
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-Our online experiments confirm behavioural game theory results, stating that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
-Moreover, we showed that participants do transfer their learning to new games with varying degrees of similarity.
-The most likely explanation as we saw is that players build a mental representation of their opponent strategy, rather than rely on associative learning or action-based heuristics.
-The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.
-
-Having said that, there remains a high degree of heterogeneity between players.
-There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
-Moreover, the computational modelling shows that a significant number of players are still using random strategies in the games.
-Whether this ability depends on engagement with the experiment or on other characteristics of the learner is an open question that more research in the area would hope to answer.
-
-\newpage
-
 \hypertarget{references}{%
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-arad201211}{}%
-Arad, A., \& Rubinstein, A. (2012). The 11-20 money request game: A level-k reasoning study. \emph{American Economic Review}, \emph{102}(7), 3561--3573.
+\leavevmode\hypertarget{ref-baarslag2016learning}{}%
+Baarslag, T., Hendrikx, M.
+J.
+C., Hindriks, K.
+V., \& Jonker, C.
+M.
+(2016).
+Learning about the opponent in automated bilateral negotiation: a comprehensive survey of opponent modeling techniques.
+\emph{Autonomous Agents and Multi-Agent Systems}, \emph{30}(5), 849--898.
+
+\leavevmode\hypertarget{ref-cooper2003lessons}{}%
+Cooper, D. J., \& Kagel, J. H. (2003). Lessons learned: generalizing learning across games. \emph{American Economic Review}, \emph{93}(2), 202--207.
+
+\leavevmode\hypertarget{ref-Cooper2008}{}%
+Cooper, D. J., \& Kagel, J. H. (2008). Learning and transfer in signaling games. \emph{Economic Theory}, \emph{34}(3), 415--439. \url{https://doi.org/10.1007/s00199-006-0192-5}
+
+\leavevmode\hypertarget{ref-ho1998iterated}{}%
+Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
+
+\leavevmode\hypertarget{ref-Juvina2013}{}%
+Juvina, I., Saleem, M., Martin, J.
+M., Gonzalez, C., \& Lebiere, C.
+(2013).
+Reciprocal trust mediates deep transfer of learning between games of strategic interaction.
+\emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215.
+\url{https://doi.org/10.1016/j.obhdp.2012.09.004}
+
+\leavevmode\hypertarget{ref-Lake2017}{}%
+Lake, B.
+M., Ullman, T.
+D., Tenenbaum, J.
+B., \& Gershman, S.
+J.
+(2017).
+Building machines that learn and think like people.
+\emph{Behavioral and Brain Sciences}, \emph{40}.
+\url{https://doi.org/10.1017/S0140525X16001837}
+
+\leavevmode\hypertarget{ref-mertens1990repeated}{}%
+Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+
+\leavevmode\hypertarget{ref-stahl1995players}{}%
+Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
+
+\leavevmode\hypertarget{ref-de2012higher}{}%
+Weerd, H.
+de, Verbrugge, R., \& Verheij, B.
+(2012).
+Higher-order social cognition in rock-paper-scissors: A simulation study.
+\emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3}, 1195--1196.
+
+\leavevmode\hypertarget{ref-Woodruff}{}%
+Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). \emph{Does the chimpanzee have a theory of mind}.
 
@@
 
-\leavevmode\hypertarget{ref-camerer1997experience}{}%
-Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
-
-\leavevmode\hypertarget{ref-cheung1994learning}{}%
-Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
-
 \leavevmode\hypertarget{ref-cooper2003lessons}{}%
@@
 \leavevmode\hypertarget{ref-Cooper2008}{}%
-Cooper, D.
-J., \& Kagel, J.
-H.
-(2008).
-Learning and transfer in signaling games.
-\emph{Economic Theory}, \emph{34}(3), 415--439.
-doi:\href{https://doi.org/10.1007/s00199-006-0192-5}{10.1007/s00199-006-0192-5}
-
-\leavevmode\hypertarget{ref-goodie2012levels}{}%
-Goodie, A. S., Doshi, P., \& Young, D. L. (2012). Levels of theory-of-mind reasoning in competitive games. \emph{Journal of Behavioral Decision Making}, \emph{25}(1), 95--108.
-
-\leavevmode\hypertarget{ref-Haruvy2012}{}%
-Haruvy, E., \& Stahl, D.
-O.
-(2012).
-Between-game rule learning in dissimilar symmetric normal-form games.
-\emph{Games and Economic Behavior}, \emph{74}(1), 208--221.
-doi:\href{https://doi.org/10.1016/j.geb.2011.06.001}{10.1016/j.geb.2011.06.001}
-
-\leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). The economics of learning models: A self-tuning theory of learning in games.
+Cooper, D. J., \& Kagel, J. H. (2008). Learning and transfer in signaling games. \emph{Economic Theory}, \emph{34}(3), 415--439. \url{https://doi.org/10.1007/s00199-006-0192-5}
 
@@
 \emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215.
-doi:\href{https://doi.org/10.1016/j.obhdp.2012.09.004}{10.1016/j.obhdp.2012.09.004}
-
-\leavevmode\hypertarget{ref-knez2000increasing}{}%
-Knez, M., \& Camerer, C.
-(2000).
-Increasing cooperation in prisoner's dilemmas by establishing a precedent of efficiency in coordination games.
-\emph{Organizational Behavior and Human Decision Processes}, \emph{82}(2), 194--216.
+\url{https://doi.org/10.1016/j.obhdp.2012.09.004}
 
@@
 \emph{Behavioral and Brain Sciences}, \emph{40}.
-doi:\href{https://doi.org/10.1017/S0140525X16001837}{10.1017/S0140525X16001837}
+\url{https://doi.org/10.1017/S0140525X16001837}
 
@@
 
-\leavevmode\hypertarget{ref-shachat2004we}{}%
-Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
-
-\leavevmode\hypertarget{ref-simon1972theories}{}%
-Simon, H. A. (1972). Theories of bounded rationality. \emph{Decision and Organization}, \emph{1}(1), 161--176.
-
-\leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
-Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
-
 \leavevmode\hypertarget{ref-stahl1995players}{}%
 Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
-
-\leavevmode\hypertarget{ref-watkins1992q}{}%
-Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
 
@@
 Higher-order social cognition in rock-paper-scissors: A simulation study.
-In \emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3} (pp.
-1195--1196).
+\emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3}, 1195--1196.
 
 \leavevmode\hypertarget{ref-Woodruff}{}%
-Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). Does the chimpanzee have a theory of mind.
-
-\leavevmode\hypertarget{ref-arad201211}{}%
-Arad, A., \& Rubinstein, A. (2012). The 11-20 money request game: A level-k reasoning study. \emph{American Economic Review}, \emph{102}(7), 3561--3573.
-
-\leavevmode\hypertarget{ref-baarslag2016learning}{}%
-Baarslag, T., Hendrikx, M.
-J.
-C., Hindriks, K.
-V., \& Jonker, C.
-M.
-(2016).
-Learning about the opponent in automated bilateral negotiation: a comprehensive survey of opponent modeling techniques.
-\emph{Autonomous Agents and Multi-Agent Systems}, \emph{30}(5), 849--898.
-
-\leavevmode\hypertarget{ref-camerer1997experience}{}%
-Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
-
-\leavevmode\hypertarget{ref-cheung1994learning}{}%
-Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
-
-\leavevmode\hypertarget{ref-cooper2003lessons}{}%
-Cooper, D. J., \& Kagel, J. H. (2003). Lessons learned: generalizing learning across games. \emph{American Economic Review}, \emph{93}(2), 202--207.
-
-\leavevmode\hypertarget{ref-Cooper2008}{}%
-Cooper, D.
-J., \& Kagel, J.
-H.
-(2008).
-Learning and transfer in signaling games.
-\emph{Economic Theory}, \emph{34}(3), 415--439.
-doi:\href{https://doi.org/10.1007/s00199-006-0192-5}{10.1007/s00199-006-0192-5}
-
-\leavevmode\hypertarget{ref-goodie2012levels}{}%
-Goodie, A. S., Doshi, P., \& Young, D. L. (2012). Levels of theory-of-mind reasoning in competitive games. \emph{Journal of Behavioral Decision Making}, \emph{25}(1), 95--108.
-
-\leavevmode\hypertarget{ref-Haruvy2012}{}%
-Haruvy, E., \& Stahl, D.
-O.
-(2012).
-Between-game rule learning in dissimilar symmetric normal-form games.
-\emph{Games and Economic Behavior}, \emph{74}(1), 208--221.
-doi:\href{https://doi.org/10.1016/j.geb.2011.06.001}{10.1016/j.geb.2011.06.001}
-
-\leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). The economics of learning models: A self-tuning theory of learning in games.
-
-\leavevmode\hypertarget{ref-ho1998iterated}{}%
-Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
-
-\leavevmode\hypertarget{ref-Juvina2013}{}%
-Juvina, I., Saleem, M., Martin, J.
-M., Gonzalez, C., \& Lebiere, C.
-(2013).
-Reciprocal trust mediates deep transfer of learning between games of strategic interaction.
-\emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215.
-doi:\href{https://doi.org/10.1016/j.obhdp.2012.09.004}{10.1016/j.obhdp.2012.09.004}
-
-\leavevmode\hypertarget{ref-knez2000increasing}{}%
-Knez, M., \& Camerer, C.
-(2000).
-Increasing cooperation in prisoner's dilemmas by establishing a precedent of efficiency in coordination games.
-\emph{Organizational Behavior and Human Decision Processes}, \emph{82}(2), 194--216.
-
-\leavevmode\hypertarget{ref-Lake2017}{}%
-Lake, B.
-M., Ullman, T.
-D., Tenenbaum, J.
-B., \& Gershman, S.
-J.
-(2017).
-Building machines that learn and think like people.
-\emph{Behavioral and Brain Sciences}, \emph{40}.
-doi:\href{https://doi.org/10.1017/S0140525X16001837}{10.1017/S0140525X16001837}
-
-\leavevmode\hypertarget{ref-mertens1990repeated}{}%
-Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
-
-\leavevmode\hypertarget{ref-shachat2004we}{}%
-Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
-
-\leavevmode\hypertarget{ref-simon1972theories}{}%
-Simon, H. A. (1972). Theories of bounded rationality. \emph{Decision and Organization}, \emph{1}(1), 161--176.
-
-\leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
-Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
-
-\leavevmode\hypertarget{ref-stahl1995players}{}%
-Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
-
-\leavevmode\hypertarget{ref-watkins1992q}{}%
-Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
-
-\leavevmode\hypertarget{ref-de2012higher}{}%
-Weerd, H.
-de, Verbrugge, R., \& Verheij, B.
-(2012).
-Higher-order social cognition in rock-paper-scissors: A simulation study.
-In \emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3} (pp.
-1195--1196).
-
-\leavevmode\hypertarget{ref-Woodruff}{}%
-Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). Does the chimpanzee have a theory of mind.
+Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). \emph{Does the chimpanzee have a theory of mind}.
 

### 2020-10-30 Report/draft_report_v3.Rmd
draft3

--- 2020-10-30 Report/_main.Rmd
@@
 ---
-title             : "Learning to learn in a changing environment"
-shorttitle        : "Learning to learn"
-
-author: 
-  - name          : "Maarten Speekenbrink"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
-    email         : "m.speekenbrink@ucl.ac.uk"
-  - name          : "Akhat Rakishev"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Experimental Psychology, University College London"
-
-author_note: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
-abstract: |
-  Enter abstract here. Each new line herein must be indented, like this line.
-
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["r-references.bib"]
-
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : yes
-mask              : no
-
-class             : "man"
-output            : papaja::apa6_pdf
----
-
-```{r load-packages, include = FALSE}
-library("papaja")
-require(knitr)
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-```
-
-```{r texreport}
-texreport <- function(object,effect.name,...) UseMethod("texreport")
-texreport.default <- function(object,effect.name,...) return(NULL)
-
-texreport.summary.merMod <- function(object,effect.name,print.estimate=TRUE) {
-  if(effect.name %in% rownames(object$coefficients)) {
-    tab <- object$coefficients
-    estimate <- tab[effect.name,"Estimate"]
-    se <- tab[effect.name,"Std. Error"]
-    Tval <- tab[effect.name,"t value"]
-    df <- tab[effect.name,"df"]
-    pval <- tab[effect.name,"Pr(>|t|)"]
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$b = ",round(estimate,2),"$, $SE = ",round(se,2),"$, $t(",round(df,2),") = ",round(Tval,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-  } else {
-    txt <- "error"
-  }
-  txt
-}
-
-texreport.summary.Anova.mlm <- function(object,effect.name,effect.size=TRUE,sphericity.correction=TRUE) {
-  if(effect.name %in% rownames(object$sphericity.tests) && sphericity.correction && object$sphericity.test[effect.name,"p-value"] < .05) {
-    epsilon <- object$pval.adjustments[effect.name,"HF eps"]
-    pval <- object$pval.adjustments[effect.name,"Pr(>F[HF])"]
-  } else {
-    epsilon <- 1
-    pval <- object$univariate.tests[effect.name,"Pr(>F)"]
-  }
-  df1 <- object$univariate.tests[effect.name,"num Df"]*epsilon
-  df2 <- object$univariate.tests[effect.name,"den Df"]*epsilon
-  Fval <- object$univariate.tests[effect.name,"F"]
-  etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-  # generate latex output
-  if(pval < .001) ptext <- "$p < .001$" else {
-    if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-      ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-    }
-  }
-  txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-  if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-  txt <- paste(txt,ptext,sep="")
-  txt
-}
-
-texreport.linearHypothesis.mlm <- function(object,effect.size=TRUE) {
-  if(ncol(object$SSPH) == 1 & nrow(object$SSPH) == 1 & ncol(object$SSPE) == 1 & nrow(object$SSPE) == 1) {
-    df1 <- object$df
-    df2 <- object$df.residual
-    Fval <- (object$SSPH/df1)/(object$SSPE/df2)
-    pval <- 1-pf(Fval,object$df,object$df.residual)
-    etasq <- object$SSPH/(object$SSPH + object$SSPE)
-    # generate latex output
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-    if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-  } else {
-    txt <- "error"
-  }
-  txt
-}
-
-texreport.anova.lme <- function(object,effect.name,effect.size=FALSE) {
-  if(effect.name %in% rownames(object)) {
-    pval <- object[effect.name,"p-value"]
-    if(is.null(pval)) pval <- object[effect.name,"Pr(>F)"]
-    df1 <- object[effect.name,"numDF"]
-    df2 <- object[effect.name,"denDF"]
-    Fval <- object[effect.name,"F-value"]
-    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-    # generate latex output
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-    txt
-  }
-}
-
-texreport.anova <- function(object,effect.name,effect.size=FALSE) {
-  if(effect.name %in% rownames(object)) {
-    pval <- object[effect.name,"Pr(>F)"]
-    df1 <- object[effect.name,"NumDF"]
-    df2 <- object[effect.name,"DenDF"]
-    Fval <- object[effect.name,"F.value"]
-    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-    # generate latex output
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-    txt
-  }
-}
-
-```
-
-```{r read-data,warning=FALSE}
-source("R/readData.R")
-demo_exit <- read.csv("data/demographics_and_exit_clean.csv")
-trial_data <- read.csv("data/trial_data_clean.csv")
-trial_data$trial <- 1:100
-```
-
-# Introduction
-
-## Optimal learning
-
-If the volatility $\sigma_{\xi}(t)$ and noise $\sigma_\epsilon$ are know, optimal Bayesian learning is implemented by the Kalman filter
-$$\hat{\mu}_{t+1} = \hat{\mu}_t + k_t (y_t - \hat{\mu}_{t})$$
-where the "Kalman gain" is $$k_t = \frac{s_t + \sigma^2_{\xi}(t)}{s_t + \sigma^2_\xi(t) + \sigma^2_\epsilon}$$ and $s_t$ is the prior uncertainty about the mean $\mu_t$, computed recursively as $$s_t = (1-k_t)(s_{t-1} + \sigma^2_\xi(t))$$.
-Note that the updating of estimates $\hat{\mu}_t$ takes the same form as the well-known delta-rule, where each update is proportional to the prediction error ($y_t - \hat{\mu}_t$), with the proportionality constant $k_t$ is the learning rate, which is usually constant in the delta-rule, but time-varying in the Kalman filter and dependent on the prior uncertainty ($s_t$), and the level of volatility ($\sigma_\xi$) and environmental noise ($\sigma_\epsilon$).
-If both latter parameters are constant, then as $t \rightarrow \infty$, the Kalman gain converges to a constant and thus becomes equal to the constant-learning rate delta-rule.
-This is the steady-state Kalman filter, and provides a means to determine the optimal (constant) learning rate.
-The steady state is
-\begin{equation}k(t)^* = \frac{1}{2} \left(\sqrt{\frac{\sigma^4_\xi}{\sigma^4_\epsilon} + 4 \frac{\sigma^2_\xi}{\sigma^2_\epsilon}} - \frac{\sigma^2_\xi}{\sigma^2_\epsilon} \right)\end{equation}
-
-## A particle filter
-
-When the parameters are unknown, the optimal learning rule becomes intractible.
-Bayesian scheme's for estimating the parameters on-line need to rely on approximations, such as Monte Carlo Markov Chain estimation, which are impractible for on-line estimation, as for each time point, estimation would have to be started fresh.
-When the parameters are time-varying,
-
-# Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
-
-## Participants and design
-
-One hundred participants (`r  sum(dat$gender[dat$trial == 1] == "Female",na.rm=TRUE)` females, `r  sum(dat$gender[dat$trial == 1] == "Male",na.rm=TRUE)` males, `r sum(is.na(dat$gender[dat$trial == 1]))` other or preferred not to say), aged between `r min(dat$age)` and `r max(dat$age)` ($M = `r round(mean(dat$age[dat$trial==1]),2)`$, $SD = `r round(sd(dat$age[dat$trial==1]),2)`$), voluntarily participated in the study.
-The participants were recruited from the UCL Psychology and Language Sciences subject pool or by personal invitation from the researchers.
-Eligible university students ($n=`r sum(dat$version[dat$trial==1] == "sona")`$) received course credit for their participation.
-In addition, all participants were invited to enter a draw to win one of two gift vouchers (worth £50 and £20).
-Participants were informed that the chance of winning the prizes was dependent on their performance during the experiment.
-The study was approved by the UCL ethics committe and all participants provided informed consent before participating in the experiment.
-
-Participants were randomly allocated to either the Gradual change and Abrupt change condition.
-In the gradual condition, the level of volatility changed according to a sinusoid function, smoothly increasing and decreasing over time.
-In the abrupt condition, the level of volatility changed in a stepwise manner, being low in some blocks of trials and abruptly increasing in others.
-
-## The Fisher Game
-
-All participants played "The Fisher Game", an online browser-based game programmed in HTML and javascript.
-In the game, particpants controlled the position of a fisherman's boat in order to catch as many fish as possible.
-They could maximise the number of fish caught by placing the horizontal position of the boat such that the fishing rod was located at the centre of a school of fish.
-The further away the rod was from the centre of the school of fish, the less fish they could catch.
-The horizontal position of the school of fish moved from trial to trial, with the level of movement dependent on the level of volatility.
-On each of 100 trials participants were asked to choose a position for their boat, effectively predicting were the school of fish would be on that trial.
-After making their prediction, participants received information about the actual location of the school of fish and how many fish they caught.
-The game then proceeded to the next trial.
-
-More formally, on each trial $t$ the location of fish $y_t$ was equal to mean fish location $\mu_t$ plus random noise $\epsilon_t$.
-The mean fish location $\mu_t$ was in turn equal to of the mean fish location on a previous trial, $\mu_{t-1}$,  plus random change $\zeta_t$ representing the effect of volatility:
-
-$$\begin{aligned}
-y_t &= \mu_t + \epsilon_t && & \epsilon_t &\sim \mathcal{N}(0,\sigma_\epsilon) \\
-\mu_t &= \mu_{t-1} + \xi_t && & \zeta_t &\sim \mathcal{N}(0,\sigma_\xi(t))
-\end{aligned}$$
-
-The standard deviation of the noise was set to $\sigma_\epsilon = 4$ in all conditions and did not vary over time.
-The level of volatility, $\sigma_\xi(t)$ (the standard deviation of the changes in mean fish location) varied over time in a way that was specific to each condition.
-In the Gradual change condition, the volatility varied according to a sinus function:
-
-$$ \sigma_\xi(t) = 16.5 + 13.5 \times \sin \left( -2.5 + \frac{5 \times (t - 1)}{99} \right)$$
-
-In the Abrupt change condition, volatility varied in stepwise way:
-
-$$\sigma_\xi(t) = \begin{cases} 3 & \text{if } t \in [1;25] \text{ or } [51;75] \\ 30 & \text{if } t \in [26;50] \text{ or } [76,;100] \end{cases} $$
-In both conditions lowest volatility was equal to $\sigma_\xi(t) = 3$ and the highest volatility was equal to $\sigma_\xi(t) = 30$.
-Overall, in both conditions there were two low and two high volatility periods.
-
-```{r task-structure, out.width = "85%", fig.cap = "Data generating process used in the experiment.
-a) schematic representation of data generation process; b) example of generated data: graphs in the top row show variation of volatility by trial, graphs in the middle row show mean fish location, graphs in the bottom row show observed fish locations."}
-include_graphics("img/task_structure.eps")
-```
-
-We generated ten different random sequences of fish location per condition in advance according to the data generating process described above.
-This allowed to let each player observe a randomly generated set of locations, making it unlikely that the results would be dependent on the particulars of a single random sequence or that players would be able to help each other by discussing known fish locations.
-
-The number of fish caught each trial  was then determined by dividing 0.1 by absolute prediction error (difference between response  and actual location , see the formula below).
-As generated data and participants’ responses were transformed to fit a 0-1 scale, the reward formula allowed players to catch very high amounts of fish in case of very accurate predictions (capped at 300).
-At the same time, they were still able to catch few fish even in case of very inaccurate predictions.
-We used this scoring method to keep players motivated, as due to the randomness in the data generating process it was impossible to exactly predict the next fish location.
-The scores were not used in actual analysis.
-
-## Procedure
-
-Participants completed the game at their own pace in a single session.
-After providing informed consent, participants provided demographic information (age, gender, and nationality).
-They then read instructions, in which they were informed about the game interface, the goal of the game, and the conditions of the prize draw.
-
-Following the instructions the game started.
-On each trial, participants could see the location of the school of fish on the previous trial on the game viewport.
-They were also able to see all past locations of the school of fish in the "location graph" on the right of the game viewport.
-They then chose the horizontal position of the fishing boat through a mouseclick at any position on the game viewport.
-After making their choice, the boat smoothly moved to the chosen location, and the school of fish moved to the new location.
-Participants were then informed about the number of fish they caught on that trial.
-
-```{r game-screen, out.width = "85%", fig.cap = "Illustration of online game interface. Yellow and blue text labels point on to respective interface elements."}
-include_graphics("img/game_screen.eps")
-```
-
-Upon completion of the game participants were redirected to a post-game questionnaire were they were asked to answer the following three questions about the study: "How do you think fish locations were determined from day to day?", "What was your strategy to determine where to fish next?", and "What do you think was the aim of this study?".
-The answers were given in a free format and were not mandatory.
-
-# Results
-
-## Exclusions
-
-Four of the 100 participants were excluded from further analysis because both the mean squared error of their choices and the mean reaction time further than two standard deviations removed from the sample mean.
-Of the remaining `r with(subset(trial_data,trial == 1),length(condition))` participants `r with(subset(trial_data,trial == 1),{tab <- table(condition); tab[names(tab) == "abrupt"]})` were in the abrupt and `r with(subset(trial_data,trial == 1),{tab <- table(condition); tab[names(tab) == "gradual"]})` in the gradual condition.
-
-## Performance
-
-Participants' average mean squared error was equal to 0.012 (SD = 0.006) and average mean reaction time to 2207.43 (SD = 949.815) milliseconds.
-Mean reaction times did not differ between conditions (t(72.37) = 1.17, p = .248).
-Mean squared error was significantly higher (t(78.09) = -4.23, p < .001) in the gradual condition (M = .015) than in the abrupt condition (M = .010).
-
-## Empirical learning rates
-
-According to the "delta-rule", fish locations are learned as
-
-$$\hat{y}_{t+1} = \hat{y}_{t} + \eta(t) \left( y_{t} - \hat{y}_{t} \right)$$
-where we allow the learning-rate $\eta(t) > 0$ to vary from trial to trial. Assuming that participants location choices $r_t$ are a noisy reflection of their location predictions:
-$$\begin{aligned} r_t = \hat{y}_t + e_t && e_t \sim \mathcal{N}(0,\sigma_e)\end{aligned}$$
-we substitute $r_t = \hat{y}_t$ and re-arrange this equation to
-
-$$\begin{aligned} r_{t+1} - r_{t} &= \eta(t) \left( y_{t} - r_{t} \right) \\ u_t &= \eta(t) d_t \end{aligned}$$
-with $u_{i,t} = (r_{i,t+1} - r_{i,t})$ representing the update in location choice from trial $t$ to trial $t+1$ and $d_{i,t}= (y_{i,t} - r_{i,t})$ the deviation between location choice and true location on trial $t$.
-To assess the relation between $\eta(t)$ and the optimal learning rate $\omega_t = \frac{\sigma_\xi^2(t)}{\sigma_\xi^2(t) + \sigma^2_\epsilon}$, we estimated a linear mixed-effects model
-
-<!-- with $u_{i,t} = (r_{i,t+1} - r_{i,t})$ (the update in location choice from trial $t$ to trial $t+1$ for participant $i$) as dependent variable and $d_{i,t}= (y_{i,t} - r_{i,t})$ (the deviation between location choice and true location on trial $t$ for participant $i$) as predictor: -->
-
-$$u_{i,t} = \left(\beta_d + b_{di} + \beta_{dC} C_i + \beta_{d\omega} \omega_{it} + b_{d\omega i} \omega_{it} \right) d_{it} + e_{t,i}$$
-where $C$ is a contrast-coded predictor for condition ($C = 1$ for the abrupt, and $C = -1$ for the gradual condition), each $\beta$ term is a fixed effect, and each $b$ term a participant-wise random effect.
-Random intercepts and slopes were allowed to correlate.
-The model was estimated with the lme4 package for R [@R-lme4], and $p$-values were computed with the lmerTest package [@R-lmerTest].
-```{r mixed-effects,cache=TRUE,echo=FALSE}
-require(lmerTest)
-dat <- subset(trial_data,trial < 100)
-dat$omega <- .5*(sqrt(dat$volatility^4/4^4 + 4*dat$volatility^2/4^2) - dat$volatility^2/4^2) # (2*dat$volatility^2)/(2*dat$volatility^2 + 4^2)
-
-mod0 <- lmer(update ~ condition_as_number*omega*error + (scale(omega)*error|id),data=dat)
-mod1 <- lmer(update ~ error + condition_as_number:error + omega:error + condition_as_number:omega:error - 1 + (0 + error + scale(omega):error|id),data=dat)
-mod1_summ <- summary(mod1)
-mod0_summ <- summary(mod0)
-aov_full_reduced <- anova(mod0,mod1)
-```
-There was a significant main effect of deviation, `r texreport(mod1_summ,"error")`.
-This effect of error was moderated by the steady-state learning rate, `r texreport(mod1_summ,"error:omega")` and condition, `r texreport(mod1_summ,"error:condition_as_number")`.
-There was also a three-way interaction between deviation, optimal learning rate, and condition, `r texreport(mod1_summ,"error:condition_as_number:omega")`.
-
-We also estimated a linear-mixed effects model which, in addition to these effects, included fixed effects of condition ($C$), optimal learning rate ($\omega$), as well as all two-way and three-way interactions between these variables and deviation ($d$).
-This model also included an additional random effect for optimal learning rate ($\omega$).
-Comparing these two models indicated that the latter, more complex model fitted the data significantly better than the first, simpler model, $\chi^2(`r aov_full_reduced$'Chi Df'[2]`) = `r printnum(aov_full_reduced$'Chisq'[2])`$, $p = `r round(aov_full_reduced$'Pr(>Chisq)'[2],3)`$.
-Hence, we report the results from the full model.
-There was a significant main effect of deviation, `r texreport(mod0_summ,"error")`.
-This effect of error was moderated by the optimal learning rate, `r texreport(mod0_summ,"omega:error")` and condition, `r texreport(mod0_summ,"condition_as_number:error")`.
-There was also a three-way interaction between deviation, optimal learning rate, and condition, `r texreport(mod0_summ,"condition_as_number:omega:error")`.
-Finally, there was a significant main effect of condition, `r texreport(mod0_summ,"condition_as_number")`, which is difficult to interpret, but indicates a small bias where ...
-
-These effects are more easily interpreted when inspecting the model-predicted learning rate (Figure \@ref(fig:learning-rate-plot)).
-As can be seen there, while on average, people adapt their learning rate to the changes in volatility, the adaptation is more marked in the gradual compared to the abrupt change condition.
-Also, the predicted learning rates are mostly higher than the optimal steady-state learning rates.
-```{r learning-rate-plot,echo=FALSE,out.width = "85%", fig.width=6, fig.height=3, fig.cap="Predicted learning rates from the linear mixed-effects model as a function of the optimal learning rate."}
-require(ggplot2)
-require(lmerTest)
-coef <- fixef(mod0)
-
-# newdata <- expand.grid(condition=c("abrupt","gradual"),omega = seq(min(dat$omega),max(dat$omega),length=100))
-# newdata$condition_as_number <- 1
-# newdata$condition_as_number[newdata$condition == "abrupt"] <- -1
-# coeff <-  fixef(mod0)
-# 
-# newdata$pred_eta <- coeff["error"] + coeff["condition_as_number:error"]*newdata$condition_as_number + coeff["omega:error"]*newdata$omega + coeff["condition_as_number:omega:error"]*newdata$condition_as_number*newdata$omega
-# ggplot(newdata,aes(x=omega,y=pred_eta,colour=condition)) + geom_line() + ylab("predicted learning rate") + xlab("optimal learning rate") + ylim(c(min(newdata$omega),max(newdata$pred_eta))) + xlim(c(min(newdata$omega),max(newdata$pred_eta))) + geom_abline(slope=1,intercept=0,lty=2,colour=grey(.5))
-
-newdata <- data.frame(condition=rep(c("abrupt","gradual"),each=100),volatility = c(subset(trial_data,condition=="abrupt")$volatility[1:100],subset(trial_data,condition=="gradual")$volatility[1:100]),trial=1:100)
-newdata$omega <- .5*(sqrt(newdata$volatility^4/4^4 + 4*newdata$volatility^2/4^2) - newdata$volatility^2/4^2) # (2*newdata$volatility^2)/(2*newdata$volatility^2 + 4^2)
-newdata$condition_as_number <- 1
-newdata$condition_as_number[newdata$condition == "abrupt"] <- -1
-newdata$type = "optimal"
-
-newdata <- rbind(newdata,cbind(newdata[,1:5],type="estimated"))
-
-coeff <-  fixef(mod1)
-newdata$omega[newdata$type=="estimated"] <- coeff["error"] + coeff["error:condition_as_number"]*newdata$condition_as_number[newdata$type=="estimated"] + coeff["error:omega"]*newdata$omega[newdata$type=="estimated"] + coeff["error:condition_as_number:omega"]*newdata$condition_as_number[newdata$type=="estimated"]*newdata$omega[newdata$type=="estimated"]
-
-# coeff <-  fixef(mod0)
-# newdata$omega[newdata$type=="estimated"] <- coeff["error"] + coeff["condition_as_number:error"]*newdata$condition_as_number[newdata$type=="estimated"] + coeff["omega:error"]*newdata$omega[newdata$type=="estimated"] + coeff["condition_as_number:omega:error"]*newdata$condition_as_number[newdata$type=="estimated"]*newdata$omega[newdata$type=="estimated"]
-
-ggplot(newdata,aes(x=trial,y=omega,colour=type)) + geom_line() + ylab("(predicted) learning rate") + xlab("trial") + facet_wrap(~condition) + theme(legend.position="bottom") #+ ylim(c(min(newdata$omega),max(newdata$pred_eta))) + xlim(c(min(newdata$omega),max(newdata$pred_eta))) + geom_abline(slope=1,intercept=0,lty=2,colour=grey(.5))
-
-```
-
-<!--
-. However, as the comparison just fails significance, we also report the results of the more complex model in the appendix.
-
-provides us with a trial-by-trial estimate of the learning rate
-$$\hat{\eta}(t) = \frac{r_{t + 1} - r_{t}}{y_t - r_t}$$
-Under the assumption that $r_t$ is Normal distributed, this empricial learning rate follows a general Cauchy distribution.
--->
-
-# Discussion
-
-\newpage
-
-# References
-```{r create_r-references}
-r_refs(file = "r-references.bib")
-```
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id = "refs"></div>
-\endgroup
-
-<!--chapter:end:article.Rmd-->
-
----
-title             : "brouillon"
+title             : "Transfer of Learned Opponent Models in Zero Sum Games"
 shorttitle        : "Draft-3"
@@
 
-author_note: |
-  <!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->
-
-  Enter author note here.
+# author_note: |
+  #<!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->
+
+  #Enter author note here.
 
@@
 output            : papaja::apa6_pdf
-citation_package  : natbib
----
-
-```{r load-packages, include = FALSE}
-library(papaja)
-require(knitr)
-require(citr)
-require(bookdown)
-
-# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
-library(plyr)
-library(tidyr)
-library(dplyr)
-library(MASS)
-library(ggpubr)
-library(afex)
-library(PairedData)
-library(multcompView)
-library(lsmeans)
-library(magick)
-library(depmixS4)
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-```
-
-```{r, include=FALSE} 
-options(tinytex.verbose = TRUE)
-```
-
-# Introduction
-Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
-Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
-More formally, @perkins1992transfer defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
-This typically human skill has so far eluded modern AI agents.
-Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
-Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-[@Lake2017] argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
-
-One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
-Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations.
-This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
-There is evidence that people learn models of their opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
-In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities [@Woodruff] play a role in determining human behaviour.
-In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
-More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to the task of opponent modelling.
-
-Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
-For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
-They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-@knez2000increasing test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
-They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
-They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity.
-If the games were only strategically similar, then the transfer was much weaker.
-
-@Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
-However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games [@cooper2003lessons; @Cooper2008] the researchers found that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
-They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
-
-# References
-
-```{r create_r-references}
-r_refs(file = "Mendeley2.bib")
-
-```
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id = "refs"></div>
-\endgroup
-
-<!--chapter:end:brouillon.Rmd-->
-
----
-title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-shorttitle        : "Draft-1"
-
-author: 
-  - name          : "Ismail Guennouni"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
-    email         : "i.guennouni.17@ucl.ac.uk"
-  - name          : "Maarten Speekenbrink"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Experimental Psychology, University College London"
-
-author_note: |
-  <!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->
-
-  Enter author note here.
-
-abstract: |
-  Enter abstract here. Each new line herein must be indented, like this line.
-
-# keywords          : "keywords"
-# wordcount         : "X"
-
-bibliography      : ["Mendeley.bib"]
-# csl               : "apa-6th-edition.csl"
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-linkcolor         : "blue"
-mask              : no
-draft             : no
-fig_caption       : yes
-
-documentclass     : "apa6"
-# classoption       : a4paper
-classoption       : man
-output            : papaja::apa6_pdf
----
-
-```{r load-packages, include = FALSE}
-library(papaja)
-require(knitr)
-require(citr)
-require(bookdown)
-# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
-library(tidyr)
-library(dplyr)
-library(MASS)
-library(ggpubr)
-library(afex)
-library(PairedData)
-library(multcompView)
-library(lsmeans)
-library(magick)
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-```
-
-```{r, include=FALSE} 
-options(tinytex.verbose = TRUE)
-```
-
-# Introduction
-Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
-Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
-More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
-This typically human skill has so far eluded modern AI agents.
-Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
-Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-@Lake2017 argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
-
-One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
-Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations.
-This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
-There is evidence that people learn models of their opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
-In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities [@Woodruff] play a role in determining human behaviour.
-In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
-More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to the task of opponent modelling.
-
-Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
-For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
-They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-@knez2000increasing test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
-They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
-They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity.
-If the games were only strategically similar, then the transfer was much weaker.
-
-@Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
-However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games [@cooper2003lessons; @Cooper2008] the researchers found that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
-They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
-
-Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
-A notable exception is the effort by @Haruvy2012 to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
-Participants played ten games, presented as 4x4 normal form (matrix payoffs).
-Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
-They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on @stahl1995players, was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
-
-Still, one of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
-@simon1972theories explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
-Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in 'level-k' theory, first adopted by @stahl1995players.
-It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment @arad201211.
-Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
-Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below, and so on.
-
-In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit @goodie2012levels.
-
-Our choice of using computer oponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-When playing against other human opponents, players are learning about the game and the strategy of the opponent simultaneously.
-Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
-The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
-For instance, @spiliopoulos2013strategic made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
-@shachat2004we made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
-
-We chose to use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
-We avoid social dilemma and coordination games that crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
-Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
-Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
-As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transferred.
-By contrast, purely competitive settings and zero sum games in particular would be more appropriate.
-They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building.
-Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learning.
-Games with unique mixed strategy Nash equilibrium leading to nil average rewards facilitate inferring whether participants have learned to exploit the non-random play of the opponent.
-
-We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
-The first two games we use are identical except for action labels.
-In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with a fixed expected reward against a Nash player.
-
-Hence, we ran a total of two experiments where human participants played 3 different games against either 1 (first experiment ) or 2 (second experiment) computer opponents.
-In the following sections, we will describe each experiment's methodology and results separately, then discuss the findings before using computational modelling to shed light on some of the results.
-
-\newpage
-
-# Experiment 1
-
-## Methods
-
-## Participants
-
-A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
-The mean age of participants was 31.2 years.
-Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
-
-## Procedure
-
-In the first experiment, participants played 3 games sequentially against the same computer opponent.
-The computer opponent either used a level-1 or level-2 strategy.
-The three games were rock-paper-scissors, fire-water-grass and the numbers game.
-A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
-If one player choses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
-Otherwise it is a draw and both players receive a reward of 0.
-It has a unique MSNE consisting of randomly playing one of the three options each time.
-
-The second game is identical to Rock-Paper-Scissors in all but action labels.
-We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
-We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
-Finally, the numbers game is a generalization of rock-paper-scissors.
-In the variant we use, 2 participants concurrently pick a number between 1 and 5.
-To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent.
-For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
-To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
-This game has a structure similar to RPS in which every action is dominated by exactly one choice.
-All other possible combination of choices that are not consecutive are considered ties.
-A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score.
-Similar to RPS, the MSNE is to play each action with equal probability in a random way.
-
-Participants were informed they would play three different games against the same computer opponent.
-Each participant plays all three games consecutively and in the same order described above.
-Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
-A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
-The score was calculated as the number of wins minus the number of losses.
-Ties did not affect the score.
-In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-The overall score of the players was translated into the bonus by making each point worth £0.02.
-This bonus is significant as players could increase the total payoff from the experiment by up to 60% assuming they'd won all rounds against the computer opponent.
-An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps).
-
-```{r feedback-rps, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align='center'}
-
-knitr::include_graphics("images/feedback_rps.png")
-
-```
-
-## Results
-
-```{r load-exp1-data, include=FALSE}
-
-dat1 <- read.csv("../data20180719.csv")
-
-# transform 'winner' variable in numeric score
-dat1$score <- recode(dat1$winner, human = 1, tie = 0, ai = -1)
-# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
-dat1$block <- factor(as.numeric(cut(dat1$round,2)),labels =c("first half", "second half"))
-
-# create a new variable "game.f" as a factor variable of games
-dat1$game.f <- factor(dat1$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))
-
-#Group data by human_id and calculate mean score per block of each game.
-dat2 <- dat1 %>% 
-  group_by(human_id,condition,game,block,game.f) %>% 
-      summarize(block_score = mean(score))
-
-# Group data by game and ID
-dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
-# head(dat3,6)
-
-# Subsetting scores data by game
-rps <- subset(dat3,  game.f == "RPS",game_score)
-fwg <- subset(dat3,  game.f == "FWG",game_score)
-num <- subset(dat3,  game.f == "NUM",game_score)
-# head(rps,6)
-```
-
-```{r exp1-avg-scores-game, fig.cap = "Average scores per game across conditions", fig.align="center"}
-# Plot average  scores per game 
-ggboxplot(dat3, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
-```
-
-Looking at the aggregate scores (See Figure\ \@ref(fig:exp1-avg-scores-game) ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
-Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value < 0.001 ;  FWG:  t(51) = 10.04 , p-value < 0.001 ; NUMBERS: t(51) = 7.17, p-value < 0.001).
-
-To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game ( F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
-The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
-The main effect of Block ( F(1,50) = 22.51 , p < .001, $\eta^{2}$ = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning.
-As players interact more with the agent, they learn how to win more often.
-The main effect of Condition (F(1,50) = 5.44, p = .024, $\eta^{2}$ = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
-This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
-
-```{r exp1-3factor-plot, fig.cap = "Average scores by game, block and condition", fig.align = "center"}
-
-# Plot results by game and block (for all 3 games, learning is happening) 
-p <- ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")
-
-p + facet_grid(. ~ condition)
-
-```
-
-Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, $\eta^{2}$ = 0.02), indicating that within-game learning differed between the games.
-Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p <.0001), while there was no significant difference between block scores for the other two games.
-This is indicative of the significant within game transfer within the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
-There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent.
-For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than agaisnt level-1 opponent.
-The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
-
-### Learning transfer
-
-As a measure for learning transfer, we focus on participants’ scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
-A group of players with no experience of the game are expected to have scores not significantly different from 0.
-Any significantly positive group average scores would therefore reflect prior learning from past experiences.
-
-We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
-As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
-In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
-This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
-
-Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-Figure\ \@ref(fig: exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players.
-Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
-To test these hypotheses, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
-
-```{r exp1-early-rounds, include=FALSE}
-dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
-exp1_dat2_6 <- dat_26 %>% 
-  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
-      summarise(early_score = mean(score))
-
-# Check group means and SDs by game and condition
-group_by(exp1_dat2_6, game.f,condition) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-
-```
-
-```{r exp1-score-by-opp, fig.cap = "Average early scores by game and type of opponent faced", fig.align='center'}
-
-p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Average Score rounds 2-6", xlab = "Games")
-
-p2 + facet_grid(. ~ condition)
-
-```
-
-<!-- Table\ \@ref(tab:table-early-scores) shows the scores on rounds 2-6 for both type of opponents in each game.
-We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
-Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
--->
-
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p < 0.001) and NUMBERS (t(150) = 3.74, p < 0.001) .
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
-
-```{r ANOVA early exp1, include = FALSE, warning=FALSE}
-
-exp1_early_anova <- afex :: aov_car(
-  early_score ~ game.f*condition + Error(human_id/(game.f))
-  , data=exp1_dat2_6
-  , type = 3)
-
-apa_lm1 <- apa_print(exp1_early_anova)
-
-means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
-trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","NUM"))
-
-```
-
-```{r table-early-scores, include = FALSE, results = "asis"}
-# apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
-```
-
-Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game.
-Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
-
-\newpage
-
-# Second Experiment
-
-## Methods
-
-### Participants 
-A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
-This was a new set of participants unrelated to those taking part in Experiment 1.
-The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
-Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
-
-### Procedure
-
-The participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
-The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
-The first two games were identical to the ones used in the first experiment.
-In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper.
-Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
-If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
-Otherwise, the goalkeeper catches the ball and the player loses the round.
-There is no possibility of ties in this game.
-Figure XXXXXXXXX shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
-A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
-As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
-
-Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
-Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
-Participants start by facing one of the opponents in stage one, then face the other in stage two.
-This is repeated in the same order in stages 3 and 4.
-Which opponent they faced first was counterbalanced.
-All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
-
-In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
-During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
-A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent.
-After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
-Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction.
-The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-
-Like games used in the first experiment, all the games used in this seeting have a unique MSNE consisting of randomising across actions.
-If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
-Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
-
-## Results
-
-```{r load_exp2_data , include=FALSE}
-dat_int <- read.csv(file = "../Experiment_2/dat_int_exp2.csv")
-```
-
-The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had the highest average score (M = 0.622, SD = 0.326).
-The higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
-Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value < 0.0001 ;  FWG:  t(49) = 7.25 , p-value < 0.0001 ; Shootout: t(49) = 13.61, p-value < 0.0001 ).
-
-Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
-We perform a two (condition: level-1 first, level-2 first) by two ( opponne type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
-
-```{r Anova exp 2, include= FALSE}
-exp2_anova <- afex::aov_car(
-  int_score ~ (game.f*interaction_lvl*condition.f*opp_type) + Error(human_id/(game.f*interaction_lvl*opp_type))
-  , data = dat_int
-  , type = 3
-)
-
-(ls0 <- lsmeans(exp2_anova, "game.f", by = "opp_type"))
-(ls0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
-apa_lm <- apa_print(exp2_anova)
-
-```
-
-```{r exp2-score-by-opp, fig.cap="Average scores per game by opponent type", fig.align="center"}
-# p3 <- ggerrorplot(dat_int, x = "game.f", y = "int_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Scores per game", xlab = "Games")
-# 
-# p3 + facet_grid(. ~ opp_type)
-
-p4 <- ggboxplot(dat_int, x = "game.f", y = "int_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","SHOOT"), fill="interaction_lvl",ylab = "Percentage score", xlab = "Games")
-
-p4 + facet_grid(. ~ opp_type)
-
-```
-
-```{r exp2-anova, results = "asis", echo=FALSE, warning=FALSE}
-# apa_table( apa_lm$table, caption = "ANOVA results for experiment 2", escape = FALSE)
-```
-
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, $\eta^{2}$ = 0.04,  p < .0001).
-To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
-We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the Shootout game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
-There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
-This means that neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
-There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,$\eta^{2}$ = 0.02,  p = .01).
-As can be seen in Figure\ \@ref(fig:exp2-score-by-opp), when facing level-1 agents, scores increase steadily after each game, with FWG score sgnificantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG  ( t(191) = 3.05, p = 0.01).
-There was no significant difference between average scores on any two games when facing level-2 agents however.
-
-### Learning transfer
-
-```{r , include=FALSE}
-dat <- read.csv(file = "../Experiment_2/dat_exp2.csv")
-```
-
-As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random.
-Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
-
-```{r, include = FALSE}
-
-#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########
-
-dat_26 <- subset(dat,(round >1 & round < 7) & (interaction_lvl == "first interaction" ), drop =TRUE)
-
-exp2_dat2_6 <- dat_26 %>% 
-  group_by(human_id,condition.f,game.f,opp_type,confidence,difficulty) %>% 
-      summarise(early_score = mean(adj_score))
-
-# Check group means and SDs
-group_by(exp2_dat2_6, game.f) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-group_by(exp2_dat2_6, game.f,opp_type) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-```
-
-```{r exp2-early-scores, fig.cap="Average early round scores by game for experiment 2", fig.align="center"}
-# plot scores per game 
-p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Score rounds 2-6", xlab = "Games")
-
-p2 + facet_grid(. ~ opp_type)
-```
-
-In Figure\ \@ref(fig:exp2-early-scores), we show the average score across participants in rounds 2-6 of the first interaction with the opponent for each game.
-These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
-For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
-(Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; Shootout:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; Shootout:  t(270) = 3.21, p =0.004 ).
-Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
-Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
-These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
-
-\newpage
-
-# Computational modelling
-
-To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent.
-As a base model, we assume play is random, and each potential action is chosen with equal probability.
-Note that this corresponds to the Nash equilibrium strategy.
-In this section, we will go through the various models we have used and explain how they update what they learn about the game or the opponent
-
-## Reinforcement Learning
-
-We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
-We will use a simple temporal difference learning update rule:
-
-$$ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) $$
-
-Where $V_{t}(a)$ is the value associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
-Actions are chosen based on action values using a softmax choice rule.
-
-We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm [@watkins1992q]. The update rule becomes:
-
-$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$
-
-Where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\gamma$ is the discount rate applied to future rewards.
-For instance, $Q(RS,P)$ denotes the value of taking action "Paper" this round if the player's last action was "Rock" and the opponent played "Scissors".
-This is a much richer model allowing the players to compute the values of actions conditional on past play.
-
-In experiment 2, we allow this richer model to have a memory of the interaction.
-In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used.
-In another instance, we fit a model in which what was learned about an opponent in the first interaction is transfered to the first round of the second interaction, so there is a within-game trasnfer of Q-values allowed (QLS-within).
-We fit both models to all participant's data in the second experiment where both opponents are faced.
-
-### EWA Models 
-Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics].
-EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning.
-Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
-In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
-The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
-
-Let's define some notation in order to write the update rule of the self-tuning EWA model.
-For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j).
-Strategies actually played by i in period t, are denoted $s_{i}(t)$, while the opponent's strategy at time t is denoted $s_{-i}(t)$.
-After playing  $s_{i}^{j}$ at time $t$, player i payoff is denoted $\pi_{i}(s_{i}^{j},s_{-i}(t))$, and the actual payoff the player received is $\pi_{i}(t)$.
-
-The EWA model is based on updating "Attractions" for each action over time.
-For instance, the attraction of strategy $j$ to player $i$ at time $t$ is written $A_{i}^{j}(t)$.
-Future action choice probabilities are based on these attractions using the softmax playing rule:
-
-$$P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} $$
-
-The attractions are updated over every time step $t$ using the followng update rule :
-
-$$ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} $$
-
-Here, I(x,y) is the indicator function equal to 1 if $ x = y$ and 0 otherwise.
-A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince ($N(t-1)$) which is itself decaying by a wight $\phi$.
-The result is added to either the payoff received (when the indicator function is 0), or to $\delta$ times the foregone payoff (when indicator function is 1).
-We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play [@cheung1994learning].
-While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].
-
-### ToM models
-
-In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
-We use values of k  in ${0,1,2}$.
-We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
-In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between trasnfer)
-
-Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
-In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
-
-We fit the above two models to experiment 1 data.
-In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive).
-And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
-
-In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).
-In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
-Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
-
-## Experiment 1 modelling :
-
-```{r load-comp-mod-distrib, include=FALSE}
-
-All_comp_results <- read.csv(file="../All_results.csv")
-exp1_comp_table <- table(All_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(All_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])
-
- #write.csv(exp1_comp_table ,file="exp1_comp_table ",row.names = TRUE)
- kable(exp1_comp_table)
-```
-
-```{r exp1-cum-score-plots, include=FALSE}
-
-exp1_dat = read.csv("../exp1_data.csv")
-# exp1_model_comp = read.csv("../exp1_model_comp.csv")
-
-exp1_model_comp <- data.frame()
-for(id in unique(exp1_dat$human_id)) {
-  tdat <- subset(exp1_dat,human_id == id)
-  tot_score <- sum(tdat$score)
-  tot_time <- sum(tdat$human_rt)
-  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
-  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
-  tr_score <- sum(early_dat$score)
-  id_results <- subset(All_comp_results, ID == id)
-  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)
-
-  best_model <- c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
-  # 
-  exp1_model_comp <- rbind(exp1_model_comp,
-                       data.frame(
-                         "human_id" = id,
-                         "condition" = exp1_dat[exp1_dat$human_id==id,"condition"][1],
-                         "Early_game_score" = tr_score,
-                         "Total_score" = tot_score,
-                         "Best_model" = best_model,
-                         "Total_time" = sum(tdat$human_rt),
-                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
-                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
-
-                       ))
-}
-
-datalist = list()
-i = 0
-new_dat <- setNames(data.frame(matrix(ncol = ncol(exp1_dat), nrow = 0)), colnames(exp1_dat))
-for(id in unique(exp1_dat$human_id)) {
-  i <- i+1
-  tdat <- subset(exp1_dat,human_id == id)
-  tdat$part_num <- i
-  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
-  datalist[[i]] <- tdat
-}
-
-# Merge all datasets into one 
-new_dat <- dplyr::bind_rows(datalist)
-# or new_dat <- data.table::rbindlist(datalist)
-
-# Add column for time t
-new_dat <- new_dat %>% group_by(exp1_dat$human_id) %>% mutate(t = row_number())
-
-# Add best fitting model per participant
-new_dat <- merge(new_dat, exp1_model_comp[, c("human_id", "Best_model")], by="human_id")
-
-temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
-dat_by_model <- temp %>% group_by(Best_model,t) %>% 
-  summarize(model_acc_sum = mean(acc_sum))
-
-```
-
-Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
-
-```{r exp1-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 1", fig.align='center'}
-
-#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
-par(las=2) # make label text perpendicular to axis
-par(mar=c(5,8,4,2)) # increase y-axis margin.
-barplot(exp1_comp_table,
-        horiz =TRUE, # rotate barplot for better visibility 
-        las=1, # change orientation x axis labels 
-        cex.names=0.8, # text label size
-        legend = rownames(exp1_comp_table),
-        beside =TRUE,
-        xlab="Number of participants",
-        args.legend=list( # positioning of legend box 
-        x=ncol(exp1_comp_table) + 4,
-        y=max(colSums(exp1_comp_table)) + 4,
-        bty = "n")
- )
-
-```
-
-Next we compared the performance of players whose actions are best fit by each of our hypothesized models.
-Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (witout transfer), followed by Q-learning conditional on last round play.
-EWA, QL and random players had, understandably the lowest performance.
-
-```{r exp1-cumScores, fig.cap = "Average cumulative scores of participants in experiment 1 by best fitting model", fig.align='center'}
-p5 <- ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
-   geom_line(aes(color= Best_model))
-
-p5+ labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
-```
-
-## Experiment 2
-
-```{r, include = FALSE}
-
-exp2_comp_results <- read.csv(file="../Experiment_2/exp2_results.csv")
-# exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
-
-exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
-
- # write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
- kable(exp2_comp_table)
-```
-
-```{r exp2-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 2", fig.align='center'}
-
-#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
-par(las=2) # make label text perpendicular to axis
-par(mar=c(5,8,4,2)) # increase y-axis margin.
-barplot(exp2_comp_table,
-        horiz =TRUE, # rotate barplot for better visibility 
-        las=1, # change orientation x axis labels 
-        cex.names=0.8, # text label size
-        beside =TRUE,
-        xlab="Number of participants",
-        # legend = c("level-1 opp first","level-2 opp first"),
-        legend = paste0(rownames(exp2_comp_table) , " faced first"),
-        args.legend=list( # positioning of legend box 
-        x=ncol(exp2_comp_table) + 6,
-        y=max(colSums(exp2_comp_table)) +1,
-        bty = "n")
- )
-
-```
-
-In experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that Q-learning with the aforementioned state-space was again more successful than the bayesian models in fitting player's action choices.
-In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) did not fit players observed data as well.
-
-```{r, include=FALSE}
-
-dat_exp2 = read.csv("../Experiment_2/data_exp2.csv")
-
-#Adjust shootout score tor eflect easier game
-dat_exp2$adj_score <- ifelse(as.character(dat_exp2$game) == "shootout", dat_exp2$score - 0.333, dat_exp2$score)
-
-# Load data comparing models BIC for each participant 
-model_comp_2 = read.csv("../Experiment_2/exp2_model_comp.csv")
-
-datalist2 = list()
-i = 0
-
-#Build empty dataframe with same names as original data
-exp2_cum_score <- setNames(data.frame(matrix(ncol = ncol(dat_exp2), nrow = 0)), colnames(dat_exp2))
-for(id in unique(dat_exp2$human_id)) {
-  i <- i+1
-  tdat <- subset(dat_exp2,human_id == id)
-  tdat$part_num <- i
-  # NB : USE ADJUSTED SCORE IN SHOOTOUT
-  tdat <- within(tdat, acc_sum <- cumsum(tdat$adj_score))
-  datalist2[[i]] <- tdat
-}
-
-# Merge all datasets into one 
-exp2_cum_score <- dplyr::bind_rows(datalist2)
-# or exp2_cum_score <- data.table::rbindlist(datalist)
-
-# Add column for time t
-exp2_cum_score <- exp2_cum_score %>% group_by(human_id) %>% mutate(t = row_number())
-
-# Participant number as a factor 
-# tdat$part_num <- as.factor(tdat$part_num)
-
-# Add best fitting model per participant
-exp2_cum_score <- merge(exp2_cum_score, model_comp_2[, c("human_id", "Best_model_2")], by="human_id")
-
-temp2 <- exp2_cum_score[,c("t","acc_sum","Best_model_2","condition","part_num")]
-dat_by_model_2 <- temp2 %>% group_by(Best_model_2,t) %>% 
-  summarize(avg_acc_sum = mean(acc_sum))
-
-```
-
-```{r exp2-cumScores, fig.cap = "Average cumulative scores of participants in experiment 2 by best fitting model", fig.align='center'}
-
- p8 <- ggplot(data = dat_by_model_2, aes(x = t, y=avg_acc_sum, group = Best_model_2)) + 
-   geom_line(aes(color= Best_model_2)) +
-  scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))
-
-p8 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
-
-```
-
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
-Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance, folowed by a model in which both within and between trasnfer of opponent models is allowed (BT).
-The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive).
-As expected, random play as well as self-tuning EWA were at the bottom of cumulative performance.
-
-\newpage
-
-# Discussion
-
-In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies.
-We were interested in uncovering evidence for transfer and exploring whether it is modulated by the degree of similarity between games and the sophistication of the agent.
-
-The results of our first online experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
-We found that using results on very early rounds is a better proxy for measuring transfer as it is not tainted by any within game learning.
-Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
-
-In the second online experiment, the paradigm was better suited to explore our main research question, related to learning transfer rather than within-game learning.
-Indeed, when facing two opponents sequentially, there are many more opportunities to test transfer than before.
-Indeed, there are 2 opportunities to transfer knowledge within each game, and a total of three games, which means 6 opportunities to test transfer.
-When we made players face only one type of opponent each, we only had two possible learning transfers to test.
-In that regard, the results on learning transfer confirmed prior findings from the first experiment.
-While there was no evidence of learning transfer across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
-We also found that learning transfer is modulated by the type of opponent faced.
-When the players faced the level-1 opponent, they were able to transfer learning.
-However, when they faced the level-2 opponent, there was weaker evidence for transfer.
-The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with.
-A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
-
-Coming back to evidence for learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
-The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
-what did the players learn exactly about the opponent strategy and what form did this learning take?
-
-We will proceed by considering multiple potential answers to this question.
-First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
-An example is a spatial heuristic that consists of choosing "weapons" in a particular order (for instance left to right).
-This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
-We took this into account in designing experiment two by randomly shuffling the spatial order of action choices in each round.
-Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.
-
-A second possible hypothesis for learning the opponent’s strategy is the use of simple rules based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
-Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
-While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
-Indeed, learning the best action in a particular state cannot easily transfer to a new game since the state space is different and there is no simgle mapping between the state spaces of the initial and latter games.
-These rules would thereofre need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
-
-Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, would require many rounds of practice.
-Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
-After all, if players were using some type of associative learning or spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
-The fact that the degree of sophisitication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
-
-We are left with two possible explanations: First, it is possible that the players have uncovered a heuristic that allows them to beat the opponent without explicitly modelling their strategy, and is robust to transfer.
-Indeed, because of the cyclicality in action choices (e.g : Rock beats Scissors beats Paper beats Rock), it is possible to beat level-2 opponents most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
-This is a rule that wins and is also robust to transfer as it does not depend on action labels and even works in the dissimilar game.
-
-The second explanation of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
-A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
-For instance, the player may think “My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be”.
-This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
-This type of learning would be deemed “explicit” in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
-It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
-Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
-
-Our second experimental design allows us to test whether the first explanation holds.
-Since there is a simple transferable heuristic that works agaisnt level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
-Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.
-
-Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first intractions across games and using early rounds analysis.
-Based on our assumptions, we conclude that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the ourse of learning.
-
-\newpage
-
-# Conclusion
-
-Our online experiments confirm behavioural game theory results, stating that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
-Moreover, we showed that participants do transfer their learning to new games with varying degrees of similarity.
-The most likely explanation as we saw is that players build a mental representation of their opponent strategy, rather than rely on associative learning or action-based heuristics.
-The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.
-
-Having said that, there remains a high degree of heterogeneity between players.
-There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
-Moreover, the computational modelling shows that a significant number of players are still using random strategies in the games.
-Whether this ability depends on engagement with the experiment or on other characteristics of the learner is an open question that more research in the area would hope to answer.
-
-\newpage
-
-# References
-
-```{r create_r-references}
-r_refs(file = "Mendeley.bib")
-
-```
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id = "refs"></div>
-\endgroup
-
-<!--chapter:end:draft_report_v1.Rmd-->
-
----
-title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-shorttitle        : "Draft-2"
-
-author: 
-  - name          : "Ismail Guennouni"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
-    email         : "i.guennouni.17@ucl.ac.uk"
-  - name          : "Maarten Speekenbrink"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Experimental Psychology, University College London"
-
-author_note: |
-  <!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->
-
-  Enter author note here.
-
-abstract: |
-  Enter abstract here. Each new line herein must be indented, like this line.
-
-# keywords          : "keywords"
-# wordcount         : "X"
-
-bibliography      : ["Mendeley2.bib"]
-# csl               : "apa-6th-edition.csl"
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-linkcolor         : "blue"
-mask              : no
-draft             : no
-fig_caption       : yes
-
-documentclass     : "apa6"
-# classoption       : a4paper
-classoption       : man
-output            : papaja::apa6_pdf
----
-
-```{r load-packages, include = FALSE}
-library(papaja)
-require(knitr)
-require(citr)
-require(bookdown)
-# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
-library(tidyr)
-library(dplyr)
-library(MASS)
-library(ggpubr)
-library(afex)
-library(PairedData)
-library(multcompView)
-library(lsmeans)
-library(magick)
-library(depmixS4)
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-```
-
-```{r, include=FALSE} 
-options(tinytex.verbose = TRUE)
-```
-
-# Introduction
-Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
-Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
-More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
-This typically human skill has so far eluded modern AI agents.
-Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
-Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-@Lake2017 argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
-
-One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
-Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations.
-This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
-There is evidence that people learn models of their opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
-In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities [@Woodruff] play a role in determining human behaviour.
-In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
-More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to the task of opponent modelling.
-
-Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
-For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
-They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-@knez2000increasing test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
-They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
-They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity.
-If the games were only strategically similar, then the transfer was much weaker.
-
-@Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
-However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games [@cooper2003lessons; @Cooper2008] the researchers found that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
-They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
-
-Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
-A notable exception is the effort by @Haruvy2012 to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
-Participants played ten games, presented as 4x4 normal form (matrix payoffs).
-Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
-They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on @stahl1995players, was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
-
-Still, one of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
-@simon1972theories explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
-Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in 'level-k' theory, first adopted by @stahl1995players.
-It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment @arad201211.
-Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
-Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below, and so on.
-
-In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit @goodie2012levels.
-
-Our choice of using computer oponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-When playing against other human opponents, players are learning about the game and the strategy of the opponent simultaneously.
-Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
-The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
-For instance, @spiliopoulos2013strategic made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
-@shachat2004we made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
-
-We chose to use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
-We avoid social dilemma and coordination games that crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
-Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
-Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
-As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transferred.
-By contrast, purely competitive settings and zero sum games in particular would be more appropriate.
-They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building.
-Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learning.
-Games with unique mixed strategy Nash equilibrium leading to nil average rewards facilitate inferring whether participants have learned to exploit the non-random play of the opponent.
-
-We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
-The first two games we use are identical except for action labels.
-In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with a fixed expected reward against a Nash player.
-
-Hence, we ran a total of two experiments where human participants played 3 different games against either 1 (first experiment ) or 2 (second experiment) computer opponents.
-In the following sections, we will describe each experiment's methodology and results separately, then discuss the findings before using computational modelling to shed light on some of the results.
-
-\newpage
-
-# Experiment 1
-
-## Methods
-
-## Participants
-
-A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
-The mean age of participants was 31.2 years.
-Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
-
-## Procedure
-
-In the first experiment, participants played 3 games sequentially against the same computer opponent.
-The computer opponent either used a level-1 or level-2 strategy.
-The three games were rock-paper-scissors, fire-water-grass and the numbers game.
-A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
-If one player choses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
-Otherwise it is a draw and both players receive a reward of 0.
-It has a unique MSNE consisting of randomly playing one of the three options each time.
-
-The second game is identical to Rock-Paper-Scissors in all but action labels.
-We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
-We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
-Finally, the numbers game is a generalization of rock-paper-scissors.
-In the variant we use, 2 participants concurrently pick a number between 1 and 5.
-To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent.
-For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
-To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
-This game has a structure similar to RPS in which every action is dominated by exactly one choice.
-All other possible combination of choices that are not consecutive are considered ties.
-A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score.
-Similar to RPS, the MSNE is to play each action with equal probability in a random way.
-
-Participants were informed they would play three different games against the same computer opponent.
-Each participant plays all three games consecutively and in the same order described above.
-Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
-A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
-The score was calculated as the number of wins minus the number of losses.
-Ties did not affect the score.
-In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-The overall score of the players was translated into the bonus by making each point worth £0.02.
-This bonus is significant as players could increase the total payoff from the experiment by up to 60% assuming they'd won all rounds against the computer opponent.
-An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps).
-
-```{r feedback-rps, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align='center'}
-
-knitr::include_graphics("images/feedback_rps.png")
-
-```
-
-## Results
-
-```{r load-exp1-data, include=FALSE}
-
-dat1 <- read.csv("../data20180719.csv")
-
-# transform 'winner' variable in numeric score
-dat1$score <- recode(dat1$winner, human = 1, tie = 0, ai = -1)
-# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
-dat1$block <- factor(as.numeric(cut(dat1$round,2)),labels =c("first half", "second half"))
-
-# create a new variable "game.f" as a factor variable of games
-dat1$game.f <- factor(dat1$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))
-
-#Group data by human_id and calculate mean score per block of each game.
-dat2 <- dat1 %>% 
-  group_by(human_id,condition,game,block,game.f) %>% 
-      summarize(block_score = mean(score))
-
-# Group data by game and ID
-dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
-# head(dat3,6)
-
-# Subsetting scores data by game
-rps <- subset(dat3,  game.f == "RPS",game_score)
-fwg <- subset(dat3,  game.f == "FWG",game_score)
-num <- subset(dat3,  game.f == "NUM",game_score)
-# head(rps,6)
-```
-
-```{r exp1-avg-scores-game, fig.cap = "Average scores per game across conditions", fig.align="center"}
-# Plot average  scores per game 
-ggboxplot(dat3, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
-```
-
-Looking at the aggregate scores (See Figure\ \@ref(fig:exp1-avg-scores-game) ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
-Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value < 0.001 ;  FWG:  t(51) = 10.04 , p-value < 0.001 ; NUMBERS: t(51) = 7.17, p-value < 0.001).
-
-To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game ( F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
-The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
-The main effect of Block ( F(1,50) = 22.51 , p < .001, $\eta^{2}$ = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning.
-As players interact more with the agent, they learn how to win more often.
-The main effect of Condition (F(1,50) = 5.44, p = .024, $\eta^{2}$ = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
-This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
-
-```{r exp1-3factor-plot, fig.cap = "Average scores by game, block and condition", fig.align = "center"}
-
-# Plot results by game and block (for all 3 games, learning is happening) 
-p <- ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")
-
-p + facet_grid(. ~ condition)
-
-```
-
-Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, $\eta^{2}$ = 0.02), indicating that within-game learning differed between the games.
-Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p <.0001), while there was no significant difference between block scores for the other two games.
-This is indicative of the significant within game learning happening in the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
-There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent.
-For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than agaisnt level-1 opponent.
-The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
-
-### Learning transfer
-
-As a measure for learning transfer, we focus on participants’ scores in the first 5 rounds excluding the initial round (rounds 2-6).
-We exclude the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response, and therefore we cannot expect the participants to exhibit any learned best responses either.
-A group of players with no experience of the game are expected to have scores not significantly different from 0 over the early rounds of a new game, as was the case in RPS.
-Any significantly positive group average scores would therefore reflect prior learning from past experiences.
-
-We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
-As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
-In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
-This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
-
-Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-Figure\ \@ref(fig: exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players.
-Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
-To test these hypotheses, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
-
-```{r exp1-early-rounds, include=FALSE}
-dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
-exp1_dat2_6 <- dat_26 %>% 
-  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
-      summarise(early_score = mean(score))
-
-# Check group means and SDs by game and condition
-group_by(exp1_dat2_6, game.f,condition) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-
-```
-
-```{r exp1-score-by-opp, fig.cap = "Average early scores by game and type of opponent faced", fig.align='center'}
-
-p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Average Score rounds 2-6", xlab = "Games")
-
-p2 + facet_grid(. ~ condition)
-
-```
-
-<!-- Table\ \@ref(tab:table-early-scores) shows the scores on rounds 2-6 for both type of opponents in each game.
-We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
-Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
--->
-
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p < 0.001) and NUMBERS (t(150) = 3.74, p < 0.001) .
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
-
-```{r ANOVA early exp1, include = FALSE, warning=FALSE}
-
-exp1_early_anova <- afex :: aov_car(
-  early_score ~ game.f*condition + Error(human_id/(game.f))
-  , data=exp1_dat2_6
-  , type = 3)
-
-#apa_lm1 <- apa_print(exp1_early_anova)
-
-means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
-trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","NUM"))
-
-```
-
-```{r table-early-scores, include = FALSE, results = "asis"}
-# apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
-```
-
-Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game.
-Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
-
-\newpage
-
-# Second Experiment
-
-## Methods
-
-### Participants 
-A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
-This was a new set of participants unrelated to those taking part in Experiment 1.
-The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
-Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
-
-### Procedure
-
-The participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
-The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
-The first two games were identical to the ones used in the first experiment.
-In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper.
-Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
-If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
-Otherwise, the goalkeeper catches the ball and the player loses the round.
-There is no possibility of ties in this game.
-Figure\ \@ref(fig:screenshot-shootout)  shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
-A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
-As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
-
-```{r screenshot-shootout, fig.cap = "Screenshot of the shootout game", fig.align='center'}
-
-knitr::include_graphics("images/shootout.png")
-```
-
-Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
-Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
-Participants start by facing one of the opponents in stage one, then face the other in stage two.
-This is repeated in the same order in stages 3 and 4.
-Which opponent they faced first was counterbalanced.
-All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
-
-In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
-During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
-A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent.
-After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
-Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction.
-The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-
-Like games used in the first experiment, all the games used in this seeting have a unique MSNE consisting of randomising across actions.
-If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
-Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
-
-## Results
-
-```{r load_exp2_data , include=FALSE}
-dat_int <- read.csv(file = "../Experiment_2/dat_int_exp2.csv")
-```
-
-The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had the highest average score (M = 0.622, SD = 0.326).
-The higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
-Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value < 0.0001 ;  FWG:  t(49) = 7.25 , p-value < 0.0001 ; Shootout: t(49) = 13.61, p-value < 0.0001 ).
-
-Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
-We perform a two (condition: level-1 first, level-2 first) by two ( opponne type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
-
-```{r Anova exp 2, include= FALSE}
-exp2_anova <- afex::aov_car(
-  int_score ~ (game.f*interaction_lvl*condition.f*opp_type) + Error(human_id/(game.f*interaction_lvl*opp_type))
-  , data = dat_int
-  , type = 3
-)
-
-(ls0 <- lsmeans(exp2_anova, "game.f", by = "opp_type"))
-(ls0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
-apa_lm <- apa_print(exp2_anova)
-
-```
-
-```{r exp2-score-by-opp, fig.cap="Average scores per game by opponent type", fig.align="center"}
-# p3 <- ggerrorplot(dat_int, x = "game.f", y = "int_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Scores per game", xlab = "Games")
-# 
-# p3 + facet_grid(. ~ opp_type)
-
-p4 <- ggboxplot(dat_int, x = "game.f", y = "int_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","SHOOT"), fill="interaction_lvl",ylab = "Percentage score", xlab = "Games")
-
-p4 + facet_grid(. ~ opp_type)
-
-```
-
-```{r exp2-anova, results = "asis", echo=FALSE, warning=FALSE}
-# apa_table( apa_lm$table, caption = "ANOVA results for experiment 2", escape = FALSE)
-```
-
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, $\eta^{2}$ = 0.04,  p < .0001).
-To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
-We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the Shootout game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
-There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
-This means that neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
-There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,$\eta^{2}$ = 0.02,  p = .01).
-As can be seen in Figure\ \@ref(fig:exp2-score-by-opp), when facing level-1 agents, scores increase steadily after each game, with FWG score sgnificantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG  ( t(191) = 3.05, p = 0.01).
-There was no significant difference between average scores on any two games when facing level-2 agents however.
-
-### Learning transfer
-
-```{r , include=FALSE}
-dat <- read.csv(file = "../Experiment_2/dat_exp2.csv")
-```
-
-As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random.
-Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
-
-```{r, include = FALSE}
-
-#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########
-
-dat_26 <- subset(dat,(round >1 & round < 7) & (interaction_lvl == "first interaction" ), drop =TRUE)
-
-exp2_dat2_6 <- dat_26 %>% 
-  group_by(human_id,condition.f,game.f,opp_type,confidence,difficulty) %>% 
-      summarise(early_score = mean(adj_score))
-
-# Check group means and SDs
-group_by(exp2_dat2_6, game.f) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-group_by(exp2_dat2_6, game.f,opp_type) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-```
-
-```{r exp2-early-scores, fig.cap="Average early round scores by game for experiment 2", fig.align="center"}
-# plot scores per game 
-p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Score rounds 2-6", xlab = "Games")
-
-p2 + facet_grid(. ~ opp_type)
-```
-
-In Figure\ \@ref(fig:exp2-early-scores), we show the average score across participants in rounds 2-6 of the first interaction with the opponent for each game.
-These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
-For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
-(Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; Shootout:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; Shootout:  t(270) = 3.21, p =0.004 ).
-Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
-Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
-These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
-
-\newpage
-
-# Computational modelling
-
-To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent.
-As a base model, we assume play is random, and each potential action is chosen with equal probability.
-Note that this corresponds to the Nash equilibrium strategy.
-In this section, we will go through the various models we have used and explain how they update what they learn about the game or the opponent
-
-## Reinforcement Learning
-
-We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
-We will use a simple temporal difference learning update rule:
-
-$$ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) $$
-
-Where $V_{t}(a)$ is the value associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
-Actions are chosen based on action values using a softmax choice rule.
-
-We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm [@watkins1992q]. The update rule becomes:
-
-$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$
-
-Where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\gamma$ is the discount rate applied to future rewards.
-For instance, $Q(RS,P)$ denotes the value of taking action "Paper" this round if the player's last action was "Rock" and the opponent played "Scissors".
-This is a much richer model allowing the players to compute the values of actions conditional on past play.
-
-In experiment 2, we allow this richer model to have a memory of the interaction.
-In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used.
-In another instance, we fit a model in which what was learned about an opponent in the first interaction is transfered to the first round of the second interaction, so there is a within-game trasnfer of Q-values allowed (QLS-within).
-We fit both models to all participant's data in the second experiment where both opponents are faced.
-
-### EWA Models 
-Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics].
-EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning.
-Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
-In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
-The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
-
-Let's define some notation in order to write the update rule of the self-tuning EWA model.
-For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j).
-Strategies actually played by i in period t, are denoted $s_{i}(t)$, while the opponent's strategy at time t is denoted $s_{-i}(t)$.
-After playing  $s_{i}^{j}$ at time $t$, player i payoff is denoted $\pi_{i}(s_{i}^{j},s_{-i}(t))$, and the actual payoff the player received is $\pi_{i}(t)$.
-
-The EWA model is based on updating "Attractions" for each action over time.
-For instance, the attraction of strategy $j$ to player $i$ at time $t$ is written $A_{i}^{j}(t)$.
-Future action choice probabilities are based on these attractions using the softmax playing rule:
-
-$$P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} $$
-
-The attractions are updated over every time step $t$ using the followng update rule :
-
-$$ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} $$
-
-Here, I(x,y) is the indicator function equal to 1 if $ x = y$ and 0 otherwise.
-A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince ($N(t-1)$) which is itself decaying by a wight $\phi$.
-The result is added to either the payoff received (when the indicator function is 0), or to $\delta$ times the foregone payoff (when indicator function is 1).
-We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play [@cheung1994learning].
-While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].
-
-### ToM models
-
-In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
-We use values of k  in ${0,1,2}$.
-We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
-In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between trasnfer)
-
-Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
-In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
-
-We fit the above two models to experiment 1 data.
-In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive).
-And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
-
-In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).
-In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
-Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
-
-## Experiment 1 modelling :
-
-```{r load-comp-mod-distrib, include=FALSE}
-
-exp1_comp_results <- read.csv(file="../exp1_all_results.csv")
-exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])
-
- #write.csv(exp1_comp_table ,file="exp1_comp_table ",row.names = TRUE)
- kable(exp1_comp_table)
-```
-
-```{r exp1-cum-score-plots, include=FALSE}
-
-exp1_dat = read.csv("../exp1_data.csv")
-# exp1_model_comp = read.csv("../exp1_model_comp.csv")
-
-exp1_model_comp <- data.frame()
-for(id in unique(exp1_dat$human_id)) {
-  tdat <- subset(exp1_dat,human_id == id)
-  tot_score <- sum(tdat$score)
-  tot_time <- sum(tdat$human_rt)
-  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
-  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
-  tr_score <- sum(early_dat$score)
-  id_results <- subset(exp1_comp_results, ID == id)
-  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)
-
-  best_model <- c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
-  # 
-  exp1_model_comp <- rbind(exp1_model_comp,
-                       data.frame(
-                         "human_id" = id,
-                         "condition" = exp1_dat[exp1_dat$human_id==id,"condition"][1],
-                         "Early_game_score" = tr_score,
-                         "Total_score" = tot_score,
-                         "Best_model" = best_model,
-                         "Total_time" = sum(tdat$human_rt),
-                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
-                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
-
-                       ))
-}
-
-datalist = list()
-i = 0
-new_dat <- setNames(data.frame(matrix(ncol = ncol(exp1_dat), nrow = 0)), colnames(exp1_dat))
-for(id in unique(exp1_dat$human_id)) {
-  i <- i+1
-  tdat <- subset(exp1_dat,human_id == id)
-  tdat$part_num <- i
-  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
-  datalist[[i]] <- tdat
-}
-
-# Merge all datasets into one 
-new_dat <- dplyr::bind_rows(datalist)
-# or new_dat <- data.table::rbindlist(datalist)
-
-# Add column for time t
-new_dat <- new_dat %>% group_by(exp1_dat$human_id) %>% mutate(t = row_number())
-
-# Add best fitting model per participant
-new_dat <- merge(new_dat, exp1_model_comp[, c("human_id", "Best_model")], by="human_id")
-
-temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
-dat_by_model <- temp %>% group_by(Best_model,t) %>% 
-  summarize(model_acc_sum = mean(acc_sum))
-
-```
-
-Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
-
-```{r exp1-comp-models, fig.cap = "Experiment 1 - Histogram of best fitting computational models by condition", fig.align='center'}
-
-#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
-par(las=2) # make label text perpendicular to axis
-par(mar=c(5,8,4,2)) # increase y-axis margin.
-barplot(exp1_comp_table,
-        horiz =TRUE, # rotate barplot for better visibility 
-        las=1, # change orientation x axis labels 
-        cex.names=0.8, # text label size
-        legend = rownames(exp1_comp_table),
-        beside =TRUE,
-        xlab="Number of participants",
-        args.legend=list( # positioning of legend box 
-        x=ncol(exp1_comp_table) + 4,
-        y=max(colSums(exp1_comp_table)) + 4,
-        bty = "n")
- )
-
-```
-
-Next we compared the performance of players whose actions are best fit by each of our hypothesized models.
-Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (witout transfer), followed by Q-learning conditional on last round play.
-EWA, QL and random players had, understandably the lowest performance.
-
-```{r exp1-cumScores, fig.cap = "Experiment 1 - Average cumulative scores of participants by best fitting model", fig.align='center'}
-p5 <- ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
-   geom_line(aes(color= Best_model))
-
-p5 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
-```
-
-However, this is at odds with the findings from the previous section regarding learning transfer: If indeed most participants use Q-learning with states to choose their actions, then they should not be able to transfer learning to the early rounds of the new game.
-In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Theory of Mind models with and without the possibility of across game transfer.
-
-Figure\ \@ref(fig:exp1-lik-by-tr) shows that in the later games, the likelihood for the ToM models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of ToM models.
-
-```{r, include= FALSE}
-
-exp1_lik_by_trial  <- read.csv("../exp1_lik_by_trial.csv")
-
-mean_lik <- exp1_lik_by_trial %>%
-  dplyr::select(human_id,condition,game, round, QLS_lik, Bayes_NT_lik, Bayes_Tr_lik) %>%
-  group_by(condition,game,round) %>%
-  dplyr::summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
-            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
-            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
-
-mean_lik$game <- factor(mean_lik$game,levels=c("rps","fwg","numbers"))
-
-data_long <- tidyr::gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
-
-```
-
-```{r exp1-lik-by-tr, fig.cap = "Experiment 1 Likelihood by trial by game and opponent faced", fig.align='center'}
-# make sure the different games are ordered in the way they were played
-# data_long$game <- factor(data_long$game,levels=c("rps","fwg","numbers"))
-ggplot(data_long,aes(x=round,y=probability,colour=strategy)) +
-  geom_line() +
-  facet_grid(game~condition)
-
-```
-
-## Experiment 2
-
-```{r, include = FALSE}
-
-exp2_comp_results <- read.csv(file="../Experiment_2/exp2_results.csv")
-# exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
-
-exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
-
- # write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
- kable(exp2_comp_table)
-```
-
-```{r exp2-comp-models, fig.cap = "Experiment 2 Histogram of best fitting computational models by condition", fig.align='center'}
-
-par(las=2) # make label text perpendicular to axis
-par(mar=c(5,8,4,2)) # increase y-axis margin.
-barplot(exp2_comp_table,
-        horiz =TRUE, # rotate barplot for better visibility 
-        las=1, # change orientation x axis labels 
-        cex.names=0.8, # text label size
-        beside =TRUE,
-        xlab="Number of participants",
-        # legend = c("level-1 opp first","level-2 opp first"),
-        legend = paste0(rownames(exp2_comp_table) , " faced first"),
-        args.legend=list( # positioning of legend box 
-        x=ncol(exp2_comp_table) + 6,
-        y=max(colSums(exp2_comp_table)) +1,
-        bty = "n")
- )
-
-```
-
-In experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that Q-learning with the aforementioned state-space was again more successful than the bayesian models in fitting player's action choices.
-In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) did not fit players observed data as well.
-
-```{r, include=FALSE}
-
-dat_exp2 = read.csv("../Experiment_2/data_exp2.csv")
-
-#Adjust shootout score tor eflect easier game
-dat_exp2$adj_score <- ifelse(as.character(dat_exp2$game) == "shootout", dat_exp2$score - 0.333, dat_exp2$score)
-
-# Load data comparing models BIC for each participant 
-model_comp_2 = read.csv("../Experiment_2/exp2_model_comp.csv")
-
-datalist2 = list()
-i = 0
-
-#Build empty dataframe with same names as original data
-exp2_cum_score <- setNames(data.frame(matrix(ncol = ncol(dat_exp2), nrow = 0)), colnames(dat_exp2))
-for(id in unique(dat_exp2$human_id)) {
-  i <- i+1
-  tdat <- subset(dat_exp2,human_id == id)
-  tdat$part_num <- i
-  # NB : USE ADJUSTED SCORE IN SHOOTOUT
-  tdat <- within(tdat, acc_sum <- cumsum(tdat$adj_score))
-  datalist2[[i]] <- tdat
-}
-
-# Merge all datasets into one 
-exp2_cum_score <- dplyr::bind_rows(datalist2)
-# or exp2_cum_score <- data.table::rbindlist(datalist)
-
-# Add column for time t
-exp2_cum_score <- exp2_cum_score %>% group_by(human_id) %>% mutate(t = row_number())
-
-# Participant number as a factor 
-# tdat$part_num <- as.factor(tdat$part_num)
-
-# Add best fitting model per participant
-exp2_cum_score <- merge(exp2_cum_score, model_comp_2[, c("human_id", "Best_model_2")], by="human_id")
-
-temp2 <- exp2_cum_score[,c("t","acc_sum","Best_model_2","condition","part_num")]
-dat_by_model_2 <- temp2 %>% group_by(Best_model_2,t) %>% 
-  summarize(avg_acc_sum = mean(acc_sum))
-
-```
-
-```{r exp2-cumScores, fig.cap = "Experiment 2 Average cumulative scores of participants by best fitting model", fig.align='center'}
-
- p8 <- ggplot(data = dat_by_model_2, aes(x = t, y=avg_acc_sum, group = Best_model_2)) + 
-   geom_line(aes(color= Best_model_2)) +
-  scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))
-
-p8 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
-
-```
-
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
-Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance (although it only fit 2 participants best), followed by a model in which both within and between trasnfer of opponent models is allowed (BT).
-The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive).
-As expected, random play was at the bottom of cumulative performance.
-
-As in experiment 1, we want to understand the dynamic of strategy choice by plotting the likelihood by trial for each strategy, using the optimal parameters found when fitting the model.
-Figure\ \@ref(fig:exp2-lik-by-tr) shows that, as in experiment 1, ToM models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
-In the third and mosre dissimilar game, we get a result that is different from experiment 1.
-In this instance, the likelihoods of the ToM models stay constant and close to their initial values.
-
-```{r, include = FALSE }
-
-exp2_lik_by_trial <- read.csv("../Experiment_2/exp2_lik_by_trial.csv")
-
-mean_lik_2 <- exp2_lik_by_trial %>%
-  dplyr::select(human_id,game,stage,round_condition, round, QLS_lik, QLS_lik_within, Bayes_NT_lik, Bayes_Tr_lik) %>%
-  group_by(game,stage,round) %>%
-  summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
-            mean_QLS_within_lik = mean(QLS_lik_within, na.rm = TRUE),
-            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
-            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
-
-mean_lik_2$game <- factor(mean_lik_2$game,levels=c("rps","fwg","shootout"))
-
-data_long2 <- gather(mean_lik_2, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
-```
-
-```{r exp2-lik-by-tr, fig.cap = "Experiment2 likelihood by trial by game and opponent faced", fig.align ='center'}
-# make sure the different games are ordered in the way they were played
-# data_long2$game <- factor(data_long$game,levels=c("rps","fwg","shootout"))
-ggplot(data_long2,aes(x=round,y=probability,colour=strategy)) +
-  geom_line() +
-  facet_grid(game~stage)
-
-```
-
-## Using Hidden Markov Model to explore strategy switching
-
-The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative of participants switching between strategies as the games progressed.
-Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the ToM based strategies fit observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
-
-In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q learning with state space consisting of previous round play, ToM based model with and without opponent model transfer).
-Hidden Markov models are useful tools to explore structure in observed time series.
-They are named because of two properties: First, they make the assumption that any observable action at time t results from a process whose state at time t , named $S_{t}$ is "hidden" from the observer.
-Second, it also assumes that this hidden process has a Markov property, meaning that given state $S_{t-1}$, the value of $S_{t}$ is independent of all states occuring before time $t-1$.
-We also assume that $S_{t}$ has a discrete probability distribution in that it take one of K discrete values.
-The model is therefore specified by initial probabilities of being in each state ${1,2,...,K}$ and transition probabilities for moving from state $i$ to state $j$.
-These probabilities are fit using obsserved actiosn generated from these hidden states.
-
-sing the R DepmixS4 package, we fit a total of two HMMs.
-In the first model, we allow for a non-nil probability of players transitioning from one state (strategy) to another.
-In the second model, we assume that such switching does not happen, and as such assume implicitly that when players start with a particular strategy, they continue using it throughout the game.
-We then compare the likleihoods of each HMM model using a likelihood ration test.
-
-### Experiment 1:
-```{r define-dummy-response, include=FALSE}
-setClass("dummyResponse", contains="response")
-
-setGeneric("dummyResponse", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("dummyResponse"))
-
-setMethod("dummyResponse", 
-    signature(y="ANY"), 
-    function(y,pstart=NULL,fixed=NULL, ...) {
-      y <- matrix(y,length(y))
-  		x <- matrix(1)
-  		parameters <- list()
-  		npar <- 0
-      mod <- new("dummyResponse",parameters=parameters,fixed=logical(0),x=x,y=y,npar=npar)
-      mod
-	}
-)
-
-setMethod("show","dummyResponse",
-    function(object) {
-        cat("Dummy for fixed likelihood Model \n")
-    }
-)
-
-setMethod("dens","dummyResponse",
-  function(object,log=FALSE) {
-   if(log) log(as.numeric(object@y)) else as.numeric(object@y)
-  }
-)
-
-setMethod("getpars","dummyResponse",
-    function(object,which="pars",...) {
-        switch(which,
-            "pars" = {
-                pars <- numeric(0)
-            },
-            "fixed" = {
-                pars <- logical(0)
-            }
-        )
-        return(pars)
-    }
-)
-
-setMethod("setpars","dummyResponse",
-    function(object, values, which="pars", ...) {
-        npar <- npar(object)
-        if(length(values)!=npar) stop("length of 'values' must be",npar)
-        # determine whether parameters or fixed constraints are being set
-		nms <- ""
-		switch(which,
-		  "pars"= {
-		      },
-		  "fixed" = {
-		    }
-		  )
-      names(object@parameters) <- nms
-      return(object)
-    }
-)
-
-setMethod("fit","dummyResponse",
-    function(object,w) {
-		  return(object)
-	}
-)
-
-setMethod("predict","dummyResponse", 
-    function(object) {
-        ret <- object@y
-        return(ret)
-    }
-)
-```
-
-```{r, include=FALSE}
-
-## EXPERIMENT 1 Data
-
-QLS_lik <- exp1_lik_by_trial$QLS_lik
-# QLS_lik[which(QLS_lik == 0)] <- .001
-# QLS_lik[is.na(QLS_lik)] <- .33 # this is a hack; there shouldn't be any missing values
-Bayes_NT_lik <- exp1_lik_by_trial$Bayes_NT_lik
-Bayes_Tr_lik <- exp1_lik_by_trial$Bayes_Tr_lik
-
-nsubject <- length(unique(exp1_lik_by_trial$human_id)) # number of participants
-ngame <- 3 # number of games
-ntrial <- c(50,50,50) # numer of trials in each game
-
-rModels <- list(
-  list(
-	  dummyResponse(QLS_lik)
-	),
-	list(
-		dummyResponse(Bayes_NT_lik)
-	),
-  list(
-    dummyResponse(Bayes_Tr_lik)
-  )
-)
-
-trstart <- matrix(c(0.8,0.1,0.1,0.1,0.8,0.1,.1,.1,.8),ncol=3)
-transition <- list()
-transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
-transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
-transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
-
-instart <- c(1/3,1/3,1/3)
-inMod <- transInit(~1,nstates=3,pstart=instart,family=multinomial("identity"),data=data.frame(rep(1,nsubject*ngame)))
-
-mod1 <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
-
-fmod1 <- fit(mod1, emcontrol=em.control(random.start=FALSE))
-```
-
-```{r no-switch, include =FALSE}
-
-# No switching. Force off diagonal initial elements of transtion matrix to 0
-trstart <- matrix(c(1,0,0,0,1,0,0,0,1),ncol=3)
-transition <- list()
-transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
-transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
-transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
-
-mod1_noswitch <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
-
-fmod1_noswitch <- fit(mod1_noswitch, emcontrol=em.control(random.start=FALSE))
-
-# p-value for comparison between a model with strategy switches and one without:
-
-1-pchisq(-2*as.numeric(logLik(fmod1_noswitch)) - (-2*as.numeric(logLik(fmod1))),df=6)
-```
-```{r, include = FALSE}
-
-exp1_lik_by_trial["post_QLS"] <- forwardbackward(fmod1)$gamma[,1]
-exp1_lik_by_trial["post_Bayes_NT"] <- forwardbackward(fmod1)$gamma[,2]
-exp1_lik_by_trial["post_Bayes_Tr"] <- forwardbackward(fmod1)$gamma[,3]
-
-mean_post_1 <- exp1_lik_by_trial %>%
-  dplyr::select(human_id,game,condition, round, post_QLS, post_Bayes_Tr) %>%
-  group_by(game,condition, round) %>%
-  summarise(QLS_posterior = mean(post_QLS, na.rm = TRUE),
-            Bayes_Transfer_posterior = mean(post_Bayes_Tr, na.rm = TRUE))
-
-mean_post_1$game <- factor(mean_post_1$game,levels=c("rps","fwg","numbers"))
-
-data_long_post1 <- gather(mean_post_1, strategy, probability, QLS_posterior,Bayes_Transfer_posterior, factor_key=TRUE)
-
-```
-
-```{r exp1-posteriors-plot, fig.cap = "Experiment1 posterior probability of strategies by game and opponent faced", fig.align ='center'}
-
-ggplot(data_long_post1,aes(x=round,y=probability,colour=strategy)) +
-  geom_line() +
-  facet_grid(game~condition)
-
-```
-
-In experiment 1, the HMM model with swithcing has a significantly higher likelihood than the non-switching one (p-value = 0.00).
-This is further statistical evidence in favour of the hypothesis that participants switch between strategies.
-In order to understand at which stage of the games the switching might happen, and whether there are any differences between games and type of opponents faced, we plot in Figure\ \@ref(fig:exp1-posteriors-plot) the average (across participants) posterior probabilities given our HMM trial by trial for each game and opponent faced.
-Th eposterior probability is the probability that an observation comes from a component distribution a posteriori, i.e.
-given the value of the observation.
-In the first experiment, we can see from the plots of fwg and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the QLS model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
-
-### Experiment 2:
-
-```{r, include =FALSE}
-## EXPERIMENT 2 DATA 
-# we need to have "dat" available and lik_by_trial
-QLS_lik <- exp2_lik_by_trial$QLS_lik
-Bayes_NT_lik <- exp2_lik_by_trial$Bayes_NT_lik
-Bayes_Tr_lik <- exp2_lik_by_trial$Bayes_Tr_lik
-
-nsubject <- length(unique(exp2_lik_by_trial$human_id)) # number of participants
-ngame <- 12 # number of games
-#ntrial <- c(60,60,60)
-
-ntrial <- c(20,20,10,10,20,20,10,10,20,20,10,10) # number of trials in each game
-
-rModels <- list(
-  list(
-	  dummyResponse(QLS_lik)
-	),
-	list(
-		dummyResponse(Bayes_NT_lik)
-	),
-  list(
-    dummyResponse(Bayes_Tr_lik)
-  )
-)
-
-trstart <- matrix(c(0.8,0.1,0.1,0.1,0.8,0.1,.1,.1,.8),ncol=3)
-transition <- list()
-transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
-transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
-transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
-
-instart <- c(1/3,1/3,1/3)
-inMod <- transInit(~1,nstates=3,pstart=instart,family=multinomial("identity"),data=data.frame(rep(1,nsubject*ngame)))
-
-mod <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
-
-fmod <- fit(mod, emcontrol=em.control(random.start=TRUE))
-```
-
-```{r}
-
-exp2_lik_by_trial["post_QLSw"] <- forwardbackward(fmod)$gamma[,1]
-exp2_lik_by_trial["post_Bayes_NT"] <- forwardbackward(fmod)$gamma[,2]
-exp2_lik_by_trial["post_Bayes_Tr"] <- forwardbackward(fmod)$gamma[,3]
-
-mean_post_2 <- exp2_lik_by_trial %>%
-  dplyr::select(human_id,game,stage,round_condition, round, post_QLSw, post_Bayes_Tr) %>%
-  group_by(game,stage, round) %>%
-  summarise(mean_post_QLSw = mean(post_QLSw, na.rm = TRUE),
-            mean_post_Tr = mean(post_Bayes_Tr, na.rm = TRUE))
-
-mean_post_2$game <- factor(mean_post_2$game,levels=c("rps","fwg","shootout"))
-
-data_long_post2 <- gather(mean_post_2, strategy, probability, mean_post_QLSw,mean_post_Tr, factor_key=TRUE)
-
-```
-
-```{r exp2-posteriors-plot, fig.cap = "Experiment2 likelihood by trial by game and opponent faced", fig.align ='center'}
-
-ggplot(data_long_post2,aes(x=round,y=probability,colour=strategy)) +
-  geom_line() +
-  facet_grid(game~stage)
-
-```
-
-The switching model in experiment two has also significantly higher likelihood (p-value = 0.00).
-On top of indications from looking at the liklihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
-The posterior probability plot in Figure\ \@ref(fig:exp2-posteriors-plot) shows switching much more clearly across games ans stages, indicating a robust process.
-The switchign also seems to happen very early one at the beginning of each game and stage, and is also consistently in the same direction: The probability of Bayesian models with transfer being initially high, then decreasing rapidly while the posterior probability of QL-Learning with states and within transfer learning increases rapidly.
-
-\newpage
-
-# Discussion
-
-In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies.
-We were interested in uncovering evidence for transfer and exploring whether it is modulated by the degree of similarity between games and the sophistication of the agent.
-
-The results of our first online experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
-We found that using results on very early rounds is a better proxy for measuring transfer as it is not tainted by any within game learning.
-Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
-
-In the second online experiment, the paradigm was better suited to explore our main research question, related to learning transfer rather than within-game learning.
-Indeed, when facing two opponents sequentially, there are many more opportunities to test transfer than before.
-Indeed, there are 2 opportunities to transfer knowledge within each game, and a total of three games, which means 6 opportunities to test transfer.
-When we made players face only one type of opponent each, we only had two possible learning transfers to test.
-In that regard, the results on learning transfer confirmed prior findings from the first experiment.
-While there was no evidence of learning transfer across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
-We also found that learning transfer is modulated by the type of opponent faced.
-When the players faced the level-1 opponent, they were able to transfer learning.
-However, when they faced the level-2 opponent, there was weaker evidence for transfer.
-The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with.
-A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
-
-Coming back to evidence for learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
-The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
-what did the players learn exactly about the opponent strategy and what form did this learning take?
-
-We will proceed by considering multiple potential answers to this question.
-First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
-An example is a spatial heuristic that consists of choosing "weapons" in a particular order (for instance left to right).
-This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
-We took this into account in designing experiment two by randomly shuffling the spatial order of action choices in each round.
-Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.
-
-A second possible hypothesis for learning the opponent’s strategy is the use of simple rules based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
-Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
-While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
-Indeed, learning the best action in a particular state cannot easily transfer to a new game since the state space is different and there is no simgle mapping between the state spaces of the initial and latter games.
-These rules would thereofre need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
-
-Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, would require many rounds of practice.
-Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
-After all, if players were using some type of associative learning or spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
-The fact that the degree of sophisitication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
-
-We are left with two possible explanations: First, it is possible that the players have uncovered a heuristic that allows them to beat the opponent without explicitly modelling their strategy, and is robust to transfer.
-Indeed, because of the cyclicality in action choices (e.g : Rock beats Scissors beats Paper beats Rock), it is possible to beat level-2 opponents most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
-This is a rule that wins and is also robust to transfer as it does not depend on action labels and even works in the dissimilar game.
-
-The second explanation of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
-A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
-For instance, the player may think “My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be”.
-This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
-This type of learning would be deemed “explicit” in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
-It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
-Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
-
-Our second experimental design allows us to test whether the first explanation holds.
-Since there is a simple transferable heuristic that works agaisnt level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
-Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.
-
-Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first intractions across games and using early rounds analysis.
-Based on our assumptions, we conclude that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the ourse of learning.
-
-Our computational modelling allowed us to delve deeper into what might be driving the observed learning transfer.
-Initial modelling of observations using all available data seems to indicated that the most likely model was a Q-learning type model.
-However, as we argued above, that would be inconsistent with the evidence for learning transfer.
-Breaking down likelihoods by trial and fitting a hidden markov model to the data with states being the various strategies that participants are assumes to be using, we showed evidence for within game switching of strategies.
-Participants start the early rounds of a new game acting in a way consistent with a Bayesian Theory of mind level, which would be accurate and generalisable but computationally expensive.
-However, as trials continue, participants seem to switch to a habitual type of learning (QL-models).
-
-Why is this switching happening?
-We believe that participants show flexibility in their use of learning strategies.
-When a new game is started that is similar to a previously played game with the same opponent, participants need a way to transfer prior knowledge of the opponent and apply it to the new game in order to best respond.
-Adopting a Bayesian model based on ToM achieves the goal of trasnfering the opponent model and thus coming up with best responses in the early trials.
-However, Bayesian ToM models are computationally expensive and require a lot of higher order thinking (I think that you think that I think...).
-As such, as the games progresses, they become burdensome and the higher amount of historical interaction in the new game allows participants to have enough data to start using the cognitively cheaper model-free learning strategies such as Q-learning.
-The bias towards less computationally demanding strategies is well established @Kool_2011.
-Moreover, the ability to flexibly switch is also consistent with evidence from the literature on learning strategies in humans, showing that they indeed shift between model-based and model-free learning when the environment requires it @Simon_Daw_11.
-
-\newpage
-
-# Conclusion
-
-Our online experiments confirm behavioural game theory results, stating that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
-Moreover, we showed that participants do transfer their learning to new games with varying degrees of similarity.
-The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.
-
-Having said that, there remains a high degree of heterogeneity between players.
-There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
-Moreover, the computational modelling shows that it is likely that players start each game using a model-based learning strategy that facilitates generalisation and opponent model transfer, but then switch to behvior that is consistent with a  model-free learning strategy as the experiment goes on.
-This is likely driven by a trade-off between computational complexity and accuracy between model based and model free strategies.
-\newpage
-
-# References
-
-```{r create_r-references}
-r_refs(file = "Mendeley2.bib")
-
-```
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id = "refs"></div>
-\endgroup
-
-<!--chapter:end:draft_report_v2.Rmd-->
-
----
-title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-shorttitle        : "Draft-3"
-
-author: 
-  - name          : "Ismail Guennouni"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
-    email         : "i.guennouni.17@ucl.ac.uk"
-  - name          : "Maarten Speekenbrink"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Experimental Psychology, University College London"
-
-# author_note: |
-  #<!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->
-
-  #Enter author note here.
-
-abstract: |
-  Enter abstract here. Each new line herein must be indented, like this line.
-
-# keywords          : "keywords"
-# wordcount         : "X"
-
-bibliography      : ["Mendeley2.bib"]
-csl               : "apa-6th-edition.csl"
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-linkcolor         : "blue"
-mask              : no
-draft             : no
-fig_caption       : yes
-
-documentclass     : "apa6"
-# classoption       : a4paper
-classoption       : man
-output            : papaja::apa6_pdf
-      pandoc_args : !expr rmdfiltr::add_wordcount_filter()
 #citation_package  : natbib
@@
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind @premack1978does abilities play a role in determining human behaviour.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind [@premack1978does] abilities play a role in determining human behaviour.
 In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
@@
 
-This literature adopted two types of opponents in the experimental setting: either human participants or computer algorithms.
+In exploring opponent modelling and learning transfer, most studies adopted two types of opponents in the experimental setting.
+Either human participants were matched with other participants or they played against a computer algorithm.
+Computer opponents were generally programmed not to change their strategies over the course of the task, allowing better experimental control.
 One of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
@@
 The agents will either be a level-1 or level-2 player, mimicking human theory of mind abilities and the limited recursion depth they exhibit [@goodie2012levels].
-
 Our choice of using computer opponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
@@
 They found that the players changed their strategies towards exploiting the deviations of the opponent from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
-
 We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
@@
 ### Participants and Design
-
 A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
@@
 ### Tasks
-
-In the first experiment,  The three games were rock-paper-scissors, fire-water-grass and the numbers game.
+In the first experiment, the three games were rock-paper-scissors, fire-water-grass and the numbers game.
 A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
@@
 ### Procedure
-
 Participants played 3 games sequentially against the same computer opponent.
@@
 \endgroup
-
-<!--chapter:end:draft_report_v3.Rmd-->

### 2020-10-30 Report/draft_report_v3.tex
draft3

--- 2020-09-09 Report/draft_report_v2.tex
@@
 
-\shorttitle{Draft-2}
+\shorttitle{Draft-3}
 \affiliation{
@@
 
-Enter author note here.
-
 Correspondence concerning this article should be addressed to Ismail Guennouni, Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom.
@@
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
-More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
+More formally, Perkins, Salomon, \& Others (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
 This typically human skill has so far eluded modern AI agents.
@@
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Woodruff, Sciences, Brain, \& 1978, n.d.) play a role in determining human behaviour.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind (Premack \& Woodruff, 1978) abilities play a role in determining human behaviour.
 In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
@@
 They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-({\textbf{???}}) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+Camerer \& Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
 They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
@@
 However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games (Cooper \& Kagel, 2003, 2008) the researchers found that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
-They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
-
-Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
+In a series of experiments using economic signalling games Cooper \& Kagel (2003, 2008) found that participants who have learned to play according to a Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of a different payoff structure on an opponent's actions.
+
+Most studies fail to offer a formal explanation of transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
 A notable exception is the effort by Haruvy \& Stahl (2012) to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
-Participants played ten games, presented as 4x4 normal form (matrix payoffs).
+Participants played ten games, presented in 4x4 normal form (matrix payoffs).
 Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
 They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on Stahl \& Wilson (1995), was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
-
-Still, one of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
+Their rule-learning model, based on Stahl \& Wilson (1995), was able to capture participants' dynamic behavior and shows that the propensity to select particular rules is perfectly transferred across games.
+
+In exploring opponent modelling and learning transfer, most studies adopted two types of opponents in the experimental setting.
+Either human participants were matched with other participants or they played against a computer algorithm.
+Computer opponents were generally programmed not to change their strategies over the course of the task, allowing better experimental control.
+One of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
 The strategies implemented by the computer opponents had a style of play that was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that \enquote{play like humans}, and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
-Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
+It is therefore important to have agents that \enquote{play like humans}, and one way of achieving that is to embed theses agents with human-like theory of mind abilities.
+Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally complex problems such as finding Nash equilibria.
 Instead, they will try to \enquote{satisfice} by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
 This concept finds its natural application in \enquote{level-k} theory, first adopted by Stahl \& Wilson (1995).
-It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
+It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogeneous degree of strategic sophistication.
 At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment Arad \& Rubinstein (2012).
@@
 In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit Goodie, Doshi, \& Young (2012).
-
-Our choice of using computer oponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-When playing against other human opponents, players are learning about the game and the strategy of the opponent simultaneously.
+The agents will either be a level-1 or level-2 player, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie, Doshi, \& Young, 2012).
+Our choice of using computer opponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
+When playing against other human opponents, players are learning about the game as well as trying to infer the potential dynamic strategy of the opponent simultaneously.
 Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
 The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
-For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
+For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents, designed to take advantage of known patterns in human play such as imperfect randomization and heuristics use.
+He found that human participants do adapt to the opponent they are facing.
 Shachat \& Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
-
-We chose to use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
-We avoid social dilemma and coordination games that crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
-Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
-Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
-As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transferred.
-By contrast, purely competitive settings and zero sum games in particular would be more appropriate.
-They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building.
-Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learning.
-Games with unique mixed strategy Nash equilibrium leading to nil average rewards facilitate inferring whether participants have learned to exploit the non-random play of the opponent.
-
+They found that the players changed their strategies towards exploiting the deviations of the opponent from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
 We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
-The first two games we use are identical except for action labels.
-In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with a fixed expected reward against a Nash player.
-
-Hence, we ran a total of two experiments where human participants played 3 different games against either 1 (first experiment ) or 2 (second experiment) computer opponents.
-In the following sections, we will describe each experiment's methodology and results separately, then discuss the findings before using computational modelling to shed light on some of the results.
+The first two games we use are structurally identical except for action labels.
+In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure.
+In the first experiment, participants face the same opponent throughout the three games, and the opponents are randomised to be either level-1 or level-2 players.
+In the second experiment, participants faced both level-1 and level-2 opponent sequentially, with the order in which they are faced randomised across participants.
 
@@
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\hypertarget{participants-and-design}{%
+\subsubsection{Participants and Design}\label{participants-and-design}}
 
@@
 Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-In the first experiment, participants played 3 games sequentially against the same computer opponent.
-The computer opponent either used a level-1 or level-2 strategy.
-The three games were rock-paper-scissors, fire-water-grass and the numbers game.
+The study used a 2 (computer opponent: level 1 or level 2) by 3 (games: rock-paper-scissors, fire-water-grass, numbers) design, with repeated measures on the second factor.
+
+\hypertarget{tasks}{%
+\subsubsection{Tasks}\label{tasks}}
+
+In the first experiment, the three games were rock-paper-scissors, fire-water-grass and the numbers game.
 A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
-If one player choses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
+If one player chooses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
 Otherwise it is a draw and both players receive a reward of 0.
-It has a unique MSNE consisting of randomly playing one of the three options each time.
-
-The second game is identical to Rock-Paper-Scissors in all but action labels.
+It has a unique MSNE consisting of randomly playing one of the three options each time.The second game is identical to Rock-Paper-Scissors in all but action labels.
 We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
@@
 
+\hypertarget{procedure}{%
+\subsubsection{Procedure}\label{procedure}}
+
+Participants played 3 games sequentially against the same computer opponent.
+The computer opponent either used a level-1 or level-2 strategy.
 Participants were informed they would play three different games against the same computer opponent.
@@
 In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-The overall score of the players was translated into the bonus by making each point worth £0.02.
-This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they'd won all rounds against the computer opponent.
-An example of the interface for the rock-paper-scissors game is provided in Figure~\ref{fig:feedback-rps}.
+Each point worth £0.02.
+An example of the interface for the rock-paper-scissors game is provided in Figure~\ref{fig:feedback-rps-exp2}.
 
@@
 
-\caption{Screenshot of the feedback at the end of a round of Rock-Paper-Scissors}\label{fig:feedback-rps}
+\caption{Screenshot of the feedback at the end of a round of Rock-Paper-Scissors}\label{fig:feedback-rps-exp2}
 \end{figure}
@@
 \hypertarget{results}{%
-\subsection{Results}\label{results}}
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-avg-scores-game-1}
-
-}
-
-\caption{Average scores per game across conditions}\label{fig:exp1-avg-scores-game}
+\subsubsection{Results}\label{results}}
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-avg-scores-game-1}
+
+}
+
+\caption{Boxplot of scores per game across conditions}\label{fig:exp1-avg-scores-game}
 \end{figure}
@@
 Looking at the aggregate scores (See Figure~\ref{fig:exp1-avg-scores-game} ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
-Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value \textless{} 0.001 ; FWG: t(51) = 10.04 , p-value \textless{} 0.001 ; NUMBERS: t(51) = 7.17, p-value \textless{} 0.001).
-
+Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, \(p\) \textless{} 0.001 ; FWG: t(51) = 10.04 , \(p\) \textless{} 0.001 ; NUMBERS: t(51) = 7.17, \(p\) \textless{} 0.001).
 To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
 There was a main effect of Game ( F(2,100) = 8.54, \(\eta^{2}\) = 0.05, p \textless{} 0.001), showing that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
-The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in the NUMBERS game was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
+The score in RPS was not significantly different from the score in NUMBERS ( t(100) = 0.45 , p = 0.65).
 The main effect of Block ( F(1,50) = 22.51 , p \textless{} .001, \(\eta^{2}\) = 0.03) shows that the average score in the first half of games (M = 0.29) was significantly lower than in the second half of the games played (M = 0.40), which translates to within-game learning.
-As players interact more with the agent, they learn how to win more often.
 The main effect of Condition (F(1,50) = 5.44, p = .024, \(\eta^{2}\) = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
-This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-3factor-plot-1}
+This indicates that it was harder for participants, on average, to exploit the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-3factor-plot-1}
 
@@
 
-Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, \(\eta^{2}\) = 0.02), indicating that within-game learning differed between the games.
+Finally, the analysis showed a significant block by game interaction ( F(2,100) = 6.92 , p = .002, \(\eta^{2}\) = 0.02), indicating that within-game learning differed between the games.
 Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p \textless{}.0001), while there was no significant difference between block scores for the other two games.
-This is indicative of the significant within game learning happening in the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
+This is indicative of the significant within-game learning happening in the first game when players have no experience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some experience playing against the opponent and start with higher scores indicative of transfer.
 There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, \(\eta^{2}\) = 0.01), which indicates, as seen in Figure~\ref{fig:exp1-3factor-plot} that within-game learning changes across games also depend on the sophistication of the opponent.
-For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than agaisnt level-1 opponent.
+For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than against level-1 opponent.
 The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
@@
 As a measure for learning transfer, we focus on participants' scores in the first 5 rounds excluding the initial round (rounds 2-6).
-We exclude the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response, and therefore we cannot expect the participants to exhibit any learned best responses either.
-A group of players with no experience of the game are expected to have scores not significantly different from 0 over the early rounds of a new game, as was the case in RPS.
-Any significantly positive group average scores would therefore reflect prior learning from past experiences.
-
-We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
-As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
-In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p \textless{} 0.0001).
+We exclude the very first round as the computer opponent plays randomly here and there is no opportunity yet for the human player to exploit their opponent's strategy.
+A group of players with no experience of the game are expected to perform at chance level over the early rounds of a new game, as was the case in RPS.
+Positive scores in the early rounds would therefore reflect generalization of prior experience.
+For the FWG game, the score is significantly higher than 0 ( t(148.85) = 4.58 , p \textless{} 0.0001).
 This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
+For the RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-score-by-opp-1}
+
+}
+
+\caption{Mean and CI of early scores by game and opponent}\label{fig:exp1-score-by-opp}
+\end{figure}
 
 Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-Figure~@ref(fig: exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players.
+Figure~\ref{fig:exp1-score-by-opp} shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players as well as the \(95\) percent confidence interval for the mean.
 Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
-To test these hypotheses, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-score-by-opp-1}
-
-}
-
-\caption{Average early scores by game and type of opponent faced}\label{fig:exp1-score-by-opp}
-\end{figure}
-
+To explore this, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p \textless{} 0.001) and NUMBERS (t(150) = 3.74, p \textless{} 0.001) .
 For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
+
+\hypertarget{discussion-experiment-1}{%
+\subsubsection{Discussion Experiment 1}\label{discussion-experiment-1}}
 
@@
 
+We ran a second experiment with various differentiated features to improve the opportunity to measure learning transfer.
+Instead of making participants face either the level-1 or level-2 player throughout, we made them face both opponent sequentially.
+Because there were two distinct opponents, requiring potentially holding two opponent models in memory, we also made it easier to recall the results of past rounds by providing participants with the opportunity to see the history of the game since the beginning of each interaction.
+Figure~\ref{fig:feedback-rps-exp2} shows an example of showing interaction history in the RPS game.
+Finally, we changed the third game to a penalty shootout game, which has the same number of actions as the first two.
+If we see evidence for differential play against opponents, it would show participants adapting their strategies to the opponent they are facing, which is indicative of opponent modelling.
+
 \hypertarget{methods-1}{%
@@
 
-\hypertarget{participants-1}{%
-\subsubsection{Participants}\label{participants-1}}
+\hypertarget{participants-design}{%
+\subsubsection{Participants \& Design}\label{participants-design}}
 
@@
 
-\hypertarget{procedure-1}{%
-\subsubsection{Procedure}\label{procedure-1}}
-
-The participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
-The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
+\hypertarget{tasks-1}{%
+\subsubsection{Tasks}\label{tasks-1}}
+
+The three games the participants played were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
 The first two games were identical to the ones used in the first experiment.
-In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper.
+In the final game (shootout) the participants took the role of the player shooting a football (soccer) penalty, with the AI opponent being the goalkeeper.
 Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
@@
 
+\hypertarget{procedure-1}{%
+\subsubsection{Procedure}\label{procedure-1}}
+
+The participants played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
 Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
@@
 All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
-
 In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
 During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
-A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent.
+A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response, as a way of simulating a real human opponent thinking time.
 After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
-Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction.
+Further information about the outcome of previous rounds was also visible on the game screen below the feedback area.
+Throughout each stage, participants could scroll down to recall the history of interaction.
 The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-
-Like games used in the first experiment, all the games used in this seeting have a unique MSNE consisting of randomising across actions.
+As in the first experiment, all the games have a unique MSNE consisting of randomising across actions.
 If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
@@
 
-The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had the highest average score (M = 0.622, SD = 0.326).
-The higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
+The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had an adjusted average score in between the two (M = 0.289, SD = 0.326).\footnote{A higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
 Indeed, a player not aiming to uncover the opponent's strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value \textless{} 0.0001 ; FWG: t(49) = 7.25 , p-value \textless{} 0.0001 ; Shootout: t(49) = 13.61, p-value \textless{} 0.0001 ).
-
+To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33)}.
+Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, \(p\) \textless{} 0.0001 ; FWG: t(49) = 7.25 , \(p\) \textless{} 0.0001 ; Shootout: t(49) = 13.61, \(p\) \textless{} 0.0001 ).
 Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
-We perform a two (condition: level-1 first, level-2 first) by two ( opponne type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-score-by-opp-1}
-
-}
-
-\caption{Average scores per game by opponent type}\label{fig:exp2-score-by-opp}
+We perform a two (condition: level-1 first, level-2 first) by two ( opponent type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-score-by-opp-1}
+
+}
+
+\caption{Boxplot of scores per game and interaction by opponent type}\label{fig:exp2-score-by-opp}
 \end{figure}
@@
 There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
-This means that neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
 There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,\(\eta^{2}\) = 0.02, p = .01).
-As can be seen in Figure~\ref{fig:exp2-score-by-opp}, when facing level-1 agents, scores increase steadily after each game, with FWG score sgnificantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG ( t(191) = 3.05, p = 0.01).
+Figure~\ref{fig:exp2-score-by-opp} shows boxplots of game scores, averaged across participants, by game and opponent type.
+We also distinguish between scores from the first time the players faced the opponent (first interaction) and the second time they did (second interaction).
+We see that when facing level-1 agents, scores increase steadily after each game, with FWG score significantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG ( t(191) = 3.05, p = 0.01).
 There was no significant difference between average scores on any two games when facing level-2 agents however.
@@
 As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random.
-Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-early-scores-1}
-
-}
-
-\caption{Average early round scores by game for experiment 2}\label{fig:exp2-early-scores}
-\end{figure}
-
-In Figure~\ref{fig:exp2-early-scores}, we show the average score across participants in rounds 2-6 of the first interaction with the opponent for each game.
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-early-scores-1}
+
+}
+
+\caption{Average early round scores and confidence intervals by game and opponent for experiment 2}\label{fig:exp2-early-scores}
+\end{figure}
+
+In Figure~\ref{fig:exp2-early-scores}, we show the average score across participants and its \(95\) percent confidence interval in rounds 2-6 of the first interaction with the opponent for each game.
 These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
@@
 (Level-1 opponent: FWG: t(270) = 4.99, p \textless{} 0.0001; Shootout: t(270) = 6.66, p \textless{} 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p \textless{} 0.0001; Shootout: t(270) = 3.21, p =0.004 ).
-Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
+
+\hypertarget{experiment-2-discussion}{%
+\subsubsection{Experiment 2 discussion:}\label{experiment-2-discussion}}
+
+Looking at learning transfer by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
 Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
@@
 
-To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent.
-As a base model, we assume play is random, and each potential action is chosen with equal probability.
+To gain more insight into how participants played the games against the computer opponents, we estimated and compared different computational models of strategies the players may have been using to learn how to beat the opponent.
+The baseline model assumes play is random, and each potential action is chosen with equal probability.
 Note that this corresponds to the Nash equilibrium strategy.
@@
 We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
-We will use a simple temporal difference learning update rule:
+We will use a simple delta learning update rule:
 
@@
 Where \(V_{t}(a)\) is the value associated with action \(a\) at time \(t\), \(\alpha\) is the learning rate and \(R_{t}\) the reward at time t.
-Actions are chosen based on action values using a softmax choice rule.
+The probability of player \(i\) choosing action \(j\) at time \(t+1\) denoted by \(P_{i}^{j}(t+1)\) is based on action values using a softmax choice rule:
+
+\[P_{i}^{j}(t+1) = \frac{e^{\lambda . V_{t}^{j}(a)}}{\sum_{k=1}^{m_{i}}e^{\lambda . V_{t}^{k}(a)}} \]
 
@@
 
-In experiment 2, we allow this richer model to have a memory of the interaction.
-In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used.
-In another instance, we fit a model in which what was learned about an opponent in the first interaction is transfered to the first round of the second interaction, so there is a within-game trasnfer of Q-values allowed (QLS-within).
-We fit both models to all participant's data in the second experiment where both opponents are faced.
-
 \hypertarget{ewa-models}{%
@@
 Next, we use a self-tuning Experience Weighted attraction model (Ho, Camerer, \& Chong, 2004).
-EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning.
+EWA models particularity is that they nest two seemingly different approaches, namely reinforcement learning and belief learning.
 Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
@@
 Strategies actually played by i in period t, are denoted \(s_{i}(t)\), while the opponent's strategy at time t is denoted \(s_{-i}(t)\).
-After playing \(s_{i}^{j}\) at time \(t\), player i payoff is denoted \(\pi_{i}(s_{i}^{j},s_{-i}(t))\), and the actual payoff the player received is \(\pi_{i}(t)\).
+After playing \(s_{i}^{j}\) at time \(t\), player i pay-off is denoted \(\pi_{i}(s_{i}^{j},s_{-i}(t))\), and the actual pay-off the player received is \(\pi_{i}(t)\).
 
@@
 
-The attractions are updated over every time step \(t\) using the followng update rule :
+The attractions are updated over every time step \(t\) using the following update rule :
 
@@
 
-Here, I(x,y) is the indicator function equal to 1 if \$ x = y\$ and 0 otherwise.
-A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince (\(N(t-1)\)) which is itself decaying by a wight \(\phi\).
-The result is added to either the payoff received (when the indicator function is 0), or to \(\delta\) times the foregone payoff (when indicator function is 1).
-We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play (Cheung \& Friedman, 1994).
+Here, I(x,y) is the indicator function equal to 1 if \(x = y\) and 0 otherwise.
+A simple way to think about this update rule is that attractions are multiplied by a parameter that represents experience (\(N(t-1)\)) which is itself decaying by a weight \(\phi\).
+The result is added to either the pay-off received (when the indicator function is 0), or to \(\delta\) times the foregone pay-off (when indicator function is 1).
+We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play (Cheung \& Friedman, 1994).
 While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Ho et al., 2004).
@@
 We use values of k in \({0,1,2}\).
+These models also assume the opponent can deviate from these level-k strategies and play randomly with probability \(\theta\), a parameter to be fit.
 We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
 In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between trasnfer)
+In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between transfer)
 
@@
 We fit the above two models to experiment 1 data.
-In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive).
-And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
-
-In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).
+In experiment two, on top of these two models, we fit another model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
+
+\hypertarget{estimation-and-model-comparison}{%
+\subsubsection{Estimation and model comparison}\label{estimation-and-model-comparison}}
+
 In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
@@
 
-Figure~\ref{fig:exp1-comp-models} shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-comp-models-1}
+Figure~\ref{fig:exp1-comp-models} shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning with states defined by last round play.
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:exp1weightstable}Experiment one Average BIC weights and number of participants best fit by model}
+\begin{tabular}{llllll}
+\toprule
+ & \multicolumn{1}{c}{Nash} & \multicolumn{1}{c}{ToM\_BT} & \multicolumn{1}{c}{ToM\_NBT} & \multicolumn{1}{c}{QL\_states} & \multicolumn{1}{c}{STEWA\_States}\\
+\midrule
+Model BIC weights & 0.10 & 0.07 & 0.05 & 0.73 & 0.05\\
+Count best fit & 8.00 & 1.00 & 3.00 & 39.00 & 1.00\\
+\bottomrule
+\end{tabular}
+\end{threeparttable}
+\end{center}
+\end{table}
+
+Table ~\ref{tab:exp1weightstable} shows the model BIC weights as well as the number of participants best fit by each model.
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-comp-models-1}
 
@@
 Figure~\ref{fig:exp1-cumScores} shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (witout transfer), followed by Q-learning conditional on last round play.
+We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (without transfer), followed by Q-learning conditional on last round play.
 EWA, QL and random players had, understandably the lowest performance.
@@
 
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-cumScores-1}
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-cumScores-1}
 
@@
 \caption{Experiment 1 - Average cumulative scores of participants by best fitting model}\label{fig:exp1-cumScores}
-\end{figure}
-
-However, this is at odds with the findings from the previous section regarding learning transfer: If indeed most participants use Q-learning with states to choose their actions, then they should not be able to transfer learning to the early rounds of the new game.
-In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Theory of Mind models with and without the possibility of across game transfer.
-
-Figure~\ref{fig:exp1-lik-by-tr} shows that in the later games, the likelihood for the ToM models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of ToM models.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-lik-by-tr-1}
-
-}
-
-\caption{Experiment 1 Likelihood by trial by game and opponent faced}\label{fig:exp1-lik-by-tr}
 \end{figure}
@@
 
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-comp-models-1}
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-comp-models-1}
 
@@
 
-In experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that Q-learning with the aforementioned state-space was again more successful than the bayesian models in fitting player's action choices.
-In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) did not fit players observed data as well.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-cumScores-1}
+\begin{verbatim}
+##                Nash TOM BT TOM NBT TOM NT QLS NT QLS Tr STEWA NT STEWA Tr
+## BIC weights    0.13   0.02    0.06   0.06   0.18   0.49     0.04     0.03
+## Count best fit 9.00   0.00    2.00   3.00   8.00  27.00     1.00     0.00
+\end{verbatim}
+
+\begin{table}
+
+\caption{\label{tab:exp2-weights-table}Experiment 2 - Average BIC weights and number of participants best fit by model}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
+\hline
+  & Nash & TOM BT & TOM NBT & TOM NT & QLS NT & QLS Tr & STEWA NT & STEWA Tr\\
+\hline
+BIC weights & 0.13 & 0.02 & 0.06 & 0.06 & 0.18 & 0.49 & 0.04 & 0.03\\
+\hline
+Count best fit & 9.00 & 0.00 & 2.00 & 3.00 & 8.00 & 27.00 & 1.00 & 0.00\\
+\hline
+\end{tabular}}
+\end{table}
+
+In experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that Q-learning with the aforementioned state-space was again more successful than the Bayesian models in fitting player's action choices.
+In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
+This is also reflected in BIC weights in Table ~\ref{tab:exp2-weights-table}
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-cumScores-1}
 
@@
 
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
-Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance (although it only fit 2 participants best), followed by a model in which both within and between trasnfer of opponent models is allowed (BT).
-The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive).
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a ToM model of learning the opponent strategy had the highest cumulative performance.
+Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance (although it only fit 2 participants best), followed by a model in which both within and between transfer of opponent models is allowed (BT).
+The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where players reset opponent models at each stage of each game (NT).
 As expected, random play was at the bottom of cumulative performance.
-
-As in experiment 1, we want to understand the dynamic of strategy choice by plotting the likelihood by trial for each strategy, using the optimal parameters found when fitting the model.
-Figure~\ref{fig:exp2-lik-by-tr} shows that, as in experiment 1, ToM models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
-In the third and mosre dissimilar game, we get a result that is different from experiment 1.
-In this instance, the likelihoods of the ToM models stay constant and close to their initial values.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-lik-by-tr-1}
-
-}
-
-\caption{Experiment2 likelihood by trial by game and opponent faced}\label{fig:exp2-lik-by-tr}
-\end{figure}
 
@@
 
+The computational modelling indicates that most players are best fit by Q-learning type models with states defined by last round play.
+This is at odds with the findings from the section regarding learning transfer: If indeed most participants use Q-learning with states to choose their actions, then they should not be able to transfer learning to the early rounds of the new game.
+In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Theory of Mind models with and without the possibility of across game transfer.
+
+We start with experiment 1 data.
+Figure~\ref{fig:exp1-lik-by-tr} shows that in the later games, the likelihood for the ToM models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of ToM models.
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-lik-by-tr-1}
+
+}
+
+\caption{Experiment 1 Likelihood by trial by game and opponent faced}\label{fig:exp1-lik-by-tr}
+\end{figure}
+
+Likewise, in experiment 2, we want to understand the dynamic of strategy choice by plotting the likelihood by trial for each strategy, using the optimal parameters found when fitting the model.
+Figure~\ref{fig:exp2-lik-by-tr} shows that, as in experiment 1, ToM models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
+In the third and more dissimilar game, we get a result that is different from experiment 1.
+In this instance, the likelihoods of the ToM models stay constant and close to their initial values.
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-lik-by-tr-1}
+
+}
+
+\caption{Experiment2 likelihood by trial by game and opponent faced}\label{fig:exp2-lik-by-tr}
+\end{figure}
+
 The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative of participants switching between strategies as the games progressed.
-Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the ToM based strategies fit observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
-
-In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q learning with state space consisting of previous round play, ToM based model with and without opponent model transfer).
+Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the ToM based strategies fitted observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
+
+In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q-learning with state space consisting of previous round play, ToM based model with opponent model transfer, and a base model consisting of random play consistent with a Nash equilibrium strategy).
 Hidden Markov models are useful tools to explore structure in observed time series.
-They are named because of two properties: First, they make the assumption that any observable action at time t results from a process whose state at time t , named \(S_{t}\) is \enquote{hidden} from the observer.
-Second, it also assumes that this hidden process has a Markov property, meaning that given state \(S_{t-1}\), the value of \(S_{t}\) is independent of all states occuring before time \(t-1\).
+They are named as such because of two properties: First, they make the assumption that any observable action at time t results from a process whose state at time t , named \(S_{t}\) is \enquote{hidden} from the observer.
+Second, it also assumes that this hidden process has a Markov property, meaning that given state \(S_{t-1}\), the value of \(S_{t}\) is independent of all states occurring before time \(t-1\).
 We also assume that \(S_{t}\) has a discrete probability distribution in that it take one of K discrete values.
 The model is therefore specified by initial probabilities of being in each state \({1,2,...,K}\) and transition probabilities for moving from state \(i\) to state \(j\).
-These probabilities are fit using obsserved actiosn generated from these hidden states.
-
-sing the R DepmixS4 package, we fit a total of two HMMs.
+These probabilities are fit using observed actions generated from these hidden states.
+
+To investigate the possibility of strategy switching, we fit two different hidden Markov models with the depmixS4 R package.
 In the first model, we allow for a non-nil probability of players transitioning from one state (strategy) to another.
-In the second model, we assume that such switching does not happen, and as such assume implicitly that when players start with a particular strategy, they continue using it throughout the game.
-We then compare the likleihoods of each HMM model using a likelihood ration test.
+In the second model, we assume that such switching does not happen, and as such assume implicitly that when players start with a particular strategy, they continue using it throughout the experiment.
+We then compare the likelihoods of each HMM model using a likelihood ratio test.
 
@@
 
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp1-posteriors-plot-1}
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-posteriors-plot-1}
 
@@
 
-In experiment 1, the HMM model with swithcing has a significantly higher likelihood than the non-switching one (p-value = 0.00).
+In experiment 1, the HMM model with switching fits significantly better than the non-switching one (\(p < .001\)).
 This is further statistical evidence in favour of the hypothesis that participants switch between strategies.
-In order to understand at which stage of the games the switching might happen, and whether there are any differences between games and type of opponents faced, we plot in Figure~\ref{fig:exp1-posteriors-plot} the average (across participants) posterior probabilities given our HMM trial by trial for each game and opponent faced.
-Th eposterior probability is the probability that an observation comes from a component distribution a posteriori, i.e.~given the value of the observation.
+In order to understand at which stage of the games the switching might happen, and whether there are any differences between games and type of opponents faced, we plot in Figure~\ref{fig:exp1-posteriors-plot} the average (across participants) posterior probabilities of each state (strategy), as a function of trial and opponent faced.
+The posterior probability is the probability that an observation comes from a component distribution a posteriori, i.e.~given the value of the observation.
 In the first experiment, we can see from the plots of fwg and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the QLS model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
@@
 
-{\centering \includegraphics{draft_report_v2_files/figure-latex/exp2-posteriors-plot-1}
+{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-posteriors-plot-1}
 
@@
 
-The switching model in experiment two has also significantly higher likelihood (p-value = 0.00).
-On top of indications from looking at the liklihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
-The posterior probability plot in Figure~\ref{fig:exp2-posteriors-plot} shows switching much more clearly across games ans stages, indicating a robust process.
-The switchign also seems to happen very early one at the beginning of each game and stage, and is also consistently in the same direction: The probability of Bayesian models with transfer being initially high, then decreasing rapidly while the posterior probability of QL-Learning with states and within transfer learning increases rapidly.
+The switching model in experiment two has also significantly higher likelihood (\(p\) = 0.00).
+On top of indications from looking at the likelihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
+The posterior probability plot in Figure~\ref{fig:exp2-posteriors-plot} shows switching much more clearly across games and stages.
+The switching also seems to happen very early on at the beginning of each game and stage, and is also consistently in the same direction: The probability of Bayesian models with transfer being initially high, then decreasing rapidly while the posterior probability of QL-Learning with states and within transfer learning increases rapidly.
+
+Therefore, HMM modelling shows clear evidence in favour of strategy switching by participants, specifically after a few rounds of play.
+The strategy switching is consistently from ToM models towards Q-learning with states models in both experiments.
 
@@
 In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies.
-We were interested in uncovering evidence for transfer and exploring whether it is modulated by the degree of similarity between games and the sophistication of the agent.
+We were interested in exploring whether participants learn about the strategy of their opponent and transfer such knowledge between games, and whether this is modulated by the similarity between games and the sophistication of the agent.
 
 The results of our first online experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
-We found that using results on very early rounds is a better proxy for measuring transfer as it is not tainted by any within game learning.
+We used results on very early rounds for measuring transfer as they are unlikely to be tainted by any within game learning.
 Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
 
-In the second online experiment, the paradigm was better suited to explore our main research question, related to learning transfer rather than within-game learning.
-Indeed, when facing two opponents sequentially, there are many more opportunities to test transfer than before.
-Indeed, there are 2 opportunities to transfer knowledge within each game, and a total of three games, which means 6 opportunities to test transfer.
-When we made players face only one type of opponent each, we only had two possible learning transfers to test.
-In that regard, the results on learning transfer confirmed prior findings from the first experiment.
-While there was no evidence of learning transfer across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
+In the second online experiment, there were many more opportunities to test transfer than before: 2 opportunities to transfer opponent models within each game, and a total of three games, which means 6 opportunities to test transfer.
+The results on learning transfer confirmed prior findings from the first experiment.
+While there was no evidence of higher scores across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
 We also found that learning transfer is modulated by the type of opponent faced.
@@
 
-Coming back to evidence for learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
+Coming back to learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are significantly higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
 The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
-what did the players learn exactly about the opponent strategy and what form did this learning take?
+what did the players learn specifically about the opponent strategy and what form did this learning take?
 
@@
 First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
-An example is a spatial heuristic that consists of choosing \enquote{weapons} in a particular order (for instance left to right).
+An example is a spatial heuristic that consists of choosing \enquote{weapons} in a particular order.
+For instance, it is possible to keep winning against a level-k opponent by choosing actions in a particular spatial order such as cycling through them from left to right.
 This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
@@
 
-A second possible hypothesis for learning the opponent's strategy is the use of simple rules based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc\ldots{}).
+A second possible hypothesis for learning the opponent's strategy is the use of simple rules based on last round play (for instance, I play scissors whenever opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc\ldots{}).
 Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
 While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
-Indeed, learning the best action in a particular state cannot easily transfer to a new game since the state space is different and there is no simgle mapping between the state spaces of the initial and latter games.
-These rules would thereofre need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
+Indeed, learning the best action in a particular state is not transferable to a new game since the state space is different and there is no single mapping between the state spaces of the initial and latter games.
+These rules would therefore need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
 
@@
 Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
-After all, if players were using some type of associative learning or spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
-The fact that the degree of sophisitication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
+More specifically, if we assume that participants were using some type of associative learning or relying on spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
+To be sure, if a participant learns to pick say \enquote{scissors} whenever the opponent last picked \enquote{rock}, then the degree of strategic sophistication of the opponent (its level k) should not impact this learning, and we would expect in this case there would be no difference between scores when facing level-1 and level-2 opponents, which is not the case here.
+The fact that the degree of sophistication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
 
@@
 Our second experimental design allows us to test whether the first explanation holds.
-Since there is a simple transferable heuristic that works agaisnt level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
+Since there is a simple transferable heuristic that works against level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
 Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.
 
-Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first intractions across games and using early rounds analysis.
-Based on our assumptions, we conclude that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the ourse of learning.
+Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first interactions across games and using early rounds analysis.
+Based on our assumptions, we conclude therefore that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the course of learning.
 
 Our computational modelling allowed us to delve deeper into what might be driving the observed learning transfer.
-Initial modelling of observations using all available data seems to indicated that the most likely model was a Q-learning type model.
+Initial modelling of observations using all available data seems to indicate that the most likely model was a Q-learning type model.
 However, as we argued above, that would be inconsistent with the evidence for learning transfer.
-Breaking down likelihoods by trial and fitting a hidden markov model to the data with states being the various strategies that participants are assumes to be using, we showed evidence for within game switching of strategies.
+Breaking down likelihoods by trial and fitting a hidden markov model to the data with states being the various strategies that participants are assumed to be using, we showed evidence for within game switching of strategies.
 Participants start the early rounds of a new game acting in a way consistent with a Bayesian Theory of mind level, which would be accurate and generalisable but computationally expensive.
@@
 When a new game is started that is similar to a previously played game with the same opponent, participants need a way to transfer prior knowledge of the opponent and apply it to the new game in order to best respond.
-Adopting a Bayesian model based on ToM achieves the goal of trasnfering the opponent model and thus coming up with best responses in the early trials.
-However, Bayesian ToM models are computationally expensive and require a lot of higher order thinking (I think that you think that I think\ldots{}).
-As such, as the games progresses, they become burdensome and the higher amount of historical interaction in the new game allows participants to have enough data to start using the cognitively cheaper model-free learning strategies such as Q-learning.
-The bias towards less computationally demanding strategies is well established Wouter Kool, Joseph T.
+Adopting a Bayesian model based on ToM achieves the goal of transferring the opponent model and thus coming up with best responses in the early trials.
+However, Bayesian ToM models are computationally expensive and require higher order thinking (I think that you think that I think\ldots{}).
+As such, as the games progresses, they may become burdensome and the higher amount of historical interaction in the new game allows participants to have enough data to start using the cognitively cheaper model-free learning strategies such as Q-learning.
+The preference for less computationally demanding strategies is well established (Wouter Kool, Joseph T.
 McGuire, Zev B.
 Rosen, Matthew M.
-Bovinick (2011).
-Moreover, the ability to flexibly switch is also consistent with evidence from the literature on learning strategies in humans, showing that they indeed shift between model-based and model-free learning when the environment requires it Simon \& Daw (2011).
+Bovinick, 2011).
+Moreover, the ability to flexibly switch is also consistent with evidence from the literature on learning strategies in humans, showing that they indeed shift between model-based and model-free learning when the environment requires it (Simon \& Daw, 2011).
 
@@
 
-Our online experiments confirm behavioural game theory results, stating that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
-Moreover, we showed that participants do transfer their learning to new games with varying degrees of similarity.
+Our online experiments results are consistent with behavioural game theory findings, in that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
+Moreover, we showed that participants transfer their learning to new games with varying degrees of similarity.
 The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.
@@
 There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
-Moreover, the computational modelling shows that it is likely that players start each game using a model-based learning strategy that facilitates generalisation and opponent model transfer, but then switch to behvior that is consistent with a model-free learning strategy as the experiment goes on.
+Moreover, the computational modelling shows that it is likely that players start each game using a model-based learning strategy that facilitates generalisation and opponent model transfer, but then switch to behaviour that is consistent with a model-free learning strategy as the experiment goes on.
 This is likely driven by a trade-off between computational complexity and accuracy between model based and model free strategies.
@@
 
+\leavevmode\hypertarget{ref-knez2000}{}%
+Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
+
 \leavevmode\hypertarget{ref-cheung1994learning}{}%
@@
 \leavevmode\hypertarget{ref-Cooper2008}{}%
-Cooper, D.
-J., \& Kagel, J.
-H.
-(2008).
-Learning and transfer in signaling games.
-\emph{Economic Theory}, \emph{34}(3), 415--439.
-doi:\href{https://doi.org/10.1007/s00199-006-0192-5}{10.1007/s00199-006-0192-5}
+Cooper, D. J., \& Kagel, J. H. (2008). Learning and transfer in signaling games. \emph{Economic Theory}, \emph{34}(3), 415--439. \url{https://doi.org/10.1007/s00199-006-0192-5}
 
@@
 \emph{Games and Economic Behavior}, \emph{74}(1), 208--221.
-doi:\href{https://doi.org/10.1016/j.geb.2011.06.001}{10.1016/j.geb.2011.06.001}
+\url{https://doi.org/10.1016/j.geb.2011.06.001}
 
 \leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). The economics of learning models: A self-tuning theory of learning in games.
+Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
 
@@
 \emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215.
-doi:\href{https://doi.org/10.1016/j.obhdp.2012.09.004}{10.1016/j.obhdp.2012.09.004}
+\url{https://doi.org/10.1016/j.obhdp.2012.09.004}
 
@@
 Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+
+\leavevmode\hypertarget{ref-perkins1992transfer}{}%
+Perkins, D. N., Salomon, G., \& Others. (1992). Transfer of learning. \emph{International Encyclopedia of Education}, \emph{2}, 6452--6457.
+
+\leavevmode\hypertarget{ref-premack1978does}{}%
+Premack, D., \& Woodruff, G. (1978). Does the chimpanzee have a theory of mind? \emph{Behavioral and Brain Sciences}, \emph{1}(4), 515--526.
 
@@
 Higher-order social cognition in rock-paper-scissors: A simulation study.
-In \emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3} (pp.
-1195--1196).
-
-\leavevmode\hypertarget{ref-Woodruff}{}%
-Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). Does the chimpanzee have a theory of mind.
+\emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3}, 1195--1196.
 
@@
 \emph{Experimental Psychology}.
-doi:\href{https://doi.org/10.2996/kmj/1138846322}{10.2996/kmj/1138846322}
+\url{https://doi.org/10.2996/kmj/1138846322}
 

### 2020-10-30 comp_model_1019.Rmd
draft3

@@
 #### New work 
-
-## Fitting simple Bayesian learning model with flat prior
-
-## Fit a bayesian model to observed human play. Prior is vector of possible level-k opponent strategies.
-```{r}
-# # Function to produce best reponse to ai_action 
-# best_response <- function(game,ai_action){
-#   if (game == "rps"){
-#     if (ai_action == "R") {return("P")}
-#     else if (ai_action == "P") {return("S")}
-#     else if (ai_action == "S") {return("R")}
-#   } else if (game == "fwg"){ 
-#     if (ai_action == "F") {return("W")}
-#     else if (ai_action == "W") {return("G")}
-#     else if (ai_action == "G") {return("F")}
-#   } else if (game == "numbers") {
-#     if (ai_action == "1") {return("2")}
-#     else if (ai_action == "2") {return("3")}
-#     else if (ai_action == "3") {return("4")}
-#     else if (ai_action == "4") {return("5")}
-#     else if (ai_action == "5") {return("1")}
-#   }
-# }
-# 
-# exp1_ToM <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {
-#   
-#   # dat = data subset for one participant
-#   # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
-#   # return = -2logLik 
-#   # or "likelihood_by_trial" vector  (for later plotting, etc)
-#   # opp_mod_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise. 
-#   
-#   # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
-#   # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
-#   theta <- par[1]
-#   eps <- par[2]
-#   
-#   num_strat = length(opp_strategy_vec) 
-#   
-#   # Load tables predicting oppponent move
-#   rps_predict_opp <- read.csv("rps_predict_opp.csv")
-#   fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
-#   numbers_predict_opp <- read.csv("numbers_predict_opp.csv")
-# 
-#   #lik_opp is a vector that holds and update probability distribution of opp strategy given actions.
-#   lik_opp <- matrix(0.0,num_strat, nrow(data))
-#   # Initiate prior vector as uniform
-#   opp_prior_vec <-rep(1/num_strat, num_strat)
-#   
-#   lik_hum <- matrix(0.0,nrow(data))
-#   # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
-#   br_hum <- rep(NA,num_strat)
-# 
-#   
-#   for(t in 1:nrow(data)) {
-#     t_game <- data[t,"game"]
-#     pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)
-#     
-#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
-#     if(data[t,"round"] == 1) {
-#       # first round is uniform prediction
-#       pred_opp <- NA
-#       lik_hum[t] <- 1/nopts
-#       ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer, reset prior to uniform)
-#       if (!(opp_mod_transfer)) {
-#         opp_prior_vec <- rep(1/num_strat, num_strat)
-#         lik_opp[,t] <- opp_prior_vec
-#         }
-#       
-#     # Rounds after first
-#     } else {
-#       # get prediction of opponent action from CSV files
-#       for (strategy in opp_strategy_vec) {
-#         k = match(strategy,opp_strategy_vec)
-#         pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])
-#         
-#         # Given opponent action predicted, what would be human action best response for each opp strat
-#         br_hum[[k]] <- best_response(t_game,as.character(pred_opp))
-#         
-#         # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
-#         if(as.character(data[t,"a_action"]) == pred_opp) {
-#           lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
-#         } else {
-#           lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
-#         }
-#       }
-#       # Get which opponent strategy human current actn maps to (if index = 0 then human current action is br to level-0 comp_strat...)
-#       indices <- which(br_hum %in% as.character(data[t,"h_action"]))
-# 
-#       # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
-#       # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
-#       if(length(indices) == 0){
-#         lik_hum[t] <- eps/nopts
-#       # if same br action for multiple possible ai opponents, add probabilities 
-#       } else {
-#         lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
-#       }
-#       # Standardising the probabilities and updating prior
-#       lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
-#       opp_prior_vec <- lik_opp[,t]
-#     }
-#     # for debugging uncomment the line below
-#     #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"\n")
-#   }
-#   if(return_value == "-2loglik") {
-#     ret <- -2*sum(log(lik_hum))
-#     if(is.infinite(ret) || is.nan(ret)) {
-#       return(1e+300)
-#     } else {
-#       return(ret)
-#     }
-#   }
-#   if(return_value == "likelihood_by_trial") return(lik_hum)
-# }
-# 
-# # data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
-# # exp1_ToM(c(0.9,0.99),data,c("level0","level1","level2"),"-2loglik",FALSE)
-# ```
-# 
-# ```{r}
-# # rps_predict_opp <- read.csv("rps_predict_opp.csv")
-# # red_opp <- filter(rps_predict_opp, rps_predict_opp$human_previous == "R" & rps_predict_opp$computer_previous == "S")
-# # 
-# # as.character(red_opp[["level0"]])
-# ```
-# 
-# 
-# 
-# # Fitting a bayesian model WITH BETWEEN GAME TRANSFER of opp strat distribution between games 
-# ```{r, cache=TRUE}
-# exp1_ToM_TR <- list()
-# for(id in unique(dat$human_id)) {
-#   exp1_ToM_TR[[id]] <- list()
-#   tdat <- subset(dat,human_id == id)
-#   
-#   # exp1_ToM_TR[[id]] <- DEoptim(fn=exp1_ToM, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))
-# 
-#   exp1_ToM_TR[[id]] <- optim(c(0.1,0.1),fn=exp1_ToM,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-# }
-# save(exp1_ToM_TR,file="exp1_ToM_TR.RData")
-# 
-# ```
-# 
-# 
-# # Fitting a bayesian model with NO BETWEEN GAME TRANSFER of opp strat distribution between games 
-# ```{r, cache =TRUE}
-# exp1_ToM_NT <- list()
-# for(id in unique(dat$human_id)) {
-#   exp1_ToM_NT[[id]] <- list()
-#   tdat <- subset(dat,human_id == id)
-#   
-#   # exp1_ToM_NT[[id]] <- DEoptim(fn=exp1_ToM, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
-# 
-#   exp1_ToM_NT[[id]] <- optim(c(0.1,0.1),fn=exp1_ToM,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE ,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-# }
-# 
-# save(exp1_ToM_NT,file="exp1_ToM_NT.RData")
-# 
-# ```
-# 
-# 
-# # Summarise results in dataframe for both transfer and no transfer models 
-# ```{r}
-# Nbayes_par_results <- data.frame()
-# for(id in unique(dat$human_id)) {
-# Nbayes_par_results <- rbind(Nbayes_par_results,
-#                        data.frame(
-#                          "id" = id,
-#                          "condition" = dat[dat$human_id==id,"condition"][1],
-#                          # BICs 
-#                          "BIC_transfer" = exp1_ToM_TR[[id]]$value + 2*log(150),
-#                          "BIC_no_transfer" = exp1_ToM_NT[[id]]$value+ 2*log(150),
-#                          # Theta is the parameter governing AI stochasticity. Truth is 0.9
-#                          "theta_transfer" = exp1_ToM_TR[[id]]$par[1],
-#                          "theta_no_transfer" = exp1_ToM_NT[[id]]$par[1],
-#                          # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
-#                          "eps_transfer" = exp1_ToM_TR[[id]]$par[2],
-#                          "eps_no_transfer" = exp1_ToM_NT[[id]]$par[2]))
-# }
-# 
-# #Plotting the theta/eps scatter for all participants...
-# plot(Nbayes_par_results$theta_transfer,Nbayes_par_results$eps_transfer, xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
-# # 
-# write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
-```
-
 ## Q-learning (Basic)
@@
       probs <- exp(Q_vals[curr_state,]/beta)/sum(exp(Q_vals[curr_state,]/beta))
+
       # Get actual human next action and compute likelihood
       act_index <- match(h_act, colnames(Q_vals))
-
       lik_hum[t] <- probs[[act_index]]
@@
 ```{r}
-# data34 <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")
+data34 <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")
+
 # Q_learn_states(c(5, 0.5),data34 ,return_value = "likelihood_by_trial",gamma = 0 )
@@
 
-##  Self-Tuning EWA with prior round play as state (Camerer & Ho 2007) 
-```{r}
-
-EWA_states <- function(par,data,return_value){
+##  First attempt : Self-Tuning EWA with prior round play as state (Camerer & Ho 2007) 
+```{r}
+# Initiates N(0) = 1 as in Camerer and Ho 1997 paper. 
+# 
+# EWA_states <- function(par,data,return_value){
+# 
+#   lambda <- par[1]
+# 
+#   #Define matrix of state spaces for each game 
+#   G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+#   states_RPS <- paste0(G1$Var1,G1$Var2)
+# 
+#   G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+#   states_FWG <- paste0(G2$Var1,G2$Var2)
+# 
+#   G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+#   states_NUM <- paste0(G3$Var1,G3$Var2)
+#   
+#   A_RPS = matrix(-0.5,9,3)
+#   dimnames(A_RPS) = list(states_RPS, c("R", "P", "S"))
+# 
+#   A_FWG = matrix(-0.5,9,3)
+#   dimnames(A_FWG) = list(states_FWG, c("F", "W", "G"))
+#   
+#   A_NUM = matrix(-0.5,25,5)
+#   dimnames(A_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
+# 
+#   
+#   # # Define reward matrices from the perspective of the row player (human in our case)
+#   reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+#   dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
+#   
+#   reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+#   dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
+#   
+#   reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
+#   dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+#   
+#   # Initiate likelihood by trial vector 
+#   lik_hum <- matrix(0.0,nrow(data))
+# 
+#   for(t in 1:nrow(data)) {
+#     t_game <- data[t,"game"]
+#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
+#     if(data[t,"round"] == 1) {
+#       Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
+#       state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, numbers = states_NUM)
+#       reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, numbers = reward_NUM)
+#       game_data <- subset(data, game == t_game)
+#       
+#       # first round is uniform prediction
+#       lik_hum[t] <- 1/nopts
+#       N <- 1.0
+# 
+#       R_t <- rep(0.0,nopts)
+#       H_t <- R_t
+#       
+#       # Randomly select prev_state and actions for first round
+#       curr_state <- sample(state_vec, size = 1)
+#       h_act_prev <- sample(colnames(Att), size =1)
+#       a_act_prev <- sample(colnames(Att), size =1)
+#       #reward <- 0 
+#       
+#     } else {
+#       
+#       indx <- data[t,"round"]
+#       state_indx <- match(curr_state,state_vec)
+#       #cat("this is the current state index", state_indx, "\n")
+#       
+#       # Get reward and past human action
+#       h_act_prev <- as.character(game_data[indx-1,"h_action"])
+#       a_act_prev <- as.character(game_data[indx-1,"a_action"])
+#       new_state <- paste0(h_act_prev,a_act_prev)
+# 
+#       # Estimate R(t) (recent history) then H(t) (history) then phi(t) (change detector)
+#       R_t <- as.numeric(colnames(Att) == a_act_prev)
+#       #cat("This is R(t)",R_t,"\n")
+#       
+#       H_t <- (H_t*(indx-2) + R_t)/(indx-1)
+#       #cat("this is H(t)",H_t,"\n")
+#       
+#       Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
+#       #cat("This is Phit(t)",Phi_t,"\t")
+#       
+#       # Estimate vector Delta(t)
+#       delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
+#       #cat("this is delta(t)",delta_t,"\n")
+#       
+#       for (i in 1:nopts) {
+#         action <- as.character(colnames(Att)[i])
+# 
+#         #cat("this is current indexed action",action,"\n")
+#         #cat("this is previous human action",h_act_prev,"\n")
+#         
+#         # Attraction vector update rule
+#         Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
+#       }
+#       
+#       #Update the value of N 
+#       N <- Phi_t*N + 1
+# 
+#       # Assume human chooses action probabilistically using softmax on Attraction values
+#       probs <- exp(lambda*Att[new_state,])/sum(exp(lambda*Att[new_state,]))
+#       
+#       # Get actual human action and compute likelihood
+#       h_act <- as.character(game_data[indx,"h_action"])
+#       act_index <- match(h_act, colnames(Att))
+#       lik_hum[t] <- probs[[act_index]]
+#       
+#       curr_state <- new_state
+#       
+#       # if (indx == 50) {
+#       #   cat("this is the attraction matrix at last round of", "\n")
+#       #   print(Att)
+#       # }
+#     }
+#   }
+#   
+#  if(return_value == "-2loglik") {
+#     ret <- -2*sum(log(lik_hum))
+#     if(is.infinite(ret) || is.nan(ret)) {
+#       return(1e+300)
+#     } else {
+#       return(ret)
+#     }
+#   }
+#   if(return_value == "likelihood_by_trial") return(lik_hum)
+# }
+
+```
+
+### Second attempt at ST_EWA with states and no initial guess of initial states. 
+```{r}
+ST_EWA_STATES <- function(par,data,return_value){
 
   lambda <- par[1]
-  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.
 
@@
     if(t_game == "numbers") nopts <- 5 else nopts <- 3
+
     if(data[t,"round"] == 1) {
@@
       game_data <- subset(data, game == t_game)
+
       # first round is uniform prediction
       lik_hum[t] <- 1/nopts
+      # Asumme N(0) = 1 for now...see discussion in paper
       N <- 1.0
-
-      R_t <- rep(0.0,nopts)
-      H_t <- R_t
-
-      # Randomly select prev_state and actions for first round
-      curr_state <- sample(state_vec, size = 1)
-      h_act_prev <- sample(colnames(Att), size =1)
-      a_act_prev <- sample(colnames(Att), size =1)
-      #reward <- 0
-
+      # initialize H_t by looking at first action 
+      # H_t <- rep(0.0,nopts)
+      a_act <- as.character(game_data[1,"a_action"])
+      H_t <- as.numeric(colnames(Att) == a_act)
+
+      # Rounds 2 to end 
     } else {
@@
       indx <- data[t,"round"]
-      state_indx <- match(curr_state,state_vec)
-      #cat("this is the current state index", state_indx, "\n")
 
@@
       a_act_prev <- as.character(game_data[indx-1,"a_action"])
-      new_state <- paste0(h_act_prev,a_act_prev)
-
-      # Estimate phi(t)
-      R_t <- as.numeric(colnames(Att) == a_act_prev)
+      curr_state <- paste0(h_act_prev,a_act_prev)
+
+      h_act <- as.character(game_data[indx,"h_action"])
+      a_act <- as.character(game_data[indx,"a_action"])
+      new_state <- paste0(h_act,a_act)
+
+      # Assume human chooses action probabilistically using softmax on Attraction values
+      probs <- exp(lambda*Att[curr_state,])/sum(exp(lambda*Att[curr_state,]))
+
+      # Get actual human action and compute likelihood
+      act_index <- match(h_act, colnames(Att))
+      lik_hum[t] <- probs[[act_index]]
+
+      # Update rule:
+      # Estimate R(t) (recent history) then H(t) (history) then phi(t) (change detector)
+      R_t <- as.numeric(colnames(Att) == a_act)
       #cat("This is R(t)",R_t,"\n")
 
-      H_t <- (H_t*(indx-2) + R_t)/(indx-1)
+      H_t <- (H_t*(indx-1) + R_t)/(indx)
       #cat("this is H(t)",H_t,"\n")
@@
       # Estimate vector Delta(t)
-
-      delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
+      delta_t <- as.numeric(reward[,a_act] >= as.numeric(game_data[indx,"score"]))
       #cat("this is delta(t)",delta_t,"\n")
 
-      for (i in 1:nopts) {
-        action <- as.character(colnames(Att)[i])
-
-        #cat("this is current indexed action",action,"\n")
-        #cat("this is previous human action",h_act_prev,"\n")
-
-        # Attraction vector update rule
-        Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
-      }
+      # This is a vectorised ST_EWA update rule, easier to follow the loop below in comments
+      state_indx <- match(curr_state,state_vec)
+      Att[state_indx,] <- (Phi_t*N*Att[state_indx,]  + ( delta_t + (1- delta_t)*(colnames(Att) == h_act))*as.numeric(reward[colnames(Att),a_act])) / (Phi_t*N + 1)
+
+      ##############
+      # for (i in 1:nopts) {
+      #   action <- as.character(colnames(Att)[i])
+      #   state_indx <- match(curr_state,state_vec)
+      #   #cat("this is the current state index", state_indx, "\n")
+      # 
+      #   # Attraction vector update rule
+      #   Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act))*as.numeric(reward[action,a_act])) / (Phi_t*N + 1)
+      # 
+      # }
+      # 
+      #cat("this is the current Att vector", Att, "\n")
+      ###################
 
@@
 
-      # Assume human chooses action probabilistically using softmax on Attraction values
-      probs <- exp(lambda*Att[new_state,])/sum(exp(lambda*Att[new_state,]))
-
-      # Get actual human action and compute likelihood
-      h_act <- as.character(game_data[indx,"h_action"])
-      act_index <- match(h_act, colnames(Att))
-      lik_hum[t] <- probs[[act_index]]
-
+      #Update the state 
       curr_state <- new_state 
-
-      # if (indx == 50) {
-      #   cat("this is the attraction matrix at last round of", "\n")
-      #   print(Att)
-      # }
-    }
-  }
-
+    }
+   }  
   if(return_value == "-2loglik") {
@@
   if(return_value == "likelihood_by_trial") return(lik_hum)
-}
+
+}
+
+```
+
+```{r}
+# data12 = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
+# ST_EWA_STATES(0.5, data12, "-2loglik")
+# optim(10.0,fn=ST_EWA_STATES,gr = NULL, data=data12,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
 
@@
 ```{r, cache=TRUE}
-# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
-# EWA_states(0.1, data, "-2loglik")
-# optim(10.0,fn=EWA_states,gr = NULL, data=data,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
-
-EWA_states_modelling <- list()
+
+ST_EWA_STATES_modelling <- list()
 for(id in unique(dat$human_id)) {
-  EWA_states_modelling[[id]] <- list()
+  ST_EWA_STATES_modelling[[id]] <- list()
   tdat <- subset(dat,human_id == id)
-#   EWA_states_modelling[[id]] <- optim(10.0,fn=EWA_states,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
-# }
-  EWA_states_modelling[[id]] <- DEoptim(fn=EWA_states, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
-}
-
-save(EWA_states_modelling,file="EWA_states_modelling.RData")
+#   ST_EWA_STATES_modelling[[id]] <- optim(10.0,fn=ST_EWA_STATES,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
+# }
+  ST_EWA_STATES_modelling[[id]] <- DEoptim(fn=ST_EWA_STATES, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
+}
+
+save(ST_EWA_STATES_modelling,file="ST_EWA_STATES_modelling.RData")
 
@@
 # load("MBM_modelling.RData")
-# load("EWA_states_modelling.RData")
+# load("ST_EWA_STATES_modelling.RData")
 
@@
                           # Parametric EWA BIC
-                         "EWA_self_2LL" = EWA_self_modelling[[id]]$optim$bestval,
-                         "EWA_self_BIC" = EWA_self_modelling[[id]]$optim$bestval + 1*log(150),
-                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
-                         "EWA_self_Lambda" = EWA_self_modelling[[id]]$optim$bestmem[1],
-
-                         # EWA with states
-
-                         "EWA_states_BIC" = EWA_states_modelling[[id]]$optim$bestval + 1*log(150),
-                         "EWA_states_Lambda" = EWA_states_modelling[[id]]$optim$bestmem[1]
+                         # "EWA_self_2LL" = EWA_self_modelling[[id]]$optim$bestval,
+                         # "EWA_self_BIC" = EWA_self_modelling[[id]]$optim$bestval + 1*log(150),
+                         # #Lambda is a parameter of the softmax choice function (inverse Temperature)
+                         # "EWA_self_Lambda" = EWA_self_modelling[[id]]$optim$bestmem[1],
+
+                         # self_tuning EWA with states
+
+                         "ST_EWA_STATES_BIC" = ST_EWA_STATES_modelling[[id]]$optim$bestval + 1*log(150),
+                         "ST_EWA_STATES_Lambda" = ST_EWA_STATES_modelling[[id]]$optim$bestmem[1]
 
@@
 
-comp_BICs <- All_results[c("ID","Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")]
+comp_BICs <- All_results[c("ID","Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","ST_EWA_STATES_BIC")]
 
@@
 
-Table_results <- table(All_results[, "condition"],c("random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])
+# Table_results <- table(All_results[, "condition"],c("random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","ST_EWA_STATES")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","ST_EWA_STATES_BIC")],1,which.min)])
+
+# We choose to omit the simple QL and EWA and opt to only include the ones with states as they are more relevant.
+
+Table_results <- table(All_results[, "condition"],c("random","ToM_BT","ToM_NBT", "QL_states","ST_EWA_STATES")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])
 
@@
   id_results <- subset(All_results, ID == id)
-  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)
-
-  best_model <- c("random","ToM_Game_Tr","ToM_No_Tr","QL", "QL_states","EWA","S_EWA", "EWA_states")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)]
-  # 
+  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,min)
+
+  best_model <- c("random","ToM_Game_Tr","ToM_No_Tr", "QL_states","ST_EWA_STATES")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)]
+
   exp1_model_comp <- rbind(exp1_model_comp,
@@
 
+# More exploratory work......
+
 ## Let's compare total scores of each participant by the model of best fit, see if Bayes+transfer total scores are higher than Bayes + no transfer

### 2021-04-22 HMM/HMM-results.Rmd
initial hidden Markov analysis completed

---
title: "Strategy switching HMM analysis"
author: "Maarten Speekenbrink"
date: "19/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(depmixS4)
library(dplyr)
library(tidyr)
library(ggplot2)
source("dummy-HMM.R")
source("Qlearn-HMM.R")
source("ToM-HMM.R")
```

# Hidden Markov model

Three strategies:

- Random actions (Nash); This model has no parameters
- Bayesian cognitive hierarchy learning (formerly known as Theory of Mind); This model has a single parameter: $0.5 \leq \alpha \leq 1$, which is the probability that the opponent is assumed to follow their cognitive hierarchy level. Participants are assumed to probability match best responses to this. 
- Q-learning. This model has two parameters: $0 \leq \alpha \leq 1$, the learning rate, and $0 \leq \beta \leq 1000$, the temperature in the softmax response function.

We fitted two versions:

- a model which allows for strategy swtiches within a game. This model also estimates the starting probability for each strategy (2 parameters) and the transition probabilities between states (6 free parameters)
- a restricted versions without switches, which assumes that within a game, a single strategy is used. This model doesn't estimate transition probabilities, and just uses two free parameters to estimate the initial state probabilities.

We fitted the models to all participants (assuming the model parameters are identical over participants), and for each participant separately. The latter allows parameters to differ between participants (which is good) but it may also be prone to overfitting (which is bad). Estimation was done using the `donlp2` numerical optimization routine.

# Results

## Experiment 1

The switching model for all participants:
```{r}
load("newHMMs-exp1.RData")
summary(fmod_all)
```
The non-switching model for all participants:
```{r}
summary(fmod_all_noswitch)
```

The switching model had a BIC of `r prettyNum(BIC(fmod_all))`, whilst the no-switching version had a BIC of `r prettyNum(BIC(fmod_all_noswitch))`, meaning the former fitted better. This is thus evidence for within-game switching.

```{r}
dat <- read.csv("../data20180719.csv")
tmp <- forwardbackward(fmod_all)
dat$pS1 <- tmp$gamma[,1]
dat$pS2 <- tmp$gamma[,2]
dat$pS3 <- tmp$gamma[,3]
dat %>%
  dplyr::select(human_id, condition, game, round, pS1, pS2, pS3) %>%
  group_by(human_id, condition, game, round) %>%
  pivot_longer(cols=starts_with("pS"), names_to = "strategy", values_to = "probability") %>%
  group_by(strategy, condition, game, round) %>%
  summarise(p = mean(probability)) %>%
  mutate(strategy = recode_factor(strategy, pS1 = "Nash", pS2 = "BCH", pS3 = "Q")) %>%
  mutate(game = factor(game, levels = c("rps","fwg","numbers"))) %>%
  ggplot(aes(x=round, y = p, group=strategy, colour=strategy)) + geom_line() + facet_wrap(condition~game) + ylab("probability")
```

Individual models

```{r}
res <- data.frame()
for(i in 1:length(fmod_ind)) {
  pars <- getpars(fmod_ind[[i]])[13:15]
  tab <- table(posterior(fmod_ind[[i]])[,1])
  res <- rbind(res,
               data.frame(id=i, BCH_alpha = pars[1], Q_alpha = pars[2], Q_beta = pars[3], n_S1 = as.numeric(tab["1"]), n_S2 = as.numeric(tab["2"]), n_S3 = as.numeric(tab["3"]), AIC = as.numeric(-2*logLik(fmod_ind[[i]]) + 2*11), BIC = as.numeric(-2*logLik(fmod_ind[[i]]) + 11*log(150))))
}
res_ind <- res

res <- data.frame()
for(i in 1:length(fmod_ind_noswitch)) {
  pars <- getpars(fmod_ind_noswitch[[i]])[13:15]
  tab <- table(posterior(fmod_ind_noswitch[[i]])[,1])
  res <- rbind(res,
               data.frame(id=i, BCH_alpha = pars[1], Q_alpha = pars[2], Q_beta = pars[3], n_S1 = as.numeric(tab["1"]), n_S2 = as.numeric(tab["2"]), n_S3 = as.numeric(tab["3"]), AIC = as.numeric(-2*logLik(fmod_ind_noswitch[[i]]) + 2*5), BIC = as.numeric(-2*logLik(fmod_ind_noswitch[[i]]) + 5*log(150))))
}
res_ind_noswitch <- res
```

According to the BIC, the switching version fitted better than the no switching version for `r sum(res_ind$BIC < res_ind_noswitch$BIC)` out of `r nrow(res_ind)` participants. According to the AIC, the switching version fitted better than the no switching version for `r sum(res_ind$AIC < res_ind_noswitch$AIC)` out of `r nrow(res_ind)` participants. On an individual level, the six additional parameters required to model the state transitions are thus not entirely justified, which is unsurprising, given the relatively little number of observations and expected switches.

```{r}
ind_states <- data.frame()
for(i in 1:length(fmod_ind)) {
  tmp <- forwardbackward(fmod_ind[[i]])
  tdat <- data.frame(pS1 = tmp$gamma[,1],
                     pS2 = tmp$gamma[,2],
                     pS3 = tmp$gamma[,3])
  ind_states <- rbind(ind_states,tdat)
}
ind_states <- cbind(dplyr::select(dat,human_id, condition, game, round),ind_states)
ind_states %>%
  dplyr::select(human_id, condition, game, round, pS1, pS2, pS3) %>%
  group_by(human_id, condition, game, round) %>%
  pivot_longer(cols=starts_with("pS"), names_to = "strategy", values_to = "probability") %>%
  group_by(strategy, condition, game, round) %>%
  summarise(p = mean(probability)) %>%
  mutate(strategy = recode_factor(strategy, pS1 = "Nash", pS2 = "BCH", pS3 = "Q")) %>%
  mutate(game = factor(game, levels = c("rps","fwg","numbers"))) %>%
  ggplot(aes(x=round, y = p, group=strategy, colour=strategy)) + geom_line() + facet_wrap(condition~game) + ylab("probability")
```

Parameter estimates

```{r}
res_ind %>%
  mutate(condition = filter(dat, round == 1 & game == "rps")$condition) %>%
  group_by(id,condition) %>%
  pivot_longer(cols=c("BCH_alpha", "Q_alpha", "Q_beta"), names_to = "parameter", values_to = "estimate") %>%
  ggplot(aes(x=estimate)) + geom_histogram(bins=20) + facet_grid(condition ~ parameter, scales = "free")

```

## Experiment 2

The switching model for all participants:
```{r}
load("newHMMs-exp2.RData")
summary(fmod_all)
```
The non-switching model for all participants:
```{r}
summary(fmod_all_noswitch)
```

The switching model had a BIC of `r prettyNum(BIC(fmod_all))`, whilst the no-switching version had a BIC of `r prettyNum(BIC(fmod_all_noswitch))`, meaning the former fitted better. This is thus evidence for within-game switching.

```{r}
dat <- read.csv("../Experiment_2/MyData.csv")
dat$round <- 1:60
tmp <- forwardbackward(fmod_all)
dat$pS1 <- tmp$gamma[,1]
dat$pS2 <- tmp$gamma[,2]
dat$pS3 <- tmp$gamma[,3]
dat %>%
  dplyr::select(human_id, condition, game, round, pS1, pS2, pS3) %>%
  group_by(human_id, condition, game, round) %>%
  pivot_longer(cols=starts_with("pS"), names_to = "strategy", values_to = "probability") %>%
  group_by(strategy, condition, game, round) %>%
  summarise(p = mean(probability)) %>%
  mutate(strategy = recode_factor(strategy, pS1 = "Nash", pS2 = "BCH", pS3 = "Q")) %>%
  mutate(game = factor(game, levels = c("rps","fwg","shootout"))) %>%
  ggplot(aes(x=round, y = p, group=strategy, colour=strategy)) + geom_line() + facet_wrap(condition~game) + ylab("probability")
```

Individual models

```{r}
res <- data.frame()
for(i in 1:length(fmod_ind)) {
  pars <- getpars(fmod_ind[[i]])[13:15]
  tab <- table(posterior(fmod_ind[[i]])[,1])
  res <- rbind(res,
               data.frame(id=i, BCH_alpha = pars[1], Q_alpha = pars[2], Q_beta = pars[3], n_S1 = as.numeric(tab["1"]), n_S2 = as.numeric(tab["2"]), n_S3 = as.numeric(tab["3"]), AIC = as.numeric(-2*logLik(fmod_ind[[i]]) + 2*11), BIC = as.numeric(-2*logLik(fmod_ind[[i]]) + 11*log(180))))
}
res_ind <- res

res <- data.frame()
for(i in 1:length(fmod_ind_noswitch)) {
  pars <- getpars(fmod_ind_noswitch[[i]])[13:15]
  tab <- table(posterior(fmod_ind_noswitch[[i]])[,1])
  res <- rbind(res,
               data.frame(id=i, BCH_alpha = pars[1], Q_alpha = pars[2], Q_beta = pars[3], n_S1 = as.numeric(tab["1"]), n_S2 = as.numeric(tab["2"]), n_S3 = as.numeric(tab["3"]), AIC = as.numeric(-2*logLik(fmod_ind_noswitch[[i]]) + 2*5), BIC = as.numeric(-2*logLik(fmod_ind_noswitch[[i]]) + 5*log(180))))
}
res_ind_noswitch <- res
```

According to the BIC, the switching version fitted better than the no switching version for `r sum(res_ind$BIC < res_ind_noswitch$BIC)` out of `r nrow(res_ind)` participants. According to the AIC, the switching version fitted better than the no switching version for `r sum(res_ind$AIC < res_ind_noswitch$AIC)` out of `r nrow(res_ind)` participants. On an individual level, the six additional parameters required to model the state transitions are thus not entirely justified, which is unsurprising, given the relatively little number of observations and expected switches.

```{r}
ind_states <- data.frame()
for(i in 1:length(fmod_ind)) {
  tmp <- forwardbackward(fmod_ind[[i]])
  tdat <- data.frame(pS1 = tmp$gamma[,1],
                     pS2 = tmp$gamma[,2],
                     pS3 = tmp$gamma[,3])
  ind_states <- rbind(ind_states,tdat)
}
ind_states <- cbind(dplyr::select(dat,human_id, condition, game, round),ind_states)
ind_states %>%
  dplyr::select(human_id, condition, game, round, pS1, pS2, pS3) %>%
  group_by(human_id, condition, game, round) %>%
  pivot_longer(cols=starts_with("pS"), names_to = "strategy", values_to = "probability") %>%
  group_by(strategy, condition, game, round) %>%
  summarise(p = mean(probability)) %>%
  mutate(strategy = recode_factor(strategy, pS1 = "Nash", pS2 = "BCH", pS3 = "Q")) %>%
  mutate(game = factor(game, levels = c("rps","fwg","shootout"))) %>%
  ggplot(aes(x=round, y = p, group=strategy, colour=strategy)) + geom_line() + facet_wrap(condition~game) + ylab("probability")
```

Parameter estimates

```{r}
res_ind %>%
  mutate(condition = filter(dat, round == 1 & game == "rps")$condition) %>%
  group_by(id,condition) %>%
  pivot_longer(cols=c("BCH_alpha", "Q_alpha", "Q_beta"), names_to = "parameter", values_to = "estimate") %>%
  ggplot(aes(x=estimate)) + geom_histogram(bins=20) + facet_grid(condition ~ parameter, scales = "free")
```

### 2021-04-22 HMM/Qlearn-HMM-exp2.R

@@ -1,51 +1,58 @@
 library(depmixS4)
 
 setClass(
-  "ToM",
+  "Qlearn",
   representation(
+    reward = "numeric",
+    state = "numeric",
     act = "numeric",
-    opp_act = "numeric",
-    pred = "array", # nT * nA * nS 
-    n_act = "numeric", # for each trial
+    act_mask = "matrix",
+    opponent_id = "numeric",
     nS = "numeric",
-    nA = "numeric", # max n(act)
+    nA = "numeric",
+    nO = "numeric",
     ntimes = "numeric"
   ),
   prototype(
+    reward = 1,
+    state = 1,
     act = 1,
-    opp_act = 1,
-    pred = array(1.0, dim=c(1,1,1)),
-    n_act = 1,
+    act_mask = matrix(1),
+    opponent_id = 1,
     nS = 1,
     nA = 1,
+    nO = 1,
     ntimes = 1
   ),
   contains = "response"
 )
 
-setGeneric("ToM", function(act,
-                           opp_act,
-                           pred,
-                           n_act,
-                           data = NULL,
-                           ntimes = NULL,
-                           pstart = NULL,
-                           fixed = NULL,
-                           ...)
-  standardGeneric("ToM"))
+setGeneric("Qlearn", function(reward,
+                              state,
+                              act,
+                              act_mask,
+                              opponent_id,
+                              data = NULL,
+                              ntimes = NULL,
+                              pstart = NULL,
+                              fixed = NULL,
+                              ...)
+  standardGeneric("Qlearn"))
 
-setMethod("ToM",
+setMethod("Qlearn",
           signature(
+            reward = "numeric",
+            state = "numeric",
             act = "numeric",
-            opp_act = "numeric",
-            pred = "array",
-            n_act = "numeric",
+            act_mask = "matrix",
+            opponent_id = "numeric",
             ntimes = "numeric"
           ),
-          function(act,
-                   opp_act,
-                   pred,
-                   n_act,
+          function(reward,
+                   state,
+                   act,
+                   act_mask,
+                   opponent_id,
                    data = NULL,
                    ntimes = NULL,
                    pstart = NULL,
@@ -53,13 +60,16 @@ setMethod("ToM",
                    prob = TRUE,
                    na.action = "na.pass",
                    ...) {
[…]

### 2021-04-22 HMM/Qlearn-HMM.R

@@ -193,18 +193,18 @@ setMethod("predict", "Qlearn",
             bt <- c(1, et[-lt] + 1)
             
             nT <- et[lt]
-            pred <- matrix(1.0, nrow=nT, ncol=object@nA)
+            pred <- matrix(0.0, nrow=nT, ncol=object@nA)
             
             for (id in 1:lt) {
               Q <- array(0.0, dim = c(object@nA, object@nS))
               for (t in bt[id]:et[id]) {
                 # prob of action
                 if (is.na(object@state[t])) {
-                  pred[t, object@act_mask[t, ]] <- 1 / sum(object@act_mask[t, ])
+                  pred[t, as.logical(object@act_mask[t, ])] <- 1 / sum(object@act_mask[t, ])
                 } else {
-                  pred[t, object@act_mask[t, ]] <-
-                    exp(Q[object@act_mask[t, ], object@state[t]] / object@parameters$beta) /
-                    sum(exp(Q[object@act_mask[t, ], object@state[t]] / object@parameters$beta))
+                  pred[t, as.logical(object@act_mask[t, ])] <-
+                    exp(Q[as.logical(object@act_mask[t, ]), object@state[t]] / object@parameters$beta) /
+                    sum(exp(Q[as.logical(object@act_mask[t, ]), object@state[t]] / object@parameters$beta))
                 }
                 # update Q
                 if (!is.na(object@state[t])) {

### 2021-04-22 HMM/ToM-HMM-exp2.R

@@ -7,8 +7,11 @@ setClass(
     opp_act = "numeric",
     pred = "array", # nT * nA * nS 
     n_act = "numeric", # for each trial
+    opponent_id = "numeric",
+    game_id = "numeric",
     nS = "numeric",
     nA = "numeric", # max n(act)
+    nO = "numeric",
     ntimes = "numeric"
   ),
   prototype(
@@ -16,8 +19,11 @@ setClass(
     opp_act = 1,
     pred = array(1.0, dim=c(1,1,1)),
     n_act = 1,
+    opponent_id = 1,
+    game_id = 1,
     nS = 1,
     nA = 1,
+    nO = 1,
     ntimes = 1
   ),
   contains = "response"
@@ -27,6 +33,8 @@ setGeneric("ToM", function(act,
                            opp_act,
                            pred,
                            n_act,
+                           opponent_id,
+                           game_id,
                            data = NULL,
                            ntimes = NULL,
                            pstart = NULL,
@@ -40,12 +48,16 @@ setMethod("ToM",
             opp_act = "numeric",
             pred = "array",
             n_act = "numeric",
+            opponent_id = "numeric",
+            game_id = "numeric",
             ntimes = "numeric"
           ),
           function(act,
                    opp_act,
                    pred,
                    n_act,
+                   opponent_id,
+                   game_id,
                    data = NULL,
                    ntimes = NULL,
                    pstart = NULL,
@@ -53,12 +65,13 @@ setMethod("ToM",
                    prob = TRUE,
                    na.action = "na.pass",
                    ...) {
-            if (!all.equal(length(act), length(opp_act), length(n_act), dim(pred)[1]))
+            if (!all.equal(length(act), length(opp_act), length(n_act), dim(pred)[1], length(opponent_id)))
               stop("unequal length of data")
             
             nT <- length(act)
             nS <- dim(pred)[3]
             nA <- dim(pred)[2]
+            nO <- max(opponent_id)
         
             if (!is.null(ntimes)) {
               if (sum(ntimes) != nT)
@@ -92,8 +105,11 @@ setMethod("ToM",
                 opp_act = opp_act,
                 pred = pred,
                 n_act = n_act,
[…]

### 2021-04-22 HMM/exp2-HMM.R

@@ -1,144 +1,112 @@
 library(dplyr)
 library(depmixS4)
-source("HMM/Qlearn-HMM.R")
-source("HMM/ToM-HMM.R")
+source("HMM/Qlearn-HMM-exp2.R")
+source("HMM/ToM-HMM-exp2.R")
 source("HMM/dummy-HMM.R")
 
-dat <- read.csv("data20180719.csv")
+dat <- read.csv("Experiment_2/MyData.csv")
 
 dat <- as_tibble(dat) %>% group_by(human_id,game)
 dat <- dat %>%
   mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1)) %>%
-    mutate(state = interaction(ai_action_prev,human_action_prev))
+  mutate(state = interaction(ai_action_prev,human_action_prev))
 dat <- dat %>% mutate(pred_a1_level0 = case_when(
   game == "rps" & ai_action_prev == "rock" ~ 1,
   game == "fwg" & ai_action_prev == "fire" ~ 1,
-  game == "numbers" & ai_action_prev == "one" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
+  game == "shootout" & ai_action_prev == "left" ~ 1,
   is.na(ai_action_prev) ~ 1/3,
   !is.na(ai_action_prev) ~ 0))
 dat <- dat %>% mutate(pred_a2_level0 = case_when(
   game == "rps" & ai_action_prev == "paper" ~ 1,
   game == "fwg" & ai_action_prev == "water" ~ 1,
-  game == "numbers" & ai_action_prev == "two" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
+  game == "shootout" & ai_action_prev == "center" ~ 1,
   is.na(ai_action_prev) ~ 1/3,
   !is.na(ai_action_prev) ~ 0))
 dat <- dat %>% mutate(pred_a3_level0 = case_when(
   game == "rps" & ai_action_prev == "scissors" ~ 1,
   game == "fwg" & ai_action_prev == "grass" ~ 1,
-  game == "numbers" & ai_action_prev == "three" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
+  game == "shootout" & ai_action_prev == "right" ~ 1,
   is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
[…]

### 2021-06-04 Bayesian_models_exp1.Rmd
fixed Q learning bugs
added report in papaja and softmax to BCH models

@@
 ---
-title: "Bayesian_models_exp2"
+title: "Bayesian_models_exp1"
 output: html_document
@@
 knitr::opts_chunk$set(echo = TRUE)
+library(dplyr)
 ```
@@
 
-dat <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")
+#dat <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")
 
@@
 # if human does not generalize, we need to reset the prior at the start of each ?stage?
-exp1_Bayes_model_LL <- function(par,data, generalize = c("game","no"), return_value = "-2loglik") {
+exp1_Bayes_model_LL <- function(par,data, generalize = c("game","no"), softmax= TRUE, return_value = "-2loglik") {
+
   # return_value=c("-2loglik","likelihood_by_trial")
-  # data is a subset for a single participant
+  # input data for this function should be a subset for a single participant
   generalize <- match.arg(generalize)
   alpha <- par[1] # probability that ai opponent plays according to strategy
-  if(length(par) > 1) {
-    beta <- par[2] # probability that human plays according to best response 
-  } else{
-    beta <- 1 # probability that human plays according to best response 
+
+  if(softmax) {
+    lambda <- par[2] # inverse temperature parameter in softmax function
   }
 
+  beta <- 1 # probability that human plays according to best response 
   prior <- c(1,1,1) # prior alpha for dirichlet on p(level)
@@
 
+  #cat(as.character(c(round(dat$p_self_a1,2), "\n", "\n")))
+
   # now finally compute the likelihood of human actions 
+  if (softmax) {
+
+        dat <- dat %>% 
+    mutate(sumexp = exp(lambda*p_self_a1) + exp(lambda*p_self_a2) + exp(lambda*p_self_a3) + exp(lambda*p_self_a4) + exp(lambda*p_self_a5)) %>%
+             mutate(
+               loglik = case_when(
+                 human_action_num == 1 ~ log(exp(lambda*p_self_a1)/sumexp),
+                 human_action_num == 2 ~ log(exp(lambda*p_self_a2)/sumexp),
+                 human_action_num == 3 ~ log(exp(lambda*p_self_a3)/sumexp),
+                 human_action_num == 4 ~ log(exp(lambda*p_self_a4)/sumexp),
+                 human_action_num == 5 ~ log(exp(lambda*p_self_a5)/sumexp)
+      )
+    )
+  } else {
     dat <- dat %>% 
@@
     )
+
+  }
 
@@
 ```{r}
-exp1_Bayes_model_LL(0.4,data = dat, generalize = "no", "likelihood_by_trial")
+# testing funcrion. Careful dat here can be all participants data, check how it is defined. 
+exp1_Bayes_model_LL(c(0.4, 1) ,data = dat, generalize = "no", softmax = TRUE, "likelihood_by_trial")[51]
+exp1_Bayes_model_LL(c(0.4) ,data = dat, generalize = "no", softmax = FALSE, "likelihood_by_trial")[51]
+```
+## Compare loglikelihood: probability matching vs softmax (with Between game transfer for now)
+
+```{r echo=FALSE}
+library(DEoptim)
+
+prob_match_tr <- use_softmax_tr <- use_softmax_NT <- list()
+
+# # Using DEOptim 
+for(id in levels(dat$human_id)) {
+  tdat <- subset(dat,human_id == id)
+  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))
+
+  prob_match_tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
+                                  generalize = "game",FALSE, control=ctrl)
+
+  use_softmax_tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat, generalize = "game",TRUE, control=ctrl)
+
+  use_softmax_NT[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat, generalize = "no",TRUE, control=ctrl)
+
+}
+
+save(prob_match_tr,file="BCH_prob_match_tr.RData")
+save(use_softmax_tr,file="BCH_use_softmax_tr.RData")
+save(use_softmax_NT,file="BCH_use_softmax_NT.RData")
+```
+
+```{r}
+compare_table <- data.frame()
+for(id in levels(dat$human_id)) {
+  compare_table <- rbind(compare_table,
+                       data.frame(
+                         "ID" = id,
+                         "prob_match_tr_BIC" = prob_match_tr[[id]]$optim$bestval+ 1*log(150),
+                         "softmax_tr_BIC" = use_softmax_tr[[id]]$optim$bestval+ 2*log(150)
+                         ))
+}
+
+```
+
+```{r}
+
+comp_models <- compare_table[c("ID","prob_match_tr_BIC","softmax_tr_BIC")]
+
+BIC_weights_BCH <- comp_models["ID"]
+BIC_weights_BCH[,2:ncol(comp_models)] <- t(apply(comp_models[,2:ncol(comp_models)], 1, function(i) exp(-0.5*(i-min(i)) )))
+colnames(BIC_weights_BCH) <-colnames(comp_models)
+
+BIC_weights_BCH[,2:ncol(BIC_weights_BCH)] <- t(apply(BIC_weights_BCH[,-1], 1, function(i) round(i/sum(i),2)))
+
+colMeans(BIC_weights_BCH[,2:ncol(BIC_weights_BCH)])
+```
+
+```{r}
+
 ```
@@
 
-# # USing DEOptim 
+# # Using DEOptim 
 for(id in levels(dat$human_id)) {

### 2021-06-04 Experiment_2/Bayesian_models_exp2.Rmd
added report in papaja and softmax to BCH models

@@
 # dat <- subset(dat,human_id == "gRRZ0rUagyVejWTOAAFl")
-dat <- subset(dat,human_id == "vGnDPRowetREQVmwAADL")
+#dat <- subset(dat,human_id == "vGnDPRowetREQVmwAADL")
 # dat <- subset(dat,human_id == "wi_zWhftr9MdqTmCAAHs")
@@
 
-Bayes_model_LL <- function(par,data,distinct_opponent = TRUE, generalize = c("game","stage","no"), return = "-2loglik"){
+Bayes_model_LL <- function(par,data,distinct_opponent = TRUE, softmax = TRUE, generalize = c("game","stage","no"), return = "-2loglik"){
 
   # data is a subset for a single participant
+
   generalize <- match.arg(generalize)
   alpha <- par[1] # probability that ai opponent plays according to strategy
-  if(length(par) > 1) {
-    beta <- par[2] # probability that human plays according to best response 
-  } else{
   beta <- 1 # probability that human plays according to best response
+
+  if(softmax) {
+    lambda <- par[2] # inverse temperature parameter in softmax function
   }
@@
   # now finally compute the likelihood of human actions
+
+    # now finally compute the likelihood of human actions 
+  if (softmax) {
+
+    dat <- dat %>% 
+    mutate(sumexp = exp(lambda*p_self_a1) + exp(lambda*p_self_a2) + exp(lambda*p_self_a3)) %>%
+             mutate(
+               loglik = case_when(
+                 human_action_num == 1 ~ log(exp(lambda*p_self_a1)/sumexp),
+                 human_action_num == 2 ~ log(exp(lambda*p_self_a2)/sumexp),
+                 human_action_num == 3 ~ log(exp(lambda*p_self_a3)/sumexp)
+      )
+    )
+
+  } else {
     dat <- dat %>% 
@@
         human_action_num == 2 ~ log(p_self_a2),
-        human_action_num == 3 ~ log(p_self_a3))
+        human_action_num == 3 ~ log(p_self_a3)
       )
+    )
+
+  }
 
@@
 ```{r}
-Bayes_model_LL(0.5,data = dat,distinct_opponent = TRUE, generalize = "game", return = "likelihood_by_trial")
+Bayes_model_LL(c(0.5,1),data = dat,distinct_opponent = TRUE, generalize = "game", softmax = TRUE, return = "likelihood_by_trial")
 
@@
 
-# USing DEOptim
+# Using DEOptim
 
@@
   tdat <- subset(dat,human_id == id)
-  ctrl <- DEoptim.control(NP = 20, itermax=50)
-  Bayes_same_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-                                   distinct_opponent = FALSE, generalize = "game",control=ctrl)
-  Bayes_same_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-                                   distinct_opponent = FALSE, generalize = "stage",control=ctrl)
-  Bayes_same_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-                                   distinct_opponent = FALSE, generalize = "no",control=ctrl)
-  Bayes_distinct_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
+  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))
+
+  # Here, optimisation implies softmax = TRUE as it was omitted as input and default is true 
+  # Bayes_same_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
+  #                                  distinct_opponent = FALSE, generalize = "game", control=ctrl)
+  # 
+  # Bayes_same_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
+  #                                  distinct_opponent = FALSE, generalize = "stage",control=ctrl)
+  # 
+  # Bayes_same_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
+  #                                  distinct_opponent = FALSE, generalize = "no",control=ctrl)
+
+  Bayes_distinct_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
                                    distinct_opponent = TRUE, generalize = "game",control=ctrl)
-  Bayes_distinct_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
+
+  Bayes_distinct_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
                                         distinct_opponent = TRUE, generalize = "stage",control=ctrl)
-  Bayes_distinct_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
+
+  Bayes_distinct_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat,
                                  distinct_opponent = TRUE, generalize = "no",control=ctrl)
@@
 
+#save(prob_match_tr,file="BCH_prob_match_tr.RData")
+
+# All these below use softmax for choice function rather than prob matching. For prob matching, choose softmax = FALSE above.
+save(Bayes_distinct_game,file="Bayes_distinct_game.RData")
+save(Bayes_distinct_stage,file="Bayes_distinct_stage.RData")
+save(Bayes_distinct_no,file="Bayes_distinct_no.RData")
+
+```
+
+```{r}
 # using optim

### 2021-06-04 Experiment_2/Experiment_2_modelling.Rmd
added report in papaja and softmax to BCH models

@@
 ```{r, cache=TRUE}
+# Set seed to random number to check you get same results
+set.seed(43)
 
@@
 ```{r}
+
+load("exp2_QLS_modelling.Rdata")
+load("exp2_QLS_within_Tr.Rdata")
+load("exp2_STEWA_NT.Rdata")
+load("exp2_STEWA_Tr.Rdata")
+load("MBM2_modelling.Rdata")
+
 exp2_results <- data.frame()
@@
                           # Bayesian updating with between and within game transfer
-                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$optim$bestval + 1*log(180),
+                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$optim$bestval + 2*log(180),
                          "theta_transfer" = Bayes_distinct_game[[id]]$optim$bestmem[1],
+                         "lambda_transfer" = Bayes_distinct_game[[id]]$optim$bestmem[2],
 
                           # Bayesian updating with within but no btwn game transfer
-                         "Distinct_stage_BIC" = Bayes_distinct_stage[[id]]$optim$bestval + 1*log(180),
+                         "Distinct_stage_BIC" = Bayes_distinct_stage[[id]]$optim$bestval + 2*log(180),
                          "theta_no_btw_tr" = Bayes_distinct_stage[[id]]$optim$bestmem[1],
+                         "lambda_no_btw_tr" = Bayes_distinct_stage[[id]]$optim$bestmem[2],
 
                           #  No within or between game transfer
-                         "Bayes_distinct_no" = Bayes_distinct_no[[id]]$optim$bestval + 1*log(180),
+                         "Bayes_distinct_no" = Bayes_distinct_no[[id]]$optim$bestval + 2*log(180),
                          "theta_no_tr" =  Bayes_distinct_no[[id]]$optim$bestmem[1],
+                         "lambda_no_tr" =  Bayes_distinct_no[[id]]$optim$bestmem[2],
 
                           # No distinction between players, transfer within and between
-                         "Bayes_same_game" = Bayes_same_game[[id]]$optim$bestval + 1*log(180),
-                         "theta_naive" = Bayes_same_game[[id]]$optim$bestmem[1],
-                          ###########
+                         # "Bayes_same_game" = Bayes_same_game[[id]]$optim$bestval + 1*log(180),
+                         # "theta_naive" = Bayes_same_game[[id]]$optim$bestmem[1],
+                         #  ###########
 
@@
 ```{r}
-
-# WIth MS results for Bayesian models
-exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT", "QL_states","QLS_within","STEWA_NT","STEWA_Tr")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])
-
- write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
- kable(exp2_table_results)
-```
-
-```{r}
-
+# WITH MS results for bayesian models 
+# exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+# 
+#  write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
+#  kable(exp2_table_results)
 ```
@@
   tot_score <- sum(tdat$score)
-  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
+  tot_time <- sum(tdat$human_rt)
+  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
+  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
   tr_score <- sum(early_dat$score)
@@
   # MS BAYES MODELS
-  min_BIC <- apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,min)
+  min_BIC <- apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no", "QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,min)
 
-  best_model <- c("random","TOM_BT","TOM_NBT", "TOM_NT", "QL_states","QLS_within","STEWA_NT","STEWA_Tr")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)]
+  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","QL_states_NT","QLS_within_Tr","STEWA_NT","STEWA_Tr")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)]
 
@@
 write.csv(exp2_model_comp,file="exp2_model_comp.csv",row.names = FALSE)
+
+```
+
+## Calucalting BIC weights 
+```{r}
+
+exp2_comp_BICs <- exp2_results[c("ID","Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no", "QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")]
+
+exp2_BIC_weights <- exp2_comp_BICs["ID"]
+exp2_BIC_weights[,2:ncol(exp2_comp_BICs)] <- t(apply(exp2_comp_BICs[,2:ncol(exp2_comp_BICs)], 1, function(i) exp(-0.5*(i-min(i)) )))
+
+exp2_BIC_weights[,-1] <- t(apply(exp2_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
+colnames(exp2_BIC_weights) <- c("ID", "random","ToM_BT","ToM_NBT", "ToM_NT","QL_states_NT","QLS_within_Tr","STEWA_NT","STEWA_Tr")
+
+BIC_comp_table <- as.data.frame(t(colMeans(exp2_BIC_weights[,2:ncol(exp2_BIC_weights)])))
+
+colnames(BIC_comp_table) <- c("random","ToM_BT","ToM_NBT", "ToM_NT","QL_states_NT","QLS_within_Tr","STEWA_NT","STEWA_Tr")
+# 
+BIC_comp_table
+
+table(exp2_model_comp$Best_model_2)
+
 ```

### 2021-06-04 Experiment_2/exp2_lik_by_trial.Rmd
fixed bugs in report
added report in papaja and softmax to BCH models

@@
   # QLS likelihoods 
-  pars_QLS <- unlist(filter(exp2_optim_results, ID == id)%>%select(QL_states_Beta, QL_states_alpha))
-  tdat$QLS_lik <-  exp2_QL_states(pars_QLS,tdat,"likelihood_by_trial",0.0, FALSE)
+  pars_QLS <- unlist(filter(exp2_optim_results, ID == id)%>% dplyr::select(QL_states_Beta, QL_states_alpha))
+  tdat$QLS_lik <-  exp2_QL_states(pars_QLS,tdat,"likelihood_by_trial",gamma =0.0, FALSE)
 
   # QLS within Transfer likelihoods 
-  pars_QLS_within <- unlist(filter(exp2_optim_results, ID == id)%>%select(QLS_within_Tr_Beta,QLS_within_Tr_alpha))
+  pars_QLS_within <- unlist(filter(exp2_optim_results, ID == id)%>% dplyr::select(QLS_within_Tr_Beta,QLS_within_Tr_alpha))
   tdat$QLS_lik_within <-  exp2_QL_states(pars_QLS_within,tdat,"likelihood_by_trial",gamma = 0, TRUE)
@@
   # 
-  # Bayes model no transfer likelihoods
-  theta_NT <- unlist(filter(exp2_optim_results, ID == id)%>%select(theta_no_tr))
-  tdat$Bayes_NT_lik <- Bayes_model_LL(theta_NT, tdat, distinct_opponent = TRUE, generalize = "no",return = "likelihood_by_trial")
+  # Bayes model no transfer likelihoods. Assume softmax = TRUE as default. 
+  # theta_NT <- unlist(filter(exp2_optim_results, ID == id)%>%select(theta_no_tr))
+  # lambda_NT <- unlist(filter(exp2_optim_results, ID == id)%>%select(lambda_no_tr))
+  pars_BCH_NT2 <- unlist(filter(exp2_optim_results, ID == id)%>% dplyr::select(theta_no_tr, lambda_no_tr))
+  tdat$Bayes_NT_lik <- Bayes_model_LL(pars_BCH_NT2, tdat, distinct_opponent = TRUE, generalize = "no",return = "likelihood_by_trial")
 
   # Bayes model with Transfer likelihood
-  theta_Tr <- unlist(filter(exp2_optim_results, ID == id)%>%select(theta_transfer))
-  tdat$Bayes_Tr_lik <- Bayes_model_LL(theta_Tr, tdat, distinct_opponent = TRUE, generalize = "game",return = "likelihood_by_trial")
+  # theta_Tr <- unlist(filter(exp2_optim_results, ID == id)%>%select(theta_transfer))
+  pars_BCH_BT2 <- unlist(filter(exp2_optim_results, ID == id)%>% dplyr::select(theta_transfer, lambda_transfer))
+  tdat$Bayes_Tr_lik <- Bayes_model_LL(pars_BCH_BT2, tdat, distinct_opponent = TRUE, generalize = "game",return = "likelihood_by_trial")
 
@@
 }
+
+write.csv(lik_by_trial_2,file="exp2_lik_by_trial.csv",row.names = FALSE)
 ```
@@
 mean_lik_2 <- lik_by_trial_2 %>%
-  select(human_id,game,stage,round_condition, round, QLS_lik, QLS_lik_within, Bayes_NT_lik, Bayes_Tr_lik) %>%
+  dplyr::select(human_id,game,stage,round_condition, round, QLS_lik, QLS_lik_within, Bayes_NT_lik, Bayes_Tr_lik) %>%
   group_by(game,stage,round) %>%

### 2021-06-04 Report/CSS_submission_2021.Rmd
added report in papaja and softmax to BCH models

--- 2020-10-30 Report/draft_report_v3.Rmd
@@
 title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-shorttitle        : "Draft-3"
+shorttitle        : "Upgrade Report"
 
@@
 abstract: |
-  Enter abstract here. Each new line herein must be indented, like this line.
+  Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and 
+  causal models of the environment. One way to build abstract representations of the environment when the task involves interactions with others is to build 
+  a model of the opponent that may inform what actions they are likely to take next. In this study, we propose to explore opponent modelling and its transfer with the use of
+  computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning. Through two differentiated experiments, we find that participants can
+  deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it. Moreover, we showed that participants transfer their learning to new games and that
+  the transfer is moderated by the level of  sophistication of the opponent. Computational modelling shows that it is likely that players start each game using a model-based
+  learning strategy that facilitates generalisation and opponent model transfer, but then switch to behaviour that is consistent with a  model-free learning strategy in the latter
+  stages of the interaction.
 
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 linkcolor         : "blue"
@@
 output            : papaja::apa6_pdf
-#citation_package  : natbib
+header-includes:
+  - \shorttitle{}
 ---
@@
 library(depmixS4)
-library(rmdfiltr)
+
 ```
@@
 options(tinytex.verbose = TRUE)
-add_wordcount_filter(NULL, error = FALSE)
+#add_wordcount_filter(NULL, error = FALSE)
 ```
@@
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
-More formally, @perkins1992transfer defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
+More formally, @perkins1992transfer define transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
 This typically human skill has so far eluded modern AI agents.
@@
 
-Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
+<!-- Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
 For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
@@
 If the games were only strategically similar, then the transfer was much weaker.
-
-@Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
+-->
+
+<!-- @Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
 However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
@@
 They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of a different payoff structure on an opponent's actions.
-
-Most studies fail to offer a formal explanation of transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
-A notable exception is the effort by @Haruvy2012 to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
-Participants played ten games, presented in 4x4 normal form (matrix payoffs).
-Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
-They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on @stahl1995players, was able to capture participants' dynamic behavior and shows that the propensity to select particular rules is perfectly transferred across games.
+-->
 
@@
 One of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision, or at detecting patterns from long sequences of past play due to cognitive constraints.
 It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities.
@@
 Otherwise it is a draw and both players receive a reward of 0.
-It has a unique MSNE consisting of randomly playing one of the three options each time.The second game is identical to Rock-Paper-Scissors in all but action labels.
+It has a unique MSNE consisting of randomly playing one of the three options each time.
+The second game is identical to Rock-Paper-Scissors in all but action labels.
 We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
@@
 In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-Each point worth £0.02.
+Each point is worth £0.02.
 An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps-exp2).
@@
 To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game ( F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in the NUMBERS game was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
-The score in RPS was not significantly different from the score in NUMBERS ( t(100) = 0.45 , p = 0.65).
-The main effect of Block ( F(1,50) = 22.51 , p < .001, $\eta^{2}$ = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning.
+There was a main effect of Game (F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games.
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game (t(100) =3.78, p = 0.0008), and the performance in the NUMBERS game was significantly lower than FWG game (t(100) = -3.32 , p = 0.0024).
+The score in RPS was not significantly different from the score in NUMBERS (t(100) = 0.45 , p = 0.65).
+The main effect of Block (F(1,50) = 22.51 , p < .001, $\eta^{2}$ = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning.
 The main effect of Condition (F(1,50) = 5.44, p = .024, $\eta^{2}$ = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
@@
 
-```{r exp1-3factor-plot, fig.cap = "Average scores by game, block and condition", fig.align = "center"}
+```{r exp1-3factor-plot, fig.cap = "Boxplots of scores by game, block and condition", fig.align = "center"}
 
@@
 This is indicative of the significant within-game learning happening in the first game when players have no experience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some experience playing against the opponent and start with higher scores indicative of transfer.
-There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent.
+There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88, p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent.
 For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than against level-1 opponent.
@@
 
-```{r exp1-score-by-opp, fig.cap = "Mean and CI of early scores by game and opponent", fig.align ='center'}
-
-p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","Numbers"), ylab = "Early rounds score", xlab = "Games", legend.title = "Games")
+(ref:figure4-caption) Mean and standard error of early scores by game and opponent
+```{r exp1-score-by-opp, fig.cap = "(ref:figure4-caption)", fig.align ='center'}
+
+p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","Numbers"), ylab = "Early rounds score", xlab = "Games", legend.title = "Games")
 
@@
 
-```{r ANOVA early exp1, include = FALSE, warning=FALSE}
+```{r ANOVA early exp1, include = TRUE, warning=FALSE}
 
@@
 
+exp1_early_anova
 #apa_lm1 <- apa_print(exp1_early_anova)
@@
 
-\newpage
-
-# Second Experiment
+# Experiment 2
 
 We ran a second experiment with various differentiated features to improve the opportunity to measure learning transfer.
-Instead of making participants face either the level-1 or level-2 player throughout, we made them face both opponent sequentially.
+Instead of making participants face either the level-1 or level-2 player throughout, we made them face both opponents sequentially.
 Because there were two distinct opponents, requiring potentially holding two opponent models in memory, we also made it easier to recall the results of past rounds by providing participants with the opportunity to see the history of the game since the beginning of each interaction.
@@
 
-```{r exp2-early-scores, fig.cap="Average early round scores and confidence intervals by game and opponent for experiment 2", fig.align="center"}
+(ref:figure7-caption) Mean and standard error of early scores by game and opponent for experiment 2
+```{r exp2-early-scores, fig.cap="(ref:figure7-caption)", fig.align="center"}
 # plot scores per game 
-p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Score rounds 2-6", xlab = "Games")
+p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Early rounds score", xlab = "Games", legend.title = "Games")
 
@@
 
-$$ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) $$
+$$ V_{t+1}(a) = V_{t}(a) + \alpha \times ( R_{t}  - V_{t}(a)) $$
 
@@
 
-$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$
+$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha \times( R_{t}  + \gamma \times \underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$
 
@@
 
-<!-- In experiment 2, we allow this richer model to have a memory of the interaction.
-In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used.
-In another instance, we fit a model in which what was learned about an opponent in the first interaction is transferred to the first round of the second interaction, so there is a within-game transfer of Q-values allowed (QLS-within).
-We fit both models to all participant's data in the second experiment where both opponents are faced.
--->
-
-### EWA Models 
+## EWA Models 
 Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics].
@@
 The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
-
 Let's define some notation in order to write the update rule of the self-tuning EWA model.
@@
 After playing  $s_{i}^{j}$ at time $t$, player i pay-off is denoted $\pi_{i}(s_{i}^{j},s_{-i}(t))$, and the actual pay-off the player received is $\pi_{i}(t)$.
-
 The EWA model is based on updating "Attractions" for each action over time.
@@
 
-$$P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} $$
+$$P_{i}^{j}(t+1) = \frac{e^{\lambda  A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda A_{i}^{k}(t)}} $$
 
@@
 
-$$ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} $$
-
-Here, I(x,y) is the indicator function equal to 1 if $x = y$ and 0 otherwise.
+$$ A_{i}^{j}(t) =  \frac{\phi \times N(t-1) \times A_{i}^{j}(t-1) + [ \delta + (1-\delta) \times I(s_{i}^{j},s_{i}(t))] \times \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi \times N(t-1) + 1} $$
+
+Here, $I(x,y)$ is the indicator function equal to 1 if $x = y$ and 0 otherwise.
 A simple way to think about this update rule is that attractions are multiplied by a parameter that represents experience ($N(t-1)$) which is itself decaying by a weight $\phi$.
@@
 
-### ToM models
-
-In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
-We use values of k  in ${0,1,2}$.
+## BCH models
+
+In this set of models, we assume that participants start with a prior belief that the opponent is a level-k agent, with uniform probability of the level $k \in \{ 0, 1, 2\}$, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
+More formally, if we define $D_{t}$ as data available at time $t$ then the probability of the opponent being a level-k is updated using:
+
+$$ P(level=k | D_{t})  \propto  P(D_{t}|level=k ) \times P(level=k)$$
+
 These models also assume the opponent can deviate from these level-k strategies and play randomly with probability $\theta$, a parameter to be fit.
-We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
+We also assume that participants base their actions on their beliefs about the level of the opponent, so actions get chosen probabilistically using a softamx choice rule with probabilities of each opponent level as inputs.
+We distinguish between multiple BCH models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
 In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between transfer)
-
-Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
+In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (within but no between transfer).Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
 In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
-
-We fit the above two models to experiment 1 data.
 In experiment two, on top of these two models, we fit another model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
 
-### Estimation and model comparison
+## Estimation and model comparison
 In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
@@
 
+In experiment 1, we fit a total of 5 models: A baseline model assuming random play (Nash),  Bayesian Cognitive Hierarchy model allowing transfer betwen games (BCH_BT) and another with no transfer between games (BCH_NBT), as well as a Q-learning model with state space consisting of last round play (QL_states), and finally a self tuning EWA model with the same state space (STEWA_states).
+In experiment 2, because participants were interacting with each opponent twice within each game, we allowed models to transfer learning within games between the first and second interactions.
+Therefore on top of the two BCH models mentionned above (BCH_BT and BCH_NBT), we also allow the Q-learning model with states to either have the ability to transfer learning between the first and second interaction (QLS_Tr) or not (QLS_NT).
+Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (STEWA_Tr) or without transfer (STEWA_NT).
+Counting the base model wiht random play (Nash) we therefore fit a total of 8 models in experiment 2.
+
 ## Experiment 1 modelling :
@@
 exp1_comp_results <- read.csv(file="../exp1_all_results.csv")
-exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Nash","ToM_BT","ToM_NBT", "QL_states","ST_EWA_states")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])
+exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Nash","BCH_BT","BCH_NBT", "RL","EWA")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])
 
@@
 
-  best_model <- c("Nash","ToM_BT","ToM_NBT", "QL_states","STEWA_States")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)]
+  best_model <- c("Nash","BCH_BT","BCH_NBT", "RL","EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)]
   # 
@@
                          "Total_score" = tot_score,
-                         "Best_model" = best_model,
-                         "Total_time" = sum(tdat$human_rt),
-                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
-                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
-
+                         "Best_model" = best_model
+                         #"Total_time" = sum(tdat$human_rt),
                        ))
@@
 temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
-dat_by_model <- temp %>% group_by(Best_model,t) %>% 
-  summarize(model_acc_sum = mean(acc_sum))
+dat_by_model <- temp %>% group_by(Best_model,t) %>% summarize(model_acc_sum = mean(acc_sum))
 
@@
 Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning with states defined by last round play.
+Table \ \@ref(tab:exp1weightstable) shows the model BIC weights  as well as the number of participants best fit by each model.
 
@@
 exp1_BIC_weights[,2:ncol(exp1_comp_BICs)] <- t(apply(exp1_comp_BICs[,-1], 1, function(i) exp(-0.5*(i-min(i)) )))
-colnames(exp1_BIC_weights) <- c("ID","Nash","ToM_BT","ToM_NBT","QL_states","STEWA_States")
+colnames(exp1_BIC_weights) <- c("ID","Nash","BCH_BT","BCH_NBT","RL","EWA")
 exp1_BIC_weights[,-1] <- t(apply(exp1_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
 
-Average_BIC_weights <- as.data.frame(t(round(apply(exp1_BIC_weights[,-1],2,mean),2)))
-row.names(Average_BIC_weights) <- c("Model BIC weights")
-Average_BIC_weights
-
-#Count_Best_fit <- table(exp1_model_comp$Best_model)
-temp <- plyr::count(exp1_model_comp,"Best_model")
-Count_Best_fit <- tidyr::spread(temp,Best_model, freq)
-row.names(Count_Best_fit) <- c("Count best fit")
-Count_Best_fit
-
-table_exp_1 <- rbind.fill(Average_BIC_weights,Count_Best_fit)
-row.names(table_exp_1) <- c("Model BIC weights","Count best fit")
-table_exp_1
+```
+
+```{r}
+library(reshape2)
+d <- melt(exp1_BIC_weights, id.vars="ID", variable.name = "Model",value.name = "BIC_weight")
+
+# Everything on the same plot
+ggplot(d, aes(ID,BIC_weight, col=Model)) + 
+  geom_point() + 
+  stat_smooth() +
+  facet_wrap(~Model) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) + 
+  theme(legend.position = c(0.8, 0.3))
+
+# 
+# Average_BIC_weights <- as.data.frame(t(round(apply(exp1_BIC_weights[,-1],2,mean),2)))
+# row.names(Average_BIC_weights) <- c("Model BIC weights")
+# Average_BIC_weights
+# 
+# #Count_Best_fit <- table(exp1_model_comp$Best_model)
+# temp <- plyr::count(exp1_model_comp,"Best_model")
+# Count_Best_fit <- tidyr::spread(temp,Best_model, freq)
+# row.names(Count_Best_fit) <- c("Count best fit")
+# Count_Best_fit
+# 
+# 
+# table_exp_1 <- rbind.fill(Average_BIC_weights,Count_Best_fit)
+# row.names(table_exp_1) <- c("Model BIC weights","Count best fit")
+# table_exp_1
 
@@
 ```
-
-Table \ \@ref(tab:exp1weightstable) shows the model BIC weights  as well as the number of participants best fit by each model.
 
@@
         args.legend=list( # positioning of legend box 
-        x=ncol(exp1_comp_table) + 4,
-        y=max(colSums(exp1_comp_table)) + 4,
+        x  = 15,
+        y  = 10,
+        #x=ncol(exp1_comp_table) -3 ,
+        #y=max(colSums(exp1_comp_table)) ,
         bty = "n")
@@
 Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (without transfer), followed by Q-learning conditional on last round play.
+We can see that participants whose actions are most consistent with learning a BCH opponent model in a Bayesian way had the best overall performance (without transfer), followed by Q-learning conditional on last round play.
 EWA, QL and random players had, understandably the lowest performance.
@@
 
-exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Nash","TOM BT","TOM NBT", "TOM NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])
+exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Nash","BCH BT","BCH NBT", "BCH NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])
 
@@
 
-  best_model <- c("Nash","TOM BT","TOM NBT", "TOM NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)]
+  best_model <- c("Nash","BCH BT","BCH NBT", "BCH NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)]
 
@@
 
-```{r, include=TRUE}
+```{r, include=FALSE}
 
@@
 exp2_BIC_weights[,2:ncol(exp2_comp_BICs)] <- t(apply(exp2_comp_BICs[,-1], 1, function(i) exp(-0.5*(i-min(i)) )))
-colnames(exp2_BIC_weights) <- c("ID","Nash","TOM BT","TOM NBT", "TOM NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")
+colnames(exp2_BIC_weights) <- c("ID","Nash","BCH BT","BCH NBT", "BCH NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")
 exp2_BIC_weights[,-1] <- t(apply(exp2_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
@@
 
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the opponent strategy had the highest cumulative performance.
-Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance (although it only fit 2 participants best), followed by a model in which both within and between transfer of opponent models is allowed (BT).
-The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where players reset opponent models at each stage of each game (NT).
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a BCH model of learning the opponent strategy had the highest cumulative performance.
+Out of these BCH models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance (although it only fit 2 participants best), followed by a model in which both within and between transfer of opponent models is allowed (BT).
+The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by BCH models where players reset opponent models at each stage of each game (NT).
 As expected, random play was at the bottom of cumulative performance.
@@
 This is at odds with the findings from the section regarding learning transfer: If indeed most participants use Q-learning with states to choose their actions, then they should not be able to transfer learning to the early rounds of the new game.
-In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Theory of Mind models with and without the possibility of across game transfer.
+In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Bayesian Cognitive Hierarchy models with and without the possibility of across game transfer.
 
 We start with experiment 1 data.
-Figure\ \@ref(fig:exp1-lik-by-tr) shows that in the later games, the likelihood for the ToM models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of ToM models.
+Figure\ \@ref(fig:exp1-lik-by-tr) shows that in the later games, the likelihood for the BCH models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of BCH models.
 
@@
   facet_grid(game~condition) +
-  scale_colour_discrete(name = "Strategy", labels = c("Nash", "Q_learning", "ToM + Tr"))
+  scale_colour_discrete(name = "Strategy", labels = c("Nash", "RL", "BCH_BT"))
 
@@
 Likewise, in experiment 2,  we want to understand the dynamic of strategy choice by plotting the likelihood by trial for each strategy, using the optimal parameters found when fitting the model.
-Figure\ \@ref(fig:exp2-lik-by-tr) shows that, as in experiment 1, ToM models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
+Figure\ \@ref(fig:exp2-lik-by-tr) shows that, as in experiment 1, BCH models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
 In the third and more dissimilar game, we get a result that is different from experiment 1.
-In this instance, the likelihoods of the ToM models stay constant and close to their initial values.
+In this instance, the likelihoods of the BCH models stay constant and close to their initial values.
 
@@
              mean_QLS_within_lik = mean(QLS_lik_within, na.rm = TRUE),
-             mean_ToM_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
+             mean_BCH_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
 
@@
 
-data_long2 <- gather(mean_lik_2, strategy, probability, mean_Nash_lik:mean_ToM_Tr_lik, factor_key=TRUE)
+data_long2 <- gather(mean_lik_2, strategy, probability, mean_Nash_lik:mean_BCH_Tr_lik, factor_key=TRUE)
 ```
@@
   facet_grid(game~stage) +
-  scale_colour_discrete(name = "Strategy", labels = c( "Nash", "Q_Learning + within Tr", "ToM + Tr"))
+  scale_colour_discrete(name = "Strategy", labels = c( "Nash", "Q_Learning + within Tr", "BCH + Tr"))
 
@@
 The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative of participants switching between strategies as the games progressed.
-Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the ToM based strategies fitted observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
-
-In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q-learning with state space consisting of previous round play, ToM based model with opponent model transfer, and a base model consisting of random play consistent with a Nash equilibrium strategy).
+Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the BCH based strategies fitted observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
+
+In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q-learning with state space consisting of previous round play, BCH based model with opponent model transfer, and a base model consisting of random play consistent with a Nash equilibrium strategy).
 Hidden Markov models are useful tools to explore structure in observed time series.
@@
 
-```{r no-switch, include=FALSE}
+```{r no-switch, include=TRUE}
 
@@
 
+llratio(fmod1,fmod1_noswitch)
+
 1-pchisq(-2*as.numeric(logLik(fmod1_noswitch)) - (-2*as.numeric(logLik(fmod1))),df=6)
@@
 mean_post_1 <- exp1_lik_by_trial %>%
-  dplyr::select(human_id,game,condition, round, post_QLS, post_Bayes_Tr) %>%
+  dplyr::select(human_id,game,condition, round, post_Nash, post_QLS, post_Bayes_Tr) %>%
   dplyr::group_by(game,condition, round) %>%
-  dplyr::summarise(QLS_posterior = mean(post_QLS, na.rm = TRUE),
-            Bayes_Transfer_posterior = mean(post_Bayes_Tr, na.rm = TRUE))
+  dplyr::summarise(Nash_posterior = mean(post_Nash, na.rm = TRUE),
+                   RL_posterior = mean(post_QLS, na.rm = TRUE),
+            BCH_BT_posterior = mean(post_Bayes_Tr, na.rm = TRUE))
 
@@
 
-data_long_post1 <- gather(mean_post_1, strategy, probability, QLS_posterior,Bayes_Transfer_posterior, factor_key=TRUE)
+data_long_post1 <- gather(mean_post_1, strategy, probability, Nash_posterior, RL_posterior,BCH_BT_posterior, factor_key=TRUE)
 
@@
 given the value of the observation.
-In the first experiment, we can see from the plots of fwg and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the QLS model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
+In the first experiment, we can see from the plots of FWG and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the QLS model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
 
@@
 Therefore, HMM modelling shows clear evidence in favour of strategy switching by participants, specifically after a few rounds of play.
-The strategy switching is consistently from ToM models towards Q-learning with states models in both experiments.
+The strategy switching is consistently from BCH models towards Q-learning with states models in both experiments.
 
@@
 
-The results of our first online experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
+The results of our first experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
 We used results on very early rounds for measuring transfer as they are unlikely to be tainted by any within game learning.
@@
 We will proceed by considering multiple potential answers to this question.
-First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
-An example is a spatial heuristic that consists of choosing "weapons" in a particular order.
-For instance, it is possible to keep winning against a level-k opponent by choosing actions in a particular spatial order such as cycling through them from left to right.
-This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
-We took this into account in designing experiment two by randomly shuffling the spatial order of action choices in each round.
-Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.
-
-A second possible hypothesis for learning the opponent’s strategy is the use of simple rules based on last round play (for instance, I play scissors whenever opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
+A possible hypothesis for learning the opponent’s strategy is the use of simple rules based on last round play (for instance, I play scissors whenever opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
 Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
-While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
+While this approach certainly seemed to be the best fit for many player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
 Indeed, learning the best action in a particular state is not transferable to a new game since the state space is different and there is no single mapping between the state spaces of the initial and latter games.
@@
 However, as we argued above, that would be inconsistent with the evidence for learning transfer.
-Breaking down likelihoods by trial and fitting a hidden markov model to the data with states being the various strategies that participants are assumed to be using, we showed evidence for within game switching of strategies.
-Participants start the early rounds of a new game acting in a way consistent with a Bayesian Theory of mind level, which would be accurate and generalisable but computationally expensive.
+Breaking down likelihoods by trial and fitting a hidden Markov model to the data with states being the various strategies that participants are assumed to be using, we showed evidence for within game switching of strategies.
+Participants start the early rounds of a new game acting in a way consistent with a Bayesian Bayesian Cognitive Hierarchy level, which would be accurate and generalisable but computationally expensive.
 However, as trials continue, participants seem to switch to a habitual type of learning (QL-models).
@@
 When a new game is started that is similar to a previously played game with the same opponent, participants need a way to transfer prior knowledge of the opponent and apply it to the new game in order to best respond.
-Adopting a Bayesian model based on ToM achieves the goal of transferring the opponent model and thus coming up with best responses in the early trials.
-However, Bayesian ToM models are computationally expensive and require higher order thinking (I think that you think that I think...).
+Adopting a Bayesian model based on BCH achieves the goal of transferring the opponent model and thus coming up with best responses in the early trials.
+However, Bayesian BCH models are computationally expensive and require higher order thinking (I think that you think that I think...).
 As such, as the games progresses, they may become burdensome and the higher amount of historical interaction in the new game allows participants to have enough data to start using the cognitively cheaper model-free learning strategies such as Q-learning.
@@
 Moreover, the ability to flexibly switch is also consistent with evidence from the literature on learning strategies in humans, showing that they indeed shift between model-based and model-free learning when the environment requires it [@Simon_Daw_11].
-
-\newpage
 

### 2021-06-04 Report/draft_report_v3.Rmd
added report in papaja and softmax to BCH models

@@
   Enter abstract here. Each new line herein must be indented, like this line.
+
+  Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and 
+  causal models of the environment. One way to build abstract representations of the environment when the task involves interactions with others is to build 
+  a model of the opponent that may inform what actions they are likely to take next. In this study, we propose to explore opponent modelling and its transfer with the use of
+  computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning. Through two differentiated experiments, we find that participants can
+  deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it. Moreover, we showed that participants transfer their learning to new games and that
+  the transfer is moderated by the level of  sophistication of the opponent. Computational modelling shows that it is likely that players start each game using a model-based
+  learning strategy that facilitates generalisation and opponent model transfer, but then switch to behaviour that is consistent with a  model-free learning strategy in the latter
+  stages of the interaction.
 

### 2021-06-04 Report/draft_report_v3.tex
added report in papaja and softmax to BCH models

@@
 
+Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and
+causal models of the environment. One way to build abstract representations of the environment when the task involves interactions with others is to build
+a model of the opponent that may inform what actions they are likely to take next. In this study, we propose to explore opponent modelling and its transfer with the use of
+computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning. Through two differentiated experiments, we find that participants can
+deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it. Moreover, we showed that participants transfer their learning to new games and that
+the transfer is moderated by the level of sophistication of the opponent. Computational modelling shows that it is likely that players start each game using a model-based
+learning strategy that facilitates generalisation and opponent model transfer, but then switch to behaviour that is consistent with a model-free learning strategy in the latter
+stages of the interaction.
+
 }
@@
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
-More formally, Perkins, Salomon, \& Others (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
+More formally, @perkins1992transfer defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
 This typically human skill has so far eluded modern AI agents.
@@
 Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-Lake, Ullman, Tenenbaum, \& Gershman (2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
+@Lake2017 argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
-There is evidence that people learn models of their opponents when they play repeated economic games (Stahl \& Wilson, 1995), engage in bilateral negotiations (Baarslag, Hendrikx, Hindriks, \& Jonker, 2016), or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors (Weerd, Verbrugge, \& Verheij, 2012).
+There is evidence that people learn models of their opponents when they play repeated economic games {[}@stahl1995players{]}, engage in bilateral negotiations {[}@baarslag2016learning{]}, or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors {[}@de2012higher{]}.
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind (Premack \& Woodruff, 1978) abilities play a role in determining human behaviour.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind {[}@premack1978does{]} abilities play a role in determining human behaviour.
 In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
 More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to the task of opponent modelling.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences {[}@mertens1990repeated{]} are particularly adapted to the task of opponent modelling.
 
 Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
-For instance, Ho, Camerer, \& Weigelt (1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
+For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
 They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-Camerer \& Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+@knez2000 test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
 They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
@@
 
-Juvina, Saleem, Martin, Gonzalez, \& Lebiere (2013) made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
+@Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
 However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games Cooper \& Kagel (2003, 2008) found that participants who have learned to play according to a Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+In a series of experiments using economic signalling games Cooper \& Kagel {[}-@cooper2003lessons; -@Cooper2008{]} found that participants who have learned to play according to a Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
 They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of a different payoff structure on an opponent's actions.
@@
 Most studies fail to offer a formal explanation of transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
-A notable exception is the effort by Haruvy \& Stahl (2012) to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
+A notable exception is the effort by @Haruvy2012 to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
 Participants played ten games, presented in 4x4 normal form (matrix payoffs).
@@
 They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on Stahl \& Wilson (1995), was able to capture participants' dynamic behavior and shows that the propensity to select particular rules is perfectly transferred across games.
+Their rule-learning model, based on @stahl1995players, was able to capture participants' dynamic behavior and shows that the propensity to select particular rules is perfectly transferred across games.
 
@@
 It is therefore important to have agents that \enquote{play like humans}, and one way of achieving that is to embed theses agents with human-like theory of mind abilities.
-Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally complex problems such as finding Nash equilibria.
+@simon1972theories explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally complex problems such as finding Nash equilibria.
 Instead, they will try to \enquote{satisfice} by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in \enquote{level-k} theory, first adopted by Stahl \& Wilson (1995).
+This concept finds its natural application in \enquote{level-k} theory, first adopted by @stahl1995players.
 It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogeneous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment Arad \& Rubinstein (2012).
+At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment @arad201211.
 Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
@@
 In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will either be a level-1 or level-2 player, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie, Doshi, \& Young, 2012).
+The agents will either be a level-1 or level-2 player, mimicking human theory of mind abilities and the limited recursion depth they exhibit {[}@goodie2012levels{]}.
 Our choice of using computer opponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
@@
 The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
-For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents, designed to take advantage of known patterns in human play such as imperfect randomization and heuristics use.
+For instance, @spiliopoulos2013strategic made humans play constant sum games against 3 computer opponents, designed to take advantage of known patterns in human play such as imperfect randomization and heuristics use.
 He found that human participants do adapt to the opponent they are facing.
-Shachat \& Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
+@shachat2004we made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
 They found that the players changed their strategies towards exploiting the deviations of the opponent from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
@@
 
-We extend this very simple model by adding a state space that consists of last round human and agent play.
-This is akin to using a Q-learning algorithm (Watkins \& Dayan, 1992).
-The update rule becomes:
+We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm {[}@watkins1992q{]}. The update rule becomes:
 
@@
 
-Next, we use a self-tuning Experience Weighted attraction model (Ho, Camerer, \& Chong, 2004).
+Next, we use a self-tuning Experience Weighted attraction model {[}@ho2004economics{]}.
 EWA models particularity is that they nest two seemingly different approaches, namely reinforcement learning and belief learning.
@@
 The result is added to either the pay-off received (when the indicator function is 0), or to \(\delta\) times the foregone pay-off (when indicator function is 1).
-We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play (Cheung \& Friedman, 1994).
-While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Ho et al., 2004).
+We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play {[}@cheung1994learning{]}.
+While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters {[}@camerer1997experience{]}, the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in {[}@ho2004economics{]}.
 
@@
 As such, as the games progresses, they may become burdensome and the higher amount of historical interaction in the new game allows participants to have enough data to start using the cognitively cheaper model-free learning strategies such as Q-learning.
-The preference for less computationally demanding strategies is well established (Wouter Kool, Joseph T.
-McGuire, Zev B.
-Rosen, Matthew M.
-Bovinick, 2011).
-Moreover, the ability to flexibly switch is also consistent with evidence from the literature on learning strategies in humans, showing that they indeed shift between model-based and model-free learning when the environment requires it (Simon \& Daw, 2011).
+The preference for less computationally demanding strategies is well established {[}@Kool\_2011{]}.
+Moreover, the ability to flexibly switch is also consistent with evidence from the literature on learning strategies in humans, showing that they indeed shift between model-based and model-free learning when the environment requires it {[}@Simon\_Daw\_11{]}.
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-arad201211}{}%
-Arad, A., \& Rubinstein, A. (2012). The 11-20 money request game: A level-k reasoning study. \emph{American Economic Review}, \emph{102}(7), 3561--3573.
-
-\leavevmode\hypertarget{ref-baarslag2016learning}{}%
-Baarslag, T., Hendrikx, M.
-J.
-C., Hindriks, K.
-V., \& Jonker, C.
-M.
-(2016).
-Learning about the opponent in automated bilateral negotiation: a comprehensive survey of opponent modeling techniques.
-\emph{Autonomous Agents and Multi-Agent Systems}, \emph{30}(5), 849--898.
-
-\leavevmode\hypertarget{ref-camerer1997experience}{}%
-Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
-
-\leavevmode\hypertarget{ref-knez2000}{}%
-Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
-
-\leavevmode\hypertarget{ref-cheung1994learning}{}%
-Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
-
-\leavevmode\hypertarget{ref-cooper2003lessons}{}%
-Cooper, D. J., \& Kagel, J. H. (2003). Lessons learned: generalizing learning across games. \emph{American Economic Review}, \emph{93}(2), 202--207.
-
-\leavevmode\hypertarget{ref-Cooper2008}{}%
-Cooper, D. J., \& Kagel, J. H. (2008). Learning and transfer in signaling games. \emph{Economic Theory}, \emph{34}(3), 415--439. \url{https://doi.org/10.1007/s00199-006-0192-5}
-
-\leavevmode\hypertarget{ref-goodie2012levels}{}%
-Goodie, A. S., Doshi, P., \& Young, D. L. (2012). Levels of theory-of-mind reasoning in competitive games. \emph{Journal of Behavioral Decision Making}, \emph{25}(1), 95--108.
-
-\leavevmode\hypertarget{ref-Haruvy2012}{}%
-Haruvy, E., \& Stahl, D.
-O.
-(2012).
-Between-game rule learning in dissimilar symmetric normal-form games.
-\emph{Games and Economic Behavior}, \emph{74}(1), 208--221.
-\url{https://doi.org/10.1016/j.geb.2011.06.001}
-
-\leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
-
-\leavevmode\hypertarget{ref-ho1998iterated}{}%
-Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
-
-\leavevmode\hypertarget{ref-Juvina2013}{}%
-Juvina, I., Saleem, M., Martin, J.
-M., Gonzalez, C., \& Lebiere, C.
-(2013).
-Reciprocal trust mediates deep transfer of learning between games of strategic interaction.
-\emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215.
-\url{https://doi.org/10.1016/j.obhdp.2012.09.004}
-
-\leavevmode\hypertarget{ref-Lake2017}{}%
-Lake, B.
-M., Ullman, T.
-D., Tenenbaum, J.
-B., \& Gershman, S.
-J.
-(2017).
-Building machines that learn and think like people.
-\emph{Behavioral and Brain Sciences}, \emph{40}.
-\url{https://doi.org/10.1017/S0140525X16001837}
-
-\leavevmode\hypertarget{ref-mertens1990repeated}{}%
-Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
-
-\leavevmode\hypertarget{ref-perkins1992transfer}{}%
-Perkins, D. N., Salomon, G., \& Others. (1992). Transfer of learning. \emph{International Encyclopedia of Education}, \emph{2}, 6452--6457.
-
-\leavevmode\hypertarget{ref-premack1978does}{}%
-Premack, D., \& Woodruff, G. (1978). Does the chimpanzee have a theory of mind? \emph{Behavioral and Brain Sciences}, \emph{1}(4), 515--526.
-
-\leavevmode\hypertarget{ref-shachat2004we}{}%
-Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
-
-\leavevmode\hypertarget{ref-Simon_Daw_11}{}%
-Simon, D.
-A., \& Daw, N.
-D.
-(2011).
-Environmental statistics and the trade-off between model-based and TD learning in humans.
-\emph{Advances in Neural Information Processing Systems 24: 25th Annual Conference on Neural Information Processing Systems 2011, NIPS 2011}, 1--9.
-
-\leavevmode\hypertarget{ref-simon1972theories}{}%
-Simon, H. A. (1972). Theories of bounded rationality. \emph{Decision and Organization}, \emph{1}(1), 161--176.
-
-\leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
-Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
-
-\leavevmode\hypertarget{ref-stahl1995players}{}%
-Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
-
-\leavevmode\hypertarget{ref-watkins1992q}{}%
-Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
-
-\leavevmode\hypertarget{ref-de2012higher}{}%
-Weerd, H.
-de, Verbrugge, R., \& Verheij, B.
-(2012).
-Higher-order social cognition in rock-paper-scissors: A simulation study.
-\emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3}, 1195--1196.
-
-\leavevmode\hypertarget{ref-Kool_2011}{}%
-Wouter Kool, Joseph T.
-McGuire, Zev B.
-Rosen, Matthew M.
-Bovinick.
-(2011).
-Decision Making and the Avoidance of Cognitive Demand.
-\emph{Experimental Psychology}.
-\url{https://doi.org/10.2996/kmj/1138846322}
-
-\leavevmode\hypertarget{ref-arad201211}{}%
-Arad, A., \& Rubinstein, A. (2012). The 11-20 money request game: A level-k reasoning study. \emph{American Economic Review}, \emph{102}(7), 3561--3573.
-
-\leavevmode\hypertarget{ref-baarslag2016learning}{}%
-Baarslag, T., Hendrikx, M.
-J.
-C., Hindriks, K.
-V., \& Jonker, C.
-M.
-(2016).
-Learning about the opponent in automated bilateral negotiation: a comprehensive survey of opponent modeling techniques.
-\emph{Autonomous Agents and Multi-Agent Systems}, \emph{30}(5), 849--898.
-
-\leavevmode\hypertarget{ref-camerer1997experience}{}%
-Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
-
-\leavevmode\hypertarget{ref-knez2000}{}%
-Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
-
-\leavevmode\hypertarget{ref-cheung1994learning}{}%
-Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
-
-\leavevmode\hypertarget{ref-cooper2003lessons}{}%
-Cooper, D. J., \& Kagel, J. H. (2003). Lessons learned: generalizing learning across games. \emph{American Economic Review}, \emph{93}(2), 202--207.
-
-\leavevmode\hypertarget{ref-Cooper2008}{}%
-Cooper, D. J., \& Kagel, J. H. (2008). Learning and transfer in signaling games. \emph{Economic Theory}, \emph{34}(3), 415--439. \url{https://doi.org/10.1007/s00199-006-0192-5}
-
-\leavevmode\hypertarget{ref-goodie2012levels}{}%
-Goodie, A. S., Doshi, P., \& Young, D. L. (2012). Levels of theory-of-mind reasoning in competitive games. \emph{Journal of Behavioral Decision Making}, \emph{25}(1), 95--108.
-
-\leavevmode\hypertarget{ref-Haruvy2012}{}%
-Haruvy, E., \& Stahl, D.
-O.
-(2012).
-Between-game rule learning in dissimilar symmetric normal-form games.
-\emph{Games and Economic Behavior}, \emph{74}(1), 208--221.
-\url{https://doi.org/10.1016/j.geb.2011.06.001}
-
-\leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
-
-\leavevmode\hypertarget{ref-ho1998iterated}{}%
-Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
-
-\leavevmode\hypertarget{ref-Juvina2013}{}%
-Juvina, I., Saleem, M., Martin, J.
-M., Gonzalez, C., \& Lebiere, C.
-(2013).
-Reciprocal trust mediates deep transfer of learning between games of strategic interaction.
-\emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215.
-\url{https://doi.org/10.1016/j.obhdp.2012.09.004}
-
-\leavevmode\hypertarget{ref-Lake2017}{}%
-Lake, B.
-M., Ullman, T.
-D., Tenenbaum, J.
-B., \& Gershman, S.
-J.
-(2017).
-Building machines that learn and think like people.
-\emph{Behavioral and Brain Sciences}, \emph{40}.
-\url{https://doi.org/10.1017/S0140525X16001837}
-
-\leavevmode\hypertarget{ref-mertens1990repeated}{}%
-Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
-
-\leavevmode\hypertarget{ref-perkins1992transfer}{}%
-Perkins, D. N., Salomon, G., \& Others. (1992). Transfer of learning. \emph{International Encyclopedia of Education}, \emph{2}, 6452--6457.
-
-\leavevmode\hypertarget{ref-premack1978does}{}%
-Premack, D., \& Woodruff, G. (1978). Does the chimpanzee have a theory of mind? \emph{Behavioral and Brain Sciences}, \emph{1}(4), 515--526.
-
-\leavevmode\hypertarget{ref-shachat2004we}{}%
-Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
-
-\leavevmode\hypertarget{ref-Simon_Daw_11}{}%
-Simon, D.
-A., \& Daw, N.
-D.
-(2011).
-Environmental statistics and the trade-off between model-based and TD learning in humans.
-\emph{Advances in Neural Information Processing Systems 24: 25th Annual Conference on Neural Information Processing Systems 2011, NIPS 2011}, 1--9.
-
-\leavevmode\hypertarget{ref-simon1972theories}{}%
-Simon, H. A. (1972). Theories of bounded rationality. \emph{Decision and Organization}, \emph{1}(1), 161--176.
-
-\leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
-Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
-
-\leavevmode\hypertarget{ref-stahl1995players}{}%
-Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
-
-\leavevmode\hypertarget{ref-watkins1992q}{}%
-Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
-
-\leavevmode\hypertarget{ref-de2012higher}{}%
-Weerd, H.
-de, Verbrugge, R., \& Verheij, B.
-(2012).
-Higher-order social cognition in rock-paper-scissors: A simulation study.
-\emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3}, 1195--1196.
-
-\leavevmode\hypertarget{ref-Kool_2011}{}%
-Wouter Kool, Joseph T.
-McGuire, Zev B.
-Rosen, Matthew M.
-Bovinick.
-(2011).
-Decision Making and the Avoidance of Cognitive Demand.
-\emph{Experimental Psychology}.
-\url{https://doi.org/10.2996/kmj/1138846322}
 

### 2021-06-04 Report/draft_upgrade_final.tex
added report in papaja and softmax to BCH models

--- 2020-10-30 Report/draft_report_v3.tex
@@
 
-\shorttitle{Draft-3}
+\shorttitle{Upgrade Report}
 \affiliation{
@@
 \newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-\usepackage{lineno}
-
-\linenumbers
-
+\shorttitle{}
+\thispagestyle{headings}
 \title{Transfer of Learned Opponent Models in Zero Sum Games}
@@
 \abstract{
-Enter abstract here. Each new line herein must be indented, like this line.
+Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and
+causal models of the environment. One way to build abstract representations of the environment when the task involves interactions with others is to build
+a model of the opponent that may inform what actions they are likely to take next. In this study, we propose to explore opponent modelling and its transfer with the use of
+computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning. Through two differentiated experiments, we find that participants can
+deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it. Moreover, we showed that participants transfer their learning to new games and that
+the transfer is moderated by the level of sophistication of the opponent. Computational modelling shows that it is likely that players start each game using a model-based
+learning strategy that facilitates generalisation and opponent model transfer, but then switch to behaviour that is consistent with a model-free learning strategy in the latter
+stages of the interaction.
 
@@
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
-More formally, Perkins, Salomon, \& Others (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
+More formally, Perkins \& Salomon (1992) define transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
 This typically human skill has so far eluded modern AI agents.
@@
 
-Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
-For instance, Ho, Camerer, \& Weigelt (1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
-They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-Camerer \& Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
-They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
-They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity.
-If the games were only strategically similar, then the transfer was much weaker.
-
-Juvina, Saleem, Martin, Gonzalez, \& Lebiere (2013) made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
-However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games Cooper \& Kagel (2003, 2008) found that participants who have learned to play according to a Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
-They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of a different payoff structure on an opponent's actions.
-
-Most studies fail to offer a formal explanation of transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
-A notable exception is the effort by Haruvy \& Stahl (2012) to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
-Participants played ten games, presented in 4x4 normal form (matrix payoffs).
-Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
-They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on Stahl \& Wilson (1995), was able to capture participants' dynamic behavior and shows that the propensity to select particular rules is perfectly transferred across games.
-
 In exploring opponent modelling and learning transfer, most studies adopted two types of opponents in the experimental setting.
@@
 One of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-The strategies implemented by the computer opponents had a style of play that was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+The strategies implemented by the computer opponents had a style of play that was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with any precision, or at detecting patterns from long sequences of past play due to cognitive constraints.
 It is therefore important to have agents that \enquote{play like humans}, and one way of achieving that is to embed theses agents with human-like theory of mind abilities.
@@
 In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-Each point worth £0.02.
+Each point is worth £0.02.
 An example of the interface for the rock-paper-scissors game is provided in Figure~\ref{fig:feedback-rps-exp2}.
@@
 
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-avg-scores-game-1}
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-avg-scores-game-1}
 
@@
 To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game ( F(2,100) = 8.54, \(\eta^{2}\) = 0.05, p \textless{} 0.001), showing that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in the NUMBERS game was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
-The score in RPS was not significantly different from the score in NUMBERS ( t(100) = 0.45 , p = 0.65).
-The main effect of Block ( F(1,50) = 22.51 , p \textless{} .001, \(\eta^{2}\) = 0.03) shows that the average score in the first half of games (M = 0.29) was significantly lower than in the second half of the games played (M = 0.40), which translates to within-game learning.
+There was a main effect of Game (F(2,100) = 8.54, \(\eta^{2}\) = 0.05, p \textless{} 0.001), showing that average scores varied significantly over the games.
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game (t(100) =3.78, p = 0.0008), and the performance in the NUMBERS game was significantly lower than FWG game (t(100) = -3.32 , p = 0.0024).
+The score in RPS was not significantly different from the score in NUMBERS (t(100) = 0.45 , p = 0.65).
+The main effect of Block (F(1,50) = 22.51 , p \textless{} .001, \(\eta^{2}\) = 0.03) shows that the average score in the first half of games (M = 0.29) was significantly lower than in the second half of the games played (M = 0.40), which translates to within-game learning.
 The main effect of Condition (F(1,50) = 5.44, p = .024, \(\eta^{2}\) = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
@@
 
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-3factor-plot-1}
-
-}
-
-\caption{Average scores by game, block and condition}\label{fig:exp1-3factor-plot}
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-3factor-plot-1}
+
+}
+
+\caption{Boxplots of scores by game, block and condition}\label{fig:exp1-3factor-plot}
 \end{figure}
@@
 This is indicative of the significant within-game learning happening in the first game when players have no experience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some experience playing against the opponent and start with higher scores indicative of transfer.
-There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, \(\eta^{2}\) = 0.01), which indicates, as seen in Figure~\ref{fig:exp1-3factor-plot} that within-game learning changes across games also depend on the sophistication of the opponent.
+There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88, p = .023, \(\eta^{2}\) = 0.01), which indicates, as seen in Figure~\ref{fig:exp1-3factor-plot} that within-game learning changes across games also depend on the sophistication of the opponent.
 For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than against level-1 opponent.
@@
 
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-score-by-opp-1}
-
-}
-
-\caption{Mean and CI of early scores by game and opponent}\label{fig:exp1-score-by-opp}
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-score-by-opp-1}
+
+}
+
+\caption{Mean and 95\% confidence Intervals of early scores by game and opponent}\label{fig:exp1-score-by-opp}
 \end{figure}
@@
 
-\newpage
-
-\hypertarget{second-experiment}{%
-\section{Second Experiment}\label{second-experiment}}
+\hypertarget{experiment-2}{%
+\section{Experiment 2}\label{experiment-2}}
 
 We ran a second experiment with various differentiated features to improve the opportunity to measure learning transfer.
-Instead of making participants face either the level-1 or level-2 player throughout, we made them face both opponent sequentially.
+Instead of making participants face either the level-1 or level-2 player throughout, we made them face both opponents sequentially.
 Because there were two distinct opponents, requiring potentially holding two opponent models in memory, we also made it easier to recall the results of past rounds by providing participants with the opportunity to see the history of the game since the beginning of each interaction.
@@
 
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-score-by-opp-1}
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-score-by-opp-1}
 
@@
 
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-early-scores-1}
-
-}
-
-\caption{Average early round scores and confidence intervals by game and opponent for experiment 2}\label{fig:exp2-early-scores}
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-early-scores-1}
+
+}
+
+\caption{Average early round scores and 95\% confidence intervals by game and opponent for experiment 2}\label{fig:exp2-early-scores}
 \end{figure}
@@
 
-\[ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) \]
+\[ V_{t+1}(a) = V_{t}(a) + \alpha \times ( R_{t}  - V_{t}(a)) \]
 
@@
 
-\[ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) \]
+\[ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha \times( R_{t}  + \gamma \times \underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) \]
 
@@
 \hypertarget{ewa-models}{%
-\subsubsection{EWA Models}\label{ewa-models}}
+\subsection{EWA Models}\label{ewa-models}}
 
@@
 After playing \(s_{i}^{j}\) at time \(t\), player i pay-off is denoted \(\pi_{i}(s_{i}^{j},s_{-i}(t))\), and the actual pay-off the player received is \(\pi_{i}(t)\).
-
 The EWA model is based on updating \enquote{Attractions} for each action over time.
@@
 
-\[P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} \]
+\[P_{i}^{j}(t+1) = \frac{e^{\lambda  A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda A_{i}^{k}(t)}} \]
 
@@
 
-\[ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} \]
-
-Here, I(x,y) is the indicator function equal to 1 if \(x = y\) and 0 otherwise.
+\[ A_{i}^{j}(t) =  \frac{\phi \times N(t-1) \times A_{i}^{j}(t-1) + [ \delta + (1-\delta) \times I(s_{i}^{j},s_{i}(t))] \times \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi \times N(t-1) + 1} \]
+
+Here, \(I(x,y)\) is the indicator function equal to 1 if \(x = y\) and 0 otherwise.
 A simple way to think about this update rule is that attractions are multiplied by a parameter that represents experience (\(N(t-1)\)) which is itself decaying by a weight \(\phi\).
@@
 \hypertarget{tom-models}{%
-\subsubsection{ToM models}\label{tom-models}}
-
-In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
-We use values of k in \({0,1,2}\).
+\subsection{ToM models}\label{tom-models}}
+
+In this set of models, we assume that participants start with a prior belief that the opponent is a level-k agent, with uniform probability of the level \(k \in \{ 0, 1, 2\}\), and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
+More formally, if we define \(D_{t}\) as data available at time \(t\) then the probability of the opponent being a level-k is updated using:
+
+\[ P(level=k | D_{t})  \propto  P(D_{t}|level=k ) \times P(level=k)\]
+
 These models also assume the opponent can deviate from these level-k strategies and play randomly with probability \(\theta\), a parameter to be fit.
+We also assume that participants base their actions on their beliefs about the level of the opponent, so actions get chosen probabilistically using a softamx choice rule with probabilities of each opponent level as inputs.
 We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
 In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between transfer)
-
-Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
+In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (within but no between transfer).Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
 In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
-
-We fit the above two models to experiment 1 data.
 In experiment two, on top of these two models, we fit another model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
@@
 \hypertarget{estimation-and-model-comparison}{%
-\subsubsection{Estimation and model comparison}\label{estimation-and-model-comparison}}
+\subsection{Estimation and model comparison}\label{estimation-and-model-comparison}}
 
@@
 
+In experiment 1, we fit a total of 5 models: A baseline model assuming random play (Nash), a Bayesian Theory of mind model allowing transfer betwen games (TOM\_BT) and another with no transfer between games (TOM\_NBT), as well as a Q-learning model with state space consisting of last round play (QL\_states), and finally a self tuning EWA model with the same state space (STEWA\_states).
+In experiment 2, because participants were interacting with each opponent twice within each game, we allowed models to transfer learning within games between the first and second interactions.
+Therefore on top of the two ToM models mentionned above (ToM\_BT and Tom\_NBT), we also allow the Q-learning model with states to either have the ability to transfer learning between the first and second interaction (QLS\_Tr) or not (QLS\_NT).
+Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (STEWA\_Tr) or without transfer (STEWA\_NT).
+Counting the base model wiht random play (Nash) we therefore fit a total of 8 models in experiment 2.
+
 \hypertarget{experiment-1-modelling}{%
@@
 Figure~\ref{fig:exp1-comp-models} shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning with states defined by last round play.
+Table ~\ref{tab:exp1weightstable} shows the model BIC weights as well as the number of participants best fit by each model.
 
@@
 
-Table ~\ref{tab:exp1weightstable} shows the model BIC weights as well as the number of participants best fit by each model.
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-comp-models-1}
+\begin{figure}
+
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-comp-models-1}
 
@@
 
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-cumScores-1}
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-cumScores-1}
 
@@
 
-\hypertarget{experiment-2}{%
-\subsection{Experiment 2}\label{experiment-2}}
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-comp-models-1}
+\hypertarget{experiment-2-1}{%
+\subsection{Experiment 2}\label{experiment-2-1}}
+
+\begin{figure}
+
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-comp-models-1}
 
@@
 \end{figure}
-
-\begin{verbatim}
-##                Nash TOM BT TOM NBT TOM NT QLS NT QLS Tr STEWA NT STEWA Tr
-## BIC weights    0.13   0.02    0.06   0.06   0.18   0.49     0.04     0.03
-## Count best fit 9.00   0.00    2.00   3.00   8.00  27.00     1.00     0.00
-\end{verbatim}
 
@@
 
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-cumScores-1}
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-cumScores-1}
 
@@
 
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-lik-by-tr-1}
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-lik-by-tr-1}
 
@@
 
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-lik-by-tr-1}
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-lik-by-tr-1}
 
@@
 
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp1-posteriors-plot-1}
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-posteriors-plot-1}
 
@@
 The posterior probability is the probability that an observation comes from a component distribution a posteriori, i.e.~given the value of the observation.
-In the first experiment, we can see from the plots of fwg and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the QLS model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
-
-\hypertarget{experiment-2-1}{%
-\subsubsection{Experiment 2:}\label{experiment-2-1}}
-
-\begin{figure}
-
-{\centering \includegraphics{draft_report_v3_files/figure-latex/exp2-posteriors-plot-1}
+In the first experiment, we can see from the plots of FWG and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the QLS model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
+
+\hypertarget{experiment-2-2}{%
+\subsubsection{Experiment 2:}\label{experiment-2-2}}
+
+\begin{figure}
+
+{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-posteriors-plot-1}
 
@@
 We will proceed by considering multiple potential answers to this question.
-First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
-An example is a spatial heuristic that consists of choosing \enquote{weapons} in a particular order.
-For instance, it is possible to keep winning against a level-k opponent by choosing actions in a particular spatial order such as cycling through them from left to right.
-This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
-We took this into account in designing experiment two by randomly shuffling the spatial order of action choices in each round.
-Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.
-
-A second possible hypothesis for learning the opponent's strategy is the use of simple rules based on last round play (for instance, I play scissors whenever opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc\ldots{}).
+A possible hypothesis for learning the opponent's strategy is the use of simple rules based on last round play (for instance, I play scissors whenever opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc\ldots{}).
 Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
-While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
+While this approach certainly seemed to be the best fit for many player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
 Indeed, learning the best action in a particular state is not transferable to a new game since the state space is different and there is no single mapping between the state spaces of the initial and latter games.
@@
 However, as we argued above, that would be inconsistent with the evidence for learning transfer.
-Breaking down likelihoods by trial and fitting a hidden markov model to the data with states being the various strategies that participants are assumed to be using, we showed evidence for within game switching of strategies.
+Breaking down likelihoods by trial and fitting a hidden Markov model to the data with states being the various strategies that participants are assumed to be using, we showed evidence for within game switching of strategies.
 Participants start the early rounds of a new game acting in a way consistent with a Bayesian Theory of mind level, which would be accurate and generalisable but computationally expensive.
@@
 
-\newpage
-
 \hypertarget{conclusion}{%
@@
 
-\leavevmode\hypertarget{ref-knez2000}{}%
-Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
-
 \leavevmode\hypertarget{ref-cheung1994learning}{}%
@@
 
-\leavevmode\hypertarget{ref-cooper2003lessons}{}%
-Cooper, D. J., \& Kagel, J. H. (2003). Lessons learned: generalizing learning across games. \emph{American Economic Review}, \emph{93}(2), 202--207.
-
-\leavevmode\hypertarget{ref-Cooper2008}{}%
-Cooper, D. J., \& Kagel, J. H. (2008). Learning and transfer in signaling games. \emph{Economic Theory}, \emph{34}(3), 415--439. \url{https://doi.org/10.1007/s00199-006-0192-5}
-
 \leavevmode\hypertarget{ref-goodie2012levels}{}%
@@
 
-\leavevmode\hypertarget{ref-Haruvy2012}{}%
-Haruvy, E., \& Stahl, D.
-O.
-(2012).
-Between-game rule learning in dissimilar symmetric normal-form games.
-\emph{Games and Economic Behavior}, \emph{74}(1), 208--221.
-\url{https://doi.org/10.1016/j.geb.2011.06.001}
-
 \leavevmode\hypertarget{ref-ho2004economics}{}%
 Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
-
-\leavevmode\hypertarget{ref-ho1998iterated}{}%
-Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
-
-\leavevmode\hypertarget{ref-Juvina2013}{}%
-Juvina, I., Saleem, M., Martin, J.
-M., Gonzalez, C., \& Lebiere, C.
-(2013).
-Reciprocal trust mediates deep transfer of learning between games of strategic interaction.
-\emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215.
-\url{https://doi.org/10.1016/j.obhdp.2012.09.004}
 
@@
 \leavevmode\hypertarget{ref-perkins1992transfer}{}%
-Perkins, D. N., Salomon, G., \& Others. (1992). Transfer of learning. \emph{International Encyclopedia of Education}, \emph{2}, 6452--6457.
+Perkins, D. N., \& Salomon, G. (1992). Transfer of learning. \emph{International Encyclopedia of Education}, \emph{2}, 6452--6457.
 

### 2021-06-04 Report/draft_upgrade_v1.Rmd
added report in papaja and softmax to BCH models

--- 2021-06-04 Report/draft_report_v3.Rmd
@@
 abstract: |
-  Enter abstract here. Each new line herein must be indented, like this line.
-
   Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and 
@@
 
-### ToM models
-
-In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
-We use values of k  in ${0,1,2}$.
+## ToM models
+
+In this set of models, we assume that participants start with a prior belief that the opponent is a level-k agent, with uniform probability of the level $k \in \{ 0, 1, 2\}$, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
+More formally, if we define $D_{t}$ as data available at time $t$ then the probability of the opponent being a level-k is updated using:
+
+$$ P(level=k | D_{t})  \propto  P(D_{t}|level=k ) \times P(level=k)$$
+
 These models also assume the opponent can deviate from these level-k strategies and play randomly with probability $\theta$, a parameter to be fit.
+We also assume that participants base their actions on their beliefs about the level of the opponent, so actions get chosen probabilistically using a softamx choice rule with probabilities of each opponent level as inputs.
 We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
 In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between transfer)
-
-Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
+In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (within but no between transfer).Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
 In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
-
-We fit the above two models to experiment 1 data.
 In experiment two, on top of these two models, we fit another model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
 
-### Estimation and model comparison
+## Estimation and model comparison
 In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
 Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
+
+In experiment 1, we fit a total of 5 models: A baseline model assuming random play (Nash), a Bayesian Theory of mind model allowing transfer betwen games (TOM_BT) and another with no transfer between games (TOM_NBT), as well as a Q-learning model with state space consisting of last round play (QL_states), and finally a self tuning EWA model with the same state space (STEWA_states).
+In experiment 2, because participants were interacting with each opponent twice within each game, we allowed models to transfer learning within games between the first and second interactions.
+Therefore on top of the two ToM models mentionned above (ToM_BT and Tom_NBT), we also allow the Q-learning model with states to either have the ability to transfer learning between the first and second interaction (QLS_Tr) or not (QLS_NT).
+Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (STEWA_Tr) or without transfer (STEWA_NT).
+Counting the base model wiht random play (Nash) we therefore fit a total of 8 models in experiment 2.
 
@@
 
-ggplot(data_long_post1,aes(x=round,y=probability,colour=strategy)) +
+p <- ggplot(data_long_post1,aes(x=round,y=probability,colour=strategy)) +
   geom_line() +
   facet_grid(game~condition)
+
+p
+
+# p + theme(legend.position = c(0.3,0.5)
+#           ,legend.background = element_rect(fill = "#ffffffaa", colour = NA))
 
@@
 
-\newpage
-
 # Conclusion

### 2021-06-04 Report/paper_draft_2021.Rmd
added report in papaja and softmax to BCH models

--- 2021-06-04 Report/CSS_submission_2021.Rmd
@@
 # Introduction
+
 Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
+This ability relies on important cognitive building blocks, such as an abstract representation of concepts underlying tasks [@Lake2017].
+One way to form these representations when the task involves interactions with others, is to build a model of the person we are interacting with that offers predictions of the actions they are likely to take next.
+There is evidence that people learn such models of their opponents when playing repeated economic games [@stahl1995players].
+
+In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to this task.
+The early literature on learning transfer in repeated games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously [@ho1998iterated; @knez2000].
+This doesn't allow for the possibility of learning about the opponent's strategy and potentially exploiting it.
+
+When studies have specifically explored this aspect, they have used computer opponents that were generally programmed not to change their strategies over the course of the task, allowing better experimental control.
+However, they have mostly looked at the ability of players to detect and exploit action-based learning rules [@spiliopoulos2013strategic; @shachat2004we].
+The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with precision, or at detecting patterns from long sequences of past play.
+Thus, in this study, we aim to explore opponent modelling and its transfer with the use of computer agents endowed with human-like limited degrees of iterated reasoning.
+The agents are either a level-1 or level-2 player, mimicking ``I know that you know that I know'' type reasoning, and the limited recursion depth they exhibit [@goodie2012levels].
+A level 1 player adapts their play to what they believe their opponent will play, without considering what their opponent might believe they will play.
+A level 2 player, on the other hand, takes their opponent's belief about their actions into account, assuming they face a level 1 player, and choosing actions to beat the actions of that player.
+The choice of this type of strategy is also motivated by evidence that humans strategically use information from last round play of their opponents in zero sum games [@batzilis; @wang2014social].
+
+We have conducted two experiments where participants interact with a computer opponent.
+In each experiment, we measure transfer of learning about the opponent's strategy between games with varying degrees of similarity.
+The first two games we use are structurally identical except for action labels.
+In the first experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure.
+In the first experiment, participants face the same opponent throughout the three games, and the opponents are randomised to be either level-1 or level-2 players.
+In the second experiment, participants faced both level-1 and level-2 opponent sequentially, with the order in which they are faced randomised across participants.
+
+<!-- Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
@@
 @Lake2017 argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
-
-One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
+-->
+
+<!-- One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
 Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations.
@@
 Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to the task of opponent modelling.
+-->
 
@@
 
-In exploring opponent modelling and learning transfer, most studies adopted two types of opponents in the experimental setting.
+<!-- In exploring opponent modelling and learning transfer, most studies adopted two types of opponents in the experimental setting.
 Either human participants were matched with other participants or they played against a computer algorithm.
@@
 Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below, and so on.
-
-In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
+-->
+
+<!-- In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
 The agents will either be a level-1 or level-2 player, mimicking human theory of mind abilities and the limited recursion depth they exhibit [@goodie2012levels].
@@
 They found that the players changed their strategies towards exploiting the deviations of the opponent from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
-We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
-The first two games we use are structurally identical except for action labels.
-In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure.
-In the first experiment, participants face the same opponent throughout the three games, and the opponents are randomised to be either level-1 or level-2 players.
-In the second experiment, participants faced both level-1 and level-2 opponent sequentially, with the order in which they are faced randomised across participants.
+-->
 
@@
 Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The study used a 2 (computer opponent: level 1 or  level 2) by 3 (games: rock-paper-scissors, fire-water-grass, numbers) design, with repeated measures on the second factor.
+The experiment used a 2 (computer opponent: level 1 or level 2) by 3 (games: rock-paper-scissors, fire-water-grass, numbers) design, with repeated measures on the second factor.
+Participants were randomly assigned to one of the two levels of the first factor.
 
 ### Tasks
-In the first experiment, the three games were rock-paper-scissors, fire-water-grass and the numbers game.
-A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
+In the first experiment, participants played the three games against their computer opponent.
+These games were rock-paper-scissors, fire-water-grass, and the numbers game.
+A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between the two player's actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
 If one player chooses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
 Otherwise it is a draw and both players receive a reward of 0.
-It has a unique MSNE consisting of randomly playing one of the three options each time.
-The second game is identical to Rock-Paper-Scissors in all but action labels.
-We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
-We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
-Finally, the numbers game is a generalization of rock-paper-scissors.
+RPS has a unique mixed-strategy Nash equilibrium, which consists of each player in each round randomly selecting from the three options with uniform probability.
+The Fire-Water-Grass (FWG) game is identical to RPS in all but action labels: Fire burns grass, water extinguishes fire, and grass absorbs water.
+We use this game as we are interested in whether learning is transferred in a fundamentally similar game where the only difference is in the description of the possible actions.
+This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level 1 or 2 player.
+Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'', as might be learned by a simple reinforcement learning algorithm, will not be able to generalize to such a game, as these contingencies are tied to the labels of the actions.
+The numbers game is a generalization of RPS.
 In the variant we use, 2 participants concurrently pick a number between 1 and 5.
-To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent.
+To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by their opponent.
 For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
 To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
-This game has a structure similar to RPS in which every action is dominated by exactly one choice.
-All other possible combination of choices that are not consecutive are considered ties.
-A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score.
-Similar to RPS, the MSNE is to play each action with equal probability in a random way.
+This game has a structure similar to RPS in which every action is dominated by exactly one other action.
+All other possible combinations of choices are considered ties.
+Similar to RPS and FWG, the mixed-strategy Nash equilibrium is to play each action with equal probability in a random way.
+
+The computer opponent was programmed to use either a level-1 or level-2 strategy in all the games.
+A level 1 player is defined as a player who best responds to a level 0 player.
+A level 0 player plays in a non-strategic way and does not consider their opponent's actions.
+Here, we assume a level 0 player simply repeats their previous action.
+There are other ways to define a level 0 player.
+For instance, as repeating their action if it resulted in a win, and choosing randomly from the remaining actions otherwise.
+As a best response to a random action is itself a random action, defining a level 0 player in such a way would make a level 1 opponent's strategy much harder to discern.
+Because we are mainly interested in generalization of knowledge of an opponent's strategy to other games, which rests on good knowledge of this strategy, we opted for this more deterministic formulation of a level 0 player (whilst also introducing some randomness in the computer opponent's play).
+A level-2 computer opponent, will assume in turn that the participant is a level-1 opponent, playing according to the strategy just described.
+We also introduced some noise over the actions of computer opponents making them play randomly in 10\% of all trials.
+
+\begin{table}[bth!]
+\centering
+\begin{tabular}{||c c c c||} 
+ \hline
+ Human last & Agent last & level-1 Agent & level-2 Agent\\ [0.5ex] 
+ \hline\hline
+ Paper & Rock & Scissors & Scissors \\ 
+ Scissors  & Scissors & Rock & Paper \\
+ Rock & Paper & Paper & Rock \\
+ ... & ... & ... & ... \\ [1ex] 
+ \hline
+\end{tabular}
+\caption{Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round.}
+\label{table:1}
+\end{table}
 
 ### Procedure
-Participants played 3 games sequentially against the same computer opponent.
+
+Participants were informed they would play three different games against the same computer opponent.
+Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
+After providing informed consent and reading the instructions, participants answered a number of comprehension questions.
+They then played the three games against their opponent in the order RPS, FGW, and NUMBERS.
+A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
+The score was calculated as the number of wins minus the number of losses.
+Ties did not affect the score.
+In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
+Each point is worth £0.02.
+An example of the interface for the RPS game is provided in Figure\ \@ref(fig:feedback-rps-exp2).
+After playing all the games, participants were asked questions about their beliefs about the computer opponent, related to whether they think they have learned their strategy and how hard they found playing against that particular opponent.
+They were then debriefed and thanked for their participation.
+
+<!-- Participants played 3 games sequentially against the same computer opponent.
 The computer opponent either used a level-1 or level-2 strategy.
@@
 An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps-exp2).
+-->
 
@@
 ```
-
-Looking at the aggregate scores (See Figure\ \@ref(fig:exp1-avg-scores-game) ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
+On average, participants obtained the lowest score in the RPS game ($M = 0.289$, $SD = 0.348$), followed by NUMBERS ($M = 0.31$, $SD = 0.347$).
+Participants' performance was highest in the FWG game ($M = 0.454$, $SD = 0.354$).
+Scores in each game were significantly different from 0, the expected score of random play (RPS: $t(51) = 7.26$, $p < .001$;  FWG:  $t(51) = 10.04$ , $p < .001$; NUMBERS: $t(51) = 7.17$, $p < .001$).
+To assess learning within and between games, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants.
+This showed a main effect of Game ($F(2,100) = 8.54$, $\eta^{2}  = 0.05$,  $p < .001$), indicating that average scores varied significantly over the games.
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ($t(100) =3.78$, $p < .001$) and the NUMBERS game ($t(100) = 3.32$ , $p = .002$).
+The score in RPS was not significantly different from the score in NUMBERS ($t(100) = 0.45$ , $p = .65$).
+The main effect of Block ($F(1,50) = 22.51$ ,  $\eta^{2} = 0.03$, $p < .001$) shows that the score in the first half of each game ($M = 0.29$) was significantly lower than in the second half ($M = 0.40$), which indicates within-game learning.
+The main effect of Condition ($F(1,50) = 5.44$, $\eta^{2} = 0.05$, $p = .024$) indicates that scores were higher against the level-1 player ($M = 0.43$) than against the level-2 player ($M = 0.27$).
+Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
+
+<!-- Looking at the aggregate scores (See Figure\ \@ref(fig:exp1-avg-scores-game) ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
 Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, $p$ < 0.001 ;  FWG:  t(51) = 10.04 , $p$ < 0.001 ; NUMBERS: t(51) = 7.17, $p$ < 0.001).
-To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
+-->
+<!-- To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
 There was a main effect of Game (F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games.
@@
 This indicates that it was harder for participants, on average, to exploit the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
-
-```{r exp1-3factor-plot, fig.cap = "Boxplots of scores by game, block and condition", fig.align = "center"}
+-->
+
+```{r exp1-3factor-plot, include= FALSE, fig.cap = "Boxplots of scores by game, block and condition", fig.align = "center"}
 
@@
 
-Finally, the analysis showed a significant block by game interaction ( F(2,100) = 6.92 , p = .002, $\eta^{2}$ = 0.02), indicating that within-game learning differed between the games.
+<!-- Finally, the analysis showed a significant block by game interaction ( F(2,100) = 6.92 , p = .002, $\eta^{2}$ = 0.02), indicating that within-game learning differed between the games.
 Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p <.0001), while there was no significant difference between block scores for the other two games.
@@
 The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
+-->
 
@@
 
-As a measure for learning transfer, we focus on participants’ scores in the first 5 rounds excluding the initial round (rounds 2-6).
+<!-- As a measure for learning transfer, we focus on participants’ scores in the first 5 rounds excluding the initial round (rounds 2-6).
 We exclude the very first round as the computer opponent plays randomly here and there is no opportunity yet for the human player to exploit their opponent's strategy.
@@
 For the RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
+-->
+
+As a measure for learning transfer, we focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game (see Figure \ref{fig:exp1-score-by-opp}).
+We exclude the very first round as the computer opponent plays randomly here and there is no opportunity yet for the human player to exploit their opponent's strategy.
+Players with no knowledge of their opponent's strategy are expected to perform at chance level in these early rounds.
+Positive scores in rounds 2-6 reflect generalization of prior experience.
+The FWG early score score is significantly higher than 0 ($t(148.85) = 4.584$, $p < .001$).
+This is also the case for the NUMBERS game ($t(148.85) = 3.00$, $p = .009$).
+We did not expect positive scores for the RPS game, as it was the first game played and there was no opportunity for learning about the opponent's strategy.
+Scores in this game was indeed not significantly different from 0 ($t(148.85) = 1.04$ , $p = .89$).
 
@@
 (ref:figure4-caption) Mean and standard error of early scores by game and opponent
-```{r exp1-score-by-opp, fig.cap = "(ref:figure4-caption)", fig.align ='center'}
-
-p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","Numbers"), ylab = "Early rounds score", xlab = "Games", legend.title = "Games")
+```{r exp1-early-score-by-opp, fig.cap = "(ref:figure4-caption)", fig.align ='center'}
+
+p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","Numbers"), ylab = "Early rounds score", xlab = "Games")
 
@@
 
-Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
+<!-- Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
 Figure\ \@ref(fig:exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players as well as the $95$ percent confidence interval for the mean.
@@
 For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
-
-```{r ANOVA early exp1, include = TRUE, warning=FALSE}
+-->
+
+Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
+We expected better transfer between more similar games (i.e.
+better transfer from RPS to FWG than from RPS/FWG to NUMBERS), and worse transfer for the more sophisticated level 2 agent.
+Figure~\ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 players.
+To explore this, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) repeated measures ANOVA with the first factor varying between participants.
+There was a main effect of Game ($F(2,92) = 3.35$, $\eta^{2}  = 0.04$,  $p < .04$).
+We then run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( $t(150) = 3.96$, $p < .001$) and NUMBERS ($t(150) = 3.74$, $p < .001$).
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ($t(150) = 2.48$, $p = .01$) but not to the dissimilar game of NUMBERS.
+
+### Experiment 1 discussion:
+
+These results indicate that learning transfer to the more dissimilar game (NUMBERS) we found earlier is exclusively driven by level-1 facing players, as average early round scores in the NUMBERS game of level-2 facing players are close to 0.
+Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar FWG game, but only those facing the less sophisticated opponent are able to generalise to the less similar NUMBERS game.
+
+```{r ANOVA early exp1, include = FALSE, warning=FALSE}
 
@@
 
-### Discussion Experiment 1
-
-Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
+<!-- ### Discussion Experiment 1  -->
+
+<!-- Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
 We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game.
 Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
+-->
 
@@
 Figure\ \@ref(fig:feedback-rps-exp2) shows an example of showing interaction history in the RPS game.
-Finally, we changed the third game to a penalty shootout game, which has the same number of actions as the first two.
+Finally, we changed the third game to a penalty shootout game, whith participants aiming to score a goal and opponents playing the role of goal keepers.
+Whilst this game has the same number of actions as the first two, it is strategically dissimilar.
+Unlike the third game in the first experiment, it did not have a cyclical hierarchy between actions, making it harder to win by just following simple heuristics leveraging this cyclicality.
 If we see evidence for differential play against opponents, it would show participants adapting their strategies to the opponent they are facing, which is indicative of opponent modelling.
@@
 
-To gain more insight into how participants played the games against the computer opponents, we estimated and compared different computational models of strategies the players may have been using to learn how to beat the opponent.
+To gain more insight into participants' strategies against their computer opponents, we constructed and tested several computational models of strategy learning.
 The baseline model assumes play is random, and each potential action is chosen with equal probability.
 Note that this corresponds to the Nash equilibrium strategy.
-In this section, we will go through the various models we have used and explain how they update what they learn about the game or the opponent
-
-## Reinforcement Learning
-
-We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
-We will use a simple delta learning update rule:
-
-$$ V_{t+1}(a) = V_{t}(a) + \alpha \times ( R_{t}  - V_{t}(a)) $$
-
-Where $V_{t}(a)$ is the value associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
-The probability of player $i$ choosing action $j$ at time $t+1$ denoted by $P_{i}^{j}(t+1)$ is based on action values using a softmax choice rule:
-
-$$P_{i}^{j}(t+1) = \frac{e^{\lambda . V_{t}^{j}(a)}}{\sum_{k=1}^{m_{i}}e^{\lambda . V_{t}^{k}(a)}} $$
-
-We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm [@watkins1992q]. The update rule becomes:
-
-$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha \times( R_{t}  + \gamma \times \underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$
-
-Where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\gamma$ is the discount rate applied to future rewards.
-For instance, $Q(RS,P)$ denotes the value of taking action "Paper" this round if the player's last action was "Rock" and the opponent played "Scissors".
-This is a much richer model allowing the players to compute the values of actions conditional on past play.
-
-## EWA Models 
-Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics].
-EWA models particularity is that they nest two seemingly different approaches, namely reinforcement learning and belief learning.
-Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
-In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
-The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
-Let's define some notation in order to write the update rule of the self-tuning EWA model.
-For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j).
-Strategies actually played by i in period t, are denoted $s_{i}(t)$, while the opponent's strategy at time t is denoted $s_{-i}(t)$.
-After playing  $s_{i}^{j}$ at time $t$, player i pay-off is denoted $\pi_{i}(s_{i}^{j},s_{-i}(t))$, and the actual pay-off the player received is $\pi_{i}(t)$.
-The EWA model is based on updating "Attractions" for each action over time.
-For instance, the attraction of strategy $j$ to player $i$ at time $t$ is written $A_{i}^{j}(t)$.
-Future action choice probabilities are based on these attractions using the softmax playing rule:
-
-$$P_{i}^{j}(t+1) = \frac{e^{\lambda  A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda A_{i}^{k}(t)}} $$
-
-The attractions are updated over every time step $t$ using the following update rule :
-
-$$ A_{i}^{j}(t) =  \frac{\phi \times N(t-1) \times A_{i}^{j}(t-1) + [ \delta + (1-\delta) \times I(s_{i}^{j},s_{i}(t))] \times \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi \times N(t-1) + 1} $$
-
-Here, $I(x,y)$ is the indicator function equal to 1 if $x = y$ and 0 otherwise.
-A simple way to think about this update rule is that attractions are multiplied by a parameter that represents experience ($N(t-1)$) which is itself decaying by a weight $\phi$.
-The result is added to either the pay-off received (when the indicator function is 0), or to $\delta$ times the foregone pay-off (when indicator function is 1).
-We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play [@cheung1994learning].
+The other models adapted their play to the opponent, either by reinforcing successful actions in each game (reinforcement learning), or by determining the type of opponent through Bayesian learning (Bayesian Cognitive Hierarchy models).
+We also include the Expected Weighted Attraction (EWA), which is a popular model in behavioral economics.
+
+We use the following notation.
+In each game $g \in \{\text{RPS},\text{FWG}, \text{NUMBERS}\}$, on each trial $t$, the participant chooses an action $a_t \in \mathcal{A}_g$, and the opponent chooses action $o_t \in \mathcal{A}_g$, where $\mathcal{A}_g$ is the set of allowed actions in game $g$, e.g.
+$\mathcal{A}_\text{RPS} = \{R,P,S\}$.
+The participant then receives reward $r_t \in \{1,0,-1\}$, and the opponent receives $-r_t$.
+We use the state variable $s_t = \{a_{t-1},o_{t-1}\}$ to denote the actions taken in the previous round $t-1$ by the participant and opponent.
+
+In the following, we will describe the models in more detail, and provide some intuition into how they they learn about the game and/or the opponent.
+
+## Reinforcement learning (RL) model
+
+We first consider a model-free reinforcement learning algorithm, where actions that have led to positive rewards are reinforced, and the likelihood of actions that led to a negative reward is lowered.
+Since the computer players in this experiment based their play on the actions in the previous round, a suitable RL model for this situation is one which learns the value of actions contingent on plays in the previous round, i.e.
+by defining the state $s_{t}$ as above.
+The resulting RL model learns a Q value [@watkins1992q] for each state-action pair:
+
+$$ Q_{t+1}(s_{t},a_{t}) = Q_{t}(s_{t},a_{t}) + \alpha \left( r_{t}  - Q(s_{t},a_{t}) \right) $$
+
+where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\alpha \in [0,1]$ the learning rate.
+For instance, $Q_t(\{R,S\},P)$ denotes the value of taking action  ''Paper'' this round if the player's last action was ''Rock'' and the opponent played ''Scissors''.
+Actions are taken according to a softmax rule:
+$$P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}$$ 
+While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different action space $\mathcal{A}_g$, and there is no simple way to map actions between games.
+
+The RL model has two free parameters: the learning rate ($\alpha$) and the inverse temperature parameter of the softmax decision rule ($\lambda$).
+We've assumed $\gamma = 0$ as changes in this parameter didn't affect the other parameter estimations or ultimately the value of the likelihoods.
+
+## Experience-weighted attraction (EWA) model
+
+The self-tuning Experience Weighted Attraction (EWA) model [@ho2004economics] combines two seemingly different approaches, namely reinforcement learning and belief learning.
+Belief learning models are based on the assumption that players keep track of the frequency of past actions and best respond to that.
+By contrast, reinforcement learning does not explicitly take into account beliefs about other players, but simply increases the probability of repeating a more rewarding action.
+The self-tuning EWA model has been shown to perform better than either RL or belief learning alone in various repeated games and has the advantage of having only one free parameter, the inverse temperature of the softmax choice function.
+The EWA model is based on updating ``Attractions'' for each action over time.
+The attraction of action $a$ time $t$ is written $A_{t}(a)$ and is updated as
+
+$$ A_{t+1}(a) =  \frac{\phi \ N(t) \ A_{t}(a) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} $$
+where $I(x)$ is an indicator function which takes the value 1 is its argument is true, and 0 otherwise, and $R(a,o_t)$ is the reward that would be obtained from playing action $a$ against opponent action $o_t$, which equals the actual obtained reward when $a = a_t$, and otherwise is a counterfactual reward that would have been obtained if a different action were taken.
+Unlike reinforcement learning, this uses knowledge of the rules of the game to allow reinforcing actions that were not taken.
+We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play @[cheung1994learning].
 While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].
-
-## BCH models
-
-In this set of models, we assume that participants start with a prior belief that the opponent is a level-k agent, with uniform probability of the level $k \in \{ 0, 1, 2\}$, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
-More formally, if we define $D_{t}$ as data available at time $t$ then the probability of the opponent being a level-k is updated using:
-
-$$ P(level=k | D_{t})  \propto  P(D_{t}|level=k ) \times P(level=k)$$
-
-These models also assume the opponent can deviate from these level-k strategies and play randomly with probability $\theta$, a parameter to be fit.
-We also assume that participants base their actions on their beliefs about the level of the opponent, so actions get chosen probabilistically using a softamx choice rule with probabilities of each opponent level as inputs.
-We distinguish between multiple BCH models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
-In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (within but no between transfer).Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
-In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
-In experiment two, on top of these two models, we fit another model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
+$ N(t)$ represents an experience weights and can be interpreted as the number of "observation-equivalents" of past experience.
+We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
+
+As in the models above, actions are chosen based on a softmax decision rule:
+$$P_t(a) = \frac{\exp \{\lambda  A_{t}(a) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a') \} }$$
+The self-tuning EWA has one free parameter: the inverse temperature of the softmax decision rule ($\lambda$).
+
+\subsection{Bayesian Cognitive Hierarchy (BCH) model}
+
+In what we call the Bayesian Cognitive Hierarchy (BCH) model, the participant attempts to learn the type of opponent they are facing through Bayesian learning.
+We assume the participant considers the opponent could be either a level 0, level 1, or level 2 player, and starts with a prior belief that each of these types is equally likely.
+They then use observations of the opponents actions to infer a posterior probability of each type:
+$$ P(\text{level}=k | D_{t})  \propto  P(D_{t}|\text{level}=k ) \times P(\text{level}=k)$$
+where $D_{t} = \{a_1,o_1,\ldots,a_t,o_t\}$ is the data available at time $t$. The likelihood is defined as
+$$P(D_{t}|\text{level}=k) = \prod_{j=1}^t \left( \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o_j|a_{j-1},o_{j-1})\right)$$
+where $f_k(o_t|a_{t-1},o_{t-1}) = 1$ if $o_t$ is the action taken by a level $k$ player when the previous round play was $a_{t-1}$ and $o_{t-1}$, and 0 otherwise.
+Note that the likelihood assumes (correctly) that there is a probability $\theta \in [0,1]$ that the opponent takes a random action.
+The posterior at time $t-1$ forms the prior at time $t$.
+We assume a participant chooses an action by using the softmax function over the best response to predicted actions:
+$$\begin{aligned} B_t(a) &= \sum_{k = 0}^2 \sum_{o \in \mathcal{A}_g} b(a,o) P_k(o|a_{t-1},o_{t-1})  P(\text{level}=k|\mathcal{D}_{t-1})\\
+P_t(a) &= \frac{\exp{\lambda B_t(a)}}{\sum_{a' \in \mathcal{A}_g} \exp \lambda B_t(a')} \end{aligned}$$
+where $b(a,o) = 1$ if action $a$ is a best response to opponent's action $o$ (i.e.
+it leads to a win), and $P_k(o|a_{t-1},o_{t-1}) = \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o|a_{t-1},o_{t-1})$ is the probability that a level $k$ agent takes action $o$, as also used in the likelihood above.
+
+Unlike the models above, the BCH model allows for between-game transfer, as knowledge of the level of the opponent can be used to generate predictions in games that have not been played before.
+However, the participant might also assume that the level of reasoning of their opponent does not generalize over games.
+We hence distinguish between two versions of the BCH model.
+In the No-Between-Transfer (BCH\_NBT) variant, participants assume a uniform probability of the different levels at the start of each game (and hence do not transfer knowledge of their opponent between games).
+In the Between-Transfer model (BCH\_BT), participants use the posterior probability over the levels of their opponent as the prior at the start of a new game (i.e.
+complete transfer of the knowledge of their opponent).
+Both versions of the BCH model have two free parameters: the assumed probability that the opponent chooses a random action ($\theta$), and the temperature parameter of the softmax function ($\lambda$).
 
@@
 
-In experiment 1, we fit a total of 5 models: A baseline model assuming random play (Nash),  Bayesian Cognitive Hierarchy model allowing transfer betwen games (BCH_BT) and another with no transfer between games (BCH_NBT), as well as a Q-learning model with state space consisting of last round play (QL_states), and finally a self tuning EWA model with the same state space (STEWA_states).
-In experiment 2, because participants were interacting with each opponent twice within each game, we allowed models to transfer learning within games between the first and second interactions.
-Therefore on top of the two BCH models mentionned above (BCH_BT and BCH_NBT), we also allow the Q-learning model with states to either have the ability to transfer learning between the first and second interaction (QLS_Tr) or not (QLS_NT).
-Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (STEWA_Tr) or without transfer (STEWA_NT).
+In experiment 1, we fit a total of 5 models: A baseline model assuming random play (Nash),  Bayesian Cognitive Hierarchy model allowing transfer betwen games (BCH_BT) and another with no transfer between games (BCH_NBT), as well as a Reinforcement Learning model with state space consisting of last round play (RL), and finally a self tuning EWA model with the same state space (EWA).
+
+In experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two type of opponent model transfer.
+We can have transfer within games, between the first and second interaction with the opponent.
+We can also have transfer between games, as in transfering models of the opponent from RPS to FWG for instance.
+Therefore, we
+give models more flexibility to allow for these two types of transfer.
+As such, for Bayesian Cognitive Hierarchy, we fit a total of three models.
+BCH_BT allows for between game transfer.
+We assume that if such transfer is possible, then within game transfer should also be possible and therefore this model allows for both types of transfer.
+BCH_NBT allows for within but no between game transfer.
+Whereas BCH_NT allows for neither.
+For Reinforcement learning models, because RL models can't account for between game transfer due to change in ation labels, we can only have models allowing for within game transfer (RL Tr) or with no transfer within games (RL NT).
+Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (EWA_Tr) or without transfer (EWA_NT).
 Counting the base model wiht random play (Nash) we therefore fit a total of 8 models in experiment 2.
@@
 
-Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning with states defined by last round play.
-Table \ \@ref(tab:exp1weightstable) shows the model BIC weights  as well as the number of participants best fit by each model.
-
+Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: We can see that the RL model clearly described most participants' behaviour best, followed by the random (Nash) model.
+Only a few participants were best described by one of the BCH models, or the EWA model.
+Looking at BIC weights, we confirm this as seen in  Figure \ \@ref(fig:xp1-BIC-weigths).
+RL models hve high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, whihc fits the picture drawn by the histogram.
 ```{r, include=FALSE}
@@
 
-```{r}
-library(reshape2)
-d <- melt(exp1_BIC_weights, id.vars="ID", variable.name = "Model",value.name = "BIC_weight")
-
-# Everything on the same plot
-ggplot(d, aes(ID,BIC_weight, col=Model)) + 
-  geom_point() + 
-  stat_smooth() +
-  facet_wrap(~Model) +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank()) + 
-  theme(legend.position = c(0.8, 0.3))
-
-# 
-# Average_BIC_weights <- as.data.frame(t(round(apply(exp1_BIC_weights[,-1],2,mean),2)))
-# row.names(Average_BIC_weights) <- c("Model BIC weights")
-# Average_BIC_weights
-# 
-# #Count_Best_fit <- table(exp1_model_comp$Best_model)
-# temp <- plyr::count(exp1_model_comp,"Best_model")
-# Count_Best_fit <- tidyr::spread(temp,Best_model, freq)
-# row.names(Count_Best_fit) <- c("Count best fit")
-# Count_Best_fit
-# 
-# 
-# table_exp_1 <- rbind.fill(Average_BIC_weights,Count_Best_fit)
-# row.names(table_exp_1) <- c("Model BIC weights","Count best fit")
-# table_exp_1
-
-```
-
-```{r exp1weightstable, results="asis", echo=FALSE, warning=FALSE}
-
-######apa_table breaks knitr....not sure why.
-#######
-papaja::apa_table(table_exp_1, caption = "Experiment one Average BIC weights and number of participants best fit by model")
-
-#knitr::kable(table_exp_1, caption = "Experiment 1 - Average BIC weights and number of participants best fit by model")
-
-```
-
-```{r exp1-comp-models, fig.cap = "Experiment 1 - Histogram of best fitting computational models by condition", fig.align='center'}
+```{r exp1-comp-models, fig.cap = "Experiment 1 - Histogram of best fitting computational models by condition", out.width="\\textwidth", fig.align='center'}
 
@@
 
-Next we compared the performance of players whose actions are best fit by each of our hypothesized models.
+```{r, include= FALSE}
+library(reshape2)
+d <- melt(exp1_BIC_weights, id.vars="ID", variable.name = "Model",value.name = "BIC_weight")
+```
+
+(ref:figure9-caption) Model BIC weights for participants in experiment 1
+```{r, xp1-BIC-weigths, fig.cap="(ref:figure9-caption)", fig.align="center"}
+# Everything on the same plot
+ggplot(d, aes(ID,BIC_weight, col=Model)) + 
+  geom_point() + 
+  stat_smooth() +
+  facet_wrap(~Model) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) + 
+  theme(legend.position = c(0.8, 0.3))
+
+# 
+# Average_BIC_weights <- as.data.frame(t(round(apply(exp1_BIC_weights[,-1],2,mean),2)))
+# row.names(Average_BIC_weights) <- c("Model BIC weights")
+# Average_BIC_weights
+# 
+# #Count_Best_fit <- table(exp1_model_comp$Best_model)
+# temp <- plyr::count(exp1_model_comp,"Best_model")
+# Count_Best_fit <- tidyr::spread(temp,Best_model, freq)
+# row.names(Count_Best_fit) <- c("Count best fit")
+# Count_Best_fit
+# 
+# 
+# table_exp_1 <- rbind.fill(Average_BIC_weights,Count_Best_fit)
+# row.names(table_exp_1) <- c("Model BIC weights","Count best fit")
+# table_exp_1
+
+```
+
+```{r exp1weightstable, results="asis", include =FALSE, echo=FALSE, warning=FALSE}
+
+######apa_table breaks knitr....not sure why.
+
+#papaja::apa_table(table_exp_1, caption = "Experiment one Average BIC weights and number of participants best fit by model")
+
+#knitr::kable(table_exp_1, caption = "Experiment 1 - Average BIC weights and number of participants best fit by model")
+
+```
+
+<!-- Next we compared the performance of players whose actions are best fit by each of our hypothesized models.
 Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning a BCH opponent model in a Bayesian way had the best overall performance (without transfer), followed by Q-learning conditional on last round play.
-EWA, QL and random players had, understandably the lowest performance.
+We can see that participants whose actions are most consistent with learning a BCH opponent model in a Bayesian way had the best overall performance (without transfer), followed by RL, EWA.
+Random players had, understandably the lowest performance.
+-->
 
 ```{r exp1-cumScores, fig.cap = "Experiment 1 - Average cumulative scores of participants by best fitting model", fig.align='center'}
-p5 <- ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
-   geom_line(aes(color= Best_model))
-
-p5 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
+# p5 <- ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
+#    geom_line(aes(color= Best_model))  
+# 
+# p5 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
 ```
@@
 
+In experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that the RL model was again more successful than the Bayesian models in fitting player's action choices.
+In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
+This is also reflected in BIC weights in Figure \ \@ref(fig:xp2-BIC-weigths)
+
 ```{r, include = FALSE}
@@
 
-exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Nash","BCH BT","BCH NBT", "BCH NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])
+exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Nash","BCH BT","BCH NBT", "BCH NT", "RL NT","RL Tr","EWA NT","EWA Tr")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])
 
@@
 
-```{r exp2-comp-models, fig.cap = "Experiment 2 Histogram of best fitting computational models by condition", fig.align='center'}
+```{r exp2-comp-models, fig.cap = "Experiment 2 Histogram of best fitting computational models by condition", out.width="\\textwidth", fig.align='center'}
 
@@
         xlab="Number of participants",
-        # legend = c("level-1 opp first","level-2 opp first"),
+        #legend = c("level-1 opp first","level-2 opp first"),
         legend = paste0(rownames(exp2_comp_table) , " faced first"),
         args.legend=list( # positioning of legend box 
-        x=ncol(exp2_comp_table) + 6,
-        y=max(colSums(exp2_comp_table)) +1,
+        x  = 15,
+        y  = 10,
+        # x=ncol(exp2_comp_table) + 6,
+        # y=max(colSums(exp2_comp_table)) +1,
         bty = "n")
@@
 
-  best_model <- c("Nash","BCH BT","BCH NBT", "BCH NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)]
+  best_model <- c("Nash","BCH BT","BCH NBT", "BCH NT", "RL NT","RL Tr","STEWA NT","STEWA Tr")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)]
 
@@
 exp2_BIC_weights[,2:ncol(exp2_comp_BICs)] <- t(apply(exp2_comp_BICs[,-1], 1, function(i) exp(-0.5*(i-min(i)) )))
-colnames(exp2_BIC_weights) <- c("ID","Nash","BCH BT","BCH NBT", "BCH NT", "QLS NT","QLS Tr","STEWA NT","STEWA Tr")
+colnames(exp2_BIC_weights) <- c("ID","Nash","BCH BT","BCH NBT", "BCH NT", "RL NT","RL Tr","EWA NT","EWA Tr")
 exp2_BIC_weights[,-1] <- t(apply(exp2_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
@@
 (ref:my-table2-caption) Experiment 2 BIC weights and number of participants best fit by model.
-```{r exp2-weights-table, results="asis", echo=FALSE}
+```{r exp2-weights-table, results="asis", echo=FALSE, include =FALSE}
 
@@
 ```
-
-In experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that Q-learning with the aforementioned state-space was again more successful than the Bayesian models in fitting player's action choices.
-In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
-This is also reflected in BIC weights in Table \ \@ref(tab:exp2-weights-table)
-
-```{r exp2-cumScores, fig.cap = "Experiment 2 Average cumulative scores of participants by best fitting model", fig.align='center'}
+```{r, include= FALSE}
+library(reshape2)
+d <- melt(exp2_BIC_weights, id.vars="ID", variable.name = "Model",value.name = "BIC_weight")
+```
+
+(ref:figure11-caption) Model BIC weights for participants in experiment 2
+```{r, xp2-BIC-weigths, fig.cap="(ref:figure11-caption)", fig.align="center", out.width="\\textwidth"}
+# Everything on the same plot
+ggplot(d, aes(ID,BIC_weight, col=Model)) + 
+  geom_point() + 
+  stat_smooth() +
+  facet_wrap(~Model) +
+  theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) + 
+        theme(legend.position = c(0.8, 0.17), 
+        legend.direction = "vertical",
+        legend.key.size = unit(0.4, "cm"),
+        legend.key.width = unit(0.6,"cm")) 
+        # + guides(fill=guide_legend(nrow=4,ncol=2))
+```
+
+```{r exp2-cumScores, fig.cap = "Experiment 2 Average cumulative scores of participants by best fitting model", include =FALSE, fig.align='center', out.width="\\textwidth"}
 
@@
 
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a BCH model of learning the opponent strategy had the highest cumulative performance.
+<!-- Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a BCH model of learning the opponent strategy had the highest cumulative performance.
 Out of these BCH models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance (although it only fit 2 participants best), followed by a model in which both within and between transfer of opponent models is allowed (BT).
@@
 As expected, random play was at the bottom of cumulative performance.
+-->
 
@@
   facet_grid(game~stage) +
-  scale_colour_discrete(name = "Strategy", labels = c( "Nash", "Q_Learning + within Tr", "BCH + Tr"))
+  scale_colour_discrete(name = "Strategy", labels = c( "Nash", "RL + within Tr", "BCH + within & btw Tr"))
 
@@
 Nash_lik <- exp1_lik_by_trial$Nash_lik
-QLS_lik <- exp1_lik_by_trial$QLS_lik
+RL_lik <- exp1_lik_by_trial$QLS_lik
 Bayes_Tr_lik <- exp1_lik_by_trial$Bayes_Tr_lik
@@
   list(
-	  dummyResponse(QLS_lik)
+	  dummyResponse(RL_lik)
 	),
@@
 
-exp1_lik_by_trial["post_QLS"] <- forwardbackward(fmod1)$gamma[,1]
+exp1_lik_by_trial["post_RL"] <- forwardbackward(fmod1)$gamma[,1]
 exp1_lik_by_trial["post_Nash"] <- forwardbackward(fmod1)$gamma[,2]
@@
 mean_post_1 <- exp1_lik_by_trial %>%
-  dplyr::select(human_id,game,condition, round, post_Nash, post_QLS, post_Bayes_Tr) %>%
+  dplyr::select(human_id,game,condition, round, post_Nash, post_RL, post_Bayes_Tr) %>%
   dplyr::group_by(game,condition, round) %>%
   dplyr::summarise(Nash_posterior = mean(post_Nash, na.rm = TRUE),
-                   RL_posterior = mean(post_QLS, na.rm = TRUE),
+                   RL_posterior = mean(post_RL, na.rm = TRUE),
             BCH_BT_posterior = mean(post_Bayes_Tr, na.rm = TRUE))
@@
 given the value of the observation.
-In the first experiment, we can see from the plots of FWG and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the QLS model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
+In the first experiment, we can see from the plots of FWG and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the RL model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
 
@@
 # we need to have "dat" available and lik_by_trial
-QLS_lik <- exp2_lik_by_trial$QLS_lik
+RL_lik <- exp2_lik_by_trial$QLS_lik
 Nash_lik <- exp2_lik_by_trial$Nash_lik
@@
 
-exp2_lik_by_trial["post_QLSw"] <- forwardbackward(fmod)$gamma[,1]
+exp2_lik_by_trial["post_RLw"] <- forwardbackward(fmod)$gamma[,1]
 exp2_lik_by_trial["post_Nash"] <- forwardbackward(fmod)$gamma[,2]
@@
 mean_post_2 <- exp2_lik_by_trial %>%
-  dplyr::select(human_id,game,stage,round_condition, round, post_QLSw, post_Bayes_Tr) %>%
+  dplyr::select(human_id,game,stage,round_condition, round, post_Nash, post_RLw, post_Bayes_Tr) %>%
   dplyr::group_by(game,stage, round) %>%
-  dplyr::summarise(mean_post_QLSw = mean(post_QLSw, na.rm = TRUE),
-            mean_post_Tr = mean(post_Bayes_Tr, na.rm = TRUE))
+  dplyr::summarise(Nash_posterior = mean(post_Nash, na.rm = TRUE),
+                   RL_posterior = mean(post_RLw, na.rm = TRUE),
+            BCH_BT_posterior = mean(post_Bayes_Tr, na.rm = TRUE))
 
@@
 
-data_long_post2 <- gather(mean_post_2, strategy, probability, mean_post_QLSw,mean_post_Tr, factor_key=TRUE)
+data_long_post2 <- gather(mean_post_2, strategy, probability, Nash_posterior, RL_posterior, BCH_BT_posterior, factor_key=TRUE)
 

### 2021-06-04 Report/paper_draft_2021.tex
added report in papaja and softmax to BCH models

--- 2021-06-04 Report/draft_upgrade_final.tex
@@
 \shorttitle{}
-\thispagestyle{headings}
+
 \title{Transfer of Learned Opponent Models in Zero Sum Games}
@@
 Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
-Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
-More formally, Perkins \& Salomon (1992) define transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
-This typically human skill has so far eluded modern AI agents.
-Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
-Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-Lake, Ullman, Tenenbaum, \& Gershman (2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
+This ability relies on important cognitive building blocks, such as an abstract representation of concepts underlying tasks (Lake, Ullman, Tenenbaum, \& Gershman, 2017).
+One way to form these representations when the task involves interactions with others, is to build a model of the person we are interacting with that offers predictions of the actions they are likely to take next.
+There is evidence that people learn such models of their opponents when playing repeated economic games (Stahl \& Wilson, 1995).
 
-One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
-Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations.
-This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
-There is evidence that people learn models of their opponents when they play repeated economic games (Stahl \& Wilson, 1995), engage in bilateral negotiations (Baarslag, Hendrikx, Hindriks, \& Jonker, 2016), or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors (Weerd, Verbrugge, \& Verheij, 2012).
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind (Premack \& Woodruff, 1978) abilities play a role in determining human behaviour.
-In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
-More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to the task of opponent modelling.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to this task.
+The early literature on learning transfer in repeated games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously (Camerer \& Knez, 2000; Ho, Camerer, \& Weigelt, 1998).
+This doesn't allow for the possibility of learning about the opponent's strategy and potentially exploiting it.
 
-In exploring opponent modelling and learning transfer, most studies adopted two types of opponents in the experimental setting.
-Either human participants were matched with other participants or they played against a computer algorithm.
-Computer opponents were generally programmed not to change their strategies over the course of the task, allowing better experimental control.
-One of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-The strategies implemented by the computer opponents had a style of play that was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with any precision, or at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that \enquote{play like humans}, and one way of achieving that is to embed theses agents with human-like theory of mind abilities.
-Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally complex problems such as finding Nash equilibria.
-Instead, they will try to \enquote{satisfice} by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in \enquote{level-k} theory, first adopted by Stahl \& Wilson (1995).
-It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogeneous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment Arad \& Rubinstein (2012).
-Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
-Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below, and so on.
+When studies have specifically explored this aspect, they have used computer opponents that were generally programmed not to change their strategies over the course of the task, allowing better experimental control.
+However, they have mostly looked at the ability of players to detect and exploit action-based learning rules (Shachat \& Swarthout, 2004; Spiliopoulos, 2013).
+The strategies implemented by the computer opponents had a style of play that was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with precision, or at detecting patterns from long sequences of past play.
+Thus, in this study, we aim to explore opponent modelling and its transfer with the use of computer agents endowed with human-like limited degrees of iterated reasoning.
+The agents are either a level-1 or level-2 player, mimicking ``I know that you know that I know'' type reasoning, and the limited recursion depth they exhibit (Goodie, Doshi, \& Young, 2012).
+A level 1 player adapts their play to what they believe their opponent will play, without considering what their opponent might believe they will play.
+A level 2 player, on the other hand, takes their opponent's belief about their actions into account, assuming they face a level 1 player, and choosing actions to beat the actions of that player.
+The choice of this type of strategy is also motivated by evidence that humans strategically use information from last round play of their opponents in zero sum games (Batzilis, Jaffe, Levitt, List, \& Picel, 2016; Wang, Xu, \& Zhou, 2014).
 
-In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will either be a level-1 or level-2 player, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie, Doshi, \& Young, 2012).
-Our choice of using computer opponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-When playing against other human opponents, players are learning about the game as well as trying to infer the potential dynamic strategy of the opponent simultaneously.
-Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
-The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
-For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents, designed to take advantage of known patterns in human play such as imperfect randomization and heuristics use.
-He found that human participants do adapt to the opponent they are facing.
-Shachat \& Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations of the opponent from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
-We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
+We have conducted two experiments where participants interact with a computer opponent.
+In each experiment, we measure transfer of learning about the opponent's strategy between games with varying degrees of similarity.
 The first two games we use are structurally identical except for action labels.
-In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure.
+In the first experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure.
 In the first experiment, participants face the same opponent throughout the three games, and the opponents are randomised to be either level-1 or level-2 players.
@@
 Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The study used a 2 (computer opponent: level 1 or level 2) by 3 (games: rock-paper-scissors, fire-water-grass, numbers) design, with repeated measures on the second factor.
+The experiment used a 2 (computer opponent: level 1 or level 2) by 3 (games: rock-paper-scissors, fire-water-grass, numbers) design, with repeated measures on the second factor.
+Participants were randomly assigned to one of the two levels of the first factor.
 
@@
 
-In the first experiment, the three games were rock-paper-scissors, fire-water-grass and the numbers game.
-A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
+In the first experiment, participants played the three games against their computer opponent.
+These games were rock-paper-scissors, fire-water-grass, and the numbers game.
+A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between the two player's actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
 If one player chooses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
 Otherwise it is a draw and both players receive a reward of 0.
-It has a unique MSNE consisting of randomly playing one of the three options each time.
-The second game is identical to Rock-Paper-Scissors in all but action labels.
-We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
-We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
-Finally, the numbers game is a generalization of rock-paper-scissors.
+RPS has a unique mixed-strategy Nash equilibrium, which consists of each player in each round randomly selecting from the three options with uniform probability.
+The Fire-Water-Grass (FWG) game is identical to RPS in all but action labels: Fire burns grass, water extinguishes fire, and grass absorbs water.
+We use this game as we are interested in whether learning is transferred in a fundamentally similar game where the only difference is in the description of the possible actions.
+This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level 1 or 2 player.
+Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'', as might be learned by a simple reinforcement learning algorithm, will not be able to generalize to such a game, as these contingencies are tied to the labels of the actions.
+The numbers game is a generalization of RPS.
 In the variant we use, 2 participants concurrently pick a number between 1 and 5.
-To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent.
+To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by their opponent.
 For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
 To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
-This game has a structure similar to RPS in which every action is dominated by exactly one choice.
-All other possible combination of choices that are not consecutive are considered ties.
-A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score.
-Similar to RPS, the MSNE is to play each action with equal probability in a random way.
+This game has a structure similar to RPS in which every action is dominated by exactly one other action.
+All other possible combinations of choices are considered ties.
+Similar to RPS and FWG, the mixed-strategy Nash equilibrium is to play each action with equal probability in a random way.
+
+The computer opponent was programmed to use either a level-1 or level-2 strategy in all the games.
+A level 1 player is defined as a player who best responds to a level 0 player.
+A level 0 player plays in a non-strategic way and does not consider their opponent's actions.
+Here, we assume a level 0 player simply repeats their previous action.
+There are other ways to define a level 0 player.
+For instance, as repeating their action if it resulted in a win, and choosing randomly from the remaining actions otherwise.
+As a best response to a random action is itself a random action, defining a level 0 player in such a way would make a level 1 opponent's strategy much harder to discern.
+Because we are mainly interested in generalization of knowledge of an opponent's strategy to other games, which rests on good knowledge of this strategy, we opted for this more deterministic formulation of a level 0 player (whilst also introducing some randomness in the computer opponent's play).
+A level-2 computer opponent, will assume in turn that the participant is a level-1 opponent, playing according to the strategy just described.
+We also introduced some noise over the actions of computer opponents making them play randomly in 10\% of all trials.
+
+\begin{table}[bth!]
+\centering
+\begin{tabular}{||c c c c||} 
+ \hline
+ Human last & Agent last & level-1 Agent & level-2 Agent\\ [0.5ex] 
+ \hline\hline
+ Paper & Rock & Scissors & Scissors \\ 
+ Scissors  & Scissors & Rock & Paper \\
+ Rock & Paper & Paper & Rock \\
+ ... & ... & ... & ... \\ [1ex] 
+ \hline
+\end{tabular}
+\caption{Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round.}
+\label{table:1}
+\end{table}
 
@@
 
-Participants played 3 games sequentially against the same computer opponent.
-The computer opponent either used a level-1 or level-2 strategy.
 Participants were informed they would play three different games against the same computer opponent.
-Each participant plays all three games consecutively and in the same order described above.
 Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
+After providing informed consent and reading the instructions, participants answered a number of comprehension questions.
+They then played the three games against their opponent in the order RPS, FGW, and NUMBERS.
 A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
@@
 Each point is worth £0.02.
-An example of the interface for the rock-paper-scissors game is provided in Figure~\ref{fig:feedback-rps-exp2}.
+An example of the interface for the RPS game is provided in Figure~\ref{fig:feedback-rps-exp2}.
+After playing all the games, participants were asked questions about their beliefs about the computer opponent, related to whether they think they have learned their strategy and how hard they found playing against that particular opponent.
+They were then debriefed and thanked for their participation.
 
@@
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-avg-scores-game-1}
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp1-avg-scores-game-1}
 
@@
 
-Looking at the aggregate scores (See Figure~\ref{fig:exp1-avg-scores-game} ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
-Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, \(p\) \textless{} 0.001 ; FWG: t(51) = 10.04 , \(p\) \textless{} 0.001 ; NUMBERS: t(51) = 7.17, \(p\) \textless{} 0.001).
-To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game (F(2,100) = 8.54, \(\eta^{2}\) = 0.05, p \textless{} 0.001), showing that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game (t(100) =3.78, p = 0.0008), and the performance in the NUMBERS game was significantly lower than FWG game (t(100) = -3.32 , p = 0.0024).
-The score in RPS was not significantly different from the score in NUMBERS (t(100) = 0.45 , p = 0.65).
-The main effect of Block (F(1,50) = 22.51 , p \textless{} .001, \(\eta^{2}\) = 0.03) shows that the average score in the first half of games (M = 0.29) was significantly lower than in the second half of the games played (M = 0.40), which translates to within-game learning.
-The main effect of Condition (F(1,50) = 5.44, p = .024, \(\eta^{2}\) = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
-This indicates that it was harder for participants, on average, to exploit the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
-
-\begin{figure}
-
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-3factor-plot-1}
-
-}
-
-\caption{Boxplots of scores by game, block and condition}\label{fig:exp1-3factor-plot}
-\end{figure}
-
-Finally, the analysis showed a significant block by game interaction ( F(2,100) = 6.92 , p = .002, \(\eta^{2}\) = 0.02), indicating that within-game learning differed between the games.
-Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p \textless{}.0001), while there was no significant difference between block scores for the other two games.
-This is indicative of the significant within-game learning happening in the first game when players have no experience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some experience playing against the opponent and start with higher scores indicative of transfer.
-There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88, p = .023, \(\eta^{2}\) = 0.01), which indicates, as seen in Figure~\ref{fig:exp1-3factor-plot} that within-game learning changes across games also depend on the sophistication of the opponent.
-For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than against level-1 opponent.
-The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
+On average, participants obtained the lowest score in the RPS game (\(M = 0.289\), \(SD = 0.348\)), followed by NUMBERS (\(M = 0.31\), \(SD = 0.347\)).
+Participants' performance was highest in the FWG game (\(M = 0.454\), \(SD = 0.354\)).
+Scores in each game were significantly different from 0, the expected score of random play (RPS: \(t(51) = 7.26\), \(p < .001\); FWG: \(t(51) = 10.04\) , \(p < .001\); NUMBERS: \(t(51) = 7.17\), \(p < .001\)).
+To assess learning within and between games, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants.
+This showed a main effect of Game (\(F(2,100) = 8.54\), \(\eta^{2} = 0.05\), \(p < .001\)), indicating that average scores varied significantly over the games.
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game (\(t(100) =3.78\), \(p < .001\)) and the NUMBERS game (\(t(100) = 3.32\) , \(p = .002\)).
+The score in RPS was not significantly different from the score in NUMBERS (\(t(100) = 0.45\) , \(p = .65\)).
+The main effect of Block (\(F(1,50) = 22.51\) , \(\eta^{2} = 0.03\), \(p < .001\)) shows that the score in the first half of each game (\(M = 0.29\)) was significantly lower than in the second half (\(M = 0.40\)), which indicates within-game learning.
+The main effect of Condition (\(F(1,50) = 5.44\), \(\eta^{2} = 0.05\), \(p = .024\)) indicates that scores were higher against the level-1 player (\(M = 0.43\)) than against the level-2 player (\(M = 0.27\)).
+Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
 
@@
 
-As a measure for learning transfer, we focus on participants' scores in the first 5 rounds excluding the initial round (rounds 2-6).
+As a measure for learning transfer, we focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game (see Figure \ref{fig:exp1-score-by-opp}).
 We exclude the very first round as the computer opponent plays randomly here and there is no opportunity yet for the human player to exploit their opponent's strategy.
-A group of players with no experience of the game are expected to perform at chance level over the early rounds of a new game, as was the case in RPS.
-Positive scores in the early rounds would therefore reflect generalization of prior experience.
-For the FWG game, the score is significantly higher than 0 ( t(148.85) = 4.58 , p \textless{} 0.0001).
-This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
-For the RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
+Players with no knowledge of their opponent's strategy are expected to perform at chance level in these early rounds.
+Positive scores in rounds 2-6 reflect generalization of prior experience.
+The FWG early score score is significantly higher than 0 (\(t(148.85) = 4.584\), \(p < .001\)).
+This is also the case for the NUMBERS game (\(t(148.85) = 3.00\), \(p = .009\)).
+We did not expect positive scores for the RPS game, as it was the first game played and there was no opportunity for learning about the opponent's strategy.
+Scores in this game was indeed not significantly different from 0 (\(t(148.85) = 1.04\) , \(p = .89\)).
 
@@
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-score-by-opp-1}
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp1-early-score-by-opp-1}
 
@@
 
-\caption{Mean and 95\% confidence Intervals of early scores by game and opponent}\label{fig:exp1-score-by-opp}
+\caption{Mean and standard error of early scores by game and opponent}\label{fig:exp1-early-score-by-opp}
 \end{figure}
@@
 Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-Figure~\ref{fig:exp1-score-by-opp} shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players as well as the \(95\) percent confidence interval for the mean.
-Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
-To explore this, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p \textless{} 0.001) and NUMBERS (t(150) = 3.74, p \textless{} 0.001) .
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
+We expected better transfer between more similar games (i.e.~better transfer from RPS to FWG than from RPS/FWG to NUMBERS), and worse transfer for the more sophisticated level 2 agent.
+Figure\textasciitilde{}\ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 players.
+To explore this, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) repeated measures ANOVA with the first factor varying between participants.
+There was a main effect of Game (\(F(2,92) = 3.35\), \(\eta^{2} = 0.04\), \(p < .04\)).
+We then run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( \(t(150) = 3.96\), \(p < .001\)) and NUMBERS (\(t(150) = 3.74\), \(p < .001\)).
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player (\(t(150) = 2.48\), \(p = .01\)) but not to the dissimilar game of NUMBERS.
 
-\hypertarget{discussion-experiment-1}{%
-\subsubsection{Discussion Experiment 1}\label{discussion-experiment-1}}
+\hypertarget{experiment-1-discussion}{%
+\subsubsection{Experiment 1 discussion:}\label{experiment-1-discussion}}
 
-Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game.
-Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
+These results indicate that learning transfer to the more dissimilar game (NUMBERS) we found earlier is exclusively driven by level-1 facing players, as average early round scores in the NUMBERS game of level-2 facing players are close to 0.
+Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar FWG game, but only those facing the less sophisticated opponent are able to generalise to the less similar NUMBERS game.
 
@@
 Figure~\ref{fig:feedback-rps-exp2} shows an example of showing interaction history in the RPS game.
-Finally, we changed the third game to a penalty shootout game, which has the same number of actions as the first two.
+Finally, we changed the third game to a penalty shootout game, whith participants aiming to score a goal and opponents playing the role of goal keepers.
+Whilst this game has the same number of actions as the first two, it is strategically dissimilar.
+Unlike the third game in the first experiment, it did not have a cyclical hierarchy between actions, making it harder to win by just following simple heuristics leveraging this cyclicality.
 If we see evidence for differential play against opponents, it would show participants adapting their strategies to the opponent they are facing, which is indicative of opponent modelling.
@@
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-score-by-opp-1}
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-score-by-opp-1}
 
@@
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-early-scores-1}
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-early-scores-1}
 
@@
 
-\caption{Average early round scores and 95\% confidence intervals by game and opponent for experiment 2}\label{fig:exp2-early-scores}
+\caption{Mean and standard error of early scores by game and opponent for experiment 2}\label{fig:exp2-early-scores}
 \end{figure}
@@
 
-To gain more insight into how participants played the games against the computer opponents, we estimated and compared different computational models of strategies the players may have been using to learn how to beat the opponent.
+To gain more insight into participants' strategies against their computer opponents, we constructed and tested several computational models of strategy learning.
 The baseline model assumes play is random, and each potential action is chosen with equal probability.
 Note that this corresponds to the Nash equilibrium strategy.
-In this section, we will go through the various models we have used and explain how they update what they learn about the game or the opponent
+The other models adapted their play to the opponent, either by reinforcing successful actions in each game (reinforcement learning), or by determining the type of opponent through Bayesian learning (Bayesian Cognitive Hierarchy models).
+We also include the Expected Weighted Attraction (EWA), which is a popular model in behavioral economics.
 
-\hypertarget{reinforcement-learning}{%
-\subsection{Reinforcement Learning}\label{reinforcement-learning}}
+We use the following notation.
+In each game \(g \in \{\text{RPS},\text{FWG}, \text{NUMBERS}\}\), on each trial \(t\), the participant chooses an action \(a_t \in \mathcal{A}_g\), and the opponent chooses action \(o_t \in \mathcal{A}_g\), where \(\mathcal{A}_g\) is the set of allowed actions in game \(g\), e.g.
+\(\mathcal{A}_\text{RPS} = \{R,P,S\}\).
+The participant then receives reward \(r_t \in \{1,0,-1\}\), and the opponent receives \(-r_t\).
+We use the state variable \(s_t = \{a_{t-1},o_{t-1}\}\) to denote the actions taken in the previous round \(t-1\) by the participant and opponent.
 
-We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
-We will use a simple delta learning update rule:
+In the following, we will describe the models in more detail, and provide some intuition into how they they learn about the game and/or the opponent.
 
-\[ V_{t+1}(a) = V_{t}(a) + \alpha \times ( R_{t}  - V_{t}(a)) \]
+\hypertarget{reinforcement-learning-rl-model}{%
+\subsection{Reinforcement learning (RL) model}\label{reinforcement-learning-rl-model}}
 
-Where \(V_{t}(a)\) is the value associated with action \(a\) at time \(t\), \(\alpha\) is the learning rate and \(R_{t}\) the reward at time t.
-The probability of player \(i\) choosing action \(j\) at time \(t+1\) denoted by \(P_{i}^{j}(t+1)\) is based on action values using a softmax choice rule:
+We first consider a model-free reinforcement learning algorithm, where actions that have led to positive rewards are reinforced, and the likelihood of actions that led to a negative reward is lowered.
+Since the computer players in this experiment based their play on the actions in the previous round, a suitable RL model for this situation is one which learns the value of actions contingent on plays in the previous round, i.e.~by defining the state \(s_{t}\) as above.
+The resulting RL model learns a Q value (Watkins \& Dayan, 1992) for each state-action pair:
 
-\[P_{i}^{j}(t+1) = \frac{e^{\lambda . V_{t}^{j}(a)}}{\sum_{k=1}^{m_{i}}e^{\lambda . V_{t}^{k}(a)}} \]
+\[ Q_{t+1}(s_{t},a_{t}) = Q_{t}(s_{t},a_{t}) + \alpha \left( r_{t}  - Q(s_{t},a_{t}) \right) \]
 
-We extend this very simple model by adding a state space that consists of last round human and agent play.
-This is akin to using a Q-learning algorithm (Watkins \& Dayan, 1992).
-The update rule becomes:
+where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), \(\alpha \in [0,1]\) the learning rate.
+For instance, \(Q_t(\{R,S\},P)\) denotes the value of taking action \enquote{'Paper}' this round if the player's last action was \enquote{'Rock}' and the opponent played \enquote{'Scissors}'.
+Actions are taken according to a softmax rule:
+\[P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}\]
+While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different action space \(\mathcal{A}_g\), and there is no simple way to map actions between games.
 
-\[ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha \times( R_{t}  + \gamma \times \underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) \]
+The RL model has two free parameters: the learning rate (\(\alpha\)) and the inverse temperature parameter of the softmax decision rule (\(\lambda\)).
+We've assumed \(\gamma = 0\) as changes in this parameter didn't affect the other parameter estimations or ultimately the value of the likelihoods.
 
-Where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), \(\gamma\) is the discount rate applied to future rewards.
-For instance, \(Q(RS,P)\) denotes the value of taking action \enquote{Paper} this round if the player's last action was \enquote{Rock} and the opponent played \enquote{Scissors}.
-This is a much richer model allowing the players to compute the values of actions conditional on past play.
+\hypertarget{experience-weighted-attraction-ewa-model}{%
+\subsection{Experience-weighted attraction (EWA) model}\label{experience-weighted-attraction-ewa-model}}
 
-\hypertarget{ewa-models}{%
-\subsection{EWA Models}\label{ewa-models}}
+The self-tuning Experience Weighted Attraction (EWA) model (Ho, Camerer, \& Chong, 2004) combines two seemingly different approaches, namely reinforcement learning and belief learning.
+Belief learning models are based on the assumption that players keep track of the frequency of past actions and best respond to that.
+By contrast, reinforcement learning does not explicitly take into account beliefs about other players, but simply increases the probability of repeating a more rewarding action.
+The self-tuning EWA model has been shown to perform better than either RL or belief learning alone in various repeated games and has the advantage of having only one free parameter, the inverse temperature of the softmax choice function.
+The EWA model is based on updating ``Attractions'' for each action over time.
+The attraction of action \(a\) time \(t\) is written \(A_{t}(a)\) and is updated as
 
-Next, we use a self-tuning Experience Weighted attraction model (Ho, Camerer, \& Chong, 2004).
-EWA models particularity is that they nest two seemingly different approaches, namely reinforcement learning and belief learning.
-Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
-In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
-The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
-Let's define some notation in order to write the update rule of the self-tuning EWA model.
-For player i, there are \(m_{i}\) strategies, denoted \(s_{i}^{j}\) (i.e player i's strategy number j).
-Strategies actually played by i in period t, are denoted \(s_{i}(t)\), while the opponent's strategy at time t is denoted \(s_{-i}(t)\).
-After playing \(s_{i}^{j}\) at time \(t\), player i pay-off is denoted \(\pi_{i}(s_{i}^{j},s_{-i}(t))\), and the actual pay-off the player received is \(\pi_{i}(t)\).
-The EWA model is based on updating \enquote{Attractions} for each action over time.
-For instance, the attraction of strategy \(j\) to player \(i\) at time \(t\) is written \(A_{i}^{j}(t)\).
-Future action choice probabilities are based on these attractions using the softmax playing rule:
+\[ A_{t+1}(a) =  \frac{\phi \ N(t) \ A_{t}(a) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} \]
+where \(I(x)\) is an indicator function which takes the value 1 is its argument is true, and 0 otherwise, and \(R(a,o_t)\) is the reward that would be obtained from playing action \(a\) against opponent action \(o_t\), which equals the actual obtained reward when \(a = a_t\), and otherwise is a counterfactual reward that would have been obtained if a different action were taken.
+Unlike reinforcement learning, this uses knowledge of the rules of the game to allow reinforcing actions that were not taken.
+We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play @{[}cheung1994learning{]}.
+While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Ho et al., 2004).
+\$ N(t)\$ represents an experience weights and can be interpreted as the number of \enquote{observation-equivalents} of past experience.
+We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
 
-\[P_{i}^{j}(t+1) = \frac{e^{\lambda  A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda A_{i}^{k}(t)}} \]
+As in the models above, actions are chosen based on a softmax decision rule:
+\[P_t(a) = \frac{\exp \{\lambda  A_{t}(a) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a') \} }\]
+The self-tuning EWA has one free parameter: the inverse temperature of the softmax decision rule (\(\lambda\)).
 
-The attractions are updated over every time step \(t\) using the following update rule :
+\subsection{Bayesian Cognitive Hierarchy (BCH) model}
 
-\[ A_{i}^{j}(t) =  \frac{\phi \times N(t-1) \times A_{i}^{j}(t-1) + [ \delta + (1-\delta) \times I(s_{i}^{j},s_{i}(t))] \times \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi \times N(t-1) + 1} \]
+In what we call the Bayesian Cognitive Hierarchy (BCH) model, the participant attempts to learn the type of opponent they are facing through Bayesian learning.
+We assume the participant considers the opponent could be either a level 0, level 1, or level 2 player, and starts with a prior belief that each of these types is equally likely.
+They then use observations of the opponents actions to infer a posterior probability of each type:
+\[ P(\text{level}=k | D_{t})  \propto  P(D_{t}|\text{level}=k ) \times P(\text{level}=k)\]
+where \(D_{t} = \{a_1,o_1,\ldots,a_t,o_t\}\) is the data available at time \(t\). The likelihood is defined as
+\[P(D_{t}|\text{level}=k) = \prod_{j=1}^t \left( \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o_j|a_{j-1},o_{j-1})\right)\]
+where \(f_k(o_t|a_{t-1},o_{t-1}) = 1\) if \(o_t\) is the action taken by a level \(k\) player when the previous round play was \(a_{t-1}\) and \(o_{t-1}\), and 0 otherwise.
+Note that the likelihood assumes (correctly) that there is a probability \(\theta \in [0,1]\) that the opponent takes a random action.
+The posterior at time \(t-1\) forms the prior at time \(t\).
+We assume a participant chooses an action by using the softmax function over the best response to predicted actions:
+\[\begin{aligned} B_t(a) &= \sum_{k = 0}^2 \sum_{o \in \mathcal{A}_g} b(a,o) P_k(o|a_{t-1},o_{t-1})  P(\text{level}=k|\mathcal{D}_{t-1})\\
+P_t(a) &= \frac{\exp{\lambda B_t(a)}}{\sum_{a' \in \mathcal{A}_g} \exp \lambda B_t(a')} \end{aligned}\]
+where \(b(a,o) = 1\) if action \(a\) is a best response to opponent's action \(o\) (i.e.~it leads to a win), and \(P_k(o|a_{t-1},o_{t-1}) = \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o|a_{t-1},o_{t-1})\) is the probability that a level \(k\) agent takes action \(o\), as also used in the likelihood above.
 
-Here, \(I(x,y)\) is the indicator function equal to 1 if \(x = y\) and 0 otherwise.
-A simple way to think about this update rule is that attractions are multiplied by a parameter that represents experience (\(N(t-1)\)) which is itself decaying by a weight \(\phi\).
-The result is added to either the pay-off received (when the indicator function is 0), or to \(\delta\) times the foregone pay-off (when indicator function is 1).
-We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play (Cheung \& Friedman, 1994).
-While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Ho et al., 2004).
-
-\hypertarget{tom-models}{%
-\subsection{ToM models}\label{tom-models}}
-
-In this set of models, we assume that participants start with a prior belief that the opponent is a level-k agent, with uniform probability of the level \(k \in \{ 0, 1, 2\}\), and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
-More formally, if we define \(D_{t}\) as data available at time \(t\) then the probability of the opponent being a level-k is updated using:
-
-\[ P(level=k | D_{t})  \propto  P(D_{t}|level=k ) \times P(level=k)\]
-
-These models also assume the opponent can deviate from these level-k strategies and play randomly with probability \(\theta\), a parameter to be fit.
-We also assume that participants base their actions on their beliefs about the level of the opponent, so actions get chosen probabilistically using a softamx choice rule with probabilities of each opponent level as inputs.
-We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
-In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (within but no between transfer).Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
-In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
-In experiment two, on top of these two models, we fit another model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
+Unlike the models above, the BCH model allows for between-game transfer, as knowledge of the level of the opponent can be used to generate predictions in games that have not been played before.
+However, the participant might also assume that the level of reasoning of their opponent does not generalize over games.
+We hence distinguish between two versions of the BCH model.
+In the No-Between-Transfer (BCH\_NBT) variant, participants assume a uniform probability of the different levels at the start of each game (and hence do not transfer knowledge of their opponent between games).
+In the Between-Transfer model (BCH\_BT), participants use the posterior probability over the levels of their opponent as the prior at the start of a new game (i.e.~complete transfer of the knowledge of their opponent).
+Both versions of the BCH model have two free parameters: the assumed probability that the opponent chooses a random action (\(\theta\)), and the temperature parameter of the softmax function (\(\lambda\)).
 
@@
 
-In experiment 1, we fit a total of 5 models: A baseline model assuming random play (Nash), a Bayesian Theory of mind model allowing transfer betwen games (TOM\_BT) and another with no transfer between games (TOM\_NBT), as well as a Q-learning model with state space consisting of last round play (QL\_states), and finally a self tuning EWA model with the same state space (STEWA\_states).
-In experiment 2, because participants were interacting with each opponent twice within each game, we allowed models to transfer learning within games between the first and second interactions.
-Therefore on top of the two ToM models mentionned above (ToM\_BT and Tom\_NBT), we also allow the Q-learning model with states to either have the ability to transfer learning between the first and second interaction (QLS\_Tr) or not (QLS\_NT).
-Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (STEWA\_Tr) or without transfer (STEWA\_NT).
+In experiment 1, we fit a total of 5 models: A baseline model assuming random play (Nash), Bayesian Cognitive Hierarchy model allowing transfer betwen games (BCH\_BT) and another with no transfer between games (BCH\_NBT), as well as a Reinforcement Learning model with state space consisting of last round play (RL), and finally a self tuning EWA model with the same state space (EWA).
+
+In experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two type of opponent model transfer.
+We can have transfer within games, between the first and second interaction with the opponent.
+We can also have transfer between games, as in transfering models of the opponent from RPS to FWG for instance.
+Therefore, we
+give models more flexibility to allow for these two types of transfer.
+As such, for Bayesian Cognitive Hierarchy, we fit a total of three models.
+BCH\_BT allows for between game transfer.
+We assume that if such transfer is possible, then within game transfer should also be possible and therefore this model allows for both types of transfer.
+BCH\_NBT allows for within but no between game transfer.
+Whereas BCH\_NT allows for neither.
+For Reinforcement learning models, because RL models can't account for between game transfer due to change in ation labels, we can only have models allowing for within game transfer (RL Tr) or with no transfer within games (RL NT).
+Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (EWA\_Tr) or without transfer (EWA\_NT).
 Counting the base model wiht random play (Nash) we therefore fit a total of 8 models in experiment 2.
@@
 
-Figure~\ref{fig:exp1-comp-models} shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning with states defined by last round play.
-Table ~\ref{tab:exp1weightstable} shows the model BIC weights as well as the number of participants best fit by each model.
-
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:exp1weightstable}Experiment one Average BIC weights and number of participants best fit by model}
-\begin{tabular}{llllll}
-\toprule
- & \multicolumn{1}{c}{Nash} & \multicolumn{1}{c}{ToM\_BT} & \multicolumn{1}{c}{ToM\_NBT} & \multicolumn{1}{c}{QL\_states} & \multicolumn{1}{c}{STEWA\_States}\\
-\midrule
-Model BIC weights & 0.10 & 0.07 & 0.05 & 0.73 & 0.05\\
-Count best fit & 8.00 & 1.00 & 3.00 & 39.00 & 1.00\\
-\bottomrule
-\end{tabular}
-\end{threeparttable}
-\end{center}
-\end{table}
+Figure~\ref{fig:exp1-comp-models} shows the results for experiment 1: We can see that the RL model clearly described most participants' behaviour best, followed by the random (Nash) model.
+Only a few participants were best described by one of the BCH models, or the EWA model.
+Looking at BIC weights, we confirm this as seen in Figure ~\ref{fig:xp1-BIC-weigths}.
+RL models hve high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, whihc fits the picture drawn by the histogram.
 
@@
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-comp-models-1}
+{\centering \includegraphics[width=\textwidth]{paper_draft_2021_files/figure-latex/exp1-comp-models-1}
 
@@
 
-Next we compared the performance of players whose actions are best fit by each of our hypothesized models.
-Figure~\ref{fig:exp1-cumScores} shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (without transfer), followed by Q-learning conditional on last round play.
-EWA, QL and random players had, understandably the lowest performance.
-
 \begin{figure}
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-cumScores-1}
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/xp1-BIC-weigths-1}
 
@@
 
-\caption{Experiment 1 - Average cumulative scores of participants by best fitting model}\label{fig:exp1-cumScores}
+\caption{Model BIC weights for participants in experiment 1}\label{fig:xp1-BIC-weigths}
 \end{figure}
@@
 
+In experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that the RL model was again more successful than the Bayesian models in fitting player's action choices.
+In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
+This is also reflected in BIC weights in Figure ~\ref{fig:xp2-BIC-weigths}
+
 \begin{figure}
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-comp-models-1}
+{\centering \includegraphics[width=\textwidth]{paper_draft_2021_files/figure-latex/exp2-comp-models-1}
 
@@
 
-\begin{table}
-
-\caption{\label{tab:exp2-weights-table}Experiment 2 - Average BIC weights and number of participants best fit by model}
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
-\hline
-  & Nash & TOM BT & TOM NBT & TOM NT & QLS NT & QLS Tr & STEWA NT & STEWA Tr\\
-\hline
-BIC weights & 0.13 & 0.02 & 0.06 & 0.06 & 0.18 & 0.49 & 0.04 & 0.03\\
-\hline
-Count best fit & 9.00 & 0.00 & 2.00 & 3.00 & 8.00 & 27.00 & 1.00 & 0.00\\
-\hline
-\end{tabular}}
-\end{table}
-
-In experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that Q-learning with the aforementioned state-space was again more successful than the Bayesian models in fitting player's action choices.
-In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
-This is also reflected in BIC weights in Table ~\ref{tab:exp2-weights-table}
-
 \begin{figure}
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-cumScores-1}
+{\centering \includegraphics[width=\textwidth]{paper_draft_2021_files/figure-latex/xp2-BIC-weigths-1}
 
@@
 
-\caption{Experiment 2 Average cumulative scores of participants by best fitting model}\label{fig:exp2-cumScores}
+\caption{Model BIC weights for participants in experiment 2}\label{fig:xp2-BIC-weigths}
 \end{figure}
-
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a ToM model of learning the opponent strategy had the highest cumulative performance.
-Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance (although it only fit 2 participants best), followed by a model in which both within and between transfer of opponent models is allowed (BT).
-The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where players reset opponent models at each stage of each game (NT).
-As expected, random play was at the bottom of cumulative performance.
 
@@
 This is at odds with the findings from the section regarding learning transfer: If indeed most participants use Q-learning with states to choose their actions, then they should not be able to transfer learning to the early rounds of the new game.
-In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Theory of Mind models with and without the possibility of across game transfer.
+In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Bayesian Cognitive Hierarchy models with and without the possibility of across game transfer.
 
 We start with experiment 1 data.
-Figure~\ref{fig:exp1-lik-by-tr} shows that in the later games, the likelihood for the ToM models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of ToM models.
+Figure~\ref{fig:exp1-lik-by-tr} shows that in the later games, the likelihood for the BCH models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of BCH models.
 
@@
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-lik-by-tr-1}
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp1-lik-by-tr-1}
 
@@
 Likewise, in experiment 2, we want to understand the dynamic of strategy choice by plotting the likelihood by trial for each strategy, using the optimal parameters found when fitting the model.
-Figure~\ref{fig:exp2-lik-by-tr} shows that, as in experiment 1, ToM models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
+Figure~\ref{fig:exp2-lik-by-tr} shows that, as in experiment 1, BCH models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
 In the third and more dissimilar game, we get a result that is different from experiment 1.
-In this instance, the likelihoods of the ToM models stay constant and close to their initial values.
+In this instance, the likelihoods of the BCH models stay constant and close to their initial values.
 
@@
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-lik-by-tr-1}
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-lik-by-tr-1}
 
@@
 The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative of participants switching between strategies as the games progressed.
-Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the ToM based strategies fitted observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
+Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the BCH based strategies fitted observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
 
-In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q-learning with state space consisting of previous round play, ToM based model with opponent model transfer, and a base model consisting of random play consistent with a Nash equilibrium strategy).
+In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q-learning with state space consisting of previous round play, BCH based model with opponent model transfer, and a base model consisting of random play consistent with a Nash equilibrium strategy).
 Hidden Markov models are useful tools to explore structure in observed time series.
@@
 
+\begin{verbatim}
+## converged at iteration 7 with logLik: -7415.978
+\end{verbatim}
+
+\begin{verbatim}
+## log Likelihood ratio (chi^2): 211.087 (df=0), p=0.
+\end{verbatim}
+
+\begin{verbatim}
+## [1] 0
+\end{verbatim}
+
 \begin{figure}
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp1-posteriors-plot-1}
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp1-posteriors-plot-1}
 
@@
 The posterior probability is the probability that an observation comes from a component distribution a posteriori, i.e.~given the value of the observation.
-In the first experiment, we can see from the plots of FWG and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the QLS model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
+In the first experiment, we can see from the plots of FWG and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the RL model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
 
@@
 
-{\centering \includegraphics{draft_upgrade_v1_files/figure-latex/exp2-posteriors-plot-1}
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-posteriors-plot-1}
 
@@
 Breaking down likelihoods by trial and fitting a hidden Markov model to the data with states being the various strategies that participants are assumed to be using, we showed evidence for within game switching of strategies.
-Participants start the early rounds of a new game acting in a way consistent with a Bayesian Theory of mind level, which would be accurate and generalisable but computationally expensive.
+Participants start the early rounds of a new game acting in a way consistent with a Bayesian Bayesian Cognitive Hierarchy level, which would be accurate and generalisable but computationally expensive.
 However, as trials continue, participants seem to switch to a habitual type of learning (QL-models).
@@
 When a new game is started that is similar to a previously played game with the same opponent, participants need a way to transfer prior knowledge of the opponent and apply it to the new game in order to best respond.
-Adopting a Bayesian model based on ToM achieves the goal of transferring the opponent model and thus coming up with best responses in the early trials.
-However, Bayesian ToM models are computationally expensive and require higher order thinking (I think that you think that I think\ldots{}).
+Adopting a Bayesian model based on BCH achieves the goal of transferring the opponent model and thus coming up with best responses in the early trials.
+However, Bayesian BCH models are computationally expensive and require higher order thinking (I think that you think that I think\ldots{}).
 As such, as the games progresses, they may become burdensome and the higher amount of historical interaction in the new game allows participants to have enough data to start using the cognitively cheaper model-free learning strategies such as Q-learning.
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-arad201211}{}%
-Arad, A., \& Rubinstein, A. (2012). The 11-20 money request game: A level-k reasoning study. \emph{American Economic Review}, \emph{102}(7), 3561--3573.
-
-\leavevmode\hypertarget{ref-baarslag2016learning}{}%
-Baarslag, T., Hendrikx, M.
-J.
-C., Hindriks, K.
-V., \& Jonker, C.
-M.
+\leavevmode\hypertarget{ref-batzilis}{}%
+Batzilis, D., Jaffe, S., Levitt, S., List, J.
+A., \& Picel, J.
 (2016).
-Learning about the opponent in automated bilateral negotiation: a comprehensive survey of opponent modeling techniques.
-\emph{Autonomous Agents and Multi-Agent Systems}, \emph{30}(5), 849--898.
+\emph{How facebook can deepen our understanding of behavior in strategic settings: Evidence from a million rock-paper-scissors games}.
+working paper.
 
@@
 
-\leavevmode\hypertarget{ref-cheung1994learning}{}%
-Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
+\leavevmode\hypertarget{ref-knez2000}{}%
+Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
 
@@
 Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
+
+\leavevmode\hypertarget{ref-ho1998iterated}{}%
+Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
 
@@
 
-\leavevmode\hypertarget{ref-perkins1992transfer}{}%
-Perkins, D. N., \& Salomon, G. (1992). Transfer of learning. \emph{International Encyclopedia of Education}, \emph{2}, 6452--6457.
-
-\leavevmode\hypertarget{ref-premack1978does}{}%
-Premack, D., \& Woodruff, G. (1978). Does the chimpanzee have a theory of mind? \emph{Behavioral and Brain Sciences}, \emph{1}(4), 515--526.
-
 \leavevmode\hypertarget{ref-shachat2004we}{}%
@@
 
-\leavevmode\hypertarget{ref-simon1972theories}{}%
-Simon, H. A. (1972). Theories of bounded rationality. \emph{Decision and Organization}, \emph{1}(1), 161--176.
-
 \leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
@@
 
+\leavevmode\hypertarget{ref-wang2014social}{}%
+Wang, Z., Xu, B., \& Zhou, H.-J. (2014). Social cycling and conditional responses in the rock-paper-scissors game. \emph{Scientific Reports}, \emph{4}(1), 1--7.
+
 \leavevmode\hypertarget{ref-watkins1992q}{}%
 Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
-
-\leavevmode\hypertarget{ref-de2012higher}{}%
-Weerd, H.
-de, Verbrugge, R., \& Verheij, B.
-(2012).
-Higher-order social cognition in rock-paper-scissors: A simulation study.
-\emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3}, 1195--1196.
 
@@
 
-\leavevmode\hypertarget{ref-arad201211}{}%
-Arad, A., \& Rubinstein, A. (2012). The 11-20 money request game: A level-k reasoning study. \emph{American Economic Review}, \emph{102}(7), 3561--3573.
-
-\leavevmode\hypertarget{ref-baarslag2016learning}{}%
-Baarslag, T., Hendrikx, M.
-J.
-C., Hindriks, K.
-V., \& Jonker, C.
-M.
+\leavevmode\hypertarget{ref-batzilis}{}%
+Batzilis, D., Jaffe, S., Levitt, S., List, J.
+A., \& Picel, J.
 (2016).
-Learning about the opponent in automated bilateral negotiation: a comprehensive survey of opponent modeling techniques.
-\emph{Autonomous Agents and Multi-Agent Systems}, \emph{30}(5), 849--898.
+\emph{How facebook can deepen our understanding of behavior in strategic settings: Evidence from a million rock-paper-scissors games}.
+working paper.
 

### 2021-06-04 _main.Rmd
added report in papaja and softmax to BCH models

---
title: "Bayesian_models_exp1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

```{r}

dat <- read.csv("data20180719.csv")

####### test data

#dat <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")

#######

dat <- as_tibble(dat) %>% group_by(human_id,game)
dat <- dat %>%
  mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1))

```

```{r}
## the following computes probabilities of ai actions assuming
## strategy is always followed. (level refers to ai level)

## level 0 predictions
dat <- dat %>% mutate(pred_a1_level0 = case_when(
  game == "rps" & ai_action_prev == "rock" ~ 1,
  game == "fwg" & ai_action_prev == "fire" ~ 1,
  game == "numbers" & ai_action_prev == "one" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level0 = case_when(
  game == "rps" & ai_action_prev == "paper" ~ 1,
  game == "fwg" & ai_action_prev == "water" ~ 1,
  game == "numbers" & ai_action_prev == "two" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level0 = case_when(
  game == "rps" & ai_action_prev == "scissors" ~ 1,
  game == "fwg" & ai_action_prev == "grass" ~ 1,
  game == "numbers" & ai_action_prev == "three" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a4_level0 = case_when(
  game == "numbers" & ai_action_prev == "four" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))
dat <- dat %>% mutate(pred_a5_level0 = case_when(
  game == "numbers" & ai_action_prev == "five" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))

## level 1 predictions
dat <- dat %>% mutate(pred_a1_level1 = case_when(
  game == "rps" & human_action_prev == "scissors" ~ 1,
  game == "fwg" & human_action_prev == "grass" ~ 1,
  game == "numbers" & human_action_prev == "five" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level1 = case_when(
  game == "rps" & human_action_prev == "rock" ~ 1,
  game == "fwg" & human_action_prev == "fire" ~ 1,
  game == "numbers" & human_action_prev == "one" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level1 = case_when(
  game == "rps" & human_action_prev == "paper" ~ 1,
  game == "fwg" & human_action_prev == "water" ~ 1,
  game == "numbers" & ai_action_prev == "two" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a4_level1 = case_when(
  game == "numbers" & ai_action_prev == "three" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))
dat <- dat %>% mutate(pred_a5_level1 = case_when(
  game == "numbers" & ai_action_prev == "four" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))

## level 2 predictions
dat <- dat %>% mutate(pred_a1_level2 = case_when(
  game == "rps" & ai_action_prev == "paper" ~ 1,
  game == "fwg" & ai_action_prev == "water" ~ 1,
  game == "numbers" & ai_action_prev == "four" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level2 = case_when(
  game == "rps" & ai_action_prev == "scissors" ~ 1,
  game == "fwg" & ai_action_prev == "grass" ~ 1,
  game == "numbers" & ai_action_prev == "five" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level2 = case_when(
  game == "rps" & ai_action_prev == "rock" ~ 1,
  game == "fwg" & ai_action_prev == "fire" ~ 1,
  game == "numbers" & ai_action_prev == "one" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a4_level2 = case_when(
  game == "numbers" & ai_action_prev == "two" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))
dat <- dat %>% mutate(pred_a5_level2 = case_when(
  game == "numbers" & ai_action_prev == "three" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))

dat$ai_action_num <- recode(dat$ai_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "one" = 1, "two" = 2, "three" = 3, "four" = 4 , "five" = 5)
dat$human_action_num <- recode(dat$human_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "one" = 1, "two" = 2, "three" = 3, "four" = 4 , "five" = 5)

```

```{r}
# group data by subjective component id

# if human generalizes over games, we can run update the prior generally
# if human does not generalize, we need to reset the prior at the start of each ?stage?
exp1_Bayes_model_LL <- function(par,data, generalize = c("game","no"), softmax= TRUE, return_value = "-2loglik") {

  # return_value=c("-2loglik","likelihood_by_trial")
  # input data for this function should be a subset for a single participant
  generalize <- match.arg(generalize)
  alpha <- par[1] # probability that ai opponent plays according to strategy

  if(softmax) {
    lambda <- par[2] # inverse temperature parameter in softmax function
  }

  beta <- 1 # probability that human plays according to best response 
  prior <- c(1,1,1) # prior alpha for dirichlet on p(level)
  prior <- prior/sum(prior)

  # use alpha to change the "deterministic" prediction

  dat <- ungroup(data) %>%
     mutate_at(.vars = vars(c(starts_with("pred_a1"),starts_with("pred_a2"),starts_with("pred_a3"))), 
                            funs (case_when(
      game == "numbers" ~  alpha*. + (1-alpha)/5,
                  TRUE ~ alpha*. + (1-alpha)/3))) %>%
     mutate_at(.vars = vars(c(starts_with("pred_a4"),starts_with("pred_a5"))), 
                            funs (case_when(
      game == "numbers" ~  alpha*. + (1-alpha)/5,
                  TRUE ~ 0)))

  if(generalize == "no") {
    # group by game and stage
    dat <- group_by(dat,game,add=TRUE)
  }

  # compute likelihood of ai action
  dat <- dat %>%
    mutate(
      lik_level0 = case_when(
        ai_action_num == 1 ~ pred_a1_level0,
        ai_action_num == 2 ~ pred_a2_level0,
        ai_action_num == 3 ~ pred_a3_level0,
        ai_action_num == 4 ~ pred_a4_level0,
        ai_action_num == 5 ~ pred_a5_level0
      ),
      lik_level1 = case_when(
        ai_action_num == 1 ~ pred_a1_level1,
        ai_action_num == 2 ~ pred_a2_level1,
        ai_action_num == 3 ~ pred_a3_level1,
        ai_action_num == 4 ~ pred_a4_level1,
        ai_action_num == 5 ~ pred_a5_level1
      ),
      lik_level2 = case_when(
        ai_action_num == 1 ~ pred_a1_level2,
        ai_action_num == 2 ~ pred_a2_level2,
        ai_action_num == 3 ~ pred_a3_level2,
        ai_action_num == 4 ~ pred_a4_level2,
        ai_action_num == 5 ~ pred_a5_level2
      )
    )

  # use likelihood to compute the posterior predictive probability of each level
  dat <- dat %>%
    mutate(logpost_level0 = lag(log(prior[1]) + cumsum(log(lik_level0)),default=log(prior[1])),
           logpost_level1 = lag(log(prior[2]) + cumsum(log(lik_level1)),default=log(prior[2])),
           logpost_level2 = lag(log(prior[3]) + cumsum(log(lik_level2)),default=log(prior[3]))) %>%
    # you can add or subtract any constant from the log-likelihoods; this can aid in precision
    mutate(min = pmin(logpost_level0,logpost_level1, logpost_level2)) %>%
      mutate(normalize = exp(logpost_level0 - min) + exp(logpost_level1 - min) + exp(logpost_level2 - min)) %>%
        mutate(post_level0 = exp(logpost_level0 - min)/normalize,
               post_level1 = exp(logpost_level1 - min)/normalize,
               post_level2 = exp(logpost_level2 - min)/normalize)

   #cat(as.character(c(round(dat$post_level0,2), round(dat$post_level1,2), round(dat$post_level2,2)), "\n", "\n"))

  # use posterior predictive probability to predict probability of each ai and then human action
  # opp is ai and self is human player here
  dat <- dat %>%
    mutate(p_opp_a1 = post_level0*pred_a1_level0 + post_level1*pred_a1_level1 + post_level2*pred_a1_level2,
           p_opp_a2 = post_level0*pred_a2_level0 + post_level1*pred_a2_level1 + post_level2*pred_a2_level2,
           p_opp_a3 = post_level0*pred_a3_level0 + post_level1*pred_a3_level1 + post_level2*pred_a3_level2,
           p_opp_a4 = post_level0*pred_a4_level0 + post_level1*pred_a4_level1 + post_level2*pred_a4_level2,
           p_opp_a5 = post_level0*pred_a5_level0 + post_level1*pred_a5_level1 + post_level2*pred_a5_level2
    ) %>%
      mutate(p_self_a1 = case_when(
              game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a5,
              TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a3)
                ),
             p_self_a2 = case_when(
               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a1,
               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a1)
             ),
             p_self_a3 = case_when(
               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a2,
               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a2)
             ),
             p_self_a4 = case_when(
               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a3,
               TRUE ~ 0
             ),
             p_self_a5 = case_when(
               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a4,
               TRUE ~ 0
             )
        )

  #cat(as.character(c(round(dat$p_self_a1,2), "\n", "\n")))

  # now finally compute the likelihood of human actions 
  if (softmax) {

        dat <- dat %>% 
    mutate(sumexp = exp(lambda*p_self_a1) + exp(lambda*p_self_a2) + exp(lambda*p_self_a3) + exp(lambda*p_self_a4) + exp(lambda*p_self_a5)) %>%
             mutate(
               loglik = case_when(
                 human_action_num == 1 ~ log(exp(lambda*p_self_a1)/sumexp),
                 human_action_num == 2 ~ log(exp(lambda*p_self_a2)/sumexp),
                 human_action_num == 3 ~ log(exp(lambda*p_self_a3)/sumexp),
                 human_action_num == 4 ~ log(exp(lambda*p_self_a4)/sumexp),
                 human_action_num == 5 ~ log(exp(lambda*p_self_a5)/sumexp)
      )
    )
  } else {
    dat <- dat %>% 
    mutate(
      loglik = case_when(
        human_action_num == 1 ~ log(p_self_a1),
        human_action_num == 2 ~ log(p_self_a2),
        human_action_num == 3 ~ log(p_self_a3),
        human_action_num == 4 ~ log(p_self_a4),
        human_action_num == 5 ~ log(p_self_a5))
    )

  }

  #cat(as.character(exp(dat$loglik)), "\n", "\n")

  ret <- -2*sum(dat$loglik)
  if(return_value == "-2loglik") {
    if(is.infinite(ret) || is.nan(ret)) {
    return(1e+300)
    } else {
      return(ret)
    } 
  } else if ((return_value == "likelihood_by_trial")) {
    return(exp(dat$loglik))
  }

}

```

```{r}
# testing funcrion. Careful dat here can be all participants data, check how it is defined. 
exp1_Bayes_model_LL(c(0.4, 1) ,data = dat, generalize = "no", softmax = TRUE, "likelihood_by_trial")[51]
exp1_Bayes_model_LL(c(0.4) ,data = dat, generalize = "no", softmax = FALSE, "likelihood_by_trial")[51]
```
## Compare loglikelihood: probability matching vs softmax (with Between game transfer for now)

```{r echo=FALSE}
library(DEoptim)

prob_match_tr <- use_softmax_tr <- use_softmax_NT <- list()

# # Using DEOptim 
for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))

  prob_match_tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                  generalize = "game",FALSE, control=ctrl)

  use_softmax_tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat, generalize = "game",TRUE, control=ctrl)

  use_softmax_NT[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat, generalize = "no",TRUE, control=ctrl)

}

save(prob_match_tr,file="BCH_prob_match_tr.RData")
save(use_softmax_tr,file="BCH_use_softmax_tr.RData")
save(use_softmax_NT,file="BCH_use_softmax_NT.RData")
```

```{r}
compare_table <- data.frame()
for(id in levels(dat$human_id)) {
  compare_table <- rbind(compare_table,
                       data.frame(
                         "ID" = id,
                         "prob_match_tr_BIC" = prob_match_tr[[id]]$optim$bestval+ 1*log(150),
                         "softmax_tr_BIC" = use_softmax_tr[[id]]$optim$bestval+ 2*log(150)
                         ))
}

```

```{r}

comp_models <- compare_table[c("ID","prob_match_tr_BIC","softmax_tr_BIC")]

BIC_weights_BCH <- comp_models["ID"]
BIC_weights_BCH[,2:ncol(comp_models)] <- t(apply(comp_models[,2:ncol(comp_models)], 1, function(i) exp(-0.5*(i-min(i)) )))
colnames(BIC_weights_BCH) <-colnames(comp_models)

BIC_weights_BCH[,2:ncol(BIC_weights_BCH)] <- t(apply(BIC_weights_BCH[,-1], 1, function(i) round(i/sum(i),2)))

colMeans(BIC_weights_BCH[,2:ncol(BIC_weights_BCH)])
```

```{r}

```

```{r}
#PLot likelihood for first participant as function of parameter

dat <- subset(dat, human_id == "QSuzBXpbyRc370HsAACW")
likelihoods <- list()
for (t in 1:95) {
  likelihoods[t] <- exp1_Bayes_model_LL(t/100,data = dat, generalize = "game")
}

jpeg(file="QSuzBXpbyRc370HsAACW.jpeg")
plot(unlist(likelihoods))
dev.off()

```

```{r, ECHO = FALSE}

library(DEoptim)

exp1_Bayes_game_Tr <- exp1_Bayes_no_Tr <- list()

# # Using DEOptim 
for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))
  exp1_Bayes_game_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                  generalize = "game",control=ctrl)
  exp1_Bayes_no_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                  generalize = "no",control=ctrl)
}

# using optim

# for(id in levels(dat$human_id)) {
#   tdat <- subset(dat,human_id == id)
#   # ctrl <- DEoptim.control(NP = 20, itermax=50)
#   
#   Bayes_same_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
#   
#   
#   Bayes_same_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_same_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_distinct_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_distinct_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_distinct_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
# }
```
```{r}

exp1_Bayes_game_Tr[["QSuzBXpbyRc370HsAACW"]]$optim$bestval
exp1_Bayes_game_Tr[["QSuzBXpbyRc370HsAACW"]]$optim$bestmem[[1]]
```

<!--chapter:end:Bayesian_models_exp1.Rmd-->

---
title: "opponent modelling"
author: "Ismail Guennouni & Maarten Speekenbrink"
date: "1 November 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

## Reading data

```{r}
dat <- read.csv("data20180719.csv")
#dat <- read.csv("test_data.csv")
```

## Preprosessing and transforming data

```{r}
# using some functions from the 'tidyverse' (also for me to get use to them ;-)
library(tidyr)
library(dplyr)
library(DEoptim)
library(optimParallel)
library(ggpubr)

# create a new data.frame in a 'wide format'
# widedata <- dat %>%
#   unite(game_block,game,block) %>% # this creates a new variable which combines game and block
#     group_by(human_id,condition,game_block) %>% # let the functions know you want to separate things by ID, condition, and game_block
#       summarize(mean_score = mean(score)) %>% # compute average score (i.e wins - losses)
#         spread(game_block,mean_score) # reformat in the 'wide' format
# # save the data file as a .csv to use in e.g. SPSS
# write.csv(widedata,row.names=FALSE,file="scores_wide.csv")

```

```{r estimate-models, cache=TRUE}
# read in the various files which 
rps_predict_opp <- read.csv("rps_predict_opp.csv")
fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
numbers_predict_opp <- read.csv("numbers_predict_opp.csv")

# transform 'winner' variable in numeric score
dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat$block <- as.numeric(cut(dat$round,2))

# recode actions to make them equal to the codes in these files
dat$h_action <- recode(dat$human_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
dat$a_action <- recode(dat$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")

write.csv(dat,file = "exp1_data.csv", row.names = FALSE)

# logit tranformation
my_logit <- function(x) {
  ret <- log(x/(1-x))
  ret[x==0] <- -Inf
  ret[x==1] <- Inf 
  return(ret)
}

# inverse logit transformation
my_logistic <- function(x) {
  ret <- 1/(1+exp(-x))
  ret[x == -Inf] <- 0.0
  ret[x == Inf] <- 1.0
  return(ret)
}

```

#### New work 
## Q-learning (Basic)
```{r}
Q_learn <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
  # actions
  # beta= inverse temperature parameter in softmax choice function
  # lambda = learning rate (one per game?)
  # data : participant and ai choice data.
  # Returns Q-values per trial and predicts choice using softmax
  beta <- par[1]
  alpha <- par[2]
  Q_vals_RPS = matrix(0.0,3)
  names(Q_vals_RPS) <- c("R","P","S")
  Q_vals_FWG = matrix(0.0,3)
  names(Q_vals_FWG) <- c("F","W","G")
  Q_vals_NUM = matrix(0.0,5)
  names(Q_vals_NUM) <- c("1","2","3","4","5")

  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
      lik_hum[t] <- 1/nopts
    } else {
      # Get reward and past human action
      reward <- as.numeric(data[t-1,"score"])
      h_act_prev <- as.character(data[t-1,"h_action"])
      Q_vals[h_act_prev] <- Q_vals[[h_act_prev]] + as.numeric(alpha)*( reward - Q_vals[[h_act_prev]])

      # cat(Q_vals,"\n")

      # Assume human chooses action probabilistically using softmax on Q values
      probs <- exp(Q_vals/beta)/sum(exp(Q_vals/beta))

      # Get actual human action and compute likelihood
      h_act <- as.character(data[t,"h_action"])
      act_index <- match(h_act, names(Q_vals))
      #cat(as.character(act_index))
      lik_hum[t] <- probs[[act_index]]
    }
  }
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)

}

```

## Q-learning fit
```{r, cache=TRUE}
QL_modelling <- list()
for(id in unique(dat$human_id)) {
  QL_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
  QL_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
}
save(QL_modelling,file="QL_modelling.RData")

```

## First attempt : Q-Learning with state space consisting of last round play (deprecated) 
```{r}

# Q_learn_states <- function(par,data,return_value,gamma){
#   # Par[1] -> beta= inverse temperature parameter in softmax choice function
#   # Par[2] -> lambda = learning rate (one per game?)
#   # data : participant and ai choice data.
#   # return_value=c("-2loglik","likelihood_by_trial")
#   # Gamma is discount factor for future rewards 
#   # Returns Q-values per trial and predicts choice using softmax
#   beta <- par[1]
#   alpha <- par[2]
# 
#   #gamma <- 0.9 
# 
#   #Define matrix of state spaces for each game 
#   G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
#   states_RPS <- paste0(G1$Var1,G1$Var2)
# 
#   G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
#   states_FWG <- paste0(G2$Var1,G2$Var2)
# 
#   G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
#   states_NUM <- paste0(G3$Var1,G3$Var2)
#   
#   Q_vals_RPS = matrix(-0.5,9,3)
#   dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
# 
#   Q_vals_FWG = matrix(-0.5,9,3)
#   dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
#   
#   Q_vals_NUM = matrix(-0.5,25,5)
#   dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
#  
#   lik_hum <- matrix(0.0,nrow(data))
# 
#   for(t in 1:nrow(data)) {
#     t_game <- data[t,"game"]
#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
#     
#     if(data[t,"round"] == 1) {
#       # first round is uniform prediction
#       Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
#       state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
#       lik_hum[t] <- 1/nopts
#       # Randomly select prev_state and actions for first round
#       curr_state <- sample(state_vec, size = 1)
#       h_act <- sample(colnames(Q_vals), size =1)
#       ai_act <- sample(colnames(Q_vals), size =1)
#       reward <- 0 
#       
#     } else {
#       # Get past human action and associated reward 
#       h_act <- as.character(data[t-1,"h_action"])
#       ai_act <- as.character(data[t-1,"a_action"])
#       reward <- as.numeric(data[t-1,"score"])
#     }
#     
#     
#     # cat(curr_state, " This is the previous state", "\n")
#     new_state <- paste0(h_act,ai_act)
#     # cat(new_state,"This is new state","\n")
#     
#     # Q_learning: update rule (time  = t-1)
#     Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
#     
#     # Assume human chooses action probabilistically using softmax on Q values
#     probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
#     #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }
#     
#     # Get actual human action and compute likelihood
#     h_act <- as.character(data[t,"h_action"])
#     act_index <- match(h_act, colnames(Q_vals))
#     lik_hum[t] <- probs[[act_index]]
#       
#     # Update state
#     curr_state <- new_state 
#     #}
#   }
#   if(return_value == "-2loglik") {
#     ret <- -2*sum(log(lik_hum))
#     if(is.infinite(ret) || is.nan(ret)) {
#       return(1e+300)
#     } else {
#       return(ret)
#     }
#   }
#   if(return_value == "likelihood_by_trial") return(lik_hum)
#   
# }

```

#Second attempt at QL algorithm with states: No guessing of initial states
```{r}
Q_learn_states <- function(par,data,return_value,gamma){
  # Par[1] -> beta= inverse temperature parameter in softmax choice function
  # Par[2] -> lambda = learning rate (one per game?)
  # data : participant and ai choice data.
  # return_value=c("-2loglik","likelihood_by_trial")
  # Gamma is discount factor for future rewards 
  # Returns Q-values per trial and predicts choice using softmax
  beta <- par[[1]]
  alpha <- par[[2]]

  #Define matrix of state spaces for each game 
  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
  states_RPS <- paste0(G1$Var1,G1$Var2)

  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
  states_FWG <- paste0(G2$Var1,G2$Var2)

  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
  states_NUM <- paste0(G3$Var1,G3$Var2)

  Q_vals_RPS = matrix(-0.5,9,3)
  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))

  Q_vals_FWG = matrix(-0.5,9,3)
  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))

  Q_vals_NUM = matrix(-0.5,25,5)
  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))

  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {

    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3

    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
      lik_hum[t] <- 1/nopts

    } else {
      # Get past human action and associated reward 
      h_act_prev <- as.character(data[t-1,"h_action"])
      ai_act_prev <- as.character(data[t-1,"a_action"])
      curr_state <- paste0(h_act_prev,ai_act_prev)

      h_act <- as.character(data[t,"h_action"])
      ai_act <- as.character(data[t,"a_action"])
      reward <- as.numeric(data[t,"score"])

      new_state <- paste0(h_act,ai_act)

      # Assume human chooses action probabilistically using softmax on Q values
      probs <- exp(Q_vals[curr_state,]/beta)/sum(exp(Q_vals[curr_state,]/beta))

      # Get actual human next action and compute likelihood
      act_index <- match(h_act, colnames(Q_vals))
      lik_hum[t] <- probs[[act_index]]

       # Q_learning: update rule (time = t)
      Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])

      # Update state
      curr_state <- new_state

    }

  }
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)

}

```

```{r}
data34 <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")

# Q_learn_states(c(5, 0.5),data34 ,return_value = "likelihood_by_trial",gamma = 0 )

```

## Fitting Q_learning with states
```{r , cache =TRUE}
# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
# Q_learn_states(c(0.1,0.1), data, "-2loglik")

QL_states_modelling <- list()
for(id in unique(dat$human_id)) {
  QL_states_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
  # QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")

   QL_states_modelling[[id]] <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))
}

save(QL_states_modelling, file="QL_states_modelling.RData")

# QL_states_gamma <- list()
# for(id in unique(dat$human_id)) {
#   QL_states_gamma[[id]] <- list()
#   tdat <- subset(dat,human_id == id)
#   QL_states_gamma[[id]] <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0.9, control=list(trace = FALSE,parallelType=1))
# }
# save(QL_states_gamma,file="QL_states_gamma.RData")

```

```{r}
# OK, let's compare BICs and parameters for Gamma = 0 and Gamma = 0.9 (both for initial Q-values of -0.5)

compare_QL_states <- data.frame()
for(id in unique(dat$human_id)) {
compare_QL_states  <- rbind(compare_QL_states ,
                       data.frame(
                         "id" = id,
                         "condition" = dat[dat$human_id==id,"condition"][1],
                         "Zero_Gamma_BIC" = QL_states_modelling[[id]]$optim$bestval + 2*log(150),
                         "High_gamma_BIC" = QL_states_gamma[[id]]$optim$bestval + 2*log(150),
                         "diff" = QL_states_modelling[[id]]$optim$bestval - QL_states_gamma[[id]]$optim$bestval
                       ))
}

```
#Notes: Q-Learning as done above is far from optimal. The reason is that most states are never visited during play ( anecdotal evidence, about 40-60% in RPS/FWG and 10-20% in NUM). This method needs a lot more rounds to start modelling players behavior correctly.

## Parametric Experience Weighted Attraction model (Camerer & Ho 1997)
```{r}
EWA_par <- function(par,data,return_value){
  # par: vector of parameters to the EWA model
  # Data :choice data by trial for each participant
  # Returns sum of loglikelihoods or likelihood per trial
  phi <- par[1]
  delta <- par[2]
  rho <- par[3]
  lambda <- par[4]

  # Define attraction vectors for each game
  A_RPS = matrix(0.0,3)
  names(A_RPS) <- c("R","P","S")
  A_FWG = matrix(0.0,3)
  names(A_FWG) <- c("F","W","G")
  A_NUM = matrix(0.0,5)
  names(A_NUM) <- c("1","2","3","4","5")

  # # Define reward matrices from the prospective of the row player (human in our case)
  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))

  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))

  # Initiate likelihood by trial vector
  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
      reward <- switch(as.character(t_game),rps=reward_RPS,fwg = reward_FWG, numbers = reward_NUM)
      lik_hum[t] <- 1/nopts
      # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.
      N <- 1

    } else {
      # Get reward and past human action
      h_act_prev <- as.character(data[t-1,"h_action"])
      a_act_prev <- as.character(data[t-1,"a_action"])
      for (i in 1:length(Att)) {
        action <- as.character(names(Att)[i])
        # cat("this is current strat",action,"\n")
        # cat("this is previous human action",h_act_prev,"\n")

        # Attraction vector update rule
        Att[[i]] <- (phi*N*Att[[i]]  + ( delta + (1- delta)*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (rho*N + 1)
      }
      #Update the value of N
      N <- rho*N + 1

      # Assume human chooses action probabilistically using softmax on Attraction values
      probs <- exp(lambda*Att)/sum(exp(lambda*Att))

      # Get actual human action and compute likelihood
      h_act <- as.character(data[t,"h_action"])
      act_index <- match(h_act, names(Att))
      lik_hum[t] <- probs[[act_index]]
    }
  }

 if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret) ) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)
}
```

## Fitting Parametric EWA to data 
```{r, cache =TRUE}

EWA_modelling <- list()
for(id in unique(dat$human_id)) {
  EWA_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
  # EWA_modelling[[id]] <- optim(c(0.5,0.5,0.5,0.5),fn=EWA_par,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.001,0.001,0.001), upper = c(1,0.99,0.99,1), method="L-BFGS-B")
  EWA_modelling[[id]] <- DEoptim(fn=EWA_par,lower = c(0.01,0.01,0.01,0.01), upper = c(10,1,1,10), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))
}

save(EWA_modelling,file="EWA_modelling.RData")

```

##  Self-Tuning EWA (Camerer & Ho 2007) 
```{r}

EWA_self <- function(par,data,return_value){

  lambda <- par[1]
  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.

  # Define attraction vectors for each game 
  A_RPS = matrix(0.0,3)
  names(A_RPS) <- c("R","P","S")
  A_FWG = matrix(0.0,3)
  names(A_FWG) <- c("F","W","G")
  A_NUM = matrix(0.0,5)
  names(A_NUM) <- c("1","2","3","4","5")

  # # Define reward matrices from the prospective of the row player (human in our case)
  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))

  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))

  # Initiate likelihood by trial vector 
  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
      reward <- switch(as.character(t_game),rps=reward_RPS,fwg = reward_FWG, numbers = reward_NUM)
      game_data <- subset(data, game == t_game)
      lik_hum[t] <- 1/nopts
      N <- 1.0

      R_t <- rep(0.0,nopts)
      H_t <- R_t

    } else {

      indx <- data[t,"round"]
      # Get reward and past human action
      h_act_prev <- as.character(game_data[indx-1,"h_action"])
      a_act_prev <- as.character(game_data[indx-1,"a_action"])

      # Estimate phi(t)
      R_t <- as.numeric(names(Att) == a_act_prev)
      # cat("This is R(t)",R_t,"\n")

      H_t <- (H_t*(indx-2) + R_t)/(indx-1)
      # cat("this is H(t)",H_t,"\n")

      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
      # cat("This is Phit(t)",Phi_t,"\t")

      # Estimate vector Delta(t)

      delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
      #cat("this is delta(t)",delta_t,"\n")

      for (i in 1:length(Att)) {
        action <- as.character(names(Att)[i])
        # cat("this is current strat",action,"\n")
        # cat("this is previous humna action",h_act_prev,"\n")

        # Attraction vector update rule 
        Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
      }
      #Update the value of N 
      N <- Phi_t*N + 1
      #cat(Att,'\n')

      # Assume human chooses action probabilistically using softmax on Attraction values
      probs <- exp(lambda*Att)/sum(exp(lambda*Att))

      # Get actual human action and compute likelihood
      h_act <- as.character(game_data[indx,"h_action"])
      act_index <- match(h_act, names(Att))
      lik_hum[t] <- probs[[act_index]]
    }
  }

 if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)
}

```

```{r}
##Plotting self_tuning EWA likelihood function for lambda from 0 to 100 
# 
# lambdas <- seq(1,10,0.01)
# count = 0.0
# 
# 
# 
# for(id in unique(dat$human_id)) {
#   if (count <= 15) {
#       tdat <- subset(dat,human_id == id)
#       likelihoods <- sapply(lambdas, EWA_self, tdat, "-2loglik")
#       plot(lambdas,likelihoods)
#       count <- count + 1
#   }
# }

```

## Fitting Self-Tuning EWA to data 
```{r, cache=TRUE}

EWA_self_modelling <- list()
for(id in unique(dat$human_id)) {
  EWA_self_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
#   EWA_self_modelling[[id]] <- optim(10.0,fn=EWA_self,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
# }
  EWA_self_modelling[[id]] <- DEoptim(fn=EWA_self, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
}

save(EWA_self_modelling,file="EWA_self_modelling.RData")

```

```{r}
# cat(EWA_self_modelling[["38VxtUSv_h6RR5-tAAA2"]]$optim$bestmem)
```

##  First attempt : Self-Tuning EWA with prior round play as state (Camerer & Ho 2007) 
```{r}
# Initiates N(0) = 1 as in Camerer and Ho 1997 paper. 
# 
# EWA_states <- function(par,data,return_value){
# 
#   lambda <- par[1]
# 
#   #Define matrix of state spaces for each game 
#   G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
#   states_RPS <- paste0(G1$Var1,G1$Var2)
# 
#   G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
#   states_FWG <- paste0(G2$Var1,G2$Var2)
# 
#   G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
#   states_NUM <- paste0(G3$Var1,G3$Var2)
#   
#   A_RPS = matrix(-0.5,9,3)
#   dimnames(A_RPS) = list(states_RPS, c("R", "P", "S"))
# 
#   A_FWG = matrix(-0.5,9,3)
#   dimnames(A_FWG) = list(states_FWG, c("F", "W", "G"))
#   
#   A_NUM = matrix(-0.5,25,5)
#   dimnames(A_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
# 
#   
#   # # Define reward matrices from the perspective of the row player (human in our case)
#   reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
#   dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
#   
#   reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
#   dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
#   
#   reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
#   dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
#   
#   # Initiate likelihood by trial vector 
#   lik_hum <- matrix(0.0,nrow(data))
# 
#   for(t in 1:nrow(data)) {
#     t_game <- data[t,"game"]
#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
#     if(data[t,"round"] == 1) {
#       Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
#       state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, numbers = states_NUM)
#       reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, numbers = reward_NUM)
#       game_data <- subset(data, game == t_game)
#       
#       # first round is uniform prediction
#       lik_hum[t] <- 1/nopts
#       N <- 1.0
# 
#       R_t <- rep(0.0,nopts)
#       H_t <- R_t
#       
#       # Randomly select prev_state and actions for first round
#       curr_state <- sample(state_vec, size = 1)
#       h_act_prev <- sample(colnames(Att), size =1)
#       a_act_prev <- sample(colnames(Att), size =1)
#       #reward <- 0 
#       
#     } else {
#       
#       indx <- data[t,"round"]
#       state_indx <- match(curr_state,state_vec)
#       #cat("this is the current state index", state_indx, "\n")
#       
#       # Get reward and past human action
#       h_act_prev <- as.character(game_data[indx-1,"h_action"])
#       a_act_prev <- as.character(game_data[indx-1,"a_action"])
#       new_state <- paste0(h_act_prev,a_act_prev)
# 
#       # Estimate R(t) (recent history) then H(t) (history) then phi(t) (change detector)
#       R_t <- as.numeric(colnames(Att) == a_act_prev)
#       #cat("This is R(t)",R_t,"\n")
#       
#       H_t <- (H_t*(indx-2) + R_t)/(indx-1)
#       #cat("this is H(t)",H_t,"\n")
#       
#       Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
#       #cat("This is Phit(t)",Phi_t,"\t")
#       
#       # Estimate vector Delta(t)
#       delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
#       #cat("this is delta(t)",delta_t,"\n")
#       
#       for (i in 1:nopts) {
#         action <- as.character(colnames(Att)[i])
# 
#         #cat("this is current indexed action",action,"\n")
#         #cat("this is previous human action",h_act_prev,"\n")
#         
#         # Attraction vector update rule
#         Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
#       }
#       
#       #Update the value of N 
#       N <- Phi_t*N + 1
# 
#       # Assume human chooses action probabilistically using softmax on Attraction values
#       probs <- exp(lambda*Att[new_state,])/sum(exp(lambda*Att[new_state,]))
#       
#       # Get actual human action and compute likelihood
#       h_act <- as.character(game_data[indx,"h_action"])
#       act_index <- match(h_act, colnames(Att))
#       lik_hum[t] <- probs[[act_index]]
#       
#       curr_state <- new_state
#       
#       # if (indx == 50) {
#       #   cat("this is the attraction matrix at last round of", "\n")
#       #   print(Att)
#       # }
#     }
#   }
#   
#  if(return_value == "-2loglik") {
#     ret <- -2*sum(log(lik_hum))
#     if(is.infinite(ret) || is.nan(ret)) {
#       return(1e+300)
#     } else {
#       return(ret)
#     }
#   }
#   if(return_value == "likelihood_by_trial") return(lik_hum)
# }

```

### Second attempt at ST_EWA with states and no initial guess of initial states. 
```{r}
ST_EWA_STATES <- function(par,data,return_value){

  lambda <- par[1]

  #Define matrix of state spaces for each game 
  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
  states_RPS <- paste0(G1$Var1,G1$Var2)

  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
  states_FWG <- paste0(G2$Var1,G2$Var2)

  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
  states_NUM <- paste0(G3$Var1,G3$Var2)

  A_RPS = matrix(-0.5,9,3)
  dimnames(A_RPS) = list(states_RPS, c("R", "P", "S"))

  A_FWG = matrix(-0.5,9,3)
  dimnames(A_FWG) = list(states_FWG, c("F", "W", "G"))

  A_NUM = matrix(-0.5,25,5)
  dimnames(A_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))

  # # Define reward matrices from the perspective of the row player (human in our case)
  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))

  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))

  # Initiate likelihood by trial vector 
  lik_hum <- matrix(0.0,nrow(data))

   for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3

    if(data[t,"round"] == 1) {
      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
      state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, numbers = states_NUM)
      reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, numbers = reward_NUM)
      game_data <- subset(data, game == t_game)

      # first round is uniform prediction
      lik_hum[t] <- 1/nopts
      # Asumme N(0) = 1 for now...see discussion in paper
      N <- 1.0
      # initialize H_t by looking at first action 
      # H_t <- rep(0.0,nopts)
      a_act <- as.character(game_data[1,"a_action"])
      H_t <- as.numeric(colnames(Att) == a_act)

      # Rounds 2 to end 
    } else {

      indx <- data[t,"round"]

      # Get reward and past human action
      h_act_prev <- as.character(game_data[indx-1,"h_action"])
      a_act_prev <- as.character(game_data[indx-1,"a_action"])
      curr_state <- paste0(h_act_prev,a_act_prev)

      h_act <- as.character(game_data[indx,"h_action"])
      a_act <- as.character(game_data[indx,"a_action"])
      new_state <- paste0(h_act,a_act)

      # Assume human chooses action probabilistically using softmax on Attraction values
      probs <- exp(lambda*Att[curr_state,])/sum(exp(lambda*Att[curr_state,]))

      # Get actual human action and compute likelihood
      act_index <- match(h_act, colnames(Att))
      lik_hum[t] <- probs[[act_index]]

      # Update rule:
      # Estimate R(t) (recent history) then H(t) (history) then phi(t) (change detector)
      R_t <- as.numeric(colnames(Att) == a_act)
      #cat("This is R(t)",R_t,"\n")

      H_t <- (H_t*(indx-1) + R_t)/(indx)
      #cat("this is H(t)",H_t,"\n")

      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
      #cat("This is Phit(t)",Phi_t,"\t")

      # Estimate vector Delta(t)
      delta_t <- as.numeric(reward[,a_act] >= as.numeric(game_data[indx,"score"]))
      #cat("this is delta(t)",delta_t,"\n")

      # This is a vectorised ST_EWA update rule, easier to follow the loop below in comments
      state_indx <- match(curr_state,state_vec)
      Att[state_indx,] <- (Phi_t*N*Att[state_indx,]  + ( delta_t + (1- delta_t)*(colnames(Att) == h_act))*as.numeric(reward[colnames(Att),a_act])) / (Phi_t*N + 1)

      ##############
      # for (i in 1:nopts) {
      #   action <- as.character(colnames(Att)[i])
      #   state_indx <- match(curr_state,state_vec)
      #   #cat("this is the current state index", state_indx, "\n")
      # 
      #   # Attraction vector update rule
      #   Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act))*as.numeric(reward[action,a_act])) / (Phi_t*N + 1)
      # 
      # }
      # 
      #cat("this is the current Att vector", Att, "\n")
      ###################

      #Update the value of N 
      N <- Phi_t*N + 1

      #Update the state 
      curr_state <- new_state 
    }
   }  
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)

}

```

```{r}
# data12 = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
# ST_EWA_STATES(0.5, data12, "-2loglik")
# optim(10.0,fn=ST_EWA_STATES,gr = NULL, data=data12,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")

```

```{r, cache=TRUE}

ST_EWA_STATES_modelling <- list()
for(id in unique(dat$human_id)) {
  ST_EWA_STATES_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
#   ST_EWA_STATES_modelling[[id]] <- optim(10.0,fn=ST_EWA_STATES,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
# }
  ST_EWA_STATES_modelling[[id]] <- DEoptim(fn=ST_EWA_STATES, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
}

save(ST_EWA_STATES_modelling,file="ST_EWA_STATES_modelling.RData")

```

## What next?: Fitting models that explicitly take into account opponent strategy. LOLA? Won't work, it suffers from same issues as normal QL in that most states are not visited during game play. Influence model? Like belief lerning. it still has no sequential memory, still computes distribution on beliefs. We need to incorporate models that can mimic human memory by looking at history of play and leverage sequence prediction capabilities.

### Model based model: learn transition probabilities to new states. Weigh the value of an action by the conditional probability of ending up in a future state times the value of the new state.... once you take an action in current round, you can only end up in 3 states, with probabilities p, q and 1-p-q. You are learning these probabilities by updating priors (initial prior is dirichlet). 
```{r}
MBM <- function(par,data,return_value,gamma){
  # Par[1] -> beta= inverse temperature parameter in softmax choice function
  # Par[2] -> lambda = learning rate (one per game?)
  # data : participant and ai choice data.
  # return_value=c("-2loglik","likelihood_by_trial")
  # Gamma is discount factor for future rewards 
  # Returns Q-values per trial and predicts choice using softmax
  beta <- par[1]
  alpha <- par[2]

  #gamma <- 0.9

  #Define matrix of state spaces for each game 
  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
  states_RPS <- paste0(G1$Var1,G1$Var2)

  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
  states_FWG <- paste0(G2$Var1,G2$Var2)

  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
  states_NUM <- paste0(G3$Var1,G3$Var2)

  # Matrices to store Q_values in each state 
  Q_vals_RPS = matrix(-0.5,9,3)
  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
  Q_vals_FWG = matrix(-0.5,9,3)
  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
  Q_vals_NUM = matrix(-0.5,25,5)
  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))

  # Transition Matrices 
  Transit_RPS = matrix(1/9,9,9)
  dimnames(Transit_RPS) = list(states_RPS, states_RPS)
  Transit_FWG = matrix(1/9,9,9)
  dimnames(Transit_FWG) = list(states_FWG, states_FWG)
  Transit_NUM = matrix(1/25,25,25)
  dimnames(Transit_NUM) = list(states_NUM, states_NUM)

  lik_hum <- matrix(0.0,nrow(data))

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    if(t_game == "numbers") nopts <- 5 else nopts <- 3

    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
      Transit <- switch(as.character(t_game),rps=Transit_RPS,fwg = Transit_FWG, numbers = Transit_NUM)
      lik_hum[t] <- 1/nopts
      # Randomly select prev_state and actions for first round
      curr_state <- sample(state_vec, size = 1)
      h_act <- sample(colnames(Q_vals), size =1)
      ai_act <- sample(colnames(Q_vals), size =1)
      reward <- 0

    } else {
      # Get past human action and associated reward 
      h_act <- as.character(data[t-1,"h_action"])
      ai_act <- as.character(data[t-1,"a_action"])
      reward <- as.numeric(data[t-1,"score"])
    }

    # cat(curr_state, " This is the previous state", "\n")
    new_state <- paste0(h_act,ai_act)
    # cat(new_state,"This is new state","\n")

    # Update Transit matrix ....first create hot vector = 1 if new state, 0 otherwise 
    hot_vector <- state_vec == new_state

    # Transit probs update: TD learning on transition matrix, learning rate fixed at 0.1
    Transit[curr_state,] <- Transit[curr_state,] + 0.1* (hot_vector - Transit[curr_state,])
    #cat(Transit[curr_state,], "\n")

    # Update Q-values as current reward + a weighted (by trasnsit probs) average of future Q-values.
    Q_Row_max <- apply(Q_vals, 1, max, na.rm = TRUE)
    #cat(Transit[curr_state,] * Q_Row_max, "\n")
    Q_vals[curr_state, h_act] <- reward +  gamma*( Transit[curr_state,] %*% Q_Row_max  )

    # Assume human chooses action probabilistically using softmax on Q values
    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
    #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }

    # Get actual human action and compute likelihood
    h_act <- as.character(data[t,"h_action"])
    act_index <- match(h_act, colnames(Q_vals))
    lik_hum[t] <- probs[[act_index]]

    # Update state
    curr_state<- new_state 
    #}
  }
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret) || is.nan(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)

}

```

```{r, cache=TRUE}
MBM_modelling <- list()
for(id in unique(dat$human_id)) {
  MBM_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
  # MBM_modelling[[id]] <- optim(c(1,0.1),fn=QMBM,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")

   MBM_modelling[[id]] <- DEoptim(fn=MBM,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0.9, control=list(trace = FALSE,parallelType=1))
}

save(MBM_modelling, file="MBM_modelling.RData")

```

## Putting results together 
```{r}
load("QL_modelling.RData")
load("QL_states_modelling.RData")
load("EWA_modelling.RData")
load("EWA_self_modelling.RData")
load("MBM_modelling.RData")
load("ST_EWA_STATES_modelling.RData")

All_results <- data.frame()
for(id in unique(dat$human_id)) {
  All_results <- rbind(All_results,
                       data.frame(
                         "ID" = id,
                         "condition" = dat[dat$human_id==id,"condition"][1],
                         "Random_BIC" = -2*(100*log(1/3) + 50*log(1/5)),

                         # Bayesian updating with/without transfer 
                         # "Bayes_Tr_BIC" = exp1_Bayes_game_Tr[[id]]$optim$bestval+ 1*log(150),
                         # "Bayes_No_Tr_BIC" = exp1_Bayes_no_Tr[[id]]$optim$bestval + 1*log(150),
                         # # Theta is the parameter governing AI stochasticity. Truth is 0.9
                         # "theta_transfer" = exp1_Bayes_game_Tr[[id]]$optim$bestmem[[1]],
                         # "theta_no_transfer" = exp1_Bayes_no_Tr[[id]]$optim$bestmem[[1]],
                         #

                         # BCH with/without transfer (With Softmax) 
                         "Bayes_Tr_BIC" = use_softmax_tr[[id]]$optim$bestval+ 2*log(150),
                         "Bayes_No_Tr_BIC" = use_softmax_NT[[id]]$optim$bestval+ 2*log(150),

                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
                         "theta_transfer" = use_softmax_tr[[id]]$optim$bestmem[[1]],
                         "lambda_transfer" = use_softmax_tr[[id]]$optim$bestmem[[2]],

                         "theta_no_transfer" = use_softmax_NT[[id]]$optim$bestmem[[1]],
                         "lambda_no_transfer" = use_softmax_NT[[id]]$optim$bestmem[[2]],

                         # Q-Learning
                         "QL_BIC" = QL_modelling[[id]]$value + 2*log(150),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QL_Beta" = QL_modelling[[id]]$par[1],
                         # alpha -> learning rate in QL update
                         "QL_alpha" = QL_modelling[[id]]$par[2],

                         # Q-learning with last round states
                         "QL_states_BIC" = QL_states_modelling[[id]]$optim$bestval + 2*log(150),
                         # beta ->  inverse temperature parameter in softmax choice function
                         "QL_states_Beta" = QL_states_modelling[[id]]$optim$bestmem[1],
                         # alpha -> learning rate in QL update
                         "QL_states_alpha" = QL_states_modelling[[id]]$optim$bestmem[2],

                         # Parametric EWA
                         # Parametric EWA BIC
                         "EWA_BIC" = EWA_modelling[[id]]$optim$bestval + 4*log(150),
                         "EWA_2LL" = EWA_modelling[[id]]$optim$bestval,
                         # Phi is depreciation of past attractions
                         "EWA_Phi" = EWA_modelling[[id]]$optim$bestmem[1],
                         # Delta is weight of foregone payoffs vs actual payoffs
                         "EWA_Delta" = EWA_modelling[[id]]$optim$bestmem[2],
                         # Rho is depreciation of the experience measure N(t)
                         "EWA_Rho" = EWA_modelling[[id]]$optim$bestmem[3],
                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
                         "EWA_Lambda" = EWA_modelling[[id]]$optim$bestmem[4],

                         # Self-Tuning EWA (only 1 parameter)
                          # Parametric EWA BIC
                         # "EWA_self_2LL" = EWA_self_modelling[[id]]$optim$bestval,
                         # "EWA_self_BIC" = EWA_self_modelling[[id]]$optim$bestval + 1*log(150),
                         # #Lambda is a parameter of the softmax choice function (inverse Temperature)
                         # "EWA_self_Lambda" = EWA_self_modelling[[id]]$optim$bestmem[1],

                         # self_tuning EWA with states

                         "ST_EWA_STATES_BIC" = ST_EWA_STATES_modelling[[id]]$optim$bestval + 1*log(150),
                         "ST_EWA_STATES_Lambda" = ST_EWA_STATES_modelling[[id]]$optim$bestmem[1]

                         ))
}

write.csv(All_results,file="exp1_all_results.csv",row.names = FALSE)

```

## Calucalting BIC weights
```{r}

comp_BICs <- All_results[c("ID","Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","ST_EWA_STATES_BIC")]

exp1_BIC_weights <- comp_BICs["ID"]
exp1_BIC_weights[,2:ncol(comp_BICs)] <- t(apply(comp_BICs[,2:ncol(comp_BICs)], 1, function(i) exp(-0.5*(i-min(i)) )))
colnames(exp1_BIC_weights) <-colnames(comp_BICs)

exp1_BIC_weights[,2:ncol(exp1_BIC_weights)] <- t(apply(exp1_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))

```

## Building table of best model per participant
```{r}

# Table_results <- table(All_results[, "condition"],c("random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","ST_EWA_STATES")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","ST_EWA_STATES_BIC")],1,which.min)])

# We choose to omit the simple QL and EWA and opt to only include the ones with states as they are more relevant.

Table_results <- table(All_results[, "condition"],c("random","ToM_BT","ToM_NBT", "QL_states","ST_EWA_STATES")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])

 write.csv(Table_results,file="Table_results.csv",row.names = TRUE)
 kable(Table_results)
 #barplot(Table_results)

```
##### Looks like most participants behavior can be explained by QL_states. Bayesian models best explain a few more behaviors, while the others are consistent with random behavior, and only 1 with QL and 1 with S_EWA.

###### Question: Can we see evidence for transfer by looking at difference in BICS btwn Bayes with and without transfer. Let's test correlation between difference in BICs  with early rounds score (evidence for transfer) 
```{r}
# id_results_tst <- subset(All_results, ID == "38VxtUSv_h6RR5-tAAA2")
```

```{r}

exp1_model_comp <- data.frame()
for(id in unique(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(All_results, ID == id)
  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,min)

  best_model <- c("random","ToM_Game_Tr","ToM_No_Tr", "QL_states","ST_EWA_STATES")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)]

  exp1_model_comp <- rbind(exp1_model_comp,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat[dat$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

                       ))
}

write.csv(exp1_model_comp,file = "exp1_model_comp.csv", row.names = FALSE)

```

### Correlate difference between BICs of Bayes transfer and no transfer with early rounds score (evidence for transfer) 
```{r}

cor.test(exp1_model_comp$TR_minus_NT_BIC,exp1_model_comp$Early_game_score, method="spearman")

```

### Correlation between early game score and difference between best model and random BIC
```{r}
cor.test(exp1_model_comp$Rand_minus_best_BIC, exp1_model_comp$Early_game_score, method="spearman")

```
### Histogram of best fitting models 
```{r}
barplot(table(exp1_model_comp$Best_model))
```
# Notes : There is positive and stat significant correlation between the difference between the best model BIC and random BIC on one hand, and the early scores from the target games ( FWG and NUM). What does this mean? It can be interpreted as a validation of early game score as good measure of how non-random play is....

# More exploratory work......

## Let's compare total scores of each participant by the model of best fit, see if Bayes+transfer total scores are higher than Bayes + no transfer

```{r}

# ggboxplot(exp1_model_comp, x = "model", y = "Total_score",
#           color = "model", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
#           order = c("Random", "No Transfer", "Transfer"),
#           ylab = "Total Score", xlab = "Model with best fit")

exp1_model_comp$model <- recode(exp1_model_comp$Best_model,"Bayes Tr" = "Tranfer","Bayes No Tr" = "No Transfer", "QL_states" = "Q_Learning",  .default = "Random")
model <- factor(exp1_model_comp$model)
condition <- factor(exp1_model_comp$condition)

# Total score by best predictive model 
tapply(exp1_model_comp$Total_score, model, mean)

# Compute the analysis of variance
res.aov <- aov(Total_score ~ model + condition, data = exp1_model_comp)
# Summary of the analysis
summary(res.aov)
TukeyHSD(res.aov)
```

## What if we remove from data people who play randomly and then compare Transfer v No Transfer? 
```{r}

Non_Random_Only <- subset(exp1_model_comp, model != "Random" )

group_by(Non_Random_Only, model) %>%
  summarise(
    count = n(),
    mean = mean(Early_game_score, na.rm = TRUE),
    sd = sd(Early_game_score, na.rm = TRUE)
  )

res2 <- aov(Early_game_score ~ model, data = Non_Random_Only) 
summary(res2)
TukeyHSD(res2)
```

# Total time by best predictive model
```{r}
tapply(exp1_model_comp$Total_time, model, mean)

time.aov <- aov(Total_time ~ model, data = exp1_model_comp)
# Summary of the analysis
summary(time.aov)
TukeyHSD(time.aov)

``` 
#Early game scores for people best modelled with a Bayesian model with transfer are indeed higher than those best modelled without transfer but difference is not statistically significant.

<!--chapter:end:comp_model_1019.Rmd-->

---
output:
  html_document: default
  word_document: default
---
--
title: "opponent modelling"
author: "Ismail Guennouni"
date: "30 July 2018"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dat1 <- read.csv("data20180719.csv")
```

```{r}
# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
library(tidyr)
library(dplyr)
library(MASS)
library(ggpubr)
library(PairedData)
library(multcompView)
library(lsmeans)

# transform 'winner' variable in numeric score
dat1$score <- recode(dat1$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat1$block <- factor(as.numeric(cut(dat1$round,2)),labels =c("first half", "second half"))

# create a new variable "game.f" as a factor variable of games
dat1$game.f <- factor(dat1$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))

# overall score to pay bonuses 
dat_score <- dat1 %>% 
  group_by(human_id) %>% 
      summarize(overall_score = sum(score))
(avg_bonus <- floor(mean(abs(dat_score$overall_score))))*0.02

#Group data by human_id and calculate mean score per block of each game.
dat2 <- dat1 %>% 
  group_by(human_id,condition,game,block,game.f) %>% 
      summarize(block_score = mean(score))

# Group data by game and ID
dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
# head(dat3,6)

# Subsetting scores data by game
rps <- subset(dat3,  game.f == "RPS",game_score)
fwg <- subset(dat3,  game.f == "FWG",game_score)
num <- subset(dat3,  game.f == "NUM",game_score)
# head(rps,6)
```

```{r}
# Look at some summary statistics of group means #############################

group_by(dat2, game.f) %>%
  summarise(
    mean = mean(block_score, na.rm = TRUE),
    sd = sd(block_score, na.rm = TRUE)
  )

group_by(dat2, game.f, block) %>%
  summarise(
    count = n(),
    mean = mean(block_score, na.rm = TRUE),
    sd = sd(block_score, na.rm = TRUE)
  )

group_by(dat2, game.f, condition,block) %>%
  summarise(
    count = n(),
    mean = mean(block_score, na.rm = TRUE),
    sd = sd(block_score, na.rm = TRUE)
  )
```

```{r}
# PLOTS  #############################

# Plot scores per game

ggboxplot(dat3, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")

ggerrorplot(dat3, x = "game.f", y = "game_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")

# Plot paired scores between games
#pd <- paired(rps,fwg)
#pd2 <- paired(fwg,num)
#head(pd)
#plot(pd, type = "profile")
#plot(pd2, type = "profile")
ggpaired(dat3, x = "game.f", y = "game_score",color = "game.f", id = "human_id", line.color = "gray", line.size = 0.4, palette = "npg")

# Plot results by game and block (for all 3 games, learning is happening) 
ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")

# Group data by game and ID
dat4 <- group_by(dat2, human_id,condition,game.f) %>% summarise(game_score = mean(block_score))

# Level 2 is harder to win against than level 1
ggboxplot(dat2, x = "condition", y = "block_score", palette = c("#00AFBB", "#E7B800"), fill="condition",ylab = "Percentage score", xlab = "Conditions")

ggerrorplot(dat2, x = "condition", y = "block_score", desc_stat = "mean_ci" , palette = c("#00AFBB", "#E7B800"), color="condition",ylab = "Percentage score", xlab = "Conditions")

# Main effect of block 
ggerrorplot(dat2, x = "block", y = "block_score", desc_stat = "mean_ci" , palette = c("#00AFBB", "#E7B800"), color="block",ylab = "Percentage score", xlab = "Block")

# Breaking it down by game (seems to be true for RPS and FWG, less so for Numbers )
ggboxplot(dat4, x = "game.f", y = "game_score", palette = c("#00AFBB","#E7B800","#FC4E07"), fill="condition",order = c("RPS", "FWG","NUM"),ylab = "Game Score", xlab = "Conditions")

```

```{r}
# Testing score against hypothesis of random play  ######################################

# Normality of scores 
shapiro.test(dat3$game_score)

# Testing Scores against random play (expected 0 average score)
t.test(as.numeric(rps$game_score), mu = 0, alternative = "two.sided")
t.test(as.numeric(fwg$game_score), mu = 0, alternative = "two.sided")
t.test(as.numeric(num$game_score), mu = 0, alternative = "two.sided")

```

```{r}
# AFEX PACKAGE FOR RUNNING RM ANOVA AND POST HOC TESTS ############################
citation(package = "afex", lib.loc = NULL, auto = NULL)
library(afex)
a1 <- aov_car( block_score ~ game.f*block*condition + Error(human_id/(game.f*block)), dat2)
summary(a1)
(a1_nice <- nice(a1, es = attr(a1$anova_table, "es"),
  observed = attr(a1$anova_table, "observed"),
  correction = attr(a1$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(a1$anova_table,
  "p_adjust_method"), sig_symbols = attr(a1$anova_table, "sig_symbols")))

write.table(a1_nice,file = "a1.txt", sep = ",", quote = FALSE, row.names = F)

## Note to Self: no need to worry abour the HF warning. You don't have pb with sphericity according to Mauchly tests, and the warning only applies to Huynh-Feldt corrections for violations of sphericity. 
```

```{r}
#Pair waise comparison and post hoc tests for the interaction: Game * Block using lsmeans

# game score differences statistically significant?
(ls0 <- lsmeans(a1, "game.f"))
(lsm0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))

# Main effect of block 
(ls01 <- lsmeans(a1, "block"))
(lsm01 <- update(pairs(ls01, reverse = TRUE), by=NULL, adjust = "holm"))
lsmip(a1, ~block)

# Main effect of condition
(ls02 <- lsmeans(a1, "condition"))
(lsm02 <- update(pairs(ls02, reverse = TRUE), by=NULL, adjust = "holm"))

```

```{r}
# Pairwise comparison of first halves by game ( first half RPS vs first half WFG scores....)
(ls1 <- lsmeans(a1, "block" , by="game.f"))
(lsm1 <- update(pairs(ls1, reverse = TRUE), by=NULL, adjust = "holm"))
lsmip(a1, game.f ~ block)
```

```{r}
# Pairwise comparison of each game score by block (first half RPS vs second half RPS....) + Control for family wise error:
ls2 <- lsmeans(a1, c("block","game.f"))
(lsm2 <- update(pairs(ls2, reverse = TRUE), by=NULL, adjust = "holm"))
(contr2 <- contrast(ls2, list(G1H2vG2H1 = c(0,1,-1,0,0,0))))
(contr3 <- contrast(ls2, list(G1H1vs0 = c(1,0,0,0,0,0))))
lsmip(a1, block ~ game.f)
lsmip(a1, ~ block * game.f)
```

```{r}
# Pairwise comparison of scores facing the two types of players by game: 
lsc <- lsmeans(a1, "condition", by="game.f")
(lsmc <- update(pairs(lsc), by=NULL, adjust = "holm"))
plot(lsmc,by="game.f")
lsmip(a1, condition ~ game.f)

```

```{r}
#Pair waise comparison and post hoc tests : Game by Block and Condition

#library(multcompView)
#use cld to check for comparison pairs belonging to same group, meaning not significantly different from each other...
#cld(lsm4)

#plots
ls4 <- lsmeans(a1, "block",c("condition","game.f"))
ls4
(lsm4 <- update(pairs(ls4, reverse = TRUE), by=NULL, adjust = "holm"))

plot(lsm4,by="game.f")
lsmip(a1, game.f ~ block | condition)

# Interaction plot of game and block by condition 
lsmip(a1, game.f ~ block | condition)
lsmip(a1, condition ~ block * game.f)
```

```{r}
# Transfer harder for level2 opponent than when facing level 1 opponent? 
# learning to specifiy contrasts - 
# the below compares the score on each block and game for each type and tells me which scores belong to same group
# the idea is that if transfer is harder vs lvl2 player, then fwg first half score for lvl2 facing player should be sig lower than fwg first-half score vs lvl1 agent.not the case here as thye belong to same group.

(means.int <- lsmeans(a1, specs = c("game.f","block","condition")))

# Transfer level1: compare H1FWG with H1RPS 
con1  <- contrast(means.int, list(H1_G2vsH1_G1forlvl1 = c(-1,1,0,0,0,0,0,0,0,0,0,0), H1_G3vsH1_G1forlvl1=c(-1,0,1,0,0,0,0,0,0,0,0,0)))
summary(con1, adjust = "holm")

# Transfer level2: compare H1FWG with H1RPS 
con2  <- contrast(means.int, list(H1_G2vsH1_G1forlvl2 = c(0,0,0,0,0,0,-1,1,0,0,0,0), H1_G3vsH1_G1forlvl2=c(0,0,0,0,0,0,-1,0,1,0,0,0)))
summary(con2, adjust = "holm")

# compare first half (H1) scores between level 1 and level 2 players in FWG and NUM
con3 <- contrast(means.int, list(G1vG2forH1 = c(0,1,0,0,0,0,0,-1,0,0,0,0), G2vG3forh1=c(0,0,1,0,0,0,0,0,-1,0,0,0)))
summary(con3, adjust ="holm")

# Within game learning harder for level2 opponent than when facing level 1 opponent? compare differences between block for each game and type
con4 <- contrast(means.int, list(L2vL1forRPS = c(1,0,0,-1,0,0,-1,0,0,1,0,0), L2vL1forFWG=c(0,1,0,0,-1,0,0,-1,0,0,1,0), L2vL1forNUM=c(0,0,1,0,0,-1,0,0,-1,0,0,1)))
summary(con4, adjust ="holm")

```

```{r}

#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########

dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
dat2_6 <- dat_26 %>% 
  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
      summarise(early_score = mean(score))

write.csv(dat2_6,"exp1_early_rounds.csv")

# Check group means and SDs
group_by(dat2_6, game.f) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
group_by(dat2_6, game.f,condition) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
# plot early scores per game 
ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")

# testing differences between early scores across games 
library(afex)
aov_early <- aov_car(early_score ~ game.f*condition + Error(human_id/(game.f)),data=dat2_6)
summary(aov_early)

aov_ear_nice <- nice(aov_early, es = attr(aov_early$anova_table, "es"),
  observed = attr(aov_early$anova_table, "observed"),
  correction = attr(aov_early$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(aov_early$anova_table,
  "p_adjust_method"), sig_symbols = attr(aov_early$anova_table, "sig_symbols"))

write.table(aov_ear_nice,file = "aov_ear.txt", sep = ",", quote = FALSE, row.names = F)

# including confidence 
#aov_conf_26 <- aov_car(early_score ~ game.f*condition*difficulty + Error(human_id/(game.f)),data=dat2_6)
#summary(aov_conf_26)

```

```{r}

# (ls4 <- lsmeans(aov_early, "game.f"))
# (summary(ls4, infer = c(TRUE,TRUE), null = 0,level = 0.95, adjust = "bon"))

(means.int2 <- lsmeans(aov_early, specs = c("game.f","condition")))
(trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "none",ref=c("FWG","NUM")))
#(contr26 <- contrast(means.int2, list(G2L1vsG2L2 = c(0,1,0,0,-1,0))))

write.table(format(trans26, digits=2),file = "trans26.txt", sep = ",", quote = FALSE, row.names = F)

# compare early scores in FWG for lvl 1 and lvl2 / same for NUM

contrast(means.int2, list(G1vG2for26 = c(0,1,0,0,-1,0), G2vG3for26=c(0,0,1,0,0,-1)))

# Plot interactions for early rouns, condition by game

lsmip(aov_early, ~ game.f | condition )

# plots overall effect by game :
ggboxplot(dat2_6,"game.f", "early_score", fill = "game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"),order = c("RPS","FWG","NUM"))

# Note to Self: possible future work exstension is to pick the guys who scored highly on the first rounds of the second game and fit the various learning models to them only. 
# Two ways to test learning: compare first half between games for different conditions 
# compare early score between games for different conditions 
# Check whteher confidence and difficulty  -> add them as covariates in big anova and early score anova *confidence*difficulty.... --> too hard to interpret

# do a model comparison with model without confidence and difficulty -> start witn ANCOVA (try and see what happens with various interactions).  
```

```{r}
# adding confidence and difficulty feedback 
datcd <- dat1 %>% 
  group_by(human_id,condition,confidence,difficulty) %>% 
      summarise(avg_score = mean(score))

# testing conf, diff and score for normality 
shapiro.test(datcd$avg_score)
shapiro.test(datcd$confidence)
shapiro.test(datcd$difficulty)

# histograms 
hist(datcd$confidence, breaks = 20)
hist(datcd$difficulty, breaks=10)

# descriptive stats 
group_by(datcd, condition) %>%
  summarise(
    count = n(),
    median = median(confidence, na.rm = TRUE),
    IQR = IQR(confidence, na.rm = TRUE)
  )

group_by(datcd, condition) %>%
  summarise(
    count = n(),
    median = median(difficulty, na.rm = TRUE),
    IQR = IQR(difficulty, na.rm = TRUE)
  )
# Comparing confidence and difficulty by condition
(res1 <- wilcox.test(confidence ~ condition, data = datcd,exact = FALSE))
(res2 <- wilcox.test(difficulty ~ condition, data = datcd,exact = FALSE))

# Correlation confidence difficulty and score: 
mat <- as.matrix(datcd[,unlist(lapply(datcd, is.numeric))])
cor.test(datcd$confidence, datcd$avg_score, method="spearman")
cor.test(datcd$difficulty, datcd$avg_score, method="spearman")

# Transforming confidence into 4 lvl factor
datcd$confidence.f <- factor(as.numeric(cut(datcd$confidence,2)),labels =c("low conf","high conf"))
summary(datcd$confidence.f)
table(datcd$confidence.f,datcd$condition)

#  explore interaction block confidence
#(lsm7 <- lsmeans(acd, c("confidence.f","block")))
#(update(pairs(lsm7, reverse = TRUE, adjust = "holm"), by=NULL))
#plot(lsm7, by ="confidence.f")
#lsmip(acd, confidence.f ~ block)

#
#(lsm8 <- lsmeans(acd, c("confidence.f","block","game.f")))
#lsmip(acd, confidence.f ~ block*game.f)
# checking that low confidence NUMBERS play is not different from random play
#con3 <- contrast(lsm8, list(G1vG2forconf = c(0,0,0,0,0,0,0,0,0,0,1,0)))
#summary(con3, adjust ="holm")

# low and high confidence players have similar initial score in RPS
#con4 <- contrast(lsm8, list(HCvLCforRPS = c(-1,1,0,0,0,0,0,0,0,0,0,0)))
#summary(con4, adjust="holm")
```

```{r}
# ANCOVA with confidence as covariate 
dat_ancova <- dat1 %>% 
  group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 
      summarise(avg_score = mean(score))
# Centering variables for ANCOVA 
dat_ancova$conf_cen <- scale(dat_ancova$confidence, center=TRUE, scale=FALSE) 
dat_ancova$diff_cen <- scale(dat_ancova$difficulty, center=TRUE, scale=FALSE)

# run RM anova using afex library (ran anova including difficulty as well but wasn't significant)
library(afex)
acd <- aov_car( avg_score ~ game.f*block*condition + conf_cen + diff_cen + Error(human_id/(game.f*block)), factorize = FALSE,dat_ancova)
summary(acd)

nice(acd, es = attr(acd$anova_table, "es"),
  observed = attr(acd$anova_table, "observed"),
  correction = attr(acd$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(acd$anova_table,
  "p_adjust_method"), sig_symbols = attr(acd$anova_table, "sig_symbols"))

# post hoc tests
(anc1 <- lsmeans(acd, c("conf_cen")))

(lsm6 <- lsmeans(acd, c("conf_cen","condition")))
update(pairs(lsm6, reverse = TRUE, adjust = "holm"), by=NULL)
plot(lsm6, by ="condition")
plot(lsm6, by ="conf_cen")
lsmip(acd, conf_cen ~ condition)

```

```{r}

# transform data by differencing two consecutive scores, filter for first and second transfer 
library(dplyr)
dat_test1 <- dat1 %>% 
  group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 
      summarise(avg_score = mean(score)) %>%
         group_by(human_id) %>%
            mutate(diff_score = avg_score - lag(avg_score, default = 0)) %>%
              mutate(learn_phase =c("init RPS","within RPS","transfer 1","within WFG","transfer 2","within MOD"))

head(dat_test1)        
# define dataset with first transfer only 
dat_trans1 <- dat_test1 %>%
  filter (learn_phase == "transfer 1") %>%
    select(-c(game.f,block,avg_score,learn_phase))

head(dat_trans1)
# Data of transfer as difference between RPS_H2 and FWG_H1 is normally distributed
shapiro.test(dat_trans1$diff_score)

# Regression transfer score on condition and confidence
summary(lm(diff_score~ confidence + difficulty + factor(condition)+confidence*factor(condition), data = dat_trans1))

# tets hypothesis diff_score = 0 (transfer) against alternative it is negative -> No transfer
t.test( dat_trans1$diff_score, mu = 0 ,alternative = "less")

# To be sure.... Compare means of two condition 
t.test(dat_trans1$diff_score ~ condition, data = dat_trans1,exact = FALSE)

#DOING THE SAME FOR TRANSFER 2 :

dat_trans2 <- dat_test1 %>%
  filter (learn_phase == "transfer 2") %>%
    select(-c(game.f,block,avg_score,learn_phase))

# Regression transfer score on condition and confidence -> no effects 
summary(lm(diff_score~ confidence + difficulty + factor(condition) + confidence*factor(condition), data = dat_trans2))
```

```{r}
# Does confidence moderate transfer ?
# Looking at early rounds only as proxy for transfer 
dat_fwg <- dat2_6 %>%
  filter (game.f == "FWG")
dat_num <- dat2_6 %>%
  filter (game.f == "NUM")

# correlation confidence and transfer as proxied by score in early rounds : 
shapiro.test(dat_fwg$confidence)
cor.test(dat_fwg$confidence, dat_fwg$early_score, method="spearman")
cor.test(dat_num$confidence, dat_num$early_score, method="spearman")

# model explaining early scores in fwg by confidene and condition -> no effects 
summary(lm(early_score ~ confidence*condition, data=dat_fwg))
summary(lm(early_score ~ confidence*condition, data=dat_num))

```

```{r}
# checking whether theta changes between games

# lvl1 opponent 
bic <- read.csv("BIC_result.csv")
head(bic)

dat_lvl1 <- bic %>%
  select(c(id,condition,level2_3_theta1,level2_3_theta2,level2_3_theta3)) %>%
    gather(key = game, value = theta,-c(id,condition)) %>%
      group_by(id)
dat_lvl1$games <- factor(dat_lvl1$game, labels=c("RPS","FWG","MOD"),levels=c("level2_3_theta1","level2_3_theta2","level2_3_theta3"))

library(afex)
aov2 <- aov_car( theta ~ games + Error(id/(games)), dat_lvl1)
summary(aov2)

table2 <- nice(aov2, es = attr(aov2$anova_table, "es"),
  observed = attr(aov2$anova_table, "observed"),
  correction = attr(aov2$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(aov2$anova_table,
  "p_adjust_method"), sig_symbols = attr(aov2$anova_table, "sig_symbols"))

kable(table2)

dat_lvl1 %>% 
  group_by(games) %>%
  summarise(theta.m = mean(theta),
            SD = sd(theta, na.rm =TRUE ))

#plot 
ggerrorplot(dat_lvl1, x = "games", y = "theta", group = 1, color="games", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","MOD"), ylab = "Theta", xlab = "Games")

# lvl2 opponent 
dat_lvl2 <- bic %>%
  select(c(id,condition,level3_3_theta1,level3_3_theta2,level3_3_theta3)) %>%
    gather(key = game, value = theta,-c(id,condition)) %>%
      group_by(id)
dat_lvl2$games <- factor(dat_lvl2$game, labels=c("RPS","FWG","MOD"),levels=c("level3_3_theta1","level3_3_theta2","level3_3_theta3"))

# anova
aov3 <- aov_car( theta ~ games + Error(id/(games)), dat_lvl2)
summary(aov3)

table3 <- nice(aov3, es = attr(aov3$anova_table, "es"),
  observed = attr(aov3$anova_table, "observed"),
  correction = attr(aov3$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(aov3$anova_table,
  "p_adjust_method"), sig_symbols = attr(aov3$anova_table, "sig_symbols"))

kable(table3)

# mean comparison
dat_lvl2 %>% 
  group_by(games) %>%
  summarise(theta.m = mean(theta),
            SD = sd(theta, na.rm =TRUE ))

require(gridExtra)
#plot lvl1 
plot1 <- ggerrorplot(dat_lvl1, x = "games", y = "theta", group = 1, color="games", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","MOD"), ylab = "Theta", xlab = "Games")
#plot lvl2
plot2 <- ggerrorplot(dat_lvl2, x = "games", y = "theta", group = 1, color="games", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","MOD"), ylab = "Theta", xlab = "Games")

grid.arrange(plot1, plot2, ncol=2)

```

<!--chapter:end:exp1_clean_analysis.Rmd-->

---
title: "Hidden Markov strategy model"
author: "Maarten Speekenbrink"
date: "25/08/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(depmixS4)
```

```{r define-dummy-response}
setClass("dummyResponse", contains="response")

setGeneric("dummyResponse", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("dummyResponse"))

setMethod("dummyResponse", 
    signature(y="ANY"), 
    function(y,pstart=NULL,fixed=NULL, ...) {
      y <- matrix(y,length(y))
  		x <- matrix(1)
  		parameters <- list()
  		npar <- 0
      mod <- new("dummyResponse",parameters=parameters,fixed=logical(0),x=x,y=y,npar=npar)
      mod
	}
)

setMethod("show","dummyResponse",
    function(object) {
        cat("Dummy for fixed likelihood Model \n")
    }
)

setMethod("dens","dummyResponse",
  function(object,log=FALSE) {
   if(log) log(as.numeric(object@y)) else as.numeric(object@y)
  }
)

setMethod("getpars","dummyResponse",
    function(object,which="pars",...) {
        switch(which,
            "pars" = {
                pars <- numeric(0)
            },
            "fixed" = {
                pars <- logical(0)
            }
        )
        return(pars)
    }
)

setMethod("setpars","dummyResponse",
    function(object, values, which="pars", ...) {
        npar <- npar(object)
        if(length(values)!=npar) stop("length of 'values' must be",npar)
        # determine whether parameters or fixed constraints are being set
		nms <- ""
		switch(which,
		  "pars"= {
		      },
		  "fixed" = {
		    }
		  )
      names(object@parameters) <- nms
      return(object)
    }
)

setMethod("fit","dummyResponse",
    function(object,w) {
		  return(object)
	}
)

setMethod("predict","dummyResponse", 
    function(object) {
        ret <- object@y
        return(ret)
    }
)
```

```{r}
# we need to have "dat" available and lik_by_trial
QLS_lik <- lik_by_trial$QLS_lik
QLS_lik[which(QLS_lik == 0)] <- .001
QLS_lik[is.na(QLS_lik)] <- .33 # this is a hack; there shouldn't be any missing values
Bayes_NT_lik <- lik_by_trial$Bayes_NT_lik
Bayes_Tr_lik <- lik_by_trial$Bayes_Tr_lik

nsubject <- length(unique(dat$human_id)) # number of participants
ngame <- 3 # number of games
ntrial <- c(50,50,50) # numer of trials in each game

rModels <- list(
  list(
	  dummyResponse(QLS_lik)
	),
	list(
		dummyResponse(Bayes_NT_lik)
	),
  list(
    dummyResponse(Bayes_Tr_lik)
  )
)

trstart <- matrix(c(0.8,0.1,0.1,0.1,0.8,0.1,.1,.1,.8),ncol=3)
transition <- list()
transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))

instart <- c(1/3,1/3,1/3)
inMod <- transInit(~1,nstates=3,pstart=instart,family=multinomial("identity"),data=data.frame(rep(1,nsubject*ngame)))

mod <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))

fmod <- fit(mod, emcontrol=em.control(random.start=FALSE))

# No switching. Force off diagonal initial elements of transtion matrix to 0
trstart <- matrix(c(1,0,0,0,1,0,0,0,1),ncol=3)
transition <- list()
transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))

mod_noswitch <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))

fmod_noswitch <- fit(mod_noswitch, emcontrol=em.control(random.start=FALSE))

# p-value for comparison between a model with strategy switches and one without:

1-pchisq(-2*as.numeric(logLik(fmod_noswitch)) - (-2*as.numeric(logLik(fmod))),df=6)

```

<!--chapter:end:exp1_hmm_strategies.Rmd-->

---
title: "exp1_lik_by_trial"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
```

```{r}
# Get Data for experiment 1, remove unecessary columns

dat <- read.csv("data20180719.csv")
#####
# dat <- subset(dat, human_id == "38VxtUSv_h6RR5-tAAA2")
####

optim_results <- read.csv("exp1_all_results.csv")

```

```{r}

#preparing data for functions to claculate likelihood

#Prepping data for Bayesian code
dat <- as_tibble(dat) %>% group_by(human_id,game)
dat <- dat %>%
  mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1))

## level 0 predictions
dat <- dat %>% mutate(pred_a1_level0 = case_when(
  game == "rps" & ai_action_prev == "rock" ~ 1,
  game == "fwg" & ai_action_prev == "fire" ~ 1,
  game == "numbers" & ai_action_prev == "one" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level0 = case_when(
  game == "rps" & ai_action_prev == "paper" ~ 1,
  game == "fwg" & ai_action_prev == "water" ~ 1,
  game == "numbers" & ai_action_prev == "two" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level0 = case_when(
  game == "rps" & ai_action_prev == "scissors" ~ 1,
  game == "fwg" & ai_action_prev == "grass" ~ 1,
  game == "numbers" & ai_action_prev == "three" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a4_level0 = case_when(
  game == "numbers" & ai_action_prev == "four" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))
dat <- dat %>% mutate(pred_a5_level0 = case_when(
  game == "numbers" & ai_action_prev == "five" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))

## level 1 predictions
dat <- dat %>% mutate(pred_a1_level1 = case_when(
  game == "rps" & human_action_prev == "scissors" ~ 1,
  game == "fwg" & human_action_prev == "grass" ~ 1,
  game == "numbers" & human_action_prev == "five" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level1 = case_when(
  game == "rps" & human_action_prev == "rock" ~ 1,
  game == "fwg" & human_action_prev == "fire" ~ 1,
  game == "numbers" & human_action_prev == "one" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level1 = case_when(
  game == "rps" & human_action_prev == "paper" ~ 1,
  game == "fwg" & human_action_prev == "water" ~ 1,
  game == "numbers" & ai_action_prev == "two" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a4_level1 = case_when(
  game == "numbers" & ai_action_prev == "three" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))
dat <- dat %>% mutate(pred_a5_level1 = case_when(
  game == "numbers" & ai_action_prev == "four" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))

## level 2 predictions
dat <- dat %>% mutate(pred_a1_level2 = case_when(
  game == "rps" & ai_action_prev == "paper" ~ 1,
  game == "fwg" & ai_action_prev == "water" ~ 1,
  game == "numbers" & ai_action_prev == "four" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a2_level2 = case_when(
  game == "rps" & ai_action_prev == "scissors" ~ 1,
  game == "fwg" & ai_action_prev == "grass" ~ 1,
  game == "numbers" & ai_action_prev == "five" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a3_level2 = case_when(
  game == "rps" & ai_action_prev == "rock" ~ 1,
  game == "fwg" & ai_action_prev == "fire" ~ 1,
  game == "numbers" & ai_action_prev == "one" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  is.na(ai_action_prev) ~ 1/3,
  !is.na(ai_action_prev) ~ 0))
dat <- dat %>% mutate(pred_a4_level2 = case_when(
  game == "numbers" & ai_action_prev == "two" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))
dat <- dat %>% mutate(pred_a5_level2 = case_when(
  game == "numbers" & ai_action_prev == "three" ~ 1,
  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
  TRUE ~ 0))

dat$ai_action_num <- recode(dat$ai_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "one" = 1, "two" = 2, "three" = 3, "four" = 4 , "five" = 5)
dat$human_action_num <- recode(dat$human_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "one" = 1, "two" = 2, "three" = 3, "four" = 4 , "five" = 5)

# transform 'winner' variable in numeric score
dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat$block <- as.numeric(cut(dat$round,2))

# recode actions to make them equal to the codes in these files
dat$h_action <- recode(dat$human_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
dat$a_action <- recode(dat$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")

```

```{r}
dat <-as.data.frame(dat)
exp1_lik_by_trial <- data.frame()

# dat%>% group_by(human_id) %>%
#   mutate(pars_QLS = as.vector(optim_results%>% dplyr::select(QL_states_Beta,QL_states_alpha))) %>%
#   mutate(QLS_lik = Q_learn_states(pars_QLS[1,] ,tdat,"likelihood_by_trial",gamma = 0))

for(id in unique(dat$human_id)) {

  tdat <- dat %>% subset(human_id == id)

  # QLS likelihoods 
  pars_QLS <- as.vector(filter(optim_results, ID == id)%>% dplyr::select(QL_states_Beta,QL_states_alpha))
  tdat$QLS_lik <- Q_learn_states(pars_QLS ,tdat,"likelihood_by_trial",gamma = 0)

  #Bayes model no transfer likelihoods
  theta_NT <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_no_transfer))
  tdat$Bayes_NT_lik <- exp1_Bayes_model_LL(theta_NT ,data = tdat, generalize = "no", "likelihood_by_trial")

  # Bayes model with Transfer likelihood
  theta_Tr <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_transfer))
  tdat$Bayes_Tr_lik <- exp1_Bayes_model_LL(theta_Tr ,data = tdat, generalize = "game", "likelihood_by_trial")

  exp1_lik_by_trial <- dplyr::bind_rows(exp1_lik_by_trial,tdat)

  # 
  # exp1_lik_by_trial <- rbind(exp1_lik_by_trial,
  #                       data.frame(
  #                         "human_id" = id,
  #                         "condition" = dat$condition,
  #                         "game" = dat$game,
  #                         "round" = dat$round,
  #                         "QLS_lik" = QLS_lik,
  #                         "Bayes_NT_lik" = Bayes_NT_lik,
  #                         "Bayes_Tr_lik" = Bayes_Tr_lik
  #                       ))
  #cat(as.character(Bayes_Tr_lik[c(1,51,101)]))
}

write.csv(exp1_lik_by_trial,file="exp1_lik_by_trial.csv",row.names = FALSE)

```

```{r}

summary(exp1_lik_by_trial$QLS_lik == 1.0 )
summary(exp1_lik_by_trial$QLS_lik == 0.0 )
summary(is.na(exp1_lik_by_trial$QLS_lik))

```

```{r}

mean_lik <- exp1_lik_by_trial %>%
  select(human_id,condition,game, round,QLS_lik,Bayes_NT_lik,Bayes_Tr_lik) %>%
  group_by(game, condition, round)  %>%
  dplyr::summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))

data_long <- tidyr::gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)

# make sure the different games are ordered in the way they were played
data_long$game <- factor(data_long$game,levels=c("rps","fwg","numbers"))
ggplot(data_long,aes(x=round,y=probability,colour=strategy)) + geom_line() + facet_grid(game~condition)

```

<!--chapter:end:exp1_lik_by_trial.Rmd-->

---
title: "Simulation_EWA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### Parameter and model recovery Q-Learning with past round as state

## Build function that will simulate a QL_states player given parameters alpha and beta, and generate actions for 50 rounds
## of each game. 
```{r}
gen_data_QL_states <- function(beta, alpha, num_rounds, gamma) {

  games <- c("rps","fwg","numbers")
  condition <- sample(c("level1","level2"),1)
  data <- data.frame()

  #Define matrix of state spaces for each game 
  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
  states_RPS <- paste0(G1$Var1,G1$Var2)

  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
  states_FWG <- paste0(G2$Var1,G2$Var2)

  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
  states_NUM <- paste0(G3$Var1,G3$Var2)

  # Initialize Matrix of Q-values 
  Q_vals_RPS = matrix(-0.5,9,3)
  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))

  Q_vals_FWG = matrix(-0.5,9,3)
  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))

  Q_vals_NUM = matrix(-0.5,25,5)
  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))

  # Build tables that give reward for human player(Row) vs ai player(column) actions. 
  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))

  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))

   for (t_game in games){
      # Initiate dataframe
      game_data <- setNames(data.frame(matrix(ncol = 6, nrow = num_rounds)), c("condition","game", "round", "h_action","a_action","score"))

      # Initialize attraction vector, rewards + randomly select first actions
      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
      game_actions <- switch(as.character(t_game),rps=c("R", "P", "S"),fwg = c("F", "W", "G"), numbers = c("1", "2", "3", "4", "5"))
      reward <- switch(as.character(t_game), rps=reward_RPS, fwg=reward_FWG, numbers=reward_NUM)
      pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)

      for(t in 1:num_rounds) {
        if(t_game == "numbers") nopts <- 5 else nopts <- 3
        game_data[t,"game"]<- t_game
        game_data[t,"round"] <- t
        game_data[t,"condition"] <- condition

        if(t == 1) {
          # Initialize previous state randomly. 
          prev_state  <- sample(state_vec, size = 1)
          # Sample huamn and ai actions in first round randomly 
          h_act <- as.character(sample(game_actions, 1 ))
          ai_act  <- as.character(sample(game_actions, 1 ))
          # Get reward from first round. 
          R <- reward[h_act, ai_act]

          #Fill in table 
          game_data[t,"h_action"] <- h_act
          game_data[t,"a_action"] <- ai_act 
          game_data[t,"score"] <- R

        } else {
          h_act<- as.character(game_data[t-1,"h_action"])
          ai_act <- as.character(game_data[t-1,"a_action"])
          R <- as.numeric(game_data[t-1,"score"])

        }

        # cat("round", t, "\n")
        # cat(prev_state, " This is the previous state", "\n")
        # cat("observed human action",h_act, "\n")
        # cat("observed ai action",ai_act, "\n")

        ###### New state is the state we get to after human plays h_act and ai plays  ai_act 
        new_state <- paste0(h_act,ai_act)
        ######
        # cat(new_state,"This is new state","\n")
        # cat("this is alpha",alpha,"\n")

        # Q_learning: update rule
        # cat("this is the Q vals",Q_vals[prev_state, h_act],"\n")
        # cat("max Q_vals",max(Q_vals[new_state,]),"\n")
        # cat("This is the reward", R ,"\n")

        Q_vals[prev_state, h_act] <- Q_vals[prev_state, h_act] + alpha*( R + gamma*max(Q_vals[new_state,]) - Q_vals[prev_state, h_act])
        probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))

        # Select human action with softmax
        game_data[t,"h_action"] <- sample(game_actions, size=1,prob=probs)

        # Update state
        prev_state <- new_state

         # Simulate opponent action and get score 
        game_data[t,"a_action"] <- as.character(filter(pred_file_opp,human_previous == h_act & computer_previous == ai_act)[condition][1,])
        # Calculate score 
        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]

      }# End for loop over rounds
      data <- rbind(data,game_data)
  }
  # end of game for loop
  return(data)

}

# QL_dta <- gen_data_QL_states(5,0.5, num_rounds = 5, gamma = 0.9)

```

# Function to fit various models to simulated QL learner data and get table of results.
```{r}

fit_models <- function(tdat,num_rounds =50) {

  optim_S_EWA  <- DEoptim(fn=EWA_self, lower = 0.0, upper = 10.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))

  optim_EWA    <- DEoptim(fn=EWA_par,lower = c(0,0,0,0), upper = c(20,1,1,20), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))

  #optim_QL     <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")

  optim_QL_states <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))

  optim_NB     <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")

  dataframe <-  data.frame(

  # Get condition
   "condition"  = as.character(tdat$condition[1]),

  # Get best fit parameters and -2 Log Likelihoods for all models

  # Self-tuning EWA 
   "S_EWA_infrd_lambda" = optim_S_EWA$optim$bestmem[1],
   "S_EWA_2LL"          = optim_S_EWA$optim$bestval,

  #Parametric EWA
    "EWA_infrd_phi"    = optim_EWA$optim$bestmem[1],
    "EWA_infrd_delta"  = optim_EWA$optim$bestmem[2],
    "EWA_infrd_rho"    = optim_EWA$optim$bestmem[3],
    "EWA_infrd_lambda" = optim_EWA$optim$bestmem[4],
    "EWA_2LL"          = optim_EWA$optim$bestval,

  # Q-Learning with state as prev round
    "QL_states_infrd_beta"   = optim_QL_states$optim$bestmem[1],
    "QL_states_infrd_alpha"  = optim_QL_states$optim$bestmem[2],
    "QL_states_2LL"          = optim_QL_states$optim$bestval,

  # Naive Bayes (nopts-arm bandit with prior vec transfered across games)
    "NB_infrd_theta" = optim_NB$par[1],
    "NB_infrd_eps"   = optim_NB$par[2],
    "NB_2LL"         = optim_NB$value,

  # Random
   "Random_2LL"     = -2*(2*num_rounds*log(1/3) + num_rounds*log(1/5))

  )

  return(dataframe)

}

sim_results <- function(beta,alpha,num_rounds,gamma) {
  #Generate simulated data using Q_learning with previous round as state
  tdat = gen_data_QL_states(beta,alpha, num_rounds, gamma)
  # Fit various models to generated data 
  df <- fit_models(tdat)
  df$alpha <- alpha
  df$beta <- beta
  return(df)
}

```

## Run simulation to generate datasets and return results of model fits 
```{r}

betas = runif(100,0,10)
alphas = runif(100,0,1)

pars <- as.array(mapply(c,betas, alphas, SIMPLIFY = FALSE ))

list_of_dataframes <- mapply(FUN = sim_results, betas, alphas,num_rounds = 50.0, gamma = 0.0, SIMPLIFY = FALSE)

QL_states_mod_recovery <- bind_rows(list_of_dataframes, .id = "column_label")

save(QL_states_mod_recovery,file="QL_states_mod_recovery.RData")

```

## Plot infered vs real params, summarise model fitting results and return table of best fitting models
```{r}
# PLot real vs infered QL_states parameters
plot(QL_states_mod_recovery$alpha,QL_states_mod_recovery$QL_states_infrd_alpha, xlab = "True alpha", ylab = " Infered alpha")
plot(QL_states_mod_recovery$beta,QL_states_mod_recovery$QL_states_infrd_beta, xlab = "True beta", ylab = " Infered beta")

# Evaluate the correlation between real and infered alphas/lambdas and test it for significance
cor.test(QL_states_mod_recovery$alpha,QL_states_mod_recovery$QL_states_infrd_alpha, method= "spearman")
cor.test(QL_states_mod_recovery$beta,QL_states_mod_recovery$QL_states_infrd_beta, method= "spearman")

# Model recovery: create a table with best fitting models by condition
QL_states_model_recov <- table(QL_states_mod_recovery[, "condition"],c("random","N_Bayes","QL_states","EWA","S_EWA")[apply(QL_states_mod_recovery[,c("Random_2LL","NB_2LL","QL_states_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])

 write.csv(QL_states_model_recov,file="QL_states_model_recov.csv",row.names = TRUE)
 kable(QL_states_model_recov)

```

## What if we increase num rounds to 200, does that improve model recovery? 
```{r}
betas = runif(100,0,10)
alphas = runif(100,0,1)

pars <- as.array(mapply(c,betas, alphas, SIMPLIFY = FALSE ))

list_of_dataframes200 <- mapply(FUN = sim_results, betas, alphas,num_rounds = 200.0, gamma = 0.0, SIMPLIFY = FALSE)

QL_states_recov_200 <- bind_rows(list_of_dataframes200, .id = "column_label")

save(QL_states_recov_200,file="QL_states_recov_200.RData")

# PLot real vs infered QL_states parameters
plot(QL_states_recov_200$alpha,QL_states_recov_200$QL_states_infrd_alpha, xlab = "True alpha", ylab = " Infered alpha")
plot(QL_states_recov_200$beta,QL_states_recov_200$QL_states_infrd_beta, xlab = "True beta", ylab = " Infered beta")

# Evaluate the correlation between real and infered alphas/lambdas and test it for significance
cor.test(QL_states_recov_200$alpha,QL_states_recov_200$QL_states_infrd_alpha, method= "spearman")
cor.test(QL_states_recov_200$beta,QL_states_recov_200$QL_states_infrd_beta, method= "spearman")

# Model recovery: create a table with best fitting models by condition
QL_recov200_tab <- table(QL_states_recov_200[, "condition"],c("random","N_Bayes","QL_states","EWA","S_EWA")[apply(QL_states_recov_200[,c("Random_2LL","NB_2LL","QL_states_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])

 write.csv(QL_recov200_tab,file="QL_recov200_tab",row.names = TRUE)
 kable(QL_recov200_tab)
```

### Model and parameter recovery for Self Tuning EWA model

## Build function that will simulate a self tuning EWA player given parameter Lambda, and generate actions for 50 rounds
# of each game. 
```{r}

# NOTE : haven't introduced noise in either human or computer actions.

gen_data_SEWA <- function(par,num_rounds){

  lambda <- par[1]
  games <- c("rps","fwg","numbers")
  condition <- sample(c("level1","level2"),1)
  data <- data.frame()

  # Define attraction vectors for each game 
  A_RPS = matrix(0.0,3)
  names(A_RPS) <- c("R","P","S")
  A_FWG = matrix(0.0,3)
  names(A_FWG) <- c("F","W","G")
  A_NUM = matrix(0.0,5)
  names(A_NUM) <- c("1","2","3","4","5")

  # # Define reward matrices from the prospective of the row player (human in our case)
  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))

  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))

  for (t_game in games){
      # Initiate dataframe
      game_data <- setNames(data.frame(matrix(ncol = 6, nrow = num_rounds)), c("condition","game", "round", "h_action","a_action","score"))
      # Initialize attraction vector, rewards + randomly select first actions
      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
      game_actions <- names(Att)
      reward <- switch(as.character(t_game), rps=reward_RPS, fwg=reward_FWG, numbers=reward_NUM)
      pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)

    for(t in 1:num_rounds) {
      if(t_game == "numbers") nopts <- 5 else nopts <- 3
      game_data[t,"game"]<- t_game
      game_data[t,"round"] <- t
      game_data[t,"condition"] <- condition

      if(t == 1) {

        game_data[t,"h_action"] <- as.character(sample(game_actions, 1 ))
        game_data[t,"a_action"] <- as.character(sample(game_actions, 1 ))
        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]
        lik_hum <- c(1/nopts)
        N <- 1.0
        R_t <- rep(0.0,nopts)
        H_t <- R_t

      } else {

        # Get reward and past human action
        h_act_prev <- as.character(game_data[t-1,"h_action"])
        a_act_prev <- as.character(game_data[t-1,"a_action"])

        # Estimate phi(t)
        R_t <- as.numeric(game_actions == a_act_prev)
        # cat("This is R(t)",R_t,"\n")

        H_t <- (H_t*(t-2) + R_t)/(t-1)
        # cat("this is H(t)",H_t,"\n")

        Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
        # cat("This is Phit(t)",Phi_t,"\t")

        # Estimate vector Delta(t)
        delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[t-1,"score"]))
        #cat("this is delta(t)",delta_t,"\n")

        for (i in 1:length(Att)) {
          action <- as.character(game_actions[i])
          # Attraction vector update rule 
          Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
        }
        #Update the value of N 
        N <- Phi_t*N + 1
        #cat(Att,'\n')

        # Assume human chooses action probabilistically using softmax on Attraction values
        probs <- exp(lambda*Att)/sum(exp(lambda*Att))

        # Get actual human action and compute likelihood
        game_data[t,"h_action"] <- sample(game_actions, size=1,prob=probs)
        act_index <- match(game_data[t,"h_action"], game_actions)
        lik_hum[t] <- probs[[act_index]]

        # Simulate opponent action and get score 
        game_data[t,"a_action"] <- as.character(filter(pred_file_opp,human_previous == as.character(game_data[t-1,"h_action"]) & computer_previous == as.character(game_data[t-1,"a_action"]))[condition][1,])
        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]

      }

    }# End for loop over rounds
    data <- rbind(data,game_data)

  }# end of game for loop
  return(data)

}

```

## Generate 100 datasets using S_EWA agent, one for each lambda and fit the 4 models to it : NB, QL, EWA and S_EWA 
```{r}
## Generate N lambdas in chosen interval, get the corresponding datasets of actions and scores, use Self_EWA to infer Lambda from these datasets. 
EWA_self_simulation <- data.frame()
lambdas = runif(100, 0, 10)
num_rounds <- 50 
count <- 1

for(lambda in lambdas) {

  EWA_self_simulation[count,"real_lambda"] <- lambda
  tdat <- gen_data_SEWA(par = lambda, num_rounds)

  # Fit various models to generated data (from S_EWA type player)
  optim_S_EWA  <- DEoptim(fn = EWA_self, lower = 0.0, upper = 10.0, data= tdat, "-2loglik", control = list(trace = FALSE,parallelType =1))

  optim_EWA    <- DEoptim(fn = EWA_par,lower = c(0,0,0,0), upper = c(20,1,1,20), data=tdat,"-2loglik",control= list(trace = FALSE,parallelType=1))

  # optim_QL     <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")

  optim_QL_states <- DEoptim(fn = Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))

  optim_NB     <- optim(c(0.1,0.1),fn=naive_bayes, gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")

  # Get condition
  EWA_self_simulation[count, "condition"]  <- as.character(tdat$condition[1])

  # Get best fit parameters and -2 Log Likelihoods for all models

  # Self-tuning EWA 
  EWA_self_simulation[count, "S_EWA_infrd_lambda"] <- optim_S_EWA$optim$bestmem[1]
  EWA_self_simulation[count, "S_EWA_2LL"]          <- optim_S_EWA$optim$bestval

  #Parametric EWA
  EWA_self_simulation[count, "EWA_infrd_phi"]    <- optim_EWA$optim$bestmem[1]
  EWA_self_simulation[count, "EWA_infrd_delta"]  <- optim_EWA$optim$bestmem[2]
  EWA_self_simulation[count, "EWA_infrd_rho"]    <- optim_EWA$optim$bestmem[3]
  EWA_self_simulation[count, "EWA_infrd_lambda"] <- optim_EWA$optim$bestmem[4]
  EWA_self_simulation[count, "EWA_2LL"]          <- optim_EWA$optim$bestval

  # Q-Learning with previous round as state
  EWA_self_simulation[count, "QL_infrd_beta"]   <- optim_QL_states$optim$bestmem[1]
  EWA_self_simulation[count, "QL_infrd_alpha"]  <- optim_QL_states$optim$bestmem[2]
  EWA_self_simulation[count, "QL_2LL"]          <- optim_QL_states$optim$bestval

  # Naive Bayes (nopts-arm bandit with prior vec transfered across games)
  EWA_self_simulation[count, "NB_infrd_theta"] <- optim_NB$par[1]
  EWA_self_simulation[count, "NB_infrd_eps"]   <- optim_NB$par[2]
  EWA_self_simulation[count, "NB_2LL"]         <- optim_NB$value

  # Random
  EWA_self_simulation[count, "Random_2LL"]     <- -2*(2*num_rounds*log(1/3) + num_rounds*log(1/5))

  count <- count + 1
}

save(EWA_self_simulation,file="SEWA_simulation.RData")

```

## Plotting parameter recovery scatter plots and model recovery results
```{r}

plot(EWA_self_simulation$real_lambda,EWA_self_simulation$S_EWA_infrd_lambda)
# We can evaluate the correlation between real and infered lambdas and test it for significance
cor.test(EWA_self_simulation$real_lambda, EWA_self_simulation$S_EWA_infrd_lambda, method=c("spearman"))

# Model recovery: create a table with best fitting models by condition
SEWA_recov_results <- table(EWA_self_simulation[, "condition"],c("random","N_Bayes","QL","EWA","S_EWA")[apply(EWA_self_simulation[,c("Random_2LL","NB_2LL","QL_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])

 write.csv(SEWA_recov_results,file="SEWA_recov_results.csv",row.names = TRUE)
 kable(SEWA_recov_results)
```

```{r}

```

<!--chapter:end:param_model_recovery.Rmd-->

---
title: "Score_plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggpubr)

```

```{r}

exp1_dat = read.csv("exp1_data.csv")
exp1_model_comp = read.csv("exp1_model_comp.csv")

datalist = list()
i = 0
new_dat <- setNames(data.frame(matrix(ncol = ncol(exp1_dat), nrow = 0)), colnames(exp1_dat))
for(id in unique(exp1_dat$human_id)) {
  i <- i+1
  tdat <- subset(exp1_dat,human_id == id)
  tdat$part_num <- i
  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
  datalist[[i]] <- tdat
}

# Merge all datasets into one 
new_dat <- dplyr::bind_rows(datalist)
# or new_dat <- data.table::rbindlist(datalist)

# Add column for time t
new_dat <- new_dat %>% group_by(exp1_dat$human_id) %>% mutate(t = row_number())

# Participant number as a factor 
# tdat$part_num <- as.factor(tdat$part_num)

# Add best fitting model per participant
new_dat <- merge(new_dat, exp1_model_comp[, c("human_id", "Best_model")], by="human_id")
```

```{r}
ggplot(data = new_dat, aes(x = t, y=acc_sum, group = part_num)) + 
  geom_line(aes(color= Best_model))
```

```{r}
temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
dat_by_model <- temp %>% group_by(Best_model,t) %>% 
  summarize(model_acc_sum = mean(acc_sum))

ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
   geom_line(aes(color= Best_model))
```

<!--chapter:end:score_plots.Rmd-->

### 2021-06-04 comp_model_1019.Rmd
added report in papaja and softmax to BCH models

@@
 save(QL_modelling,file="QL_modelling.RData")
-
-```
-
-## First attempt : Q-Learning with state space consisting of last round play (deprecated) 
-```{r}
-
-# Q_learn_states <- function(par,data,return_value,gamma){
-#   # Par[1] -> beta= inverse temperature parameter in softmax choice function
-#   # Par[2] -> lambda = learning rate (one per game?)
-#   # data : participant and ai choice data.
-#   # return_value=c("-2loglik","likelihood_by_trial")
-#   # Gamma is discount factor for future rewards 
-#   # Returns Q-values per trial and predicts choice using softmax
-#   beta <- par[1]
-#   alpha <- par[2]
-# 
-#   #gamma <- 0.9 
-# 
-#   #Define matrix of state spaces for each game 
-#   G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
-#   states_RPS <- paste0(G1$Var1,G1$Var2)
-# 
-#   G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
-#   states_FWG <- paste0(G2$Var1,G2$Var2)
-# 
-#   G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-#   states_NUM <- paste0(G3$Var1,G3$Var2)
-#   
-#   Q_vals_RPS = matrix(-0.5,9,3)
-#   dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
-# 
-#   Q_vals_FWG = matrix(-0.5,9,3)
-#   dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
-#   
-#   Q_vals_NUM = matrix(-0.5,25,5)
-#   dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
-#  
-#   lik_hum <- matrix(0.0,nrow(data))
-# 
-#   for(t in 1:nrow(data)) {
-#     t_game <- data[t,"game"]
-#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
-#     
-#     if(data[t,"round"] == 1) {
-#       # first round is uniform prediction
-#       Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
-#       state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
-#       lik_hum[t] <- 1/nopts
-#       # Randomly select prev_state and actions for first round
-#       curr_state <- sample(state_vec, size = 1)
-#       h_act <- sample(colnames(Q_vals), size =1)
-#       ai_act <- sample(colnames(Q_vals), size =1)
-#       reward <- 0 
-#       
-#     } else {
-#       # Get past human action and associated reward 
-#       h_act <- as.character(data[t-1,"h_action"])
-#       ai_act <- as.character(data[t-1,"a_action"])
-#       reward <- as.numeric(data[t-1,"score"])
-#     }
-#     
-#     
-#     # cat(curr_state, " This is the previous state", "\n")
-#     new_state <- paste0(h_act,ai_act)
-#     # cat(new_state,"This is new state","\n")
-#     
-#     # Q_learning: update rule (time  = t-1)
-#     Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
-#     
-#     # Assume human chooses action probabilistically using softmax on Q values
-#     probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
-#     #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }
-#     
-#     # Get actual human action and compute likelihood
-#     h_act <- as.character(data[t,"h_action"])
-#     act_index <- match(h_act, colnames(Q_vals))
-#     lik_hum[t] <- probs[[act_index]]
-#       
-#     # Update state
-#     curr_state <- new_state 
-#     #}
-#   }
-#   if(return_value == "-2loglik") {
-#     ret <- -2*sum(log(lik_hum))
-#     if(is.infinite(ret) || is.nan(ret)) {
-#       return(1e+300)
-#     } else {
-#       return(ret)
-#     }
-#   }
-#   if(return_value == "likelihood_by_trial") return(lik_hum)
-#   
-# }
 
@@
 
-##  First attempt : Self-Tuning EWA with prior round play as state (Camerer & Ho 2007) 
-```{r}
-# Initiates N(0) = 1 as in Camerer and Ho 1997 paper. 
-# 
-# EWA_states <- function(par,data,return_value){
-# 
-#   lambda <- par[1]
-# 
-#   #Define matrix of state spaces for each game 
-#   G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
-#   states_RPS <- paste0(G1$Var1,G1$Var2)
-# 
-#   G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
-#   states_FWG <- paste0(G2$Var1,G2$Var2)
-# 
-#   G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-#   states_NUM <- paste0(G3$Var1,G3$Var2)
-#   
-#   A_RPS = matrix(-0.5,9,3)
-#   dimnames(A_RPS) = list(states_RPS, c("R", "P", "S"))
-# 
-#   A_FWG = matrix(-0.5,9,3)
-#   dimnames(A_FWG) = list(states_FWG, c("F", "W", "G"))
-#   
-#   A_NUM = matrix(-0.5,25,5)
-#   dimnames(A_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
-# 
-#   
-#   # # Define reward matrices from the perspective of the row player (human in our case)
-#   reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-#   dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
-#   
-#   reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-#   dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
-#   
-#   reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
-#   dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-#   
-#   # Initiate likelihood by trial vector 
-#   lik_hum <- matrix(0.0,nrow(data))
-# 
-#   for(t in 1:nrow(data)) {
-#     t_game <- data[t,"game"]
-#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
-#     if(data[t,"round"] == 1) {
-#       Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
-#       state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, numbers = states_NUM)
-#       reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, numbers = reward_NUM)
-#       game_data <- subset(data, game == t_game)
-#       
-#       # first round is uniform prediction
-#       lik_hum[t] <- 1/nopts
-#       N <- 1.0
-# 
-#       R_t <- rep(0.0,nopts)
-#       H_t <- R_t
-#       
-#       # Randomly select prev_state and actions for first round
-#       curr_state <- sample(state_vec, size = 1)
-#       h_act_prev <- sample(colnames(Att), size =1)
-#       a_act_prev <- sample(colnames(Att), size =1)
-#       #reward <- 0 
-#       
-#     } else {
-#       
-#       indx <- data[t,"round"]
-#       state_indx <- match(curr_state,state_vec)
-#       #cat("this is the current state index", state_indx, "\n")
-#       
-#       # Get reward and past human action
-#       h_act_prev <- as.character(game_data[indx-1,"h_action"])
-#       a_act_prev <- as.character(game_data[indx-1,"a_action"])
-#       new_state <- paste0(h_act_prev,a_act_prev)
-# 
-#       # Estimate R(t) (recent history) then H(t) (history) then phi(t) (change detector)
-#       R_t <- as.numeric(colnames(Att) == a_act_prev)
-#       #cat("This is R(t)",R_t,"\n")
-#       
-#       H_t <- (H_t*(indx-2) + R_t)/(indx-1)
-#       #cat("this is H(t)",H_t,"\n")
-#       
-#       Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
-#       #cat("This is Phit(t)",Phi_t,"\t")
-#       
-#       # Estimate vector Delta(t)
-#       delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
-#       #cat("this is delta(t)",delta_t,"\n")
-#       
-#       for (i in 1:nopts) {
-#         action <- as.character(colnames(Att)[i])
-# 
-#         #cat("this is current indexed action",action,"\n")
-#         #cat("this is previous human action",h_act_prev,"\n")
-#         
-#         # Attraction vector update rule
-#         Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
-#       }
-#       
-#       #Update the value of N 
-#       N <- Phi_t*N + 1
-# 
-#       # Assume human chooses action probabilistically using softmax on Attraction values
-#       probs <- exp(lambda*Att[new_state,])/sum(exp(lambda*Att[new_state,]))
-#       
-#       # Get actual human action and compute likelihood
-#       h_act <- as.character(game_data[indx,"h_action"])
-#       act_index <- match(h_act, colnames(Att))
-#       lik_hum[t] <- probs[[act_index]]
-#       
-#       curr_state <- new_state
-#       
-#       # if (indx == 50) {
-#       #   cat("this is the attraction matrix at last round of", "\n")
-#       #   print(Att)
-#       # }
-#     }
-#   }
-#   
-#  if(return_value == "-2loglik") {
-#     ret <- -2*sum(log(lik_hum))
-#     if(is.infinite(ret) || is.nan(ret)) {
-#       return(1e+300)
-#     } else {
-#       return(ret)
-#     }
-#   }
-#   if(return_value == "likelihood_by_trial") return(lik_hum)
-# }
-
-```
-
 ### Second attempt at ST_EWA with states and no initial guess of initial states. 
@@
 ```{r}
-# load("QL_modelling.RData")
-# load("QL_states_modelling.RData")
-# load("EWA_modelling.RData")
-# load("EWA_self_modelling.RData")
-# load("MBM_modelling.RData")
-# load("ST_EWA_STATES_modelling.RData")
+load("QL_modelling.RData")
+load("QL_states_modelling.RData")
+load("EWA_modelling.RData")
+load("EWA_self_modelling.RData")
+load("MBM_modelling.RData")
+load("ST_EWA_STATES_modelling.RData")
 
@@
                          # Bayesian updating with/without transfer 
-                         "Bayes_Tr_BIC" = exp1_Bayes_game_Tr[[id]]$optim$bestval+ 1*log(150),
-                         "Bayes_No_Tr_BIC" = exp1_Bayes_no_Tr[[id]]$optim$bestval + 1*log(150),
+                         # "Bayes_Tr_BIC" = exp1_Bayes_game_Tr[[id]]$optim$bestval+ 1*log(150),
+                         # "Bayes_No_Tr_BIC" = exp1_Bayes_no_Tr[[id]]$optim$bestval + 1*log(150),
+                         # # Theta is the parameter governing AI stochasticity. Truth is 0.9
+                         # "theta_transfer" = exp1_Bayes_game_Tr[[id]]$optim$bestmem[[1]],
+                         # "theta_no_transfer" = exp1_Bayes_no_Tr[[id]]$optim$bestmem[[1]],
+                         #
+
+                         # BCH with/without transfer (With Softmax) 
+                         "Bayes_Tr_BIC" = use_softmax_tr[[id]]$optim$bestval+ 2*log(150),
+                         "Bayes_No_Tr_BIC" = use_softmax_NT[[id]]$optim$bestval+ 2*log(150),
+
                          # Theta is the parameter governing AI stochasticity. Truth is 0.9
-                         "theta_transfer" = exp1_Bayes_game_Tr[[id]]$optim$bestmem[[1]],
-                         "theta_no_transfer" = exp1_Bayes_no_Tr[[id]]$optim$bestmem[[1]],
+                         "theta_transfer" = use_softmax_tr[[id]]$optim$bestmem[[1]],
+                         "lambda_transfer" = use_softmax_tr[[id]]$optim$bestmem[[2]],
+
+                         "theta_no_transfer" = use_softmax_NT[[id]]$optim$bestmem[[1]],
+                         "lambda_no_transfer" = use_softmax_NT[[id]]$optim$bestmem[[2]],
 

### 2021-06-04 exp1_lik_by_trial.Rmd
added report in papaja and softmax to BCH models

@@
   #Bayes model no transfer likelihoods
-  theta_NT <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_no_transfer))
-  tdat$Bayes_NT_lik <- exp1_Bayes_model_LL(theta_NT ,data = tdat, generalize = "no", "likelihood_by_trial")
+  pars_BCH_NT <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_no_transfer,lambda_no_transfer))
+  tdat$Bayes_NT_lik <- exp1_Bayes_model_LL(pars_BCH_NT ,data = tdat, generalize = "no", softmax = TRUE, "likelihood_by_trial")
 
   # Bayes model with Transfer likelihood
-  theta_Tr <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_transfer))
-  tdat$Bayes_Tr_lik <- exp1_Bayes_model_LL(theta_Tr ,data = tdat, generalize = "game", "likelihood_by_trial")
+  pars_BCH_Tr <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_transfer,lambda_transfer))
+  tdat$Bayes_Tr_lik <- exp1_Bayes_model_LL(pars_BCH_Tr,data = tdat, generalize = "game", softmax = TRUE, "likelihood_by_trial")
 
@@
 mean_lik <- exp1_lik_by_trial %>%
-  select(human_id,condition,game, round,QLS_lik,Bayes_NT_lik,Bayes_Tr_lik) %>%
+  dplyr::select(human_id,condition,game, round,QLS_lik,Bayes_NT_lik,Bayes_Tr_lik) %>%
   group_by(game, condition, round)  %>%

### 2021-07-05 Report/paper_draft_2021.Rmd
went through draft

@@
   causal models of the environment. One way to build abstract representations of the environment when the task involves interactions with others is to build 
-  a model of the opponent that may inform what actions they are likely to take next. In this study, we propose to explore opponent modelling and its transfer with the use of
-  computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning. Through two differentiated experiments, we find that participants can
-  deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it. Moreover, we showed that participants transfer their learning to new games and that
-  the transfer is moderated by the level of  sophistication of the opponent. Computational modelling shows that it is likely that players start each game using a model-based
-  learning strategy that facilitates generalisation and opponent model transfer, but then switch to behaviour that is consistent with a  model-free learning strategy in the latter
-  stages of the interaction.
+  a model of the opponent that may inform what actions they are likely to take next. In this study, we explore opponent modelling and its transfer with the use of
+  computer agents with human-like limited degrees of iterated reasoning. In two experiments, we find that participants
+  deviate from Nash equilibrium play and learn to adapt to the opponent's strategy and exploit it. Moreover, we show that participants transfer their learning to new games and that
+  this transfer is moderated by the level of sophistication of the opponent. Computational modelling shows that players start each game with a model-based
+  learning strategy that facilitates between-game transfer of the opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
 
@@
 
-In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to this task.
-The early literature on learning transfer in repeated games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously [@ho1998iterated; @knez2000].
-This doesn't allow for the possibility of learning about the opponent's strategy and potentially exploiting it.
-
-When studies have specifically explored this aspect, they have used computer opponents that were generally programmed not to change their strategies over the course of the task, allowing better experimental control.
+A model of the opponent can help increase performance in a particular game, but learning more general characteristics of an opponent may also help increase performance in other games.
+In this paper, we are specifically interested in the latter: How do people build and use models of their opponent to facilitate learning transfer?
+<!-- when engaged in situations involving an interaction with strategic considerations.--> Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly useful to address this question.
+The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.
+Nash equilibrium play) or use salient actions (e.g.
+risk dominance) in later games, having had experience with a similar game environment previously [@ho1998iterated; @knez2000].
+As is well-known, a Nash equilibrium means that all players in a game play such that no-one can unilaterally improve their performance by deviating from their strategy.
+When playing against an opponent with a Nash-optimal strategy, I can do no better than play according to the Nash-equilibrium strategy as well.
+However, when faced with a player who deviates from the Nash-optimal strategy, it may be better for me to exploit this and also deviate from this strategy, increasing my performance beyond what is expected at a Nash equilibrium.
+Of course, this comes with some risk, as my own deviation from Nash-optimal play may leave myself open to similar exploitation.
+
+<!-- his doesn't allow for the possibility of learning about the opponent's strategy and potentially exploiting it. !-->
+
+Studies that focused on whether people can learn to exploit deviations from Nash-equilibrium play have mostly looked at the ability of players to detect and exploit action-based learning rules [@spiliopoulos2013strategic; @shachat2004we].
+These studies used computer opponents with fixed strategies (no adaptation to their human opponent) consisting of playing each action with a fixed probability (a mixed strategy).
+Findings showed ....
+However, the use of mixed strategies may have limited people's ability to form accurate opponent models.
+Rather than thinking of their opponents and drawing a random action from a (non-uniform) probability distribution, people may rather think of their opponents as applying a form of iterated reasoning to determine their next action.
+The type of reasoning we refer to takes the form of ``I believe that you believe that I believe ...'' and has been shown to correspond to people's casual introspection (REFERENCE).
+It also underlies successful models in behavioural economics, such as Level-$k$ and Cognitive Hierarchy models, which posit that people assume their opponent has a limited level of iterative reasoning, with the player best responding to their (modelled) opponent.
+
+In Level-$k$ theory, a level-0 player uses a fixed strategy without explicitly considering the strategy of their opponent.
+A level-1 player assumes their opponent is a level-0 player, and chooses actions to best respond to the strategy of their opponent, without considering what their opponent might believe that they will play.
+A level-2 player, on the other hand, takes their opponent's belief about their actions into account, assuming they face a level-1 player, and choosing actions to best respond to the actions of that player.
+Cognitive Hierarchy theory works on similar principles, but rather than assuming an opponent always adopts a particular level-$k$ strategy, they assume their opponent adopts each pf the level-$k$ strategies with a particular probability (i.e., the strategy is a mixture over pure level-$k$ strategies).
+
+Iterative reasoniing strategies can explain non-equilibrium play in a range of games, such as ...
+In the present study, we endow our computer opponents with limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
+In two experiments, participants face the same opponent (Experiment 1) or same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, a structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
+To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of the opponent and the similarity of the games.
+Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a morehabiltual and cognitively less demanding strategy in the later stages of the games.
+
+<!--
+with that were generally programmed not to change their strategies over the course of the task, allowing better experimental control.
 However, they have mostly looked at the ability of players to detect and exploit action-based learning rules [@spiliopoulos2013strategic; @shachat2004we].
@@
 
-\newpage
-
 # Experiment 1
+
+In the first experiment, we .... [intro to first exp]
 
@@
 The Fire-Water-Grass (FWG) game is identical to RPS in all but action labels: Fire burns grass, water extinguishes fire, and grass absorbs water.
-We use this game as we are interested in whether learning is transferred in a fundamentally similar game where the only difference is in the description of the possible actions.
-This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level 1 or 2 player.
-Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'', as might be learned by a simple reinforcement learning algorithm, will not be able to generalize to such a game, as these contingencies are tied to the labels of the actions.
-The numbers game is a generalization of RPS.
+We use this game as we are interested in whether learning is transferred in a fundamentally similar game where the only difference is in the name of the possible actions.
+This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level-1 or level-2 player.
+Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'', <!-- as might be learned by a simple reinforcement learning algorithm,--> is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
+The Numbers game is a generalization of RPS.
 In the variant we use, 2 participants concurrently pick a number between 1 and 5.
@@
 All other possible combinations of choices are considered ties.
-Similar to RPS and FWG, the mixed-strategy Nash equilibrium is to play each action with equal probability in a random way.
+Similar to RPS and FWG, the mixed-strategy Nash equilibrium is to randomly play each action with equal probability.
 
 The computer opponent was programmed to use either a level-1 or level-2 strategy in all the games.
-A level 1 player is defined as a player who best responds to a level 0 player.
-A level 0 player plays in a non-strategic way and does not consider their opponent's actions.
-Here, we assume a level 0 player simply repeats their previous action.
-There are other ways to define a level 0 player.
-For instance, as repeating their action if it resulted in a win, and choosing randomly from the remaining actions otherwise.
-As a best response to a random action is itself a random action, defining a level 0 player in such a way would make a level 1 opponent's strategy much harder to discern.
-Because we are mainly interested in generalization of knowledge of an opponent's strategy to other games, which rests on good knowledge of this strategy, we opted for this more deterministic formulation of a level 0 player (whilst also introducing some randomness in the computer opponent's play).
+A level-1 player is defined as a player who best responds to a level-0 player.
+A level-0 player plays in a non-strategic way and does not consider their opponent's actions.
+Here, we assume a level-0 player simply repeats their previous action.
+There are other ways to define a level-0 player.
+For instance, as repeating their action if it resulted in a win and choosing randomly from the remaining actions otherwise, or choosing randomly from all actions.
+As a best response to a uniformly random action is itself a random action, defining a level-0 player in such a way would make a level-1 opponent's strategy much harder to discern.
+Because we are mainly interested in generalization of knowledge of an opponent's strategy to other games, which rests on good knowledge of this strategy, we opted for this more deterministic formulation of a level-0 player (whilst also introducing some randomness in the computer opponent's play).
 A level-2 computer opponent, will assume in turn that the participant is a level-1 opponent, playing according to the strategy just described.
 We also introduced some noise over the actions of computer opponents making them play randomly in 10\% of all trials.
+Note that at all levels, the strategies are contingent on the actions taken in the previous round.
+The choice of this type of strategy is consistent with evidence that humans strategically use information from last round play of their opponents in zero sum games [@batzilis; @wang2014social].
 
@@
 \centering
-\begin{tabular}{||c c c c||} 
+\begin{tabular}{||c c | c c||} 
  \hline
- Human last & Agent last & level-1 Agent & level-2 Agent\\ [0.5ex] 
+ Human action $t-1$ & Computer action $t-1$  & Computer level-1 action $t$ & Computer level-2 action $t$ \\ [0.5ex] 
  \hline\hline
@@
 Participants were informed they would play three different games against the same computer opponent.
-Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
+Participants were told that the opponent cannot cheat and will choose its actions simultaneously with them, without prior knowledge of the participant's choice.
 After providing informed consent and reading the instructions, participants answered a number of comprehension questions.
-They then played the three games against their opponent in the order RPS, FGW, and NUMBERS.
+They then played the three games against their opponent in the order RPS, FGW, and Numbers.
+An example of the interface for the RPS game is provided in Figure\ \@ref(fig:feedback-rps-exp2).
+On each round, tHe human player chooses an action, and after a random delay, is shown the action chosen by the computer opponent, and the outcome of that round.
+A history of the chosen actions over all rounds is available in the centre panel.
 A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
@@
 Each point is worth £0.02.
-An example of the interface for the RPS game is provided in Figure\ \@ref(fig:feedback-rps-exp2).
-After playing all the games, participants were asked questions about their beliefs about the computer opponent, related to whether they think they have learned their strategy and how hard they found playing against that particular opponent.
+After playing all the games, participants were asked questions about their beliefs about the computer opponent, related to whether they thought they learned their opponent's strategy, and how difficult they found playing against their particular opponent.
 They were then debriefed and thanked for their participation.
@@
 
-```{r feedback-rps-exp2, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align='center'}
+```{r feedback-rps-exp2, fig.cap = "Screenshot of the Rock-Paper-Scissors game in Experiment 2.
+Shown here is the feedback stage, after both the human (left) and computer (right) players have chosen their action.
+The interface was similar in Experiment 1, but excluded the history of game play in the center panel.", fig.align='center'}
 
@@
 
-```{r exp1-avg-scores-game, fig.cap = "Boxplot of scores per game across conditions", fig.align="center"}
+```{r exp1-avg-scores-game, fig.cap = "Performance per game and block across conditions in Experiment 1.
+Points are scores of individual participants and boxes reflect the 95\\% confidence intervals of the mean (center line equals the mean).", fig.align="center", fig.width=8, fig.height = 4}
 # Plot average  scores per game
-ggboxplot(dat3, x = "game", y = "game_score",group = 1, add =c("mean_ci"), color="game", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("rps", "fwg","numbers"), ylab = "Score", xlab = "Game", legend.title = "Game") + geom_jitter( aes(color = game), width = 0.2, alpha = 0.3 )
-
-```
-On average, participants obtained the lowest score in the RPS game ($M = 0.289$, $SD = 0.348$), followed by NUMBERS ($M = 0.31$, $SD = 0.347$).
+
+dat2 %>%
+  mutate(game = factor(game)) %>%
+  mutate(game = forcats::fct_recode(game, RPS = "rps", FWG = "fwg", Numbers = "numbers")) %>%
+  mutate(game = factor(game, levels = c("RPS", "FWG", "Numbers"))) %>%
+  mutate(condition = factor(condition, levels = c("Level1", "Level2"))) %>%
+  mutate(condition = forcats::fct_recode(condition, "Level 1" = "Level1", "Level 2" = "Level2")) %>%
+  ggplot(aes(x = game, y = block_score, colour = block)) + stat_summary(fun.data = "mean_ci", position = position_dodge2(width=.8), geom = "crossbar")  + geom_point(position=position_jitterdodge(), alpha=.4) + ylab("Score") + xlab("Game") + facet_grid(.
+~ condition) + theme_apa() + geom_hline(yintercept = 0, lty=2)
+
+#+ geom_boxplot(alpha=.4) + geom_point(position=position_jitterdodge(), alpha=.4) + ylab("Score") + xlab("Game") + facet_grid(. ~ condition) + theme_apa() + geom_hline(yintercept = 0, lty=2)
+
+#geom_jitter(aes(colour=block, fill=block), width=.2) + facet_grid(. ~ condition)
+
+# ggboxplot(x = "game", y = "block_score", colour="block", fill="block", add =c("mean_ci"), palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUMBERS"), ylab = "Score", xlab = "Game", legend.title = "Block") + geom_jitter(aes(color = block, fill = block), width = 0.2, alpha = 0.3 ) + facet_grid(.
+~ condition)
+
+```
+On average, participants obtained the lowest score in the RPS game ($M = 0.289$, $SD = 0.348$), followed by Numbers ($M = 0.31$, $SD = 0.347$).
 Participants' performance was highest in the FWG game ($M = 0.454$, $SD = 0.354$).
-Scores in each game were significantly different from 0, the expected score of random play (RPS: $t(51) = 7.26$, $p < .001$;  FWG:  $t(51) = 10.04$ , $p < .001$; NUMBERS: $t(51) = 7.17$, $p < .001$).
-To assess learning within and between games, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants.
+Scores in each game were significantly different from 0, the expected score of uniformly random play (RPS: $t(51) = 7.26$, $p < .001$;  FWG:  $t(51) = 10.04$ , $p < .001$; Numbers: $t(51) = 7.17$, $p < .001$).
+As uniformly random play is the Nash equilibrium, this indicates successful deviation from a Nash-optimal strategy.
+
+To assess learning within and between games, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants.
 This showed a main effect of Game ($F(2,100) = 8.54$, $\eta^{2}  = 0.05$,  $p < .001$), indicating that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ($t(100) =3.78$, $p < .001$) and the NUMBERS game ($t(100) = 3.32$ , $p = .002$).
-The score in RPS was not significantly different from the score in NUMBERS ($t(100) = 0.45$ , $p = .65$).
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ($t(100) =3.78$, $p < .001$) and the Numbers game ($t(100) = 3.32$ , $p = .002$).
+The score in RPS was not significantly different from the score in Numbers ($t(100) = 0.45$ , $p = .65$).
 The main effect of Block ($F(1,50) = 22.51$ ,  $\eta^{2} = 0.03$, $p < .001$) shows that the score in the first half of each game ($M = 0.29$) was significantly lower than in the second half ($M = 0.40$), which indicates within-game learning.
@@
 Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
+**MS: Need to check test results and report GG degrees of freedom, etc.**
 
@@
 
-```{r exp1-3factor-plot, include= FALSE, fig.cap = "Boxplots of scores by game, block and condition", fig.align = "center"}
+```{r exp1-3factor-plot, include= FALSE, fig.cap = "Performance in early rounds (2-6) per game and block across conditions in Experiment 1.
+Points are scores of individual participants and boxes reflect the 95\\% confidence intervals of the mean (center line equals the mean).", fig.align = "center", fig.width=8, fig.height=4}
 
 # Plot results by game and block (for all 3 games, learning is happening) 
-p <- ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")
-
-p + facet_grid(. ~ condition)
+dat2 %>%
+  mutate(game = forcats::fct_recode(as.factor(game), RPS = "rps", FWG = "fwg", Numbers = "numbers")) %>%
+  mutate(condition = factor(condition, levels = c("Level1", "Level2"))) %>%
+  mutate(condition = forcats::fct_recode(condition, "Level 1" = "Level1", "Level 2" = "Level2")) %>%
+  ggboxplot(x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","Numbers"), fill="block", ylab = "Percentage score", xlab = "Games") +  facet_grid(. ~ condition)
+
+```
+
+```{r ANOVAexp1, include = FALSE, warning=FALSE}
+
+afex::aov_car(
+  block_score ~ game.f*condition*block + Error(human_id/(game.f*block))
+  , data=dat2
+  , type = 3)
+
+#apa_lm1 <- apa_print(exp1_early_anova)
+
+#means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
+#trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","Numbers"))
 
@@
 
-As a measure for learning transfer, we focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game (see Figure \ref{fig:exp1-score-by-opp}).
+As a measure for learning transfer, we focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game (see Figure \ref{fig:exp1-early-score-by-opp}).
 We exclude the very first round as the computer opponent plays randomly here and there is no opportunity yet for the human player to exploit their opponent's strategy.
@@
 The FWG early score score is significantly higher than 0 ($t(148.85) = 4.584$, $p < .001$).
-This is also the case for the NUMBERS game ($t(148.85) = 3.00$, $p = .009$).
+This is also the case for the Numbers game ($t(148.85) = 3.00$, $p = .009$).
 We did not expect positive scores for the RPS game, as it was the first game played and there was no opportunity for learning about the opponent's strategy.
@@
 
-(ref:figure4-caption) Mean and standard error of early scores by game and opponent
-```{r exp1-early-score-by-opp, fig.cap = "(ref:figure4-caption)", fig.align ='center'}
-
-p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","Numbers"), ylab = "Early rounds score", xlab = "Games")
-
-p2 + facet_grid(. ~ condition)
+<!-- (ref:figure4-caption) Mean and standard error of early scores by game and opponent -->
+```{r exp1-early-score-by-opp, fig.cap = "\\label{ref:figure4-caption}Performance in early rounds (2-6) per game and block across conditions in Experiment 1.
+Points are scores of individual participants and boxes reflect the 95\\% confidence intervals of the mean (center line equals the mean).", fig.align ='center', fig.width=8, fig.height=4}
+exp1_dat2_6 %>%
+  mutate(game = factor(game.f)) %>%
+  mutate(game = forcats::fct_recode(game, Numbers = "Numbers")) %>%
+  mutate(game = factor(game, levels = c("RPS", "FWG", "Numbers"))) %>%
+  mutate(condition = factor(condition, levels = c("Level1", "Level2"))) %>%
+  mutate(condition = forcats::fct_recode(condition, "Level 1" = "Level1", "Level 2" = "Level2")) %>%
+  ggplot(aes(x = game, y = early_score, colour=game)) + stat_summary(fun.data = "mean_ci", geom = "crossbar")  + geom_jitter(alpha=.4) + ylab("Early score") + xlab("Game") + facet_grid(.
+~ condition) + theme_apa() + geom_hline(yintercept = 0, lty=2) + scale_color_discrete() + theme(legend.position = "none")
+
+#p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","Numbers"), ylab = "Early rounds score", xlab = "Games")
+
+#p2 + facet_grid(. ~ condition)
 
@@
 We expected better transfer between more similar games (i.e.
-better transfer from RPS to FWG than from RPS/FWG to NUMBERS), and worse transfer for the more sophisticated level 2 agent.
-Figure~\ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 players.
-To explore this, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game ($F(2,92) = 3.35$, $\eta^{2}  = 0.04$,  $p < .04$).
+better transfer from RPS to FWG than from RPS/FWG to Numbers), and worse transfer for the more sophisticated level 2 agent.
+Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents.
+To explore this, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants.
+There was a main effect of Game ($F(1.84,91.77) = 3.35$, $\eta^{2}  = 0.04$,  $p = .043$, Greenhouse-Geisser correction to degrees of freedom applied to correct for non-sphericity).
 We then run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( $t(150) = 3.96$, $p < .001$) and NUMBERS ($t(150) = 3.74$, $p < .001$).
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ($t(150) = 2.48$, $p = .01$) but not to the dissimilar game of NUMBERS.
-
-### Experiment 1 discussion:
-
-These results indicate that learning transfer to the more dissimilar game (NUMBERS) we found earlier is exclusively driven by level-1 facing players, as average early round scores in the NUMBERS game of level-2 facing players are close to 0.
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(150) = 3.96$, $p < .001$) and Numbers ($t(150) = 3.74$, $p < .001$).
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ($t(150) = 2.48$, $p = .01$) but not to the dissimilar game of Numbers.
+
+### Discussion
+
+The results of Experiment 1 indicate that participants were able to learn successful strategies which exploited the deviation from Nash-optimal play of their opponents.
+Moreover, they were able to transfer knowledge about their opponent to other games, but this was moderated by the type of game and opponent.
+There was evidence of transfer from the RPS game to the similar FWG game for both opponents.
+However, transfer to the dissimilar Numbers game was only evident for participants facing a level-1 opponent.
+<!-- These results indicate that learning transfer to the more dissimilar game (NUMBERS) we found earlier is exclusively driven by level-1 facing players, as average early round scores in the NUMBERS game of level-2 facing players are close to 0.
 Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar FWG game, but only those facing the less sophisticated opponent are able to generalise to the less similar NUMBERS game.
+-->
 
@@
 
-We ran a second experiment with various differentiated features to improve the opportunity to measure learning transfer.
-Instead of making participants face either the level-1 or level-2 player throughout, we made them face both opponents sequentially.
-Because there were two distinct opponents, requiring potentially holding two opponent models in memory, we also made it easier to recall the results of past rounds by providing participants with the opportunity to see the history of the game since the beginning of each interaction.
+In Experiment 2, we aimed to obtain a stronger test of learning transfer.
+<!-- We ran a second experiment with various differentiated features to improve the opportunity to measure learning transfer.--> Instead of facing a single level-1 or level-2 opponent throughout all games, participants face both types of opponents sequentially in this experiment.
+To perform well against both opponents, participants would need to learn distinct strategies in each game.
+To reduce effects of increased memory load due to facing distinct opponents, we provided participants access to the history of play against an opponent within each game (see Figure \@ref(fig:feedback-rps-exp2)).
+Finally, we changed the third game to a penalty shootout game, with participants aiming to score a goal and opponents playing the role of goal keepers.
+Whilst this game has the same number of actions as the first two (aim left, center, or right), it is strategically dissimilar.
+Unlike the Numbers game in Experiment 1, the Shootout game does not have a cyclical hierarchy between actions, making it harder to win through a heuristic based on this cyclicity.
+
+<!-- Because there were two distinct opponents, requiring potentially holding two opponent models in memory, we also made it easier to recall the results of past rounds by providing participants with the opportunity to see the history of the game since the beginning of each interaction.
 Figure\ \@ref(fig:feedback-rps-exp2) shows an example of showing interaction history in the RPS game.
@@
 If we see evidence for differential play against opponents, it would show participants adapting their strategies to the opponent they are facing, which is indicative of opponent modelling.
+-->
 
@@
 
-A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
-This was a new set of participants unrelated to those taking part in Experiment 1.
-The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
+A total of 48 participants (21 females, 28 males, 1 unknown) were recruited via the Prolific platform, none of which took part in Experiment 1.
+The average age was 30.2 years, and the mean duration to complete the task was 39 minutes.
 Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
@@
 
-The three games the participants played were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
+The three games the participants played were Rock-Paper-Scissors (RPS), Fire-Water-Grass (FWG), and the penalty Shootout game.
 The first two games were identical to the ones used in the first experiment.
-In the final game (shootout) the participants took the role of the player shooting a football (soccer) penalty, with the AI opponent being the goalkeeper.
-Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
-If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
+In the final game (Shootout) participants took the role of the a football (soccer) player in a penalty situation, with the computer opponent taking the role of the goalkeeper.
+Players had the choice between three actions: shooting the football to the left, right or centre of the goal.
+Similarly, the goalkeeper chooses between defending the left, right, or centre of the goal.
+If participants shoot in a different direction than where the goalkeeper defends, they win the round and the goalkeeper loses.
 Otherwise, the goalkeeper catches the ball and the player loses the round.
@@
 Figure\ \@ref(fig:screenshot-shootout) shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
-A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
-As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
+What makes this game different to the other games is that there are two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend ''right'' in the next round, they can win by either choosing to shoot ''left'' or ''center''.
+A level-1 shooter who thinks that their goalkeeper opponent will repeat their last action has thus two possible best responses.
+A level-1 goalkeeper, however, has only a single best response (defending where their opponent aimed in the last round).
+A level-2 goalkeeper, who believes their opponent is a level-1 shooter, will have two best responses however.
+We programmed the level-2 computer player to choose randomly between these two best responses.
 
@@
 
-knitr::include_graphics("images/shootout.png")
+knitr::include_graphics("images/shootout.jpg")
 ```
@@
 
-The participants played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
+Participants played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
 Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
@@
 In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
-During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
-A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response, as a way of simulating a real human opponent thinking time.
-After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
-Further information about the outcome of previous rounds was also visible on the game screen below the feedback area.
-Throughout each stage, participants could scroll down to recall the history of interaction.
+During those 3 seconds, participants could not choose an action and had to wait for the timer to run out.
+A small random delay between 0.5 and 3 seconds was also introduced before the computer agent made their choice, as a way of simulating a real human opponent thinking time.
+After each round, participants were given detailed feedback about their opponent's action and whether they won or lost the round.
+Further information about the history of play in previous rounds was also provided and participants could scroll down to recall the full history of each interaction against an opponent in a particular stage of a game.
 The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-As in the first experiment, all the games have a unique MSNE consisting of randomising across actions.
+As in the first experiment, all the games have a unique mixed-strategy Nash equilibrium consisting of uniformly random actions.
 If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
-Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
+Evidence of sustained wins would indicate that participants have learned to exploit patterns in their opponents' play.
 
@@
 
-The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had an adjusted average score in between the two (M = 0.289, SD = 0.326).^[ A higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
+Participants scores are depicted in Figure \ref{fig:exp2-score-by-opp}.
+The RPS game had the lowest average score per round ($M = 0.194$, SD = 0.345) followed by FWG ($M = 0.27$, SD = 0.394) and finally the Shootout game ($M = 0.289$, SD = 0.326).^[ A higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
 Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33)].
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, $p$ < 0.0001 ;  FWG:  t(49) = 7.25 , $p$ < 0.0001 ; Shootout: t(49) = 13.61, $p$ < 0.0001 ).
-Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
-We perform a two (condition: level-1 first, level-2 first) by two ( opponent type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
+To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33)] Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: $t(49) = 6.26$, $p < .001$; FWG: $t(49) = 7.25$, $p < .001$; Shootout: $t(49) = 13.61$, $p < .001$).
 
@@
 
-```{r exp2-score-by-opp, fig.cap="Boxplot of scores per game and interaction by opponent type", fig.align="center"}
+```{r exp2-score-by-opp, include= FALSE, fig.cap = "\\label{fig:exp2-score-by-opp}Performance per game and interaction across opponents in Experiment 2.
+Points are scores of individual participants and boxes reflect the 95\\% confidence intervals of the mean (center line equals the mean).", fig.align = "center", fig.width=8, fig.height=4}
+# Plot results by game and block (for all 3 games, learning is happening) 
+dat_int %>%
+  mutate(game.f = forcats::fct_recode(game.f, Shootout = "SHOOT")) %>%
+  mutate(game.f = factor(game.f, levels = c("RPS", "FWG", "Shootout"))) %>%
+  mutate(opp_type = forcats::fct_recode(as.factor(opp_type), "Level 1" = "Level_1", "Level 2" = "Level_2")) %>%
+  mutate(encounter = interaction_lvl) %>%
+  ggplot(aes(x = game.f, y = int_score, colour = encounter)) + stat_summary(fun.data = "mean_ci", position = position_dodge2(width=.8), geom = "crossbar")  + geom_point(position=position_jitterdodge(), alpha=.4) + ylab("Score") + xlab("Game") + facet_grid(.
+~ opp_type) + theme_apa() + geom_hline(yintercept = 0, lty=2)
+
 # p3 <- ggerrorplot(dat_int, x = "game.f", y = "int_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Scores per game", xlab = "Games")
@@
 
-p4 <- ggboxplot(dat_int, x = "game.f", y = "int_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","SHOOT"), fill="interaction_lvl",ylab = "Percentage score", xlab = "Games", legend.title = "interaction level")
-
-p4 + facet_grid(. ~ opp_type)
+#p4 <- ggboxplot(dat_int, x = "game.f", y = "int_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","SHOOT"), fill="interaction_lvl",ylab = "Percentage score", xlab = "Games", legend.title = "interaction level")
+
+#p4 + facet_grid(. ~ opp_type)
 
@@
 
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, $\eta^{2}$ = 0.04,  p < .0001).
-To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
-We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the Shootout game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
-There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
-There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,$\eta^{2}$ = 0.02,  p = .01).
-Figure\ \@ref(fig:exp2-score-by-opp) shows boxplots of game scores, averaged across participants, by game and opponent type.
+To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA on the average score per round, with the first factor varying between participants.
+This shows a main effect of Game ($F(1.85,88.7) = 11.81$, $\eta^{2} = 0.04$,  $p < .001$).
+Post-hoc pairwise comparisons between games (p-values adjusted using Holm method for multiple comparisons) indicate performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS ($t(96) =2.53$, $p = .025$), and performance in the Shootout game significantly higher than in FWG ($t(96) = 2.32$, $p = .025$).
+Whilst the ANOVA shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type ($F(1.7, 81.82) = 5.31$ ,$\eta^{2} = 0.02$,  $p = .01$).
+Follow-up analysis shows that when facing level-1 agents, scores increase steadily after each game, with FWG score significantly higher than RPS ($t(191) = 2.70$, $p = .03$) and Shootout scores in turn significantly higher than FWG  ($t(191) = 3.05$, $p = .01$).
+There was no significant difference between average scores on any two games when facing level-2 agents however.
+
+<!--Figure\ \@ref(fig:exp2-score-by-opp) shows boxplots of game scores, averaged across participants, by game and opponent type.
 We also distinguish between scores from the first time the players faced the opponent (first interaction) and the second time they did (second interaction).
-We see that when facing level-1 agents, scores increase steadily after each game, with FWG score significantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG  ( t(191) = 3.05, p = 0.01).
+We see that when facing level-1 agents, scores increase steadily after each game, with FWG score significantly higher than RPS ($t(191) = 2.70$, $p = .03$) and Shootout scores in turn significantly higher than FWG  ($t(191) = 3.05$, $p = .01$).
 There was no significant difference between average scores on any two games when facing level-2 agents however.
+-->
 
@@
 ```
-
-As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random.
 
@@
 
-(ref:figure7-caption) Mean and standard error of early scores by game and opponent for experiment 2
-```{r exp2-early-scores, fig.cap="(ref:figure7-caption)", fig.align="center"}
+```{r exp2-early-score-by-opp, fig.cap = "\\label{ref:figure4-caption}Performance in early rounds (2-6) per game and opponent in Experiment 2.
+Points are scores of individual participants and boxes reflect the 95\\% confidence intervals of the mean (center line equals the mean).", fig.align ='center', fig.width=8, fig.height=4}
+exp2_dat2_6 %>%
+  mutate(game = factor(game.f)) %>%
+  mutate(game = forcats::fct_recode(game, Shootout = "SHOOT")) %>%
+  mutate(game = factor(game, levels = c("RPS", "FWG", "Shootout"))) %>%
+  mutate(opp_type = factor(opp_type, levels = c("Level_1", "Level_2"))) %>%
+  mutate(opp_type = forcats::fct_recode(opp_type, "Level 1" = "Level_1", "Level 2" = "Level_2")) %>%
+  ggplot(aes(x = game, y = early_score, colour=game)) + stat_summary(fun.data = "mean_ci", geom = "crossbar")  + geom_jitter(alpha=.4) + ylab("Early score") + xlab("Game") + facet_grid(.
+~ opp_type) + theme_apa() + geom_hline(yintercept = 0, lty=2) + scale_color_discrete() + theme(legend.position = "none")
+
 # plot scores per game 
-p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Early rounds score", xlab = "Games", legend.title = "Games")
-
-p2 + facet_grid(. ~ opp_type)
-```
-
-In Figure\ \@ref(fig:exp2-early-scores), we show the average score across participants and its $95$ percent confidence interval in rounds 2-6 of the first interaction with the opponent for each game.
-These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
-For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
-(Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; Shootout:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; Shootout:  t(270) = 3.21, p =0.004 ).
-
-### Experiment 2 discussion:
+#p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Early rounds score", xlab = "Games", legend.title = "Games")
+
+#p2 + facet_grid(. ~ opp_type)
+
+```
+
+As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random (Figure\ \@ref(fig:exp2-early-scores)).
+For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types (Level-1 opponent: FWG: $t(270) = 4.99$, $p < .001$; Shootout: $t(270) = 6.66$, $p < .001$; Level-2 opponent: FWG: $t(270) = 4.40$, $p < .001$; Shootout: $t(270) = 3.21$, $p=.004$).
+**MS: Should also report ANOVA, as for Experiment 1**
+
+### Discussion
+
+The results of Experiment 2...
+**MS: give summary of main findings, as done for Experiment 1.
+You should not report new statistical tests in the discussion, which should go in the results section before.**
 
@@
 These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
-
-\newpage
 
@@
 The other models adapted their play to the opponent, either by reinforcing successful actions in each game (reinforcement learning), or by determining the type of opponent through Bayesian learning (Bayesian Cognitive Hierarchy models).
-We also include the Expected Weighted Attraction (EWA), which is a popular model in behavioral economics.
-
-We use the following notation.
-In each game $g \in \{\text{RPS},\text{FWG}, \text{NUMBERS}\}$, on each trial $t$, the participant chooses an action $a_t \in \mathcal{A}_g$, and the opponent chooses action $o_t \in \mathcal{A}_g$, where $\mathcal{A}_g$ is the set of allowed actions in game $g$, e.g.
+We also include the Expected Weighted Attraction (EWA) model, which is a popular model in behavioural economics.
+
+In the following, we will describe the models in more detail, and provide some intuition into how they they learn about the game and/or the opponent.
+We use the following notation: In each game $g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}$, on each trial $t$, the participant chooses an action $a_t \in \mathcal{A}_g$, and the opponent chooses action $o_t \in \mathcal{A}_g$, where $\mathcal{A}_g$ is the set of allowed actions in game $g$, e.g.
 $\mathcal{A}_\text{RPS} = \{R,P,S\}$.
@@
 
-In the following, we will describe the models in more detail, and provide some intuition into how they they learn about the game and/or the opponent.
-
 ## Reinforcement learning (RL) model
@@
 by defining the state $s_{t}$ as above.
-The resulting RL model learns a Q value [@watkins1992q] for each state-action pair:
-
-$$ Q_{t+1}(s_{t},a_{t}) = Q_{t}(s_{t},a_{t}) + \alpha \left( r_{t}  - Q(s_{t},a_{t}) \right) $$
-
-where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\alpha \in [0,1]$ the learning rate.
+The resulting RL model learns a $Q$-value [@watkins1992q] for each state-action pair:
+$$ Q_{t+1}(s_{t},a_{t}) = Q_{t}(s_{t},a_{t}) + \alpha \left( r_{t}  - Q(s_{t},a_{t}) \right) ,$$  
+where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$, and $\alpha \in [0,1]$ the learning rate.
 For instance, $Q_t(\{R,S\},P)$ denotes the value of taking action  ''Paper'' this round if the player's last action was ''Rock'' and the opponent played ''Scissors''.
 Actions are taken according to a softmax rule:
-$$P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}$$ 
-While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different action space $\mathcal{A}_g$, and there is no simple way to map actions between games.
-
-The RL model has two free parameters: the learning rate ($\alpha$) and the inverse temperature parameter of the softmax decision rule ($\lambda$).
-We've assumed $\gamma = 0$ as changes in this parameter didn't affect the other parameter estimations or ultimately the value of the likelihoods.
+$$P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}, $$ 
+where the inverse temperature parameter $\lambda$ determines the consistency of the strategu (the higher $\lambda$, the more often the action with the highest $Q$-value is chosen.
+While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different state $\mathcal{S}_g$ and action space $\mathcal{A}_g$, and there is no simple way to map states and actions between games.
+
+The RL model has two free parameters: the learning rate ($\alpha$) and the inverse temperature ($\lambda$).
+<!-- We've assumed $\gamma = 0$ as changes in this parameter didn't affect the other parameter estimations or ultimately the value of the likelihoods.
+-->
 
@@
 The attraction of action $a$ time $t$ is written $A_{t}(a)$ and is updated as
-
 $$ A_{t+1}(a) =  \frac{\phi \ N(t) \ A_{t}(a) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} $$
@@
 Unlike reinforcement learning, this uses knowledge of the rules of the game to allow reinforcing actions that were not taken.
-We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play @[cheung1994learning].
+We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play [@cheung1994learning].
 While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].
-$ N(t)$ represents an experience weights and can be interpreted as the number of "observation-equivalents" of past experience.
+$N(t)$ represents an experience weight and can be interpreted as the number of "observation-equivalents" of past experience.
 We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
+**MS: Should describe how the parameters are self-tuned with equations **
 
@@
 The self-tuning EWA has one free parameter: the inverse temperature of the softmax decision rule ($\lambda$).
+**MS: Are there no states in the EWA?
+If not, it is unsurprising that this model doesn't fit well **
 
@@
 They then use observations of the opponents actions to infer a posterior probability of each type:
-$$ P(\text{level}=k | D_{t})  \propto  P(D_{t}|\text{level}=k ) \times P(\text{level}=k)$$
-where $D_{t} = \{a_1,o_1,\ldots,a_t,o_t\}$ is the data available at time $t$. The likelihood is defined as
-$$P(D_{t}|\text{level}=k) = \prod_{j=1}^t \left( \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o_j|a_{j-1},o_{j-1})\right)$$
-where $f_k(o_t|a_{t-1},o_{t-1}) = 1$ if $o_t$ is the action taken by a level $k$ player when the previous round play was $a_{t-1}$ and $o_{t-1}$, and 0 otherwise.
+$$P(\text{level}=k | \mathcal{D}_{t})  \propto  P(\mathcal{D}_{t}|\text{level}=k ) \times P(\text{level}=k)$$
+where $\mathcal{D}_{t} = \{s_1,\ldots,s_t\}$ is the data available at time $t$. The likelihood is defined as
+$$P(\mathcal{D}_{t}|\text{level}=k) = \prod_{j=1}^t \left( \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o_j|s_{j})\right)$$
+where $f_k(o_t|s_{t}) = 1$ if $o_t$ is the action taken by a level $k$ player when the previous round play was $s_t = (a_{t-1}, o_{t-1})$, and 0 otherwise.
 Note that the likelihood assumes (correctly) that there is a probability $\theta \in [0,1]$ that the opponent takes a random action.
@@
 We assume a participant chooses an action by using the softmax function over the best response to predicted actions:
-$$\begin{aligned} B_t(a) &= \sum_{k = 0}^2 \sum_{o \in \mathcal{A}_g} b(a,o) P_k(o|a_{t-1},o_{t-1})  P(\text{level}=k|\mathcal{D}_{t-1})\\
-P_t(a) &= \frac{\exp{\lambda B_t(a)}}{\sum_{a' \in \mathcal{A}_g} \exp \lambda B_t(a')} \end{aligned}$$
+$$\begin{aligned} B_t(a) &= \sum_{k = 0}^2 \sum_{o \in \mathcal{A}_g} b(a,o) P_k(o|s_{t})  P(\text{level}=k|\mathcal{D}_{t-1})\\
+P_t(a) &= \frac{\exp\{\lambda B_t(a) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{ \lambda B_t(a')\}} \end{aligned}$$
 where $b(a,o) = 1$ if action $a$ is a best response to opponent's action $o$ (i.e.
@@
 Unlike the models above, the BCH model allows for between-game transfer, as knowledge of the level of the opponent can be used to generate predictions in games that have not been played before.
+This generalization is done simply by using the posterior $P(\text{level} = k|\mathcal{D}_T)$ from the previous game as rhe prior distribution in the next game.
 However, the participant might also assume that the level of reasoning of their opponent does not generalize over games.
+This would mean starting with a "fresh" prior $P(\text{level} = k)$ at the start of each game.
 We hence distinguish between two versions of the BCH model.
@@
 ## Estimation and model comparison
-In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
-Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
-
-In experiment 1, we fit a total of 5 models: A baseline model assuming random play (Nash),  Bayesian Cognitive Hierarchy model allowing transfer betwen games (BCH_BT) and another with no transfer between games (BCH_NBT), as well as a Reinforcement Learning model with state space consisting of last round play (RL), and finally a self tuning EWA model with the same state space (EWA).
-
-In experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two type of opponent model transfer.
+
+For both experiments, we fitted all models to individual participant data by maximum likelihood estimation.
+We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
+<!--, the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
+-->
+
+For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NBT), as well as a Reinforcement Learning model with state space consisting of last round play (RL), and finally a self-tuning EWA model with the same state space (EWA).
+
+In Experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two type of opponent model transfer.
 We can have transfer within games, between the first and second interaction with the opponent.
-We can also have transfer between games, as in transfering models of the opponent from RPS to FWG for instance.
-Therefore, we
-give models more flexibility to allow for these two types of transfer.
-As such, for Bayesian Cognitive Hierarchy, we fit a total of three models.
-BCH_BT allows for between game transfer.
-We assume that if such transfer is possible, then within game transfer should also be possible and therefore this model allows for both types of transfer.
-BCH_NBT allows for within but no between game transfer.
-Whereas BCH_NT allows for neither.
-For Reinforcement learning models, because RL models can't account for between game transfer due to change in ation labels, we can only have models allowing for within game transfer (RL Tr) or with no transfer within games (RL NT).
-Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (EWA_Tr) or without transfer (EWA_NT).
-Counting the base model wiht random play (Nash) we therefore fit a total of 8 models in experiment 2.
-
-## Experiment 1 modelling :
+We can also have transfer between games, as in e.g.
+transferring a learned opponent model from RPS to FWG.
+Therefore, we fitted a total of three versions of the Bayesian Cognitive Hierarchy model: BCH\_BT allows for both within and between game transfer (between game transfer without within game transfer is implausible); BCH\_NBT allows for within but not between game transfer; BCH\_NT allows for no transfer within or between games.
+For Reinforcement learning models, because RL models can't account for between game transfer due to change in state and action space, we can only have models that allowing for within game transfer (RL\_TR) or with no transfer within games (RL\_NT).
+Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (EWA\_TR) or without transfer (EWA\_NT).
+Counting the base model with random play (Nash) we therefore fit a total of 8 models for Experiment 2.
 
@@
 
-Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: We can see that the RL model clearly described most participants' behaviour best, followed by the random (Nash) model.
+Figure\ \@ref(fig:exp1-comp-models)  shows the results for Experiment 1.
+We can see that the RL model clearly described most participants' behaviour best, followed by the random (Nash) model.
 Only a few participants were best described by one of the BCH models, or the EWA model.
 Looking at BIC weights, we confirm this as seen in  Figure \ \@ref(fig:xp1-BIC-weigths).
-RL models hve high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, whihc fits the picture drawn by the histogram.
+RL models have high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, which fits the picture drawn by the histogram.
 ```{r, include=FALSE}
@@
 
-(ref:figure9-caption) Model BIC weights for participants in experiment 1
+(ref:figure9-caption) Model BIC weights for participants in Experiment 1.
 ```{r, xp1-BIC-weigths, fig.cap="(ref:figure9-caption)", fig.align="center"}
+ggplot(d, aes(y = BIC_weight, x = 1)) + 
+  geom_violin() +
+  geom_jitter(width=.2, alpha=.6) + 
+  facet_wrap(~Model) + theme_apa() + theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) + xlab("") + ylab("BIC weight")
+#  theme(legend.position = c(0.8, 0.3))
+
 # Everything on the same plot
-ggplot(d, aes(ID,BIC_weight, col=Model)) + 
-  geom_point() + 
-  stat_smooth() +
-  facet_wrap(~Model) +
-  theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank()) + 
-  theme(legend.position = c(0.8, 0.3))
+# ggplot(d, aes(ID,BIC_weight, col=Model)) + 
+#   geom_point() + 
+#   stat_smooth() +
+#   facet_wrap(~Model) +
+#   theme(axis.title.x=element_blank(),
+#         axis.text.x=element_blank(),
+#         axis.ticks.x=element_blank()) + 
+#   theme(legend.position = c(0.8, 0.3))
 
@@
 
-## Experiment 2
-
-In experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that the RL model was again more successful than the Bayesian models in fitting player's action choices.
-In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
-This is also reflected in BIC weights in Figure \ \@ref(fig:xp2-BIC-weigths)
+In Experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that the RL model was again more successful than the Bayesian Cognitive Hierarchy models (with or without transfer) in fitting participants' action choices.
+<!--  In Experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
+--> This is also reflected in BIC weights in Figure \@ref(fig:xp2-BIC-weigths).
+**MS: model labels in Figures should correspond to those in the text**
 
@@
 
-(ref:figure11-caption) Model BIC weights for participants in experiment 2
+(ref:figure11-caption) BIC weights for each model and participant in Experiment 2.
 ```{r, xp2-BIC-weigths, fig.cap="(ref:figure11-caption)", fig.align="center", out.width="\\textwidth"}
-# Everything on the same plot
-ggplot(d, aes(ID,BIC_weight, col=Model)) + 
-  geom_point() + 
-  stat_smooth() +
-  facet_wrap(~Model) +
-  theme(axis.title.x=element_blank(),
+ggplot(d, aes(y = BIC_weight, x = 1)) + 
+  geom_violin() +
+  geom_jitter(width=.2, alpha=.6) + 
+  facet_wrap(~Model) + theme_apa() + theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
-        axis.ticks.x=element_blank()) + 
-        theme(legend.position = c(0.8, 0.17), 
-        legend.direction = "vertical",
-        legend.key.size = unit(0.4, "cm"),
-        legend.key.width = unit(0.6,"cm")) 
-        # + guides(fill=guide_legend(nrow=4,ncol=2))
+        axis.ticks.x=element_blank()) + xlab("") + ylab("BIC weight")
+
+# # Everything on the same plot
+# ggplot(d, aes(ID,BIC_weight, col=Model)) + 
+#   geom_point() + 
+#   stat_smooth() +
+#   facet_wrap(~Model) +
+#   theme(axis.title.x=element_blank(),
+#         axis.text.x=element_blank(),
+#         axis.ticks.x=element_blank()) + 
+#         theme(legend.position = c(0.8, 0.17), 
+#         legend.direction = "vertical",
+#         legend.key.size = unit(0.4, "cm"),
+#         legend.key.width = unit(0.6,"cm")) 
+#         # + guides(fill=guide_legend(nrow=4,ncol=2))
 ```
@@
 
-The computational modelling indicates that most players are best fit by Q-learning type models with states defined by last round play.
-This is at odds with the findings from the section regarding learning transfer: If indeed most participants use Q-learning with states to choose their actions, then they should not be able to transfer learning to the early rounds of the new game.
-In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Bayesian Cognitive Hierarchy models with and without the possibility of across game transfer.
-
-We start with experiment 1 data.
-Figure\ \@ref(fig:exp1-lik-by-tr) shows that in the later games, the likelihood for the BCH models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of BCH models.
-
+The computational modelling indicates that most players are best fit by a reinforcement learning which learns good actions conditional upon the last round play.
+This is at odds with the behavioural findings, where we found evidence of transfer in early rounds of each game.
+If indeed most participants adopt a reinforcement learning strategy, they should not be able to transfer their learning to the early rounds of a new game.
+In order to investigate this discrepancy further, we plot the likelihood by trial for each game and three strategies: RL, Bayesian Cognitive Hierarchy models with between-game transfer, and the random (Nash) strategy.
+Figure\ \@ref(fig:exp1-lik-by-tr) shows that in the later games of Experiment 1, the likelihood for the BCH models is higher than that of the other models in the initial rounds of the games.
+However, over time, the likelihood of the RL model increases and exceeds that of BCH model.
 ```{r, include= FALSE}
@@
 ```
-
 ```{r exp1-lik-by-tr, fig.cap = "Experiment 1 Likelihood by trial by game and opponent faced", fig.align='center'}
@@
 ```
-
-Likewise, in experiment 2,  we want to understand the dynamic of strategy choice by plotting the likelihood by trial for each strategy, using the optimal parameters found when fitting the model.
-Figure\ \@ref(fig:exp2-lik-by-tr) shows that, as in experiment 1, BCH models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
+The same pattern holds for Experiment 2 (Figure\ \@ref(fig:exp2-lik-by-tr)).
+Again, the BCH model with between-game transfer has the highest likelihood in the early stages of the later games (apart from stage 1 of the shootout game, where the RL model is better).
+In later rounds, the likelihood of the RL model exceeds that of the BCH model.
+<!-- second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
 In the third and more dissimilar game, we get a result that is different from experiment 1.
-In this instance, the likelihoods of the BCH models stay constant and close to their initial values.
+In this instance, the likelihoods of the BCH models stay constant and close to their initial values.-->
 
@@
 
-The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative of participants switching between strategies as the games progressed.
-Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the BCH based strategies fitted observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
-
-In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q-learning with state space consisting of previous round play, BCH based model with opponent model transfer, and a base model consisting of random play consistent with a Nash equilibrium strategy).
+The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative that participants switch between strategies as the games progress.
+According to this interpretation, participants base their responses in early rounds on the learned level of their opponents iterative reasoning, switching later to learned actions through reinforcement.
+<!--use a Bayesian Cognitive Hierarchy Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the BCH based strategies fitted observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.-->
+
+We use hidden Markov models to more formally test for strategy switching in participants' play.
+In these models, the three strategies (RL, BCH with between-game transfer, and Nash) correspond to latent states which determine the overt responses (actions chosen).
+The models allow for switching between the states over time, and such switches correspond to strategy switches.
+Hidden Markov models assume that an observable action at time $t$ depends on a latent state at time $t$.
+Second, it is assumed that the latent state at time $t$ depends on the latent state at the previous time $t-1$.
+The model is specified by the state-conditional action distributions (these are provided by the likelihood of the fitted models), an initial state distribution (the distribution over the strategies at the initial round), and the state-transition probabilities (probability of switching from one state/strategy to another).
+Initial state probabilities and the transition probabilities were estimated with the depmixS4 package [@R-depmixS4].
+As a statistical test of strategy switching, we compare the hidden Markov model to a constrained version which assumes the probability of switching from one strategy to a different one is 0.
+This model thus assumes that when players start with a particular strategy, they continue using it throughout the experiment.
+
+<!-- In the first model, we allow for a non-nil probability of players transitioning from one state (strategy) to another.
+In the second model, we assume that such switching does not happen, and as such assume implicitly that when players start with a particular strategy, they continue using it throughout the experiment.
+We then compare the likelihoods of each HMM model using a likelihood ratio test.
+
+that this hidden process has a Markov property, meaning that given state $S_{t-1}$, the value of $S_{t}$ is independent of all states occurring before time $t-1$.
+We also assume that $S_{t}$ has a discrete probability distribution in that it take one of K discrete values.
+The model is therefore specified by initial probabilities of being in each state ${1,2,...,K}$ and transition probabilities for moving from state $i$ to state $j$.
+These probabilities are fit using observed actions generated from these hidden states.
+
+, we fitted Hidden Markov Models in which the latent states are the 3 strategies used (Q-learning with state space consisting of previous round play, BCH based model with opponent model transfer, and a base model consisting of random play consistent with a Nash equilibrium strategy).
 Hidden Markov models are useful tools to explore structure in observed time series.
@@
 We then compare the likelihoods of each HMM model using a likelihood ratio test.
-
-### Experiment 1:
+-->
+
 ```{r define-dummy-response, include=FALSE}
@@
 
-In experiment 1, the HMM model with switching fits significantly better than the non-switching one ($p < .001$).
-This is further statistical evidence in favour of the hypothesis that participants switch between strategies.
-In order to understand at which stage of the games the switching might happen, and whether there are any differences between games and type of opponents faced, we plot in Figure\ \@ref(fig:exp1-posteriors-plot) the average (across participants) posterior probabilities of each state (strategy), as a function of trial and opponent faced.
+In Experiment 1, a likelihood-ratio test shows that the HMM model with switching fits significantly better than the non-switching one ($p < .001$).
+**MS: we should really use a bootstrapped Likelihood Ratio test here ** This provides further statistical evidence in favour of the hypothesis that participants switch between strategies.
+Figure\ \@ref(fig:exp1-posteriors-plot) depicts the average (across participants) posterior probabilities of each state (strategy), as a function of trial and opponent faced.
+As can be seen, there is evidence of strategy switching in the FWG and Numbers games: Initially, participants appear to use a random strategy (in the first round of a game, there is no way to predict the opponent's action), after which the BCH strategy becomes dominant.
+In the later rounds of the games, the RL strategy becomes dominant, however.
+<!--This is then when there is no past play.
 The posterior probability is the probability that an observation comes from a component distribution a posteriori, i.e.
@@
 In the first experiment, we can see from the plots of FWG and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the RL model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
-
-### Experiment 2:
+-->
 
@@
 
-The switching model in experiment two has also significantly higher likelihood ($p$ = 0.00).
-On top of indications from looking at the likelihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
-The posterior probability plot in Figure\ \@ref(fig:exp2-posteriors-plot) shows switching much more clearly across games and stages.
+The switching model in Experiment 2 is also significantly better than the restricted non-switching model ($p < .001$).
+<!-- On top of indications from looking at the likelihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
+--> The posterior probabilities of the strategies (Figure\ \@ref(fig:exp2-posteriors-plot)) show very clear evidence of strategy switching across games and stages, from using a BCH model in the initial rounds to an RL strategy later on.
+<!--.
 The switching also seems to happen very early on at the beginning of each game and stage, and is also consistently in the same direction: The probability of Bayesian models with transfer being initially high, then decreasing rapidly while the posterior probability of QL-Learning with states and within transfer learning increases rapidly.
@@
 
+-->
+
 # Discussion
 
-In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies.
-We were interested in exploring whether participants learn about the strategy of their opponent and transfer such knowledge between games, and whether this is modulated by the similarity between games and the sophistication of the agent.
-
-The results of our first experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
-We used results on very early rounds for measuring transfer as they are unlikely to be tainted by any within game learning.
-Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
-
-In the second online experiment, there were many more opportunities to test transfer than before: 2 opportunities to transfer opponent models within each game, and a total of three games, which means 6 opportunities to test transfer.
-The results on learning transfer confirmed prior findings from the first experiment.
-While there was no evidence of higher scores across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
-We also found that learning transfer is modulated by the type of opponent faced.
-When the players faced the level-1 opponent, they were able to transfer learning.
-However, when they faced the level-2 opponent, there was weaker evidence for transfer.
+In this study, we investigated human learning transfer across games by making human participants play against computer agents with limited levels of iterated reasoning.
+We were interested whether participants learn about the strategy of their opponent and transfer such knowledge between games, and whether this is modulated by the similarity between games and the sophistication of the agent.
+
+The results of our first experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to a similar game.
+Performance in early rounds indicated that transfer to the more dissimilar game was moderated by the degree of sophistication of the opponent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
+In the second experiment, participants faced both types of opponents, which allows for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent within a game.
+In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
+Experiment 2 alsp offers more opportunities to test transfer of a learnt opponent model.
+There were two opportunities to transfer opponent models within each game as well as two opportunities to transfer from each game to the next, giving a total of 6 transfer opportunities.
+**MS: we did not test transfer at all these points, or did we?** The results on learning transfer confirmed the findings from the first experiment.
+Again, there was clear evidence of transfer in the early rounds of the later games.
+<!--While there was no evidence of higher scores across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
+--> We also found that learning transfer is moderated by the type of opponent faced: Evidence of transfer was weaker for the level-2 opponent as compared to the level-1 opponent.
+That transfer was less evident for the more sophisticated level-2 opponent in both experiments may be due to a higher difficulty of learning that opponent's strategy.
+If it is more difficult to establish a model of the level-2 opponent, there is likely less knowledge to transfer to the new game.
+A player cannot transfer what they have not learnt.
+<!-- and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
+.
+When the players faced a level-1 opponent, they were able to transfer learning.
+However, when they faced a level-2 opponent, there was weaker evidence for transfer.
 The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with.
 A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
-
-Coming back to learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are significantly higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
-The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
-what did the players learn specifically about the opponent strategy and what form did this learning take?
-
-We will proceed by considering multiple potential answers to this question.
-A possible hypothesis for learning the opponent’s strategy is the use of simple rules based on last round play (for instance, I play scissors whenever opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
-Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
-While this approach certainly seemed to be the best fit for many player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
+-->
+
+<!-- Coming back to learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are significantly higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
+The question we ask ourselves therefore is: -->
+
+What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
+what did the players learn specifically about their opponent's strategy and what form did this learning take?
+
+<!-- We will proceed by considering multiple potential answers to this question. A possible hypothesis for learning the opponent’s strategy is the use of -->
+
+One possible answer is that participants learned simple rules based on last round play.
+For instance, "play scissors whenever my opponent played rock in last round", or "play paper whenever the last round play was either rock or scissors".
+These are the type of strategies that are learned by the model-free reinforcement learning we used in our computational modelling.
+While this strategy fitted participants' actions the best overall, there are at least two reasons why this account is not satisfactory as a complete description of participants' behaviour.
+Firstly, the learned strategies are not transferable to new games.
+There is no simple way to map "play scissors whenever my opponent played rock in last round" in the RPS game to "play grass whenever my opponent played fire in last round".
+Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this.
+Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
+Secondly, a reinforcement learning strategy would fare equally well against the level-1 and level-2 opponent.
+Whilst choosing different actions, the contingency between the state (last round play) and actions is the same for both opponents.
+Yet, we found that participants performed better against the level-1 opponent compared to the level-2 opponent.
+The difference in performance between the two types of opponent indicate that the actions of the more sophisticated level-2 opponent, or the best response to these, were somehow more difficult to predict.
+
+<!--
+it is unsatisfactory in explaining some of the learning transfer evidence we showed.
 Indeed, learning the best action in a particular state is not transferable to a new game since the state space is different and there is no single mapping between the state spaces of the initial and latter games.
@@
 The fact that the degree of sophistication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
-
-We are left with two possible explanations: First, it is possible that the players have uncovered a heuristic that allows them to beat the opponent without explicitly modelling their strategy, and is robust to transfer.
-Indeed, because of the cyclicality in action choices (e.g : Rock beats Scissors beats Paper beats Rock), it is possible to beat level-2 opponents most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
-This is a rule that wins and is also robust to transfer as it does not depend on action labels and even works in the dissimilar game.
-
-The second explanation of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
+-->
+
+We are left with two possible explanations: First, it is possible that participants discovered a heuristic that allowed them to beat their opponent without explicitly modelling their strategy, and that this heuristic is transferable to new games.
+Because of the cyclicity in action choices (e.g., rock beats scissors, scissors beats paper, paper beats rock), it is possible to beat a level-2 opponent most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
+This is a rule that wins and is transferable to other games as it does not depend on action labels.
+In the same vein, a heuristic that beats a level-1 player can be stated as "Choose the action that would have been beaten by my previous action".
+Intuitively, it seems that the heuristic for the level-2 player is simpler than that for the level-1 player, which is at odds with the difference in performance.
+
+A second explanation is that participants engaged in iterative reasoning, inferring their opponent's beliefs and countering the resulting actions.
+For instance, this would be reasoning of the form "My opponent expects me to repeat my last action, choosing an action that would beat my last action.
+Hence, I will choose the action that beats their best response" or "My opponent thinks I expect them to repeat their action, hence expecting me to choose the action that beats their last action.
+They will therefore choose the action that beats this one, and hence I should choose the action that beats their best response." Beating a level-1 player, in this account, requires being a level-2 player, and beating a level-2 player requires being a level-3 player.
+Intuitively, the additional step of iterative reasoning involved in beating a level-2 player makes the level-3 strategy more demanding and difficult to implement, which is consistent with the lower performance against the level-2 opponent.
+
+The differences in performance between the two players, coupled with the finding of positive transfer, point to participants engaging in iterative reasoning, and learning something useful about their opponent's limitations in this regard.
+This is the type of learning encapsulated by our Bayesian Cognitive Hierarchy model.
+It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
+Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
+**MS: need to check relevance of these citations.
+Also, they need to be in reference list ** We admit that our implementation in the BCH models does not predict a performance difference between the types of opponents.
+Starting with an equal prior belief over the different levels of sophistication, a BCH player would perform equally well against the level-1 and level-2 opponent.
+There are two routes to explain the difference in performance.
+Firstly, prior beliefs might be biased against higher-level opponents (i.e., participants might have believed it is more likely that they would face level-1 opponent than a level-2 opponent).
+Secondly, if the actions of a level-2 opponent are more difficult to predict than those of a level-1 opponent, this might introduce more noise in the likelihood of the opponents actions given their level of sophistication.
+Either of these mechanisms would explain why learning the strategy of the level-2 opponent is more difficult and slower than learning the strategy of the level-1 opponent.
+**MS: This could be something to implement, actually** Using hidden Markov models, we found evidence of strategy switching between the BCH and RL strategies, and such switching seems more consistent with the latter idea.
+If predicting an opponent's actions through iterative reasoning is cognitively demanding and error-prone, it is resource-rational to switch to less costly yet equally successful strategies when these are available.
+**MS: add reference to resource-rational approach by Lieder & Griffiths ** Initially, a model-free reinforcement learning strategy will be less successful than an iterative reasoning one.
+However, given enough experience, it will be on par with an iterative reasoning strategy.
+As it involves simple state-action contingencies, a model-free RL strategy may also be computationally less costly, making it overall more effective to rely on this than iterative reasoning.
+This is similar to the arbitration between model-free and model-based RL [@Simon_Daw_11] **MS: add more references here**.
+In repeated and well-practised situations, relying on habits allows one to save cognitive resources for other demands.
+However, when the environment -- or game -- changes, it is prudent to use all available resources to reorient oneself.
+
+<!--
+building a mental representation of their opponent's strategy.
+
+of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
 A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
@@
 
+-->
+
 # Conclusion
 
-Our online experiments results are consistent with behavioural game theory findings, in that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
+Our results show that people can successfully deviate from Nash equilibrium play to exploit deviations from such play by their opponents.
+Moreover, people can transfer knowledge about the limitations of their opponents to new situations.
+This transfer of a model of the opponent depends on the similarity between the prior and new game, as well as the sophistication of the opponent.
+Transfer is better to similar games, and for less sophisticated agents.
+Within games, we found evidence for a switch from a more reasoning-based strategy which allows for between-game transfer, to a more habitual strategy which does not.
+This is consistent with a rational trade-off between the goal of maximising performance and minimizing the cost of computing the best possible actions.
+
+<!--
+
+online experiments results are consistent with behavioural game theory findings, in that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
 Moreover, we showed that participants transfer their learning to new games with varying degrees of similarity.
@@
 \newpage
+-->
 

### 2021-07-05 Report/paper_draft_2021.tex
went through draft

@@
-\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
 \PassOptionsToPackage{hyphens}{url}
@@
 %
-\documentclass[man,floatsintext]{apa6}
+\documentclass[
+  english,
+  man,floatsintext]{apa6}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provides euro and other symbols
-\else % if luatex or xelatex
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
   \usepackage{unicode-math}
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
 }{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
   \IfFileExists{parskip.sty}{%
@@
     \setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
 \usepackage{xcolor}
-\usepackage{hyperref}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
   pdftitle={Transfer of Learned Opponent Models in Zero Sum Games},
-            pdfauthor={Ismail Guennouni~\& Maarten Speekenbrink},
+  pdfauthor={Ismail Guennouni1 \& Maarten Speekenbrink1},
+  pdflang={en-EN},
   colorlinks=true,
@@
   urlcolor=Blue,
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{graphicx,grffile}
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage{graphicx}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
 \ifx\paragraph\undefined\else
@@
 \fi
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-\shorttitle{Upgrade Report}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Department of Experimental Psychology, University College London}
-\usepackage{csquotes}
+% Manuscript styling
 \usepackage{upgreek}
@@
 
+% Table formatting
 \usepackage{longtable}
 \usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
 
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
 \newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
 \makeatletter
@@
 \newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+\shorttitle{Upgrade Report}
+\usepackage{csquotes}
 \shorttitle{}
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
 \title{Transfer of Learned Opponent Models in Zero Sum Games}
-\author{Ismail Guennouni\textsuperscript{1}~\& Maarten Speekenbrink\textsuperscript{1}}
+\author{Ismail Guennouni\textsuperscript{1} \& Maarten Speekenbrink\textsuperscript{1}}
 \date{}
 
-\authornote{
-
-Correspondence concerning this article should be addressed to Ismail Guennouni, Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom.
-E-mail: \href{mailto:i.guennouni.17@ucl.ac.uk}{\nolinkurl{i.guennouni.17@ucl.ac.uk}}}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Experimental Psychology, University College London}
 
@@
 causal models of the environment. One way to build abstract representations of the environment when the task involves interactions with others is to build
-a model of the opponent that may inform what actions they are likely to take next. In this study, we propose to explore opponent modelling and its transfer with the use of
-computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning. Through two differentiated experiments, we find that participants can
-deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it. Moreover, we showed that participants transfer their learning to new games and that
-the transfer is moderated by the level of sophistication of the opponent. Computational modelling shows that it is likely that players start each game using a model-based
-learning strategy that facilitates generalisation and opponent model transfer, but then switch to behaviour that is consistent with a model-free learning strategy in the latter
-stages of the interaction.
-
+a model of the opponent that may inform what actions they are likely to take next. In this study, we explore opponent modelling and its transfer with the use of
+computer agents with human-like limited degrees of iterated reasoning. In two experiments, we find that participants
+deviate from Nash equilibrium play and learn to adapt to the opponent's strategy and exploit it. Moreover, we show that participants transfer their learning to new games and that
+this transfer is moderated by the level of sophistication of the opponent. Computational modelling shows that players start each game with a model-based
+learning strategy that facilitates between-game transfer of the opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
 }
@@
 
-In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to this task.
-The early literature on learning transfer in repeated games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously (Camerer \& Knez, 2000; Ho, Camerer, \& Weigelt, 1998).
-This doesn't allow for the possibility of learning about the opponent's strategy and potentially exploiting it.
+A model of the opponent can help increase performance in a particular game, but learning more general characteristics of an opponent may also help increase performance in other games.
+In this paper, we are specifically interested in the latter: How do people build and use models of their opponent to facilitate learning transfer?
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly useful to address this question.
+The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.~Nash equilibrium play) or use salient actions (e.g.~risk dominance) in later games, having had experience with a similar game environment previously (Camerer \& Knez, 2000; Teck-Hua Ho, Camerer, \& Weigelt, 1998).
+As is well-known, a Nash equilibrium means that all players in a game play such that no-one can unilaterally improve their performance by deviating from their strategy.
+When playing against an opponent with a Nash-optimal strategy, I can do no better than play according to the Nash-equilibrium strategy as well.
+However, when faced with a player who deviates from the Nash-optimal strategy, it may be better for me to exploit this and also deviate from this strategy, increasing my performance beyond what is expected at a Nash equilibrium.
+Of course, this comes with some risk, as my own deviation from Nash-optimal play may leave myself open to similar exploitation.
 
-When studies have specifically explored this aspect, they have used computer opponents that were generally programmed not to change their strategies over the course of the task, allowing better experimental control.
-However, they have mostly looked at the ability of players to detect and exploit action-based learning rules (Shachat \& Swarthout, 2004; Spiliopoulos, 2013).
-The strategies implemented by the computer opponents had a style of play that was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with precision, or at detecting patterns from long sequences of past play.
-Thus, in this study, we aim to explore opponent modelling and its transfer with the use of computer agents endowed with human-like limited degrees of iterated reasoning.
-The agents are either a level-1 or level-2 player, mimicking ``I know that you know that I know'' type reasoning, and the limited recursion depth they exhibit (Goodie, Doshi, \& Young, 2012).
-A level 1 player adapts their play to what they believe their opponent will play, without considering what their opponent might believe they will play.
-A level 2 player, on the other hand, takes their opponent's belief about their actions into account, assuming they face a level 1 player, and choosing actions to beat the actions of that player.
-The choice of this type of strategy is also motivated by evidence that humans strategically use information from last round play of their opponents in zero sum games (Batzilis, Jaffe, Levitt, List, \& Picel, 2016; Wang, Xu, \& Zhou, 2014).
+Studies that focused on whether people can learn to exploit deviations from Nash-equilibrium play have mostly looked at the ability of players to detect and exploit action-based learning rules (Shachat \& Swarthout, 2004; Spiliopoulos, 2013).
+These studies used computer opponents with fixed strategies (no adaptation to their human opponent) consisting of playing each action with a fixed probability (a mixed strategy).
+Findings showed \ldots.
+However, the use of mixed strategies may have limited people's ability to form accurate opponent models.
+Rather than thinking of their opponents and drawing a random action from a (non-uniform) probability distribution, people may rather think of their opponents as applying a form of iterated reasoning to determine their next action.
+The type of reasoning we refer to takes the form of ``I believe that you believe that I believe \ldots'\,' and has been shown to correspond to people's casual introspection (REFERENCE).
+It also underlies successful models in behavioural economics, such as Level-\(k\) and Cognitive Hierarchy models, which posit that people assume their opponent has a limited level of iterative reasoning, with the player best responding to their (modelled) opponent.
 
-We have conducted two experiments where participants interact with a computer opponent.
-In each experiment, we measure transfer of learning about the opponent's strategy between games with varying degrees of similarity.
-The first two games we use are structurally identical except for action labels.
-In the first experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure.
-In the first experiment, participants face the same opponent throughout the three games, and the opponents are randomised to be either level-1 or level-2 players.
-In the second experiment, participants faced both level-1 and level-2 opponent sequentially, with the order in which they are faced randomised across participants.
+In Level-\(k\) theory, a level-0 player uses a fixed strategy without explicitly considering the strategy of their opponent.
+A level-1 player assumes their opponent is a level-0 player, and chooses actions to best respond to the strategy of their opponent, without considering what their opponent might believe that they will play.
+A level-2 player, on the other hand, takes their opponent's belief about their actions into account, assuming they face a level-1 player, and choosing actions to best respond to the actions of that player.
+Cognitive Hierarchy theory works on similar principles, but rather than assuming an opponent always adopts a particular level-\(k\) strategy, they assume their opponent adopts each pf the level-\(k\) strategies with a particular probability (i.e., the strategy is a mixture over pure level-\(k\) strategies).
 
-\newpage
+Iterative reasoniing strategies can explain non-equilibrium play in a range of games, such as \ldots{} In the present study, we endow our computer opponents with limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
+In two experiments, participants face the same opponent (Experiment 1) or same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, a structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
+To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of the opponent and the similarity of the games.
+Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a morehabiltual and cognitively less demanding strategy in the later stages of the games.
 
@@
 \section{Experiment 1}\label{experiment-1}}
+
+In the first experiment, we \ldots. {[}intro to first exp{]}
 
@@
 The Fire-Water-Grass (FWG) game is identical to RPS in all but action labels: Fire burns grass, water extinguishes fire, and grass absorbs water.
-We use this game as we are interested in whether learning is transferred in a fundamentally similar game where the only difference is in the description of the possible actions.
-This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level 1 or 2 player.
-Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'', as might be learned by a simple reinforcement learning algorithm, will not be able to generalize to such a game, as these contingencies are tied to the labels of the actions.
-The numbers game is a generalization of RPS.
+We use this game as we are interested in whether learning is transferred in a fundamentally similar game where the only difference is in the name of the possible actions.
+This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level-1 or level-2 player.
+Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'\,', is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
+The Numbers game is a generalization of RPS.
 In the variant we use, 2 participants concurrently pick a number between 1 and 5.
@@
 All other possible combinations of choices are considered ties.
-Similar to RPS and FWG, the mixed-strategy Nash equilibrium is to play each action with equal probability in a random way.
+Similar to RPS and FWG, the mixed-strategy Nash equilibrium is to randomly play each action with equal probability.
 
 The computer opponent was programmed to use either a level-1 or level-2 strategy in all the games.
-A level 1 player is defined as a player who best responds to a level 0 player.
-A level 0 player plays in a non-strategic way and does not consider their opponent's actions.
-Here, we assume a level 0 player simply repeats their previous action.
-There are other ways to define a level 0 player.
-For instance, as repeating their action if it resulted in a win, and choosing randomly from the remaining actions otherwise.
-As a best response to a random action is itself a random action, defining a level 0 player in such a way would make a level 1 opponent's strategy much harder to discern.
-Because we are mainly interested in generalization of knowledge of an opponent's strategy to other games, which rests on good knowledge of this strategy, we opted for this more deterministic formulation of a level 0 player (whilst also introducing some randomness in the computer opponent's play).
+A level-1 player is defined as a player who best responds to a level-0 player.
+A level-0 player plays in a non-strategic way and does not consider their opponent's actions.
+Here, we assume a level-0 player simply repeats their previous action.
+There are other ways to define a level-0 player.
+For instance, as repeating their action if it resulted in a win and choosing randomly from the remaining actions otherwise, or choosing randomly from all actions.
+As a best response to a uniformly random action is itself a random action, defining a level-0 player in such a way would make a level-1 opponent's strategy much harder to discern.
+Because we are mainly interested in generalization of knowledge of an opponent's strategy to other games, which rests on good knowledge of this strategy, we opted for this more deterministic formulation of a level-0 player (whilst also introducing some randomness in the computer opponent's play).
 A level-2 computer opponent, will assume in turn that the participant is a level-1 opponent, playing according to the strategy just described.
 We also introduced some noise over the actions of computer opponents making them play randomly in 10\% of all trials.
+Note that at all levels, the strategies are contingent on the actions taken in the previous round.
+The choice of this type of strategy is consistent with evidence that humans strategically use information from last round play of their opponents in zero sum games (Batzilis, Jaffe, Levitt, List, \& Picel, 2016; Wang, Xu, \& Zhou, 2014).
 
@@
 Participants were informed they would play three different games against the same computer opponent.
-Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
+Participants were told that the opponent cannot cheat and will choose its actions simultaneously with them, without prior knowledge of the participant's choice.
 After providing informed consent and reading the instructions, participants answered a number of comprehension questions.
-They then played the three games against their opponent in the order RPS, FGW, and NUMBERS.
+They then played the three games against their opponent in the order RPS, FGW, and Numbers.
+An example of the interface for the RPS game is provided in Figure~\ref{fig:feedback-rps-exp2}.
+On each round, tHe human player chooses an action, and after a random delay, is shown the action chosen by the computer opponent, and the outcome of that round.
+A history of the chosen actions over all rounds is available in the centre panel.
 A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
@@
 Each point is worth £0.02.
-An example of the interface for the RPS game is provided in Figure~\ref{fig:feedback-rps-exp2}.
-After playing all the games, participants were asked questions about their beliefs about the computer opponent, related to whether they think they have learned their strategy and how hard they found playing against that particular opponent.
+After playing all the games, participants were asked questions about their beliefs about the computer opponent, related to whether they thought they learned their opponent's strategy, and how difficult they found playing against their particular opponent.
 They were then debriefed and thanked for their participation.
@@
 
-{\centering \includegraphics{images/feedback_rps}
+{\centering \includegraphics[width=3.13in]{images/feedback_rps}
 
@@
 
-\caption{Screenshot of the feedback at the end of a round of Rock-Paper-Scissors}\label{fig:feedback-rps-exp2}
+\caption{Screenshot of the Rock-Paper-Scissors game in Experiment 2.
+Shown here is the feedback stage, after both the human (left) and computer (right) players have chosen their action.
+The interface was similar in Experiment 1, but excluded the history of game play in the center panel.}\label{fig:feedback-rps-exp2}
 \end{figure}
@@
 
-\caption{Boxplot of scores per game across conditions}\label{fig:exp1-avg-scores-game}
+\caption{Performance per game and block across conditions in Experiment 1.
+Points are scores of individual participants and boxes reflect the 95\% confidence intervals of the mean (center line equals the mean).}\label{fig:exp1-avg-scores-game}
 \end{figure}
 
-On average, participants obtained the lowest score in the RPS game (\(M = 0.289\), \(SD = 0.348\)), followed by NUMBERS (\(M = 0.31\), \(SD = 0.347\)).
+On average, participants obtained the lowest score in the RPS game (\(M = 0.289\), \(SD = 0.348\)), followed by Numbers (\(M = 0.31\), \(SD = 0.347\)).
 Participants' performance was highest in the FWG game (\(M = 0.454\), \(SD = 0.354\)).
-Scores in each game were significantly different from 0, the expected score of random play (RPS: \(t(51) = 7.26\), \(p < .001\); FWG: \(t(51) = 10.04\) , \(p < .001\); NUMBERS: \(t(51) = 7.17\), \(p < .001\)).
-To assess learning within and between games, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants.
+Scores in each game were significantly different from 0, the expected score of uniformly random play (RPS: \(t(51) = 7.26\), \(p < .001\); FWG: \(t(51) = 10.04\) , \(p < .001\); Numbers: \(t(51) = 7.17\), \(p < .001\)).
+As uniformly random play is the Nash equilibrium, this indicates successful deviation from a Nash-optimal strategy.
+
+To assess learning within and between games, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants.
 This showed a main effect of Game (\(F(2,100) = 8.54\), \(\eta^{2} = 0.05\), \(p < .001\)), indicating that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game (\(t(100) =3.78\), \(p < .001\)) and the NUMBERS game (\(t(100) = 3.32\) , \(p = .002\)).
-The score in RPS was not significantly different from the score in NUMBERS (\(t(100) = 0.45\) , \(p = .65\)).
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game (\(t(100) =3.78\), \(p < .001\)) and the Numbers game (\(t(100) = 3.32\) , \(p = .002\)).
+The score in RPS was not significantly different from the score in Numbers (\(t(100) = 0.45\) , \(p = .65\)).
 The main effect of Block (\(F(1,50) = 22.51\) , \(\eta^{2} = 0.03\), \(p < .001\)) shows that the score in the first half of each game (\(M = 0.29\)) was significantly lower than in the second half (\(M = 0.40\)), which indicates within-game learning.
@@
 Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
+\textbf{MS: Need to check test results and report GG degrees of freedom, etc.}
 
@@
 
-As a measure for learning transfer, we focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game (see Figure \ref{fig:exp1-score-by-opp}).
+As a measure for learning transfer, we focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game (see Figure \ref{fig:exp1-early-score-by-opp}).
 We exclude the very first round as the computer opponent plays randomly here and there is no opportunity yet for the human player to exploit their opponent's strategy.
@@
 The FWG early score score is significantly higher than 0 (\(t(148.85) = 4.584\), \(p < .001\)).
-This is also the case for the NUMBERS game (\(t(148.85) = 3.00\), \(p = .009\)).
+This is also the case for the Numbers game (\(t(148.85) = 3.00\), \(p = .009\)).
 We did not expect positive scores for the RPS game, as it was the first game played and there was no opportunity for learning about the opponent's strategy.
@@
 
-\caption{Mean and standard error of early scores by game and opponent}\label{fig:exp1-early-score-by-opp}
+\caption{\label{ref:figure4-caption}Performance in early rounds (2-6) per game and block across conditions in Experiment 1.
+Points are scores of individual participants and boxes reflect the 95\% confidence intervals of the mean (center line equals the mean).}\label{fig:exp1-early-score-by-opp}
 \end{figure}
@@
 Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-We expected better transfer between more similar games (i.e.~better transfer from RPS to FWG than from RPS/FWG to NUMBERS), and worse transfer for the more sophisticated level 2 agent.
-Figure\textasciitilde{}\ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 players.
-To explore this, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game (\(F(2,92) = 3.35\), \(\eta^{2} = 0.04\), \(p < .04\)).
+We expected better transfer between more similar games (i.e.~better transfer from RPS to FWG than from RPS/FWG to Numbers), and worse transfer for the more sophisticated level 2 agent.
+Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents.
+To explore this, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants.
+There was a main effect of Game (\(F(1.84,91.77) = 3.35\), \(\eta^{2} = 0.04\), \(p = .043\), Greenhouse-Geisser correction to degrees of freedom applied to correct for non-sphericity).
 We then run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( \(t(150) = 3.96\), \(p < .001\)) and NUMBERS (\(t(150) = 3.74\), \(p < .001\)).
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player (\(t(150) = 2.48\), \(p = .01\)) but not to the dissimilar game of NUMBERS.
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG (\(t(150) = 3.96\), \(p < .001\)) and Numbers (\(t(150) = 3.74\), \(p < .001\)).
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player (\(t(150) = 2.48\), \(p = .01\)) but not to the dissimilar game of Numbers.
 
-\hypertarget{experiment-1-discussion}{%
-\subsubsection{Experiment 1 discussion:}\label{experiment-1-discussion}}
+\hypertarget{discussion}{%
+\subsubsection{Discussion}\label{discussion}}
 
-These results indicate that learning transfer to the more dissimilar game (NUMBERS) we found earlier is exclusively driven by level-1 facing players, as average early round scores in the NUMBERS game of level-2 facing players are close to 0.
-Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar FWG game, but only those facing the less sophisticated opponent are able to generalise to the less similar NUMBERS game.
+The results of Experiment 1 indicate that participants were able to learn successful strategies which exploited the deviation from Nash-optimal play of their opponents.
+Moreover, they were able to transfer knowledge about their opponent to other games, but this was moderated by the type of game and opponent.
+There was evidence of transfer from the RPS game to the similar FWG game for both opponents.
+However, transfer to the dissimilar Numbers game was only evident for participants facing a level-1 opponent.
 
@@
 
-We ran a second experiment with various differentiated features to improve the opportunity to measure learning transfer.
-Instead of making participants face either the level-1 or level-2 player throughout, we made them face both opponents sequentially.
-Because there were two distinct opponents, requiring potentially holding two opponent models in memory, we also made it easier to recall the results of past rounds by providing participants with the opportunity to see the history of the game since the beginning of each interaction.
-Figure~\ref{fig:feedback-rps-exp2} shows an example of showing interaction history in the RPS game.
-Finally, we changed the third game to a penalty shootout game, whith participants aiming to score a goal and opponents playing the role of goal keepers.
-Whilst this game has the same number of actions as the first two, it is strategically dissimilar.
-Unlike the third game in the first experiment, it did not have a cyclical hierarchy between actions, making it harder to win by just following simple heuristics leveraging this cyclicality.
-If we see evidence for differential play against opponents, it would show participants adapting their strategies to the opponent they are facing, which is indicative of opponent modelling.
+In Experiment 2, we aimed to obtain a stronger test of learning transfer.
+Instead of facing a single level-1 or level-2 opponent throughout all games, participants face both types of opponents sequentially in this experiment.
+To perform well against both opponents, participants would need to learn distinct strategies in each game.
+To reduce effects of increased memory load due to facing distinct opponents, we provided participants access to the history of play against an opponent within each game (see Figure \ref{fig:feedback-rps-exp2}).
+Finally, we changed the third game to a penalty shootout game, with participants aiming to score a goal and opponents playing the role of goal keepers.
+Whilst this game has the same number of actions as the first two (aim left, center, or right), it is strategically dissimilar.
+Unlike the Numbers game in Experiment 1, the Shootout game does not have a cyclical hierarchy between actions, making it harder to win through a heuristic based on this cyclicity.
 
@@
 Figure~\ref{fig:screenshot-shootout} shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose \enquote{'right}' in the next round, we can win by both choosing \enquote{'left}' and \enquote{'center}'.
-A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
-As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
+What makes this game different to the other games is that there are two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend `'right'' in the next round, they can win by either choosing to shoot `'left'' or `'center''.
+A level-1 shooter who thinks that their goalkeeper opponent will repeat their last action has thus two possible best responses.
+A level-1 goalkeeper, however, has only a single best response (defending where their opponent aimed in the last round).
+A level-2 goalkeeper, who believes their opponent is a level-1 shooter, will have two best responses however.
+We programmed the level-2 computer player to choose randomly between these two best responses.
 
@@
 
-{\centering \includegraphics{images/shootout}
+{\centering \includegraphics[width=6.4in]{images/shootout}
 
@@
 
-The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had an adjusted average score in between the two (M = 0.289, SD = 0.326).\footnote{A higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
+Participants scores are depicted in Figure \ref{fig:exp2-score-by-opp}.
+The RPS game had the lowest average score per round (\(M = 0.194\), SD = 0.345) followed by FWG (\(M = 0.27\), SD = 0.394) and finally the Shootout game (\(M = 0.289\), SD = 0.326).\footnote{ A higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
 Indeed, a player not aiming to uncover the opponent's strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33)}.
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, \(p\) \textless{} 0.0001 ; FWG: t(49) = 7.25 , \(p\) \textless{} 0.0001 ; Shootout: t(49) = 13.61, \(p\) \textless{} 0.0001 ).
-Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
-We perform a two (condition: level-1 first, level-2 first) by two ( opponent type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
+To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33)} Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: \(t(49) = 6.26\), \(p < .001\); FWG: \(t(49) = 7.25\), \(p < .001\); Shootout: \(t(49) = 13.61\), \(p < .001\)).
 
-\begin{figure}
-
-{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-score-by-opp-1}
-
-}
-
-\caption{Boxplot of scores per game and interaction by opponent type}\label{fig:exp2-score-by-opp}
-\end{figure}
-
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, \(\eta^{2}\) = 0.04, p \textless{} .0001).
-To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
-We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the Shootout game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
-There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
-There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,\(\eta^{2}\) = 0.02, p = .01).
-Figure~\ref{fig:exp2-score-by-opp} shows boxplots of game scores, averaged across participants, by game and opponent type.
-We also distinguish between scores from the first time the players faced the opponent (first interaction) and the second time they did (second interaction).
-We see that when facing level-1 agents, scores increase steadily after each game, with FWG score significantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG ( t(191) = 3.05, p = 0.01).
+To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA on the average score per round, with the first factor varying between participants.
+This shows a main effect of Game (\(F(1.85,88.7) = 11.81\), \(\eta^{2} = 0.04\), \(p < .001\)).
+Post-hoc pairwise comparisons between games (p-values adjusted using Holm method for multiple comparisons) indicate performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (\(t(96) =2.53\), \(p = .025\)), and performance in the Shootout game significantly higher than in FWG (\(t(96) = 2.32\), \(p = .025\)).
+Whilst the ANOVA shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type (\(F(1.7, 81.82) = 5.31\) ,\(\eta^{2} = 0.02\), \(p = .01\)).
+Follow-up analysis shows that when facing level-1 agents, scores increase steadily after each game, with FWG score significantly higher than RPS (\(t(191) = 2.70\), \(p = .03\)) and Shootout scores in turn significantly higher than FWG (\(t(191) = 3.05\), \(p = .01\)).
 There was no significant difference between average scores on any two games when facing level-2 agents however.
@@
 
-As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random.
-
 \begin{figure}
 
-{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-early-scores-1}
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-early-score-by-opp-1}
 
@@
 
-\caption{Mean and standard error of early scores by game and opponent for experiment 2}\label{fig:exp2-early-scores}
+\caption{\label{ref:figure4-caption}Performance in early rounds (2-6) per game and opponent in Experiment 2.
+Points are scores of individual participants and boxes reflect the 95\% confidence intervals of the mean (center line equals the mean).}\label{fig:exp2-early-score-by-opp}
 \end{figure}
 
-In Figure~\ref{fig:exp2-early-scores}, we show the average score across participants and its \(95\) percent confidence interval in rounds 2-6 of the first interaction with the opponent for each game.
-These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
-For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
-(Level-1 opponent: FWG: t(270) = 4.99, p \textless{} 0.0001; Shootout: t(270) = 6.66, p \textless{} 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p \textless{} 0.0001; Shootout: t(270) = 3.21, p =0.004 ).
+As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random (Figure~\ref{fig:exp2-early-scores}).
+For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types (Level-1 opponent: FWG: \(t(270) = 4.99\), \(p < .001\); Shootout: \(t(270) = 6.66\), \(p < .001\); Level-2 opponent: FWG: \(t(270) = 4.40\), \(p < .001\); Shootout: \(t(270) = 3.21\), \(p=.004\)).
+\textbf{MS: Should also report ANOVA, as for Experiment 1}
 
-\hypertarget{experiment-2-discussion}{%
-\subsubsection{Experiment 2 discussion:}\label{experiment-2-discussion}}
+\hypertarget{discussion-1}{%
+\subsubsection{Discussion}\label{discussion-1}}
+
+The results of Experiment 2\ldots{} \textbf{MS: give summary of main findings, as done for Experiment 1.
+You should not report new statistical tests in the discussion, which should go in the results section before.}
 
@@
 The other models adapted their play to the opponent, either by reinforcing successful actions in each game (reinforcement learning), or by determining the type of opponent through Bayesian learning (Bayesian Cognitive Hierarchy models).
-We also include the Expected Weighted Attraction (EWA), which is a popular model in behavioral economics.
+We also include the Expected Weighted Attraction (EWA) model, which is a popular model in behavioural economics.
 
-We use the following notation.
-In each game \(g \in \{\text{RPS},\text{FWG}, \text{NUMBERS}\}\), on each trial \(t\), the participant chooses an action \(a_t \in \mathcal{A}_g\), and the opponent chooses action \(o_t \in \mathcal{A}_g\), where \(\mathcal{A}_g\) is the set of allowed actions in game \(g\), e.g.
-\(\mathcal{A}_\text{RPS} = \{R,P,S\}\).
+In the following, we will describe the models in more detail, and provide some intuition into how they they learn about the game and/or the opponent.
+We use the following notation: In each game \(g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}\), on each trial \(t\), the participant chooses an action \(a_t \in \mathcal{A}_g\), and the opponent chooses action \(o_t \in \mathcal{A}_g\), where \(\mathcal{A}_g\) is the set of allowed actions in game \(g\), e.g.~\(\mathcal{A}_\text{RPS} = \{R,P,S\}\).
 The participant then receives reward \(r_t \in \{1,0,-1\}\), and the opponent receives \(-r_t\).
 We use the state variable \(s_t = \{a_{t-1},o_{t-1}\}\) to denote the actions taken in the previous round \(t-1\) by the participant and opponent.
-
-In the following, we will describe the models in more detail, and provide some intuition into how they they learn about the game and/or the opponent.
 
@@
 Since the computer players in this experiment based their play on the actions in the previous round, a suitable RL model for this situation is one which learns the value of actions contingent on plays in the previous round, i.e.~by defining the state \(s_{t}\) as above.
-The resulting RL model learns a Q value (Watkins \& Dayan, 1992) for each state-action pair:
+The resulting RL model learns a \(Q\)-value (Watkins \& Dayan, 1992) for each state-action pair:
+\[ Q_{t+1}(s_{t},a_{t}) = Q_{t}(s_{t},a_{t}) + \alpha \left( r_{t}  - Q(s_{t},a_{t}) \right) ,\]\\
+where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), and \(\alpha \in [0,1]\) the learning rate.
+For instance, \(Q_t(\{R,S\},P)\) denotes the value of taking action `'Paper'' this round if the player's last action was `'Rock'' and the opponent played `'Scissors''.
+Actions are taken according to a softmax rule:
+\[P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}, \]
+where the inverse temperature parameter \(\lambda\) determines the consistency of the strategu (the higher \(\lambda\), the more often the action with the highest \(Q\)-value is chosen.
+While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different state \(\mathcal{S}_g\) and action space \(\mathcal{A}_g\), and there is no simple way to map states and actions between games.
 
-\[ Q_{t+1}(s_{t},a_{t}) = Q_{t}(s_{t},a_{t}) + \alpha \left( r_{t}  - Q(s_{t},a_{t}) \right) \]
-
-where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), \(\alpha \in [0,1]\) the learning rate.
-For instance, \(Q_t(\{R,S\},P)\) denotes the value of taking action \enquote{'Paper}' this round if the player's last action was \enquote{'Rock}' and the opponent played \enquote{'Scissors}'.
-Actions are taken according to a softmax rule:
-\[P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}\]
-While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different action space \(\mathcal{A}_g\), and there is no simple way to map actions between games.
-
-The RL model has two free parameters: the learning rate (\(\alpha\)) and the inverse temperature parameter of the softmax decision rule (\(\lambda\)).
-We've assumed \(\gamma = 0\) as changes in this parameter didn't affect the other parameter estimations or ultimately the value of the likelihoods.
+The RL model has two free parameters: the learning rate (\(\alpha\)) and the inverse temperature (\(\lambda\)).
 
@@
 
-The self-tuning Experience Weighted Attraction (EWA) model (Ho, Camerer, \& Chong, 2004) combines two seemingly different approaches, namely reinforcement learning and belief learning.
+The self-tuning Experience Weighted Attraction (EWA) model (Teck H.
+Ho, Camerer, \& Chong, 2004) combines two seemingly different approaches, namely reinforcement learning and belief learning.
 Belief learning models are based on the assumption that players keep track of the frequency of past actions and best respond to that.
@@
 The self-tuning EWA model has been shown to perform better than either RL or belief learning alone in various repeated games and has the advantage of having only one free parameter, the inverse temperature of the softmax choice function.
-The EWA model is based on updating ``Attractions'' for each action over time.
+The EWA model is based on updating ``Attractions'\,' for each action over time.
 The attraction of action \(a\) time \(t\) is written \(A_{t}(a)\) and is updated as
-
 \[ A_{t+1}(a) =  \frac{\phi \ N(t) \ A_{t}(a) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} \]
@@
 Unlike reinforcement learning, this uses knowledge of the rules of the game to allow reinforcing actions that were not taken.
-We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play @{[}cheung1994learning{]}.
-While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Ho et al., 2004).
-\$ N(t)\$ represents an experience weights and can be interpreted as the number of \enquote{observation-equivalents} of past experience.
+We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play (Cheung \& Friedman, 1994).
+While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Teck H.
+Ho, Camerer, \& Chong, 2004).
+\(N(t)\) represents an experience weight and can be interpreted as the number of ``observation-equivalents'' of past experience.
 We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
+\textbf{MS: Should describe how the parameters are self-tuned with equations }
 
@@
 The self-tuning EWA has one free parameter: the inverse temperature of the softmax decision rule (\(\lambda\)).
+\textbf{MS: Are there no states in the EWA?
+If not, it is unsurprising that this model doesn't fit well }
 
@@
 They then use observations of the opponents actions to infer a posterior probability of each type:
-\[ P(\text{level}=k | D_{t})  \propto  P(D_{t}|\text{level}=k ) \times P(\text{level}=k)\]
-where \(D_{t} = \{a_1,o_1,\ldots,a_t,o_t\}\) is the data available at time \(t\). The likelihood is defined as
-\[P(D_{t}|\text{level}=k) = \prod_{j=1}^t \left( \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o_j|a_{j-1},o_{j-1})\right)\]
-where \(f_k(o_t|a_{t-1},o_{t-1}) = 1\) if \(o_t\) is the action taken by a level \(k\) player when the previous round play was \(a_{t-1}\) and \(o_{t-1}\), and 0 otherwise.
+\[P(\text{level}=k | \mathcal{D}_{t})  \propto  P(\mathcal{D}_{t}|\text{level}=k ) \times P(\text{level}=k)\]
+where \(\mathcal{D}_{t} = \{s_1,\ldots,s_t\}\) is the data available at time \(t\). The likelihood is defined as
+\[P(\mathcal{D}_{t}|\text{level}=k) = \prod_{j=1}^t \left( \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o_j|s_{j})\right)\]
+where \(f_k(o_t|s_{t}) = 1\) if \(o_t\) is the action taken by a level \(k\) player when the previous round play was \(s_t = (a_{t-1}, o_{t-1})\), and 0 otherwise.
 Note that the likelihood assumes (correctly) that there is a probability \(\theta \in [0,1]\) that the opponent takes a random action.
@@
 We assume a participant chooses an action by using the softmax function over the best response to predicted actions:
-\[\begin{aligned} B_t(a) &= \sum_{k = 0}^2 \sum_{o \in \mathcal{A}_g} b(a,o) P_k(o|a_{t-1},o_{t-1})  P(\text{level}=k|\mathcal{D}_{t-1})\\
-P_t(a) &= \frac{\exp{\lambda B_t(a)}}{\sum_{a' \in \mathcal{A}_g} \exp \lambda B_t(a')} \end{aligned}\]
+\[\begin{aligned} B_t(a) &= \sum_{k = 0}^2 \sum_{o \in \mathcal{A}_g} b(a,o) P_k(o|s_{t})  P(\text{level}=k|\mathcal{D}_{t-1})\\
+P_t(a) &= \frac{\exp\{\lambda B_t(a) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{ \lambda B_t(a')\}} \end{aligned}\]
 where \(b(a,o) = 1\) if action \(a\) is a best response to opponent's action \(o\) (i.e.~it leads to a win), and \(P_k(o|a_{t-1},o_{t-1}) = \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o|a_{t-1},o_{t-1})\) is the probability that a level \(k\) agent takes action \(o\), as also used in the likelihood above.
@@
 Unlike the models above, the BCH model allows for between-game transfer, as knowledge of the level of the opponent can be used to generate predictions in games that have not been played before.
+This generalization is done simply by using the posterior \(P(\text{level} = k|\mathcal{D}_T)\) from the previous game as rhe prior distribution in the next game.
 However, the participant might also assume that the level of reasoning of their opponent does not generalize over games.
+This would mean starting with a ``fresh'' prior \(P(\text{level} = k)\) at the start of each game.
 We hence distinguish between two versions of the BCH model.
@@
 
-In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
-Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
+For both experiments, we fitted all models to individual participant data by maximum likelihood estimation.
+We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
 
-In experiment 1, we fit a total of 5 models: A baseline model assuming random play (Nash), Bayesian Cognitive Hierarchy model allowing transfer betwen games (BCH\_BT) and another with no transfer between games (BCH\_NBT), as well as a Reinforcement Learning model with state space consisting of last round play (RL), and finally a self tuning EWA model with the same state space (EWA).
+For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NBT), as well as a Reinforcement Learning model with state space consisting of last round play (RL), and finally a self-tuning EWA model with the same state space (EWA).
 
-In experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two type of opponent model transfer.
+In Experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two type of opponent model transfer.
 We can have transfer within games, between the first and second interaction with the opponent.
-We can also have transfer between games, as in transfering models of the opponent from RPS to FWG for instance.
-Therefore, we
-give models more flexibility to allow for these two types of transfer.
-As such, for Bayesian Cognitive Hierarchy, we fit a total of three models.
-BCH\_BT allows for between game transfer.
-We assume that if such transfer is possible, then within game transfer should also be possible and therefore this model allows for both types of transfer.
-BCH\_NBT allows for within but no between game transfer.
-Whereas BCH\_NT allows for neither.
-For Reinforcement learning models, because RL models can't account for between game transfer due to change in ation labels, we can only have models allowing for within game transfer (RL Tr) or with no transfer within games (RL NT).
-Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (EWA\_Tr) or without transfer (EWA\_NT).
-Counting the base model wiht random play (Nash) we therefore fit a total of 8 models in experiment 2.
+We can also have transfer between games, as in e.g.~transferring a learned opponent model from RPS to FWG.
+Therefore, we fitted a total of three versions of the Bayesian Cognitive Hierarchy model: BCH\_BT allows for both within and between game transfer (between game transfer without within game transfer is implausible); BCH\_NBT allows for within but not between game transfer; BCH\_NT allows for no transfer within or between games.
+For Reinforcement learning models, because RL models can't account for between game transfer due to change in state and action space, we can only have models that allowing for within game transfer (RL\_TR) or with no transfer within games (RL\_NT).
+Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (EWA\_TR) or without transfer (EWA\_NT).
+Counting the base model with random play (Nash) we therefore fit a total of 8 models for Experiment 2.
 
-\hypertarget{experiment-1-modelling}{%
-\subsection{Experiment 1 modelling :}\label{experiment-1-modelling}}
-
-Figure~\ref{fig:exp1-comp-models} shows the results for experiment 1: We can see that the RL model clearly described most participants' behaviour best, followed by the random (Nash) model.
+Figure~\ref{fig:exp1-comp-models} shows the results for Experiment 1.
+We can see that the RL model clearly described most participants' behaviour best, followed by the random (Nash) model.
 Only a few participants were best described by one of the BCH models, or the EWA model.
 Looking at BIC weights, we confirm this as seen in Figure ~\ref{fig:xp1-BIC-weigths}.
-RL models hve high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, whihc fits the picture drawn by the histogram.
+RL models have high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, which fits the picture drawn by the histogram.
 
@@
 
-\caption{Model BIC weights for participants in experiment 1}\label{fig:xp1-BIC-weigths}
+\caption{Model BIC weights for participants in Experiment 1.}\label{fig:xp1-BIC-weigths}
 \end{figure}
 
-\hypertarget{experiment-2-1}{%
-\subsection{Experiment 2}\label{experiment-2-1}}
-
-In experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that the RL model was again more successful than the Bayesian models in fitting player's action choices.
-In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
-This is also reflected in BIC weights in Figure ~\ref{fig:xp2-BIC-weigths}
+In Experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that the RL model was again more successful than the Bayesian Cognitive Hierarchy models (with or without transfer) in fitting participants' action choices.
+This is also reflected in BIC weights in Figure \ref{fig:xp2-BIC-weigths}.
+\textbf{MS: model labels in Figures should correspond to those in the text}
 
@@
 
-\caption{Model BIC weights for participants in experiment 2}\label{fig:xp2-BIC-weigths}
+\caption{BIC weights for each model and participant in Experiment 2.}\label{fig:xp2-BIC-weigths}
 \end{figure}
@@
 
-The computational modelling indicates that most players are best fit by Q-learning type models with states defined by last round play.
-This is at odds with the findings from the section regarding learning transfer: If indeed most participants use Q-learning with states to choose their actions, then they should not be able to transfer learning to the early rounds of the new game.
-In order to understand better what is going on, we plot the likelihood by trial for each game and each of the three strategies: Q-learning with states, and Bayesian Cognitive Hierarchy models with and without the possibility of across game transfer.
-
-We start with experiment 1 data.
-Figure~\ref{fig:exp1-lik-by-tr} shows that in the later games, the likelihood for the BCH models is higher in the initial rounds in which learning transfer is measured, but that over time, the likelihood of Q-learning model becomes more important and exceeds that of BCH models.
+The computational modelling indicates that most players are best fit by a reinforcement learning which learns good actions conditional upon the last round play.
+This is at odds with the behavioural findings, where we found evidence of transfer in early rounds of each game.
+If indeed most participants adopt a reinforcement learning strategy, they should not be able to transfer their learning to the early rounds of a new game.
+In order to investigate this discrepancy further, we plot the likelihood by trial for each game and three strategies: RL, Bayesian Cognitive Hierarchy models with between-game transfer, and the random (Nash) strategy.
+Figure~\ref{fig:exp1-lik-by-tr} shows that in the later games of Experiment 1, the likelihood for the BCH models is higher than that of the other models in the initial rounds of the games.
+However, over time, the likelihood of the RL model increases and exceeds that of BCH model.
 
@@
 
-Likewise, in experiment 2, we want to understand the dynamic of strategy choice by plotting the likelihood by trial for each strategy, using the optimal parameters found when fitting the model.
-Figure~\ref{fig:exp2-lik-by-tr} shows that, as in experiment 1, BCH models had higher likelihood in the early stages of the second (most similar) game, however the likelihood of Q-learning with states models increases steadily to be the highest in the later stages of all games.
-In the third and more dissimilar game, we get a result that is different from experiment 1.
-In this instance, the likelihoods of the BCH models stay constant and close to their initial values.
+The same pattern holds for Experiment 2 (Figure~\ref{fig:exp2-lik-by-tr}).
+Again, the BCH model with between-game transfer has the highest likelihood in the early stages of the later games (apart from stage 1 of the shootout game, where the RL model is better).
+In later rounds, the likelihood of the RL model exceeds that of the BCH model.
 
@@
 
-The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative of participants switching between strategies as the games progressed.
-Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the BCH based strategies fitted observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.
+The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative that participants switch between strategies as the games progress.
+According to this interpretation, participants base their responses in early rounds on the learned level of their opponents iterative reasoning, switching later to learned actions through reinforcement.
 
-In order to test for the existence of strategy switching in participants' play, we fit Hidden Markov Models in which the latent states are the 3 strategies used (Q-learning with state space consisting of previous round play, BCH based model with opponent model transfer, and a base model consisting of random play consistent with a Nash equilibrium strategy).
-Hidden Markov models are useful tools to explore structure in observed time series.
-They are named as such because of two properties: First, they make the assumption that any observable action at time t results from a process whose state at time t , named \(S_{t}\) is \enquote{hidden} from the observer.
-Second, it also assumes that this hidden process has a Markov property, meaning that given state \(S_{t-1}\), the value of \(S_{t}\) is independent of all states occurring before time \(t-1\).
-We also assume that \(S_{t}\) has a discrete probability distribution in that it take one of K discrete values.
-The model is therefore specified by initial probabilities of being in each state \({1,2,...,K}\) and transition probabilities for moving from state \(i\) to state \(j\).
-These probabilities are fit using observed actions generated from these hidden states.
-
-To investigate the possibility of strategy switching, we fit two different hidden Markov models with the depmixS4 R package.
-In the first model, we allow for a non-nil probability of players transitioning from one state (strategy) to another.
-In the second model, we assume that such switching does not happen, and as such assume implicitly that when players start with a particular strategy, they continue using it throughout the experiment.
-We then compare the likelihoods of each HMM model using a likelihood ratio test.
-
-\hypertarget{experiment-1-1}{%
-\subsubsection{Experiment 1:}\label{experiment-1-1}}
+We use hidden Markov models to more formally test for strategy switching in participants' play.
+In these models, the three strategies (RL, BCH with between-game transfer, and Nash) correspond to latent states which determine the overt responses (actions chosen).
+The models allow for switching between the states over time, and such switches correspond to strategy switches.
+Hidden Markov models assume that an observable action at time \(t\) depends on a latent state at time \(t\).
+Second, it is assumed that the latent state at time \(t\) depends on the latent state at the previous time \(t-1\).
+The model is specified by the state-conditional action distributions (these are provided by the likelihood of the fitted models), an initial state distribution (the distribution over the strategies at the initial round), and the state-transition probabilities (probability of switching from one state/strategy to another).
+Initial state probabilities and the transition probabilities were estimated with the depmixS4 package (Visser \& Speekenbrink, 2010).
+As a statistical test of strategy switching, we compare the hidden Markov model to a constrained version which assumes the probability of switching from one strategy to a different one is 0.
+This model thus assumes that when players start with a particular strategy, they continue using it throughout the experiment.
 
@@
 
-In experiment 1, the HMM model with switching fits significantly better than the non-switching one (\(p < .001\)).
-This is further statistical evidence in favour of the hypothesis that participants switch between strategies.
-In order to understand at which stage of the games the switching might happen, and whether there are any differences between games and type of opponents faced, we plot in Figure~\ref{fig:exp1-posteriors-plot} the average (across participants) posterior probabilities of each state (strategy), as a function of trial and opponent faced.
-The posterior probability is the probability that an observation comes from a component distribution a posteriori, i.e.~given the value of the observation.
-In the first experiment, we can see from the plots of FWG and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the RL model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
-
-\hypertarget{experiment-2-2}{%
-\subsubsection{Experiment 2:}\label{experiment-2-2}}
+In Experiment 1, a likelihood-ratio test shows that the HMM model with switching fits significantly better than the non-switching one (\(p < .001\)).
+\textbf{MS: we should really use a bootstrapped Likelihood Ratio test here } This provides further statistical evidence in favour of the hypothesis that participants switch between strategies.
+Figure~\ref{fig:exp1-posteriors-plot} depicts the average (across participants) posterior probabilities of each state (strategy), as a function of trial and opponent faced.
+As can be seen, there is evidence of strategy switching in the FWG and Numbers games: Initially, participants appear to use a random strategy (in the first round of a game, there is no way to predict the opponent's action), after which the BCH strategy becomes dominant.
+In the later rounds of the games, the RL strategy becomes dominant, however.
 
@@
 
-The switching model in experiment two has also significantly higher likelihood (\(p\) = 0.00).
-On top of indications from looking at the likelihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
-The posterior probability plot in Figure~\ref{fig:exp2-posteriors-plot} shows switching much more clearly across games and stages.
-The switching also seems to happen very early on at the beginning of each game and stage, and is also consistently in the same direction: The probability of Bayesian models with transfer being initially high, then decreasing rapidly while the posterior probability of QL-Learning with states and within transfer learning increases rapidly.
+The switching model in Experiment 2 is also significantly better than the restricted non-switching model (\(p < .001\)).
+The posterior probabilities of the strategies (Figure~\ref{fig:exp2-posteriors-plot}) show very clear evidence of strategy switching across games and stages, from using a BCH model in the initial rounds to an RL strategy later on.
 
-Therefore, HMM modelling shows clear evidence in favour of strategy switching by participants, specifically after a few rounds of play.
-The strategy switching is consistently from BCH models towards Q-learning with states models in both experiments.
+\hypertarget{discussion-2}{%
+\section{Discussion}\label{discussion-2}}
 
-\newpage
+In this study, we investigated human learning transfer across games by making human participants play against computer agents with limited levels of iterated reasoning.
+We were interested whether participants learn about the strategy of their opponent and transfer such knowledge between games, and whether this is modulated by the similarity between games and the sophistication of the agent.
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+The results of our first experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to a similar game.
+Performance in early rounds indicated that transfer to the more dissimilar game was moderated by the degree of sophistication of the opponent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
+In the second experiment, participants faced both types of opponents, which allows for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent within a game.
+In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
+Experiment 2 alsp offers more opportunities to test transfer of a learnt opponent model.
+There were two opportunities to transfer opponent models within each game as well as two opportunities to transfer from each game to the next, giving a total of 6 transfer opportunities.
+\textbf{MS: we did not test transfer at all these points, or did we?} The results on learning transfer confirmed the findings from the first experiment.
+Again, there was clear evidence of transfer in the early rounds of the later games.
+We also found that learning transfer is moderated by the type of opponent faced: Evidence of transfer was weaker for the level-2 opponent as compared to the level-1 opponent.
+That transfer was less evident for the more sophisticated level-2 opponent in both experiments may be due to a higher difficulty of learning that opponent's strategy.
+If it is more difficult to establish a model of the level-2 opponent, there is likely less knowledge to transfer to the new game.
+A player cannot transfer what they have not learnt.
 
-In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies.
-We were interested in exploring whether participants learn about the strategy of their opponent and transfer such knowledge between games, and whether this is modulated by the similarity between games and the sophistication of the agent.
+What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
+what did the players learn specifically about their opponent's strategy and what form did this learning take?
 
-The results of our first experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
-We used results on very early rounds for measuring transfer as they are unlikely to be tainted by any within game learning.
-Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
+One possible answer is that participants learned simple rules based on last round play.
+For instance, ``play scissors whenever my opponent played rock in last round,'' or ``play paper whenever the last round play was either rock or scissors.'' These are the type of strategies that are learned by the model-free reinforcement learning we used in our computational modelling.
+While this strategy fitted participants' actions the best overall, there are at least two reasons why this account is not satisfactory as a complete description of participants' behaviour.
+Firstly, the learned strategies are not transferable to new games.
+There is no simple way to map ``play scissors whenever my opponent played rock in last round'' in the RPS game to ``play grass whenever my opponent played fire in last round.'' Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this.
+Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
+Secondly, a reinforcement learning strategy would fare equally well against the level-1 and level-2 opponent.
+Whilst choosing different actions, the contingency between the state (last round play) and actions is the same for both opponents.
+Yet, we found that participants performed better against the level-1 opponent compared to the level-2 opponent.
+The difference in performance between the two types of opponent indicate that the actions of the more sophisticated level-2 opponent, or the best response to these, were somehow more difficult to predict.
 
-In the second online experiment, there were many more opportunities to test transfer than before: 2 opportunities to transfer opponent models within each game, and a total of three games, which means 6 opportunities to test transfer.
-The results on learning transfer confirmed prior findings from the first experiment.
-While there was no evidence of higher scores across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
-We also found that learning transfer is modulated by the type of opponent faced.
-When the players faced the level-1 opponent, they were able to transfer learning.
-However, when they faced the level-2 opponent, there was weaker evidence for transfer.
-The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with.
-A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
+We are left with two possible explanations: First, it is possible that participants discovered a heuristic that allowed them to beat their opponent without explicitly modelling their strategy, and that this heuristic is transferable to new games.
+Because of the cyclicity in action choices (e.g., rock beats scissors, scissors beats paper, paper beats rock), it is possible to beat a level-2 opponent most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
+This is a rule that wins and is transferable to other games as it does not depend on action labels.
+In the same vein, a heuristic that beats a level-1 player can be stated as ``Choose the action that would have been beaten by my previous action.'' Intuitively, it seems that the heuristic for the level-2 player is simpler than that for the level-1 player, which is at odds with the difference in performance.
 
-Coming back to learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are significantly higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
-The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
-what did the players learn specifically about the opponent strategy and what form did this learning take?
+A second explanation is that participants engaged in iterative reasoning, inferring their opponent's beliefs and countering the resulting actions.
+For instance, this would be reasoning of the form ``My opponent expects me to repeat my last action, choosing an action that would beat my last action.
+Hence, I will choose the action that beats their best response'' or ``My opponent thinks I expect them to repeat their action, hence expecting me to choose the action that beats their last action.
+They will therefore choose the action that beats this one, and hence I should choose the action that beats their best response.'' Beating a level-1 player, in this account, requires being a level-2 player, and beating a level-2 player requires being a level-3 player.
+Intuitively, the additional step of iterative reasoning involved in beating a level-2 player makes the level-3 strategy more demanding and difficult to implement, which is consistent with the lower performance against the level-2 opponent.
 
-We will proceed by considering multiple potential answers to this question.
-A possible hypothesis for learning the opponent's strategy is the use of simple rules based on last round play (for instance, I play scissors whenever opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc\ldots{}).
-Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
-While this approach certainly seemed to be the best fit for many player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
-Indeed, learning the best action in a particular state is not transferable to a new game since the state space is different and there is no single mapping between the state spaces of the initial and latter games.
-These rules would therefore need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
-
-Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, would require many rounds of practice.
-Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
-More specifically, if we assume that participants were using some type of associative learning or relying on spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
-To be sure, if a participant learns to pick say \enquote{scissors} whenever the opponent last picked \enquote{rock}, then the degree of strategic sophistication of the opponent (its level k) should not impact this learning, and we would expect in this case there would be no difference between scores when facing level-1 and level-2 opponents, which is not the case here.
-The fact that the degree of sophistication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
-
-We are left with two possible explanations: First, it is possible that the players have uncovered a heuristic that allows them to beat the opponent without explicitly modelling their strategy, and is robust to transfer.
-Indeed, because of the cyclicality in action choices (e.g : Rock beats Scissors beats Paper beats Rock), it is possible to beat level-2 opponents most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
-This is a rule that wins and is also robust to transfer as it does not depend on action labels and even works in the dissimilar game.
-
-The second explanation of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
-A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
-For instance, the player may think \enquote{My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be}.
-This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
-This type of learning would be deemed \enquote{explicit} in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
+The differences in performance between the two players, coupled with the finding of positive transfer, point to participants engaging in iterative reasoning, and learning something useful about their opponent's limitations in this regard.
+This is the type of learning encapsulated by our Bayesian Cognitive Hierarchy model.
 It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
 Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
-
-Our second experimental design allows us to test whether the first explanation holds.
-Since there is a simple transferable heuristic that works against level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
-Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.
-
-Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first interactions across games and using early rounds analysis.
-Based on our assumptions, we conclude therefore that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the course of learning.
-
-Our computational modelling allowed us to delve deeper into what might be driving the observed learning transfer.
-Initial modelling of observations using all available data seems to indicate that the most likely model was a Q-learning type model.
-However, as we argued above, that would be inconsistent with the evidence for learning transfer.
-Breaking down likelihoods by trial and fitting a hidden Markov model to the data with states being the various strategies that participants are assumed to be using, we showed evidence for within game switching of strategies.
-Participants start the early rounds of a new game acting in a way consistent with a Bayesian Bayesian Cognitive Hierarchy level, which would be accurate and generalisable but computationally expensive.
-However, as trials continue, participants seem to switch to a habitual type of learning (QL-models).
-
-Why is this switching happening?
-We believe that participants show flexibility in their use of learning strategies.
-When a new game is started that is similar to a previously played game with the same opponent, participants need a way to transfer prior knowledge of the opponent and apply it to the new game in order to best respond.
-Adopting a Bayesian model based on BCH achieves the goal of transferring the opponent model and thus coming up with best responses in the early trials.
-However, Bayesian BCH models are computationally expensive and require higher order thinking (I think that you think that I think\ldots{}).
-As such, as the games progresses, they may become burdensome and the higher amount of historical interaction in the new game allows participants to have enough data to start using the cognitively cheaper model-free learning strategies such as Q-learning.
-The preference for less computationally demanding strategies is well established (Wouter Kool, Joseph T.
-McGuire, Zev B.
-Rosen, Matthew M.
-Bovinick, 2011).
-Moreover, the ability to flexibly switch is also consistent with evidence from the literature on learning strategies in humans, showing that they indeed shift between model-based and model-free learning when the environment requires it (Simon \& Daw, 2011).
+\textbf{MS: need to check relevance of these citations.
+Also, they need to be in reference list } We admit that our implementation in the BCH models does not predict a performance difference between the types of opponents.
+Starting with an equal prior belief over the different levels of sophistication, a BCH player would perform equally well against the level-1 and level-2 opponent.
+There are two routes to explain the difference in performance.
+Firstly, prior beliefs might be biased against higher-level opponents (i.e., participants might have believed it is more likely that they would face level-1 opponent than a level-2 opponent).
+Secondly, if the actions of a level-2 opponent are more difficult to predict than those of a level-1 opponent, this might introduce more noise in the likelihood of the opponents actions given their level of sophistication.
+Either of these mechanisms would explain why learning the strategy of the level-2 opponent is more difficult and slower than learning the strategy of the level-1 opponent.
+\textbf{MS: This could be something to implement, actually} Using hidden Markov models, we found evidence of strategy switching between the BCH and RL strategies, and such switching seems more consistent with the latter idea.
+If predicting an opponent's actions through iterative reasoning is cognitively demanding and error-prone, it is resource-rational to switch to less costly yet equally successful strategies when these are available.
+\textbf{MS: add reference to resource-rational approach by Lieder \& Griffiths } Initially, a model-free reinforcement learning strategy will be less successful than an iterative reasoning one.
+However, given enough experience, it will be on par with an iterative reasoning strategy.
+As it involves simple state-action contingencies, a model-free RL strategy may also be computationally less costly, making it overall more effective to rely on this than iterative reasoning.
+This is similar to the arbitration between model-free and model-based RL (Simon \& Daw, 2011) \textbf{MS: add more references here}.
+In repeated and well-practised situations, relying on habits allows one to save cognitive resources for other demands.
+However, when the environment -- or game -- changes, it is prudent to use all available resources to reorient oneself.
 
@@
 
-Our online experiments results are consistent with behavioural game theory findings, in that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
-Moreover, we showed that participants transfer their learning to new games with varying degrees of similarity.
-The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.
-
-Having said that, there remains a high degree of heterogeneity between players.
-There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
-Moreover, the computational modelling shows that it is likely that players start each game using a model-based learning strategy that facilitates generalisation and opponent model transfer, but then switch to behaviour that is consistent with a model-free learning strategy as the experiment goes on.
-This is likely driven by a trade-off between computational complexity and accuracy between model based and model free strategies.
-\newpage
+Our results show that people can successfully deviate from Nash equilibrium play to exploit deviations from such play by their opponents.
+Moreover, people can transfer knowledge about the limitations of their opponents to new situations.
+This transfer of a model of the opponent depends on the similarity between the prior and new game, as well as the sophistication of the opponent.
+Transfer is better to similar games, and for less sophisticated agents.
+Within games, we found evidence for a switch from a more reasoning-based strategy which allows for between-game transfer, to a more habitual strategy which does not.
+This is consistent with a rational trade-off between the goal of maximising performance and minimizing the cost of computing the best possible actions.
 
@@
 \hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-batzilis}{}%
@@
 \leavevmode\hypertarget{ref-camerer1997experience}{}%
-Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
+Camerer, C., Ho, T.-H., \& Others. (1997). \emph{{Experience-weighted attraction learning in games: A unifying approach}}.
 
 \leavevmode\hypertarget{ref-knez2000}{}%
-Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
+Camerer, C., \& Knez, M. (2000). \emph{{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}}.
 
-\leavevmode\hypertarget{ref-goodie2012levels}{}%
-Goodie, A. S., Doshi, P., \& Young, D. L. (2012). Levels of theory-of-mind reasoning in competitive games. \emph{Journal of Behavioral Decision Making}, \emph{25}(1), 95--108.
+\leavevmode\hypertarget{ref-cheung1994learning}{}%
+Cheung, Y.-W., \& Friedman, D. (1994). \emph{{Learning in evolutionary games: some laboratory results}}. University of California, Santa Cruz.
 
 \leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
+Ho, Teck H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{{The economics of learning models: A self-tuning theory of learning in games}}.
 
 \leavevmode\hypertarget{ref-ho1998iterated}{}%
-Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
+Ho, Teck-Hua, Camerer, C., \& Weigelt, K. (1998). {Iterated dominance and iterated best response in experimental" p-beauty contests"}. \emph{The American Economic Review}, \emph{88}(4), 947--969.
 
@@
 (2017).
-Building machines that learn and think like people.
+{Building machines that learn and think like people}.
 \emph{Behavioral and Brain Sciences}, \emph{40}.
@@
 \leavevmode\hypertarget{ref-mertens1990repeated}{}%
-Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+Mertens, J.-F. (1990). {Repeated games}. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
 
 \leavevmode\hypertarget{ref-shachat2004we}{}%
-Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
+Shachat, J., \& Swarthout, J. T. (2004). {Do we detect and exploit mixed strategy play by opponents?} \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
 
@@
 (2011).
-Environmental statistics and the trade-off between model-based and TD learning in humans.
+{Environmental statistics and the trade-off between model-based and TD learning in humans}.
 \emph{Advances in Neural Information Processing Systems 24: 25th Annual Conference on Neural Information Processing Systems 2011, NIPS 2011}, 1--9.
@@
 \leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
-Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
+Spiliopoulos, L. (2013). {Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game}. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
 
 \leavevmode\hypertarget{ref-stahl1995players}{}%
-Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
+Stahl, D. O., \& Wilson, P. W. (1995). {On players models of other players: Theory and experimental evidence}. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
+
+\leavevmode\hypertarget{ref-R-depmixS4}{}%
+Visser, I., \& Speekenbrink, M.
+(2010).
+{depmixS4}: An {R} package for hidden markov models.
+\emph{Journal of Statistical Software}, \emph{36}(7), 1--21.
+Retrieved from \url{http://www.jstatsoft.org/v36/i07/}
 
@@
 \leavevmode\hypertarget{ref-watkins1992q}{}%
-Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
+Watkins, C. J. C. H., \& Dayan, P. (1992). {Q-learning}. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
 
-\leavevmode\hypertarget{ref-Kool_2011}{}%
-Wouter Kool, Joseph T.
-McGuire, Zev B.
-Rosen, Matthew M.
-Bovinick.
-(2011).
-Decision Making and the Avoidance of Cognitive Demand.
-\emph{Experimental Psychology}.
-\url{https://doi.org/10.2996/kmj/1138846322}
-
-\leavevmode\hypertarget{ref-batzilis}{}%
-Batzilis, D., Jaffe, S., Levitt, S., List, J.
-A., \& Picel, J.
-(2016).
-\emph{How facebook can deepen our understanding of behavior in strategic settings: Evidence from a million rock-paper-scissors games}.
-working paper.
-
-\leavevmode\hypertarget{ref-camerer1997experience}{}%
-Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
-
-\leavevmode\hypertarget{ref-knez2000}{}%
-Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
-
-\leavevmode\hypertarget{ref-goodie2012levels}{}%
-Goodie, A. S., Doshi, P., \& Young, D. L. (2012). Levels of theory-of-mind reasoning in competitive games. \emph{Journal of Behavioral Decision Making}, \emph{25}(1), 95--108.
-
-\leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
-
-\leavevmode\hypertarget{ref-ho1998iterated}{}%
-Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
-
-\leavevmode\hypertarget{ref-Lake2017}{}%
-Lake, B.
-M., Ullman, T.
-D., Tenenbaum, J.
-B., \& Gershman, S.
-J.
-(2017).
-Building machines that learn and think like people.
-\emph{Behavioral and Brain Sciences}, \emph{40}.
-\url{https://doi.org/10.1017/S0140525X16001837}
-
-\leavevmode\hypertarget{ref-mertens1990repeated}{}%
-Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
-
-\leavevmode\hypertarget{ref-shachat2004we}{}%
-Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
-
-\leavevmode\hypertarget{ref-Simon_Daw_11}{}%
-Simon, D.
-A., \& Daw, N.
-D.
-(2011).
-Environmental statistics and the trade-off between model-based and TD learning in humans.
-\emph{Advances in Neural Information Processing Systems 24: 25th Annual Conference on Neural Information Processing Systems 2011, NIPS 2011}, 1--9.
-
-\leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
-Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
-
-\leavevmode\hypertarget{ref-stahl1995players}{}%
-Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
-
-\leavevmode\hypertarget{ref-wang2014social}{}%
-Wang, Z., Xu, B., \& Zhou, H.-J. (2014). Social cycling and conditional responses in the rock-paper-scissors game. \emph{Scientific Reports}, \emph{4}(1), 1--7.
-
-\leavevmode\hypertarget{ref-watkins1992q}{}%
-Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
-
-\leavevmode\hypertarget{ref-Kool_2011}{}%
-Wouter Kool, Joseph T.
-McGuire, Zev B.
-Rosen, Matthew M.
-Bovinick.
-(2011).
-Decision Making and the Avoidance of Cognitive Demand.
-\emph{Experimental Psychology}.
-\url{https://doi.org/10.2996/kmj/1138846322}
+\end{CSLReferences}
 

### 2021-08-24 Experiment_2/exp2_clean_analysis.Rmd
checks ismail

---
output:
  html_document: default
  word_document: default
---
--
title: "opponent modelling"
author: "Ismail Guennouni"
date: "18 August 2019"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dat <- read.csv("MyData.csv")
```

```{r}
# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
library(tidyr)
library(dplyr)
library(MASS)
library(ggpubr)
library(PairedData)
library(multcompView)

# transform 'winner' variable in numeric score
dat$score <- recode(dat$winner, human = 1, tie = 0, AI = -1)

# Create a new variable stage.f as a factor for the stages 1,2 ,3 4 in game
dat$stage.f <- factor(dat$stage, labels = c("Stage 1","Stage 2","Stage 3", "Stage 4"),levels=c(1,2,3,4))

# create a new variable "game.f" as a factor variable of games
dat$game.f <- factor(dat$game, labels = c("RPS","FWG","SHOOT"),levels=c("rps","fwg","shootout"))

# overall score to pay bonuses 
dat_score <- dat %>% 
  group_by(prolific_id, condition) %>% 
      summarize(overall_score = sum(score))
dat_score$avg_bonus <- floor(dat_score$overall_score)*0.02

write.csv(dat_score,row.names=FALSE,file="bonus_payment.csv")

#Average bonus per participant 
#bonus_to_be_paid <- mean(dat_score$avg_bonus)

# check num level 1 and level 2 facing players
group_by(dat_score, condition) %>%
  summarise(count_conditions = n()) 
```

```{r}

#Group data by human_id and calculate mean score per stage of each game.
dat$interaction_lvl <- recode(dat$stage, "1" = 1, "2" = 1, "3" = 2, "4" = 2) %>% factor(levels = c(1,2), labels = c("first interaction", "second interaction"))

# Create factor variable that determines type of opponent 
dat$opp_type <- factor(dat$round_condition, labels=c("Level_1", "Level_2"), levels = c("Level1", "Level2"))

# Create factor variable coding condition (which opponent was faced first)
dat$condition.f <- factor(dat$condition, labels = c("lvl_1 first", "lvl_2 first"), levels = c("Level1","Level2"))

#Adjust shootout score tor eflect easier game
dat$adj_score <- recode(dat$score, ifelse(dat$game.f =="SHOOT", dat$score -0.33,dat$score))

# Create summarised dataset by interaction (all of first/second  opponent interactions by game)
dat_int <- dat %>% 
  group_by(human_id,game.f,opp_type,interaction_lvl,condition.f) %>% 
  summarize(int_score = mean(adj_score))

write.csv(dat, file = "dat_exp2.csv")
write.csv(dat_int, file = "dat_int_exp2.csv")
```

```{r}

# correlation between score vs levels 1 and 2

dat_opps <- dat_int %>%
  group_by(human_id, opp_type) %>%
  summarize(opp_score = mean(int_score))

data_opps_wide <- spread(dat_opps,opp_type, opp_score)

ggscatter(data_opps_wide, x = "Level_1", y = "Level_2", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "scores against Level1", ylab = "scores against Level2")

# Create summarised dataset by stage
dat_stages <- dat %>% 
  group_by(human_id,game.f,stage.f,opp_type) %>% 
  summarize(stage_score = mean(adj_score))

# Group data by game and ID
dat_games <- group_by(dat, human_id,game.f) %>% summarise(game_score = mean(adj_score))
# head(dat3,6)

# Subsetting scores data by game
rps <- subset(dat_games,  game.f == "RPS",game_score)
fwg <- subset(dat_games,  game.f == "FWG",game_score)
shoot <- subset(dat_games,  game.f == "SHOOT",game_score)
# head(rps,6)
```

```{r}
# Look at some summary statistics of group means #############################

group_by(dat_int, game.f) %>%
  summarise(
    mean = mean(int_score, na.rm = TRUE),
    sd = sd(int_score, na.rm = TRUE)
  )

group_by(dat_int, game.f, opp_type,interaction_lvl) %>%
  summarise(
    count = n(),
    mean = mean(int_score, na.rm = TRUE),
    sd = sd(int_score, na.rm = TRUE)
  )
```

```{r}
# PLOTS  #############################

# Plot scores per game

#ggboxplot(dat_games, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average score per round", xlab = "Games")

#ggerrorplot(dat_games, x = "game.f", y = "game_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average score per round", xlab = "Games")

```

```{r}
# Plot paired scores between games
#ggpaired(dat3, x = "game.f", y = "game_score",color = "game.f", id = "human_id", line.color = "gray", line.size = 0.4, palette = "npg")

# Plot results by game and stage (for all 3 games, learning is happening) 
#ggboxplot(dat_stages, x = "game.f", y = "stage_score", palette = c("#00AFBB", "#E7B800","#FC4E07"), order = c("RPS", "FWG","SHOOT"), fill="game.f", ylab = "Percentage score", xlab = "Games")
```

```{r}

# Group data by game, condition and ID
#dat4 <- group_by(dat_block, human_id,condition,game.f) %>% summarise(game_score = mean(block_opp_score))
#ggerrorplot(dat4, x = "game.f", y = "game_score", desc_stat = "mean_ci" , palette =c("#00AFBB","#E7B800","#FC4E07"),color = "game.f", ylab = "Game score", xlab = "Games")

# Facing Level 2 first is harder than facing level 1 first?
#ggboxplot(dat2, x = "condition", y = "stage_score", palette = c("#00AFBB", "#E7B800"), fill="condition",ylab = "Percentage score", xlab = "Conditions")

#ggerrorplot(dat2, x = "condition", y = "stage_score", desc_stat = "mean_ci" , palette = c("#00AFBB", "#E7B800"), color="condition",ylab = "Percentage score", xlab = "Conditions")

# Main effect of Stage
#ggerrorplot(dat2, x = "stage", y = "stage_score", desc_stat = "mean_ci" , palette = c("blue", "red", "purple", "orange"), color="stage",ylab = "Percentage score", xlab = "stage")

# Breaking it down by game (seems to be true for RPS and FWG, less so for Numbers )
#ggboxplot(dat4, x = "game.f", y = "game_score", palette = c("#00AFBB","#E7B800","#FC4E07"),order = c("RPS", "FWG","SHOOT"), ylab = "Game Score", xlab = "Conditions")

```

```{r}
# Testing score against hypothesis of random play  ######################################

# Normality of scores 
shapiro.test(dat_games$game_score)

# Testing Scores against random play (expected 0 average score)
t.test(as.numeric(rps$game_score), mu = 0, alternative = "two.sided")
t.test(as.numeric(fwg$game_score), mu = 0, alternative = "two.sided")
t.test(as.numeric(shoot$game_score), mu = 0, alternative = "two.sided")

```

```{r}
# AFEX PACKAGE FOR RUNNING RM ANOVA AND POST HOC TESTS ############################
#citation(package = "afex", lib.loc = NULL, auto = NULL)
library(afex)
a1 <- aov_car(int_score ~ game.f*interaction_lvl*condition.f*opp_type + Error(human_id/(game.f*interaction_lvl*opp_type)), dat_int)
summary(a1)

(a1_nice <- nice(a1, es = attr(a1$anova_table, "es"),
  observed = attr(a1$anova_table, "observed"),
  correction = attr(a1$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(a1$anova_table,
  "p_adjust_method"), sig_symbols = attr(a1$anova_table, "sig_symbols")))

write.table(a1_nice,file = "a1.txt", sep = ",", quote = FALSE, row.names = F)

## Note to Self: no need to worry abour the HF warning. You don't have pb with sphericity according to Mauchly tests, and the warning only applies to Huynh-Feldt corrections for violations of sphericity. 
```

```{r}
#Pair waise comparison and post hoc tests for the interactions
library(lsmeans)

# game score differences statistically significant? by opponent type?
(ls0 <- lsmeans(a1, "game.f", by = "opp_type"))
(ls0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))

# Interaction effect by game for within game learning 
(ls01 <- lsmeans(a1, "game.f", by = "interaction_lvl"))
(lsm01 <- update(pairs(ls01, reverse = TRUE), by=NULL, adjust = "holm"))
lsmip(a1, game.f ~ interaction_lvl |opp_type)

# Pairwise comparison of first halves by game ( first interaction RPS vs first interaction WFG scores....)
(ls1 <- lsmeans(a1, "opp_type", by="game.f"))
(lsm1 <- update(pairs(ls1, reverse = TRUE), by=NULL, adjust = "holm"))
#plot(lsm1,by="opp_type")

#Pairwise comparison of each game score by block (first opponent RPS vs second opponent RPS....) + Control for family wise error:
(ls2 <- lsmeans(a1, c("interaction_lvl","game.f"), by="opp_type"))

# Test differences  between first and second ineractions by game and opponent type
(contr_g1_12 <- contrast(ls2, list(G1_I1vsG1_I2 = c(-1,1,0,0,0,0))))
(contr_g2_12 <- contrast(ls2, list(G2_I1vsG2_I2 = c(0,0,-1,1,0,0))))
(contr_g3_12 <- contrast(ls2, list(G3_I1vsG3_I2 = c(-1,1,0,0,0,0))))

# Learning transfer: compare first interaction by game and type of opponent 
(contr4 <- contrast(ls2, list(G1_I1vsG2_I1 = c(-1,0,1,0,0,0))))
(contr5 <- contrast(ls2, list(G3_I1vsG2_I1 = c(0,0,-1,0,1,0))))
(contr6 <- contrast(ls2, list(G3_I1vsG1_I1 = c(-1,0,0,0,1,0))))

#plots
lsmip(a1, interaction_lvl ~ game.f)
lsmip(a1, interaction_lvl ~ game.f| opp_type)

# Pairwise comparison of scores facing the two types of players by game: 
#lsc <- lsmeans(a1, "condition", by="game.f")
#(lsmc <- update(pairs(lsc), by=NULL, adjust = "holm"))
#plot(lsmc,by="game.f")
#lsmip(a1, condition ~ game.f)

```

```{r}
#Pair waise comparison and post hoc tests : Game by Block and Condition
dat_s12 = subset(dat, (stage < 3 ), drop =TRUE)
dat_S12 <- dat_s12 %>% 
  group_by(human_id,stage,condition,game.f) %>% 
      summarise(avg_score_12 = mean(score))
a2 <- aov_car( avg_score_12 ~ game.f*stage*condition + Error(human_id/(game.f*stage)), dat_S12)

#library(multcompView)
#use cld to check for comparison pairs belonging to same group, meaning not significantly different from each other...
#cld(lsm4)

#plots
ls4 <- lsmeans(a2, "stage",c("condition","game.f"))

#(lsm4 <- update(pairs(ls4, reverse = TRUE), by=NULL, adjust = "holm"))
#plot(lsm4,by="game.f")

lsmip(a2, stage ~ game.f )

# Interaction plot of game and block by condition 
lsmip(a2, stage ~ game.f | condition)
lsmip(a2, condition ~ stage * game.f)
```

```{r}
# Transfer harder for level2 opponent than when facing level 1 opponent? 
# learning to specifiy contrasts - 
# the below compares the score on each block and game for each type and tells me which scores belong to same group
# the idea is that if transfer is harder vs lvl2 player, then fwg first half score for lvl2 facing player should be sig lower than fwg first-half score vs lvl1 agent.not the case here as thye belong to same group.

(means.int <- lsmeans(a1, specs = c("game.f","stage"), by="condition"))

# Transfer level1: compare FWG_S1 and SHOOT_S1 with RPS_S1 
con1  <- contrast(means.int, list(G1_S1vsG2_S1 = c(-1,1,0,0,0,0,0,0,0,0,0,0), G3_S1vsG1_S1=c(-1,0,1,0,0,0,0,0,0,0,0,0)))
summary(con1, adjust = "holm")

# Transfer level1: compare FWG_S2 and SHOOT_S1 with RPS_S2 
#con2  <- contrast(means.int, list(G1_S2vsG2_S2 = c(0,0,0,-1,1,0,0,0,0,0,0,0), G3_S1vsG1_S1=c(0,0,0,-1,0,1,0,0,0,0,0,0)))
#summary(con2, adjust = "holm")

# Transfer level2: compare H1FWG with H1RPS 
#con2  <- contrast(means.int, list(H1_G2vsH1_G1forlvl2 = c(0,0,0,0,0,0,-1,1,0,0,0,0), #H1_G3vsH1_G1forlvl2=c(0,0,0,0,0,0,-1,0,1,0,0,0)))
#summary(con2, adjust = "holm")

# compare first half (H1) scores between level 1 and level 2 players in FWG and NUM
#con3 <- contrast(means.int, list(G1vG2forH1 = c(0,1,0,0,0,0,0,-1,0,0,0,0), G2vG3forh1=c(0,0,1,0,0,0,0,0,-1,0,0,0)))
#summary(con3, adjust ="holm")

# Within game learning harder for level2 opponent than when facing level 1 opponent? compare differences between block for each game and type
#con4 <- contrast(means.int, list(L2vL1forRPS = c(1,0,0,-1,0,0,-1,0,0,1,0,0), L2vL1forFWG=c(0,1,0,0,-1,0,0,-1,0,0,1,0), L2vL1forNUM=c(0,0,1,0,0,-1,0,0,-1,0,0,1)))
#summary(con4, adjust ="holm")

```

```{r}
# Only looking at withing game learning (3vs 1 and 4vs 2 in each game)

dat_within13 <- subset(dat_stages,(stage.f == 1 | stage.f == 3 ), drop =TRUE) %>%      
  group_by(human_id,stage.f,condition,game.f) %>% 
      summarise(first_int_score = mean(stage_score))

a1vs3 <- aov_car( first_int_score ~ game.f*stage*condition + Error(human_id/(game.f*stage)), dat_within13)

ls1_3 <- lsmeans(a1vs3, c("stage","game.f"), by = NULL)
(lsm1_3 <- update(pairs(ls1_3, reverse = TRUE), by=NULL, adjust = "holm"))
lsmip(a1vs3, game.f ~ stage)

# Now  stage 2 vs 4
dat_within24 <- subset(dat,(stage == 2 | stage == 4 ), drop =TRUE) %>%      
  group_by(human_id,stage,condition,game.f,stage) %>% 
      summarise(first_int_score = mean(score))

a2vs4 <- aov_car( first_int_score ~ game.f*stage*condition + Error(human_id/(game.f*stage)), dat_within24)

ls2_4 <- lsmeans(a2vs4, c("stage","game.f"), by="condition")
lsmip(a2vs4, game.f ~ stage)

```

```{r}

#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########

dat_26 <- subset(dat,(round >1 & round < 7) & (interaction_lvl == "first interaction" ), drop =TRUE)

dat2_6 <- dat_26 %>% 
  group_by(human_id,condition.f,game.f,opp_type,confidence,difficulty) %>% 
      summarise(early_score = mean(adj_score))

# Check group means and SDs
group_by(dat2_6, game.f) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
group_by(dat2_6, game.f,opp_type) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
# plot scores per game 
ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Score", xlab = "Games") 
```

```{r}
# testing differences between early scores across games 
library(afex)

aov_early <- aov_car(early_score ~ game.f*opp_type*condition.f + Error(human_id/(game.f*opp_type)),data=dat2_6)
summary(aov_early)

(aov_ear_nice <- nice(aov_early, es = attr(aov_early$anova_table, "es"),
  observed = attr(aov_early$anova_table, "observed"),
  correction = attr(aov_early$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(aov_early$anova_table,
  "p_adjust_method"), sig_symbols = attr(aov_early$anova_table, "sig_symbols")))

write.table(aov_ear_nice,file = "aov_ear.txt", sep = ",", quote = FALSE, row.names = F)

# Post hoc analyses : Checking early score by opponent and game 
(ls4 <- lsmeans(aov_early, "game.f", by="opp_type"))
(summary(ls4, infer = c(TRUE,TRUE), null = 0,level = 0.95, adjust = "bon"))

lsmip(aov_early,  opp_type ~ game.f )
lsmip(aov_early,  opp_type ~ game.f | condition.f)

```

```{r}
(means.int2 <- lsmeans(aov_early, specs = c("game.f","opp_type")))
(trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "none",ref=c("FWG","SHOOT")))
(contr26 <- contrast(means.int2, list(G2L1vsG2L2 = c(0,1,0,0,-1,0))))

write.table(format(trans26, digits=2),file = "trans26.txt", sep = ",", quote = FALSE, row.names = F)

# compare early scores in FWG for lvl 1 and lvl2 / same for NUM
contrast(means.int2, list(L1vL2fwg = c(0,1,0,0,-1,0), L1vL2shoot=c(0,0,1,0,0,-1)))

# Plot interactions for early rouns, condition by game
lsmip(aov_early, stage ~ game.f | condition )

# plots overall effect by game :
ggboxplot(dat2_6,"game.f", "early_score", fill = "game.f",palette = c("#00AFBB", "#E7B800", "#FC4E07"),order = c("RPS","FWG","SHOOT"))

# Note to Self: possible future work exstension is to pick the guys who scored highly on the first rounds of the second game and fit the various learning models to them only. 
# Two ways to test learning: compare first half between games for different conditions 
# compare early score between games for different conditions 
# Check whteher confidence and difficulty  -> add them as covariates in big anova and early score anova *confidence*difficulty.... --> too hard to interpret

# do a model comparison with model without confidence and difficulty -> start witn ANCOVA (try and see what happens with various interactions).  
```

```{r}
# adding confidence and difficulty feedback 
datcd <- dat %>% 
  group_by(human_id,condition,confidence,difficulty) %>% 
      summarise(avg_score = mean(score))

# testing conf, diff and score for normality 
shapiro.test(datcd$avg_score)
shapiro.test(datcd$confidence)
shapiro.test(datcd$difficulty)

# histograms 
hist(datcd$confidence, breaks = 20)
hist(datcd$difficulty, breaks=10)

# descriptive stats 
group_by(datcd, condition) %>%
  summarise(
    count = n(),
    median = median(confidence, na.rm = TRUE),
    IQR = IQR(confidence, na.rm = TRUE)
  )

group_by(datcd, condition) %>%
  summarise(
    count = n(),
    median = median(difficulty, na.rm = TRUE),
    IQR = IQR(difficulty, na.rm = TRUE)
  )
# Comparing confidence and difficulty by condition
(res1 <- wilcox.test(confidence ~ condition, data = datcd,exact = FALSE))
(res2 <- wilcox.test(difficulty ~ condition, data = datcd,exact = FALSE))

# Correlation confidence difficulty and score: 
mat <- as.matrix(datcd[,unlist(lapply(datcd, is.numeric))])
cor.test(datcd$confidence, datcd$avg_score, method="spearman")
cor.test(datcd$difficulty, datcd$avg_score, method="spearman")

# Transforming confidence into 4 lvl factor
datcd$confidence.f <- factor(as.numeric(cut(datcd$confidence,2)),labels =c("low conf","high conf"))
summary(datcd$confidence.f)
table(datcd$confidence.f,datcd$condition)

#  explore interaction block confidence
#(lsm7 <- lsmeans(acd, c("confidence.f","block")))
#(update(pairs(lsm7, reverse = TRUE, adjust = "holm"), by=NULL))
#plot(lsm7, by ="confidence.f")
#lsmip(acd, confidence.f ~ block)

#
#(lsm8 <- lsmeans(acd, c("confidence.f","block","game.f")))
#lsmip(acd, confidence.f ~ block*game.f)
# checking that low confidence NUMBERS play is not different from random play
#con3 <- contrast(lsm8, list(G1vG2forconf = c(0,0,0,0,0,0,0,0,0,0,1,0)))
#summary(con3, adjust ="holm")

# low and high confidence players have similar initial score in RPS
#con4 <- contrast(lsm8, list(HCvLCforRPS = c(-1,1,0,0,0,0,0,0,0,0,0,0)))
#summary(con4, adjust="holm")
```

```{r}
# ANCOVA with confidence as covariate 
dat_ancova <- dat %>% 
  group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 
      summarise(avg_score = mean(score))
# Centering variables for ANCOVA 
dat_ancova$conf_cen <- scale(dat_ancova$confidence, center=TRUE, scale=FALSE) 
dat_ancova$diff_cen <- scale(dat_ancova$difficulty, center=TRUE, scale=FALSE)

# run RM anova using afex library (ran anova including difficulty as well but wasn't significant)
library(afex)
acd <- aov_car( avg_score ~ game.f*block*condition + conf_cen + diff_cen + Error(human_id/(game.f*block)), factorize = FALSE,dat_ancova)
summary(acd)

nice(acd, es = attr(acd$anova_table, "es"),
  observed = attr(acd$anova_table, "observed"),
  correction = attr(acd$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(acd$anova_table,
  "p_adjust_method"), sig_symbols = attr(acd$anova_table, "sig_symbols"))

# post hoc tests
(anc1 <- lsmeans(acd, c("conf_cen")))

(lsm6 <- lsmeans(acd, c("conf_cen","condition")))
update(pairs(lsm6, reverse = TRUE, adjust = "holm"), by=NULL)
plot(lsm6, by ="condition")
plot(lsm6, by ="conf_cen")
lsmip(acd, conf_cen ~ condition)

```

```{r}
library(dplyr)

```

```{r}

# transform data by differencing two consecutive scores, filter for first and second transfer 
library(dplyr)
dat_test1 <- dat %>% 
  group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 
      summarise(avg_score = mean(score)) %>%
         group_by(human_id) %>%
            mutate(diff_score = avg_score - lag(avg_score, default = 0)) %>%
              mutate(learn_phase =c("init RPS","within RPS","transfer 1","within WFG","transfer 2","within MOD"))

head(dat_test1)        
# define dataset with first transfer only 
dat_trans1 <- dat_test1 %>%
  filter (learn_phase == "transfer 1") %>%
    select(-c(game.f,block,avg_score,learn_phase))

head(dat_trans1)
# Data of transfer as difference between RPS_H2 and FWG_H1 is normally distributed
shapiro.test(dat_trans1$diff_score)

# Regression transfer score on condition and confidence
summary(lm(diff_score~ confidence + difficulty + factor(condition)+confidence*factor(condition), data = dat_trans1))

# tets hypothesis diff_score = 0 (transfer) against alternative it is negative -> No transfer
t.test( dat_trans1$diff_score, mu = 0 ,alternative = "less")

# To be sure.... Compare means of two condition 
t.test(dat_trans1$diff_score ~ condition, data = dat_trans1,exact = FALSE)

#DOING THE SAME FOR TRANSFER 2 :

dat_trans2 <- dat_test1 %>%
  filter (learn_phase == "transfer 2") %>%
    select(-c(game.f,block,avg_score,learn_phase))

# Regression transfer score on condition and confidence -> no effects 
summary(lm(diff_score~ confidence + difficulty + factor(condition) + confidence*factor(condition), data = dat_trans2))
```

```{r}
# Does confidence moderate transfer ?
# Looking at early rounds only as proxy for transfer 
dat_fwg <- dat2_6 %>%
  filter (game.f == "FWG")
dat_num <- dat2_6 %>%
  filter (game.f == "NUM")

# correlation confidence and transfer as proxied by score in early rounds : 
shapiro.test(dat_fwg$confidence)
cor.test(dat_fwg$confidence, dat_fwg$early_score, method="spearman")
cor.test(dat_num$confidence, dat_num$early_score, method="spearman")

# model explaining early scores in fwg by confidene and condition -> no effects 
summary(lm(early_score ~ confidence*condition, data=dat_fwg))
summary(lm(early_score ~ confidence*condition, data=dat_num))

```

```{r}
# checking whether theta changes between games

# lvl1 opponent 
bic <- read.csv("BIC_result.csv")
head(bic)

dat_lvl1 <- bic %>%
  select(c(id,condition,level2_3_theta1,level2_3_theta2,level2_3_theta3)) %>%
    gather(key = game, value = theta,-c(id,condition)) %>%
      group_by(id)
dat_lvl1$games <- factor(dat_lvl1$game, labels=c("RPS","FWG","MOD"),levels=c("level2_3_theta1","level2_3_theta2","level2_3_theta3"))

library(afex)
aov2 <- aov_car( theta ~ games + Error(id/(games)), dat_lvl1)
summary(aov2)

table2 <- nice(aov2, es = attr(aov2$anova_table, "es"),
  observed = attr(aov2$anova_table, "observed"),
  correction = attr(aov2$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(aov2$anova_table,
  "p_adjust_method"), sig_symbols = attr(aov2$anova_table, "sig_symbols"))

kable(table2)

dat_lvl1 %>% 
  group_by(games) %>%
  summarise(theta.m = mean(theta),
            SD = sd(theta, na.rm =TRUE ))

#plot 
ggerrorplot(dat_lvl1, x = "games", y = "theta", group = 1, color="games", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","MOD"), ylab = "Theta", xlab = "Games")

# lvl2 opponent 
dat_lvl2 <- bic %>%
  select(c(id,condition,level3_3_theta1,level3_3_theta2,level3_3_theta3)) %>%
    gather(key = game, value = theta,-c(id,condition)) %>%
      group_by(id)
dat_lvl2$games <- factor(dat_lvl2$game, labels=c("RPS","FWG","MOD"),levels=c("level3_3_theta1","level3_3_theta2","level3_3_theta3"))

# anova
aov3 <- aov_car( theta ~ games + Error(id/(games)), dat_lvl2)
summary(aov3)

table3 <- nice(aov3, es = attr(aov3$anova_table, "es"),
  observed = attr(aov3$anova_table, "observed"),
  correction = attr(aov3$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(aov3$anova_table,
  "p_adjust_method"), sig_symbols = attr(aov3$anova_table, "sig_symbols"))

kable(table3)

# mean comparison
dat_lvl2 %>% 
  group_by(games) %>%
  summarise(theta.m = mean(theta),
            SD = sd(theta, na.rm =TRUE ))

require(gridExtra)
#plot lvl1 
plot1 <- ggerrorplot(dat_lvl1, x = "games", y = "theta", group = 1, color="games", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","MOD"), ylab = "Theta", xlab = "Games")
#plot lvl2
plot2 <- ggerrorplot(dat_lvl2, x = "games", y = "theta", group = 1, color="games", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","MOD"), ylab = "Theta", xlab = "Games")

grid.arrange(plot1, plot2, ncol=2)

```

### 2021-08-24 Report/paper_draft_2021.Rmd
checks ismail

@@
 In this paper, we are specifically interested in the latter: How do people build and use models of their opponent to facilitate learning transfer?
-<!-- when engaged in situations involving an interaction with strategic considerations.--> Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly useful to address this question.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly useful to address this question.
 The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.
@@
 
-<!-- his doesn't allow for the possibility of learning about the opponent's strategy and potentially exploiting it. !-->
-
 Studies that focused on whether people can learn to exploit deviations from Nash-equilibrium play have mostly looked at the ability of players to detect and exploit action-based learning rules [@spiliopoulos2013strategic; @shachat2004we].
-These studies used computer opponents with fixed strategies (no adaptation to their human opponent) consisting of playing each action with a fixed probability (a mixed strategy).
-Findings showed ....
+These studies used computer opponents that don't adapt play to their human opponent, mostly consisting of playing each action with a fixed probability (a mixed strategy).
+Findings showed that humans are capable of adapting to non-Nash equilibrium play and detect patterns in opponent's history of play.
 However, the use of mixed strategies may have limited people's ability to form accurate opponent models.
 Rather than thinking of their opponents and drawing a random action from a (non-uniform) probability distribution, people may rather think of their opponents as applying a form of iterated reasoning to determine their next action.
-The type of reasoning we refer to takes the form of ``I believe that you believe that I believe ...'' and has been shown to correspond to people's casual introspection (REFERENCE).
-It also underlies successful models in behavioural economics, such as Level-$k$ and Cognitive Hierarchy models, which posit that people assume their opponent has a limited level of iterative reasoning, with the player best responding to their (modelled) opponent.
+The type of reasoning we refer to takes the form of ``I believe that you believe that I believe ...'' and has been shown to underlie people's decision in the context of economic games [@camerer2003behavioural;@costa2001cognition].
+It also underlies successful models in behavioural economics, such as Level-$k$ and Cognitive Hierarchy models [@camerer2004cognitive], which posit that people assume their opponent has a limited level of iterative reasoning, with the player best responding to their (modelled) opponent.
 
@@
 
-Iterative reasoniing strategies can explain non-equilibrium play in a range of games, such as ...
+Iterative reasoning strategies can explain non-equilibrium play in a range of games, such as the p beauty contest game [@nagel1995unraveling], dominance solvable games [@camerer2004cognitive] and various standard normal form games [@costa2001cognition].
 In the present study, we endow our computer opponents with limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
@@
 To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of the opponent and the similarity of the games.
-Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a morehabiltual and cognitively less demanding strategy in the later stages of the games.
-
-<!--
-with that were generally programmed not to change their strategies over the course of the task, allowing better experimental control.
-However, they have mostly looked at the ability of players to detect and exploit action-based learning rules [@spiliopoulos2013strategic; @shachat2004we].
-The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with precision, or at detecting patterns from long sequences of past play.
-Thus, in this study, we aim to explore opponent modelling and its transfer with the use of computer agents endowed with human-like limited degrees of iterated reasoning.
-The agents are either a level-1 or level-2 player, mimicking ``I know that you know that I know'' type reasoning, and the limited recursion depth they exhibit [@goodie2012levels].
-A level 1 player adapts their play to what they believe their opponent will play, without considering what their opponent might believe they will play.
-A level 2 player, on the other hand, takes their opponent's belief about their actions into account, assuming they face a level 1 player, and choosing actions to beat the actions of that player.
-The choice of this type of strategy is also motivated by evidence that humans strategically use information from last round play of their opponents in zero sum games [@batzilis; @wang2014social].
-
-We have conducted two experiments where participants interact with a computer opponent.
-In each experiment, we measure transfer of learning about the opponent's strategy between games with varying degrees of similarity.
-The first two games we use are structurally identical except for action labels.
-In the first experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure.
-In the first experiment, participants face the same opponent throughout the three games, and the opponents are randomised to be either level-1 or level-2 players.
-In the second experiment, participants faced both level-1 and level-2 opponent sequentially, with the order in which they are faced randomised across participants.
-
-<!-- Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
-Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
-More formally, @perkins1992transfer define transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
-This typically human skill has so far eluded modern AI agents.
-Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
-Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-@Lake2017 argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
--->
-
-<!-- One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
-Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations.
-This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
-There is evidence that people learn models of their opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
-In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind [@premack1978does] abilities play a role in determining human behaviour.
-In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
-More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to the task of opponent modelling.
--->
-
-<!-- Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
-For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
-They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-@knez2000 test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
-They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
-They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity.
-If the games were only strategically similar, then the transfer was much weaker.
--->
-
-<!-- @Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
-However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games Cooper & Kagel [-@cooper2003lessons; -@Cooper2008] found that participants who have learned to play according to a Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
-They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of a different payoff structure on an opponent's actions.
--->
-
-<!-- In exploring opponent modelling and learning transfer, most studies adopted two types of opponents in the experimental setting.
-Either human participants were matched with other participants or they played against a computer algorithm.
-Computer opponents were generally programmed not to change their strategies over the course of the task, allowing better experimental control.
-One of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision, or at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities.
-@simon1972theories explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally complex problems such as finding Nash equilibria.
-Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in 'level-k' theory, first adopted by @stahl1995players.
-It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogeneous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment @arad201211.
-Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
-Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below, and so on.
--->
-
-<!-- In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will either be a level-1 or level-2 player, mimicking human theory of mind abilities and the limited recursion depth they exhibit [@goodie2012levels].
-Our choice of using computer opponents instead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-When playing against other human opponents, players are learning about the game as well as trying to infer the potential dynamic strategy of the opponent simultaneously.
-Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
-The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
-For instance, @spiliopoulos2013strategic made humans play constant sum games against 3 computer opponents, designed to take advantage of known patterns in human play such as imperfect randomization and heuristics use.
-He found that human participants do adapt to the opponent they are facing.
-@shachat2004we made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations of the opponent from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
--->
+Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a more habiltual and cognitively less demanding strategy in the later stages of the games.
 
@@
 
-In the first experiment, we .... [intro to first exp]
+In the first experiment, we aim to test learning transfer through making participants face the same computer opponent in three sequential games that vary in similarity.
 
@@
 ### Tasks
-In the first experiment, participants played the three games against their computer opponent.
+
+Participants played the three games against their computer opponent.
 These games were rock-paper-scissors, fire-water-grass, and the numbers game.
@@
 This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level-1 or level-2 player.
-Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'', <!-- as might be learned by a simple reinforcement learning algorithm,--> is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
+Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'', is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
+
 The Numbers game is a generalization of RPS.
@@
 An example of the interface for the RPS game is provided in Figure\ \@ref(fig:feedback-rps-exp2).
-On each round, tHe human player chooses an action, and after a random delay, is shown the action chosen by the computer opponent, and the outcome of that round.
+On each round, the human player chooses an action, and after a random delay, is shown the action chosen by the computer opponent, and the outcome of that round.
 A history of the chosen actions over all rounds is available in the centre panel.
@@
 
-<!-- Participants played 3 games sequentially against the same computer opponent.
-The computer opponent either used a level-1 or level-2 strategy.
-Participants were informed they would play three different games against the same computer opponent.
-Each participant plays all three games consecutively and in the same order described above.
-Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
-A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
-The score was calculated as the number of wins minus the number of losses.
-Ties did not affect the score.
-In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-Each point is worth £0.02.
-An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps-exp2).
--->
-
 ```{r feedback-rps-exp2, fig.cap = "Screenshot of the Rock-Paper-Scissors game in Experiment 2.
@@
 Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
-**MS: Need to check test results and report GG degrees of freedom, etc.**
-
-<!-- Looking at the aggregate scores (See Figure\ \@ref(fig:exp1-avg-scores-game) ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
-Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, $p$ < 0.001 ;  FWG:  t(51) = 10.04 , $p$ < 0.001 ; NUMBERS: t(51) = 7.17, $p$ < 0.001).
--->
-<!-- To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game (F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game (t(100) =3.78, p = 0.0008), and the performance in the NUMBERS game was significantly lower than FWG game (t(100) = -3.32 , p = 0.0024).
-The score in RPS was not significantly different from the score in NUMBERS (t(100) = 0.45 , p = 0.65).
-The main effect of Block (F(1,50) = 22.51 , p < .001, $\eta^{2}$ = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning.
-The main effect of Condition (F(1,50) = 5.44, p = .024, $\eta^{2}$ = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
-This indicates that it was harder for participants, on average, to exploit the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
--->
+**MS: Need to check test results and report GG degrees of freedom, etc.** **...IG: I thought GG corrections only apply when there is violation of sphericity....
+according to Mauchly Test there isn't a violation here.
+Should we report them anyway in this experiment?
+**
 
@@
 
-<!-- Finally, the analysis showed a significant block by game interaction ( F(2,100) = 6.92 , p = .002, $\eta^{2}$ = 0.02), indicating that within-game learning differed between the games.
-Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p <.0001), while there was no significant difference between block scores for the other two games.
-This is indicative of the significant within-game learning happening in the first game when players have no experience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some experience playing against the opponent and start with higher scores indicative of transfer.
-There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88, p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent.
-For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than against level-1 opponent.
-The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
--->
-
 ### Learning transfer
-
-<!-- As a measure for learning transfer, we focus on participants’ scores in the first 5 rounds excluding the initial round (rounds 2-6).
-We exclude the very first round as the computer opponent plays randomly here and there is no opportunity yet for the human player to exploit their opponent's strategy.
-A group of players with no experience of the game are expected to perform at chance level over the early rounds of a new game, as was the case in RPS.
-Positive scores in the early rounds would therefore reflect generalization of prior experience.
-For the FWG game, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
-This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
-For the RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
--->
 
@@
 
-<!-- Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-Figure\ \@ref(fig:exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players as well as the $95$ percent confidence interval for the mean.
-Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
-To explore this, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p < 0.001) and NUMBERS (t(150) = 3.74, p < 0.001) .
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
--->
-
 Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
@@
 However, transfer to the dissimilar Numbers game was only evident for participants facing a level-1 opponent.
-<!-- These results indicate that learning transfer to the more dissimilar game (NUMBERS) we found earlier is exclusively driven by level-1 facing players, as average early round scores in the NUMBERS game of level-2 facing players are close to 0.
-Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar FWG game, but only those facing the less sophisticated opponent are able to generalise to the less similar NUMBERS game.
--->
 
@@
 
-<!-- ### Discussion Experiment 1  -->
-
-<!-- Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game.
-Therefore, both participants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
--->
-
 # Experiment 2
@@
 In Experiment 2, we aimed to obtain a stronger test of learning transfer.
-<!-- We ran a second experiment with various differentiated features to improve the opportunity to measure learning transfer.--> Instead of facing a single level-1 or level-2 opponent throughout all games, participants face both types of opponents sequentially in this experiment.
+Instead of facing a single level-1 or level-2 opponent throughout all games, participants face both types of opponents sequentially in this experiment.
 To perform well against both opponents, participants would need to learn distinct strategies in each game.
@@
 Unlike the Numbers game in Experiment 1, the Shootout game does not have a cyclical hierarchy between actions, making it harder to win through a heuristic based on this cyclicity.
-
-<!-- Because there were two distinct opponents, requiring potentially holding two opponent models in memory, we also made it easier to recall the results of past rounds by providing participants with the opportunity to see the history of the game since the beginning of each interaction.
-Figure\ \@ref(fig:feedback-rps-exp2) shows an example of showing interaction history in the RPS game.
-Finally, we changed the third game to a penalty shootout game, whith participants aiming to score a goal and opponents playing the role of goal keepers.
-Whilst this game has the same number of actions as the first two, it is strategically dissimilar.
-Unlike the third game in the first experiment, it did not have a cyclical hierarchy between actions, making it harder to win by just following simple heuristics leveraging this cyclicality.
-If we see evidence for differential play against opponents, it would show participants adapting their strategies to the opponent they are facing, which is indicative of opponent modelling.
--->
 
@@
 
-```{r exp2-score-by-opp, include= FALSE, fig.cap = "\\label{fig:exp2-score-by-opp}Performance per game and interaction across opponents in Experiment 2.
+```{r exp2-score-by-opp, fig.cap = "\\label{fig:exp2-score-by-opp}Performance per game and interaction across opponents in Experiment 2.
 Points are scores of individual participants and boxes reflect the 95\\% confidence intervals of the mean (center line equals the mean).", fig.align = "center", fig.width=8, fig.height=4}
+
 # Plot results by game and block (for all 3 games, learning is happening) 
@@
 
-To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA on the average score per round, with the first factor varying between participants.
-This shows a main effect of Game ($F(1.85,88.7) = 11.81$, $\eta^{2} = 0.04$,  $p < .001$).
+To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA, with the first factor varying between participants.
+This showed a main effect of Game ($F(1.85,88.7) = 11.81$, $\eta^{2} = 0.04$,  $p < .001$).
 Post-hoc pairwise comparisons between games (p-values adjusted using Holm method for multiple comparisons) indicate performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS ($t(96) =2.53$, $p = .025$), and performance in the Shootout game significantly higher than in FWG ($t(96) = 2.32$, $p = .025$).
@@
 There was no significant difference between average scores on any two games when facing level-2 agents however.
-
-<!--Figure\ \@ref(fig:exp2-score-by-opp) shows boxplots of game scores, averaged across participants, by game and opponent type.
-We also distinguish between scores from the first time the players faced the opponent (first interaction) and the second time they did (second interaction).
-We see that when facing level-1 agents, scores increase steadily after each game, with FWG score significantly higher than RPS ($t(191) = 2.70$, $p = .03$) and Shootout scores in turn significantly higher than FWG  ($t(191) = 3.05$, $p = .01$).
-There was no significant difference between average scores on any two games when facing level-2 agents however.
--->
 
@@
 
-As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random (Figure\ \@ref(fig:exp2-early-scores)).
-For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types (Level-1 opponent: FWG: $t(270) = 4.99$, $p < .001$; Shootout: $t(270) = 6.66$, $p < .001$; Level-2 opponent: FWG: $t(270) = 4.40$, $p < .001$; Shootout: $t(270) = 3.21$, $p=.004$).
-**MS: Should also report ANOVA, as for Experiment 1**
+To measure transfer between games, we again focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with the opponent (see Figure \ref{fig:exp2-early-score-by-opp}).
+We performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) repeated-measures ANOVA, with the first factor varying between participants.
+This showed a main effect of Game ($F(1.94,92.98) = 7.67$, $\eta^{2} = 0.04$,  $p < .001$).
+We then run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(271) = 4.99$, $p < .001$) and Shootout ($t(271) = 6.66$, $p < .001$).
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ($t(271) = 4.41$, $p < .001$).
+Unike in experiment 1, there is also evidence of transfer to the dissimilar game of Shootout ($t(271) = 3.22$, $p = .004$).
+The early round scores in the similar FWG games for level-1 and level-2 facing players are not significantly different from each other.
+However, the score of the players facing the level-1 opponent in Shootout is higher than that of players facing level-2 opponents ( $t(144) = 2.45$, $p = 0.01$).
 
@@
 
-The results of Experiment 2...
-**MS: give summary of main findings, as done for Experiment 1.
-You should not report new statistical tests in the discussion, which should go in the results section before.**
-
-Looking at learning transfer by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
-Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
-These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
+The results of Experiment 2 confirm the earlier results of Experiment 1 about players adapting their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
+Knowledge about both types of opponents were transfered to both the similar and dissimilar game.
+However, transfer to the dissimilar game was easier when facing the more sophisticated agent.
 
@@
 The self-tuning EWA model has been shown to perform better than either RL or belief learning alone in various repeated games and has the advantage of having only one free parameter, the inverse temperature of the softmax choice function.
-The EWA model is based on updating ``Attractions'' for each action over time.
-The attraction of action $a$ time $t$ is written $A_{t}(a)$ and is updated as
-$$ A_{t+1}(a) =  \frac{\phi \ N(t) \ A_{t}(a) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} $$
+The EWA model is based on updating ``Attractions'' for each action over time given a particular state.
+The attraction of action $a$ at time $t$ given state $s$ composet of lkast round play is written $A_{t}(a, s)$ and is updated as
+$$ A_{t+1}(a,s) =  \frac{\phi \ N(t) \ A_{t}(a,s) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} $$
 where $I(x)$ is an indicator function which takes the value 1 is its argument is true, and 0 otherwise, and $R(a,o_t)$ is the reward that would be obtained from playing action $a$ against opponent action $o_t$, which equals the actual obtained reward when $a = a_t$, and otherwise is a counterfactual reward that would have been obtained if a different action were taken.
@@
 We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
-**MS: Should describe how the parameters are self-tuned with equations **
+For details on how the various parameters are self-tuned, please refer to [@ho2004economics].
+**MS: Should describe how the parameters are self-tuned with equations.
+IG: There are many equations for each of the parameters update, phi, delta and N...I'm concerned it would make for cumbersome reading, especially since EWA doesn't really fit well anyway.
+I've added that details of updates can be found in original camerer paper.**
 
 As in the models above, actions are chosen based on a softmax decision rule:
-$$P_t(a) = \frac{\exp \{\lambda  A_{t}(a) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a') \} }$$
+$$P_t(a,s) = \frac{\exp \{\lambda  A_{t}(a,s) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a',s) \} }$$
 The self-tuning EWA has one free parameter: the inverse temperature of the softmax decision rule ($\lambda$).
-**MS: Are there no states in the EWA?
-If not, it is unsurprising that this model doesn't fit well **
 
@@
 --> This is also reflected in BIC weights in Figure \@ref(fig:xp2-BIC-weigths).
-**MS: model labels in Figures should correspond to those in the text**
 
@@
 
-exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Nash","BCH BT","BCH NBT", "BCH NT", "RL NT","RL Tr","EWA NT","EWA Tr")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])
+exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Nash","BCH_BT","BCH_NBT", "BCH_NT", "RL_NT","RL_TR","EWA_NT","EWA_TR")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])
 
@@
         args.legend=list( # positioning of legend box 
-        x  = 15,
+        x  = 12,
         y  = 10,
@@
 exp2_BIC_weights[,2:ncol(exp2_comp_BICs)] <- t(apply(exp2_comp_BICs[,-1], 1, function(i) exp(-0.5*(i-min(i)) )))
-colnames(exp2_BIC_weights) <- c("ID","Nash","BCH BT","BCH NBT", "BCH NT", "RL NT","RL Tr","EWA NT","EWA Tr")
+colnames(exp2_BIC_weights) <- c("ID","Nash","BCH_BT","BCH_NBT", "BCH_NT", "RL_NT","RL_TR","EWA_NT","EWA_TR")
 exp2_BIC_weights[,-1] <- t(apply(exp2_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
@@
 ```
+
 ```{r, include= FALSE}
@@
 ```
-```{r exp1-lik-by-tr, fig.cap = "Experiment 1 Likelihood by trial by game and opponent faced", fig.align='center'}
+
+```{r exp1-lik-by-tr, fig.cap = "Experiment 1 Likelihood by trial, game and opponent faced", fig.align='center'}
 # make sure the different games are ordered in the way they were played
@@
 
-```{r exp2-lik-by-tr, fig.cap = "Experiment2 likelihood by trial by game and opponent faced", fig.align ='center'}
+```{r exp2-lik-by-tr, fig.cap = "Experiment2 likelihood by trial, game and opponent faced", fig.align ='center'}
 # make sure the different games are ordered in the way they were played
@@
 According to this interpretation, participants base their responses in early rounds on the learned level of their opponents iterative reasoning, switching later to learned actions through reinforcement.
-<!--use a Bayesian Cognitive Hierarchy Indeed, in both experiments, following our results, it seems that in the earlier stages of the latter games, the BCH based strategies fitted observed action choices better than Q-learning based ones, with a reversal of the roles in later stages.-->
-
 We use hidden Markov models to more formally test for strategy switching in participants' play.
@@
 This model thus assumes that when players start with a particular strategy, they continue using it throughout the experiment.
-
-<!-- In the first model, we allow for a non-nil probability of players transitioning from one state (strategy) to another.
-In the second model, we assume that such switching does not happen, and as such assume implicitly that when players start with a particular strategy, they continue using it throughout the experiment.
-We then compare the likelihoods of each HMM model using a likelihood ratio test.
-
-that this hidden process has a Markov property, meaning that given state $S_{t-1}$, the value of $S_{t}$ is independent of all states occurring before time $t-1$.
-We also assume that $S_{t}$ has a discrete probability distribution in that it take one of K discrete values.
-The model is therefore specified by initial probabilities of being in each state ${1,2,...,K}$ and transition probabilities for moving from state $i$ to state $j$.
-These probabilities are fit using observed actions generated from these hidden states.
-
-, we fitted Hidden Markov Models in which the latent states are the 3 strategies used (Q-learning with state space consisting of previous round play, BCH based model with opponent model transfer, and a base model consisting of random play consistent with a Nash equilibrium strategy).
-Hidden Markov models are useful tools to explore structure in observed time series.
-They are named as such because of two properties: First, they make the assumption that any observable action at time t results from a process whose state at time t , named $S_{t}$ is "hidden" from the observer.
-Second, it also assumes that this hidden process has a Markov property, meaning that given state $S_{t-1}$, the value of $S_{t}$ is independent of all states occurring before time $t-1$.
-We also assume that $S_{t}$ has a discrete probability distribution in that it take one of K discrete values.
-The model is therefore specified by initial probabilities of being in each state ${1,2,...,K}$ and transition probabilities for moving from state $i$ to state $j$.
-These probabilities are fit using observed actions generated from these hidden states.
-
-To investigate the possibility of strategy switching, we fit two different hidden Markov models with the depmixS4 R package.
-In the first model, we allow for a non-nil probability of players transitioning from one state (strategy) to another.
-In the second model, we assume that such switching does not happen, and as such assume implicitly that when players start with a particular strategy, they continue using it throughout the experiment.
-We then compare the likelihoods of each HMM model using a likelihood ratio test.
--->
 
@@
 
-```{r no-switch, include=TRUE}
+```{r no-switch, include=FALSE}
 
@@
 In the later rounds of the games, the RL strategy becomes dominant, however.
-<!--This is then when there is no past play.
-The posterior probability is the probability that an observation comes from a component distribution a posteriori, i.e.
-given the value of the observation.
-In the first experiment, we can see from the plots of FWG and numbers games for level-1 opponent that although the likelihoods are very close, the posterior probability of the Bayesian model with transfer is slightly higher than that of the RL model in the very early rounds, but decreases rapidly while the posterior probability of the QL-learning with states models keeps increasing.
--->
 
@@
 
-```{r}
+```{r, include=FALSE}
 
@@
 The switching model in Experiment 2 is also significantly better than the restricted non-switching model ($p < .001$).
-<!-- On top of indications from looking at the likelihood by trial graphs, we have therefore further evidence that participants did indeed switch their strategies as the games progressed.
---> The posterior probabilities of the strategies (Figure\ \@ref(fig:exp2-posteriors-plot)) show very clear evidence of strategy switching across games and stages, from using a BCH model in the initial rounds to an RL strategy later on.
-<!--.
-The switching also seems to happen very early on at the beginning of each game and stage, and is also consistently in the same direction: The probability of Bayesian models with transfer being initially high, then decreasing rapidly while the posterior probability of QL-Learning with states and within transfer learning increases rapidly.
-
-Therefore, HMM modelling shows clear evidence in favour of strategy switching by participants, specifically after a few rounds of play.
-The strategy switching is consistently from BCH models towards Q-learning with states models in both experiments.
-
-\newpage
-
--->
+The posterior probabilities of the strategies (Figure\ \@ref(fig:exp2-posteriors-plot)) show very clear evidence of strategy switching across games and stages, from using a BCH model in the initial rounds to an RL strategy later on.
 
@@
 In this study, we investigated human learning transfer across games by making human participants play against computer agents with limited levels of iterated reasoning.
-We were interested whether participants learn about the strategy of their opponent and transfer such knowledge between games, and whether this is modulated by the similarity between games and the sophistication of the agent.
+We were interested in whether participants learn about the strategy of their opponent and transfer such knowledge between games, and whether this is modulated by the similarity between games and the sophistication of the agent.
 
@@
 In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
-Experiment 2 alsp offers more opportunities to test transfer of a learnt opponent model.
-There were two opportunities to transfer opponent models within each game as well as two opportunities to transfer from each game to the next, giving a total of 6 transfer opportunities.
-**MS: we did not test transfer at all these points, or did we?** The results on learning transfer confirmed the findings from the first experiment.
+Experiment 2 also offers more opportunities to test transfer of a learnt opponent model.
+The results on learning transfer confirmed the findings from the first experiment.
 Again, there was clear evidence of transfer in the early rounds of the later games.
-<!--While there was no evidence of higher scores across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
---> We also found that learning transfer is moderated by the type of opponent faced: Evidence of transfer was weaker for the level-2 opponent as compared to the level-1 opponent.
+We also found that learning transfer is moderated by the type of opponent faced: Evidence of transfer was weaker for the level-2 opponent as compared to the level-1 opponent.
 That transfer was less evident for the more sophisticated level-2 opponent in both experiments may be due to a higher difficulty of learning that opponent's strategy.
@@
 A player cannot transfer what they have not learnt.
-<!-- and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
-.
-When the players faced a level-1 opponent, they were able to transfer learning.
-However, when they faced a level-2 opponent, there was weaker evidence for transfer.
-The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with.
-A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
--->
-
-<!-- Coming back to learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are significantly higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
-The question we ask ourselves therefore is: -->
 
@@
 what did the players learn specifically about their opponent's strategy and what form did this learning take?
-
-<!-- We will proceed by considering multiple potential answers to this question. A possible hypothesis for learning the opponent’s strategy is the use of -->
 
@@
 There is no simple way to map "play scissors whenever my opponent played rock in last round" in the RPS game to "play grass whenever my opponent played fire in last round".
-Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this.
-Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
+Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this quickly enough: Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
 Secondly, a reinforcement learning strategy would fare equally well against the level-1 and level-2 opponent.
@@
 The difference in performance between the two types of opponent indicate that the actions of the more sophisticated level-2 opponent, or the best response to these, were somehow more difficult to predict.
-
-<!--
-it is unsatisfactory in explaining some of the learning transfer evidence we showed.
-Indeed, learning the best action in a particular state is not transferable to a new game since the state space is different and there is no single mapping between the state spaces of the initial and latter games.
-These rules would therefore need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
-
-Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, would require many rounds of practice.
-Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
-More specifically, if we assume that participants were using some type of associative learning or relying on spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
-To be sure, if a participant learns to pick say "scissors" whenever the opponent last picked "rock", then the degree of strategic sophistication of the opponent (its level k) should not impact this learning, and we would expect in this case there would be no difference between scores when facing level-1 and level-2 opponents, which is not the case here.
-The fact that the degree of sophistication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
--->
 
@@
 This is the type of learning encapsulated by our Bayesian Cognitive Hierarchy model.
-It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
-Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
-**MS: need to check relevance of these citations.
-Also, they need to be in reference list ** We admit that our implementation in the BCH models does not predict a performance difference between the types of opponents.
+It involves the evaluation of explicit hypotheses and results in better problem-solving skills [@mandler2004foundations].
+Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl [@stahl2000rule; @stahl2003sophisticated].
+We admit that our implementation in the BCH models does not predict a performance difference between the types of opponents.
 Starting with an equal prior belief over the different levels of sophistication, a BCH player would perform equally well against the level-1 and level-2 opponent.
@@
 Either of these mechanisms would explain why learning the strategy of the level-2 opponent is more difficult and slower than learning the strategy of the level-1 opponent.
-**MS: This could be something to implement, actually** Using hidden Markov models, we found evidence of strategy switching between the BCH and RL strategies, and such switching seems more consistent with the latter idea.
-If predicting an opponent's actions through iterative reasoning is cognitively demanding and error-prone, it is resource-rational to switch to less costly yet equally successful strategies when these are available.
-**MS: add reference to resource-rational approach by Lieder & Griffiths ** Initially, a model-free reinforcement learning strategy will be less successful than an iterative reasoning one.
+Using hidden Markov models, we found evidence of strategy switching between the BCH and RL strategies, and such switching seems more consistent with the latter idea.
+If predicting an opponent's actions through iterative reasoning is cognitively demanding and error-prone, it is resource-rational to switch to less costly yet equally successful strategies when these are available [@lieder2020resource].
+Initially, a model-free reinforcement learning strategy will be less successful than an iterative reasoning one.
 However, given enough experience, it will be on par with an iterative reasoning strategy.
 As it involves simple state-action contingencies, a model-free RL strategy may also be computationally less costly, making it overall more effective to rely on this than iterative reasoning.
-This is similar to the arbitration between model-free and model-based RL [@Simon_Daw_11] **MS: add more references here**.
+This is similar to the arbitration between model-free and model-based RL [@daw2005uncertainty;@Simon_Daw_11; @Kool_2011].
 In repeated and well-practised situations, relying on habits allows one to save cognitive resources for other demands.
 However, when the environment -- or game -- changes, it is prudent to use all available resources to reorient oneself.
-
-<!--
-building a mental representation of their opponent's strategy.
-
-of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
-A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
-For instance, the player may think “My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be”.
-This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
-This type of learning would be deemed “explicit” in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
-It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
-Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
-
-Our second experimental design allows us to test whether the first explanation holds.
-Since there is a simple transferable heuristic that works against level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
-Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.
-
-Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first interactions across games and using early rounds analysis.
-Based on our assumptions, we conclude therefore that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the course of learning.
-
-Our computational modelling allowed us to delve deeper into what might be driving the observed learning transfer.
-Initial modelling of observations using all available data seems to indicate that the most likely model was a Q-learning type model.
-However, as we argued above, that would be inconsistent with the evidence for learning transfer.
-Breaking down likelihoods by trial and fitting a hidden Markov model to the data with states being the various strategies that participants are assumed to be using, we showed evidence for within game switching of strategies.
-Participants start the early rounds of a new game acting in a way consistent with a Bayesian Bayesian Cognitive Hierarchy level, which would be accurate and generalisable but computationally expensive.
-However, as trials continue, participants seem to switch to a habitual type of learning (QL-models).
-
-Why is this switching happening?
-We believe that participants show flexibility in their use of learning strategies.
-When a new game is started that is similar to a previously played game with the same opponent, participants need a way to transfer prior knowledge of the opponent and apply it to the new game in order to best respond.
-Adopting a Bayesian model based on BCH achieves the goal of transferring the opponent model and thus coming up with best responses in the early trials.
-However, Bayesian BCH models are computationally expensive and require higher order thinking (I think that you think that I think...).
-As such, as the games progresses, they may become burdensome and the higher amount of historical interaction in the new game allows participants to have enough data to start using the cognitively cheaper model-free learning strategies such as Q-learning.
-The preference for less computationally demanding strategies is well established [@Kool_2011].
-Moreover, the ability to flexibly switch is also consistent with evidence from the literature on learning strategies in humans, showing that they indeed shift between model-based and model-free learning when the environment requires it [@Simon_Daw_11].
-
--->
 

### 2021-08-24 Report/paper_draft_2021.tex
checks ismail

@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
 \PassOptionsToPackage{hyphens}{url}
@@
 %
-\documentclass[
-  english,
-  man,floatsintext]{apa6}
-\usepackage{amsmath,amssymb}
+\documentclass[man,floatsintext]{apa6}
 \usepackage{lmodern}
+\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
+  \usepackage{textcomp} % provides euro and other symbols
+\else % if luatex or xelatex
   \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
-% Use upquote if available, for straight quotes in verbatim environments
+% use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
+% use microtype if available
+\IfFileExists{microtype.sty}{%
 \usepackage[]{microtype}
@@
 }{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
 \IfFileExists{parskip.sty}{%
@@
 \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{hyperref}
 \hypersetup{
             pdftitle={Transfer of Learned Opponent Models in Zero Sum Games},
-  pdfauthor={Ismail Guennouni1 \& Maarten Speekenbrink1},
-  pdflang={en-EN},
+            pdfauthor={Ismail Guennouni~\& Maarten Speekenbrink},
             colorlinks=true,
@@
             urlcolor=Blue,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx}
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
 \ifx\paragraph\undefined\else
@@
 \fi
-% Manuscript styling
+
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
+\shorttitle{Upgrade Report}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Department of Experimental Psychology, University College London}
+\usepackage{csquotes}
 \usepackage{upgreek}
@@
 
-% Table formatting
 \usepackage{longtable}
 \usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
 
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
 \newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
 \makeatletter
@@
 \newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
-\shorttitle{Upgrade Report}
-\usepackage{csquotes}
 \shorttitle{}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifluatex
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
 \title{Transfer of Learned Opponent Models in Zero Sum Games}
-\author{Ismail Guennouni\textsuperscript{1} \& Maarten Speekenbrink\textsuperscript{1}}
+\author{Ismail Guennouni\textsuperscript{1}~\& Maarten Speekenbrink\textsuperscript{1}}
 \date{}
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Experimental Psychology, University College London}
+\authornote{
+
+Correspondence concerning this article should be addressed to Ismail Guennouni, Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom.
+E-mail: \href{mailto:i.guennouni.17@ucl.ac.uk}{\nolinkurl{i.guennouni.17@ucl.ac.uk}}}
 
@@
 learning strategy that facilitates between-game transfer of the opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
+
 }
@@
 Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly useful to address this question.
-The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.~Nash equilibrium play) or use salient actions (e.g.~risk dominance) in later games, having had experience with a similar game environment previously (Camerer \& Knez, 2000; Teck-Hua Ho, Camerer, \& Weigelt, 1998).
+The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.~Nash equilibrium play) or use salient actions (e.g.~risk dominance) in later games, having had experience with a similar game environment previously (Camerer \& Knez, 2000; Ho, Camerer, \& Weigelt, 1998).
 As is well-known, a Nash equilibrium means that all players in a game play such that no-one can unilaterally improve their performance by deviating from their strategy.
@@
 Studies that focused on whether people can learn to exploit deviations from Nash-equilibrium play have mostly looked at the ability of players to detect and exploit action-based learning rules (Shachat \& Swarthout, 2004; Spiliopoulos, 2013).
-These studies used computer opponents with fixed strategies (no adaptation to their human opponent) consisting of playing each action with a fixed probability (a mixed strategy).
-Findings showed \ldots.
+These studies used computer opponents that don't adapt play to their human opponent, mostly consisting of playing each action with a fixed probability (a mixed strategy).
+Findings showed that humans are capable of adapting to non-Nash equilibrium play and detect patterns in opponent's history of play.
 However, the use of mixed strategies may have limited people's ability to form accurate opponent models.
 Rather than thinking of their opponents and drawing a random action from a (non-uniform) probability distribution, people may rather think of their opponents as applying a form of iterated reasoning to determine their next action.
-The type of reasoning we refer to takes the form of ``I believe that you believe that I believe \ldots'\,' and has been shown to correspond to people's casual introspection (REFERENCE).
-It also underlies successful models in behavioural economics, such as Level-\(k\) and Cognitive Hierarchy models, which posit that people assume their opponent has a limited level of iterative reasoning, with the player best responding to their (modelled) opponent.
+The type of reasoning we refer to takes the form of ``I believe that you believe that I believe \ldots{}'' and has been shown to underlie people's decision in the context of economic games (Camerer, 2003; Costa-Gomes, Crawford, \& Broseta, 2001).
+It also underlies successful models in behavioural economics, such as Level-\(k\) and Cognitive Hierarchy models (Camerer, Ho, \& Chong, 2004), which posit that people assume their opponent has a limited level of iterative reasoning, with the player best responding to their (modelled) opponent.
 
@@
 
-Iterative reasoniing strategies can explain non-equilibrium play in a range of games, such as \ldots{} In the present study, we endow our computer opponents with limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
+Iterative reasoning strategies can explain non-equilibrium play in a range of games, such as the p beauty contest game (Nagel, 1995), dominance solvable games (Camerer et al., 2004) and various standard normal form games (Costa-Gomes et al., 2001).
+In the present study, we endow our computer opponents with limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
 In two experiments, participants face the same opponent (Experiment 1) or same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, a structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
 To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of the opponent and the similarity of the games.
-Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a morehabiltual and cognitively less demanding strategy in the later stages of the games.
+Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a more habiltual and cognitively less demanding strategy in the later stages of the games.
 
@@
 
-In the first experiment, we \ldots. {[}intro to first exp{]}
+In the first experiment, we aim to test learning transfer through making participants face the same computer opponent in three sequential games that vary in similarity.
 
@@
 
-In the first experiment, participants played the three games against their computer opponent.
+Participants played the three games against their computer opponent.
 These games were rock-paper-scissors, fire-water-grass, and the numbers game.
@@
 This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level-1 or level-2 player.
-Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'\,', is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
+Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'', is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
+
 The Numbers game is a generalization of RPS.
@@
 An example of the interface for the RPS game is provided in Figure~\ref{fig:feedback-rps-exp2}.
-On each round, tHe human player chooses an action, and after a random delay, is shown the action chosen by the computer opponent, and the outcome of that round.
+On each round, the human player chooses an action, and after a random delay, is shown the action chosen by the computer opponent, and the outcome of that round.
 A history of the chosen actions over all rounds is available in the centre panel.
@@
 
-{\centering \includegraphics[width=3.13in]{images/feedback_rps}
+{\centering \includegraphics{images/feedback_rps}
 
@@
 Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
-\textbf{MS: Need to check test results and report GG degrees of freedom, etc.}
+\textbf{MS: Need to check test results and report GG degrees of freedom, etc.} \textbf{\ldots{}IG: I thought GG corrections only apply when there is violation of sphericity\ldots{}.
+according to Mauchly Test there isn't a violation here.
+Should we report them anyway in this experiment?
+}
 
@@
 Figure~\ref{fig:screenshot-shootout} shows a snapshot of play in the shootout game.
-What makes this game different to the other games is that there are two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend `'right'' in the next round, they can win by either choosing to shoot `'left'' or `'center''.
+What makes this game different to the other games is that there are two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend \enquote{'right}' in the next round, they can win by either choosing to shoot \enquote{'left}' or \enquote{'center}'.
 A level-1 shooter who thinks that their goalkeeper opponent will repeat their last action has thus two possible best responses.
@@
 
-{\centering \includegraphics[width=6.4in]{images/shootout}
+{\centering \includegraphics{images/shootout}
 
@@
 Participants scores are depicted in Figure \ref{fig:exp2-score-by-opp}.
-The RPS game had the lowest average score per round (\(M = 0.194\), SD = 0.345) followed by FWG (\(M = 0.27\), SD = 0.394) and finally the Shootout game (\(M = 0.289\), SD = 0.326).\footnote{ A higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
+The RPS game had the lowest average score per round (\(M = 0.194\), SD = 0.345) followed by FWG (\(M = 0.27\), SD = 0.394) and finally the Shootout game (\(M = 0.289\), SD = 0.326).\footnote{A higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
 Indeed, a player not aiming to uncover the opponent's strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
@@
 
-To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA on the average score per round, with the first factor varying between participants.
-This shows a main effect of Game (\(F(1.85,88.7) = 11.81\), \(\eta^{2} = 0.04\), \(p < .001\)).
+\begin{figure}
+
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-score-by-opp-1}
+
+}
+
+\caption{\label{fig:exp2-score-by-opp}Performance per game and interaction across opponents in Experiment 2.
+Points are scores of individual participants and boxes reflect the 95\% confidence intervals of the mean (center line equals the mean).}\label{fig:exp2-score-by-opp}
+\end{figure}
+
+To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA, with the first factor varying between participants.
+This showed a main effect of Game (\(F(1.85,88.7) = 11.81\), \(\eta^{2} = 0.04\), \(p < .001\)).
 Post-hoc pairwise comparisons between games (p-values adjusted using Holm method for multiple comparisons) indicate performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (\(t(96) =2.53\), \(p = .025\)), and performance in the Shootout game significantly higher than in FWG (\(t(96) = 2.32\), \(p = .025\)).
@@
 
-As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random (Figure~\ref{fig:exp2-early-scores}).
-For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types (Level-1 opponent: FWG: \(t(270) = 4.99\), \(p < .001\); Shootout: \(t(270) = 6.66\), \(p < .001\); Level-2 opponent: FWG: \(t(270) = 4.40\), \(p < .001\); Shootout: \(t(270) = 3.21\), \(p=.004\)).
-\textbf{MS: Should also report ANOVA, as for Experiment 1}
+To measure transfer between games, we again focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with the opponent (see Figure \ref{fig:exp2-early-score-by-opp}).
+We performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) repeated-measures ANOVA, with the first factor varying between participants.
+This showed a main effect of Game (\(F(1.94,92.98) = 7.67\), \(\eta^{2} = 0.04\), \(p < .001\)).
+We then run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG (\(t(271) = 4.99\), \(p < .001\)) and Shootout (\(t(271) = 6.66\), \(p < .001\)).
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player (\(t(271) = 4.41\), \(p < .001\)).
+Unike in experiment 1, there is also evidence of transfer to the dissimilar game of Shootout (\(t(271) = 3.22\), \(p = .004\)).
+The early round scores in the similar FWG games for level-1 and level-2 facing players are not significantly different from each other.
+However, the score of the players facing the level-1 opponent in Shootout is higher than that of players facing level-2 opponents ( \(t(144) = 2.45\), \(p = 0.01\)).
 
@@
 
-The results of Experiment 2\ldots{} \textbf{MS: give summary of main findings, as done for Experiment 1.
-You should not report new statistical tests in the discussion, which should go in the results section before.}
-
-Looking at learning transfer by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
-Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
-These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
+The results of Experiment 2 confirm the earlier results of Experiment 1 about players adapting their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
+Knowledge about both types of opponents were transfered to both the similar and dissimilar game.
+However, transfer to the dissimilar game was easier when facing the more sophisticated agent.
 
@@
 In the following, we will describe the models in more detail, and provide some intuition into how they they learn about the game and/or the opponent.
-We use the following notation: In each game \(g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}\), on each trial \(t\), the participant chooses an action \(a_t \in \mathcal{A}_g\), and the opponent chooses action \(o_t \in \mathcal{A}_g\), where \(\mathcal{A}_g\) is the set of allowed actions in game \(g\), e.g.~\(\mathcal{A}_\text{RPS} = \{R,P,S\}\).
+We use the following notation: In each game \(g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}\), on each trial \(t\), the participant chooses an action \(a_t \in \mathcal{A}_g\), and the opponent chooses action \(o_t \in \mathcal{A}_g\), where \(\mathcal{A}_g\) is the set of allowed actions in game \(g\), e.g.
+\(\mathcal{A}_\text{RPS} = \{R,P,S\}\).
 The participant then receives reward \(r_t \in \{1,0,-1\}\), and the opponent receives \(-r_t\).
@@
 where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), and \(\alpha \in [0,1]\) the learning rate.
-For instance, \(Q_t(\{R,S\},P)\) denotes the value of taking action `'Paper'' this round if the player's last action was `'Rock'' and the opponent played `'Scissors''.
+For instance, \(Q_t(\{R,S\},P)\) denotes the value of taking action \enquote{'Paper}' this round if the player's last action was \enquote{'Rock}' and the opponent played \enquote{'Scissors}'.
 Actions are taken according to a softmax rule:
@@
 
-The self-tuning Experience Weighted Attraction (EWA) model (Teck H.
-Ho, Camerer, \& Chong, 2004) combines two seemingly different approaches, namely reinforcement learning and belief learning.
+The self-tuning Experience Weighted Attraction (EWA) model (Ho, Camerer, \& Chong, 2004) combines two seemingly different approaches, namely reinforcement learning and belief learning.
 Belief learning models are based on the assumption that players keep track of the frequency of past actions and best respond to that.
@@
 The self-tuning EWA model has been shown to perform better than either RL or belief learning alone in various repeated games and has the advantage of having only one free parameter, the inverse temperature of the softmax choice function.
-The EWA model is based on updating ``Attractions'\,' for each action over time.
-The attraction of action \(a\) time \(t\) is written \(A_{t}(a)\) and is updated as
-\[ A_{t+1}(a) =  \frac{\phi \ N(t) \ A_{t}(a) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} \]
+The EWA model is based on updating ``Attractions'' for each action over time given a particular state.
+The attraction of action \(a\) at time \(t\) given state \(s\) composet of lkast round play is written \(A_{t}(a, s)\) and is updated as
+\[ A_{t+1}(a,s) =  \frac{\phi \ N(t) \ A_{t}(a,s) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} \]
 where \(I(x)\) is an indicator function which takes the value 1 is its argument is true, and 0 otherwise, and \(R(a,o_t)\) is the reward that would be obtained from playing action \(a\) against opponent action \(o_t\), which equals the actual obtained reward when \(a = a_t\), and otherwise is a counterfactual reward that would have been obtained if a different action were taken.
@@
 We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play (Cheung \& Friedman, 1994).
-While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Teck H.
-Ho, Camerer, \& Chong, 2004).
-\(N(t)\) represents an experience weight and can be interpreted as the number of ``observation-equivalents'' of past experience.
+While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Ho et al., 2004).
+\(N(t)\) represents an experience weight and can be interpreted as the number of \enquote{observation-equivalents} of past experience.
 We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
-\textbf{MS: Should describe how the parameters are self-tuned with equations }
+For details on how the various parameters are self-tuned, please refer to (Ho et al., 2004).
+\textbf{MS: Should describe how the parameters are self-tuned with equations.
+IG: There are many equations for each of the parameters update, phi, delta and N\ldots{}I'm concerned it would make for cumbersome reading, especially since EWA doesn't really fit well anyway.
+I've added that details of updates can be found in original camerer paper.}
 
 As in the models above, actions are chosen based on a softmax decision rule:
-\[P_t(a) = \frac{\exp \{\lambda  A_{t}(a) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a') \} }\]
+\[P_t(a,s) = \frac{\exp \{\lambda  A_{t}(a,s) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a',s) \} }\]
 The self-tuning EWA has one free parameter: the inverse temperature of the softmax decision rule (\(\lambda\)).
-\textbf{MS: Are there no states in the EWA?
-If not, it is unsurprising that this model doesn't fit well }
 
@@
 However, the participant might also assume that the level of reasoning of their opponent does not generalize over games.
-This would mean starting with a ``fresh'' prior \(P(\text{level} = k)\) at the start of each game.
+This would mean starting with a \enquote{fresh} prior \(P(\text{level} = k)\) at the start of each game.
 We hence distinguish between two versions of the BCH model.
@@
 This is also reflected in BIC weights in Figure \ref{fig:xp2-BIC-weigths}.
-\textbf{MS: model labels in Figures should correspond to those in the text}
 
@@
 According to this interpretation, participants base their responses in early rounds on the learned level of their opponents iterative reasoning, switching later to learned actions through reinforcement.
-
 We use hidden Markov models to more formally test for strategy switching in participants' play.
@@
 This model thus assumes that when players start with a particular strategy, they continue using it throughout the experiment.
-
-\begin{verbatim}
-## converged at iteration 7 with logLik: -7415.978
-\end{verbatim}
-
-\begin{verbatim}
-## log Likelihood ratio (chi^2): 211.087 (df=0), p=0.
-\end{verbatim}
-
-\begin{verbatim}
-## [1] 0
-\end{verbatim}
 
@@
 In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
-Experiment 2 alsp offers more opportunities to test transfer of a learnt opponent model.
-There were two opportunities to transfer opponent models within each game as well as two opportunities to transfer from each game to the next, giving a total of 6 transfer opportunities.
-\textbf{MS: we did not test transfer at all these points, or did we?} The results on learning transfer confirmed the findings from the first experiment.
+Experiment 2 also offers more opportunities to test transfer of a learnt opponent model.
+The results on learning transfer confirmed the findings from the first experiment.
 Again, there was clear evidence of transfer in the early rounds of the later games.
@@
 One possible answer is that participants learned simple rules based on last round play.
-For instance, ``play scissors whenever my opponent played rock in last round,'' or ``play paper whenever the last round play was either rock or scissors.'' These are the type of strategies that are learned by the model-free reinforcement learning we used in our computational modelling.
+For instance, \enquote{play scissors whenever my opponent played rock in last round}, or \enquote{play paper whenever the last round play was either rock or scissors}.
+These are the type of strategies that are learned by the model-free reinforcement learning we used in our computational modelling.
 While this strategy fitted participants' actions the best overall, there are at least two reasons why this account is not satisfactory as a complete description of participants' behaviour.
 Firstly, the learned strategies are not transferable to new games.
-There is no simple way to map ``play scissors whenever my opponent played rock in last round'' in the RPS game to ``play grass whenever my opponent played fire in last round.'' Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this.
+There is no simple way to map \enquote{play scissors whenever my opponent played rock in last round} in the RPS game to \enquote{play grass whenever my opponent played fire in last round}.
+Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this.
 Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
@@
 This is a rule that wins and is transferable to other games as it does not depend on action labels.
-In the same vein, a heuristic that beats a level-1 player can be stated as ``Choose the action that would have been beaten by my previous action.'' Intuitively, it seems that the heuristic for the level-2 player is simpler than that for the level-1 player, which is at odds with the difference in performance.
+In the same vein, a heuristic that beats a level-1 player can be stated as \enquote{Choose the action that would have been beaten by my previous action}.
+Intuitively, it seems that the heuristic for the level-2 player is simpler than that for the level-1 player, which is at odds with the difference in performance.
 
 A second explanation is that participants engaged in iterative reasoning, inferring their opponent's beliefs and countering the resulting actions.
-For instance, this would be reasoning of the form ``My opponent expects me to repeat my last action, choosing an action that would beat my last action.
-Hence, I will choose the action that beats their best response'' or ``My opponent thinks I expect them to repeat their action, hence expecting me to choose the action that beats their last action.
-They will therefore choose the action that beats this one, and hence I should choose the action that beats their best response.'' Beating a level-1 player, in this account, requires being a level-2 player, and beating a level-2 player requires being a level-3 player.
+For instance, this would be reasoning of the form \enquote{My opponent expects me to repeat my last action, choosing an action that would beat my last action.
+Hence, I will choose the action that beats their best response} or \enquote{My opponent thinks I expect them to repeat their action, hence expecting me to choose the action that beats their last action.
+They will therefore choose the action that beats this one, and hence I should choose the action that beats their best response.} Beating a level-1 player, in this account, requires being a level-2 player, and beating a level-2 player requires being a level-3 player.
 Intuitively, the additional step of iterative reasoning involved in beating a level-2 player makes the level-3 strategy more demanding and difficult to implement, which is consistent with the lower performance against the level-2 opponent.
@@
 It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
-Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
-\textbf{MS: need to check relevance of these citations.
-Also, they need to be in reference list } We admit that our implementation in the BCH models does not predict a performance difference between the types of opponents.
+Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (Stahl, 2000, 2003).
+\textbf{MS: need to check relevance of these citations } We admit that our implementation in the BCH models does not predict a performance difference between the types of opponents.
 Starting with an equal prior belief over the different levels of sophistication, a BCH player would perform equally well against the level-1 and level-2 opponent.
@@
 \textbf{MS: This could be something to implement, actually} Using hidden Markov models, we found evidence of strategy switching between the BCH and RL strategies, and such switching seems more consistent with the latter idea.
-If predicting an opponent's actions through iterative reasoning is cognitively demanding and error-prone, it is resource-rational to switch to less costly yet equally successful strategies when these are available.
-\textbf{MS: add reference to resource-rational approach by Lieder \& Griffiths } Initially, a model-free reinforcement learning strategy will be less successful than an iterative reasoning one.
+If predicting an opponent's actions through iterative reasoning is cognitively demanding and error-prone, it is resource-rational to switch to less costly yet equally successful strategies when these are available (Lieder \& Griffiths, 2020).
+Initially, a model-free reinforcement learning strategy will be less successful than an iterative reasoning one.
 However, given enough experience, it will be on par with an iterative reasoning strategy.
 As it involves simple state-action contingencies, a model-free RL strategy may also be computationally less costly, making it overall more effective to rely on this than iterative reasoning.
-This is similar to the arbitration between model-free and model-based RL (Simon \& Daw, 2011) \textbf{MS: add more references here}.
+This is similar to the arbitration between model-free and model-based RL (Daw, Niv, \& Dayan, 2005; Simon \& Daw, 2011; Wouter Kool, Joseph T.
+McGuire, Zev B.
+Rosen, Matthew M.
+Bovinick, 2011).
 In repeated and well-practised situations, relying on habits allows one to save cognitive resources for other demands.
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-batzilis}{}%
@@
 
+\leavevmode\hypertarget{ref-camerer2003behavioural}{}%
+Camerer, C. F. (2003). Behavioural studies of strategic thinking in games. \emph{Trends in Cognitive Sciences}, \emph{7}(5), 225--231.
+
+\leavevmode\hypertarget{ref-camerer2004cognitive}{}%
+Camerer, C. F., Ho, T.-H., \& Chong, J.-K. (2004). A cognitive hierarchy model of games. \emph{The Quarterly Journal of Economics}, \emph{119}(3), 861--898.
+
 \leavevmode\hypertarget{ref-camerer1997experience}{}%
-Camerer, C., Ho, T.-H., \& Others. (1997). \emph{{Experience-weighted attraction learning in games: A unifying approach}}.
+Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
 
 \leavevmode\hypertarget{ref-knez2000}{}%
-Camerer, C., \& Knez, M. (2000). \emph{{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}}.
+Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
 
 \leavevmode\hypertarget{ref-cheung1994learning}{}%
-Cheung, Y.-W., \& Friedman, D. (1994). \emph{{Learning in evolutionary games: some laboratory results}}. University of California, Santa Cruz.
+Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
+
+\leavevmode\hypertarget{ref-costa2001cognition}{}%
+Costa-Gomes, M., Crawford, V. P., \& Broseta, B. (2001). Cognition and behavior in normal-form games: An experimental study. \emph{Econometrica}, \emph{69}(5), 1193--1235.
+
+\leavevmode\hypertarget{ref-daw2005uncertainty}{}%
+Daw, N.
+D., Niv, Y., \& Dayan, P.
+(2005).
+Uncertainty-based competition between prefrontal and dorsolateral striatal systems for behavioral control.
+\emph{Nature Neuroscience}, \emph{8}(12), 1704--1711.
 
 \leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, Teck H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{{The economics of learning models: A self-tuning theory of learning in games}}.
+Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
 
 \leavevmode\hypertarget{ref-ho1998iterated}{}%
-Ho, Teck-Hua, Camerer, C., \& Weigelt, K. (1998). {Iterated dominance and iterated best response in experimental" p-beauty contests"}. \emph{The American Economic Review}, \emph{88}(4), 947--969.
+Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
 
@@
 (2017).
-{Building machines that learn and think like people}.
+Building machines that learn and think like people.
 \emph{Behavioral and Brain Sciences}, \emph{40}.
@@
 
+\leavevmode\hypertarget{ref-lieder2020resource}{}%
+Lieder, F., \& Griffiths, T.
+L.
+(2020).
+Resource-rational analysis: Understanding human cognition as the optimal use of limited computational resources.
+\emph{Behavioral and Brain Sciences}, \emph{43}.
+
 \leavevmode\hypertarget{ref-mertens1990repeated}{}%
-Mertens, J.-F. (1990). {Repeated games}. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+
+\leavevmode\hypertarget{ref-nagel1995unraveling}{}%
+Nagel, R. (1995). Unraveling in guessing games: An experimental study. \emph{The American Economic Review}, \emph{85}(5), 1313--1326.
 
 \leavevmode\hypertarget{ref-shachat2004we}{}%
-Shachat, J., \& Swarthout, J. T. (2004). {Do we detect and exploit mixed strategy play by opponents?} \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
+Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
 
@@
 (2011).
-{Environmental statistics and the trade-off between model-based and TD learning in humans}.
+Environmental statistics and the trade-off between model-based and TD learning in humans.
 \emph{Advances in Neural Information Processing Systems 24: 25th Annual Conference on Neural Information Processing Systems 2011, NIPS 2011}, 1--9.
@@
 \leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
-Spiliopoulos, L. (2013). {Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game}. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
+Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
+
+\leavevmode\hypertarget{ref-stahl2000rule}{}%
+Stahl, D. O. (2000). Rule learning in symmetric normal-form games: Theory and evidence. \emph{Games and Economic Behavior}, \emph{32}(1), 105--138.
+
+\leavevmode\hypertarget{ref-stahl2003sophisticated}{}%
+Stahl, D. O. (2003). Sophisticated learning and learning sophistication. \emph{Available at SSRN 410921}.
 
 \leavevmode\hypertarget{ref-stahl1995players}{}%
-Stahl, D. O., \& Wilson, P. W. (1995). {On players models of other players: Theory and experimental evidence}. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
+Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
 
@@
 (2010).
-{depmixS4}: An {R} package for hidden markov models.
+depmixS4: An R package for hidden markov models.
 \emph{Journal of Statistical Software}, \emph{36}(7), 1--21.
@@
 \leavevmode\hypertarget{ref-watkins1992q}{}%
-Watkins, C. J. C. H., \& Dayan, P. (1992). {Q-learning}. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
+Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
 
-\end{CSLReferences}
+\leavevmode\hypertarget{ref-Kool_2011}{}%
+Wouter Kool, Joseph T.
+McGuire, Zev B.
+Rosen, Matthew M.
+Bovinick.
+(2011).
+Decision Making and the Avoidance of Cognitive Demand.
+\emph{Experimental Psychology}.
+\url{https://doi.org/10.2996/kmj/1138846322}
+
+\leavevmode\hypertarget{ref-batzilis}{}%
+Batzilis, D., Jaffe, S., Levitt, S., List, J.
+A., \& Picel, J.
+(2016).
+\emph{How facebook can deepen our understanding of behavior in strategic settings: Evidence from a million rock-paper-scissors games}.
+working paper.
+
+\leavevmode\hypertarget{ref-camerer2003behavioural}{}%
+Camerer, C. F. (2003). Behavioural studies of strategic thinking in games. \emph{Trends in Cognitive Sciences}, \emph{7}(5), 225--231.
+
+\leavevmode\hypertarget{ref-camerer2004cognitive}{}%
+Camerer, C. F., Ho, T.-H., \& Chong, J.-K. (2004). A cognitive hierarchy model of games. \emph{The Quarterly Journal of Economics}, \emph{119}(3), 861--898.
+
+\leavevmode\hypertarget{ref-camerer1997experience}{}%
+Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
+
+\leavevmode\hypertarget{ref-knez2000}{}%
+Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
+
+\leavevmode\hypertarget{ref-cheung1994learning}{}%
+Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
+
+\leavevmode\hypertarget{ref-costa2001cognition}{}%
+Costa-Gomes, M., Crawford, V. P., \& Broseta, B. (2001). Cognition and behavior in normal-form games: An experimental study. \emph{Econometrica}, \emph{69}(5), 1193--1235.
+
+\leavevmode\hypertarget{ref-daw2005uncertainty}{}%
+Daw, N.
+D., Niv, Y., \& Dayan, P.
+(2005).
+Uncertainty-based competition between prefrontal and dorsolateral striatal systems for behavioral control.
+\emph{Nature Neuroscience}, \emph{8}(12), 1704--1711.
+
+\leavevmode\hypertarget{ref-ho2004economics}{}%
+Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
+
+\leavevmode\hypertarget{ref-ho1998iterated}{}%
+Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
+
+\leavevmode\hypertarget{ref-Lake2017}{}%
+Lake, B.
+M., Ullman, T.
+D., Tenenbaum, J.
+B., \& Gershman, S.
+J.
+(2017).
+Building machines that learn and think like people.
+\emph{Behavioral and Brain Sciences}, \emph{40}.
+\url{https://doi.org/10.1017/S0140525X16001837}
+
+\leavevmode\hypertarget{ref-lieder2020resource}{}%
+Lieder, F., \& Griffiths, T.
+L.
+(2020).
+Resource-rational analysis: Understanding human cognition as the optimal use of limited computational resources.
+\emph{Behavioral and Brain Sciences}, \emph{43}.
+
+\leavevmode\hypertarget{ref-mertens1990repeated}{}%
+Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+
+\leavevmode\hypertarget{ref-nagel1995unraveling}{}%
+Nagel, R. (1995). Unraveling in guessing games: An experimental study. \emph{The American Economic Review}, \emph{85}(5), 1313--1326.
+
+\leavevmode\hypertarget{ref-shachat2004we}{}%
+Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
+
+\leavevmode\hypertarget{ref-Simon_Daw_11}{}%
+Simon, D.
+A., \& Daw, N.
+D.
+(2011).
+Environmental statistics and the trade-off between model-based and TD learning in humans.
+\emph{Advances in Neural Information Processing Systems 24: 25th Annual Conference on Neural Information Processing Systems 2011, NIPS 2011}, 1--9.
+
+\leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
+Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
+
+\leavevmode\hypertarget{ref-stahl2000rule}{}%
+Stahl, D. O. (2000). Rule learning in symmetric normal-form games: Theory and evidence. \emph{Games and Economic Behavior}, \emph{32}(1), 105--138.
+
+\leavevmode\hypertarget{ref-stahl2003sophisticated}{}%
+Stahl, D. O. (2003). Sophisticated learning and learning sophistication. \emph{Available at SSRN 410921}.
+
+\leavevmode\hypertarget{ref-stahl1995players}{}%
+Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
+
+\leavevmode\hypertarget{ref-R-depmixS4}{}%
+Visser, I., \& Speekenbrink, M.
+(2010).
+depmixS4: An R package for hidden markov models.
+\emph{Journal of Statistical Software}, \emph{36}(7), 1--21.
+Retrieved from \url{http://www.jstatsoft.org/v36/i07/}
+
+\leavevmode\hypertarget{ref-wang2014social}{}%
+Wang, Z., Xu, B., \& Zhou, H.-J. (2014). Social cycling and conditional responses in the rock-paper-scissors game. \emph{Scientific Reports}, \emph{4}(1), 1--7.
+
+\leavevmode\hypertarget{ref-watkins1992q}{}%
+Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
+
+\leavevmode\hypertarget{ref-Kool_2011}{}%
+Wouter Kool, Joseph T.
+McGuire, Zev B.
+Rosen, Matthew M.
+Bovinick.
+(2011).
+Decision Making and the Avoidance of Cognitive Demand.
+\emph{Experimental Psychology}.
+\url{https://doi.org/10.2996/kmj/1138846322}
 

### 2021-08-26 Report/paper_draft_2021.Rmd
pass through latest draft. Still a few things to resolve

@@
   computer agents with human-like limited degrees of iterated reasoning. In two experiments, we find that participants
-  deviate from Nash equilibrium play and learn to adapt to the opponent's strategy and exploit it. Moreover, we show that participants transfer their learning to new games and that
-  this transfer is moderated by the level of sophistication of the opponent. Computational modelling shows that players start each game with a model-based
-  learning strategy that facilitates between-game transfer of the opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
+  deviate from Nash equilibrium play and learn to adapt to their opponent's strategy to exploit it. Moreover, we show that participants transfer their learning to new games and that
+  this transfer is moderated by the level of sophistication of the opponent, as well as the similarity between games. Computational modelling shows that players start each game with a model-based
+  learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
 
@@
 In this paper, we are specifically interested in the latter: How do people build and use models of their opponent to facilitate learning transfer?
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly useful to address this question.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about their opponent's strategies and preferences [@mertens1990repeated] are particularly useful to address this question.
 The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.
@@
 risk dominance) in later games, having had experience with a similar game environment previously [@ho1998iterated; @knez2000].
-As is well-known, a Nash equilibrium means that all players in a game play such that no-one can unilaterally improve their performance by deviating from their strategy.
+As is well-known, a Nash equilibrium means that all players in a game act such that no-one can unilaterally improve their performance by deviating from their strategy.
 When playing against an opponent with a Nash-optimal strategy, I can do no better than play according to the Nash-equilibrium strategy as well.
-However, when faced with a player who deviates from the Nash-optimal strategy, it may be better for me to exploit this and also deviate from this strategy, increasing my performance beyond what is expected at a Nash equilibrium.
-Of course, this comes with some risk, as my own deviation from Nash-optimal play may leave myself open to similar exploitation.
+However, when faced with a player who deviates from the Nash-optimal strategy, I may be able to exploit this and also deviate from this strategy, increasing my performance beyond what is expected at Nash equilibrium.
+Of course, this comes with some risk, as my own deviation from Nash-optimal play may leave me open to similar exploitation.
 
@@
 These studies used computer opponents that don't adapt play to their human opponent, mostly consisting of playing each action with a fixed probability (a mixed strategy).
-Findings showed that humans are capable of adapting to non-Nash equilibrium play and detect patterns in opponent's history of play.
+Findings showed that humans are capable of adapting to non-Nash-equilibrium play and detect patterns in an opponent's history of play.
 However, the use of mixed strategies may have limited people's ability to form accurate opponent models.
-Rather than thinking of their opponents and drawing a random action from a (non-uniform) probability distribution, people may rather think of their opponents as applying a form of iterated reasoning to determine their next action.
-The type of reasoning we refer to takes the form of ``I believe that you believe that I believe ...'' and has been shown to underlie people's decision in the context of economic games [@camerer2003behavioural;@costa2001cognition].
-It also underlies successful models in behavioural economics, such as Level-$k$ and Cognitive Hierarchy models [@camerer2004cognitive], which posit that people assume their opponent has a limited level of iterative reasoning, with the player best responding to their (modelled) opponent.
+Instead of thinking of their opponents as drawing random actions from a (non-uniform) probability distribution, people may rather think of their opponents as applying a form of iterated reasoning to determine their next action.
+The type of reasoning we refer to takes the form of "I believe that you believe that I believe ..." and has been shown to underlie people's decisions in economic games [@camerer2003behavioural;@costa2001cognition].
+It also underlies successful models in behavioural economics, such as Level-$k$ and Cognitive Hierarchy models [@camerer2004cognitive], which posit that people assume their opponent applies a limited level of iterative reasoning, taking actions that are best responses to those of their (modelled) opponent.
 
@@
 A level-2 player, on the other hand, takes their opponent's belief about their actions into account, assuming they face a level-1 player, and choosing actions to best respond to the actions of that player.
-Cognitive Hierarchy theory works on similar principles, but rather than assuming an opponent always adopts a particular level-$k$ strategy, they assume their opponent adopts each pf the level-$k$ strategies with a particular probability (i.e., the strategy is a mixture over pure level-$k$ strategies).
-
-Iterative reasoning strategies can explain non-equilibrium play in a range of games, such as the p beauty contest game [@nagel1995unraveling], dominance solvable games [@camerer2004cognitive] and various standard normal form games [@costa2001cognition].
+Cognitive Hierarchy theory is based on similar principles, but rather than assuming an opponent always adopts a particular level-$k$ strategy, they are assumed to adopt each of the level-$k$ strategies with a particular probability (i.e., the opponent's strategy is a mixture over pure level-$k$ strategies).
+
+Iterative reasoning strategies can explain non-equilibrium play in a range of games, such as the $p$-beauty contest game [@nagel1995unraveling], dominance solvable games [@camerer2004cognitive], and various standard normal form games [@costa2001cognition].
 In the present study, we endow our computer opponents with limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
-In two experiments, participants face the same opponent (Experiment 1) or same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, a structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
-To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of the opponent and the similarity of the games.
-Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a more habiltual and cognitively less demanding strategy in the later stages of the games.
+In two experiments, participants face the same opponent (Experiment 1) or the same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, the structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
+To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of their opponent and the similarity of the games.
+Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a more habitual and cognitively less demanding strategy in the later stages of the games.
 
@@
 
-In the first experiment, we aim to test learning transfer through making participants face the same computer opponent in three sequential games that vary in similarity.
+In the first experiment, we aim to test learning transfer by making participants face the same computer opponent with a limited level of iterative reasoning in three sequential games that vary in similarity.
+If participants are able to learn the limitations of their opponent's iterative reasoning and generalize this to new games, their performance in (the early stages of) later games should be higher than expected if they were to completely learn a new strategy in each game.
 
@@
 ### Participants and Design
+
 A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
 The mean age of participants was 31.2 years.
-Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The experiment used a 2 (computer opponent: level 1 or level 2) by 3 (games: rock-paper-scissors, fire-water-grass, numbers) design, with repeated measures on the second factor.
+Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance (£1.06 on average).
+The experiment had a 2 (computer opponent: level 1 or level 2) by 3 (games: rock-paper-scissors, fire-water-grass, numbers) design, with repeated measures on the second factor.
 Participants were randomly assigned to one of the two levels of the first factor.
@@
 Participants played the three games against their computer opponent.
-These games were rock-paper-scissors, fire-water-grass, and the numbers game.
-A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between the two player's actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
+These games were Rock-Paper-Scissors, Fire-Water-Grass, and the Numbers game.
+A typical Rock-Paper-Scissors game (hereafter RPS) is a 3x3 zero-sum game, with a cyclical hierarchy between the two player's actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
 If one player chooses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
@@
 RPS has a unique mixed-strategy Nash equilibrium, which consists of each player in each round randomly selecting from the three options with uniform probability.
+
 The Fire-Water-Grass (FWG) game is identical to RPS in all but action labels: Fire burns grass, water extinguishes fire, and grass absorbs water.
-We use this game as we are interested in whether learning is transferred in a fundamentally similar game where the only difference is in the name of the possible actions.
+We use this game as we are interested in whether learning is transferred in a fundamentally similar game where the only difference is in the label of the possible actions.
 This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level-1 or level-2 player.
-Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'', is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
+Crucially, learning simple contingencies such as "If I played rock on the previous round, playing scissors next will likely result in a win", is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
 
@@
 As a best response to a uniformly random action is itself a random action, defining a level-0 player in such a way would make a level-1 opponent's strategy much harder to discern.
-Because we are mainly interested in generalization of knowledge of an opponent's strategy to other games, which rests on good knowledge of this strategy, we opted for this more deterministic formulation of a level-0 player (whilst also introducing some randomness in the computer opponent's play).
-A level-2 computer opponent, will assume in turn that the participant is a level-1 opponent, playing according to the strategy just described.
-We also introduced some noise over the actions of computer opponents making them play randomly in 10\% of all trials.
+Because we are mainly interested in generalization of knowledge of an opponent's strategy to other games, which requires good knowledge of this strategy, we opted for this more deterministic formulation of a level-0 player.
+The level-2 computer opponent assumes in turn that the participant is a level-1 opponent, playing according to the strategy just described.
+To make the computer opponent's strategy not too obvious, we introduced some randomness in actions of computer opponent, making them play randomly in 10\% of all trials.
 Note that at all levels, the strategies are contingent on the actions taken in the previous round.
-The choice of this type of strategy is consistent with evidence that humans strategically use information from last round play of their opponents in zero sum games [@batzilis; @wang2014social].
+The choice of this type of strategy is consistent with evidence that humans strategically use information from last round play of their opponents in zero-sum games [@batzilis; @wang2014social].
+Table \@ref(table:1) shows an example of the computer opponent's actions in response to the previous round play.
 
 \begin{table}[bth!]
+\caption{Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round.}
 \centering
+\label{table:1}
 \begin{tabular}{||c c | c c||} 
@@
 \end{tabular}
-\caption{Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round.}
-\label{table:1}
 \end{table}
@@
 An example of the interface for the RPS game is provided in Figure\ \@ref(fig:feedback-rps-exp2).
-On each round, the human player chooses an action, and after a random delay, is shown the action chosen by the computer opponent, and the outcome of that round.
-A history of the chosen actions over all rounds is available in the centre panel.
-A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
+On each round, the human player chooses an action, and after a random delay (between 0.5 and 3 seconds) is shown the action chosen by the computer opponent and the outcome of that round.
+<!-- A history of the chosen actions over all rounds is available in the centre panel.
+**MS: was this not only the case for Experiment 2?
+** --> A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
 The score was calculated as the number of wins minus the number of losses.
 Ties did not affect the score.
-In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-Each point is worth £0.02.
-After playing all the games, participants were asked questions about their beliefs about the computer opponent, related to whether they thought they learned their opponent's strategy, and how difficult they found playing against their particular opponent.
+In order to incentivise the participants to maximise the number of wins against their opponent, players were paid a bonus at the end of the experiment proportional to their final score (each point was worth £0.02).
+After playing all the games, participants were asked questions about their beliefs about the computer opponent, related to whether they thought they learned their opponent's strategy, and how difficult they found playing against their opponent.
 They were then debriefed and thanked for their participation.
@@
 Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
-**MS: Need to check test results and report GG degrees of freedom, etc.** **...IG: I thought GG corrections only apply when there is violation of sphericity....
-according to Mauchly Test there isn't a violation here.
-Should we report them anyway in this experiment?
-**
 
@@
 
-afex::aov_car(
+tmp <- afex::aov_car(
   block_score ~ game.f*condition*block + Error(human_id/(game.f*block))
@@
 We did not expect positive scores for the RPS game, as it was the first game played and there was no opportunity for learning about the opponent's strategy.
-Scores in this game was indeed not significantly different from 0 ($t(148.85) = 1.04$ , $p = .89$).
+Scores in this game were indeed not significantly different from 0 ($t(148.85) = 1.04$ , $p = .89$).
 
@@
 We expected better transfer between more similar games (i.e.
-better transfer from RPS to FWG than from RPS/FWG to Numbers), and worse transfer for the more sophisticated level 2 agent.
+better transfer from RPS to FWG than from RPS/FWG to Numbers), and worse transfer for the more sophisticated level-2 agent.
 Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents.
-To explore this, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game ($F(1.84,91.77) = 3.35$, $\eta^{2}  = 0.04$,  $p = .043$, Greenhouse-Geisser correction to degrees of freedom applied to correct for non-sphericity).
-We then run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
+To explore this, we used a 2 (Condition: Level 1, Level 2) by 3 (Game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants.
+There was a main effect of Game ($F(1.84,91.77) = 3.35$, $\eta^{2}  = 0.04$,  $p = .043$, Greenhouse-Geisser correction applied to the degrees of freedom to correct for non-sphericity).
+**MS: was this the only significant effect?
+If so, people might wonder why we next run analyses for each combination of player and game** We then ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(150) = 3.96$, $p < .001$) and Numbers ($t(150) = 3.74$, $p < .001$).
@@
 In Experiment 2, we aimed to obtain a stronger test of learning transfer.
-Instead of facing a single level-1 or level-2 opponent throughout all games, participants face both types of opponents sequentially in this experiment.
-To perform well against both opponents, participants would need to learn distinct strategies in each game.
+Instead of facing a single level-1 or level-2 opponent throughout all games, participants now faced both types of opponent.
+To perform well against both opponents, participants would need to learn distinct strategies against these opponents.
 To reduce effects of increased memory load due to facing distinct opponents, we provided participants access to the history of play against an opponent within each game (see Figure \@ref(fig:feedback-rps-exp2)).
-Finally, we changed the third game to a penalty shootout game, with participants aiming to score a goal and opponents playing the role of goal keepers.
+Finally, we changed the third game to a penalty Shootout game, with participants aiming to score a goal and opponents playing the role of goal keepers.
 Whilst this game has the same number of actions as the first two (aim left, center, or right), it is strategically dissimilar.
@@
 The average age was 30.2 years, and the mean duration to complete the task was 39 minutes.
-Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
+Participants received a fixed fee of £2.5 for completing the experiment and a performance dependent bonus (£1.32 on average).
 
@@
 
-The three games the participants played were Rock-Paper-Scissors (RPS), Fire-Water-Grass (FWG), and the penalty Shootout game.
-The first two games were identical to the ones used in the first experiment.
-In the final game (Shootout) participants took the role of the a football (soccer) player in a penalty situation, with the computer opponent taking the role of the goalkeeper.
-Players had the choice between three actions: shooting the football to the left, right or centre of the goal.
+Participants played three games: Rock-Paper-Scissors (RPS), Fire-Water-Grass (FWG), and the penalty Shootout game.
+The first two games were identical to the ones used in Experiment 1.
+In the Shootout game, participants took the role of the a football (soccer) player in a penalty situation, with the computer opponent taking the role of the goalkeeper.
+Players had the choice between three actions: shooting the football to the left, right, or centre of the goal.
 Similarly, the goalkeeper chooses between defending the left, right, or centre of the goal.
@@
 There is no possibility of ties in this game.
-Figure\ \@ref(fig:screenshot-shootout) shows a snapshot of play in the shootout game.
-What makes this game different to the other games is that there are two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend ''right'' in the next round, they can win by either choosing to shoot ''left'' or ''center''.
+Figure\ \@ref(fig:screenshot-shootout) shows a snapshot of play in the Shootout game.
+What makes this game different to the other games is that there are now two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend "right" in the next round, they can win by either choosing to shoot "left" or "center".
 A level-1 shooter who thinks that their goalkeeper opponent will repeat their last action has thus two possible best responses.
@@
 
+As in Experiment 1, all the games have a unique mixed-strategy Nash equilibrium consisting of uniformly random actions.
+If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
+Evidence of sustained wins would indicate that participants have learned to exploit patterns in their opponents' play.
+
 ```{r screenshot-shootout, fig.cap = "Screenshot of the shootout game", fig.align='center'}
@@
 
-Participants played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
-Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
-Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
-Participants start by facing one of the opponents in stage one, then face the other in stage two.
-This is repeated in the same order in stages 3 and 4.
+Participants played 3 games sequentially against both level-1 and level-2 computer opponents.
+As in Experiment 1, the computer opponents retained the same strategy throughout the 3 games.
+Participants faced each opponent twice in each game.
+Each game was divided into 4 stages, numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
+Participants started by facing one of the opponents in stage one, then the other in stage two.
+This was repeated in the same order in stages 3 and 4.
 Which opponent they faced first was counterbalanced.
-All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
+All participants engaged in the three games (RPS, FWG and Shootout) in this exact order, and were aware that their opponent could not cheat and chose their action simultaneously with the player, without knowing their choices beforehand.
 In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
 During those 3 seconds, participants could not choose an action and had to wait for the timer to run out.
-A small random delay between 0.5 and 3 seconds was also introduced before the computer agent made their choice, as a way of simulating a real human opponent thinking time.
+A random delay between 0.5 and 3 seconds was again introduced before the choice of the computer agent was revealed, as a way of simulating a real human opponent's decision time.
 After each round, participants were given detailed feedback about their opponent's action and whether they won or lost the round.
 Further information about the history of play in previous rounds was also provided and participants could scroll down to recall the full history of each interaction against an opponent in a particular stage of a game.
-The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-As in the first experiment, all the games have a unique mixed-strategy Nash equilibrium consisting of uniformly random actions.
-If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
-Evidence of sustained wins would indicate that participants have learned to exploit patterns in their opponents' play.
+The number of wins, losses and ties in each game were displayed at the top of the screen, and this scoreboard was reinitialised to zero at the onset of a new stage game.
 
@@
 
-Participants scores are depicted in Figure \ref{fig:exp2-score-by-opp}.
-The RPS game had the lowest average score per round ($M = 0.194$, SD = 0.345) followed by FWG ($M = 0.27$, SD = 0.394) and finally the Shootout game ($M = 0.289$, SD = 0.326).^[ A higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
+Participants' scores are depicted in Figure \ref{fig:exp2-score-by-opp}.
+The RPS game had the lowest average score per round ($M = 0.194$, SD = 0.345) followed by FWG ($M = 0.27$, SD = 0.394) and finally the Shootout game ($M = 0.289$, SD = 0.326).^[A higher score in the Shootout game is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
 Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33)] Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: $t(49) = 6.26$, $p < .001$; FWG: $t(49) = 7.25$, $p < .001$; Shootout: $t(49) = 13.61$, $p < .001$).
+To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the Shootout game by subtracting the average score per round of a random strategy (0.33).] Using one-sample t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: $t(49) = 6.26$, $p < .001$; FWG: $t(49) = 7.25$, $p < .001$; Shootout: $t(49) = 13.61$, $p < .001$).
 
@@
 This showed a main effect of Game ($F(1.85,88.7) = 11.81$, $\eta^{2} = 0.04$,  $p < .001$).
-Post-hoc pairwise comparisons between games (p-values adjusted using Holm method for multiple comparisons) indicate performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS ($t(96) =2.53$, $p = .025$), and performance in the Shootout game significantly higher than in FWG ($t(96) = 2.32$, $p = .025$).
+Post-hoc pairwise comparisons between games ($p$-values adjusted using Holm method for multiple comparisons) indicate performance in the games increased steadily throughout the experiment, with FWG performance significantly higher than RPS ($t(96) =2.53$, $p = .025$), and performance in the Shootout game significantly higher than in FWG ($t(96) = 2.32$, $p = .025$).
 Whilst the ANOVA shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type ($F(1.7, 81.82) = 5.31$ ,$\eta^{2} = 0.02$,  $p = .01$).
-Follow-up analysis shows that when facing level-1 agents, scores increase steadily after each game, with FWG score significantly higher than RPS ($t(191) = 2.70$, $p = .03$) and Shootout scores in turn significantly higher than FWG  ($t(191) = 3.05$, $p = .01$).
+Follow-up analysis shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS ($t(191) = 2.70$, $p = .03$) and Shootout scores in turn significantly higher than FWG  ($t(191) = 3.05$, $p = .01$).
 There was no significant difference between average scores on any two games when facing level-2 agents however.
@@
 
-To measure transfer between games, we again focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with the opponent (see Figure \ref{fig:exp2-early-score-by-opp}).
+To measure transfer between games, we again focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
 We performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) repeated-measures ANOVA, with the first factor varying between participants.
 This showed a main effect of Game ($F(1.94,92.98) = 7.67$, $\eta^{2} = 0.04$,  $p < .001$).
-We then run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
+**MS: Again, if there is no interaction, there might not be justification for running tests per opponent and game **
+We then ran statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(271) = 4.99$, $p < .001$) and Shootout ($t(271) = 6.66$, $p < .001$).
 For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ($t(271) = 4.41$, $p < .001$).
-Unike in experiment 1, there is also evidence of transfer to the dissimilar game of Shootout ($t(271) = 3.22$, $p = .004$).
+Unlike in Experiment 1, there is also evidence of transfer to the dissimilar Shootout game ($t(271) = 3.22$, $p = .004$).
 The early round scores in the similar FWG games for level-1 and level-2 facing players are not significantly different from each other.
@@
 
-The results of Experiment 2 confirm the earlier results of Experiment 1 about players adapting their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
-Knowledge about both types of opponents were transfered to both the similar and dissimilar game.
-However, transfer to the dissimilar game was easier when facing the more sophisticated agent.
+The results of Experiment 2 confirm the earlier results of Experiment 1 in a situation where participants need to learn about two distinct opponents.
+As in Experiment 1, participants adapted their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
+Knowledge about both types of opponents were transferred to both the similar and dissimilar game.
+However, transfer to the dissimilar game was easier when facing the less sophisticated agent.
 
@@
 The other models adapted their play to the opponent, either by reinforcing successful actions in each game (reinforcement learning), or by determining the type of opponent through Bayesian learning (Bayesian Cognitive Hierarchy models).
-We also include the Expected Weighted Attraction (EWA) model, which is a popular model in behavioural economics.
-
-In the following, we will describe the models in more detail, and provide some intuition into how they they learn about the game and/or the opponent.
-We use the following notation: In each game $g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}$, on each trial $t$, the participant chooses an action $a_t \in \mathcal{A}_g$, and the opponent chooses action $o_t \in \mathcal{A}_g$, where $\mathcal{A}_g$ is the set of allowed actions in game $g$, e.g.
+We also include the (self-tuning) Expected Weighted Attraction (EWA) model, which is a popular model in behavioural economics.
+
+In the following, we will describe the models in more detail, and provide some intuition into how they implement learning about the game and/or the opponent.
+Throughout, we use the following notation: In each game $g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}$, on each trial $t$, the participant chooses an action $a_t \in \mathcal{A}_g$, and the opponent chooses action $o_t \in \mathcal{A}_g$, where $\mathcal{A}_g$ is the set of allowed actions in game $g$, e.g.
 $\mathcal{A}_\text{RPS} = \{R,P,S\}$.
@@
 We use the state variable $s_t = \{a_{t-1},o_{t-1}\}$ to denote the actions taken in the previous round $t-1$ by the participant and opponent.
+The initial state is empty, and we assume that the action at a first encounter of an opponent in a game is chosen at random.
 
@@
 The resulting RL model learns a $Q$-value [@watkins1992q] for each state-action pair:
-$$ Q_{t+1}(s_{t},a_{t}) = Q_{t}(s_{t},a_{t}) + \alpha \left( r_{t}  - Q(s_{t},a_{t}) \right) ,$$  
+$$Q_{t+1}(s_{t},a_{t}) = Q_{t}(s_{t},a_{t}) + \alpha \left( r_{t}  - Q(s_{t},a_{t}) \right) ,$$
 where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$, and $\alpha \in [0,1]$ the learning rate.
-For instance, $Q_t(\{R,S\},P)$ denotes the value of taking action  ''Paper'' this round if the player's last action was ''Rock'' and the opponent played ''Scissors''.
+For instance, $Q_t(\{R,S\},P)$ denotes the value of taking action  "Paper" this round if the player's last action was "Rock" and the opponent played "Scissors".
 Actions are taken according to a softmax rule:
 $$P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}, $$ 
-where the inverse temperature parameter $\lambda$ determines the consistency of the strategu (the higher $\lambda$, the more often the action with the highest $Q$-value is chosen.
-While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different state $\mathcal{S}_g$ and action space $\mathcal{A}_g$, and there is no simple way to map states and actions between games.
+where the inverse temperature parameter $\lambda$ determines the consistency of the strategy (the higher $\lambda$, the more often the action with the highest $Q$-value is chosen.
+While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different state space $\mathcal{S}_g$ and action space $\mathcal{A}_g$, and there is no simple way to map states and actions across games.
 
@@
 The self-tuning Experience Weighted Attraction (EWA) model [@ho2004economics] combines two seemingly different approaches, namely reinforcement learning and belief learning.
-Belief learning models are based on the assumption that players keep track of the frequency of past actions and best respond to that.
+Belief learning models are based on the assumption that players keep track of their opponent's frequency of past actions, and best respond to that.
 By contrast, reinforcement learning does not explicitly take into account beliefs about other players, but simply increases the probability of repeating a more rewarding action.
@@
 The EWA model is based on updating ``Attractions'' for each action over time given a particular state.
-The attraction of action $a$ at time $t$ given state $s$ composet of lkast round play is written $A_{t}(a, s)$ and is updated as
+The attraction of action $a$ at time $t$ given state $s$ is denoted as $A_{t}(a, s)$ and updated as
 $$ A_{t+1}(a,s) =  \frac{\phi \ N(t) \ A_{t}(a,s) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} $$
-where $I(x)$ is an indicator function which takes the value 1 is its argument is true, and 0 otherwise, and $R(a,o_t)$ is the reward that would be obtained from playing action $a$ against opponent action $o_t$, which equals the actual obtained reward when $a = a_t$, and otherwise is a counterfactual reward that would have been obtained if a different action were taken.
-Unlike reinforcement learning, this uses knowledge of the rules of the game to allow reinforcing actions that were not taken.
-We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play [@cheung1994learning].
-While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].
+where $I(x)$ is an indicator function which takes the value 1 is its argument is true and 0 otherwise, and $R(a,o_t)$ is the reward that would be obtained from playing action $a$ against opponent action $o_t$.
+$R(a,o_t)$ equals the actual obtained reward when $a = a_t$, and otherwise is a counterfactual reward that would have been obtained if a different action were taken.
+Unlike reinforcement learning, this uses knowledge of the rules of the game to allow reinforcing actions that were not actually taken by the rewards they would have provided.
+The parameter $\delta$ reflects the weight given to such counterfactual rewards.
+Setting $\delta = 0$ leads to reinforcement only of actions taken, while positive values of $\delta$ makes the update rule take into account foregone payoffs, which is similar to weighted fictitious play [@cheung1994learning].
 $N(t)$ represents an experience weight and can be interpreted as the number of "observation-equivalents" of past experience.
 We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
-For details on how the various parameters are self-tuned, please refer to [@ho2004economics].
+**MS: need to better describe what $\phi$ is, and how $N(t)$ is determined.** In the earlier version of the EWA model [@camerer1997experience], $\phi$ and $\delta$ were free parameters.
+In the self-tuning EWA model [@ho2004economics], the values of $\delta$ and $\phi$ are learnt from experience.
+For details on how this is done, we refer the reader to [@ho2004economics].
 **MS: Should describe how the parameters are self-tuned with equations.
 IG: There are many equations for each of the parameters update, phi, delta and N...I'm concerned it would make for cumbersome reading, especially since EWA doesn't really fit well anyway.
-I've added that details of updates can be found in original camerer paper.**
+I've added that details of updates can be found in original camerer paper.
+MS: If it's three additional equations, that's not a big deal really.
+**
 
@@
 In what we call the Bayesian Cognitive Hierarchy (BCH) model, the participant attempts to learn the type of opponent they are facing through Bayesian learning.
-We assume the participant considers the opponent could be either a level 0, level 1, or level 2 player, and starts with a prior belief that each of these types is equally likely.
-They then use observations of the opponents actions to infer a posterior probability of each type:
+For present purposes, we assume participants consider the opponent could be either a level 0, level 1, or level 2 player, and start with a prior belief that each of these types is equally likely.
+They then use observations of the opponent's actions to infer a posterior probability of each type:
 $$P(\text{level}=k | \mathcal{D}_{t})  \propto  P(\mathcal{D}_{t}|\text{level}=k ) \times P(\text{level}=k)$$
@@
 We assume a participant chooses an action by using the softmax function over the best response to predicted actions:
-$$\begin{aligned} B_t(a) &= \sum_{k = 0}^2 \sum_{o \in \mathcal{A}_g} b(a,o) P_k(o|s_{t})  P(\text{level}=k|\mathcal{D}_{t-1})\\
+$$\begin{aligned} B_t(a) &= \sum_{k = 0}^2 \sum_{o \in \mathcal{A}_g} b(a,o) f_k(o|s_{t})  P(\text{level}=k|\mathcal{D}_{t-1})\\
 P_t(a) &= \frac{\exp\{\lambda B_t(a) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{ \lambda B_t(a')\}} \end{aligned}$$
 where $b(a,o) = 1$ if action $a$ is a best response to opponent's action $o$ (i.e.
-it leads to a win), and $P_k(o|a_{t-1},o_{t-1}) = \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o|a_{t-1},o_{t-1})$ is the probability that a level $k$ agent takes action $o$, as also used in the likelihood above.
+it leads to a win).
+<!-- and $P_k(o|a_{t-1},o_{t-1}) = \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o|a_{t-1},o_{t-1})$ is the probability that a level $k$ agent takes action $o$, as also used in the likelihood above.-->
 
 Unlike the models above, the BCH model allows for between-game transfer, as knowledge of the level of the opponent can be used to generate predictions in games that have not been played before.
-This generalization is done simply by using the posterior $P(\text{level} = k|\mathcal{D}_T)$ from the previous game as rhe prior distribution in the next game.
+This generalization is done simply by using the posterior $P(\text{level} = k|\mathcal{D}_T)$ from the previous game as the prior distribution in the next game.
 However, the participant might also assume that the level of reasoning of their opponent does not generalize over games.
@@
 For both experiments, we fitted all models to individual participant data by maximum likelihood estimation.
-We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
+**MS: need to mention the use of e.g.
+DEoptim** We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
 <!--, the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
@@
 
-For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NBT), as well as a Reinforcement Learning model with state space consisting of last round play (RL), and finally a self-tuning EWA model with the same state space (EWA).
-
-In Experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two type of opponent model transfer.
-We can have transfer within games, between the first and second interaction with the opponent.
-We can also have transfer between games, as in e.g.
+For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NBT), as well as a reinforcement learning (RL), and finally a self-tuning EWA model with the same state space (EWA).
+
+In Experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two types of opponent model transfer.
+We can have transfer *within* games between the first and second interaction with the opponent.
+In addition, we can also have transfer *between* games, as in e.g.
 transferring a learned opponent model from RPS to FWG.
-Therefore, we fitted a total of three versions of the Bayesian Cognitive Hierarchy model: BCH\_BT allows for both within and between game transfer (between game transfer without within game transfer is implausible); BCH\_NBT allows for within but not between game transfer; BCH\_NT allows for no transfer within or between games.
-For Reinforcement learning models, because RL models can't account for between game transfer due to change in state and action space, we can only have models that allowing for within game transfer (RL\_TR) or with no transfer within games (RL\_NT).
-Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (EWA\_TR) or without transfer (EWA\_NT).
-Counting the base model with random play (Nash) we therefore fit a total of 8 models for Experiment 2.
+Therefore, we fitted a total of three versions of the Bayesian Cognitive Hierarchy model: BCH\_BT allows for both within and between game transfer (between game transfer without within game transfer is implausible); BCH\_WT allows only for within-game transfer, but not between game transfer; BCH\_NT allows for no transfer within or between games.
+As the RL model can't account for between game transfer due to a change in state and action space, we can only have models that allowing for within game transfer (RL\_WT) or with no transfer within games (RL\_NT).
+Likewise, we fit both a self tuning EWA model with (EWA\_WT) and without (EWA\_NT) within-game transfer.
+Including the baseline model of random play (Nash), we therefore fitted a total of 8 models for Experiment 2.
 
@@
 exp1_comp_results <- read.csv(file="../exp1_all_results.csv")
-exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Nash","BCH_BT","BCH_NBT", "RL","EWA")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])
+exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Nash","BCH_BT","BCH_WT", "RL","EWA")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])
 
@@
 
-  best_model <- c("Nash","BCH_BT","BCH_NBT", "RL","EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)]
+  best_model <- c("Nash","BCH_BT","BCH_WT", "RL","EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)]
   # 
@@
 dat_by_model <- temp %>% group_by(Best_model,t) %>% summarize(model_acc_sum = mean(acc_sum))
-
-```
+```
+
+**MS: Please present the models in the figures in the order mentioned in text (i.e., Nash, RL, EWA, BCH), and when providing versions of each, do so in the same order as well, i.e. x_NT, x_WT, x_BT**
 
@@
 We can see that the RL model clearly described most participants' behaviour best, followed by the random (Nash) model.
-Only a few participants were best described by one of the BCH models, or the EWA model.
-Looking at BIC weights, we confirm this as seen in  Figure \ \@ref(fig:xp1-BIC-weigths).
+Only a few participants were best described by one of the BCH models or the EWA model.
+Looking at BIC weights (Figure \ \@ref(fig:xp1-BIC-weigths)), we confirm this.
 RL models have high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, which fits the picture drawn by the histogram.
+**MS: The BIC weight don't add much information, so maybe we could leave them out **
+
 ```{r, include=FALSE}
@@
 exp1_BIC_weights[,2:ncol(exp1_comp_BICs)] <- t(apply(exp1_comp_BICs[,-1], 1, function(i) exp(-0.5*(i-min(i)) )))
-colnames(exp1_BIC_weights) <- c("ID","Nash","BCH_BT","BCH_NBT","RL","EWA")
+colnames(exp1_BIC_weights) <- c("ID","Nash","BCH_BT","BCH_WT","RL","EWA")
 exp1_BIC_weights[,-1] <- t(apply(exp1_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
@@
 
-In Experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that the RL model was again more successful than the Bayesian Cognitive Hierarchy models (with or without transfer) in fitting participants' action choices.
+In Experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that the RL model was again more successful than the Bayesian Cognitive Hierarchy models (with or without transfer) and the EWA model in fitting participants' action choices.
 <!--  In Experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
@@
 
-exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Nash","BCH_BT","BCH_NBT", "BCH_NT", "RL_NT","RL_TR","EWA_NT","EWA_TR")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])
+exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Nash","BCH_BT","BCH_WT", "BCH_NT", "RL_NT","RL_WT","EWA_NT","EWA_WT")[apply(exp2_comp_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","QL_states_BIC","QLS_within_Tr_BIC","STEWA_NT_BIC","STEWA_Tr_BIC")],1,which.min)])
 
@@
 exp2_BIC_weights[,2:ncol(exp2_comp_BICs)] <- t(apply(exp2_comp_BICs[,-1], 1, function(i) exp(-0.5*(i-min(i)) )))
-colnames(exp2_BIC_weights) <- c("ID","Nash","BCH_BT","BCH_NBT", "BCH_NT", "RL_NT","RL_TR","EWA_NT","EWA_TR")
+colnames(exp2_BIC_weights) <- c("ID","Nash","BCH_BT","BCH_WT", "BCH_NT", "RL_NT","RL_WT","EWA_NT","EWA_WT")
 exp2_BIC_weights[,-1] <- t(apply(exp2_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
@@
 If indeed most participants adopt a reinforcement learning strategy, they should not be able to transfer their learning to the early rounds of a new game.
-In order to investigate this discrepancy further, we plot the likelihood by trial for each game and three strategies: RL, Bayesian Cognitive Hierarchy models with between-game transfer, and the random (Nash) strategy.
-Figure\ \@ref(fig:exp1-lik-by-tr) shows that in the later games of Experiment 1, the likelihood for the BCH models is higher than that of the other models in the initial rounds of the games.
+In order to investigate this discrepancy further, we plot the likelihood by trial for each game and three strategies: reinforcement learning (RL), Bayesian Cognitive Hierarchy with between-game transfer (BCH\_BT), and the random (Nash) strategy.
+Figure\ \@ref(fig:exp1-lik-by-tr) shows that in the initial rounds of the the later games in Experiment 1, the likelihood for the BCH models is higher than that of the other models.
 However, over time, the likelihood of the RL model increases and exceeds that of BCH model.
@@
 The same pattern holds for Experiment 2 (Figure\ \@ref(fig:exp2-lik-by-tr)).
-Again, the BCH model with between-game transfer has the highest likelihood in the early stages of the later games (apart from stage 1 of the shootout game, where the RL model is better).
+Again, the BCH\_BT model with between-game transfer has the highest likelihood in the early stages of the later games (apart from stage 1 of the shootout game, where the RL model is better).
 In later rounds, the likelihood of the RL model exceeds that of the BCH model.
@@
   dplyr::group_by(game,condition, round) %>%
-  dplyr::summarise(Nash_posterior = mean(post_Nash, na.rm = TRUE),
-                   RL_posterior = mean(post_RL, na.rm = TRUE),
-            BCH_BT_posterior = mean(post_Bayes_Tr, na.rm = TRUE))
+  dplyr::summarise(Nash = mean(post_Nash, na.rm = TRUE),
+                   RL = mean(post_RL, na.rm = TRUE),
+            BCH_BT = mean(post_Bayes_Tr, na.rm = TRUE))
 
@@
 
-data_long_post1 <- gather(mean_post_1, strategy, probability, Nash_posterior, RL_posterior,BCH_BT_posterior, factor_key=TRUE)
+data_long_post1 <- gather(mean_post_1, strategy, probability, Nash, RL,BCH_BT, factor_key=TRUE)
 
@@
   geom_line() +
-  facet_grid(game~condition)
-
-```
-
-In Experiment 1, a likelihood-ratio test shows that the HMM model with switching fits significantly better than the non-switching one ($p < .001$).
-**MS: we should really use a bootstrapped Likelihood Ratio test here ** This provides further statistical evidence in favour of the hypothesis that participants switch between strategies.
+  facet_grid(game~condition) +
+  ylab("posterior probability")
+
+```
+
+In Experiment 1, a likelihood-ratio test shows that the HMM model with switching fits significantly better than the non-switching one, $\chi^2(6) = `r round(-2*as.numeric(logLik(fmod1_noswitch)) - (-2*as.numeric(logLik(fmod1))),2)`$, $p < .001$.
+We should note that as the no switch model involves restricting parameters of the switching model on the bounds of the parameter space, the asymptotic $p$-value of this test may not be reliable.
+The switching model (AIC = `r round(-2*as.numeric(logLik(fmod1)) + 2*8,2)`, BIC = `r round(-2*as.numeric(logLik(fmod1)) + 8*log(nrow(fmod1@dens)),2)`) fits also better than the non-switching model (AIC = `r round(-2*as.numeric(logLik(fmod1_noswitch)) + 2*2,2)`, BIC = `r round(-2*as.numeric(logLik(fmod1_noswitch)) + 2*log(nrow(fmod1_noswitch@dens)),2)`) according to the AIC and BIC.
+<!-- **MS: we should really use a bootstrapped Likelihood Ratio test here ** --> This provides further statistical evidence in favour of the hypothesis that participants switch between strategies.
 Figure\ \@ref(fig:exp1-posteriors-plot) depicts the average (across participants) posterior probabilities of each state (strategy), as a function of trial and opponent faced.
@@
 
-fmod <- fit(mod, emcontrol=em.control(random.start=TRUE))
+fmod2 <- fit(mod, emcontrol=em.control(random.start=TRUE))
+
+# No switching. Force off diagonal initial elements of transtion matrix to 0
+trstart <- matrix(c(1,0,0,0,1,0,0,0,1),ncol=3)
+transition <- list()
+transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
+transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
+transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
+
+mod2_noswitch <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
+
+fmod2_noswitch <- fit(mod2_noswitch, emcontrol=em.control(random.start=FALSE))
+
 ```
@@
 
-exp2_lik_by_trial["post_RLw"] <- forwardbackward(fmod)$gamma[,1]
-exp2_lik_by_trial["post_Nash"] <- forwardbackward(fmod)$gamma[,2]
-exp2_lik_by_trial["post_Bayes_Tr"] <- forwardbackward(fmod)$gamma[,3]
+exp2_lik_by_trial["post_RLw"] <- forwardbackward(fmod2)$gamma[,1]
+exp2_lik_by_trial["post_Nash"] <- forwardbackward(fmod2)$gamma[,2]
+exp2_lik_by_trial["post_Bayes_Tr"] <- forwardbackward(fmod2)$gamma[,3]
 
@@
   dplyr::group_by(game,stage, round) %>%
-  dplyr::summarise(Nash_posterior = mean(post_Nash, na.rm = TRUE),
-                   RL_posterior = mean(post_RLw, na.rm = TRUE),
-            BCH_BT_posterior = mean(post_Bayes_Tr, na.rm = TRUE))
+  dplyr::summarise(Nash = mean(post_Nash, na.rm = TRUE),
+                   RL = mean(post_RLw, na.rm = TRUE),
+            BCH_BT = mean(post_Bayes_Tr, na.rm = TRUE))
 
@@
 
-data_long_post2 <- gather(mean_post_2, strategy, probability, Nash_posterior, RL_posterior, BCH_BT_posterior, factor_key=TRUE)
+data_long_post2 <- gather(mean_post_2, strategy, probability, Nash, RL, BCH_BT, factor_key=TRUE)
 
@@
   geom_line() +
-  facet_grid(game~stage)
-
-```
-
-The switching model in Experiment 2 is also significantly better than the restricted non-switching model ($p < .001$).
+  facet_grid(game~stage) +
+  ylab("posterior probability")
+
+```
+
+In Experiment 2, the switching model (AIC = `r round(-2*as.numeric(logLik(fmod2)) + 2*8,2)`, BIC = `r round(-2*as.numeric(logLik(fmod2)) + 8*log(nrow(fmod2@dens)),2)`) again fits better than the restricted non-switching model (AIC = `r round(-2*as.numeric(logLik(fmod2_noswitch)) + 2*2,2)`, BIC = `r round(-2*as.numeric(logLik(fmod2_noswitch)) + 2*log(nrow(fmod2_noswitch@dens)),2)`), $\chi^2(6) = `r round(-2*as.numeric(logLik(fmod2_noswitch)) - (-2*as.numeric(logLik(fmod2))),2)`$, $p < .001$.
 The posterior probabilities of the strategies (Figure\ \@ref(fig:exp2-posteriors-plot)) show very clear evidence of strategy switching across games and stages, from using a BCH model in the initial rounds to an RL strategy later on.
@@
 
-The results of our first experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to a similar game.
+The results of our first experiment show that the majority of participants learnt to adapt to their opponent's strategy over multiple interactions, and generalised this learning to a similar game.
 Performance in early rounds indicated that transfer to the more dissimilar game was moderated by the degree of sophistication of the opponent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
-In the second experiment, participants faced both types of opponents, which allows for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent within a game.
+**MS: there was stronger evidence of moderation by game!** In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
 In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
-Experiment 2 also offers more opportunities to test transfer of a learnt opponent model.
+Experiment 2 also offers more opportunities to test transfer of a learnt opponent model, as we could assess both within and between game transfer.
 The results on learning transfer confirmed the findings from the first experiment.
@@
 A player cannot transfer what they have not learnt.
-
-What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
+**MS: again, there was stronger evidence of moderation by game!**
+
+What exactly did the players learn in the first game (RPS) that allowed them to beat their opponent in the later games (FWG, and Numbers or Shootout)?
 what did the players learn specifically about their opponent's strategy and what form did this learning take?
-
 One possible answer is that participants learned simple rules based on last round play.
@@
 There is no simple way to map "play scissors whenever my opponent played rock in last round" in the RPS game to "play grass whenever my opponent played fire in last round".
-Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this quickly enough: Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
+Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this: Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
 Secondly, a reinforcement learning strategy would fare equally well against the level-1 and level-2 opponent.
@@
 Yet, we found that participants performed better against the level-1 opponent compared to the level-2 opponent.
-The difference in performance between the two types of opponent indicate that the actions of the more sophisticated level-2 opponent, or the best response to these, were somehow more difficult to predict.
+The difference in performance between the two types of opponent indicates that the actions of the more sophisticated level-2 opponent, or the best response to these, were somehow more difficult to predict.
 
@@
 Because of the cyclicity in action choices (e.g., rock beats scissors, scissors beats paper, paper beats rock), it is possible to beat a level-2 opponent most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
-This is a rule that wins and is transferable to other games as it does not depend on action labels.
+This is a rule that wins and is transferable to other games, as it does not depend on action labels.
 In the same vein, a heuristic that beats a level-1 player can be stated as "Choose the action that would have been beaten by my previous action".
-Intuitively, it seems that the heuristic for the level-2 player is simpler than that for the level-1 player, which is at odds with the difference in performance.
+Intuitively, it seems that this heuristic for a level-2 player is simpler than that for a level-1 player, which is at odds with the finding that participants performed better against the level-1 opponent.
 

### 2021-08-26 Report/paper_draft_2021.tex
pass through latest draft. Still a few things to resolve

--- 2021-07-05 Report/paper_draft_2021.tex
@@
 computer agents with human-like limited degrees of iterated reasoning. In two experiments, we find that participants
-deviate from Nash equilibrium play and learn to adapt to the opponent's strategy and exploit it. Moreover, we show that participants transfer their learning to new games and that
-this transfer is moderated by the level of sophistication of the opponent. Computational modelling shows that players start each game with a model-based
-learning strategy that facilitates between-game transfer of the opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
+deviate from Nash equilibrium play and learn to adapt to their opponent's strategy to exploit it. Moreover, we show that participants transfer their learning to new games and that
+this transfer is moderated by the level of sophistication of the opponent, as well as the similarity between games. Computational modelling shows that players start each game with a model-based
+learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
 }
@@
 In this paper, we are specifically interested in the latter: How do people build and use models of their opponent to facilitate learning transfer?
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly useful to address this question.
-The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.~Nash equilibrium play) or use salient actions (e.g.~risk dominance) in later games, having had experience with a similar game environment previously (Camerer \& Knez, 2000; Teck-Hua Ho, Camerer, \& Weigelt, 1998).
-As is well-known, a Nash equilibrium means that all players in a game play such that no-one can unilaterally improve their performance by deviating from their strategy.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about their opponent's strategies and preferences (Mertens, 1990) are particularly useful to address this question.
+The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.~Nash equilibrium play) or use salient actions (e.g.~risk dominance) in later games, having had experience with a similar game environment previously (C.
+Camerer \& Knez, 2000; Teck-Hua Ho, Camerer, \& Weigelt, 1998).
+As is well-known, a Nash equilibrium means that all players in a game act such that no-one can unilaterally improve their performance by deviating from their strategy.
 When playing against an opponent with a Nash-optimal strategy, I can do no better than play according to the Nash-equilibrium strategy as well.
-However, when faced with a player who deviates from the Nash-optimal strategy, it may be better for me to exploit this and also deviate from this strategy, increasing my performance beyond what is expected at a Nash equilibrium.
-Of course, this comes with some risk, as my own deviation from Nash-optimal play may leave myself open to similar exploitation.
+However, when faced with a player who deviates from the Nash-optimal strategy, I may be able to exploit this and also deviate from this strategy, increasing my performance beyond what is expected at Nash equilibrium.
+Of course, this comes with some risk, as my own deviation from Nash-optimal play may leave me open to similar exploitation.
 
 Studies that focused on whether people can learn to exploit deviations from Nash-equilibrium play have mostly looked at the ability of players to detect and exploit action-based learning rules (Shachat \& Swarthout, 2004; Spiliopoulos, 2013).
-These studies used computer opponents with fixed strategies (no adaptation to their human opponent) consisting of playing each action with a fixed probability (a mixed strategy).
-Findings showed \ldots.
+These studies used computer opponents that don't adapt play to their human opponent, mostly consisting of playing each action with a fixed probability (a mixed strategy).
+Findings showed that humans are capable of adapting to non-Nash-equilibrium play and detect patterns in an opponent's history of play.
 However, the use of mixed strategies may have limited people's ability to form accurate opponent models.
-Rather than thinking of their opponents and drawing a random action from a (non-uniform) probability distribution, people may rather think of their opponents as applying a form of iterated reasoning to determine their next action.
-The type of reasoning we refer to takes the form of ``I believe that you believe that I believe \ldots'\,' and has been shown to correspond to people's casual introspection (REFERENCE).
-It also underlies successful models in behavioural economics, such as Level-\(k\) and Cognitive Hierarchy models, which posit that people assume their opponent has a limited level of iterative reasoning, with the player best responding to their (modelled) opponent.
+Instead of thinking of their opponents as drawing random actions from a (non-uniform) probability distribution, people may rather think of their opponents as applying a form of iterated reasoning to determine their next action.
+The type of reasoning we refer to takes the form of ``I believe that you believe that I believe \ldots{}'' and has been shown to underlie people's decisions in economic games (C.
+F.
+Camerer, 2003; Costa-Gomes, Crawford, \& Broseta, 2001).
+It also underlies successful models in behavioural economics, such as Level-\(k\) and Cognitive Hierarchy models (C.
+F.
+Camerer, Ho, \& Chong, 2004), which posit that people assume their opponent applies a limited level of iterative reasoning, taking actions that are best responses to those of their (modelled) opponent.
 
@@
 A level-2 player, on the other hand, takes their opponent's belief about their actions into account, assuming they face a level-1 player, and choosing actions to best respond to the actions of that player.
-Cognitive Hierarchy theory works on similar principles, but rather than assuming an opponent always adopts a particular level-\(k\) strategy, they assume their opponent adopts each pf the level-\(k\) strategies with a particular probability (i.e., the strategy is a mixture over pure level-\(k\) strategies).
+Cognitive Hierarchy theory is based on similar principles, but rather than assuming an opponent always adopts a particular level-\(k\) strategy, they are assumed to adopt each of the level-\(k\) strategies with a particular probability (i.e., the opponent's strategy is a mixture over pure level-\(k\) strategies).
 
-Iterative reasoniing strategies can explain non-equilibrium play in a range of games, such as \ldots{} In the present study, we endow our computer opponents with limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
-In two experiments, participants face the same opponent (Experiment 1) or same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, a structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
-To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of the opponent and the similarity of the games.
-Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a morehabiltual and cognitively less demanding strategy in the later stages of the games.
+Iterative reasoning strategies can explain non-equilibrium play in a range of games, such as the \(p\)-beauty contest game (Nagel, 1995), dominance solvable games (C.
+F.
+Camerer, Ho, \& Chong, 2004), and various standard normal form games (Costa-Gomes, Crawford, \& Broseta, 2001).
+In the present study, we endow our computer opponents with limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
+In two experiments, participants face the same opponent (Experiment 1) or the same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, the structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
+To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of their opponent and the similarity of the games.
+Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a more habitual and cognitively less demanding strategy in the later stages of the games.
 
@@
 
-In the first experiment, we \ldots. {[}intro to first exp{]}
+In the first experiment, we aim to test learning transfer by making participants face the same computer opponent with a limited level of iterative reasoning in three sequential games that vary in similarity.
+If participants are able to learn the limitations of their opponent's iterative reasoning and generalize this to new games, their performance in (the early stages of) later games should be higher than expected if they were to completely learn a new strategy in each game.
 
@@
 The mean age of participants was 31.2 years.
-Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The experiment used a 2 (computer opponent: level 1 or level 2) by 3 (games: rock-paper-scissors, fire-water-grass, numbers) design, with repeated measures on the second factor.
+Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance (£1.06 on average).
+The experiment had a 2 (computer opponent: level 1 or level 2) by 3 (games: rock-paper-scissors, fire-water-grass, numbers) design, with repeated measures on the second factor.
 Participants were randomly assigned to one of the two levels of the first factor.
@@
 
-In the first experiment, participants played the three games against their computer opponent.
-These games were rock-paper-scissors, fire-water-grass, and the numbers game.
-A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between the two player's actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
+Participants played the three games against their computer opponent.
+These games were Rock-Paper-Scissors, Fire-Water-Grass, and the Numbers game.
+A typical Rock-Paper-Scissors game (hereafter RPS) is a 3x3 zero-sum game, with a cyclical hierarchy between the two player's actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
 If one player chooses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
@@
 RPS has a unique mixed-strategy Nash equilibrium, which consists of each player in each round randomly selecting from the three options with uniform probability.
+
 The Fire-Water-Grass (FWG) game is identical to RPS in all but action labels: Fire burns grass, water extinguishes fire, and grass absorbs water.
-We use this game as we are interested in whether learning is transferred in a fundamentally similar game where the only difference is in the name of the possible actions.
+We use this game as we are interested in whether learning is transferred in a fundamentally similar game where the only difference is in the label of the possible actions.
 This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level-1 or level-2 player.
-Crucially, learning simple contingencies such as ``If I played Rock on the previous round, playing Scissors next will likely result in a win'\,', is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
+Crucially, learning simple contingencies such as ``If I played rock on the previous round, playing scissors next will likely result in a win,'' is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
+
 The Numbers game is a generalization of RPS.
@@
 As a best response to a uniformly random action is itself a random action, defining a level-0 player in such a way would make a level-1 opponent's strategy much harder to discern.
-Because we are mainly interested in generalization of knowledge of an opponent's strategy to other games, which rests on good knowledge of this strategy, we opted for this more deterministic formulation of a level-0 player (whilst also introducing some randomness in the computer opponent's play).
-A level-2 computer opponent, will assume in turn that the participant is a level-1 opponent, playing according to the strategy just described.
-We also introduced some noise over the actions of computer opponents making them play randomly in 10\% of all trials.
+Because we are mainly interested in generalization of knowledge of an opponent's strategy to other games, which requires good knowledge of this strategy, we opted for this more deterministic formulation of a level-0 player.
+The level-2 computer opponent assumes in turn that the participant is a level-1 opponent, playing according to the strategy just described.
+To make the computer opponent's strategy not too obvious, we introduced some randomness in actions of computer opponent, making them play randomly in 10\% of all trials.
 Note that at all levels, the strategies are contingent on the actions taken in the previous round.
-The choice of this type of strategy is consistent with evidence that humans strategically use information from last round play of their opponents in zero sum games (Batzilis, Jaffe, Levitt, List, \& Picel, 2016; Wang, Xu, \& Zhou, 2014).
+The choice of this type of strategy is consistent with evidence that humans strategically use information from last round play of their opponents in zero-sum games (Batzilis, Jaffe, Levitt, List, \& Picel, 2016; Wang, Xu, \& Zhou, 2014).
+Table \ref{table:1} shows an example of the computer opponent's actions in response to the previous round play.
 
 \begin{table}[bth!]
+\caption{Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round.}
 \centering
+\label{table:1}
 \begin{tabular}{||c c | c c||} 
@@
 An example of the interface for the RPS game is provided in Figure~\ref{fig:feedback-rps-exp2}.
-On each round, tHe human player chooses an action, and after a random delay, is shown the action chosen by the computer opponent, and the outcome of that round.
-A history of the chosen actions over all rounds is available in the centre panel.
+On each round, the human player chooses an action, and after a random delay (between 0.5 and 3 seconds) is shown the action chosen by the computer opponent and the outcome of that round.
 A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
@@
 Ties did not affect the score.
-In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-Each point is worth £0.02.
-After playing all the games, participants were asked questions about their beliefs about the computer opponent, related to whether they thought they learned their opponent's strategy, and how difficult they found playing against their particular opponent.
+In order to incentivise the participants to maximise the number of wins against their opponent, players were paid a bonus at the end of the experiment proportional to their final score (each point was worth £0.02).
+After playing all the games, participants were asked questions about their beliefs about the computer opponent, related to whether they thought they learned their opponent's strategy, and how difficult they found playing against their opponent.
 They were then debriefed and thanked for their participation.
@@
 Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
-\textbf{MS: Need to check test results and report GG degrees of freedom, etc.}
 
@@
 We did not expect positive scores for the RPS game, as it was the first game played and there was no opportunity for learning about the opponent's strategy.
-Scores in this game was indeed not significantly different from 0 (\(t(148.85) = 1.04\) , \(p = .89\)).
+Scores in this game were indeed not significantly different from 0 (\(t(148.85) = 1.04\) , \(p = .89\)).
 
@@
 Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-We expected better transfer between more similar games (i.e.~better transfer from RPS to FWG than from RPS/FWG to Numbers), and worse transfer for the more sophisticated level 2 agent.
+We expected better transfer between more similar games (i.e.~better transfer from RPS to FWG than from RPS/FWG to Numbers), and worse transfer for the more sophisticated level-2 agent.
 Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents.
-To explore this, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game (\(F(1.84,91.77) = 3.35\), \(\eta^{2} = 0.04\), \(p = .043\), Greenhouse-Geisser correction to degrees of freedom applied to correct for non-sphericity).
-We then run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
+To explore this, we used a 2 (Condition: Level 1, Level 2) by 3 (Game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants.
+There was a main effect of Game (\(F(1.84,91.77) = 3.35\), \(\eta^{2} = 0.04\), \(p = .043\), Greenhouse-Geisser correction applied to the degrees of freedom to correct for non-sphericity).
+\textbf{MS: was this the only significant effect?
+If so, people might wonder why we next run analyses for each combination of player and game} We then ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG (\(t(150) = 3.96\), \(p < .001\)) and Numbers (\(t(150) = 3.74\), \(p < .001\)).
@@
 In Experiment 2, we aimed to obtain a stronger test of learning transfer.
-Instead of facing a single level-1 or level-2 opponent throughout all games, participants face both types of opponents sequentially in this experiment.
-To perform well against both opponents, participants would need to learn distinct strategies in each game.
+Instead of facing a single level-1 or level-2 opponent throughout all games, participants now faced both types of opponent.
+To perform well against both opponents, participants would need to learn distinct strategies against these opponents.
 To reduce effects of increased memory load due to facing distinct opponents, we provided participants access to the history of play against an opponent within each game (see Figure \ref{fig:feedback-rps-exp2}).
-Finally, we changed the third game to a penalty shootout game, with participants aiming to score a goal and opponents playing the role of goal keepers.
+Finally, we changed the third game to a penalty Shootout game, with participants aiming to score a goal and opponents playing the role of goal keepers.
 Whilst this game has the same number of actions as the first two (aim left, center, or right), it is strategically dissimilar.
@@
 There is no possibility of ties in this game.
-Figure~\ref{fig:screenshot-shootout} shows a snapshot of play in the shootout game.
-What makes this game different to the other games is that there are two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend `'right'' in the next round, they can win by either choosing to shoot `'left'' or `'center''.
-A level-1 shooter who thinks that their goalkeeper opponent will repeat their last action has thus two possible best responses.
+Figure~\ref{fig:screenshot-shootout} shows a snapshot of play in the Shootout game.
+What makes this game different to the other games is that there are now two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend ``right'' in the next round, they can win by either choosing to shoot ``left'' or ``center.'' A level-1 shooter who thinks that their goalkeeper opponent will repeat their last action has thus two possible best responses.
 A level-1 goalkeeper, however, has only a single best response (defending where their opponent aimed in the last round).
@@
 We programmed the level-2 computer player to choose randomly between these two best responses.
+
+As in Experiment 1, all the games have a unique mixed-strategy Nash equilibrium consisting of uniformly random actions.
+If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
+Evidence of sustained wins would indicate that participants have learned to exploit patterns in their opponents' play.
 
@@
 
-Participants scores are depicted in Figure \ref{fig:exp2-score-by-opp}.
-The RPS game had the lowest average score per round (\(M = 0.194\), SD = 0.345) followed by FWG (\(M = 0.27\), SD = 0.394) and finally the Shootout game (\(M = 0.289\), SD = 0.326).\footnote{ A higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
+Participants' scores are depicted in Figure \ref{fig:exp2-score-by-opp}.
+The RPS game had the lowest average score per round (\(M = 0.194\), SD = 0.345) followed by FWG (\(M = 0.27\), SD = 0.394) and finally the Shootout game (\(M = 0.289\), SD = 0.326).\footnote{A higher score in the Shootout game is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
 Indeed, a player not aiming to uncover the opponent's strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33)} Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: \(t(49) = 6.26\), \(p < .001\); FWG: \(t(49) = 7.25\), \(p < .001\); Shootout: \(t(49) = 13.61\), \(p < .001\)).
+To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will adjust all scores in the Shootout game by subtracting the average score per round of a random strategy (0.33).} Using one-sample t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: \(t(49) = 6.26\), \(p < .001\); FWG: \(t(49) = 7.25\), \(p < .001\); Shootout: \(t(49) = 13.61\), \(p < .001\)).
 
-To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA on the average score per round, with the first factor varying between participants.
-This shows a main effect of Game (\(F(1.85,88.7) = 11.81\), \(\eta^{2} = 0.04\), \(p < .001\)).
-Post-hoc pairwise comparisons between games (p-values adjusted using Holm method for multiple comparisons) indicate performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (\(t(96) =2.53\), \(p = .025\)), and performance in the Shootout game significantly higher than in FWG (\(t(96) = 2.32\), \(p = .025\)).
+\begin{figure}
+
+{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-score-by-opp-1}
+
+}
+
+\caption{\label{fig:exp2-score-by-opp}Performance per game and interaction across opponents in Experiment 2.
+Points are scores of individual participants and boxes reflect the 95\% confidence intervals of the mean (center line equals the mean).}\label{fig:exp2-score-by-opp}
+\end{figure}
+
+To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA, with the first factor varying between participants.
+This showed a main effect of Game (\(F(1.85,88.7) = 11.81\), \(\eta^{2} = 0.04\), \(p < .001\)).
+Post-hoc pairwise comparisons between games (\(p\)-values adjusted using Holm method for multiple comparisons) indicate performance in the games increased steadily throughout the experiment, with FWG performance significantly higher than RPS (\(t(96) =2.53\), \(p = .025\)), and performance in the Shootout game significantly higher than in FWG (\(t(96) = 2.32\), \(p = .025\)).
 Whilst the ANOVA shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type (\(F(1.7, 81.82) = 5.31\) ,\(\eta^{2} = 0.02\), \(p = .01\)).
-Follow-up analysis shows that when facing level-1 agents, scores increase steadily after each game, with FWG score significantly higher than RPS (\(t(191) = 2.70\), \(p = .03\)) and Shootout scores in turn significantly higher than FWG (\(t(191) = 3.05\), \(p = .01\)).
+Follow-up analysis shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS (\(t(191) = 2.70\), \(p = .03\)) and Shootout scores in turn significantly higher than FWG (\(t(191) = 3.05\), \(p = .01\)).
 There was no significant difference between average scores on any two games when facing level-2 agents however.
@@
 
-As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random (Figure~\ref{fig:exp2-early-scores}).
-For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types (Level-1 opponent: FWG: \(t(270) = 4.99\), \(p < .001\); Shootout: \(t(270) = 6.66\), \(p < .001\); Level-2 opponent: FWG: \(t(270) = 4.40\), \(p < .001\); Shootout: \(t(270) = 3.21\), \(p=.004\)).
-\textbf{MS: Should also report ANOVA, as for Experiment 1}
+To measure transfer between games, we again focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
+We performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) repeated-measures ANOVA, with the first factor varying between participants.
+This showed a main effect of Game (\(F(1.94,92.98) = 7.67\), \(\eta^{2} = 0.04\), \(p < .001\)).
+\textbf{MS: Again, if there is no interaction, there might not be justification for running tests per opponent and game }
+We then ran statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG (\(t(271) = 4.99\), \(p < .001\)) and Shootout (\(t(271) = 6.66\), \(p < .001\)).
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player (\(t(271) = 4.41\), \(p < .001\)).
+Unlike in Experiment 1, there is also evidence of transfer to the dissimilar Shootout game (\(t(271) = 3.22\), \(p = .004\)).
+The early round scores in the similar FWG games for level-1 and level-2 facing players are not significantly different from each other.
+However, the score of the players facing the level-1 opponent in Shootout is higher than that of players facing level-2 opponents ( \(t(144) = 2.45\), \(p = 0.01\)).
 
@@
 
-The results of Experiment 2\ldots{} \textbf{MS: give summary of main findings, as done for Experiment 1.
-You should not report new statistical tests in the discussion, which should go in the results section before.}
-
-Looking at learning transfer by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
-Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
-These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
+The results of Experiment 2 confirm the earlier results of Experiment 1 in a situation where participants need to learn about two distinct opponents.
+As in Experiment 1, participants adapted their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
+Knowledge about both types of opponents were transferred to both the similar and dissimilar game.
+However, transfer to the dissimilar game was easier when facing the less sophisticated agent.
 
@@
 The other models adapted their play to the opponent, either by reinforcing successful actions in each game (reinforcement learning), or by determining the type of opponent through Bayesian learning (Bayesian Cognitive Hierarchy models).
-We also include the Expected Weighted Attraction (EWA) model, which is a popular model in behavioural economics.
+We also include the (self-tuning) Expected Weighted Attraction (EWA) model, which is a popular model in behavioural economics.
 
-In the following, we will describe the models in more detail, and provide some intuition into how they they learn about the game and/or the opponent.
-We use the following notation: In each game \(g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}\), on each trial \(t\), the participant chooses an action \(a_t \in \mathcal{A}_g\), and the opponent chooses action \(o_t \in \mathcal{A}_g\), where \(\mathcal{A}_g\) is the set of allowed actions in game \(g\), e.g.~\(\mathcal{A}_\text{RPS} = \{R,P,S\}\).
+In the following, we will describe the models in more detail, and provide some intuition into how they implement learning about the game and/or the opponent.
+Throughout, we use the following notation: In each game \(g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}\), on each trial \(t\), the participant chooses an action \(a_t \in \mathcal{A}_g\), and the opponent chooses action \(o_t \in \mathcal{A}_g\), where \(\mathcal{A}_g\) is the set of allowed actions in game \(g\), e.g.~\(\mathcal{A}_\text{RPS} = \{R,P,S\}\).
 The participant then receives reward \(r_t \in \{1,0,-1\}\), and the opponent receives \(-r_t\).
 We use the state variable \(s_t = \{a_{t-1},o_{t-1}\}\) to denote the actions taken in the previous round \(t-1\) by the participant and opponent.
+The initial state is empty, and we assume that the action at a first encounter of an opponent in a game is chosen at random.
 
@@
 The resulting RL model learns a \(Q\)-value (Watkins \& Dayan, 1992) for each state-action pair:
-\[ Q_{t+1}(s_{t},a_{t}) = Q_{t}(s_{t},a_{t}) + \alpha \left( r_{t}  - Q(s_{t},a_{t}) \right) ,\]\\
+\[Q_{t+1}(s_{t},a_{t}) = Q_{t}(s_{t},a_{t}) + \alpha \left( r_{t}  - Q(s_{t},a_{t}) \right) ,\]
 where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), and \(\alpha \in [0,1]\) the learning rate.
-For instance, \(Q_t(\{R,S\},P)\) denotes the value of taking action `'Paper'' this round if the player's last action was `'Rock'' and the opponent played `'Scissors''.
-Actions are taken according to a softmax rule:
+For instance, \(Q_t(\{R,S\},P)\) denotes the value of taking action ``Paper'' this round if the player's last action was ``Rock'' and the opponent played ``Scissors.'' Actions are taken according to a softmax rule:
 \[P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}, \]
-where the inverse temperature parameter \(\lambda\) determines the consistency of the strategu (the higher \(\lambda\), the more often the action with the highest \(Q\)-value is chosen.
-While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different state \(\mathcal{S}_g\) and action space \(\mathcal{A}_g\), and there is no simple way to map states and actions between games.
+where the inverse temperature parameter \(\lambda\) determines the consistency of the strategy (the higher \(\lambda\), the more often the action with the highest \(Q\)-value is chosen.
+While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different state space \(\mathcal{S}_g\) and action space \(\mathcal{A}_g\), and there is no simple way to map states and actions across games.
 
@@
 Ho, Camerer, \& Chong, 2004) combines two seemingly different approaches, namely reinforcement learning and belief learning.
-Belief learning models are based on the assumption that players keep track of the frequency of past actions and best respond to that.
+Belief learning models are based on the assumption that players keep track of their opponent's frequency of past actions, and best respond to that.
 By contrast, reinforcement learning does not explicitly take into account beliefs about other players, but simply increases the probability of repeating a more rewarding action.
 The self-tuning EWA model has been shown to perform better than either RL or belief learning alone in various repeated games and has the advantage of having only one free parameter, the inverse temperature of the softmax choice function.
-The EWA model is based on updating ``Attractions'\,' for each action over time.
-The attraction of action \(a\) time \(t\) is written \(A_{t}(a)\) and is updated as
-\[ A_{t+1}(a) =  \frac{\phi \ N(t) \ A_{t}(a) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} \]
-where \(I(x)\) is an indicator function which takes the value 1 is its argument is true, and 0 otherwise, and \(R(a,o_t)\) is the reward that would be obtained from playing action \(a\) against opponent action \(o_t\), which equals the actual obtained reward when \(a = a_t\), and otherwise is a counterfactual reward that would have been obtained if a different action were taken.
-Unlike reinforcement learning, this uses knowledge of the rules of the game to allow reinforcing actions that were not taken.
-We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone pay-offs, which is similar to weighted fictitious play (Cheung \& Friedman, 1994).
-While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Teck H.
-Ho, Camerer, \& Chong, 2004).
+The EWA model is based on updating ``Attractions'\,' for each action over time given a particular state.
+The attraction of action \(a\) at time \(t\) given state \(s\) is denoted as \(A_{t}(a, s)\) and updated as
+\[ A_{t+1}(a,s) =  \frac{\phi \ N(t) \ A_{t}(a,s) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} \]
+where \(I(x)\) is an indicator function which takes the value 1 is its argument is true and 0 otherwise, and \(R(a,o_t)\) is the reward that would be obtained from playing action \(a\) against opponent action \(o_t\).
+\(R(a,o_t)\) equals the actual obtained reward when \(a = a_t\), and otherwise is a counterfactual reward that would have been obtained if a different action were taken.
+Unlike reinforcement learning, this uses knowledge of the rules of the game to allow reinforcing actions that were not actually taken by the rewards they would have provided.
+The parameter \(\delta\) reflects the weight given to such counterfactual rewards.
+Setting \(\delta = 0\) leads to reinforcement only of actions taken, while positive values of \(\delta\) makes the update rule take into account foregone payoffs, which is similar to weighted fictitious play (Cheung \& Friedman, 1994).
 \(N(t)\) represents an experience weight and can be interpreted as the number of ``observation-equivalents'' of past experience.
 We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
-\textbf{MS: Should describe how the parameters are self-tuned with equations }
+\textbf{MS: need to better describe what \(\phi\) is, and how \(N(t)\) is determined.} In the earlier version of the EWA model (C.
+Camerer, Ho, \& Others, 1997), \(\phi\) and \(\delta\) were free parameters.
+In the self-tuning EWA model (Teck H.
+Ho, Camerer, \& Chong, 2004), the values of \(\delta\) and \(\phi\) are learnt from experience.
+For details on how this is done, we refer the reader to (Teck H.
+Ho, Camerer, \& Chong, 2004).
+\textbf{MS: Should describe how the parameters are self-tuned with equations.
+IG: There are many equations for each of the parameters update, phi, delta and N\ldots I'm concerned it would make for cumbersome reading, especially since EWA doesn't really fit well anyway.
+I've added that details of updates can be found in original camerer paper.
+MS: If it's three additional equations, that's not a big deal really.
+}
 
 As in the models above, actions are chosen based on a softmax decision rule:
-\[P_t(a) = \frac{\exp \{\lambda  A_{t}(a) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a') \} }\]
+\[P_t(a,s) = \frac{\exp \{\lambda  A_{t}(a,s) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a',s) \} }\]
 The self-tuning EWA has one free parameter: the inverse temperature of the softmax decision rule (\(\lambda\)).
-\textbf{MS: Are there no states in the EWA?
-If not, it is unsurprising that this model doesn't fit well }
 
@@
 In what we call the Bayesian Cognitive Hierarchy (BCH) model, the participant attempts to learn the type of opponent they are facing through Bayesian learning.
-We assume the participant considers the opponent could be either a level 0, level 1, or level 2 player, and starts with a prior belief that each of these types is equally likely.
-They then use observations of the opponents actions to infer a posterior probability of each type:
+For present purposes, we assume participants consider the opponent could be either a level 0, level 1, or level 2 player, and start with a prior belief that each of these types is equally likely.
+They then use observations of the opponent's actions to infer a posterior probability of each type:
 \[P(\text{level}=k | \mathcal{D}_{t})  \propto  P(\mathcal{D}_{t}|\text{level}=k ) \times P(\text{level}=k)\]
@@
 We assume a participant chooses an action by using the softmax function over the best response to predicted actions:
-\[\begin{aligned} B_t(a) &= \sum_{k = 0}^2 \sum_{o \in \mathcal{A}_g} b(a,o) P_k(o|s_{t})  P(\text{level}=k|\mathcal{D}_{t-1})\\
+\[\begin{aligned} B_t(a) &= \sum_{k = 0}^2 \sum_{o \in \mathcal{A}_g} b(a,o) f_k(o|s_{t})  P(\text{level}=k|\mathcal{D}_{t-1})\\
 P_t(a) &= \frac{\exp\{\lambda B_t(a) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{ \lambda B_t(a')\}} \end{aligned}\]
-where \(b(a,o) = 1\) if action \(a\) is a best response to opponent's action \(o\) (i.e.~it leads to a win), and \(P_k(o|a_{t-1},o_{t-1}) = \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o|a_{t-1},o_{t-1})\) is the probability that a level \(k\) agent takes action \(o\), as also used in the likelihood above.
+where \(b(a,o) = 1\) if action \(a\) is a best response to opponent's action \(o\) (i.e.~it leads to a win).
 
 Unlike the models above, the BCH model allows for between-game transfer, as knowledge of the level of the opponent can be used to generate predictions in games that have not been played before.
-This generalization is done simply by using the posterior \(P(\text{level} = k|\mathcal{D}_T)\) from the previous game as rhe prior distribution in the next game.
+This generalization is done simply by using the posterior \(P(\text{level} = k|\mathcal{D}_T)\) from the previous game as the prior distribution in the next game.
 However, the participant might also assume that the level of reasoning of their opponent does not generalize over games.
@@
 For both experiments, we fitted all models to individual participant data by maximum likelihood estimation.
-We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
+\textbf{MS: need to mention the use of e.g.~DEoptim} We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
 
-For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NBT), as well as a Reinforcement Learning model with state space consisting of last round play (RL), and finally a self-tuning EWA model with the same state space (EWA).
+For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NBT), as well as a reinforcement learning (RL), and finally a self-tuning EWA model with the same state space (EWA).
 
-In Experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two type of opponent model transfer.
-We can have transfer within games, between the first and second interaction with the opponent.
-We can also have transfer between games, as in e.g.~transferring a learned opponent model from RPS to FWG.
-Therefore, we fitted a total of three versions of the Bayesian Cognitive Hierarchy model: BCH\_BT allows for both within and between game transfer (between game transfer without within game transfer is implausible); BCH\_NBT allows for within but not between game transfer; BCH\_NT allows for no transfer within or between games.
-For Reinforcement learning models, because RL models can't account for between game transfer due to change in state and action space, we can only have models that allowing for within game transfer (RL\_TR) or with no transfer within games (RL\_NT).
-Likewise, we fit both a self tuning EWA model with transfer between stages of the same game (EWA\_TR) or without transfer (EWA\_NT).
-Counting the base model with random play (Nash) we therefore fit a total of 8 models for Experiment 2.
+In Experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two types of opponent model transfer.
+We can have transfer \emph{within} games between the first and second interaction with the opponent.
+In addition, we can also have transfer \emph{between} games, as in e.g.~transferring a learned opponent model from RPS to FWG.
+Therefore, we fitted a total of three versions of the Bayesian Cognitive Hierarchy model: BCH\_BT allows for both within and between game transfer (between game transfer without within game transfer is implausible); BCH\_WT allows only for within-game transfer, but not between game transfer; BCH\_NT allows for no transfer within or between games.
+As the RL model can't account for between game transfer due to a change in state and action space, we can only have models that allowing for within game transfer (RL\_WT) or with no transfer within games (RL\_NT).
+Likewise, we fit both a self tuning EWA model with (EWA\_WT) and without (EWA\_NT) within-game transfer.
+Including the baseline model of random play (Nash), we therefore fitted a total of 8 models for Experiment 2.
+
+\textbf{MS: Please present the models in the figures in the order mentioned in text (i.e., Nash, RL, EWA, BCH), and when providing versions of each, do so in the same order as well, i.e.~x\_NT, x\_WT, x\_BT}
 
@@
 We can see that the RL model clearly described most participants' behaviour best, followed by the random (Nash) model.
-Only a few participants were best described by one of the BCH models, or the EWA model.
-Looking at BIC weights, we confirm this as seen in Figure ~\ref{fig:xp1-BIC-weigths}.
+Only a few participants were best described by one of the BCH models or the EWA model.
+Looking at BIC weights (Figure ~\ref{fig:xp1-BIC-weigths}), we confirm this.
 RL models have high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, which fits the picture drawn by the histogram.
+\textbf{MS: The BIC weight don't add much information, so maybe we could leave them out }
 
@@
 
-In Experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that the RL model was again more successful than the Bayesian Cognitive Hierarchy models (with or without transfer) in fitting participants' action choices.
+In Experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that the RL model was again more successful than the Bayesian Cognitive Hierarchy models (with or without transfer) and the EWA model in fitting participants' action choices.
 This is also reflected in BIC weights in Figure \ref{fig:xp2-BIC-weigths}.
-\textbf{MS: model labels in Figures should correspond to those in the text}
 
@@
 If indeed most participants adopt a reinforcement learning strategy, they should not be able to transfer their learning to the early rounds of a new game.
-In order to investigate this discrepancy further, we plot the likelihood by trial for each game and three strategies: RL, Bayesian Cognitive Hierarchy models with between-game transfer, and the random (Nash) strategy.
-Figure~\ref{fig:exp1-lik-by-tr} shows that in the later games of Experiment 1, the likelihood for the BCH models is higher than that of the other models in the initial rounds of the games.
+In order to investigate this discrepancy further, we plot the likelihood by trial for each game and three strategies: reinforcement learning (RL), Bayesian Cognitive Hierarchy with between-game transfer (BCH\_BT), and the random (Nash) strategy.
+Figure~\ref{fig:exp1-lik-by-tr} shows that in the initial rounds of the the later games in Experiment 1, the likelihood for the BCH models is higher than that of the other models.
 However, over time, the likelihood of the RL model increases and exceeds that of BCH model.
@@
 
-\caption{Experiment 1 Likelihood by trial by game and opponent faced}\label{fig:exp1-lik-by-tr}
+\caption{Experiment 1 Likelihood by trial, game and opponent faced}\label{fig:exp1-lik-by-tr}
 \end{figure}
@@
 The same pattern holds for Experiment 2 (Figure~\ref{fig:exp2-lik-by-tr}).
-Again, the BCH model with between-game transfer has the highest likelihood in the early stages of the later games (apart from stage 1 of the shootout game, where the RL model is better).
+Again, the BCH\_BT model with between-game transfer has the highest likelihood in the early stages of the later games (apart from stage 1 of the shootout game, where the RL model is better).
 In later rounds, the likelihood of the RL model exceeds that of the BCH model.
@@
 
-\caption{Experiment2 likelihood by trial by game and opponent faced}\label{fig:exp2-lik-by-tr}
+\caption{Experiment2 likelihood by trial, game and opponent faced}\label{fig:exp2-lik-by-tr}
 \end{figure}
@@
 
-\begin{verbatim}
-## converged at iteration 7 with logLik: -7415.978
-\end{verbatim}
-
-\begin{verbatim}
-## log Likelihood ratio (chi^2): 211.087 (df=0), p=0.
-\end{verbatim}
-
-\begin{verbatim}
-## [1] 0
-\end{verbatim}
-
 \begin{figure}
@@
 
-In Experiment 1, a likelihood-ratio test shows that the HMM model with switching fits significantly better than the non-switching one (\(p < .001\)).
-\textbf{MS: we should really use a bootstrapped Likelihood Ratio test here } This provides further statistical evidence in favour of the hypothesis that participants switch between strategies.
+In Experiment 1, a likelihood-ratio test shows that the HMM model with switching fits significantly better than the non-switching one, \(\chi^2(6) = 211.09\), \(p < .001\).
+We should note that as the no switch model involves restricting parameters of the switching model on the bounds of the parameter space, the asymptotic \(p\)-value of this test may not be reliable.
+The switching model (AIC = 14,636.87, BIC = 14,692.56) fits also better than the non-switching model (AIC = 14,835.96, BIC = 14,849.88) according to the AIC and BIC.
+This provides further statistical evidence in favour of the hypothesis that participants switch between strategies.
 Figure~\ref{fig:exp1-posteriors-plot} depicts the average (across participants) posterior probabilities of each state (strategy), as a function of trial and opponent faced.
@@
 
-The switching model in Experiment 2 is also significantly better than the restricted non-switching model (\(p < .001\)).
+The switching model (AIC = 16,879.97, BIC = 16,936.81) in Experiment 2 again fits better than the restricted non-switching model (AIC = 16,938.41, BIC = 16,952.62), \(\chi^2(6) = 70.44\), \(p < .001\).
 The posterior probabilities of the strategies (Figure~\ref{fig:exp2-posteriors-plot}) show very clear evidence of strategy switching across games and stages, from using a BCH model in the initial rounds to an RL strategy later on.
@@
 Firstly, the learned strategies are not transferable to new games.
-There is no simple way to map ``play scissors whenever my opponent played rock in last round'' in the RPS game to ``play grass whenever my opponent played fire in last round.'' Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this.
-Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
+There is no simple way to map ``play scissors whenever my opponent played rock in last round'' in the RPS game to ``play grass whenever my opponent played fire in last round.'' Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this quickly enough: Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
 Secondly, a reinforcement learning strategy would fare equally well against the level-1 and level-2 opponent.
@@
 This is the type of learning encapsulated by our Bayesian Cognitive Hierarchy model.
-It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
-Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
-\textbf{MS: need to check relevance of these citations.
-Also, they need to be in reference list } We admit that our implementation in the BCH models does not predict a performance difference between the types of opponents.
+It involves the evaluation of explicit hypotheses and results in better problem-solving skills (\textbf{mandler2004foundations?}).
+Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (Stahl, 2000, 2003).
+We admit that our implementation in the BCH models does not predict a performance difference between the types of opponents.
 Starting with an equal prior belief over the different levels of sophistication, a BCH player would perform equally well against the level-1 and level-2 opponent.
@@
 Either of these mechanisms would explain why learning the strategy of the level-2 opponent is more difficult and slower than learning the strategy of the level-1 opponent.
-\textbf{MS: This could be something to implement, actually} Using hidden Markov models, we found evidence of strategy switching between the BCH and RL strategies, and such switching seems more consistent with the latter idea.
-If predicting an opponent's actions through iterative reasoning is cognitively demanding and error-prone, it is resource-rational to switch to less costly yet equally successful strategies when these are available.
-\textbf{MS: add reference to resource-rational approach by Lieder \& Griffiths } Initially, a model-free reinforcement learning strategy will be less successful than an iterative reasoning one.
+Using hidden Markov models, we found evidence of strategy switching between the BCH and RL strategies, and such switching seems more consistent with the latter idea.
+If predicting an opponent's actions through iterative reasoning is cognitively demanding and error-prone, it is resource-rational to switch to less costly yet equally successful strategies when these are available (Lieder \& Griffiths, 2020).
+Initially, a model-free reinforcement learning strategy will be less successful than an iterative reasoning one.
 However, given enough experience, it will be on par with an iterative reasoning strategy.
 As it involves simple state-action contingencies, a model-free RL strategy may also be computationally less costly, making it overall more effective to rely on this than iterative reasoning.
-This is similar to the arbitration between model-free and model-based RL (Simon \& Daw, 2011) \textbf{MS: add more references here}.
+This is similar to the arbitration between model-free and model-based RL (Daw, Niv, \& Dayan, 2005; Simon \& Daw, 2011; Wouter Kool, Joseph T.
+McGuire, Zev B.
+Rosen, Matthew M.
+Bovinick, 2011).
 In repeated and well-practised situations, relying on habits allows one to save cognitive resources for other demands.
@@
 
+\leavevmode\hypertarget{ref-camerer2003behavioural}{}%
+Camerer, C. F. (2003). Behavioural studies of strategic thinking in games. \emph{Trends in Cognitive Sciences}, \emph{7}(5), 225--231.
+
+\leavevmode\hypertarget{ref-camerer2004cognitive}{}%
+Camerer, C. F., Ho, T.-H., \& Chong, J.-K. (2004). A cognitive hierarchy model of games. \emph{The Quarterly Journal of Economics}, \emph{119}(3), 861--898.
+
 \leavevmode\hypertarget{ref-camerer1997experience}{}%
@@
 Cheung, Y.-W., \& Friedman, D. (1994). \emph{{Learning in evolutionary games: some laboratory results}}. University of California, Santa Cruz.
+
+\leavevmode\hypertarget{ref-costa2001cognition}{}%
+Costa-Gomes, M., Crawford, V. P., \& Broseta, B. (2001). Cognition and behavior in normal-form games: An experimental study. \emph{Econometrica}, \emph{69}(5), 1193--1235.
+
+\leavevmode\hypertarget{ref-daw2005uncertainty}{}%
+Daw, N.
+D., Niv, Y., \& Dayan, P.
+(2005).
+Uncertainty-based competition between prefrontal and dorsolateral striatal systems for behavioral control.
+\emph{Nature Neuroscience}, \emph{8}(12), 1704--1711.
 
@@
 
+\leavevmode\hypertarget{ref-lieder2020resource}{}%
+Lieder, F., \& Griffiths, T.
+L.
+(2020).
+Resource-rational analysis: Understanding human cognition as the optimal use of limited computational resources.
+\emph{Behavioral and Brain Sciences}, \emph{43}.
+
 \leavevmode\hypertarget{ref-mertens1990repeated}{}%
 Mertens, J.-F. (1990). {Repeated games}. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+
+\leavevmode\hypertarget{ref-nagel1995unraveling}{}%
+Nagel, R. (1995). Unraveling in guessing games: An experimental study. \emph{The American Economic Review}, \emph{85}(5), 1313--1326.
 
@@
 Spiliopoulos, L. (2013). {Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game}. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
+
+\leavevmode\hypertarget{ref-stahl2000rule}{}%
+Stahl, D. O. (2000). Rule learning in symmetric normal-form games: Theory and evidence. \emph{Games and Economic Behavior}, \emph{32}(1), 105--138.
+
+\leavevmode\hypertarget{ref-stahl2003sophisticated}{}%
+Stahl, D. O. (2003). Sophisticated learning and learning sophistication. \emph{Available at SSRN 410921}.
 
@@
 
+\leavevmode\hypertarget{ref-Kool_2011}{}%
+Wouter Kool, Joseph T.
+McGuire, Zev B.
+Rosen, Matthew M.
+Bovinick.
+(2011).
+{Decision Making and the Avoidance of Cognitive Demand}.
+\emph{Experimental Psychology}.
+\url{https://doi.org/10.2996/kmj/1138846322}
+
 \end{CSLReferences}

### 2021-09-01 Experiment_2/exp2_clean_analysis.Rmd
exp1 updated results and MS inputs

@@
 
+# Set contrasts
+contrasts(dat2_6$game.f) <- cbind(c(1,-1,0),c(0,-1,1))
+contrasts(dat2_6$opp_type) <- c(1,-1)
+contrasts(dat2_6$condition.f) <- c(1,-1)
+
 aov_early <- aov_car(early_score ~ game.f*opp_type*condition.f + Error(human_id/(game.f*opp_type)),data=dat2_6)
 summary(aov_early)
+
+# Random intercecprt for participants
+lme_early <- mixed(early_score ~ game.f*opp_type*condition.f + (1 | human_id),data=dat2_6,check_contrasts = FALSE, type = 3, method = "KR")
+summary(lme_early)
+
+lme_early
 

### 2021-09-01 Report/paper_draft_2021.Rmd
exp1 updated results and MS inputs

@@
 In two experiments, participants face the same opponent (Experiment 1) or the same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, the structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
-To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of their opponent and the similarity of the games.
+To foreshadow our results, **we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of their opponent and the similarity of the games** **IG: I guess we can still say that given findings of exp 2...** .
 Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a more habitual and cognitively less demanding strategy in the later stages of the games.
@@
 An example of the interface for the RPS game is provided in Figure\ \@ref(fig:feedback-rps-exp2).
-On each round, the human player chooses an action, and after a random delay (between 0.5 and 3 seconds) is shown the action chosen by the computer opponent and the outcome of that round.
-<!-- A history of the chosen actions over all rounds is available in the centre panel.
-**MS: was this not only the case for Experiment 2?
-** --> A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
+On each round, the human player chooses an action, and after a random delay (between 0.5 and 3 seconds) is shown the action chosen by the computer opponent and the outcome of that round.A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
 The score was calculated as the number of wins minus the number of losses.
@@
 There was a main effect of Game ($F(1.84,91.77) = 3.35$, $\eta^{2}  = 0.04$,  $p = .043$, Greenhouse-Geisser correction applied to the degrees of freedom to correct for non-sphericity).
-**MS: was this the only significant effect?
-If so, people might wonder why we next run analyses for each combination of player and game** We then ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
+
+To test for transfer by type of opponent faced, we ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(150) = 3.96$, $p < .001$) and Numbers ($t(150) = 3.74$, $p < .001$).
@@
 The results of Experiment 1 indicate that participants were able to learn successful strategies which exploited the deviation from Nash-optimal play of their opponents.
-Moreover, they were able to transfer knowledge about their opponent to other games, but this was moderated by the type of game and opponent.
+Moreover, they were able to transfer knowledge about their opponent to other games, but this was moderated by the type of game.
 There was evidence of transfer from the RPS game to the similar FWG game for both opponents.
@@
 
-To measure transfer between games, we again focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
-We performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) repeated-measures ANOVA, with the first factor varying between participants.
+**To measure transfer between games, we again focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
+We estimate a linear mixed effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables.
+Random model intercepts are assumed for participants.
+We found a main effect of Game($F(2,240) = 6.57$, $p = .002$) and an interaction effect between Game and Opponent type ( $F(2,240) = 3.34$,  $p = .037$).**
+
+<!-- We performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) repeated-measures ANOVA, with the first factor varying between participants.
 This showed a main effect of Game ($F(1.94,92.98) = 7.67$, $\eta^{2} = 0.04$,  $p < .001$).
-**MS: Again, if there is no interaction, there might not be justification for running tests per opponent and game **
+**MS: Again, if there is no interaction, there might not be justification for running tests per opponent and game ** -->
+
 We then ran statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
@@
 
-The results of Experiment 2 confirm the earlier results of Experiment 1 in a situation where participants need to learn about two distinct opponents.
+**The results of Experiment 2 confirm earlier results from Experiment 1 on learning transfer in a situation where participants need to learn about two distinct opponents.
 As in Experiment 1, participants adapted their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
 Knowledge about both types of opponents were transferred to both the similar and dissimilar game.
-However, transfer to the dissimilar game was easier when facing the less sophisticated agent.
+This transfer was moderated by the degree of similarity between games.
+The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.
+**
 
@@
 The attraction of action $a$ at time $t$ given state $s$ is denoted as $A_{t}(a, s)$ and updated as
-$$ A_{t+1}(a,s) =  \frac{\phi \ N(t) \ A_{t}(a,s) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} $$
+$$ A_{t+1}(a,s) =  \frac{\phi(t) \ N(t) \ A_{t}(a,s) + [ \delta_{a}(t) + (1-\delta_{a}(t)) \ I(a_t = a )] \ R(a,o_t) } {\phi(t)N(t) + 1} $$
 where $I(x)$ is an indicator function which takes the value 1 is its argument is true and 0 otherwise, and $R(a,o_t)$ is the reward that would be obtained from playing action $a$ against opponent action $o_t$.
@@
 We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
-**MS: need to better describe what $\phi$ is, and how $N(t)$ is determined.** In the earlier version of the EWA model [@camerer1997experience], $\phi$ and $\delta$ were free parameters.
+**MS: need to better describe what $\phi$ is, and how $N(t)$ is determined.
+IG: done** In the earlier version of the EWA model [@camerer1997experience], $\phi$ and $\delta$ were free parameters.
 In the self-tuning EWA model [@ho2004economics], the values of $\delta$ and $\phi$ are learnt from experience.
-For details on how this is done, we refer the reader to [@ho2004economics].
-**MS: Should describe how the parameters are self-tuned with equations.
-IG: There are many equations for each of the parameters update, phi, delta and N...I'm concerned it would make for cumbersome reading, especially since EWA doesn't really fit well anyway.
-I've added that details of updates can be found in original camerer paper.
-MS: If it's three additional equations, that's not a big deal really.
-**
-
-As in the models above, actions are chosen based on a softmax decision rule:
-$$P_t(a,s) = \frac{\exp \{\lambda  A_{t}(a,s) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a',s) \} }$$
+$\delta$ is updated using the
+
+$$ \delta_{a}(t)  = 1  \text{  if  }  R(a,o_{t}) \geq r_{t}  \text{  and }  0 \text{  otherwise } $$
+
+**$\phi_{t}$ can be interpreted as the discount on prior experiences, modelling either limited agent memory or changes in the game conditions.
+At the core, $\phi_{t}$ depends on the surprise index $ S_{p}(t)$**:
+
+$$ \phi(t) = 1 - \frac{1}{2}S_{p}(t) $$
+
+**$S_{p}(t)$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play $ h_{k}(t)$**:
+
+$$  h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k,o_{\tau})}{t} $$
+
+As well as an indicator vector of the most recent opponent play:
+
+$$r^k(t) = I(o^k,o_{t})$$
+
+**Where $I$ is the indicator function as defined above.
+To get the surprise index, we simply sum all the squared deviations between the cumulative history vector $ h^{k}(t) $ and the immediate history $r^k(t)$**:
+
+$$S_{p}(t) = \sum_{k=1}^{|\mathcal{A}_g|} (h^{k}(t) - r^k(t))^2 $$
+
+For more details on the self-tuning EWA model, we refer the reader to [@ho2004economics].As in the models above, actions are chosen based on a softmax decision rule:
+
+$$P_t(a,s) = \frac{\exp \{\lambda  A_{t}(a,s) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a',s) \} } $$
 The self-tuning EWA has one free parameter: the inverse temperature of the softmax decision rule ($\lambda$).
@@
 
-For both experiments, we fitted all models to individual participant data by maximum likelihood estimation.
-**MS: need to mention the use of e.g.
-DEoptim** We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
+For both experiments, we fitted all models to individual participant data by maximum likelihood estimation using the DEoptim R package [@R-DEoptim].
+We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
 <!--, the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
@@
 exp1_comp_results <- read.csv(file="../exp1_all_results.csv")
-exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Nash","BCH_BT","BCH_WT", "RL","EWA")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])
+exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Nash","BCH_BT","BCH_NBT", "RL","EWA")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])
 
  #write.csv(exp1_comp_table ,file="exp1_comp_table ",row.names = TRUE)
- kable(exp1_comp_table)
+
 ```
@@
 
-**MS: Please present the models in the figures in the order mentioned in text (i.e., Nash, RL, EWA, BCH), and when providing versions of each, do so in the same order as well, i.e. x_NT, x_WT, x_BT**
+**MS: Please present the models in the figures in the order mentioned in text (i.e., Nash, RL, EWA, BCH), and when providing versions of each, do so in the same order as well, i.e.
+x_NT, x_WT, x_BT.
+IG : DONE **
 
@@
 Only a few participants were best described by one of the BCH models or the EWA model.
-Looking at BIC weights (Figure \ \@ref(fig:xp1-BIC-weigths)), we confirm this.
+We have also estimated BIC weights for each model and we confirm that <!-- (Figure \ \@ref(fig:xp1-BIC-weigths)), we confirm this -->.
 RL models have high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, which fits the picture drawn by the histogram.
-**MS: The BIC weight don't add much information, so maybe we could leave them out **
+**IG: mentioned we looked at BIC weights and removed BIC wgt plot **
 
@@
 
-#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
-par(las=2) # make label text perpendicular to axis
-par(mar=c(5,8,4,2)) # increase y-axis margin.
-barplot(exp1_comp_table,
-        horiz =TRUE, # rotate barplot for better visibility 
-        las=1, # change orientation x axis labels 
-        cex.names=0.8, # text label size
-        legend = rownames(exp1_comp_table),
-        beside =TRUE,
-        xlab="Number of participants",
-        args.legend=list( # positioning of legend box 
-        x  = 15,
-        y  = 10,
-        #x=ncol(exp1_comp_table) -3 ,
-        #y=max(colSums(exp1_comp_table)) ,
-        bty = "n")
- )
+exp1_comp_df <- as.data.frame(exp1_comp_table)
+colnames(exp1_comp_df) <- c("Opponent","model","Freq")
+
+exp1_comp_df$model.f <- factor(exp1_comp_df$model, levels = c("Nash","RL","EWA", "BCH_NBT", "BCH_BT"), ordered =TRUE)
+
+ggplot(data = exp1_comp_df,aes(x = model.f, y = Freq, fill = Opponent)) +geom_bar(stat = "identity") + xlab("Best fitting model") + ylab("Number of participants") + theme_apa()  + coord_flip()
+
+# #knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
+# par(las=2) # make label text perpendicular to axis
+# par(mar=c(5,8,4,2)) # increase y-axis margin.
+# barplot(exp1_comp_table,
+#         horiz =TRUE, # rotate barplot for better visibility 
+#         las=1, # change orientation x axis labels 
+#         cex.names=0.8, # text label size
+#         legend = rownames(exp1_comp_table),
+#         beside =TRUE,
+#         xlab="Number of participants",
+#         args.legend=list( # positioning of legend box 
+#         x  = 15,
+#         y  = 10,
+#         #x=ncol(exp1_comp_table) -3 ,
+#         #y=max(colSums(exp1_comp_table)) ,
+#         bty = "n")
+#  )
 
@@
 (ref:figure9-caption) Model BIC weights for participants in Experiment 1.
-```{r, xp1-BIC-weigths, fig.cap="(ref:figure9-caption)", fig.align="center"}
+```{r, include = FALSE, xp1-BIC-weigths, fig.cap="(ref:figure9-caption)", fig.align="center"}
 ggplot(d, aes(y = BIC_weight, x = 1)) + 
@@
 <!--  In Experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
---> This is also reflected in BIC weights in Figure \@ref(fig:xp2-BIC-weigths).
+-->
+
+<!-- This is also reflected in BIC weights in Figure \@ref(fig:xp2-BIC-weigths). -->
 
@@
 
-par(las=2) # make label text perpendicular to axis
-par(mar=c(5,8,4,2)) # increase y-axis margin.
-barplot(exp2_comp_table,
-        horiz =TRUE, # rotate barplot for better visibility 
-        las=1, # change orientation x axis labels 
-        cex.names=0.8, # text label size
-        beside =TRUE,
-        xlab="Number of participants",
-        #legend = c("level-1 opp first","level-2 opp first"),
-        legend = paste0(rownames(exp2_comp_table) , " faced first"),
-        args.legend=list( # positioning of legend box 
-        x  = 12,
-        y  = 10,
-        # x=ncol(exp2_comp_table) + 6,
-        # y=max(colSums(exp2_comp_table)) +1,
-        bty = "n")
- )
+exp2_comp_df <- as.data.frame(exp2_comp_table)
+colnames(exp2_comp_df) <- c("condition","model","Freq")
+
+exp2_comp_df$model.f <- factor(exp2_comp_df$model, levels = c("Nash","RL_NT","RL_WT","EWA_NT","EWA_WT","BCH_NT", "BCH_WT","BCH_BT"), ordered =TRUE)
+
+ggplot(data = exp2_comp_df,aes(x = model.f, y = Freq, fill = condition)) +geom_bar(stat = "identity") + xlab("Best fitting model") + ylab("Number of participants") + theme_apa() +coord_flip() + labs(fill = "Opponent faced first")
+
+# 
+# 
+# par(las=2) # make label text perpendicular to axis
+# par(mar=c(5,8,4,2)) # increase y-axis margin.
+# barplot(exp2_comp_table,
+#         horiz =TRUE, # rotate barplot for better visibility 
+#         las=1, # change orientation x axis labels 
+#         cex.names=0.8, # text label size
+#         beside =TRUE,
+#         xlab="Number of participants",
+#         #legend = c("level-1 opp first","level-2 opp first"),
+#         legend = paste0(rownames(exp2_comp_table) , " faced first"),
+#         args.legend=list( # positioning of legend box 
+#         x  = 12,
+#         y  = 10,
+#         # x=ncol(exp2_comp_table) + 6,
+#         # y=max(colSums(exp2_comp_table)) +1,
+#         bty = "n")
+#  )
 
@@
 (ref:figure11-caption) BIC weights for each model and participant in Experiment 2.
-```{r, xp2-BIC-weigths, fig.cap="(ref:figure11-caption)", fig.align="center", out.width="\\textwidth"}
+```{r, include = FALSE, xp2-BIC-weigths, fig.cap="(ref:figure11-caption)", fig.align="center", out.width="\\textwidth"}
 ggplot(d, aes(y = BIC_weight, x = 1)) + 
@@
 The results of our first experiment show that the majority of participants learnt to adapt to their opponent's strategy over multiple interactions, and generalised this learning to a similar game.
-Performance in early rounds indicated that transfer to the more dissimilar game was moderated by the degree of sophistication of the opponent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
-**MS: there was stronger evidence of moderation by game!** In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
+**Performance in early rounds indicated that learning transfer was moderated by the degree of similarity between games.
+There was not enough evidence for a difference in learning transfer between the two opponents.** In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
 In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
-Experiment 2 also offers more opportunities to test transfer of a learnt opponent model, as we could assess both within and between game transfer.
-The results on learning transfer confirmed the findings from the first experiment.
-Again, there was clear evidence of transfer in the early rounds of the later games.
-We also found that learning transfer is moderated by the type of opponent faced: Evidence of transfer was weaker for the level-2 opponent as compared to the level-1 opponent.
-That transfer was less evident for the more sophisticated level-2 opponent in both experiments may be due to a higher difficulty of learning that opponent's strategy.
+**There was clear evidence of transfer in the early rounds of the later games.
+On top of the moderation of the transfer by degree of similarity between games, we also found that learning transfer is moderated by the type of opponent faced: Transfer was harder when facing the level-2 opponent as compared to the level-1 opponent.** That evidence for transfer was weaker when facing the more sophisticated level-2 opponent may be due to a higher difficulty of learning that opponent's strategy.
 If it is more difficult to establish a model of the level-2 opponent, there is likely less knowledge to transfer to the new game.
 A player cannot transfer what they have not learnt.
-**MS: again, there was stronger evidence of moderation by game!**
 
@@
 ```{r create_r-references}
-r_refs(file = "Mendeley2.bib")
-
-```
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id = "refs"></div>
-\endgroup
+#r_refs(file = "Mendeley2.bib")
+```
+
+<!-- \begingroup -->
+<!-- \setlength{\parindent}{-0.5in} -->
+<!-- \setlength{\leftskip}{0.5in} -->
+<!-- <div id = "refs"></div> -->
+<!-- \endgroup -->

### 2021-09-01 Report/paper_draft_2021.tex
exp1 updated results and MS inputs

@@
 learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
+
 }
@@
 Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about their opponent's strategies and preferences (Mertens, 1990) are particularly useful to address this question.
-The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.~Nash equilibrium play) or use salient actions (e.g.~risk dominance) in later games, having had experience with a similar game environment previously (C.
-Camerer \& Knez, 2000; Teck-Hua Ho, Camerer, \& Weigelt, 1998).
+The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.~Nash equilibrium play) or use salient actions (e.g.~risk dominance) in later games, having had experience with a similar game environment previously (Camerer \& Knez, 2000; Ho, Camerer, \& Weigelt, 1998).
 As is well-known, a Nash equilibrium means that all players in a game act such that no-one can unilaterally improve their performance by deviating from their strategy.
@@
 Instead of thinking of their opponents as drawing random actions from a (non-uniform) probability distribution, people may rather think of their opponents as applying a form of iterated reasoning to determine their next action.
-The type of reasoning we refer to takes the form of ``I believe that you believe that I believe \ldots{}'' and has been shown to underlie people's decisions in economic games (C.
-F.
-Camerer, 2003; Costa-Gomes, Crawford, \& Broseta, 2001).
-It also underlies successful models in behavioural economics, such as Level-\(k\) and Cognitive Hierarchy models (C.
-F.
-Camerer, Ho, \& Chong, 2004), which posit that people assume their opponent applies a limited level of iterative reasoning, taking actions that are best responses to those of their (modelled) opponent.
+The type of reasoning we refer to takes the form of \enquote{I believe that you believe that I believe \ldots{}} and has been shown to underlie people's decisions in economic games (Camerer, 2003; Costa-Gomes, Crawford, \& Broseta, 2001).
+It also underlies successful models in behavioural economics, such as Level-\(k\) and Cognitive Hierarchy models (Camerer, Ho, \& Chong, 2004), which posit that people assume their opponent applies a limited level of iterative reasoning, taking actions that are best responses to those of their (modelled) opponent.
 
@@
 
-Iterative reasoning strategies can explain non-equilibrium play in a range of games, such as the \(p\)-beauty contest game (Nagel, 1995), dominance solvable games (C.
-F.
-Camerer, Ho, \& Chong, 2004), and various standard normal form games (Costa-Gomes, Crawford, \& Broseta, 2001).
+Iterative reasoning strategies can explain non-equilibrium play in a range of games, such as the \(p\)-beauty contest game (Nagel, 1995), dominance solvable games (Camerer et al., 2004), and various standard normal form games (Costa-Gomes et al., 2001).
 In the present study, we endow our computer opponents with limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
 In two experiments, participants face the same opponent (Experiment 1) or the same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, the structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
-To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of their opponent and the similarity of the games.
+To foreshadow our results, \textbf{we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of their opponent and the similarity of the games} \textbf{IG: I guess we can still say that given findings of exp 2\ldots{}} .
 Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a more habitual and cognitively less demanding strategy in the later stages of the games.
@@
 This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level-1 or level-2 player.
-Crucially, learning simple contingencies such as ``If I played rock on the previous round, playing scissors next will likely result in a win,'' is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
+Crucially, learning simple contingencies such as \enquote{If I played rock on the previous round, playing scissors next will likely result in a win}, is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
 
@@
 An example of the interface for the RPS game is provided in Figure~\ref{fig:feedback-rps-exp2}.
-On each round, the human player chooses an action, and after a random delay (between 0.5 and 3 seconds) is shown the action chosen by the computer opponent and the outcome of that round.
-A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
+On each round, the human player chooses an action, and after a random delay (between 0.5 and 3 seconds) is shown the action chosen by the computer opponent and the outcome of that round.A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
 The score was calculated as the number of wins minus the number of losses.
@@
 There was a main effect of Game (\(F(1.84,91.77) = 3.35\), \(\eta^{2} = 0.04\), \(p = .043\), Greenhouse-Geisser correction applied to the degrees of freedom to correct for non-sphericity).
-\textbf{MS: was this the only significant effect?
-If so, people might wonder why we next run analyses for each combination of player and game} We then ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
+
+To test for transfer by type of opponent faced, we ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG (\(t(150) = 3.96\), \(p < .001\)) and Numbers (\(t(150) = 3.74\), \(p < .001\)).
@@
 Figure~\ref{fig:screenshot-shootout} shows a snapshot of play in the Shootout game.
-What makes this game different to the other games is that there are now two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend ``right'' in the next round, they can win by either choosing to shoot ``left'' or ``center.'' A level-1 shooter who thinks that their goalkeeper opponent will repeat their last action has thus two possible best responses.
+What makes this game different to the other games is that there are now two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend \enquote{right} in the next round, they can win by either choosing to shoot \enquote{left} or \enquote{center}.
+A level-1 shooter who thinks that their goalkeeper opponent will repeat their last action has thus two possible best responses.
 A level-1 goalkeeper, however, has only a single best response (defending where their opponent aimed in the last round).
@@
 
-To measure transfer between games, we again focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
-We performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) repeated-measures ANOVA, with the first factor varying between participants.
-This showed a main effect of Game (\(F(1.94,92.98) = 7.67\), \(\eta^{2} = 0.04\), \(p < .001\)).
-\textbf{MS: Again, if there is no interaction, there might not be justification for running tests per opponent and game }
+\textbf{To measure transfer between games, we again focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
+We estimate a linear mixed effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables.
+Random model intercepts are assumed for participants.
+We found a main effect of Game(\(F(2,240) = 6.57\), \(p = .002\)) and an interaction effect between Game and Opponent type ( \(F(2,240) = 3.34\), \(p = .037\)).}
+
 We then ran statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
@@
 
-The results of Experiment 2 confirm the earlier results of Experiment 1 in a situation where participants need to learn about two distinct opponents.
+\textbf{The results of Experiment 2 confirm some earlier results from Experiment 1 in a situation where participants need to learn about two distinct opponents.
 As in Experiment 1, participants adapted their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
 Knowledge about both types of opponents were transferred to both the similar and dissimilar game.
-However, transfer to the dissimilar game was easier when facing the less sophisticated agent.
+This transfer was moderated by the degree of similarity between games.
+The interqaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.
+}
 
@@
 In the following, we will describe the models in more detail, and provide some intuition into how they implement learning about the game and/or the opponent.
-Throughout, we use the following notation: In each game \(g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}\), on each trial \(t\), the participant chooses an action \(a_t \in \mathcal{A}_g\), and the opponent chooses action \(o_t \in \mathcal{A}_g\), where \(\mathcal{A}_g\) is the set of allowed actions in game \(g\), e.g.~\(\mathcal{A}_\text{RPS} = \{R,P,S\}\).
+Throughout, we use the following notation: In each game \(g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}\), on each trial \(t\), the participant chooses an action \(a_t \in \mathcal{A}_g\), and the opponent chooses action \(o_t \in \mathcal{A}_g\), where \(\mathcal{A}_g\) is the set of allowed actions in game \(g\), e.g.
+\(\mathcal{A}_\text{RPS} = \{R,P,S\}\).
 The participant then receives reward \(r_t \in \{1,0,-1\}\), and the opponent receives \(-r_t\).
@@
 where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), and \(\alpha \in [0,1]\) the learning rate.
-For instance, \(Q_t(\{R,S\},P)\) denotes the value of taking action ``Paper'' this round if the player's last action was ``Rock'' and the opponent played ``Scissors.'' Actions are taken according to a softmax rule:
+For instance, \(Q_t(\{R,S\},P)\) denotes the value of taking action \enquote{Paper} this round if the player's last action was \enquote{Rock} and the opponent played \enquote{Scissors}.
+Actions are taken according to a softmax rule:
 \[P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}, \]
@@
 
-The self-tuning Experience Weighted Attraction (EWA) model (Teck H.
-Ho, Camerer, \& Chong, 2004) combines two seemingly different approaches, namely reinforcement learning and belief learning.
+The self-tuning Experience Weighted Attraction (EWA) model (Ho, Camerer, \& Chong, 2004) combines two seemingly different approaches, namely reinforcement learning and belief learning.
 Belief learning models are based on the assumption that players keep track of their opponent's frequency of past actions, and best respond to that.
@@
 The self-tuning EWA model has been shown to perform better than either RL or belief learning alone in various repeated games and has the advantage of having only one free parameter, the inverse temperature of the softmax choice function.
-The EWA model is based on updating ``Attractions'\,' for each action over time given a particular state.
+The EWA model is based on updating ``Attractions'' for each action over time given a particular state.
 The attraction of action \(a\) at time \(t\) given state \(s\) is denoted as \(A_{t}(a, s)\) and updated as
-\[ A_{t+1}(a,s) =  \frac{\phi \ N(t) \ A_{t}(a,s) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} \]
+\[ A_{t+1}(a,s) =  \frac{\phi(t) \ N(t) \ A_{t}(a,s) + [ \delta_{a}(t) + (1-\delta_{a}(t)) \ I(a_t = a )] \ R(a,o_t) } {\phi(t)N(t) + 1} \]
 where \(I(x)\) is an indicator function which takes the value 1 is its argument is true and 0 otherwise, and \(R(a,o_t)\) is the reward that would be obtained from playing action \(a\) against opponent action \(o_t\).
@@
 Setting \(\delta = 0\) leads to reinforcement only of actions taken, while positive values of \(\delta\) makes the update rule take into account foregone payoffs, which is similar to weighted fictitious play (Cheung \& Friedman, 1994).
-\(N(t)\) represents an experience weight and can be interpreted as the number of ``observation-equivalents'' of past experience.
+\(N(t)\) represents an experience weight and can be interpreted as the number of \enquote{observation-equivalents} of past experience.
 We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
-\textbf{MS: need to better describe what \(\phi\) is, and how \(N(t)\) is determined.} In the earlier version of the EWA model (C.
-Camerer, Ho, \& Others, 1997), \(\phi\) and \(\delta\) were free parameters.
-In the self-tuning EWA model (Teck H.
-Ho, Camerer, \& Chong, 2004), the values of \(\delta\) and \(\phi\) are learnt from experience.
-For details on how this is done, we refer the reader to (Teck H.
-Ho, Camerer, \& Chong, 2004).
-\textbf{MS: Should describe how the parameters are self-tuned with equations.
-IG: There are many equations for each of the parameters update, phi, delta and N\ldots I'm concerned it would make for cumbersome reading, especially since EWA doesn't really fit well anyway.
-I've added that details of updates can be found in original camerer paper.
-MS: If it's three additional equations, that's not a big deal really.
-}
+\textbf{MS: need to better describe what \(\phi\) is, and how \(N(t)\) is determined.
+IG: done} In the earlier version of the EWA model (Camerer, Ho, \& Others, 1997), \(\phi\) and \(\delta\) were free parameters.
+In the self-tuning EWA model (Ho et al., 2004), the values of \(\delta\) and \(\phi\) are learnt from experience.
+\(\delta\) is updated using the
 
-As in the models above, actions are chosen based on a softmax decision rule:
-\[P_t(a,s) = \frac{\exp \{\lambda  A_{t}(a,s) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a',s) \} }\]
+\[ \delta_{a}(t)  = 1  \text{  if  }  R(a,o_{t}) \geq r_{t}  \text{  and }  0 \text{  otherwise } \]
+
+\(\phi_{t}\) can be interpreted as the discount on prior experiences, modelling either limited agent memory or changes in the game conditions.
+At the core, \(\phi_{t}\) depends on the surprise index \$ S\_\{p\}(t)\$ :
+
+\[ \phi(t) = 1 - \frac{1}{2}S_{p}(t) \]
+
+\$ S\_\{p\}(t)\$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play \$ h\_\{k\}(t)\$ :
+
+\[  h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k,o_{\tau})}{t} \]
+
+As well as an indicator vector of the most recent opponent play:
+
+\[r^k(t) = I(o^k,o_{t})\]
+
+Where \(I\) is the indicator function as defined above.
+To get the surprise index, we simply sum all the squared deviations between the cumulative history vector \$ h\^{}\{k\}(t) \$ and the immediate history \(r^k(t)\):
+
+\[S_{p}(t) = \sum_{k=1}^{|\mathcal{A}_g|} (h^{k}(t) - r^k(t))^2 \]
+
+For more details on the self-tuning EWA model, we refer the reader to (Ho et al., 2004).As in the models above, actions are chosen based on a softmax decision rule:
+
+\[P_t(a,s) = \frac{\exp \{\lambda  A_{t}(a,s) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a',s) \} } \]
 The self-tuning EWA has one free parameter: the inverse temperature of the softmax decision rule (\(\lambda\)).
@@
 
-For both experiments, we fitted all models to individual participant data by maximum likelihood estimation.
-\textbf{MS: need to mention the use of e.g.~DEoptim} We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
+For both experiments, we fitted all models to individual participant data by maximum likelihood estimation using the DEoptim R package (Mullen, Ardia, Gil, Windover, \& Cline, 2011).
+We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
 
@@
 
-\textbf{MS: Please present the models in the figures in the order mentioned in text (i.e., Nash, RL, EWA, BCH), and when providing versions of each, do so in the same order as well, i.e.~x\_NT, x\_WT, x\_BT}
+\textbf{MS: Please present the models in the figures in the order mentioned in text (i.e., Nash, RL, EWA, BCH), and when providing versions of each, do so in the same order as well, i.e.~x\_NT, x\_WT, x\_BT.
+IG : DONE }
 
@@
 Only a few participants were best described by one of the BCH models or the EWA model.
-Looking at BIC weights (Figure ~\ref{fig:xp1-BIC-weigths}), we confirm this.
+We have also estimated BIC weights for each model and we confirm that .
 RL models have high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, which fits the picture drawn by the histogram.
-\textbf{MS: The BIC weight don't add much information, so maybe we could leave them out }
+\textbf{IG: mentioned we looked at BIC weights and removed BIC wgt plot }
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics{paper_draft_2021_files/figure-latex/xp1-BIC-weigths-1}
-
-}
-
-\caption{Model BIC weights for participants in Experiment 1.}\label{fig:xp1-BIC-weigths}
-\end{figure}
-
 In Experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that the RL model was again more successful than the Bayesian Cognitive Hierarchy models (with or without transfer) and the EWA model in fitting participants' action choices.
-This is also reflected in BIC weights in Figure \ref{fig:xp2-BIC-weigths}.
 
@@
 \caption{Experiment 2 Histogram of best fitting computational models by condition}\label{fig:exp2-comp-models}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=\textwidth]{paper_draft_2021_files/figure-latex/xp2-BIC-weigths-1}
-
-}
-
-\caption{BIC weights for each model and participant in Experiment 2.}\label{fig:xp2-BIC-weigths}
 \end{figure}
@@
 
-The switching model (AIC = 16,879.97, BIC = 16,936.81) in Experiment 2 again fits better than the restricted non-switching model (AIC = 16,938.41, BIC = 16,952.62), \(\chi^2(6) = 70.44\), \(p < .001\).
+In Experiment 2, the switching model (AIC = 16,879.97, BIC = 16,936.81) again fits better than the restricted non-switching model (AIC = 16,938.41, BIC = 16,952.62), \(\chi^2(6) = 70.44\), \(p < .001\).
 The posterior probabilities of the strategies (Figure~\ref{fig:exp2-posteriors-plot}) show very clear evidence of strategy switching across games and stages, from using a BCH model in the initial rounds to an RL strategy later on.
@@
 
-The results of our first experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to a similar game.
-Performance in early rounds indicated that transfer to the more dissimilar game was moderated by the degree of sophistication of the opponent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
-In the second experiment, participants faced both types of opponents, which allows for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent within a game.
+The results of our first experiment show that the majority of participants learnt to adapt to their opponent's strategy over multiple interactions, and generalised this learning to a similar game.
+Performance in early rounds indicated that transfer to the more dissimilar game was moderated by the degree of similarity between games.
+There was not enough evidence for a difference in learning transfer between the two opponents.
+In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
 In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
-Experiment 2 also offers more opportunities to test transfer of a learnt opponent model.
-The results on learning transfer confirmed the findings from the first experiment.
-Again, there was clear evidence of transfer in the early rounds of the later games.
-We also found that learning transfer is moderated by the type of opponent faced: Evidence of transfer was weaker for the level-2 opponent as compared to the level-1 opponent.
-That transfer was less evident for the more sophisticated level-2 opponent in both experiments may be due to a higher difficulty of learning that opponent's strategy.
+Experiment 2 also offers more opportunities to test transfer of a learnt opponent model, as we could assess both within and between game transfer.
+There was clear evidence of transfer in the early rounds of the later games.
+On top of the moderation of the transfer by degree of similarity between games, we also found that learning transfer is moderated by the type of opponent faced: Evidence of transfer was weaker for the level-2 opponent as compared to the level-1 opponent.
+That evidence for transfer was weaker when facing the more sophisticated level-2 opponent may be due to a higher difficulty of learning that opponent's strategy.
 If it is more difficult to establish a model of the level-2 opponent, there is likely less knowledge to transfer to the new game.
@@
 
-What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
+What exactly did the players learn in the first game (RPS) that allowed them to beat their opponent in the later games (FWG, and Numbers or Shootout)?
 what did the players learn specifically about their opponent's strategy and what form did this learning take?
-
 One possible answer is that participants learned simple rules based on last round play.
-For instance, ``play scissors whenever my opponent played rock in last round,'' or ``play paper whenever the last round play was either rock or scissors.'' These are the type of strategies that are learned by the model-free reinforcement learning we used in our computational modelling.
+For instance, \enquote{play scissors whenever my opponent played rock in last round}, or \enquote{play paper whenever the last round play was either rock or scissors}.
+These are the type of strategies that are learned by the model-free reinforcement learning we used in our computational modelling.
 While this strategy fitted participants' actions the best overall, there are at least two reasons why this account is not satisfactory as a complete description of participants' behaviour.
 Firstly, the learned strategies are not transferable to new games.
-There is no simple way to map ``play scissors whenever my opponent played rock in last round'' in the RPS game to ``play grass whenever my opponent played fire in last round.'' Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this quickly enough: Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
+There is no simple way to map \enquote{play scissors whenever my opponent played rock in last round} in the RPS game to \enquote{play grass whenever my opponent played fire in last round}.
+Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this: Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
 Secondly, a reinforcement learning strategy would fare equally well against the level-1 and level-2 opponent.
@@
 Because of the cyclicity in action choices (e.g., rock beats scissors, scissors beats paper, paper beats rock), it is possible to beat a level-2 opponent most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
-This is a rule that wins and is transferable to other games as it does not depend on action labels.
-In the same vein, a heuristic that beats a level-1 player can be stated as ``Choose the action that would have been beaten by my previous action.'' Intuitively, it seems that the heuristic for the level-2 player is simpler than that for the level-1 player, which is at odds with the difference in performance.
+This is a rule that wins and is transferable to other games, as it does not depend on action labels.
+In the same vein, a heuristic that beats a level-1 player can be stated as \enquote{Choose the action that would have been beaten by my previous action}.
+Intuitively, it seems that this heuristic for a level-2 player is simpler than that for a level-1 player, which is at odds with the finding that participants performed better against the level-1 opponent.
 
 A second explanation is that participants engaged in iterative reasoning, inferring their opponent's beliefs and countering the resulting actions.
-For instance, this would be reasoning of the form ``My opponent expects me to repeat my last action, choosing an action that would beat my last action.
-Hence, I will choose the action that beats their best response'' or ``My opponent thinks I expect them to repeat their action, hence expecting me to choose the action that beats their last action.
-They will therefore choose the action that beats this one, and hence I should choose the action that beats their best response.'' Beating a level-1 player, in this account, requires being a level-2 player, and beating a level-2 player requires being a level-3 player.
+For instance, this would be reasoning of the form \enquote{My opponent expects me to repeat my last action, choosing an action that would beat my last action.
+Hence, I will choose the action that beats their best response} or \enquote{My opponent thinks I expect them to repeat their action, hence expecting me to choose the action that beats their last action.
+They will therefore choose the action that beats this one, and hence I should choose the action that beats their best response.} Beating a level-1 player, in this account, requires being a level-2 player, and beating a level-2 player requires being a level-3 player.
 Intuitively, the additional step of iterative reasoning involved in beating a level-2 player makes the level-3 strategy more demanding and difficult to implement, which is consistent with the lower performance against the level-2 opponent.
@@
 This is the type of learning encapsulated by our Bayesian Cognitive Hierarchy model.
-It involves the evaluation of explicit hypotheses and results in better problem-solving skills (\textbf{mandler2004foundations?}).
+It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
 Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (Stahl, 2000, 2003).
@@
 
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-batzilis}{}%
@@
 \leavevmode\hypertarget{ref-camerer1997experience}{}%
-Camerer, C., Ho, T.-H., \& Others. (1997). \emph{{Experience-weighted attraction learning in games: A unifying approach}}.
+Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
 
 \leavevmode\hypertarget{ref-knez2000}{}%
-Camerer, C., \& Knez, M. (2000). \emph{{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}}.
+Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
 
 \leavevmode\hypertarget{ref-cheung1994learning}{}%
-Cheung, Y.-W., \& Friedman, D. (1994). \emph{{Learning in evolutionary games: some laboratory results}}. University of California, Santa Cruz.
+Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
 
@@
 \leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, Teck H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{{The economics of learning models: A self-tuning theory of learning in games}}.
+Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
 
 \leavevmode\hypertarget{ref-ho1998iterated}{}%
-Ho, Teck-Hua, Camerer, C., \& Weigelt, K. (1998). {Iterated dominance and iterated best response in experimental" p-beauty contests"}. \emph{The American Economic Review}, \emph{88}(4), 947--969.
+Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
 
@@
 
+\leavevmode\hypertarget{ref-mandler2004foundations}{}%
+Mandler, J. M. (2004). \emph{The foundations of mind: Origins of conceptual thought}. Oxford University Press.
+
 \leavevmode\hypertarget{ref-mertens1990repeated}{}%
-Mertens, J.-F. (1990). {Repeated games}. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+
+\leavevmode\hypertarget{ref-R-DEoptim}{}%
+Mullen, K., Ardia, D., Gil, D., Windover, D., \& Cline, J.
+(2011).
+DEoptim: An R package for global optimization by Differential Evolution.
+\emph{Journal of Statistical Software}, \emph{40}(6), 1--26.
+\url{https://doi.org/10.18637/jss.v040.i06}
 
@@
 \leavevmode\hypertarget{ref-shachat2004we}{}%
-Shachat, J., \& Swarthout, J. T. (2004). {Do we detect and exploit mixed strategy play by opponents?} \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
+Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
 
@@
 \leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
-Spiliopoulos, L. (2013). {Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game}. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
+Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
 
@@
 \leavevmode\hypertarget{ref-stahl1995players}{}%
-Stahl, D. O., \& Wilson, P. W. (1995). {On players models of other players: Theory and experimental evidence}. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
+Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
 
@@
 \leavevmode\hypertarget{ref-watkins1992q}{}%
-Watkins, C. J. C. H., \& Dayan, P. (1992). {Q-learning}. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
+Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
 
@@
 (2011).
-{Decision Making and the Avoidance of Cognitive Demand}.
+Decision Making and the Avoidance of Cognitive Demand.
 \emph{Experimental Psychology}.
@@
 
-\end{CSLReferences}
+\leavevmode\hypertarget{ref-batzilis}{}%
+Batzilis, D., Jaffe, S., Levitt, S., List, J.
+A., \& Picel, J.
+(2016).
+\emph{How facebook can deepen our understanding of behavior in strategic settings: Evidence from a million rock-paper-scissors games}.
+working paper.
 
-\endgroup
+\leavevmode\hypertarget{ref-camerer2003behavioural}{}%
+Camerer, C. F. (2003). Behavioural studies of strategic thinking in games. \emph{Trends in Cognitive Sciences}, \emph{7}(5), 225--231.
+
+\leavevmode\hypertarget{ref-camerer2004cognitive}{}%
+Camerer, C. F., Ho, T.-H., \& Chong, J.-K. (2004). A cognitive hierarchy model of games. \emph{The Quarterly Journal of Economics}, \emph{119}(3), 861--898.
+
+\leavevmode\hypertarget{ref-camerer1997experience}{}%
+Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
+
+\leavevmode\hypertarget{ref-knez2000}{}%
+Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
+
+\leavevmode\hypertarget{ref-cheung1994learning}{}%
+Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
+
+\leavevmode\hypertarget{ref-costa2001cognition}{}%
+Costa-Gomes, M., Crawford, V. P., \& Broseta, B. (2001). Cognition and behavior in normal-form games: An experimental study. \emph{Econometrica}, \emph{69}(5), 1193--1235.
+
+\leavevmode\hypertarget{ref-daw2005uncertainty}{}%
+Daw, N.
+D., Niv, Y., \& Dayan, P.
+(2005).
+Uncertainty-based competition between prefrontal and dorsolateral striatal systems for behavioral control.
+\emph{Nature Neuroscience}, \emph{8}(12), 1704--1711.
+
+\leavevmode\hypertarget{ref-ho2004economics}{}%
+Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
+
+\leavevmode\hypertarget{ref-ho1998iterated}{}%
+Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
+
+\leavevmode\hypertarget{ref-Lake2017}{}%
+Lake, B.
+M., Ullman, T.
+D., Tenenbaum, J.
+B., \& Gershman, S.
+J.
+(2017).
+Building machines that learn and think like people.
+\emph{Behavioral and Brain Sciences}, \emph{40}.
+\url{https://doi.org/10.1017/S0140525X16001837}
+
+\leavevmode\hypertarget{ref-lieder2020resource}{}%
+Lieder, F., \& Griffiths, T.
+L.
+(2020).
+Resource-rational analysis: Understanding human cognition as the optimal use of limited computational resources.
+\emph{Behavioral and Brain Sciences}, \emph{43}.
+
+\leavevmode\hypertarget{ref-mandler2004foundations}{}%
+Mandler, J. M. (2004). \emph{The foundations of mind: Origins of conceptual thought}. Oxford University Press.
+
+\leavevmode\hypertarget{ref-mertens1990repeated}{}%
+Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+
+\leavevmode\hypertarget{ref-R-DEoptim}{}%
+Mullen, K., Ardia, D., Gil, D., Windover, D., \& Cline, J.
+(2011).
+DEoptim: An R package for global optimization by Differential Evolution.
+\emph{Journal of Statistical Software}, \emph{40}(6), 1--26.
+\url{https://doi.org/10.18637/jss.v040.i06}
+
+\leavevmode\hypertarget{ref-nagel1995unraveling}{}%
+Nagel, R. (1995). Unraveling in guessing games: An experimental study. \emph{The American Economic Review}, \emph{85}(5), 1313--1326.
+
+\leavevmode\hypertarget{ref-shachat2004we}{}%
+Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
+
+\leavevmode\hypertarget{ref-Simon_Daw_11}{}%
+Simon, D.
+A., \& Daw, N.
+D.
+(2011).
+Environmental statistics and the trade-off between model-based and TD learning in humans.
+\emph{Advances in Neural Information Processing Systems 24: 25th Annual Conference on Neural Information Processing Systems 2011, NIPS 2011}, 1--9.
+
+\leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
+Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
+
+\leavevmode\hypertarget{ref-stahl2000rule}{}%
+Stahl, D. O. (2000). Rule learning in symmetric normal-form games: Theory and evidence. \emph{Games and Economic Behavior}, \emph{32}(1), 105--138.
+
+\leavevmode\hypertarget{ref-stahl2003sophisticated}{}%
+Stahl, D. O. (2003). Sophisticated learning and learning sophistication. \emph{Available at SSRN 410921}.
+
+\leavevmode\hypertarget{ref-stahl1995players}{}%
+Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
+
+\leavevmode\hypertarget{ref-R-depmixS4}{}%
+Visser, I., \& Speekenbrink, M.
+(2010).
+depmixS4: An R package for hidden markov models.
+\emph{Journal of Statistical Software}, \emph{36}(7), 1--21.
+Retrieved from \url{http://www.jstatsoft.org/v36/i07/}
+
+\leavevmode\hypertarget{ref-wang2014social}{}%
+Wang, Z., Xu, B., \& Zhou, H.-J. (2014). Social cycling and conditional responses in the rock-paper-scissors game. \emph{Scientific Reports}, \emph{4}(1), 1--7.
+
+\leavevmode\hypertarget{ref-watkins1992q}{}%
+Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
+
+\leavevmode\hypertarget{ref-Kool_2011}{}%
+Wouter Kool, Joseph T.
+McGuire, Zev B.
+Rosen, Matthew M.
+Bovinick.
+(2011).
+Decision Making and the Avoidance of Cognitive Demand.
+\emph{Experimental Psychology}.
+\url{https://doi.org/10.2996/kmj/1138846322}
 

### 2021-09-01 exp1_clean_analysis.Rmd
exp1 updated results and MS inputs

--- 2021-06-04 _main.Rmd
@@
----
-title: "Bayesian_models_exp1"
-output: html_document
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-library(dplyr)
-```
-
-```{r}
-
-dat <- read.csv("data20180719.csv")
-
-####### test data
-
-#dat <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")
-
-#######
-
-dat <- as_tibble(dat) %>% group_by(human_id,game)
-dat <- dat %>%
-  mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1))
-
-```
-
-```{r}
-## the following computes probabilities of ai actions assuming
-## strategy is always followed. (level refers to ai level)
-
-## level 0 predictions
-dat <- dat %>% mutate(pred_a1_level0 = case_when(
-  game == "rps" & ai_action_prev == "rock" ~ 1,
-  game == "fwg" & ai_action_prev == "fire" ~ 1,
-  game == "numbers" & ai_action_prev == "one" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a2_level0 = case_when(
-  game == "rps" & ai_action_prev == "paper" ~ 1,
-  game == "fwg" & ai_action_prev == "water" ~ 1,
-  game == "numbers" & ai_action_prev == "two" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a3_level0 = case_when(
-  game == "rps" & ai_action_prev == "scissors" ~ 1,
-  game == "fwg" & ai_action_prev == "grass" ~ 1,
-  game == "numbers" & ai_action_prev == "three" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a4_level0 = case_when(
-  game == "numbers" & ai_action_prev == "four" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-dat <- dat %>% mutate(pred_a5_level0 = case_when(
-  game == "numbers" & ai_action_prev == "five" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-
-## level 1 predictions
-dat <- dat %>% mutate(pred_a1_level1 = case_when(
-  game == "rps" & human_action_prev == "scissors" ~ 1,
-  game == "fwg" & human_action_prev == "grass" ~ 1,
-  game == "numbers" & human_action_prev == "five" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a2_level1 = case_when(
-  game == "rps" & human_action_prev == "rock" ~ 1,
-  game == "fwg" & human_action_prev == "fire" ~ 1,
-  game == "numbers" & human_action_prev == "one" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a3_level1 = case_when(
-  game == "rps" & human_action_prev == "paper" ~ 1,
-  game == "fwg" & human_action_prev == "water" ~ 1,
-  game == "numbers" & ai_action_prev == "two" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a4_level1 = case_when(
-  game == "numbers" & ai_action_prev == "three" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-dat <- dat %>% mutate(pred_a5_level1 = case_when(
-  game == "numbers" & ai_action_prev == "four" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-
-## level 2 predictions
-dat <- dat %>% mutate(pred_a1_level2 = case_when(
-  game == "rps" & ai_action_prev == "paper" ~ 1,
-  game == "fwg" & ai_action_prev == "water" ~ 1,
-  game == "numbers" & ai_action_prev == "four" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a2_level2 = case_when(
-  game == "rps" & ai_action_prev == "scissors" ~ 1,
-  game == "fwg" & ai_action_prev == "grass" ~ 1,
-  game == "numbers" & ai_action_prev == "five" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a3_level2 = case_when(
-  game == "rps" & ai_action_prev == "rock" ~ 1,
-  game == "fwg" & ai_action_prev == "fire" ~ 1,
-  game == "numbers" & ai_action_prev == "one" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a4_level2 = case_when(
-  game == "numbers" & ai_action_prev == "two" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-dat <- dat %>% mutate(pred_a5_level2 = case_when(
-  game == "numbers" & ai_action_prev == "three" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-
-dat$ai_action_num <- recode(dat$ai_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "one" = 1, "two" = 2, "three" = 3, "four" = 4 , "five" = 5)
-dat$human_action_num <- recode(dat$human_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "one" = 1, "two" = 2, "three" = 3, "four" = 4 , "five" = 5)
-
-```
-
-```{r}
-# group data by subjective component id
-
-# if human generalizes over games, we can run update the prior generally
-# if human does not generalize, we need to reset the prior at the start of each ?stage?
-exp1_Bayes_model_LL <- function(par,data, generalize = c("game","no"), softmax= TRUE, return_value = "-2loglik") {
-
-  # return_value=c("-2loglik","likelihood_by_trial")
-  # input data for this function should be a subset for a single participant
-  generalize <- match.arg(generalize)
-  alpha <- par[1] # probability that ai opponent plays according to strategy
-
-  if(softmax) {
-    lambda <- par[2] # inverse temperature parameter in softmax function
-  }
-
-  beta <- 1 # probability that human plays according to best response 
-  prior <- c(1,1,1) # prior alpha for dirichlet on p(level)
-  prior <- prior/sum(prior)
-
-  # use alpha to change the "deterministic" prediction
-
-  dat <- ungroup(data) %>%
-     mutate_at(.vars = vars(c(starts_with("pred_a1"),starts_with("pred_a2"),starts_with("pred_a3"))), 
-                            funs (case_when(
-      game == "numbers" ~  alpha*. + (1-alpha)/5,
-                  TRUE ~ alpha*. + (1-alpha)/3))) %>%
-     mutate_at(.vars = vars(c(starts_with("pred_a4"),starts_with("pred_a5"))), 
-                            funs (case_when(
-      game == "numbers" ~  alpha*. + (1-alpha)/5,
-                  TRUE ~ 0)))
-
-  if(generalize == "no") {
-    # group by game and stage
-    dat <- group_by(dat,game,add=TRUE)
-  }
-
-  # compute likelihood of ai action
-  dat <- dat %>%
-    mutate(
-      lik_level0 = case_when(
-        ai_action_num == 1 ~ pred_a1_level0,
-        ai_action_num == 2 ~ pred_a2_level0,
-        ai_action_num == 3 ~ pred_a3_level0,
-        ai_action_num == 4 ~ pred_a4_level0,
-        ai_action_num == 5 ~ pred_a5_level0
-      ),
-      lik_level1 = case_when(
-        ai_action_num == 1 ~ pred_a1_level1,
-        ai_action_num == 2 ~ pred_a2_level1,
-        ai_action_num == 3 ~ pred_a3_level1,
-        ai_action_num == 4 ~ pred_a4_level1,
-        ai_action_num == 5 ~ pred_a5_level1
-      ),
-      lik_level2 = case_when(
-        ai_action_num == 1 ~ pred_a1_level2,
-        ai_action_num == 2 ~ pred_a2_level2,
-        ai_action_num == 3 ~ pred_a3_level2,
-        ai_action_num == 4 ~ pred_a4_level2,
-        ai_action_num == 5 ~ pred_a5_level2
-      )
-    )
-
-  # use likelihood to compute the posterior predictive probability of each level
-  dat <- dat %>%
-    mutate(logpost_level0 = lag(log(prior[1]) + cumsum(log(lik_level0)),default=log(prior[1])),
-           logpost_level1 = lag(log(prior[2]) + cumsum(log(lik_level1)),default=log(prior[2])),
-           logpost_level2 = lag(log(prior[3]) + cumsum(log(lik_level2)),default=log(prior[3]))) %>%
-    # you can add or subtract any constant from the log-likelihoods; this can aid in precision
-    mutate(min = pmin(logpost_level0,logpost_level1, logpost_level2)) %>%
-      mutate(normalize = exp(logpost_level0 - min) + exp(logpost_level1 - min) + exp(logpost_level2 - min)) %>%
-        mutate(post_level0 = exp(logpost_level0 - min)/normalize,
-               post_level1 = exp(logpost_level1 - min)/normalize,
-               post_level2 = exp(logpost_level2 - min)/normalize)
-
-   #cat(as.character(c(round(dat$post_level0,2), round(dat$post_level1,2), round(dat$post_level2,2)), "\n", "\n"))
-
-  # use posterior predictive probability to predict probability of each ai and then human action
-  # opp is ai and self is human player here
-  dat <- dat %>%
-    mutate(p_opp_a1 = post_level0*pred_a1_level0 + post_level1*pred_a1_level1 + post_level2*pred_a1_level2,
-           p_opp_a2 = post_level0*pred_a2_level0 + post_level1*pred_a2_level1 + post_level2*pred_a2_level2,
-           p_opp_a3 = post_level0*pred_a3_level0 + post_level1*pred_a3_level1 + post_level2*pred_a3_level2,
-           p_opp_a4 = post_level0*pred_a4_level0 + post_level1*pred_a4_level1 + post_level2*pred_a4_level2,
-           p_opp_a5 = post_level0*pred_a5_level0 + post_level1*pred_a5_level1 + post_level2*pred_a5_level2
-    ) %>%
-      mutate(p_self_a1 = case_when(
-              game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a5,
-              TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a3)
-                ),
-             p_self_a2 = case_when(
-               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a1,
-               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a1)
-             ),
-             p_self_a3 = case_when(
-               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a2,
-               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a2)
-             ),
-             p_self_a4 = case_when(
-               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a3,
-               TRUE ~ 0
-             ),
-             p_self_a5 = case_when(
-               game == "numbers" ~ (1-beta)*(1/3) + beta*p_opp_a4,
-               TRUE ~ 0
-             )
-        )
-
-  #cat(as.character(c(round(dat$p_self_a1,2), "\n", "\n")))
-
-  # now finally compute the likelihood of human actions 
-  if (softmax) {
-
-        dat <- dat %>% 
-    mutate(sumexp = exp(lambda*p_self_a1) + exp(lambda*p_self_a2) + exp(lambda*p_self_a3) + exp(lambda*p_self_a4) + exp(lambda*p_self_a5)) %>%
-             mutate(
-               loglik = case_when(
-                 human_action_num == 1 ~ log(exp(lambda*p_self_a1)/sumexp),
-                 human_action_num == 2 ~ log(exp(lambda*p_self_a2)/sumexp),
-                 human_action_num == 3 ~ log(exp(lambda*p_self_a3)/sumexp),
-                 human_action_num == 4 ~ log(exp(lambda*p_self_a4)/sumexp),
-                 human_action_num == 5 ~ log(exp(lambda*p_self_a5)/sumexp)
-      )
-    )
-  } else {
-    dat <- dat %>% 
-    mutate(
-      loglik = case_when(
-        human_action_num == 1 ~ log(p_self_a1),
-        human_action_num == 2 ~ log(p_self_a2),
-        human_action_num == 3 ~ log(p_self_a3),
-        human_action_num == 4 ~ log(p_self_a4),
-        human_action_num == 5 ~ log(p_self_a5))
-    )
-
-  }
-
-  #cat(as.character(exp(dat$loglik)), "\n", "\n")
-
-  ret <- -2*sum(dat$loglik)
-  if(return_value == "-2loglik") {
-    if(is.infinite(ret) || is.nan(ret)) {
-    return(1e+300)
-    } else {
-      return(ret)
-    } 
-  } else if ((return_value == "likelihood_by_trial")) {
-    return(exp(dat$loglik))
-  }
-
-}
-
-```
-
-```{r}
-# testing funcrion. Careful dat here can be all participants data, check how it is defined. 
-exp1_Bayes_model_LL(c(0.4, 1) ,data = dat, generalize = "no", softmax = TRUE, "likelihood_by_trial")[51]
-exp1_Bayes_model_LL(c(0.4) ,data = dat, generalize = "no", softmax = FALSE, "likelihood_by_trial")[51]
-```
-## Compare loglikelihood: probability matching vs softmax (with Between game transfer for now)
-
-```{r echo=FALSE}
-library(DEoptim)
-
-prob_match_tr <- use_softmax_tr <- use_softmax_NT <- list()
-
-# # Using DEOptim 
-for(id in levels(dat$human_id)) {
-  tdat <- subset(dat,human_id == id)
-  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))
-
-  prob_match_tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-                                  generalize = "game",FALSE, control=ctrl)
-
-  use_softmax_tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat, generalize = "game",TRUE, control=ctrl)
-
-  use_softmax_NT[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0,0), upper = c(1,1000), data = tdat, generalize = "no",TRUE, control=ctrl)
-
-}
-
-save(prob_match_tr,file="BCH_prob_match_tr.RData")
-save(use_softmax_tr,file="BCH_use_softmax_tr.RData")
-save(use_softmax_NT,file="BCH_use_softmax_NT.RData")
-```
-
-```{r}
-compare_table <- data.frame()
-for(id in levels(dat$human_id)) {
-  compare_table <- rbind(compare_table,
-                       data.frame(
-                         "ID" = id,
-                         "prob_match_tr_BIC" = prob_match_tr[[id]]$optim$bestval+ 1*log(150),
-                         "softmax_tr_BIC" = use_softmax_tr[[id]]$optim$bestval+ 2*log(150)
-                         ))
-}
-
-```
-
-```{r}
-
-comp_models <- compare_table[c("ID","prob_match_tr_BIC","softmax_tr_BIC")]
-
-BIC_weights_BCH <- comp_models["ID"]
-BIC_weights_BCH[,2:ncol(comp_models)] <- t(apply(comp_models[,2:ncol(comp_models)], 1, function(i) exp(-0.5*(i-min(i)) )))
-colnames(BIC_weights_BCH) <-colnames(comp_models)
-
-BIC_weights_BCH[,2:ncol(BIC_weights_BCH)] <- t(apply(BIC_weights_BCH[,-1], 1, function(i) round(i/sum(i),2)))
-
-colMeans(BIC_weights_BCH[,2:ncol(BIC_weights_BCH)])
-```
-
-```{r}
-
-```
-
-```{r}
-#PLot likelihood for first participant as function of parameter
-
-dat <- subset(dat, human_id == "QSuzBXpbyRc370HsAACW")
-likelihoods <- list()
-for (t in 1:95) {
-  likelihoods[t] <- exp1_Bayes_model_LL(t/100,data = dat, generalize = "game")
-}
-
-jpeg(file="QSuzBXpbyRc370HsAACW.jpeg")
-plot(unlist(likelihoods))
-dev.off()
-
-```
-
-```{r, ECHO = FALSE}
-
-library(DEoptim)
-
-exp1_Bayes_game_Tr <- exp1_Bayes_no_Tr <- list()
-
-# # Using DEOptim 
-for(id in levels(dat$human_id)) {
-  tdat <- subset(dat,human_id == id)
-  ctrl <- DEoptim.control(NP = 20, itermax=50,parallelType = 1, packages = c("dplyr"))
-  exp1_Bayes_game_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-                                  generalize = "game",control=ctrl)
-  exp1_Bayes_no_Tr[[id]] <- DEoptim(exp1_Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
-                                  generalize = "no",control=ctrl)
-}
-
-# using optim
-
-# for(id in levels(dat$human_id)) {
-#   tdat <- subset(dat,human_id == id)
-#   # ctrl <- DEoptim.control(NP = 20, itermax=50)
-#   
-#   Bayes_same_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
-#   
-#   
-#   Bayes_same_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
-# 
-#   Bayes_same_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
-#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
-# 
-#   Bayes_distinct_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
-# 
-#   Bayes_distinct_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
-# 
-#   Bayes_distinct_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
-#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
-# }
-```
-```{r}
-
-exp1_Bayes_game_Tr[["QSuzBXpbyRc370HsAACW"]]$optim$bestval
-exp1_Bayes_game_Tr[["QSuzBXpbyRc370HsAACW"]]$optim$bestmem[[1]]
-```
-
-<!--chapter:end:Bayesian_models_exp1.Rmd-->
-
----
-title: "opponent modelling"
-author: "Ismail Guennouni & Maarten Speekenbrink"
-date: "1 November 2019"
-output:
-  pdf_document: default
-  html_document: default
----
-
-```{r setup, include=FALSE}
-library(knitr)
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-## Reading data
-
-```{r}
-dat <- read.csv("data20180719.csv")
-#dat <- read.csv("test_data.csv")
-```
-
-## Preprosessing and transforming data
-
-```{r}
-# using some functions from the 'tidyverse' (also for me to get use to them ;-)
-library(tidyr)
-library(dplyr)
-library(DEoptim)
-library(optimParallel)
-library(ggpubr)
-
-# create a new data.frame in a 'wide format'
-# widedata <- dat %>%
-#   unite(game_block,game,block) %>% # this creates a new variable which combines game and block
-#     group_by(human_id,condition,game_block) %>% # let the functions know you want to separate things by ID, condition, and game_block
-#       summarize(mean_score = mean(score)) %>% # compute average score (i.e wins - losses)
-#         spread(game_block,mean_score) # reformat in the 'wide' format
-# # save the data file as a .csv to use in e.g. SPSS
-# write.csv(widedata,row.names=FALSE,file="scores_wide.csv")
-
-```
-
-```{r estimate-models, cache=TRUE}
-# read in the various files which 
-rps_predict_opp <- read.csv("rps_predict_opp.csv")
-fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
-numbers_predict_opp <- read.csv("numbers_predict_opp.csv")
-
-# transform 'winner' variable in numeric score
-dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
-# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
-dat$block <- as.numeric(cut(dat$round,2))
-
-# recode actions to make them equal to the codes in these files
-dat$h_action <- recode(dat$human_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
-dat$a_action <- recode(dat$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
-
-write.csv(dat,file = "exp1_data.csv", row.names = FALSE)
-
-# logit tranformation
-my_logit <- function(x) {
-  ret <- log(x/(1-x))
-  ret[x==0] <- -Inf
-  ret[x==1] <- Inf 
-  return(ret)
-}
-
-# inverse logit transformation
-my_logistic <- function(x) {
-  ret <- 1/(1+exp(-x))
-  ret[x == -Inf] <- 0.0
-  ret[x == Inf] <- 1.0
-  return(ret)
-}
-
-```
-
-#### New work 
-## Q-learning (Basic)
-```{r}
-Q_learn <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
-  # actions
-  # beta= inverse temperature parameter in softmax choice function
-  # lambda = learning rate (one per game?)
-  # data : participant and ai choice data.
-  # Returns Q-values per trial and predicts choice using softmax
-  beta <- par[1]
-  alpha <- par[2]
-  Q_vals_RPS = matrix(0.0,3)
-  names(Q_vals_RPS) <- c("R","P","S")
-  Q_vals_FWG = matrix(0.0,3)
-  names(Q_vals_FWG) <- c("F","W","G")
-  Q_vals_NUM = matrix(0.0,5)
-  names(Q_vals_NUM) <- c("1","2","3","4","5")
-
-  lik_hum <- matrix(0.0,nrow(data))
-
-  for(t in 1:nrow(data)) {
-    t_game <- data[t,"game"]
-    if(t_game == "numbers") nopts <- 5 else nopts <- 3
-    if(data[t,"round"] == 1) {
-      # first round is uniform prediction
-      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
-      lik_hum[t] <- 1/nopts
-    } else {
-      # Get reward and past human action
-      reward <- as.numeric(data[t-1,"score"])
-      h_act_prev <- as.character(data[t-1,"h_action"])
-      Q_vals[h_act_prev] <- Q_vals[[h_act_prev]] + as.numeric(alpha)*( reward - Q_vals[[h_act_prev]])
-
-      # cat(Q_vals,"\n")
-
-      # Assume human chooses action probabilistically using softmax on Q values
-      probs <- exp(Q_vals/beta)/sum(exp(Q_vals/beta))
-
-      # Get actual human action and compute likelihood
-      h_act <- as.character(data[t,"h_action"])
-      act_index <- match(h_act, names(Q_vals))
-      #cat(as.character(act_index))
-      lik_hum[t] <- probs[[act_index]]
-    }
-  }
-  if(return_value == "-2loglik") {
-    ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret) || is.nan(ret)) {
-      return(1e+300)
-    } else {
-      return(ret)
-    }
-  }
-  if(return_value == "likelihood_by_trial") return(lik_hum)
-
-}
-
-```
-
-## Q-learning fit
-```{r, cache=TRUE}
-QL_modelling <- list()
-for(id in unique(dat$human_id)) {
-  QL_modelling[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
-  QL_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
-}
-save(QL_modelling,file="QL_modelling.RData")
-
-```
-
-## First attempt : Q-Learning with state space consisting of last round play (deprecated) 
-```{r}
-
-# Q_learn_states <- function(par,data,return_value,gamma){
-#   # Par[1] -> beta= inverse temperature parameter in softmax choice function
-#   # Par[2] -> lambda = learning rate (one per game?)
-#   # data : participant and ai choice data.
-#   # return_value=c("-2loglik","likelihood_by_trial")
-#   # Gamma is discount factor for future rewards 
-#   # Returns Q-values per trial and predicts choice using softmax
-#   beta <- par[1]
-#   alpha <- par[2]
-# 
-#   #gamma <- 0.9 
-# 
-#   #Define matrix of state spaces for each game 
-#   G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
-#   states_RPS <- paste0(G1$Var1,G1$Var2)
-# 
-#   G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
-#   states_FWG <- paste0(G2$Var1,G2$Var2)
-# 
-#   G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-#   states_NUM <- paste0(G3$Var1,G3$Var2)
-#   
-#   Q_vals_RPS = matrix(-0.5,9,3)
-#   dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
-# 
-#   Q_vals_FWG = matrix(-0.5,9,3)
-#   dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
-#   
-#   Q_vals_NUM = matrix(-0.5,25,5)
-#   dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
-#  
-#   lik_hum <- matrix(0.0,nrow(data))
-# 
-#   for(t in 1:nrow(data)) {
-#     t_game <- data[t,"game"]
-#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
-#     
-#     if(data[t,"round"] == 1) {
-#       # first round is uniform prediction
-#       Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
-#       state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
-#       lik_hum[t] <- 1/nopts
-#       # Randomly select prev_state and actions for first round
-#       curr_state <- sample(state_vec, size = 1)
-#       h_act <- sample(colnames(Q_vals), size =1)
-#       ai_act <- sample(colnames(Q_vals), size =1)
-#       reward <- 0 
-#       
-#     } else {
-#       # Get past human action and associated reward 
-#       h_act <- as.character(data[t-1,"h_action"])
-#       ai_act <- as.character(data[t-1,"a_action"])
-#       reward <- as.numeric(data[t-1,"score"])
-#     }
-#     
-#     
-#     # cat(curr_state, " This is the previous state", "\n")
-#     new_state <- paste0(h_act,ai_act)
-#     # cat(new_state,"This is new state","\n")
-#     
-#     # Q_learning: update rule (time  = t-1)
-#     Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
-#     
-#     # Assume human chooses action probabilistically using softmax on Q values
-#     probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
-#     #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }
-#     
-#     # Get actual human action and compute likelihood
-#     h_act <- as.character(data[t,"h_action"])
-#     act_index <- match(h_act, colnames(Q_vals))
-#     lik_hum[t] <- probs[[act_index]]
-#       
-#     # Update state
-#     curr_state <- new_state 
-#     #}
-#   }
-#   if(return_value == "-2loglik") {
-#     ret <- -2*sum(log(lik_hum))
-#     if(is.infinite(ret) || is.nan(ret)) {
-#       return(1e+300)
-#     } else {
-#       return(ret)
-#     }
-#   }
-#   if(return_value == "likelihood_by_trial") return(lik_hum)
-#   
-# }
-
-```
-
-#Second attempt at QL algorithm with states: No guessing of initial states
-```{r}
-Q_learn_states <- function(par,data,return_value,gamma){
-  # Par[1] -> beta= inverse temperature parameter in softmax choice function
-  # Par[2] -> lambda = learning rate (one per game?)
-  # data : participant and ai choice data.
-  # return_value=c("-2loglik","likelihood_by_trial")
-  # Gamma is discount factor for future rewards 
-  # Returns Q-values per trial and predicts choice using softmax
-  beta <- par[[1]]
-  alpha <- par[[2]]
-
-  #Define matrix of state spaces for each game 
-  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
-  states_RPS <- paste0(G1$Var1,G1$Var2)
-
-  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
-  states_FWG <- paste0(G2$Var1,G2$Var2)
-
-  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-  states_NUM <- paste0(G3$Var1,G3$Var2)
-
-  Q_vals_RPS = matrix(-0.5,9,3)
-  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
-
-  Q_vals_FWG = matrix(-0.5,9,3)
-  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
-
-  Q_vals_NUM = matrix(-0.5,25,5)
-  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
-
-  lik_hum <- matrix(0.0,nrow(data))
-
-  for(t in 1:nrow(data)) {
-
-    t_game <- data[t,"game"]
-    if(t_game == "numbers") nopts <- 5 else nopts <- 3
-
-    if(data[t,"round"] == 1) {
-      # first round is uniform prediction
-      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
-      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
-      lik_hum[t] <- 1/nopts
-
-    } else {
-      # Get past human action and associated reward 
-      h_act_prev <- as.character(data[t-1,"h_action"])
-      ai_act_prev <- as.character(data[t-1,"a_action"])
-      curr_state <- paste0(h_act_prev,ai_act_prev)
-
-      h_act <- as.character(data[t,"h_action"])
-      ai_act <- as.character(data[t,"a_action"])
-      reward <- as.numeric(data[t,"score"])
-
-      new_state <- paste0(h_act,ai_act)
-
-      # Assume human chooses action probabilistically using softmax on Q values
-      probs <- exp(Q_vals[curr_state,]/beta)/sum(exp(Q_vals[curr_state,]/beta))
-
-      # Get actual human next action and compute likelihood
-      act_index <- match(h_act, colnames(Q_vals))
-      lik_hum[t] <- probs[[act_index]]
-
-       # Q_learning: update rule (time = t)
-      Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
-
-      # Update state
-      curr_state <- new_state
-
-    }
-
-  }
-  if(return_value == "-2loglik") {
-    ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret) || is.nan(ret)) {
-      return(1e+300)
-    } else {
-      return(ret)
-    }
-  }
-  if(return_value == "likelihood_by_trial") return(lik_hum)
-
-}
-
-```
-
-```{r}
-data34 <- subset(dat,human_id == "QSuzBXpbyRc370HsAACW")
-
-# Q_learn_states(c(5, 0.5),data34 ,return_value = "likelihood_by_trial",gamma = 0 )
-
-```
-
-## Fitting Q_learning with states
-```{r , cache =TRUE}
-# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
-# Q_learn_states(c(0.1,0.1), data, "-2loglik")
-
-QL_states_modelling <- list()
-for(id in unique(dat$human_id)) {
-  QL_states_modelling[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
-  # QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
-
-   QL_states_modelling[[id]] <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))
-}
-
-save(QL_states_modelling, file="QL_states_modelling.RData")
-
-# QL_states_gamma <- list()
-# for(id in unique(dat$human_id)) {
-#   QL_states_gamma[[id]] <- list()
-#   tdat <- subset(dat,human_id == id)
-#   QL_states_gamma[[id]] <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0.9, control=list(trace = FALSE,parallelType=1))
-# }
-# save(QL_states_gamma,file="QL_states_gamma.RData")
-
-```
-
-```{r}
-# OK, let's compare BICs and parameters for Gamma = 0 and Gamma = 0.9 (both for initial Q-values of -0.5)
-
-compare_QL_states <- data.frame()
-for(id in unique(dat$human_id)) {
-compare_QL_states  <- rbind(compare_QL_states ,
-                       data.frame(
-                         "id" = id,
-                         "condition" = dat[dat$human_id==id,"condition"][1],
-                         "Zero_Gamma_BIC" = QL_states_modelling[[id]]$optim$bestval + 2*log(150),
-                         "High_gamma_BIC" = QL_states_gamma[[id]]$optim$bestval + 2*log(150),
-                         "diff" = QL_states_modelling[[id]]$optim$bestval - QL_states_gamma[[id]]$optim$bestval
-                       ))
-}
-
-```
-#Notes: Q-Learning as done above is far from optimal.
-The reason is that most states are never visited during play ( anecdotal evidence, about 40-60% in RPS/FWG and 10-20% in NUM).
-This method needs a lot more rounds to start modelling players behavior correctly.
-
-## Parametric Experience Weighted Attraction model (Camerer & Ho 1997)
-```{r}
-EWA_par <- function(par,data,return_value){
-  # par: vector of parameters to the EWA model
-  # Data :choice data by trial for each participant
-  # Returns sum of loglikelihoods or likelihood per trial
-  phi <- par[1]
-  delta <- par[2]
-  rho <- par[3]
-  lambda <- par[4]
-
-  # Define attraction vectors for each game
-  A_RPS = matrix(0.0,3)
-  names(A_RPS) <- c("R","P","S")
-  A_FWG = matrix(0.0,3)
-  names(A_FWG) <- c("F","W","G")
-  A_NUM = matrix(0.0,5)
-  names(A_NUM) <- c("1","2","3","4","5")
-
-  # # Define reward matrices from the prospective of the row player (human in our case)
-  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
-
-  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
-
-  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
-  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-
-  # Initiate likelihood by trial vector
-  lik_hum <- matrix(0.0,nrow(data))
-
-  for(t in 1:nrow(data)) {
-    t_game <- data[t,"game"]
-    if(t_game == "numbers") nopts <- 5 else nopts <- 3
-    if(data[t,"round"] == 1) {
-      # first round is uniform prediction
-      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
-      reward <- switch(as.character(t_game),rps=reward_RPS,fwg = reward_FWG, numbers = reward_NUM)
-      lik_hum[t] <- 1/nopts
-      # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.
-      N <- 1
-
-    } else {
-      # Get reward and past human action
-      h_act_prev <- as.character(data[t-1,"h_action"])
-      a_act_prev <- as.character(data[t-1,"a_action"])
-      for (i in 1:length(Att)) {
-        action <- as.character(names(Att)[i])
-        # cat("this is current strat",action,"\n")
-        # cat("this is previous human action",h_act_prev,"\n")
-
-        # Attraction vector update rule
-        Att[[i]] <- (phi*N*Att[[i]]  + ( delta + (1- delta)*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (rho*N + 1)
-      }
-      #Update the value of N
-      N <- rho*N + 1
-
-      # Assume human chooses action probabilistically using softmax on Attraction values
-      probs <- exp(lambda*Att)/sum(exp(lambda*Att))
-
-      # Get actual human action and compute likelihood
-      h_act <- as.character(data[t,"h_action"])
-      act_index <- match(h_act, names(Att))
-      lik_hum[t] <- probs[[act_index]]
-    }
-  }
-
- if(return_value == "-2loglik") {
-    ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret) || is.nan(ret) ) {
-      return(1e+300)
-    } else {
-      return(ret)
-    }
-  }
-  if(return_value == "likelihood_by_trial") return(lik_hum)
-}
-```
-
-## Fitting Parametric EWA to data 
-```{r, cache =TRUE}
-
-EWA_modelling <- list()
-for(id in unique(dat$human_id)) {
-  EWA_modelling[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
-  # EWA_modelling[[id]] <- optim(c(0.5,0.5,0.5,0.5),fn=EWA_par,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.001,0.001,0.001), upper = c(1,0.99,0.99,1), method="L-BFGS-B")
-  EWA_modelling[[id]] <- DEoptim(fn=EWA_par,lower = c(0.01,0.01,0.01,0.01), upper = c(10,1,1,10), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))
-}
-
-save(EWA_modelling,file="EWA_modelling.RData")
-
-```
-
-##  Self-Tuning EWA (Camerer & Ho 2007) 
-```{r}
-
-EWA_self <- function(par,data,return_value){
-
-  lambda <- par[1]
-  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.
-
-  # Define attraction vectors for each game 
-  A_RPS = matrix(0.0,3)
-  names(A_RPS) <- c("R","P","S")
-  A_FWG = matrix(0.0,3)
-  names(A_FWG) <- c("F","W","G")
-  A_NUM = matrix(0.0,5)
-  names(A_NUM) <- c("1","2","3","4","5")
-
-  # # Define reward matrices from the prospective of the row player (human in our case)
-  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
-
-  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
-
-  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
-  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-
-  # Initiate likelihood by trial vector 
-  lik_hum <- matrix(0.0,nrow(data))
-
-  for(t in 1:nrow(data)) {
-    t_game <- data[t,"game"]
-    if(t_game == "numbers") nopts <- 5 else nopts <- 3
-    if(data[t,"round"] == 1) {
-      # first round is uniform prediction
-      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
-      reward <- switch(as.character(t_game),rps=reward_RPS,fwg = reward_FWG, numbers = reward_NUM)
-      game_data <- subset(data, game == t_game)
-      lik_hum[t] <- 1/nopts
-      N <- 1.0
-
-      R_t <- rep(0.0,nopts)
-      H_t <- R_t
-
-    } else {
-
-      indx <- data[t,"round"]
-      # Get reward and past human action
-      h_act_prev <- as.character(game_data[indx-1,"h_action"])
-      a_act_prev <- as.character(game_data[indx-1,"a_action"])
-
-      # Estimate phi(t)
-      R_t <- as.numeric(names(Att) == a_act_prev)
-      # cat("This is R(t)",R_t,"\n")
-
-      H_t <- (H_t*(indx-2) + R_t)/(indx-1)
-      # cat("this is H(t)",H_t,"\n")
-
-      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
-      # cat("This is Phit(t)",Phi_t,"\t")
-
-      # Estimate vector Delta(t)
-
-      delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
-      #cat("this is delta(t)",delta_t,"\n")
-
-      for (i in 1:length(Att)) {
-        action <- as.character(names(Att)[i])
-        # cat("this is current strat",action,"\n")
-        # cat("this is previous humna action",h_act_prev,"\n")
-
-        # Attraction vector update rule 
-        Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
-      }
-      #Update the value of N 
-      N <- Phi_t*N + 1
-      #cat(Att,'\n')
-
-      # Assume human chooses action probabilistically using softmax on Attraction values
-      probs <- exp(lambda*Att)/sum(exp(lambda*Att))
-
-      # Get actual human action and compute likelihood
-      h_act <- as.character(game_data[indx,"h_action"])
-      act_index <- match(h_act, names(Att))
-      lik_hum[t] <- probs[[act_index]]
-    }
-  }
-
- if(return_value == "-2loglik") {
-    ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret) || is.nan(ret)) {
-      return(1e+300)
-    } else {
-      return(ret)
-    }
-  }
-  if(return_value == "likelihood_by_trial") return(lik_hum)
-}
-
-```
-
-```{r}
-##Plotting self_tuning EWA likelihood function for lambda from 0 to 100 
-# 
-# lambdas <- seq(1,10,0.01)
-# count = 0.0
-# 
-# 
-# 
-# for(id in unique(dat$human_id)) {
-#   if (count <= 15) {
-#       tdat <- subset(dat,human_id == id)
-#       likelihoods <- sapply(lambdas, EWA_self, tdat, "-2loglik")
-#       plot(lambdas,likelihoods)
-#       count <- count + 1
-#   }
-# }
-
-```
-
-## Fitting Self-Tuning EWA to data 
-```{r, cache=TRUE}
-
-EWA_self_modelling <- list()
-for(id in unique(dat$human_id)) {
-  EWA_self_modelling[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
-#   EWA_self_modelling[[id]] <- optim(10.0,fn=EWA_self,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
-# }
-  EWA_self_modelling[[id]] <- DEoptim(fn=EWA_self, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
-}
-
-save(EWA_self_modelling,file="EWA_self_modelling.RData")
-
-```
-
-```{r}
-# cat(EWA_self_modelling[["38VxtUSv_h6RR5-tAAA2"]]$optim$bestmem)
-```
-
-##  First attempt : Self-Tuning EWA with prior round play as state (Camerer & Ho 2007) 
-```{r}
-# Initiates N(0) = 1 as in Camerer and Ho 1997 paper. 
-# 
-# EWA_states <- function(par,data,return_value){
-# 
-#   lambda <- par[1]
-# 
-#   #Define matrix of state spaces for each game 
-#   G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
-#   states_RPS <- paste0(G1$Var1,G1$Var2)
-# 
-#   G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
-#   states_FWG <- paste0(G2$Var1,G2$Var2)
-# 
-#   G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-#   states_NUM <- paste0(G3$Var1,G3$Var2)
-#   
-#   A_RPS = matrix(-0.5,9,3)
-#   dimnames(A_RPS) = list(states_RPS, c("R", "P", "S"))
-# 
-#   A_FWG = matrix(-0.5,9,3)
-#   dimnames(A_FWG) = list(states_FWG, c("F", "W", "G"))
-#   
-#   A_NUM = matrix(-0.5,25,5)
-#   dimnames(A_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
-# 
-#   
-#   # # Define reward matrices from the perspective of the row player (human in our case)
-#   reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-#   dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
-#   
-#   reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-#   dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
-#   
-#   reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
-#   dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-#   
-#   # Initiate likelihood by trial vector 
-#   lik_hum <- matrix(0.0,nrow(data))
-# 
-#   for(t in 1:nrow(data)) {
-#     t_game <- data[t,"game"]
-#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
-#     if(data[t,"round"] == 1) {
-#       Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
-#       state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, numbers = states_NUM)
-#       reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, numbers = reward_NUM)
-#       game_data <- subset(data, game == t_game)
-#       
-#       # first round is uniform prediction
-#       lik_hum[t] <- 1/nopts
-#       N <- 1.0
-# 
-#       R_t <- rep(0.0,nopts)
-#       H_t <- R_t
-#       
-#       # Randomly select prev_state and actions for first round
-#       curr_state <- sample(state_vec, size = 1)
-#       h_act_prev <- sample(colnames(Att), size =1)
-#       a_act_prev <- sample(colnames(Att), size =1)
-#       #reward <- 0 
-#       
-#     } else {
-#       
-#       indx <- data[t,"round"]
-#       state_indx <- match(curr_state,state_vec)
-#       #cat("this is the current state index", state_indx, "\n")
-#       
-#       # Get reward and past human action
-#       h_act_prev <- as.character(game_data[indx-1,"h_action"])
-#       a_act_prev <- as.character(game_data[indx-1,"a_action"])
-#       new_state <- paste0(h_act_prev,a_act_prev)
-# 
-#       # Estimate R(t) (recent history) then H(t) (history) then phi(t) (change detector)
-#       R_t <- as.numeric(colnames(Att) == a_act_prev)
-#       #cat("This is R(t)",R_t,"\n")
-#       
-#       H_t <- (H_t*(indx-2) + R_t)/(indx-1)
-#       #cat("this is H(t)",H_t,"\n")
-#       
-#       Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
-#       #cat("This is Phit(t)",Phi_t,"\t")
-#       
-#       # Estimate vector Delta(t)
-#       delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
-#       #cat("this is delta(t)",delta_t,"\n")
-#       
-#       for (i in 1:nopts) {
-#         action <- as.character(colnames(Att)[i])
-# 
-#         #cat("this is current indexed action",action,"\n")
-#         #cat("this is previous human action",h_act_prev,"\n")
-#         
-#         # Attraction vector update rule
-#         Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
-#       }
-#       
-#       #Update the value of N 
-#       N <- Phi_t*N + 1
-# 
-#       # Assume human chooses action probabilistically using softmax on Attraction values
-#       probs <- exp(lambda*Att[new_state,])/sum(exp(lambda*Att[new_state,]))
-#       
-#       # Get actual human action and compute likelihood
-#       h_act <- as.character(game_data[indx,"h_action"])
-#       act_index <- match(h_act, colnames(Att))
-#       lik_hum[t] <- probs[[act_index]]
-#       
-#       curr_state <- new_state
-#       
-#       # if (indx == 50) {
-#       #   cat("this is the attraction matrix at last round of", "\n")
-#       #   print(Att)
-#       # }
-#     }
-#   }
-#   
-#  if(return_value == "-2loglik") {
-#     ret <- -2*sum(log(lik_hum))
-#     if(is.infinite(ret) || is.nan(ret)) {
-#       return(1e+300)
-#     } else {
-#       return(ret)
-#     }
-#   }
-#   if(return_value == "likelihood_by_trial") return(lik_hum)
-# }
-
-```
-
-### Second attempt at ST_EWA with states and no initial guess of initial states. 
-```{r}
-ST_EWA_STATES <- function(par,data,return_value){
-
-  lambda <- par[1]
-
-  #Define matrix of state spaces for each game 
-  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
-  states_RPS <- paste0(G1$Var1,G1$Var2)
-
-  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
-  states_FWG <- paste0(G2$Var1,G2$Var2)
-
-  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-  states_NUM <- paste0(G3$Var1,G3$Var2)
-
-  A_RPS = matrix(-0.5,9,3)
-  dimnames(A_RPS) = list(states_RPS, c("R", "P", "S"))
-
-  A_FWG = matrix(-0.5,9,3)
-  dimnames(A_FWG) = list(states_FWG, c("F", "W", "G"))
-
-  A_NUM = matrix(-0.5,25,5)
-  dimnames(A_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
-
-  # # Define reward matrices from the perspective of the row player (human in our case)
-  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
-
-  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
-
-  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
-  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-
-  # Initiate likelihood by trial vector 
-  lik_hum <- matrix(0.0,nrow(data))
-
-   for(t in 1:nrow(data)) {
-    t_game <- data[t,"game"]
-    if(t_game == "numbers") nopts <- 5 else nopts <- 3
-
-    if(data[t,"round"] == 1) {
-      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
-      state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, numbers = states_NUM)
-      reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, numbers = reward_NUM)
-      game_data <- subset(data, game == t_game)
-
-      # first round is uniform prediction
-      lik_hum[t] <- 1/nopts
-      # Asumme N(0) = 1 for now...see discussion in paper
-      N <- 1.0
-      # initialize H_t by looking at first action 
-      # H_t <- rep(0.0,nopts)
-      a_act <- as.character(game_data[1,"a_action"])
-      H_t <- as.numeric(colnames(Att) == a_act)
-
-      # Rounds 2 to end 
-    } else {
-
-      indx <- data[t,"round"]
-
-      # Get reward and past human action
-      h_act_prev <- as.character(game_data[indx-1,"h_action"])
-      a_act_prev <- as.character(game_data[indx-1,"a_action"])
-      curr_state <- paste0(h_act_prev,a_act_prev)
-
-      h_act <- as.character(game_data[indx,"h_action"])
-      a_act <- as.character(game_data[indx,"a_action"])
-      new_state <- paste0(h_act,a_act)
-
-      # Assume human chooses action probabilistically using softmax on Attraction values
-      probs <- exp(lambda*Att[curr_state,])/sum(exp(lambda*Att[curr_state,]))
-
-      # Get actual human action and compute likelihood
-      act_index <- match(h_act, colnames(Att))
-      lik_hum[t] <- probs[[act_index]]
-
-      # Update rule:
-      # Estimate R(t) (recent history) then H(t) (history) then phi(t) (change detector)
-      R_t <- as.numeric(colnames(Att) == a_act)
-      #cat("This is R(t)",R_t,"\n")
-
-      H_t <- (H_t*(indx-1) + R_t)/(indx)
-      #cat("this is H(t)",H_t,"\n")
-
-      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
-      #cat("This is Phit(t)",Phi_t,"\t")
-
-      # Estimate vector Delta(t)
-      delta_t <- as.numeric(reward[,a_act] >= as.numeric(game_data[indx,"score"]))
-      #cat("this is delta(t)",delta_t,"\n")
-
-      # This is a vectorised ST_EWA update rule, easier to follow the loop below in comments
-      state_indx <- match(curr_state,state_vec)
-      Att[state_indx,] <- (Phi_t*N*Att[state_indx,]  + ( delta_t + (1- delta_t)*(colnames(Att) == h_act))*as.numeric(reward[colnames(Att),a_act])) / (Phi_t*N + 1)
-
-      ##############
-      # for (i in 1:nopts) {
-      #   action <- as.character(colnames(Att)[i])
-      #   state_indx <- match(curr_state,state_vec)
-      #   #cat("this is the current state index", state_indx, "\n")
-      # 
-      #   # Attraction vector update rule
-      #   Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act))*as.numeric(reward[action,a_act])) / (Phi_t*N + 1)
-      # 
-      # }
-      # 
-      #cat("this is the current Att vector", Att, "\n")
-      ###################
-
-      #Update the value of N 
-      N <- Phi_t*N + 1
-
-      #Update the state 
-      curr_state <- new_state 
-    }
-   }  
-  if(return_value == "-2loglik") {
-    ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret) || is.nan(ret)) {
-      return(1e+300)
-    } else {
-      return(ret)
-    }
-  }
-  if(return_value == "likelihood_by_trial") return(lik_hum)
-
-}
-
-```
-
-```{r}
-# data12 = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
-# ST_EWA_STATES(0.5, data12, "-2loglik")
-# optim(10.0,fn=ST_EWA_STATES,gr = NULL, data=data12,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
-
-```
-
-```{r, cache=TRUE}
-
-ST_EWA_STATES_modelling <- list()
-for(id in unique(dat$human_id)) {
-  ST_EWA_STATES_modelling[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
-#   ST_EWA_STATES_modelling[[id]] <- optim(10.0,fn=ST_EWA_STATES,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
-# }
-  ST_EWA_STATES_modelling[[id]] <- DEoptim(fn=ST_EWA_STATES, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
-}
-
-save(ST_EWA_STATES_modelling,file="ST_EWA_STATES_modelling.RData")
-
-```
-
-## What next?: Fitting models that explicitly take into account opponent strategy.
-LOLA?
-Won't work, it suffers from same issues as normal QL in that most states are not visited during game play.
-Influence model?
-Like belief lerning.
-it still has no sequential memory, still computes distribution on beliefs.
-We need to incorporate models that can mimic human memory by looking at history of play and leverage sequence prediction capabilities.
-
-### Model based model: learn transition probabilities to new states.
-Weigh the value of an action by the conditional probability of ending up in a future state times the value of the new state....
-once you take an action in current round, you can only end up in 3 states, with probabilities p, q and 1-p-q.
-You are learning these probabilities by updating priors (initial prior is dirichlet).
-```{r}
-MBM <- function(par,data,return_value,gamma){
-  # Par[1] -> beta= inverse temperature parameter in softmax choice function
-  # Par[2] -> lambda = learning rate (one per game?)
-  # data : participant and ai choice data.
-  # return_value=c("-2loglik","likelihood_by_trial")
-  # Gamma is discount factor for future rewards 
-  # Returns Q-values per trial and predicts choice using softmax
-  beta <- par[1]
-  alpha <- par[2]
-
-  #gamma <- 0.9
-
-  #Define matrix of state spaces for each game 
-  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
-  states_RPS <- paste0(G1$Var1,G1$Var2)
-
-  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
-  states_FWG <- paste0(G2$Var1,G2$Var2)
-
-  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-  states_NUM <- paste0(G3$Var1,G3$Var2)
-
-  # Matrices to store Q_values in each state 
-  Q_vals_RPS = matrix(-0.5,9,3)
-  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
-  Q_vals_FWG = matrix(-0.5,9,3)
-  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
-  Q_vals_NUM = matrix(-0.5,25,5)
-  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
-
-  # Transition Matrices 
-  Transit_RPS = matrix(1/9,9,9)
-  dimnames(Transit_RPS) = list(states_RPS, states_RPS)
-  Transit_FWG = matrix(1/9,9,9)
-  dimnames(Transit_FWG) = list(states_FWG, states_FWG)
-  Transit_NUM = matrix(1/25,25,25)
-  dimnames(Transit_NUM) = list(states_NUM, states_NUM)
-
-  lik_hum <- matrix(0.0,nrow(data))
-
-  for(t in 1:nrow(data)) {
-    t_game <- data[t,"game"]
-    if(t_game == "numbers") nopts <- 5 else nopts <- 3
-
-    if(data[t,"round"] == 1) {
-      # first round is uniform prediction
-      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
-      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
-      Transit <- switch(as.character(t_game),rps=Transit_RPS,fwg = Transit_FWG, numbers = Transit_NUM)
-      lik_hum[t] <- 1/nopts
-      # Randomly select prev_state and actions for first round
-      curr_state <- sample(state_vec, size = 1)
-      h_act <- sample(colnames(Q_vals), size =1)
-      ai_act <- sample(colnames(Q_vals), size =1)
-      reward <- 0
-
-    } else {
-      # Get past human action and associated reward 
-      h_act <- as.character(data[t-1,"h_action"])
-      ai_act <- as.character(data[t-1,"a_action"])
-      reward <- as.numeric(data[t-1,"score"])
-    }
-
-    # cat(curr_state, " This is the previous state", "\n")
-    new_state <- paste0(h_act,ai_act)
-    # cat(new_state,"This is new state","\n")
-
-    # Update Transit matrix ....first create hot vector = 1 if new state, 0 otherwise 
-    hot_vector <- state_vec == new_state
-
-    # Transit probs update: TD learning on transition matrix, learning rate fixed at 0.1
-    Transit[curr_state,] <- Transit[curr_state,] + 0.1* (hot_vector - Transit[curr_state,])
-    #cat(Transit[curr_state,], "\n")
-
-    # Update Q-values as current reward + a weighted (by trasnsit probs) average of future Q-values.
-    Q_Row_max <- apply(Q_vals, 1, max, na.rm = TRUE)
-    #cat(Transit[curr_state,] * Q_Row_max, "\n")
-    Q_vals[curr_state, h_act] <- reward +  gamma*( Transit[curr_state,] %*% Q_Row_max  )
-
-    # Assume human chooses action probabilistically using softmax on Q values
-    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
-    #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }
-
-    # Get actual human action and compute likelihood
-    h_act <- as.character(data[t,"h_action"])
-    act_index <- match(h_act, colnames(Q_vals))
-    lik_hum[t] <- probs[[act_index]]
-
-    # Update state
-    curr_state<- new_state 
-    #}
-  }
-  if(return_value == "-2loglik") {
-    ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret) || is.nan(ret)) {
-      return(1e+300)
-    } else {
-      return(ret)
-    }
-  }
-  if(return_value == "likelihood_by_trial") return(lik_hum)
-
-}
-
-```
-
-```{r, cache=TRUE}
-MBM_modelling <- list()
-for(id in unique(dat$human_id)) {
-  MBM_modelling[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
-  # MBM_modelling[[id]] <- optim(c(1,0.1),fn=QMBM,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
-
-   MBM_modelling[[id]] <- DEoptim(fn=MBM,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0.9, control=list(trace = FALSE,parallelType=1))
-}
-
-save(MBM_modelling, file="MBM_modelling.RData")
-
-```
-
-## Putting results together 
-```{r}
-load("QL_modelling.RData")
-load("QL_states_modelling.RData")
-load("EWA_modelling.RData")
-load("EWA_self_modelling.RData")
-load("MBM_modelling.RData")
-load("ST_EWA_STATES_modelling.RData")
-
-All_results <- data.frame()
-for(id in unique(dat$human_id)) {
-  All_results <- rbind(All_results,
-                       data.frame(
-                         "ID" = id,
-                         "condition" = dat[dat$human_id==id,"condition"][1],
-                         "Random_BIC" = -2*(100*log(1/3) + 50*log(1/5)),
-
-                         # Bayesian updating with/without transfer 
-                         # "Bayes_Tr_BIC" = exp1_Bayes_game_Tr[[id]]$optim$bestval+ 1*log(150),
-                         # "Bayes_No_Tr_BIC" = exp1_Bayes_no_Tr[[id]]$optim$bestval + 1*log(150),
-                         # # Theta is the parameter governing AI stochasticity. Truth is 0.9
-                         # "theta_transfer" = exp1_Bayes_game_Tr[[id]]$optim$bestmem[[1]],
-                         # "theta_no_transfer" = exp1_Bayes_no_Tr[[id]]$optim$bestmem[[1]],
-                         #
-
-                         # BCH with/without transfer (With Softmax) 
-                         "Bayes_Tr_BIC" = use_softmax_tr[[id]]$optim$bestval+ 2*log(150),
-                         "Bayes_No_Tr_BIC" = use_softmax_NT[[id]]$optim$bestval+ 2*log(150),
-
-                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
-                         "theta_transfer" = use_softmax_tr[[id]]$optim$bestmem[[1]],
-                         "lambda_transfer" = use_softmax_tr[[id]]$optim$bestmem[[2]],
-
-                         "theta_no_transfer" = use_softmax_NT[[id]]$optim$bestmem[[1]],
-                         "lambda_no_transfer" = use_softmax_NT[[id]]$optim$bestmem[[2]],
-
-                         # Q-Learning
-                         "QL_BIC" = QL_modelling[[id]]$value + 2*log(150),
-                         # beta ->  inverse temperature parameter in softmax choice function
-                         "QL_Beta" = QL_modelling[[id]]$par[1],
-                         # alpha -> learning rate in QL update
-                         "QL_alpha" = QL_modelling[[id]]$par[2],
-
-                         # Q-learning with last round states
-                         "QL_states_BIC" = QL_states_modelling[[id]]$optim$bestval + 2*log(150),
-                         # beta ->  inverse temperature parameter in softmax choice function
-                         "QL_states_Beta" = QL_states_modelling[[id]]$optim$bestmem[1],
-                         # alpha -> learning rate in QL update
-                         "QL_states_alpha" = QL_states_modelling[[id]]$optim$bestmem[2],
-
-                         # Parametric EWA
-                         # Parametric EWA BIC
-                         "EWA_BIC" = EWA_modelling[[id]]$optim$bestval + 4*log(150),
-                         "EWA_2LL" = EWA_modelling[[id]]$optim$bestval,
-                         # Phi is depreciation of past attractions
-                         "EWA_Phi" = EWA_modelling[[id]]$optim$bestmem[1],
-                         # Delta is weight of foregone payoffs vs actual payoffs
-                         "EWA_Delta" = EWA_modelling[[id]]$optim$bestmem[2],
-                         # Rho is depreciation of the experience measure N(t)
-                         "EWA_Rho" = EWA_modelling[[id]]$optim$bestmem[3],
-                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
-                         "EWA_Lambda" = EWA_modelling[[id]]$optim$bestmem[4],
-
-                         # Self-Tuning EWA (only 1 parameter)
-                          # Parametric EWA BIC
-                         # "EWA_self_2LL" = EWA_self_modelling[[id]]$optim$bestval,
-                         # "EWA_self_BIC" = EWA_self_modelling[[id]]$optim$bestval + 1*log(150),
-                         # #Lambda is a parameter of the softmax choice function (inverse Temperature)
-                         # "EWA_self_Lambda" = EWA_self_modelling[[id]]$optim$bestmem[1],
-
-                         # self_tuning EWA with states
-
-                         "ST_EWA_STATES_BIC" = ST_EWA_STATES_modelling[[id]]$optim$bestval + 1*log(150),
-                         "ST_EWA_STATES_Lambda" = ST_EWA_STATES_modelling[[id]]$optim$bestmem[1]
-
-                         ))
-}
-
-write.csv(All_results,file="exp1_all_results.csv",row.names = FALSE)
-
-```
-
-## Calucalting BIC weights
-```{r}
-
-comp_BICs <- All_results[c("ID","Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","ST_EWA_STATES_BIC")]
-
-exp1_BIC_weights <- comp_BICs["ID"]
-exp1_BIC_weights[,2:ncol(comp_BICs)] <- t(apply(comp_BICs[,2:ncol(comp_BICs)], 1, function(i) exp(-0.5*(i-min(i)) )))
-colnames(exp1_BIC_weights) <-colnames(comp_BICs)
-
-exp1_BIC_weights[,2:ncol(exp1_BIC_weights)] <- t(apply(exp1_BIC_weights[,-1], 1, function(i) round(i/sum(i),2)))
-
-```
-
-## Building table of best model per participant
-```{r}
-
-# Table_results <- table(All_results[, "condition"],c("random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","ST_EWA_STATES")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","ST_EWA_STATES_BIC")],1,which.min)])
-
-# We choose to omit the simple QL and EWA and opt to only include the ones with states as they are more relevant.
-
-Table_results <- table(All_results[, "condition"],c("random","ToM_BT","ToM_NBT", "QL_states","ST_EWA_STATES")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])
-
- write.csv(Table_results,file="Table_results.csv",row.names = TRUE)
- kable(Table_results)
- #barplot(Table_results)
-
-```
-##### Looks like most participants behavior can be explained by QL_states.
-Bayesian models best explain a few more behaviors, while the others are consistent with random behavior, and only 1 with QL and 1 with S_EWA.
-
-###### Question: Can we see evidence for transfer by looking at difference in BICS btwn Bayes with and without transfer.
-Let's test correlation between difference in BICs  with early rounds score (evidence for transfer)
-```{r}
-# id_results_tst <- subset(All_results, ID == "38VxtUSv_h6RR5-tAAA2")
-```
-
-```{r}
-
-exp1_model_comp <- data.frame()
-for(id in unique(dat$human_id)) {
-  tdat <- subset(dat,human_id == id)
-  tot_score <- sum(tdat$score)
-  tot_time <- sum(tdat$human_rt)
-  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
-  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
-  tr_score <- sum(early_dat$score)
-  id_results <- subset(All_results, ID == id)
-  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,min)
-
-  best_model <- c("random","ToM_Game_Tr","ToM_No_Tr", "QL_states","ST_EWA_STATES")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)]
-
-  exp1_model_comp <- rbind(exp1_model_comp,
-                       data.frame(
-                         "human_id" = id,
-                         "condition" = dat[dat$human_id==id,"condition"][1],
-                         "Early_game_score" = tr_score,
-                         "Total_score" = tot_score,
-                         "Best_model" = best_model,
-                         "Total_time" = sum(tdat$human_rt),
-                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
-                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
-
-                       ))
-}
-
-write.csv(exp1_model_comp,file = "exp1_model_comp.csv", row.names = FALSE)
-
-```
-
-### Correlate difference between BICs of Bayes transfer and no transfer with early rounds score (evidence for transfer) 
-```{r}
-
-cor.test(exp1_model_comp$TR_minus_NT_BIC,exp1_model_comp$Early_game_score, method="spearman")
-
-```
-
-### Correlation between early game score and difference between best model and random BIC
-```{r}
-cor.test(exp1_model_comp$Rand_minus_best_BIC, exp1_model_comp$Early_game_score, method="spearman")
-
-```
-### Histogram of best fitting models 
-```{r}
-barplot(table(exp1_model_comp$Best_model))
-```
-# Notes : There is positive and stat significant correlation between the difference between the best model BIC and random BIC on one hand, and the early scores from the target games ( FWG and NUM).
-What does this mean?
-It can be interpreted as a validation of early game score as good measure of how non-random play is....
-
-# More exploratory work......
-
-## Let's compare total scores of each participant by the model of best fit, see if Bayes+transfer total scores are higher than Bayes + no transfer
-
-```{r}
-
-# ggboxplot(exp1_model_comp, x = "model", y = "Total_score",
-#           color = "model", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-#           order = c("Random", "No Transfer", "Transfer"),
-#           ylab = "Total Score", xlab = "Model with best fit")
-
-exp1_model_comp$model <- recode(exp1_model_comp$Best_model,"Bayes Tr" = "Tranfer","Bayes No Tr" = "No Transfer", "QL_states" = "Q_Learning",  .default = "Random")
-model <- factor(exp1_model_comp$model)
-condition <- factor(exp1_model_comp$condition)
-
-# Total score by best predictive model 
-tapply(exp1_model_comp$Total_score, model, mean)
-
-# Compute the analysis of variance
-res.aov <- aov(Total_score ~ model + condition, data = exp1_model_comp)
-# Summary of the analysis
-summary(res.aov)
-TukeyHSD(res.aov)
-```
-
-## What if we remove from data people who play randomly and then compare Transfer v No Transfer? 
-```{r}
-
-Non_Random_Only <- subset(exp1_model_comp, model != "Random" )
-
-group_by(Non_Random_Only, model) %>%
-  summarise(
-    count = n(),
-    mean = mean(Early_game_score, na.rm = TRUE),
-    sd = sd(Early_game_score, na.rm = TRUE)
-  )
-
-res2 <- aov(Early_game_score ~ model, data = Non_Random_Only) 
-summary(res2)
-TukeyHSD(res2)
-```
-
-# Total time by best predictive model
-```{r}
-tapply(exp1_model_comp$Total_time, model, mean)
-
-time.aov <- aov(Total_time ~ model, data = exp1_model_comp)
-# Summary of the analysis
-summary(time.aov)
-TukeyHSD(time.aov)
-
-``` 
-#Early game scores for people best modelled with a Bayesian model with transfer are indeed higher than those best modelled without transfer but difference is not statistically significant.
-
-<!--chapter:end:comp_model_1019.Rmd-->
-
 ---
@@
 
+#### EARLY TRIALS - LEARNING TRANSFER !!!! 
 ```{r}
@@
 
+# set contrasts for factors in dataset for condition and game
+
+# setting contrast to compare early score between games across levels 
+contrasts(dat2_6$game.f) <- cbind(c(1,-1,0),c(0,-1,1))
+contrasts(dat2_6$condition) <- c(1,-1)
+
 # testing differences between early scores across games 
 library(afex)
-aov_early <- aov_car(early_score ~ game.f*condition + Error(human_id/(game.f)),data=dat2_6)
+aov_early <- aov_car(early_score ~ game.f*condition + Error(human_id/(game.f)),data=dat2_6,check_contrasts = FALSE)
 summary(aov_early)
+
+# Random intercecprt for participants
+lme_early <- mixed(early_score ~ game.f*condition + (1 | human_id),data=dat2_6,check_contrasts = FALSE, type = 3, method = "KR")
+summary(lme_early)
+
+lme_early
 
@@
 
-contrast(means.int2, list(G1vG2for26 = c(0,1,0,0,-1,0), G2vG3for26=c(0,0,1,0,0,-1)))
-
-# Plot interactions for early rouns, condition by game
+contrast(means.int2, list(L1vL2forG2 = c(0,1,0,0,-1,0), L1vL2forG3=c(0,0,1,0,0,-1)))
+                                 # levels      c(1,-1,0,1,-1,0)
+                                 # games       c(1,1,1,-1,-1,-1)
+
+# Interaction contrast
+
+contrast(means.int2, list(G1vG2byLevel = c(1,-1,0,-1,1,0), G2vG3byLevel6=c(0,1,-1,0,-1,1)))
+
+# Plot interactions for early rounds, condition by game
 
@@
 ```
-
-<!--chapter:end:exp1_clean_analysis.Rmd-->
-
----
-title: "Hidden Markov strategy model"
-author: "Maarten Speekenbrink"
-date: "25/08/2020"
-output: html_document
----
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-
-library(depmixS4)
-```
-
-```{r define-dummy-response}
-setClass("dummyResponse", contains="response")
-
-setGeneric("dummyResponse", function(y, pstart = NULL, fixed = NULL, ...) standardGeneric("dummyResponse"))
-
-setMethod("dummyResponse", 
-    signature(y="ANY"), 
-    function(y,pstart=NULL,fixed=NULL, ...) {
-      y <- matrix(y,length(y))
-  		x <- matrix(1)
-  		parameters <- list()
-  		npar <- 0
-      mod <- new("dummyResponse",parameters=parameters,fixed=logical(0),x=x,y=y,npar=npar)
-      mod
-	}
-)
-
-setMethod("show","dummyResponse",
-    function(object) {
-        cat("Dummy for fixed likelihood Model \n")
-    }
-)
-
-setMethod("dens","dummyResponse",
-  function(object,log=FALSE) {
-   if(log) log(as.numeric(object@y)) else as.numeric(object@y)
-  }
-)
-
-setMethod("getpars","dummyResponse",
-    function(object,which="pars",...) {
-        switch(which,
-            "pars" = {
-                pars <- numeric(0)
-            },
-            "fixed" = {
-                pars <- logical(0)
-            }
-        )
-        return(pars)
-    }
-)
-
-setMethod("setpars","dummyResponse",
-    function(object, values, which="pars", ...) {
-        npar <- npar(object)
-        if(length(values)!=npar) stop("length of 'values' must be",npar)
-        # determine whether parameters or fixed constraints are being set
-		nms <- ""
-		switch(which,
-		  "pars"= {
-		      },
-		  "fixed" = {
-		    }
-		  )
-      names(object@parameters) <- nms
-      return(object)
-    }
-)
-
-setMethod("fit","dummyResponse",
-    function(object,w) {
-		  return(object)
-	}
-)
-
-setMethod("predict","dummyResponse", 
-    function(object) {
-        ret <- object@y
-        return(ret)
-    }
-)
-```
-
-```{r}
-# we need to have "dat" available and lik_by_trial
-QLS_lik <- lik_by_trial$QLS_lik
-QLS_lik[which(QLS_lik == 0)] <- .001
-QLS_lik[is.na(QLS_lik)] <- .33 # this is a hack; there shouldn't be any missing values
-Bayes_NT_lik <- lik_by_trial$Bayes_NT_lik
-Bayes_Tr_lik <- lik_by_trial$Bayes_Tr_lik
-
-nsubject <- length(unique(dat$human_id)) # number of participants
-ngame <- 3 # number of games
-ntrial <- c(50,50,50) # numer of trials in each game
-
-rModels <- list(
-  list(
-	  dummyResponse(QLS_lik)
-	),
-	list(
-		dummyResponse(Bayes_NT_lik)
-	),
-  list(
-    dummyResponse(Bayes_Tr_lik)
-  )
-)
-
-trstart <- matrix(c(0.8,0.1,0.1,0.1,0.8,0.1,.1,.1,.8),ncol=3)
-transition <- list()
-transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
-transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
-transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
-
-instart <- c(1/3,1/3,1/3)
-inMod <- transInit(~1,nstates=3,pstart=instart,family=multinomial("identity"),data=data.frame(rep(1,nsubject*ngame)))
-
-mod <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
-
-fmod <- fit(mod, emcontrol=em.control(random.start=FALSE))
-
-# No switching. Force off diagonal initial elements of transtion matrix to 0
-trstart <- matrix(c(1,0,0,0,1,0,0,0,1),ncol=3)
-transition <- list()
-transition[[1]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[1,],family=multinomial("identity"))
-transition[[2]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[2,],family=multinomial("identity"))
-transition[[3]] <- transInit(~1,nstates=3,data=data.frame(1),pstart=trstart[3,],family=multinomial("identity"))
-
-mod_noswitch <- makeDepmix(response=rModels,transition=transition,prior=inMod,ntimes=rep(ntrial,nsubject))
-
-fmod_noswitch <- fit(mod_noswitch, emcontrol=em.control(random.start=FALSE))
-
-# p-value for comparison between a model with strategy switches and one without:
-
-1-pchisq(-2*as.numeric(logLik(fmod_noswitch)) - (-2*as.numeric(logLik(fmod))),df=6)
-
-```
-
-<!--chapter:end:exp1_hmm_strategies.Rmd-->
-
----
-title: "exp1_lik_by_trial"
-output: html_document
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-
-library(dplyr)
-library(ggplot2)
-```
-
-```{r}
-# Get Data for experiment 1, remove unecessary columns
-
-dat <- read.csv("data20180719.csv")
-#####
-# dat <- subset(dat, human_id == "38VxtUSv_h6RR5-tAAA2")
-####
-
-optim_results <- read.csv("exp1_all_results.csv")
-
-```
-
-```{r}
-
-#preparing data for functions to claculate likelihood
-
-#Prepping data for Bayesian code
-dat <- as_tibble(dat) %>% group_by(human_id,game)
-dat <- dat %>%
-  mutate(ai_action_prev = lag(ai_action,1), human_action_prev = lag(human_action,1))
-
-## level 0 predictions
-dat <- dat %>% mutate(pred_a1_level0 = case_when(
-  game == "rps" & ai_action_prev == "rock" ~ 1,
-  game == "fwg" & ai_action_prev == "fire" ~ 1,
-  game == "numbers" & ai_action_prev == "one" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a2_level0 = case_when(
-  game == "rps" & ai_action_prev == "paper" ~ 1,
-  game == "fwg" & ai_action_prev == "water" ~ 1,
-  game == "numbers" & ai_action_prev == "two" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a3_level0 = case_when(
-  game == "rps" & ai_action_prev == "scissors" ~ 1,
-  game == "fwg" & ai_action_prev == "grass" ~ 1,
-  game == "numbers" & ai_action_prev == "three" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a4_level0 = case_when(
-  game == "numbers" & ai_action_prev == "four" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-dat <- dat %>% mutate(pred_a5_level0 = case_when(
-  game == "numbers" & ai_action_prev == "five" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-
-## level 1 predictions
-dat <- dat %>% mutate(pred_a1_level1 = case_when(
-  game == "rps" & human_action_prev == "scissors" ~ 1,
-  game == "fwg" & human_action_prev == "grass" ~ 1,
-  game == "numbers" & human_action_prev == "five" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a2_level1 = case_when(
-  game == "rps" & human_action_prev == "rock" ~ 1,
-  game == "fwg" & human_action_prev == "fire" ~ 1,
-  game == "numbers" & human_action_prev == "one" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a3_level1 = case_when(
-  game == "rps" & human_action_prev == "paper" ~ 1,
-  game == "fwg" & human_action_prev == "water" ~ 1,
-  game == "numbers" & ai_action_prev == "two" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a4_level1 = case_when(
-  game == "numbers" & ai_action_prev == "three" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-dat <- dat %>% mutate(pred_a5_level1 = case_when(
-  game == "numbers" & ai_action_prev == "four" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-
-## level 2 predictions
-dat <- dat %>% mutate(pred_a1_level2 = case_when(
-  game == "rps" & ai_action_prev == "paper" ~ 1,
-  game == "fwg" & ai_action_prev == "water" ~ 1,
-  game == "numbers" & ai_action_prev == "four" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a2_level2 = case_when(
-  game == "rps" & ai_action_prev == "scissors" ~ 1,
-  game == "fwg" & ai_action_prev == "grass" ~ 1,
-  game == "numbers" & ai_action_prev == "five" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a3_level2 = case_when(
-  game == "rps" & ai_action_prev == "rock" ~ 1,
-  game == "fwg" & ai_action_prev == "fire" ~ 1,
-  game == "numbers" & ai_action_prev == "one" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  is.na(ai_action_prev) ~ 1/3,
-  !is.na(ai_action_prev) ~ 0))
-dat <- dat %>% mutate(pred_a4_level2 = case_when(
-  game == "numbers" & ai_action_prev == "two" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-dat <- dat %>% mutate(pred_a5_level2 = case_when(
-  game == "numbers" & ai_action_prev == "three" ~ 1,
-  game == "numbers" & is.na(ai_action_prev) ~ 1/5,
-  TRUE ~ 0))
-
-dat$ai_action_num <- recode(dat$ai_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "one" = 1, "two" = 2, "three" = 3, "four" = 4 , "five" = 5)
-dat$human_action_num <- recode(dat$human_action,"rock" = 1, "paper" = 2, "scissors" = 3, "fire" = 1, "water" = 2, "grass" = 3, "one" = 1, "two" = 2, "three" = 3, "four" = 4 , "five" = 5)
-
-# transform 'winner' variable in numeric score
-dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
-# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
-dat$block <- as.numeric(cut(dat$round,2))
-
-# recode actions to make them equal to the codes in these files
-dat$h_action <- recode(dat$human_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
-dat$a_action <- recode(dat$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
-
-```
-
-```{r}
-dat <-as.data.frame(dat)
-exp1_lik_by_trial <- data.frame()
-
-# dat%>% group_by(human_id) %>%
-#   mutate(pars_QLS = as.vector(optim_results%>% dplyr::select(QL_states_Beta,QL_states_alpha))) %>%
-#   mutate(QLS_lik = Q_learn_states(pars_QLS[1,] ,tdat,"likelihood_by_trial",gamma = 0))
-
-for(id in unique(dat$human_id)) {
-
-  tdat <- dat %>% subset(human_id == id)
-
-  # QLS likelihoods 
-  pars_QLS <- as.vector(filter(optim_results, ID == id)%>% dplyr::select(QL_states_Beta,QL_states_alpha))
-  tdat$QLS_lik <- Q_learn_states(pars_QLS ,tdat,"likelihood_by_trial",gamma = 0)
-
-  #Bayes model no transfer likelihoods
-  theta_NT <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_no_transfer))
-  tdat$Bayes_NT_lik <- exp1_Bayes_model_LL(theta_NT ,data = tdat, generalize = "no", "likelihood_by_trial")
-
-  # Bayes model with Transfer likelihood
-  theta_Tr <- unlist(filter(optim_results, ID == id)%>% dplyr::select(theta_transfer))
-  tdat$Bayes_Tr_lik <- exp1_Bayes_model_LL(theta_Tr ,data = tdat, generalize = "game", "likelihood_by_trial")
-
-  exp1_lik_by_trial <- dplyr::bind_rows(exp1_lik_by_trial,tdat)
-
-  # 
-  # exp1_lik_by_trial <- rbind(exp1_lik_by_trial,
-  #                       data.frame(
-  #                         "human_id" = id,
-  #                         "condition" = dat$condition,
-  #                         "game" = dat$game,
-  #                         "round" = dat$round,
-  #                         "QLS_lik" = QLS_lik,
-  #                         "Bayes_NT_lik" = Bayes_NT_lik,
-  #                         "Bayes_Tr_lik" = Bayes_Tr_lik
-  #                       ))
-  #cat(as.character(Bayes_Tr_lik[c(1,51,101)]))
-}
-
-write.csv(exp1_lik_by_trial,file="exp1_lik_by_trial.csv",row.names = FALSE)
-
-```
-
-```{r}
-
-summary(exp1_lik_by_trial$QLS_lik == 1.0 )
-summary(exp1_lik_by_trial$QLS_lik == 0.0 )
-summary(is.na(exp1_lik_by_trial$QLS_lik))
-
-```
-
-```{r}
-
-mean_lik <- exp1_lik_by_trial %>%
-  select(human_id,condition,game, round,QLS_lik,Bayes_NT_lik,Bayes_Tr_lik) %>%
-  group_by(game, condition, round)  %>%
-  dplyr::summarise(mean_QLS_lik = mean(QLS_lik, na.rm = TRUE),
-            mean_NT_lik = mean(Bayes_NT_lik, na.rm = TRUE),
-            mean_Tr_lik = mean(Bayes_Tr_lik, na.rm = TRUE))
-
-data_long <- tidyr::gather(mean_lik, strategy, probability, mean_QLS_lik:mean_Tr_lik, factor_key=TRUE)
-
-# make sure the different games are ordered in the way they were played
-data_long$game <- factor(data_long$game,levels=c("rps","fwg","numbers"))
-ggplot(data_long,aes(x=round,y=probability,colour=strategy)) + geom_line() + facet_grid(game~condition)
-
-```
-
-<!--chapter:end:exp1_lik_by_trial.Rmd-->
-
----
-title: "Simulation_EWA"
-output: html_document
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
-```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
-
-### Parameter and model recovery Q-Learning with past round as state
-
-## Build function that will simulate a QL_states player given parameters alpha and beta, and generate actions for 50 rounds
-## of each game. 
-```{r}
-gen_data_QL_states <- function(beta, alpha, num_rounds, gamma) {
-
-  games <- c("rps","fwg","numbers")
-  condition <- sample(c("level1","level2"),1)
-  data <- data.frame()
-
-  #Define matrix of state spaces for each game 
-  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
-  states_RPS <- paste0(G1$Var1,G1$Var2)
-
-  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
-  states_FWG <- paste0(G2$Var1,G2$Var2)
-
-  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-  states_NUM <- paste0(G3$Var1,G3$Var2)
-
-  # Initialize Matrix of Q-values 
-  Q_vals_RPS = matrix(-0.5,9,3)
-  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
-
-  Q_vals_FWG = matrix(-0.5,9,3)
-  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
-
-  Q_vals_NUM = matrix(-0.5,25,5)
-  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
-
-  # Build tables that give reward for human player(Row) vs ai player(column) actions. 
-  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
-
-  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
-
-  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
-  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-
-   for (t_game in games){
-      # Initiate dataframe
-      game_data <- setNames(data.frame(matrix(ncol = 6, nrow = num_rounds)), c("condition","game", "round", "h_action","a_action","score"))
-
-      # Initialize attraction vector, rewards + randomly select first actions
-      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
-      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
-      game_actions <- switch(as.character(t_game),rps=c("R", "P", "S"),fwg = c("F", "W", "G"), numbers = c("1", "2", "3", "4", "5"))
-      reward <- switch(as.character(t_game), rps=reward_RPS, fwg=reward_FWG, numbers=reward_NUM)
-      pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)
-
-      for(t in 1:num_rounds) {
-        if(t_game == "numbers") nopts <- 5 else nopts <- 3
-        game_data[t,"game"]<- t_game
-        game_data[t,"round"] <- t
-        game_data[t,"condition"] <- condition
-
-        if(t == 1) {
-          # Initialize previous state randomly. 
-          prev_state  <- sample(state_vec, size = 1)
-          # Sample huamn and ai actions in first round randomly 
-          h_act <- as.character(sample(game_actions, 1 ))
-          ai_act  <- as.character(sample(game_actions, 1 ))
-          # Get reward from first round. 
-          R <- reward[h_act, ai_act]
-
-          #Fill in table 
-          game_data[t,"h_action"] <- h_act
-          game_data[t,"a_action"] <- ai_act 
-          game_data[t,"score"] <- R
-
-        } else {
-          h_act<- as.character(game_data[t-1,"h_action"])
-          ai_act <- as.character(game_data[t-1,"a_action"])
-          R <- as.numeric(game_data[t-1,"score"])
-
-        }
-
-        # cat("round", t, "\n")
-        # cat(prev_state, " This is the previous state", "\n")
-        # cat("observed human action",h_act, "\n")
-        # cat("observed ai action",ai_act, "\n")
-
-        ###### New state is the state we get to after human plays h_act and ai plays  ai_act 
-        new_state <- paste0(h_act,ai_act)
-        ######
-        # cat(new_state,"This is new state","\n")
-        # cat("this is alpha",alpha,"\n")
-
-        # Q_learning: update rule
-        # cat("this is the Q vals",Q_vals[prev_state, h_act],"\n")
-        # cat("max Q_vals",max(Q_vals[new_state,]),"\n")
-        # cat("This is the reward", R ,"\n")
-
-        Q_vals[prev_state, h_act] <- Q_vals[prev_state, h_act] + alpha*( R + gamma*max(Q_vals[new_state,]) - Q_vals[prev_state, h_act])
-        probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
-
-        # Select human action with softmax
-        game_data[t,"h_action"] <- sample(game_actions, size=1,prob=probs)
-
-        # Update state
-        prev_state <- new_state
-
-         # Simulate opponent action and get score 
-        game_data[t,"a_action"] <- as.character(filter(pred_file_opp,human_previous == h_act & computer_previous == ai_act)[condition][1,])
-        # Calculate score 
-        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]
-
-      }# End for loop over rounds
-      data <- rbind(data,game_data)
-  }
-  # end of game for loop
-  return(data)
-
-}
-
-# QL_dta <- gen_data_QL_states(5,0.5, num_rounds = 5, gamma = 0.9)
-
-```
-
-# Function to fit various models to simulated QL learner data and get table of results.
-```{r}
-
-fit_models <- function(tdat,num_rounds =50) {
-
-  optim_S_EWA  <- DEoptim(fn=EWA_self, lower = 0.0, upper = 10.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
-
-  optim_EWA    <- DEoptim(fn=EWA_par,lower = c(0,0,0,0), upper = c(20,1,1,20), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))
-
-  #optim_QL     <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
-
-  optim_QL_states <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))
-
-  optim_NB     <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-
-  dataframe <-  data.frame(
-
-  # Get condition
-   "condition"  = as.character(tdat$condition[1]),
-
-  # Get best fit parameters and -2 Log Likelihoods for all models
-
-  # Self-tuning EWA 
-   "S_EWA_infrd_lambda" = optim_S_EWA$optim$bestmem[1],
-   "S_EWA_2LL"          = optim_S_EWA$optim$bestval,
-
-  #Parametric EWA
-    "EWA_infrd_phi"    = optim_EWA$optim$bestmem[1],
-    "EWA_infrd_delta"  = optim_EWA$optim$bestmem[2],
-    "EWA_infrd_rho"    = optim_EWA$optim$bestmem[3],
-    "EWA_infrd_lambda" = optim_EWA$optim$bestmem[4],
-    "EWA_2LL"          = optim_EWA$optim$bestval,
-
-  # Q-Learning with state as prev round
-    "QL_states_infrd_beta"   = optim_QL_states$optim$bestmem[1],
-    "QL_states_infrd_alpha"  = optim_QL_states$optim$bestmem[2],
-    "QL_states_2LL"          = optim_QL_states$optim$bestval,
-
-  # Naive Bayes (nopts-arm bandit with prior vec transfered across games)
-    "NB_infrd_theta" = optim_NB$par[1],
-    "NB_infrd_eps"   = optim_NB$par[2],
-    "NB_2LL"         = optim_NB$value,
-
-  # Random
-   "Random_2LL"     = -2*(2*num_rounds*log(1/3) + num_rounds*log(1/5))
-
-  )
-
-  return(dataframe)
-
-}
-
-sim_results <- function(beta,alpha,num_rounds,gamma) {
-  #Generate simulated data using Q_learning with previous round as state
-  tdat = gen_data_QL_states(beta,alpha, num_rounds, gamma)
-  # Fit various models to generated data 
-  df <- fit_models(tdat)
-  df$alpha <- alpha
-  df$beta <- beta
-  return(df)
-}
-
-```
-
-## Run simulation to generate datasets and return results of model fits 
-```{r}
-
-betas = runif(100,0,10)
-alphas = runif(100,0,1)
-
-pars <- as.array(mapply(c,betas, alphas, SIMPLIFY = FALSE ))
-
-list_of_dataframes <- mapply(FUN = sim_results, betas, alphas,num_rounds = 50.0, gamma = 0.0, SIMPLIFY = FALSE)
-
-QL_states_mod_recovery <- bind_rows(list_of_dataframes, .id = "column_label")
-
-save(QL_states_mod_recovery,file="QL_states_mod_recovery.RData")
-
-```
-
-## Plot infered vs real params, summarise model fitting results and return table of best fitting models
-```{r}
-# PLot real vs infered QL_states parameters
-plot(QL_states_mod_recovery$alpha,QL_states_mod_recovery$QL_states_infrd_alpha, xlab = "True alpha", ylab = " Infered alpha")
-plot(QL_states_mod_recovery$beta,QL_states_mod_recovery$QL_states_infrd_beta, xlab = "True beta", ylab = " Infered beta")
-
-# Evaluate the correlation between real and infered alphas/lambdas and test it for significance
-cor.test(QL_states_mod_recovery$alpha,QL_states_mod_recovery$QL_states_infrd_alpha, method= "spearman")
-cor.test(QL_states_mod_recovery$beta,QL_states_mod_recovery$QL_states_infrd_beta, method= "spearman")
-
-# Model recovery: create a table with best fitting models by condition
-QL_states_model_recov <- table(QL_states_mod_recovery[, "condition"],c("random","N_Bayes","QL_states","EWA","S_EWA")[apply(QL_states_mod_recovery[,c("Random_2LL","NB_2LL","QL_states_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])
-
- write.csv(QL_states_model_recov,file="QL_states_model_recov.csv",row.names = TRUE)
- kable(QL_states_model_recov)
-
-```
-
-## What if we increase num rounds to 200, does that improve model recovery? 
-```{r}
-betas = runif(100,0,10)
-alphas = runif(100,0,1)
-
-pars <- as.array(mapply(c,betas, alphas, SIMPLIFY = FALSE ))
-
-list_of_dataframes200 <- mapply(FUN = sim_results, betas, alphas,num_rounds = 200.0, gamma = 0.0, SIMPLIFY = FALSE)
-
-QL_states_recov_200 <- bind_rows(list_of_dataframes200, .id = "column_label")
-
-save(QL_states_recov_200,file="QL_states_recov_200.RData")
-
-# PLot real vs infered QL_states parameters
-plot(QL_states_recov_200$alpha,QL_states_recov_200$QL_states_infrd_alpha, xlab = "True alpha", ylab = " Infered alpha")
-plot(QL_states_recov_200$beta,QL_states_recov_200$QL_states_infrd_beta, xlab = "True beta", ylab = " Infered beta")
-
-# Evaluate the correlation between real and infered alphas/lambdas and test it for significance
-cor.test(QL_states_recov_200$alpha,QL_states_recov_200$QL_states_infrd_alpha, method= "spearman")
-cor.test(QL_states_recov_200$beta,QL_states_recov_200$QL_states_infrd_beta, method= "spearman")
-
-# Model recovery: create a table with best fitting models by condition
-QL_recov200_tab <- table(QL_states_recov_200[, "condition"],c("random","N_Bayes","QL_states","EWA","S_EWA")[apply(QL_states_recov_200[,c("Random_2LL","NB_2LL","QL_states_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])
-
- write.csv(QL_recov200_tab,file="QL_recov200_tab",row.names = TRUE)
- kable(QL_recov200_tab)
-```
-
-### Model and parameter recovery for Self Tuning EWA model
-
-## Build function that will simulate a self tuning EWA player given parameter Lambda, and generate actions for 50 rounds
-# of each game. 
-```{r}
-
-# NOTE : haven't introduced noise in either human or computer actions.
-
-gen_data_SEWA <- function(par,num_rounds){
-
-  lambda <- par[1]
-  games <- c("rps","fwg","numbers")
-  condition <- sample(c("level1","level2"),1)
-  data <- data.frame()
-
-  # Define attraction vectors for each game 
-  A_RPS = matrix(0.0,3)
-  names(A_RPS) <- c("R","P","S")
-  A_FWG = matrix(0.0,3)
-  names(A_FWG) <- c("F","W","G")
-  A_NUM = matrix(0.0,5)
-  names(A_NUM) <- c("1","2","3","4","5")
-
-  # # Define reward matrices from the prospective of the row player (human in our case)
-  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
-
-  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
-
-  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
-  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-
-  for (t_game in games){
-      # Initiate dataframe
-      game_data <- setNames(data.frame(matrix(ncol = 6, nrow = num_rounds)), c("condition","game", "round", "h_action","a_action","score"))
-      # Initialize attraction vector, rewards + randomly select first actions
-      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
-      game_actions <- names(Att)
-      reward <- switch(as.character(t_game), rps=reward_RPS, fwg=reward_FWG, numbers=reward_NUM)
-      pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)
-
-    for(t in 1:num_rounds) {
-      if(t_game == "numbers") nopts <- 5 else nopts <- 3
-      game_data[t,"game"]<- t_game
-      game_data[t,"round"] <- t
-      game_data[t,"condition"] <- condition
-
-      if(t == 1) {
-
-        game_data[t,"h_action"] <- as.character(sample(game_actions, 1 ))
-        game_data[t,"a_action"] <- as.character(sample(game_actions, 1 ))
-        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]
-        lik_hum <- c(1/nopts)
-        N <- 1.0
-        R_t <- rep(0.0,nopts)
-        H_t <- R_t
-
-      } else {
-
-        # Get reward and past human action
-        h_act_prev <- as.character(game_data[t-1,"h_action"])
-        a_act_prev <- as.character(game_data[t-1,"a_action"])
-
-        # Estimate phi(t)
-        R_t <- as.numeric(game_actions == a_act_prev)
-        # cat("This is R(t)",R_t,"\n")
-
-        H_t <- (H_t*(t-2) + R_t)/(t-1)
-        # cat("this is H(t)",H_t,"\n")
-
-        Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
-        # cat("This is Phit(t)",Phi_t,"\t")
-
-        # Estimate vector Delta(t)
-        delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[t-1,"score"]))
-        #cat("this is delta(t)",delta_t,"\n")
-
-        for (i in 1:length(Att)) {
-          action <- as.character(game_actions[i])
-          # Attraction vector update rule 
-          Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
-        }
-        #Update the value of N 
-        N <- Phi_t*N + 1
-        #cat(Att,'\n')
-
-        # Assume human chooses action probabilistically using softmax on Attraction values
-        probs <- exp(lambda*Att)/sum(exp(lambda*Att))
-
-        # Get actual human action and compute likelihood
-        game_data[t,"h_action"] <- sample(game_actions, size=1,prob=probs)
-        act_index <- match(game_data[t,"h_action"], game_actions)
-        lik_hum[t] <- probs[[act_index]]
-
-        # Simulate opponent action and get score 
-        game_data[t,"a_action"] <- as.character(filter(pred_file_opp,human_previous == as.character(game_data[t-1,"h_action"]) & computer_previous == as.character(game_data[t-1,"a_action"]))[condition][1,])
-        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]
-
-      }
-
-    }# End for loop over rounds
-    data <- rbind(data,game_data)
-
-  }# end of game for loop
-  return(data)
-
-}
-
-```
-
-## Generate 100 datasets using S_EWA agent, one for each lambda and fit the 4 models to it : NB, QL, EWA and S_EWA 
-```{r}
-## Generate N lambdas in chosen interval, get the corresponding datasets of actions and scores, use Self_EWA to infer Lambda from these datasets. 
-EWA_self_simulation <- data.frame()
-lambdas = runif(100, 0, 10)
-num_rounds <- 50 
-count <- 1
-
-for(lambda in lambdas) {
-
-  EWA_self_simulation[count,"real_lambda"] <- lambda
-  tdat <- gen_data_SEWA(par = lambda, num_rounds)
-
-  # Fit various models to generated data (from S_EWA type player)
-  optim_S_EWA  <- DEoptim(fn = EWA_self, lower = 0.0, upper = 10.0, data= tdat, "-2loglik", control = list(trace = FALSE,parallelType =1))
-
-  optim_EWA    <- DEoptim(fn = EWA_par,lower = c(0,0,0,0), upper = c(20,1,1,20), data=tdat,"-2loglik",control= list(trace = FALSE,parallelType=1))
-
-  # optim_QL     <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
-
-  optim_QL_states <- DEoptim(fn = Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))
-
-  optim_NB     <- optim(c(0.1,0.1),fn=naive_bayes, gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-
-  # Get condition
-  EWA_self_simulation[count, "condition"]  <- as.character(tdat$condition[1])
-
-  # Get best fit parameters and -2 Log Likelihoods for all models
-
-  # Self-tuning EWA 
-  EWA_self_simulation[count, "S_EWA_infrd_lambda"] <- optim_S_EWA$optim$bestmem[1]
-  EWA_self_simulation[count, "S_EWA_2LL"]          <- optim_S_EWA$optim$bestval
-
-  #Parametric EWA
-  EWA_self_simulation[count, "EWA_infrd_phi"]    <- optim_EWA$optim$bestmem[1]
-  EWA_self_simulation[count, "EWA_infrd_delta"]  <- optim_EWA$optim$bestmem[2]
-  EWA_self_simulation[count, "EWA_infrd_rho"]    <- optim_EWA$optim$bestmem[3]
-  EWA_self_simulation[count, "EWA_infrd_lambda"] <- optim_EWA$optim$bestmem[4]
-  EWA_self_simulation[count, "EWA_2LL"]          <- optim_EWA$optim$bestval
-
-  # Q-Learning with previous round as state
-  EWA_self_simulation[count, "QL_infrd_beta"]   <- optim_QL_states$optim$bestmem[1]
-  EWA_self_simulation[count, "QL_infrd_alpha"]  <- optim_QL_states$optim$bestmem[2]
-  EWA_self_simulation[count, "QL_2LL"]          <- optim_QL_states$optim$bestval
-
-  # Naive Bayes (nopts-arm bandit with prior vec transfered across games)
-  EWA_self_simulation[count, "NB_infrd_theta"] <- optim_NB$par[1]
-  EWA_self_simulation[count, "NB_infrd_eps"]   <- optim_NB$par[2]
-  EWA_self_simulation[count, "NB_2LL"]         <- optim_NB$value
-
-  # Random
-  EWA_self_simulation[count, "Random_2LL"]     <- -2*(2*num_rounds*log(1/3) + num_rounds*log(1/5))
-
-  count <- count + 1
-}
-
-save(EWA_self_simulation,file="SEWA_simulation.RData")
-
-```
-
-## Plotting parameter recovery scatter plots and model recovery results
-```{r}
-
-plot(EWA_self_simulation$real_lambda,EWA_self_simulation$S_EWA_infrd_lambda)
-# We can evaluate the correlation between real and infered lambdas and test it for significance
-cor.test(EWA_self_simulation$real_lambda, EWA_self_simulation$S_EWA_infrd_lambda, method=c("spearman"))
-
-# Model recovery: create a table with best fitting models by condition
-SEWA_recov_results <- table(EWA_self_simulation[, "condition"],c("random","N_Bayes","QL","EWA","S_EWA")[apply(EWA_self_simulation[,c("Random_2LL","NB_2LL","QL_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])
-
- write.csv(SEWA_recov_results,file="SEWA_recov_results.csv",row.names = TRUE)
- kable(SEWA_recov_results)
-```
-
-```{r}
-
-```
-
-<!--chapter:end:param_model_recovery.Rmd-->
-
----
-title: "Score_plots"
-output: html_document
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-
-library(dplyr)
-library(ggpubr)
-
-```
-
-```{r}
-
-exp1_dat = read.csv("exp1_data.csv")
-exp1_model_comp = read.csv("exp1_model_comp.csv")
-
-datalist = list()
-i = 0
-new_dat <- setNames(data.frame(matrix(ncol = ncol(exp1_dat), nrow = 0)), colnames(exp1_dat))
-for(id in unique(exp1_dat$human_id)) {
-  i <- i+1
-  tdat <- subset(exp1_dat,human_id == id)
-  tdat$part_num <- i
-  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
-  datalist[[i]] <- tdat
-}
-
-# Merge all datasets into one 
-new_dat <- dplyr::bind_rows(datalist)
-# or new_dat <- data.table::rbindlist(datalist)
-
-# Add column for time t
-new_dat <- new_dat %>% group_by(exp1_dat$human_id) %>% mutate(t = row_number())
-
-# Participant number as a factor 
-# tdat$part_num <- as.factor(tdat$part_num)
-
-# Add best fitting model per participant
-new_dat <- merge(new_dat, exp1_model_comp[, c("human_id", "Best_model")], by="human_id")
-```
-
-```{r}
-ggplot(data = new_dat, aes(x = t, y=acc_sum, group = part_num)) + 
-  geom_line(aes(color= Best_model))
-```
-
-```{r}
-temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
-dat_by_model <- temp %>% group_by(Best_model,t) %>% 
-  summarize(model_acc_sum = mean(acc_sum))
-
-ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
-   geom_line(aes(color= Best_model))
-```
-
-<!--chapter:end:score_plots.Rmd-->

### 2021-09-16 Report/paper_draft_2021.Rmd
mixed effect models instead of anovas

@@
 
-#+ geom_boxplot(alpha=.4) + geom_point(position=position_jitterdodge(), alpha=.4) + ylab("Score") + xlab("Game") + facet_grid(. ~ condition) + theme_apa() + geom_hline(yintercept = 0, lty=2)
-
-#geom_jitter(aes(colour=block, fill=block), width=.2) + facet_grid(. ~ condition)
-
-# ggboxplot(x = "game", y = "block_score", colour="block", fill="block", add =c("mean_ci"), palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUMBERS"), ylab = "Score", xlab = "Game", legend.title = "Block") + geom_jitter(aes(color = block, fill = block), width = 0.2, alpha = 0.3 ) + facet_grid(.
-~ condition)
-
-```
+```
+First,we focus on participants scores oin each game (see Figure \ref{fig:exp1-avg-scores-game}).
 On average, participants obtained the lowest score in the RPS game ($M = 0.289$, $SD = 0.348$), followed by Numbers ($M = 0.31$, $SD = 0.347$).
@@
 
-To assess learning within and between games, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants.
+<!-- To assess learning within and between games, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants.
 This showed a main effect of Game ($F(2,100) = 8.54$, $\eta^{2}  = 0.05$,  $p < .001$), indicating that average scores varied significantly over the games.
@@
 Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
+-->
+
+**To assess learning within and between games, we estimate a linear mixed effects model with the scores as the dependent variable, and Condition (Level 1 or Level 2), Game (RPS, FWG, Numbers)  and Block ( first-half , second-half) as independent variables.
+Random model intercepts are assumed for participants.This showed a main effect of Game ($F(2,250) = 12.90$, $\eta^{2}  = 0.09$,  $p < .001$) indicating that average scores varied significantly over the games**.
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ($t(100) =3.78$, $p < .001$) and the Numbers game ($t(100) = 3.32$ , $p = .002$).
+The score in RPS was not significantly different from the score in Numbers ($t(100) = 0.45$ , $p = .65$).
+The main effect of Block ($F(2,250) = 15.16$ ,  $\eta^{2} = 0.06$, $p < .001$) shows that the score in the first half of each game ($M = 0.29$) was significantly lower than in the second half ($M = 0.40$), which indicates within-game learning.
+The main effect of Condition ($F(1,50) = 5.44$, $\eta^{2} = 0.10$, $p = .024$) indicates that scores were higher against the level-1 player ($M = 0.43$) than against the level-2 player ($M = 0.27$).
+Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
+**There was also an interaction effect of game by condition ($F(2,250) = 4.52$ ,  $\eta^{2} = 0.03$, $p = .01$)**
 
@@
   ggboxplot(x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","Numbers"), fill="block", ylab = "Percentage score", xlab = "Games") +  facet_grid(. ~ condition)
-
 ```
@@
 
-tmp <- afex::aov_car(
-  block_score ~ game.f*condition*block + Error(human_id/(game.f*block))
-  , data=dat2
-  , type = 3)
+# tmp <- afex::aov_car(
+#   block_score ~ game.f*condition*block + Error(human_id/(game.f*block))
+#   , data=dat2
+#   , type = 3)
+
+mod1 <- mixed(block_score ~ game.f*condition*block + (1 | human_id),data=dat2,check_contrasts = FALSE, type = 3, method = "KR")
+#summary(mod1)
+mod1
+
+# Get effect sizes from F values of mixed effect model
+library(effectsize)
+F_to_eta2(12.9, 2, 250)
+F_to_eta2(5.44, 1, 50)
+F_to_eta2(15.16, 1, 250)
+F_to_eta2(4.52, 2, 250)
 
@@
 
-```
-
-<!-- (ref:figure4-caption) Mean and standard error of early scores by game and opponent -->
+library(afex)
+
+# setting contrast to compare early score between games across levels 
+contrasts(exp1_dat2_6$game.f) <- cbind(c(1,-1,0),c(0,-1,1))
+contrasts(exp1_dat2_6$condition) <- c(1,-1)
+
+# Mixed effects Model: Random intercept for participants
+lme_early <- mixed(early_score ~ game.f*condition + (1 | human_id),data=exp1_dat2_6,check_contrasts = FALSE, type = 3, method = "KR")
+summary(lme_early)
+
+lme_early
+
+```
+
 ```{r exp1-early-score-by-opp, fig.cap = "\\label{ref:figure4-caption}Performance in early rounds (2-6) per game and block across conditions in Experiment 1.
 Points are scores of individual participants and boxes reflect the 95\\% confidence intervals of the mean (center line equals the mean).", fig.align ='center', fig.width=8, fig.height=4}
+
 exp1_dat2_6 %>%
@@
 
-#p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","Numbers"), ylab = "Early rounds score", xlab = "Games")
-
-#p2 + facet_grid(. ~ condition)
-
 ```
@@
 Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents.
-To explore this, we used a 2 (Condition: Level 1, Level 2) by 3 (Game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants.
+We estimate a linear mixed effects model with the early round scores as the dependent variable, and Condition (Level 1 or Level 2) and Game (RPS, FWG, Numbers) as independent variables.
+Random model intercepts are assumed for participants.
+We found a main effect of Game ($F(2,100) = 3.35$, $p = .04$), and no main effect for condition.
+Further investigation of the effects of game on early score using planned contrasts revealed that early scores in the FWG games are significantly higher than in the RPS ( $t(99.99) = -2.32$, $p = 0.02$).
+
+<!-- To explore this, we used a 2 (Condition: Level 1, Level 2) by 3 (Game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants.
 There was a main effect of Game ($F(1.84,91.77) = 3.35$, $\eta^{2}  = 0.04$,  $p = .043$, Greenhouse-Geisser correction applied to the degrees of freedom to correct for non-sphericity).
-
-To test for transfer by type of opponent faced, we ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
+-->
+
+To delve deeper into the differences between participants learning transfer by opponent, we ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(150) = 3.96$, $p < .001$) and Numbers ($t(150) = 3.74$, $p < .001$).
@@
 
-To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA, with the first factor varying between participants.
+```{r, include = FALSE}
+
+xp2_anova <- afex::aov_car(
+  int_score ~ (game.f*interaction_lvl*condition.f*opp_type) + Error(human_id/(game.f*interaction_lvl*opp_type))
+  , data = dat_int
+  , type = 3
+)
+
+mod2 <- mixed(int_score ~ game.f*interaction_lvl*condition.f*opp_type + (1 | human_id),data=dat_int,check_contrasts = FALSE, type = 3, method = "KR")
+#summary(mod2)
+mod2
+
+F_to_eta2(15.32,2,528)
+F_to_eta2(5.78,2,528)
+```
+
+<!-- To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA, with the first factor varying between participants.
 This showed a main effect of Game ($F(1.85,88.7) = 11.81$, $\eta^{2} = 0.04$,  $p < .001$).
@@
 There was no significant difference between average scores on any two games when facing level-2 agents however.
+-->
+
+**To explore whether learning occurred within and between game, we estimated a mixed effect model, with the participants scores as the dependent variable and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2), Game (RPS, FWG, Shootout) and Encounter (first or second) as the independent variables.
+Random model intercepts are assumed for participants.
+We found a main effect of Game ($F(2,528) = 15.32$, $\eta^{2} = 0.04$,  $p < .001$).
+Post-hoc pairwise comparisons between games ($p$-values adjusted using Holm method for multiple comparisons) indicate performance in the games increased steadily throughout the experiment, with FWG performance significantly higher than RPS ($t(96) =2.53$, $p = .025$), and performance in the Shootout game significantly higher than in FWG ($t(96) = 2.32$, $p = .025$).
+Whilst the mixed effect model shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type ($F(2, 528) = 5.78$ ,$\eta^{2} = 0.02$,  $p = .003$).
+Follow-up analysis differentiating performance by type of opponent faced shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS ($t(191) = 2.70$, $p = .03$) and Shootout scores in turn significantly higher than FWG  ($t(191) = 3.05$, $p = .01$).
+There was no significant difference between average scores on any two games when facing level-2 agents however.**
 
@@
 
-# plot scores per game 
-#p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_se",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Early rounds score", xlab = "Games", legend.title = "Games")
-
-#p2 + facet_grid(. ~ opp_type)
-
 ```
@@
 We found a main effect of Game($F(2,240) = 6.57$, $p = .002$) and an interaction effect between Game and Opponent type ( $F(2,240) = 3.34$,  $p = .037$).**
-
+```{r, include = FALSE}
+# testing differences between early scores across games 
+library(afex)
+
+# Set contrasts
+contrasts(exp2_dat2_6$game.f) <- cbind(c(1,-1,0),c(0,-1,1))
+contrasts(exp2_dat2_6$opp_type) <- c(1,-1)
+contrasts(exp2_dat2_6$condition.f) <- c(1,-1)
+
+# Random intercecprt for participants
+lme_early2 <- mixed(early_score ~ game.f*opp_type*condition.f + (1 | human_id),data=exp2_dat2_6,check_contrasts = FALSE, type = 3, method = "KR")
+summary(lme_early2)
+
+lme_early2
+```
 <!-- We performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) repeated-measures ANOVA, with the first factor varying between participants.
@@
 The early round scores in the similar FWG games for level-1 and level-2 facing players are not significantly different from each other.
-However, the score of the players facing the level-1 opponent in Shootout is higher than that of players facing level-2 opponents ( $t(144) = 2.45$, $p = 0.01$).
+However, the score of the players facing the level-1 opponent in Shootout is higher than that of players facing level-2 opponents ($t(144) = 2.45$, $p = 0.01$).
 
@@
 This transfer was moderated by the degree of similarity between games.
-The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.
-**
+The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.**
 
@@
 **$\phi_{t}$ can be interpreted as the discount on prior experiences, modelling either limited agent memory or changes in the game conditions.
-At the core, $\phi_{t}$ depends on the surprise index $ S_{p}(t)$**:
+At the core, $\phi_{t}$ depends on the surprise index $S_{p}(t)$ **:
 
@@
 
-**$S_{p}(t)$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play $ h_{k}(t)$**:
+**$S_{p}(t)$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play $h_{k}(t)$**:
 
@@
 **Where $I$ is the indicator function as defined above.
-To get the surprise index, we simply sum all the squared deviations between the cumulative history vector $ h^{k}(t) $ and the immediate history $r^k(t)$**:
+To get the surprise index, we simply sum all the squared deviations between the cumulative history vector $h^{k}(t)$ and the immediate history $r^k(t)$**:
 

### 2021-09-16 Report/paper_draft_2021.tex
mixed effect models instead of anovas

@@
 %
-\documentclass[man,floatsintext]{apa6}
+\documentclass[english,man,floatsintext]{apa6}
 \usepackage{lmodern}
@@
             pdftitle={Transfer of Learned Opponent Models in Zero Sum Games},
-            pdfauthor={Ismail Guennouni~\& Maarten Speekenbrink},
+            pdfauthor={Ismail Guennouni1 \& Maarten Speekenbrink1},
             colorlinks=true,
@@
 \setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
 
@@
 
-\shorttitle{Upgrade Report}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Department of Experimental Psychology, University College London}
-\usepackage{csquotes}
+% Manuscript styling
 \usepackage{upgreek}
@@
 
+% Table formatting
 \usepackage{longtable}
 \usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
 
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
 \makeatletter
@@
 \newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+\shorttitle{Upgrade Report}
+\usepackage{csquotes}
 \shorttitle{}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\fi
 
 \title{Transfer of Learned Opponent Models in Zero Sum Games}
-\author{Ismail Guennouni\textsuperscript{1}~\& Maarten Speekenbrink\textsuperscript{1}}
+\author{Ismail Guennouni\textsuperscript{1} \& Maarten Speekenbrink\textsuperscript{1}}
 \date{}
 
-\authornote{
-
-Correspondence concerning this article should be addressed to Ismail Guennouni, Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom.
-E-mail: \href{mailto:i.guennouni.17@ucl.ac.uk}{\nolinkurl{i.guennouni.17@ucl.ac.uk}}}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Experimental Psychology, University College London}
 
@@
 learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
-
 }
@@
 
+First,we focus on participants scores oin each game (see Figure \ref{fig:exp1-avg-scores-game}).
 On average, participants obtained the lowest score in the RPS game (\(M = 0.289\), \(SD = 0.348\)), followed by Numbers (\(M = 0.31\), \(SD = 0.347\)).
@@
 
-To assess learning within and between games, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants.
-This showed a main effect of Game (\(F(2,100) = 8.54\), \(\eta^{2} = 0.05\), \(p < .001\)), indicating that average scores varied significantly over the games.
+\textbf{To assess learning within and between games, we estimate a linear mixed effects model with the scores as the dependent variable, and Condition (Level 1 or Level 2), Game (RPS, FWG, Numbers) and Block ( first-half , second-half) as independent variables.
+Random model intercepts are assumed for participants.This showed a main effect of Game (\(F(2,250) = 12.90\), \(\eta^{2} = 0.09\), \(p < .001\)) indicating that average scores varied significantly over the games}.
 Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game (\(t(100) =3.78\), \(p < .001\)) and the Numbers game (\(t(100) = 3.32\) , \(p = .002\)).
 The score in RPS was not significantly different from the score in Numbers (\(t(100) = 0.45\) , \(p = .65\)).
-The main effect of Block (\(F(1,50) = 22.51\) , \(\eta^{2} = 0.03\), \(p < .001\)) shows that the score in the first half of each game (\(M = 0.29\)) was significantly lower than in the second half (\(M = 0.40\)), which indicates within-game learning.
-The main effect of Condition (\(F(1,50) = 5.44\), \(\eta^{2} = 0.05\), \(p = .024\)) indicates that scores were higher against the level-1 player (\(M = 0.43\)) than against the level-2 player (\(M = 0.27\)).
+The main effect of Block (\(F(2,250) = 15.16\) , \(\eta^{2} = 0.06\), \(p < .001\)) shows that the score in the first half of each game (\(M = 0.29\)) was significantly lower than in the second half (\(M = 0.40\)), which indicates within-game learning.
+The main effect of Condition (\(F(1,50) = 5.44\), \(\eta^{2} = 0.10\), \(p = .024\)) indicates that scores were higher against the level-1 player (\(M = 0.43\)) than against the level-2 player (\(M = 0.27\)).
 Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
+\textbf{There was also an interaction effect of game by condition (\(F(2,250) = 4.52\) , \(\eta^{2} = 0.03\), \(p = .01\))}
 
@@
 Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents.
-To explore this, we used a 2 (Condition: Level 1, Level 2) by 3 (Game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game (\(F(1.84,91.77) = 3.35\), \(\eta^{2} = 0.04\), \(p = .043\), Greenhouse-Geisser correction applied to the degrees of freedom to correct for non-sphericity).
+We estimate a linear mixed effects model with the early round scores as the dependent variable, and Condition (Level 1 or Level 2) and Game (RPS, FWG, Numbers) as independent variables.
+Random model intercepts are assumed for participants.
+We found a main effect of Game (\(F(2,100) = 3.35\), \(p = .04\)), and no main effect for condition.
+Further investigation of the effects of game on early score using planned contrasts revealed that early scores in the FWG games are significantly higher than in the RPS ( \(t(99.99) = -2.32\), \(p = 0.02\)).
 
-To test for transfer by type of opponent faced, we ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
+To delve deeper into the differences between participants learning transfer by opponent, we ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG (\(t(150) = 3.96\), \(p < .001\)) and Numbers (\(t(150) = 3.74\), \(p < .001\)).
@@
 
-To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA, with the first factor varying between participants.
-This showed a main effect of Game (\(F(1.85,88.7) = 11.81\), \(\eta^{2} = 0.04\), \(p < .001\)).
+\textbf{To explore whether learning occurred within and between game, we estimated a mixed effect model, with the participants scores as the dependent variable and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2), Game (RPS, FWG, Shootout) and Encounter (first or second) as the independent variables.
+Random model intercepts are assumed for participants.
+We found a main effect of Game (\(F(2,528) = 15.32\), \(\eta^{2} = 0.04\), \(p < .001\)).
 Post-hoc pairwise comparisons between games (\(p\)-values adjusted using Holm method for multiple comparisons) indicate performance in the games increased steadily throughout the experiment, with FWG performance significantly higher than RPS (\(t(96) =2.53\), \(p = .025\)), and performance in the Shootout game significantly higher than in FWG (\(t(96) = 2.32\), \(p = .025\)).
-Whilst the ANOVA shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type (\(F(1.7, 81.82) = 5.31\) ,\(\eta^{2} = 0.02\), \(p = .01\)).
-Follow-up analysis shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS (\(t(191) = 2.70\), \(p = .03\)) and Shootout scores in turn significantly higher than FWG (\(t(191) = 3.05\), \(p = .01\)).
-There was no significant difference between average scores on any two games when facing level-2 agents however.
+Whilst the mixed effect model shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type (\(F(2, 528) = 5.78\) ,\(\eta^{2} = 0.02\), \(p = .003\)).
+Follow-up analysis differentiating performance by type of opponent faced shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS (\(t(191) = 2.70\), \(p = .03\)) and Shootout scores in turn significantly higher than FWG (\(t(191) = 3.05\), \(p = .01\)).
+There was no significant difference between average scores on any two games when facing level-2 agents however.}
 
@@
 The early round scores in the similar FWG games for level-1 and level-2 facing players are not significantly different from each other.
-However, the score of the players facing the level-1 opponent in Shootout is higher than that of players facing level-2 opponents ( \(t(144) = 2.45\), \(p = 0.01\)).
+However, the score of the players facing the level-1 opponent in Shootout is higher than that of players facing level-2 opponents (\(t(144) = 2.45\), \(p = 0.01\)).
 
@@
 
-\textbf{The results of Experiment 2 confirm some earlier results from Experiment 1 in a situation where participants need to learn about two distinct opponents.
+\textbf{The results of Experiment 2 confirm earlier results from Experiment 1 on learning transfer in a situation where participants need to learn about two distinct opponents.
 As in Experiment 1, participants adapted their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
@@
 This transfer was moderated by the degree of similarity between games.
-The interqaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.
-}
+The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.}
 
@@
 
-\(\phi_{t}\) can be interpreted as the discount on prior experiences, modelling either limited agent memory or changes in the game conditions.
-At the core, \(\phi_{t}\) depends on the surprise index \$ S\_\{p\}(t)\$ :
+\textbf{\(\phi_{t}\) can be interpreted as the discount on prior experiences, modelling either limited agent memory or changes in the game conditions.
+At the core, \(\phi_{t}\) depends on the surprise index \(S_{p}(t)\) }:
 
@@
 
-\$ S\_\{p\}(t)\$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play \$ h\_\{k\}(t)\$ :
+\textbf{\(S_{p}(t)\) quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play \(h_{k}(t)\)}:
 
@@
 
-Where \(I\) is the indicator function as defined above.
-To get the surprise index, we simply sum all the squared deviations between the cumulative history vector \$ h\^{}\{k\}(t) \$ and the immediate history \(r^k(t)\):
+\textbf{Where \(I\) is the indicator function as defined above.
+To get the surprise index, we simply sum all the squared deviations between the cumulative history vector \(h^{k}(t)\) and the immediate history \(r^k(t)\)}:
 
@@
 The results of our first experiment show that the majority of participants learnt to adapt to their opponent's strategy over multiple interactions, and generalised this learning to a similar game.
-Performance in early rounds indicated that transfer to the more dissimilar game was moderated by the degree of similarity between games.
-There was not enough evidence for a difference in learning transfer between the two opponents.
-In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
+\textbf{Performance in early rounds indicated that learning transfer was moderated by the degree of similarity between games.
+There was not enough evidence for a difference in learning transfer between the two opponents.} In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
 In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
-Experiment 2 also offers more opportunities to test transfer of a learnt opponent model, as we could assess both within and between game transfer.
-There was clear evidence of transfer in the early rounds of the later games.
-On top of the moderation of the transfer by degree of similarity between games, we also found that learning transfer is moderated by the type of opponent faced: Evidence of transfer was weaker for the level-2 opponent as compared to the level-1 opponent.
-That evidence for transfer was weaker when facing the more sophisticated level-2 opponent may be due to a higher difficulty of learning that opponent's strategy.
+\textbf{There was clear evidence of transfer in the early rounds of the later games.
+On top of the moderation of the transfer by degree of similarity between games, we also found that learning transfer is moderated by the type of opponent faced: Transfer was harder when facing the level-2 opponent as compared to the level-1 opponent.} That evidence for transfer was weaker when facing the more sophisticated level-2 opponent may be due to a higher difficulty of learning that opponent's strategy.
 If it is more difficult to establish a model of the level-2 opponent, there is likely less knowledge to transfer to the new game.
@@
 
-\leavevmode\hypertarget{ref-batzilis}{}%
-Batzilis, D., Jaffe, S., Levitt, S., List, J.
-A., \& Picel, J.
-(2016).
-\emph{How facebook can deepen our understanding of behavior in strategic settings: Evidence from a million rock-paper-scissors games}.
-working paper.
-
-\leavevmode\hypertarget{ref-camerer2003behavioural}{}%
-Camerer, C. F. (2003). Behavioural studies of strategic thinking in games. \emph{Trends in Cognitive Sciences}, \emph{7}(5), 225--231.
-
-\leavevmode\hypertarget{ref-camerer2004cognitive}{}%
-Camerer, C. F., Ho, T.-H., \& Chong, J.-K. (2004). A cognitive hierarchy model of games. \emph{The Quarterly Journal of Economics}, \emph{119}(3), 861--898.
-
-\leavevmode\hypertarget{ref-camerer1997experience}{}%
-Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
-
-\leavevmode\hypertarget{ref-knez2000}{}%
-Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
-
-\leavevmode\hypertarget{ref-cheung1994learning}{}%
-Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
-
-\leavevmode\hypertarget{ref-costa2001cognition}{}%
-Costa-Gomes, M., Crawford, V. P., \& Broseta, B. (2001). Cognition and behavior in normal-form games: An experimental study. \emph{Econometrica}, \emph{69}(5), 1193--1235.
-
-\leavevmode\hypertarget{ref-daw2005uncertainty}{}%
-Daw, N.
-D., Niv, Y., \& Dayan, P.
-(2005).
-Uncertainty-based competition between prefrontal and dorsolateral striatal systems for behavioral control.
-\emph{Nature Neuroscience}, \emph{8}(12), 1704--1711.
-
-\leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
-
-\leavevmode\hypertarget{ref-ho1998iterated}{}%
-Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
-
-\leavevmode\hypertarget{ref-Lake2017}{}%
-Lake, B.
-M., Ullman, T.
-D., Tenenbaum, J.
-B., \& Gershman, S.
-J.
-(2017).
-Building machines that learn and think like people.
-\emph{Behavioral and Brain Sciences}, \emph{40}.
-\url{https://doi.org/10.1017/S0140525X16001837}
-
-\leavevmode\hypertarget{ref-lieder2020resource}{}%
-Lieder, F., \& Griffiths, T.
-L.
-(2020).
-Resource-rational analysis: Understanding human cognition as the optimal use of limited computational resources.
-\emph{Behavioral and Brain Sciences}, \emph{43}.
-
-\leavevmode\hypertarget{ref-mandler2004foundations}{}%
-Mandler, J. M. (2004). \emph{The foundations of mind: Origins of conceptual thought}. Oxford University Press.
-
-\leavevmode\hypertarget{ref-mertens1990repeated}{}%
-Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
-
-\leavevmode\hypertarget{ref-R-DEoptim}{}%
-Mullen, K., Ardia, D., Gil, D., Windover, D., \& Cline, J.
-(2011).
-DEoptim: An R package for global optimization by Differential Evolution.
-\emph{Journal of Statistical Software}, \emph{40}(6), 1--26.
-\url{https://doi.org/10.18637/jss.v040.i06}
-
-\leavevmode\hypertarget{ref-nagel1995unraveling}{}%
-Nagel, R. (1995). Unraveling in guessing games: An experimental study. \emph{The American Economic Review}, \emph{85}(5), 1313--1326.
-
-\leavevmode\hypertarget{ref-shachat2004we}{}%
-Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
-
-\leavevmode\hypertarget{ref-Simon_Daw_11}{}%
-Simon, D.
-A., \& Daw, N.
-D.
-(2011).
-Environmental statistics and the trade-off between model-based and TD learning in humans.
-\emph{Advances in Neural Information Processing Systems 24: 25th Annual Conference on Neural Information Processing Systems 2011, NIPS 2011}, 1--9.
-
-\leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
-Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
-
-\leavevmode\hypertarget{ref-stahl2000rule}{}%
-Stahl, D. O. (2000). Rule learning in symmetric normal-form games: Theory and evidence. \emph{Games and Economic Behavior}, \emph{32}(1), 105--138.
-
-\leavevmode\hypertarget{ref-stahl2003sophisticated}{}%
-Stahl, D. O. (2003). Sophisticated learning and learning sophistication. \emph{Available at SSRN 410921}.
-
-\leavevmode\hypertarget{ref-stahl1995players}{}%
-Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
-
-\leavevmode\hypertarget{ref-R-depmixS4}{}%
-Visser, I., \& Speekenbrink, M.
-(2010).
-depmixS4: An R package for hidden markov models.
-\emph{Journal of Statistical Software}, \emph{36}(7), 1--21.
-Retrieved from \url{http://www.jstatsoft.org/v36/i07/}
-
-\leavevmode\hypertarget{ref-wang2014social}{}%
-Wang, Z., Xu, B., \& Zhou, H.-J. (2014). Social cycling and conditional responses in the rock-paper-scissors game. \emph{Scientific Reports}, \emph{4}(1), 1--7.
-
-\leavevmode\hypertarget{ref-watkins1992q}{}%
-Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
-
-\leavevmode\hypertarget{ref-Kool_2011}{}%
-Wouter Kool, Joseph T.
-McGuire, Zev B.
-Rosen, Matthew M.
-Bovinick.
-(2011).
-Decision Making and the Avoidance of Cognitive Demand.
-\emph{Experimental Psychology}.
-\url{https://doi.org/10.2996/kmj/1138846322}
-
 \end{document}

### 2021-09-16 exp1_clean_analysis.Rmd
mixed effect models instead of anovas

@@
 ```
+```{r}
+library(afex)
+mod_exp1 <- fixed( block_score ~ game.f*block*condition + Error(human_id/(game.f*block)), dat2)
+summary(a1)
+```
 
@@
 
-# set contrasts for factors in dataset for condition and game
+library(afex)
 
@@
 # testing differences between early scores across games 
-library(afex)
 aov_early <- aov_car(early_score ~ game.f*condition + Error(human_id/(game.f)),data=dat2_6,check_contrasts = FALSE)
@@
 
-# Random intercecprt for participants
+# Mixed effects Model: Random intercecept for participants
 lme_early <- mixed(early_score ~ game.f*condition + (1 | human_id),data=dat2_6,check_contrasts = FALSE, type = 3, method = "KR")

### 2021-09-20 Report/paper_draft_2021.Rmd
a few final issues to resolve

@@
 In two experiments, participants face the same opponent (Experiment 1) or the same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, the structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
-To foreshadow our results, **we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of their opponent and the similarity of the games** **IG: I guess we can still say that given findings of exp 2...** .
+To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, and that this transfer is moderated by the sophistication of their opponent and the similarity between the games.
 Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a more habitual and cognitively less demanding strategy in the later stages of the games.
@@
 ```
-First,we focus on participants scores oin each game (see Figure \ref{fig:exp1-avg-scores-game}).
+First, we focus on participants scores in each game (see Figure \ref{fig:exp1-avg-scores-game}).
 On average, participants obtained the lowest score in the RPS game ($M = 0.289$, $SD = 0.348$), followed by Numbers ($M = 0.31$, $SD = 0.347$).
@@
 
-**To assess learning within and between games, we estimate a linear mixed effects model with the scores as the dependent variable, and Condition (Level 1 or Level 2), Game (RPS, FWG, Numbers)  and Block ( first-half , second-half) as independent variables.
-Random model intercepts are assumed for participants.This showed a main effect of Game ($F(2,250) = 12.90$, $\eta^{2}  = 0.09$,  $p < .001$) indicating that average scores varied significantly over the games**.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ($t(100) =3.78$, $p < .001$) and the Numbers game ($t(100) = 3.32$ , $p = .002$).
+To assess learning within and between games, we estimate a linear mixed-effects model with score as the dependent variable, and Condition (Level 1 or Level 2), Game (RPS, FWG, Numbers) and Block (first-half , second-half) as independent variables, including all main effects and interactions.
+The model included random intercepts for participants.
+The results show a main effect of Game ($F(2,250) = 12.90$, $\eta^{2}  = 0.09$,  $p < .001$) indicating that performance differs between the games.
+Post-hoc pairwise comparisons show that performance in the FWG game was significantly higher than in the RPS game ($t(100) =3.78$, $p < .001$) and the Numbers game ($t(100) = 3.32$ , $p = .002$).
 The score in RPS was not significantly different from the score in Numbers ($t(100) = 0.45$ , $p = .65$).
@@
 Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
-**There was also an interaction effect of game by condition ($F(2,250) = 4.52$ ,  $\eta^{2} = 0.03$, $p = .01$)**
+There was also an interaction between Game and Condition ($F(2,250) = 4.52$ ,  $\eta^{2} = 0.03$, $p = .01$).
+**MS: What does this interaction indicate?**
 
@@
 # setting contrast to compare early score between games across levels 
+exp1_dat2_6$game.f <- as.factor(exp1_dat2_6$game.f)
+exp1_dat2_6$condition <- as.factor(exp1_dat2_6$condition)
+
 contrasts(exp1_dat2_6$game.f) <- cbind(c(1,-1,0),c(0,-1,1))
@@
 Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents.
-We estimate a linear mixed effects model with the early round scores as the dependent variable, and Condition (Level 1 or Level 2) and Game (RPS, FWG, Numbers) as independent variables.
-Random model intercepts are assumed for participants.
-We found a main effect of Game ($F(2,100) = 3.35$, $p = .04$), and no main effect for condition.
+We estimates a linear mixed-effects model with the early round score as the dependent variable, and Condition (Level 1 or Level 2) and Game (RPS, FWG, Numbers), as well as their interaction, as independent variables.
+The model included random intercepts for participants.
+The results indicated a main effect of Game ($F(2,100) = 3.35$, $p = .04$), but no effect for condition.
 Further investigation of the effects of game on early score using planned contrasts revealed that early scores in the FWG games are significantly higher than in the RPS ( $t(99.99) = -2.32$, $p = 0.02$).
@@
 
-To delve deeper into the differences between participants learning transfer by opponent, we ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
+<!-- To delve deeper into the differences between participants learning transfer by opponent,--> We next ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(150) = 3.96$, $p < .001$) and Numbers ($t(150) = 3.74$, $p < .001$).
@@
 
-**To explore whether learning occurred within and between game, we estimated a mixed effect model, with the participants scores as the dependent variable and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2), Game (RPS, FWG, Shootout) and Encounter (first or second) as the independent variables.
-Random model intercepts are assumed for participants.
+To explore whether learning occurred within and between games, we estimated a linear mixed-effects model, with score as the dependent variable and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2), Game (RPS, FWG, Shootout) and Encounter (first or second) as the independent variables, including all main effects and interactions.
+The model included random intercepts for participants.
 We found a main effect of Game ($F(2,528) = 15.32$, $\eta^{2} = 0.04$,  $p < .001$).
 Post-hoc pairwise comparisons between games ($p$-values adjusted using Holm method for multiple comparisons) indicate performance in the games increased steadily throughout the experiment, with FWG performance significantly higher than RPS ($t(96) =2.53$, $p = .025$), and performance in the Shootout game significantly higher than in FWG ($t(96) = 2.32$, $p = .025$).
-Whilst the mixed effect model shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type ($F(2, 528) = 5.78$ ,$\eta^{2} = 0.02$,  $p = .003$).
+Whilst the model shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type ($F(2, 528) = 5.78$ ,$\eta^{2} = 0.02$,  $p = .003$).
 Follow-up analysis differentiating performance by type of opponent faced shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS ($t(191) = 2.70$, $p = .03$) and Shootout scores in turn significantly higher than FWG  ($t(191) = 3.05$, $p = .01$).
-There was no significant difference between average scores on any two games when facing level-2 agents however.**
+There was no significant difference between scores on games when facing level-2 agents however.
 
@@
 
-**To measure transfer between games, we again focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
-We estimate a linear mixed effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables.
-Random model intercepts are assumed for participants.
-We found a main effect of Game($F(2,240) = 6.57$, $p = .002$) and an interaction effect between Game and Opponent type ( $F(2,240) = 3.34$,  $p = .037$).**
+To measure transfer between games, we again focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
+We estimated a linear mixed-effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables, including all main effects and interactions.
+The model also included random intercepts for participants.
+We found a main effect of Game ($F(2,240) = 6.57$, $p = .002$) and an interaction effect between Game and Opponent type ($F(2,240) = 3.34$,  $p = .037$).
+**MS: What do these effects indicate?
+Report post-hoc comparisons between games, and e.g.
+differences between opponents for each game, here.
+The later tests against 0 are not adequate to understand the effects here.**
+
 ```{r, include = FALSE}
@@
 library(afex)
+
+exp2_dat2_6$game.f <- as.factor(exp2_dat2_6$game.f)
+exp2_dat2_6$opp_type <- as.factor(exp2_dat2_6$opp_type)
+exp2_dat2_6$condition.f <- as.factor(exp2_dat2_6$condition.f)
 
@@
 
-**The results of Experiment 2 confirm earlier results from Experiment 1 on learning transfer in a situation where participants need to learn about two distinct opponents.
+The results of Experiment 2 confirm earlier findings from Experiment 1 on learning transfer in a situation where participants need to learn about two distinct opponents.
 As in Experiment 1, participants adapted their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
 Knowledge about both types of opponents were transferred to both the similar and dissimilar game.
-This transfer was moderated by the degree of similarity between games.
-The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.**
+This transfer was moderated by the degree of similarity between games, as well as opponent type.
+The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.
 
@@
 We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
-**MS: need to better describe what $\phi$ is, and how $N(t)$ is determined.
-IG: done** In the earlier version of the EWA model [@camerer1997experience], $\phi$ and $\delta$ were free parameters.
+
+In the earlier version of the EWA model [@camerer1997experience], $\phi$ and $\delta$ were time-invariant free parameters.
 In the self-tuning EWA model [@ho2004economics], the values of $\delta$ and $\phi$ are learnt from experience.
-$\delta$ is updated using the
-
-$$ \delta_{a}(t)  = 1  \text{  if  }  R(a,o_{t}) \geq r_{t}  \text{  and }  0 \text{  otherwise } $$
-
-**$\phi_{t}$ can be interpreted as the discount on prior experiences, modelling either limited agent memory or changes in the game conditions.
-At the core, $\phi_{t}$ depends on the surprise index $S_{p}(t)$ **:
-
-$$ \phi(t) = 1 - \frac{1}{2}S_{p}(t) $$
-
-**$S_{p}(t)$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play $h_{k}(t)$**:
-
-$$  h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k,o_{\tau})}{t} $$
-
-As well as an indicator vector of the most recent opponent play:
-
-$$r^k(t) = I(o^k,o_{t})$$
-
-**Where $I$ is the indicator function as defined above.
-To get the surprise index, we simply sum all the squared deviations between the cumulative history vector $h^{k}(t)$ and the immediate history $r^k(t)$**:
-
+Over time, $\delta$ is updated as
+$$\delta_{a}(t) = \begin{cases} 1 & \text{if }  R(a,o_{t}) \geq r_{t}  \\
+0 & \text{otherwise} \end{cases}$$ 
+The $\phi_{t}$ parameter can be interpreted as a discount of prior experience, modelling either limited agent memory or changes in the game conditions.
+At the core, $\phi(t)$ depends on a surprise index $S_{p}(t)$:
+$$\phi(t) = 1 - \frac{1}{2}S_{p}(t) ,$$
+where $S_{p}(t)$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play $h_{k}(t)$:
+$$h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k,o_{\tau})}{t}, $$ 
+as well as an indicator vector of the most recent opponent play:
+$$r^k(t) = I(o^k,o_{t}), $$ 
+Where $I$ is the indicator function as defined above.
+To get the surprise index, we simply sum all the squared deviations between the cumulative history vector $h^{k}(t)$ and the immediate history $r^k(t)$:
 $$S_{p}(t) = \sum_{k=1}^{|\mathcal{A}_g|} (h^{k}(t) - r^k(t))^2 $$ 
-
-For more details on the self-tuning EWA model, we refer the reader to [@ho2004economics].As in the models above, actions are chosen based on a softmax decision rule:
+**MS: why is there a superscript in $h^k$ and $r^k$? And is the indicator variable $I(o^k = o_{t})$? And is $\delta_a(t)$ always 0 or 1?**
+
+For more details on the self-tuning EWA model, we refer the reader to [@ho2004economics]. As in the RL model above, actions are chosen based on a softmax decision rule:
 
@@
 
-For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NBT), as well as a reinforcement learning (RL), and finally a self-tuning EWA model with the same state space (EWA).
+For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NT), as well as a reinforcement learning (RL), and finally a self-tuning EWA model with the same state space (EWA).
 
@@
 exp1_comp_results <- read.csv(file="../exp1_all_results.csv")
-exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Nash","BCH_BT","BCH_NBT", "RL","EWA")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])
+exp1_comp_table <- table(exp1_comp_results[, "condition"],c("Nash","BCH_BT","BCH_NT", "RL","EWA")[apply(exp1_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","ST_EWA_STATES_BIC")],1,which.min)])
 
@@
 
-**MS: Please present the models in the figures in the order mentioned in text (i.e., Nash, RL, EWA, BCH), and when providing versions of each, do so in the same order as well, i.e.
-x_NT, x_WT, x_BT.
-IG : DONE **
-
 Figure\ \@ref(fig:exp1-comp-models)  shows the results for Experiment 1.
@@
 Only a few participants were best described by one of the BCH models or the EWA model.
-We have also estimated BIC weights for each model and we confirm that <!-- (Figure \ \@ref(fig:xp1-BIC-weigths)), we confirm this -->.
+<!-- We have also estimated BIC weights for each model and we confirm that <!-- (Figure \ \@ref(fig:xp1-BIC-weigths)), we confirm this .
 RL models have high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, which fits the picture drawn by the histogram.
-**IG: mentioned we looked at BIC weights and removed BIC wgt plot **
+**IG: mentioned we looked at BIC weights and removed BIC wgt plot ** -->
 
@@
 
-exp1_comp_df$model.f <- factor(exp1_comp_df$model, levels = c("Nash","RL","EWA", "BCH_NBT", "BCH_BT"), ordered =TRUE)
+exp1_comp_df$model.f <- factor(exp1_comp_df$model, levels = c("Nash","RL","EWA", "BCH_NT", "BCH_BT"), ordered =TRUE)
 
@@
 
-```{r exp2-comp-models, fig.cap = "Experiment 2 Histogram of best fitting computational models by condition", out.width="\\textwidth", fig.align='center'}
+```{r exp2-comp-models, fig.cap = "Experiment 2 histogram of best fitting computational models by condition.", out.width="\\textwidth", fig.align='center'}
 
@@
 
-```{r exp1-lik-by-tr, fig.cap = "Experiment 1 Likelihood by trial, game and opponent faced", fig.align='center'}
+```{r exp1-lik-by-tr, fig.cap = "Experiment 1 likelihood by trial, game and opponent faced", fig.align='center'}
 # make sure the different games are ordered in the way they were played
@@
   facet_grid(game~stage) +
-  scale_colour_discrete(name = "Strategy", labels = c( "Nash", "RL + within Tr", "BCH + within & btw Tr"))
+  scale_colour_discrete(name = "Strategy", labels = c( "Nash", "RL_WT", "BCH_BT"))
 
@@
   dplyr::summarise(Nash = mean(post_Nash, na.rm = TRUE),
-                   RL = mean(post_RL, na.rm = TRUE),
+                   RL_WT = mean(post_RL, na.rm = TRUE),
             BCH_BT = mean(post_Bayes_Tr, na.rm = TRUE))
@@
 
-data_long_post1 <- gather(mean_post_1, strategy, probability, Nash, RL,BCH_BT, factor_key=TRUE)
+data_long_post1 <- gather(mean_post_1, strategy, probability, Nash, RL_WT, BCH_BT, factor_key=TRUE)
 
@@
 The results of our first experiment show that the majority of participants learnt to adapt to their opponent's strategy over multiple interactions, and generalised this learning to a similar game.
-**Performance in early rounds indicated that learning transfer was moderated by the degree of similarity between games.
-There was not enough evidence for a difference in learning transfer between the two opponents.** In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
+Performance in early rounds indicated that learning transfer was moderated by the degree of similarity between games.
+In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
 In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
-**There was clear evidence of transfer in the early rounds of the later games.
-On top of the moderation of the transfer by degree of similarity between games, we also found that learning transfer is moderated by the type of opponent faced: Transfer was harder when facing the level-2 opponent as compared to the level-1 opponent.** That evidence for transfer was weaker when facing the more sophisticated level-2 opponent may be due to a higher difficulty of learning that opponent's strategy.
+In Experiment 2, we again found clear evidence of transfer in the early rounds of the later games.
+In addition to the moderation of transfer by the similarity between games, we also found that learning transfer was moderated by the type of opponent faced: Transfer was harder when facing the level-2 opponent as compared to the level-1 opponent.
+That evidence for transfer was weaker when facing the more sophisticated level-2 opponent may be due to a higher difficulty of learning that opponent's strategy.
 If it is more difficult to establish a model of the level-2 opponent, there is likely less knowledge to transfer to the new game.

### 2021-09-20 Report/paper_draft_2021.tex
a few final issues to resolve

--- 2021-08-26 Report/paper_draft_2021.tex
@@
 In two experiments, participants face the same opponent (Experiment 1) or the same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, the structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
-To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of their opponent and the similarity of the games.
+To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, and that this transfer is moderated by the sophistication of their opponent and the similarity between the games.
 Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a more habitual and cognitively less demanding strategy in the later stages of the games.
@@
 
+First, we focus on participants scores in each game (see Figure \ref{fig:exp1-avg-scores-game}).
 On average, participants obtained the lowest score in the RPS game (\(M = 0.289\), \(SD = 0.348\)), followed by Numbers (\(M = 0.31\), \(SD = 0.347\)).
@@
 
-To assess learning within and between games, we used a 2 (condition: Level 1, Level 2) by 3 (game: RPS, FWG, Numbers) by 2 (block: first half, second half) repeated-measures ANOVA, with the first factor varying between participants.
-This showed a main effect of Game (\(F(2,100) = 8.54\), \(\eta^{2} = 0.05\), \(p < .001\)), indicating that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game (\(t(100) =3.78\), \(p < .001\)) and the Numbers game (\(t(100) = 3.32\) , \(p = .002\)).
+To assess learning within and between games, we estimate a linear mixed-effects model with score as the dependent variable, and Condition (Level 1 or Level 2), Game (RPS, FWG, Numbers) and Block (first-half , second-half) as independent variables, including all main effects and interactions.
+The model included random intercepts for participants.
+The results show a main effect of Game (\(F(2,250) = 12.90\), \(\eta^{2} = 0.09\), \(p < .001\)) indicating that performance differs between the games.
+Post-hoc pairwise comparisons show that performance in the FWG game was significantly higher than in the RPS game (\(t(100) =3.78\), \(p < .001\)) and the Numbers game (\(t(100) = 3.32\) , \(p = .002\)).
 The score in RPS was not significantly different from the score in Numbers (\(t(100) = 0.45\) , \(p = .65\)).
-The main effect of Block (\(F(1,50) = 22.51\) , \(\eta^{2} = 0.03\), \(p < .001\)) shows that the score in the first half of each game (\(M = 0.29\)) was significantly lower than in the second half (\(M = 0.40\)), which indicates within-game learning.
-The main effect of Condition (\(F(1,50) = 5.44\), \(\eta^{2} = 0.05\), \(p = .024\)) indicates that scores were higher against the level-1 player (\(M = 0.43\)) than against the level-2 player (\(M = 0.27\)).
+The main effect of Block (\(F(2,250) = 15.16\) , \(\eta^{2} = 0.06\), \(p < .001\)) shows that the score in the first half of each game (\(M = 0.29\)) was significantly lower than in the second half (\(M = 0.40\)), which indicates within-game learning.
+The main effect of Condition (\(F(1,50) = 5.44\), \(\eta^{2} = 0.10\), \(p = .024\)) indicates that scores were higher against the level-1 player (\(M = 0.43\)) than against the level-2 player (\(M = 0.27\)).
 Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
+There was also an interaction between Game and Condition (\(F(2,250) = 4.52\) , \(\eta^{2} = 0.03\), \(p = .01\)).
+\textbf{MS: What does this interaction indicate?}
 
@@
 Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents.
-To explore this, we used a 2 (Condition: Level 1, Level 2) by 3 (Game: RPS, FWG, Numbers) repeated measures ANOVA with the first factor varying between participants.
-There was a main effect of Game (\(F(1.84,91.77) = 3.35\), \(\eta^{2} = 0.04\), \(p = .043\), Greenhouse-Geisser correction applied to the degrees of freedom to correct for non-sphericity).
-\textbf{MS: was this the only significant effect?
-If so, people might wonder why we next run analyses for each combination of player and game} We then ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
+We estimates a linear mixed-effects model with the early round score as the dependent variable, and Condition (Level 1 or Level 2) and Game (RPS, FWG, Numbers), as well as their interaction, as independent variables.
+The model included random intercepts for participants.
+The results indicated a main effect of Game (\(F(2,100) = 3.35\), \(p = .04\)), but no effect for condition.
+Further investigation of the effects of game on early score using planned contrasts revealed that early scores in the FWG games are significantly higher than in the RPS ( \(t(99.99) = -2.32\), \(p = 0.02\)).
+
+We next ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG (\(t(150) = 3.96\), \(p < .001\)) and Numbers (\(t(150) = 3.74\), \(p < .001\)).
@@
 
-To explore whether learning occurred within and between games, we performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) by two (Encounter: first or second) repeated-measures ANOVA, with the first factor varying between participants.
-This showed a main effect of Game (\(F(1.85,88.7) = 11.81\), \(\eta^{2} = 0.04\), \(p < .001\)).
+To explore whether learning occurred within and between games, we estimated a linear mixed-effects model, with score as the dependent variable and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2), Game (RPS, FWG, Shootout) and Encounter (first or second) as the independent variables, including all main effects and interactions.
+The model included random intercepts for participants.
+We found a main effect of Game (\(F(2,528) = 15.32\), \(\eta^{2} = 0.04\), \(p < .001\)).
 Post-hoc pairwise comparisons between games (\(p\)-values adjusted using Holm method for multiple comparisons) indicate performance in the games increased steadily throughout the experiment, with FWG performance significantly higher than RPS (\(t(96) =2.53\), \(p = .025\)), and performance in the Shootout game significantly higher than in FWG (\(t(96) = 2.32\), \(p = .025\)).
-Whilst the ANOVA shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type (\(F(1.7, 81.82) = 5.31\) ,\(\eta^{2} = 0.02\), \(p = .01\)).
-Follow-up analysis shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS (\(t(191) = 2.70\), \(p = .03\)) and Shootout scores in turn significantly higher than FWG (\(t(191) = 3.05\), \(p = .01\)).
-There was no significant difference between average scores on any two games when facing level-2 agents however.
+Whilst the model shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type (\(F(2, 528) = 5.78\) ,\(\eta^{2} = 0.02\), \(p = .003\)).
+Follow-up analysis differentiating performance by type of opponent faced shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS (\(t(191) = 2.70\), \(p = .03\)) and Shootout scores in turn significantly higher than FWG (\(t(191) = 3.05\), \(p = .01\)).
+There was no significant difference between scores on games when facing level-2 agents however.
 
@@
 To measure transfer between games, we again focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
-We performed a two (Condition: level-1 first, level-2 first) by two (Opponent type: level-1 or level-2) by three (Game: RPS, FWG, Shootout) repeated-measures ANOVA, with the first factor varying between participants.
-This showed a main effect of Game (\(F(1.94,92.98) = 7.67\), \(\eta^{2} = 0.04\), \(p < .001\)).
-\textbf{MS: Again, if there is no interaction, there might not be justification for running tests per opponent and game }
+We estimated a linear mixed-effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables, including all main effects and interactions.
+The model also included random intercepts for participants.
+We found a main effect of Game (\(F(2,240) = 6.57\), \(p = .002\)) and an interaction effect between Game and Opponent type (\(F(2,240) = 3.34\), \(p = .037\)).
+\textbf{MS: What do these effects indicate?
+Report post-hoc comparisons between games, and e.g.~differences between opponents for each game, here.
+The later tests against 0 are not adequate to understand the effects here.}
+
 We then ran statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
@@
 
-The results of Experiment 2 confirm the earlier results of Experiment 1 in a situation where participants need to learn about two distinct opponents.
+The results of Experiment 2 confirm earlier findings from Experiment 1 on learning transfer in a situation where participants need to learn about two distinct opponents.
 As in Experiment 1, participants adapted their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
 Knowledge about both types of opponents were transferred to both the similar and dissimilar game.
-However, transfer to the dissimilar game was easier when facing the less sophisticated agent.
+This transfer was moderated by the degree of similarity between games, as well as opponent type.
+The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.
 
@@
 The attraction of action \(a\) at time \(t\) given state \(s\) is denoted as \(A_{t}(a, s)\) and updated as
-\[ A_{t+1}(a,s) =  \frac{\phi \ N(t) \ A_{t}(a,s) + [ \delta + (1-\delta) \ I(a_t = a )] \ R(a,o_t) } {\phi \ N(t) + 1} \]
+\[ A_{t+1}(a,s) =  \frac{\phi(t) \ N(t) \ A_{t}(a,s) + [ \delta_{a}(t) + (1-\delta_{a}(t)) \ I(a_t = a )] \ R(a,o_t) } {\phi(t)N(t) + 1} \]
 where \(I(x)\) is an indicator function which takes the value 1 is its argument is true and 0 otherwise, and \(R(a,o_t)\) is the reward that would be obtained from playing action \(a\) against opponent action \(o_t\).
@@
 We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
-\textbf{MS: need to better describe what \(\phi\) is, and how \(N(t)\) is determined.} In the earlier version of the EWA model (C.
-Camerer, Ho, \& Others, 1997), \(\phi\) and \(\delta\) were free parameters.
+
+In the earlier version of the EWA model (C.
+Camerer, Ho, \& Others, 1997), \(\phi\) and \(\delta\) were time-invariant free parameters.
 In the self-tuning EWA model (Teck H.
 Ho, Camerer, \& Chong, 2004), the values of \(\delta\) and \(\phi\) are learnt from experience.
-For details on how this is done, we refer the reader to (Teck H.
-Ho, Camerer, \& Chong, 2004).
-\textbf{MS: Should describe how the parameters are self-tuned with equations.
-IG: There are many equations for each of the parameters update, phi, delta and N\ldots I'm concerned it would make for cumbersome reading, especially since EWA doesn't really fit well anyway.
-I've added that details of updates can be found in original camerer paper.
-MS: If it's three additional equations, that's not a big deal really.
-}
+Over time, \(\delta\) is updated as
+\[\delta_{a}(t) = \begin{cases} 1 & \text{if }  R(a,o_{t}) \geq r_{t}  \\
+0 & \text{otherwise} \end{cases}\]
+The \(\phi_{t}\) parameter can be interpreted as a discount of prior experience, modelling either limited agent memory or changes in the game conditions.
+At the core, \(\phi(t)\) depends on a surprise index \(S_{p}(t)\):
+\[\phi(t) = 1 - \frac{1}{2}S_{p}(t) ,\]
+where \(S_{p}(t)\) quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play \(h_{k}(t)\):
+\[h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k,o_{\tau})}{t}, \]
+as well as an indicator vector of the most recent opponent play:
+\[r^k(t) = I(o^k,o_{t}), \]
+Where \(I\) is the indicator function as defined above.
+To get the surprise index, we simply sum all the squared deviations between the cumulative history vector \(h^{k}(t)\) and the immediate history \(r^k(t)\):
+\[S_{p}(t) = \sum_{k=1}^{|\mathcal{A}_g|} (h^{k}(t) - r^k(t))^2 \]
+\textbf{MS: why is there a superscript in \(h^k\) and \(r^k\)? And is the indicator variable \(I(o^k = o_{t})\)? And is \(\delta_a(t)\) always 0 or 1?}
 
-As in the models above, actions are chosen based on a softmax decision rule:
-\[P_t(a,s) = \frac{\exp \{\lambda  A_{t}(a,s) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a',s) \} }\]
+For more details on the self-tuning EWA model, we refer the reader to (Teck H. Ho, Camerer, \& Chong, 2004). As in the RL model above, actions are chosen based on a softmax decision rule:
+
+\[P_t(a,s) = \frac{\exp \{\lambda  A_{t}(a,s) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a',s) \} } \]
 The self-tuning EWA has one free parameter: the inverse temperature of the softmax decision rule (\(\lambda\)).
@@
 
-For both experiments, we fitted all models to individual participant data by maximum likelihood estimation.
-\textbf{MS: need to mention the use of e.g.~DEoptim} We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
+For both experiments, we fitted all models to individual participant data by maximum likelihood estimation using the DEoptim R package (Mullen, Ardia, Gil, Windover, \& Cline, 2011).
+We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
 
-For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NBT), as well as a reinforcement learning (RL), and finally a self-tuning EWA model with the same state space (EWA).
+For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NT), as well as a reinforcement learning (RL), and finally a self-tuning EWA model with the same state space (EWA).
 
@@
 
-\textbf{MS: Please present the models in the figures in the order mentioned in text (i.e., Nash, RL, EWA, BCH), and when providing versions of each, do so in the same order as well, i.e.~x\_NT, x\_WT, x\_BT}
-
 Figure~\ref{fig:exp1-comp-models} shows the results for Experiment 1.
@@
 Only a few participants were best described by one of the BCH models or the EWA model.
-Looking at BIC weights (Figure ~\ref{fig:xp1-BIC-weigths}), we confirm this.
-RL models have high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, which fits the picture drawn by the histogram.
-\textbf{MS: The BIC weight don't add much information, so maybe we could leave them out }
 
@@
 
-\caption{Experiment 2 Histogram of best fitting computational models by condition}\label{fig:exp2-comp-models}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=\textwidth]{paper_draft_2021_files/figure-latex/xp2-BIC-weigths-1}
-
-}
-
-\caption{BIC weights for each model and participant in Experiment 2.}\label{fig:xp2-BIC-weigths}
+\caption{Experiment 2 histogram of best fitting computational models by condition.}\label{fig:exp2-comp-models}
 \end{figure}
@@
 
-\caption{Experiment 1 Likelihood by trial, game and opponent faced}\label{fig:exp1-lik-by-tr}
+\caption{Experiment 1 likelihood by trial, game and opponent faced}\label{fig:exp1-lik-by-tr}
 \end{figure}
@@
 
-The results of our first experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to a similar game.
-Performance in early rounds indicated that transfer to the more dissimilar game was moderated by the degree of sophistication of the opponent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
-In the second experiment, participants faced both types of opponents, which allows for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent within a game.
+The results of our first experiment show that the majority of participants learnt to adapt to their opponent's strategy over multiple interactions, and generalised this learning to a similar game.
+Performance in early rounds indicated that learning transfer was moderated by the degree of similarity between games.
+In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
 In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
-Experiment 2 also offers more opportunities to test transfer of a learnt opponent model.
-The results on learning transfer confirmed the findings from the first experiment.
-Again, there was clear evidence of transfer in the early rounds of the later games.
-We also found that learning transfer is moderated by the type of opponent faced: Evidence of transfer was weaker for the level-2 opponent as compared to the level-1 opponent.
-That transfer was less evident for the more sophisticated level-2 opponent in both experiments may be due to a higher difficulty of learning that opponent's strategy.
+In Experiment 2, we again found clear evidence of transfer in the early rounds of the later games.
+In addition to the moderation of transfer by the similarity between games, we also found that learning transfer was moderated by the type of opponent faced: Transfer was harder when facing the level-2 opponent as compared to the level-1 opponent.
+That evidence for transfer was weaker when facing the more sophisticated level-2 opponent may be due to a higher difficulty of learning that opponent's strategy.
 If it is more difficult to establish a model of the level-2 opponent, there is likely less knowledge to transfer to the new game.
@@
 
-What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
+What exactly did the players learn in the first game (RPS) that allowed them to beat their opponent in the later games (FWG, and Numbers or Shootout)?
 what did the players learn specifically about their opponent's strategy and what form did this learning take?
-
 One possible answer is that participants learned simple rules based on last round play.
@@
 Firstly, the learned strategies are not transferable to new games.
-There is no simple way to map ``play scissors whenever my opponent played rock in last round'' in the RPS game to ``play grass whenever my opponent played fire in last round.'' Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this quickly enough: Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
+There is no simple way to map ``play scissors whenever my opponent played rock in last round'' in the RPS game to ``play grass whenever my opponent played fire in last round.'' Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this: Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
 Secondly, a reinforcement learning strategy would fare equally well against the level-1 and level-2 opponent.
@@
 Because of the cyclicity in action choices (e.g., rock beats scissors, scissors beats paper, paper beats rock), it is possible to beat a level-2 opponent most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
-This is a rule that wins and is transferable to other games as it does not depend on action labels.
-In the same vein, a heuristic that beats a level-1 player can be stated as ``Choose the action that would have been beaten by my previous action.'' Intuitively, it seems that the heuristic for the level-2 player is simpler than that for the level-1 player, which is at odds with the difference in performance.
+This is a rule that wins and is transferable to other games, as it does not depend on action labels.
+In the same vein, a heuristic that beats a level-1 player can be stated as ``Choose the action that would have been beaten by my previous action.'' Intuitively, it seems that this heuristic for a level-2 player is simpler than that for a level-1 player, which is at odds with the finding that participants performed better against the level-1 opponent.
 
@@
 \section{References}\label{references}}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
 
@@
 
+\leavevmode\hypertarget{ref-mandler2004foundations}{}%
+Mandler, J. M. (2004). \emph{The foundations of mind: Origins of conceptual thought}. Oxford University Press.
+
 \leavevmode\hypertarget{ref-mertens1990repeated}{}%
 Mertens, J.-F. (1990). {Repeated games}. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+
+\leavevmode\hypertarget{ref-R-DEoptim}{}%
+Mullen, K., Ardia, D., Gil, D., Windover, D., \& Cline, J.
+(2011).
+{DEoptim}: An {R} package for global optimization by {D}ifferential {E}volution.
+\emph{Journal of Statistical Software}, \emph{40}(6), 1--26.
+\url{https://doi.org/10.18637/jss.v040.i06}
 
@@
 
-\endgroup
-
 \end{document}

### 2021-09-22 Report/paper_draft_2021.Rmd
ismail added effect interpretations

@@
   computer agents with human-like limited degrees of iterated reasoning. In two experiments, we find that participants
-  deviate from Nash equilibrium play and learn to adapt to their opponent's strategy to exploit it. Moreover, we show that participants transfer their learning to new games and that
-  this transfer is moderated by the level of sophistication of the opponent, as well as the similarity between games. Computational modelling shows that players start each game with a model-based
+  deviate from Nash equilibrium play and learn to adapt to their opponent's strategy to exploit it. **Moreover, we show that participants transfer their learning to new games and that
+  this transfer is moderated by the level of sophistication of the opponent (second experiment), as well as the similarity between games**.
+Computational modelling shows that players start each game with a model-based
   learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
@@
 -->
-
+```{r MIXEDexp1, include = FALSE, warning=FALSE}
+
+# tmp <- afex::aov_car(
+#   block_score ~ game.f*condition*block + Error(human_id/(game.f*block))
+#   , data=dat2
+#   , type = 3)
+
+#apa_lm1 <- apa_print(exp1_early_anova)
+
+#means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
+#trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","Numbers"))
+
+mod1 <- mixed(block_score ~ game.f*condition*block + (1 | human_id),data=dat2,check_contrasts = FALSE, type = 3, method = "KR")
+#summary(mod1)
+mod1
+
+lsmeans(mod1, pairwise~game.f*condition, adjust="tukey")
+
+library(emmeans)
+emm = emmeans(mod1, ~ game.f*condition)
+pairs(emm)
+
+# Get effect sizes from F values of mixed effect model
+library(effectsize)
+F_to_eta2(12.9, 2, 250)
+F_to_eta2(5.44, 1, 50)
+F_to_eta2(15.16, 1, 250)
+F_to_eta2(4.52, 2, 250)
+
+```
 To assess learning within and between games, we estimate a linear mixed-effects model with score as the dependent variable, and Condition (Level 1 or Level 2), Game (RPS, FWG, Numbers) and Block (first-half , second-half) as independent variables, including all main effects and interactions.
@@
 There was also an interaction between Game and Condition ($F(2,250) = 4.52$ ,  $\eta^{2} = 0.03$, $p = .01$).
-**MS: What does this interaction indicate?**
+**Post-hoc pairwise comparisons show that, for participants facing level-1 opponents, scores on the FWG game were significantly higher than RPS ($t(250) = 3.85$ , $p = .002$), and also significantly higher than Numbers ($t(250) = 3.79$ , $p = .002$).
+For participants facing level-2 opponents however, there was no significant difference between scores on the three games.**
 
@@
   ggboxplot(x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","Numbers"), fill="block", ylab = "Percentage score", xlab = "Games") +  facet_grid(. ~ condition)
-```
-
-```{r ANOVAexp1, include = FALSE, warning=FALSE}
-
-# tmp <- afex::aov_car(
-#   block_score ~ game.f*condition*block + Error(human_id/(game.f*block))
-#   , data=dat2
-#   , type = 3)
-
-mod1 <- mixed(block_score ~ game.f*condition*block + (1 | human_id),data=dat2,check_contrasts = FALSE, type = 3, method = "KR")
-#summary(mod1)
-mod1
-
-# Get effect sizes from F values of mixed effect model
-library(effectsize)
-F_to_eta2(12.9, 2, 250)
-F_to_eta2(5.44, 1, 50)
-F_to_eta2(15.16, 1, 250)
-F_to_eta2(4.52, 2, 250)
-
-#apa_lm1 <- apa_print(exp1_early_anova)
-
-#means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
-#trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","Numbers"))
-
 ```
@@
 The model also included random intercepts for participants.
-We found a main effect of Game ($F(2,240) = 6.57$, $p = .002$) and an interaction effect between Game and Opponent type ($F(2,240) = 3.34$,  $p = .037$).
+We found a main effect of Game ($F(2,240) = 6.57$, $p = .002$).
+**The effect of game reflects early scores on FWG being significantly higher than on RPS ($t(240) = 3.01$, $p = .005$) as well as scores on shootout being significantly higher than RPS ($t(240) = 3.25$, $p = .003$).
+We also found an interaction effect between Game and Opponent type ($F(2,240) = 3.34$,  $p = .037$).
+Post-hoc pairwise comparisons (p-values adjusted using Holm method for multiple comparisons) show that the difference between early scores in RPS and shootout was mostly driven by participants facing level-1 players (($t(240) = 4.12$, $p < .001$)).
+No signifcant differences were found between participants facing different opponents in the same game, or between games when facing the same opponent.**
+
 **MS: What do these effects indicate?
@@
 lme_early2
+
+lsmeans(lme_early2, pairwise~game.f*opp_type, adjust="holm")
+# lsmeans(lme_early2, pairwise~game.f, adjust="holm")
+
 ```
@@
 $$\phi(t) = 1 - \frac{1}{2}S_{p}(t) ,$$
-where $S_{p}(t)$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play $h_{k}(t)$:
-$$h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k,o_{\tau})}{t}, $$ 
+where $S_{p}(t)$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play, across opponent possible actions k, as $h^{k}(t)$:
+$$h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k=o_{\tau})}{t}, $$ 
 as well as an indicator vector of the most recent opponent play:
-$$r^k(t) = I(o^k,o_{t}), $$ 
+$$r^k(t) = I(o^k=o_{t}), $$ 
 Where $I$ is the indicator function as defined above.
 To get the surprise index, we simply sum all the squared deviations between the cumulative history vector $h^{k}(t)$ and the immediate history $r^k(t)$:
+
 $$S_{p}(t) = \sum_{k=1}^{|\mathcal{A}_g|} (h^{k}(t) - r^k(t))^2 $$
-**MS: why is there a superscript in $h^k$ and $r^k$? And is the indicator variable $I(o^k = o_{t})$? And is $\delta_a(t)$ always 0 or 1?**
+
+**MS: why is there a superscript in $h^k$ and $r^k$? ** 
+**IG : Because they depend on opponent action k**
+
+**MS: And is the indicator variable $I(o^k = o_{t})$?**
+**IG: Yes, corrected**
+
+**And is $\delta_a(t)$ always 0 or 1?**
+**IG: yes. Pls refer to: Camerer, C. F., & Ho, T. H. (2015). Behavioral game theory experiments and modeling. Handbook of game theory with economic applications, 4, 517-573.**
 

### 2021-09-22 Report/paper_draft_2021.tex
ismail added effect interpretations

--- 2021-09-16 Report/paper_draft_2021.tex
@@
 In two experiments, participants face the same opponent (Experiment 1) or the same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, the structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
-To foreshadow our results, \textbf{we find evidence that participants transfer the learned strategy of their opponent to other games, but that this transfer is moderated by the sophistication of their opponent and the similarity of the games} \textbf{IG: I guess we can still say that given findings of exp 2\ldots{}} .
+To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, and that this transfer is moderated by the sophistication of their opponent and the similarity between the games.
 Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a more habitual and cognitively less demanding strategy in the later stages of the games.
@@
 
-First,we focus on participants scores oin each game (see Figure \ref{fig:exp1-avg-scores-game}).
+First, we focus on participants scores in each game (see Figure \ref{fig:exp1-avg-scores-game}).
 On average, participants obtained the lowest score in the RPS game (\(M = 0.289\), \(SD = 0.348\)), followed by Numbers (\(M = 0.31\), \(SD = 0.347\)).
@@
 
-\textbf{To assess learning within and between games, we estimate a linear mixed effects model with the scores as the dependent variable, and Condition (Level 1 or Level 2), Game (RPS, FWG, Numbers) and Block ( first-half , second-half) as independent variables.
-Random model intercepts are assumed for participants.This showed a main effect of Game (\(F(2,250) = 12.90\), \(\eta^{2} = 0.09\), \(p < .001\)) indicating that average scores varied significantly over the games}.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game (\(t(100) =3.78\), \(p < .001\)) and the Numbers game (\(t(100) = 3.32\) , \(p = .002\)).
+To assess learning within and between games, we estimate a linear mixed-effects model with score as the dependent variable, and Condition (Level 1 or Level 2), Game (RPS, FWG, Numbers) and Block (first-half , second-half) as independent variables, including all main effects and interactions.
+The model included random intercepts for participants.
+The results show a main effect of Game (\(F(2,250) = 12.90\), \(\eta^{2} = 0.09\), \(p < .001\)) indicating that performance differs between the games.
+Post-hoc pairwise comparisons show that performance in the FWG game was significantly higher than in the RPS game (\(t(100) =3.78\), \(p < .001\)) and the Numbers game (\(t(100) = 3.32\) , \(p = .002\)).
 The score in RPS was not significantly different from the score in Numbers (\(t(100) = 0.45\) , \(p = .65\)).
@@
 Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
-\textbf{There was also an interaction effect of game by condition (\(F(2,250) = 4.52\) , \(\eta^{2} = 0.03\), \(p = .01\))}
+There was also an interaction between Game and Condition (\(F(2,250) = 4.52\) , \(\eta^{2} = 0.03\), \(p = .01\)).
+\textbf{Post-hoc pairwise comparisons show that, for participants facing level-1 opponents, scores on the FWG game were significantly higher than RPS (\(t(250) = 3.85\) , \(p = .002\)), and also significantly higher than Numbers (\(t(250) = 3.79\) , \(p = .002\)).
+For participants facing level-2 opponents however, there was no significant difference between scores on the three games.}
 
@@
 Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents.
-We estimate a linear mixed effects model with the early round scores as the dependent variable, and Condition (Level 1 or Level 2) and Game (RPS, FWG, Numbers) as independent variables.
-Random model intercepts are assumed for participants.
-We found a main effect of Game (\(F(2,100) = 3.35\), \(p = .04\)), and no main effect for condition.
+We estimates a linear mixed-effects model with the early round score as the dependent variable, and Condition (Level 1 or Level 2) and Game (RPS, FWG, Numbers), as well as their interaction, as independent variables.
+The model included random intercepts for participants.
+The results indicated a main effect of Game (\(F(2,100) = 3.35\), \(p = .04\)), but no effect for condition.
 Further investigation of the effects of game on early score using planned contrasts revealed that early scores in the FWG games are significantly higher than in the RPS ( \(t(99.99) = -2.32\), \(p = 0.02\)).
 
-To delve deeper into the differences between participants learning transfer by opponent, we ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
+We next ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG (\(t(150) = 3.96\), \(p < .001\)) and Numbers (\(t(150) = 3.74\), \(p < .001\)).
@@
 
-\textbf{To explore whether learning occurred within and between game, we estimated a mixed effect model, with the participants scores as the dependent variable and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2), Game (RPS, FWG, Shootout) and Encounter (first or second) as the independent variables.
-Random model intercepts are assumed for participants.
+To explore whether learning occurred within and between games, we estimated a linear mixed-effects model, with score as the dependent variable and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2), Game (RPS, FWG, Shootout) and Encounter (first or second) as the independent variables, including all main effects and interactions.
+The model included random intercepts for participants.
 We found a main effect of Game (\(F(2,528) = 15.32\), \(\eta^{2} = 0.04\), \(p < .001\)).
 Post-hoc pairwise comparisons between games (\(p\)-values adjusted using Holm method for multiple comparisons) indicate performance in the games increased steadily throughout the experiment, with FWG performance significantly higher than RPS (\(t(96) =2.53\), \(p = .025\)), and performance in the Shootout game significantly higher than in FWG (\(t(96) = 2.32\), \(p = .025\)).
-Whilst the mixed effect model shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type (\(F(2, 528) = 5.78\) ,\(\eta^{2} = 0.02\), \(p = .003\)).
+Whilst the model shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type (\(F(2, 528) = 5.78\) ,\(\eta^{2} = 0.02\), \(p = .003\)).
 Follow-up analysis differentiating performance by type of opponent faced shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS (\(t(191) = 2.70\), \(p = .03\)) and Shootout scores in turn significantly higher than FWG (\(t(191) = 3.05\), \(p = .01\)).
-There was no significant difference between average scores on any two games when facing level-2 agents however.}
+There was no significant difference between scores on games when facing level-2 agents however.
 
@@
 
-\textbf{To measure transfer between games, we again focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
-We estimate a linear mixed effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables.
-Random model intercepts are assumed for participants.
-We found a main effect of Game(\(F(2,240) = 6.57\), \(p = .002\)) and an interaction effect between Game and Opponent type ( \(F(2,240) = 3.34\), \(p = .037\)).}
+To measure transfer between games, we again focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
+We estimated a linear mixed-effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables, including all main effects and interactions.
+The model also included random intercepts for participants.
+We found a main effect of Game (\(F(2,240) = 6.57\), \(p = .002\)).
+\textbf{The effect of game reflects early scores on FWG being significantly higher than on RPS (\(t(240) = 3.01\), \(p = .005\)) as well as scores on shootout being significantly higher than RPS (\(t(240) = 3.25\), \(p = .003\)).
+We also found an interaction effect between Game and Opponent type (\(F(2,240) = 3.34\), \(p = .037\)).
+Post-hoc pairwise comparisons (applying Holm correction for multiple comparisons) show that the difference between early scores in RPS and shootout was mostly driven by participants facing level-1 players ((\(t(240) = 4.12\), \(p < .001\))).
+No signifcant differences were found between opponents for other games, or between games when facing the same opponent.}
+
+\textbf{MS: What do these effects indicate?
+Report post-hoc comparisons between games, and e.g.~differences between opponents for each game, here.
+The later tests against 0 are not adequate to understand the effects here.}
 
@@
 
-\textbf{The results of Experiment 2 confirm earlier results from Experiment 1 on learning transfer in a situation where participants need to learn about two distinct opponents.
+The results of Experiment 2 confirm earlier findings from Experiment 1 on learning transfer in a situation where participants need to learn about two distinct opponents.
 As in Experiment 1, participants adapted their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
 Knowledge about both types of opponents were transferred to both the similar and dissimilar game.
-This transfer was moderated by the degree of similarity between games.
-The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.}
+This transfer was moderated by the degree of similarity between games, as well as opponent type.
+The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.
 
@@
 We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
-\textbf{MS: need to better describe what \(\phi\) is, and how \(N(t)\) is determined.
-IG: done} In the earlier version of the EWA model (Camerer, Ho, \& Others, 1997), \(\phi\) and \(\delta\) were free parameters.
+
+In the earlier version of the EWA model (Camerer, Ho, \& Others, 1997), \(\phi\) and \(\delta\) were time-invariant free parameters.
 In the self-tuning EWA model (Ho et al., 2004), the values of \(\delta\) and \(\phi\) are learnt from experience.
-\(\delta\) is updated using the
-
-\[ \delta_{a}(t)  = 1  \text{  if  }  R(a,o_{t}) \geq r_{t}  \text{  and }  0 \text{  otherwise } \]
-
-\textbf{\(\phi_{t}\) can be interpreted as the discount on prior experiences, modelling either limited agent memory or changes in the game conditions.
-At the core, \(\phi_{t}\) depends on the surprise index \(S_{p}(t)\) }:
-
-\[ \phi(t) = 1 - \frac{1}{2}S_{p}(t) \]
-
-\textbf{\(S_{p}(t)\) quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play \(h_{k}(t)\)}:
-
-\[  h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k,o_{\tau})}{t} \]
-
-As well as an indicator vector of the most recent opponent play:
-
-\[r^k(t) = I(o^k,o_{t})\]
-
-\textbf{Where \(I\) is the indicator function as defined above.
-To get the surprise index, we simply sum all the squared deviations between the cumulative history vector \(h^{k}(t)\) and the immediate history \(r^k(t)\)}:
+Over time, \(\delta\) is updated as
+\[\delta_{a}(t) = \begin{cases} 1 & \text{if }  R(a,o_{t}) \geq r_{t}  \\
+0 & \text{otherwise} \end{cases}\]
+The \(\phi_{t}\) parameter can be interpreted as a discount of prior experience, modelling either limited agent memory or changes in the game conditions.
+At the core, \(\phi(t)\) depends on a surprise index \(S_{p}(t)\):
+\[\phi(t) = 1 - \frac{1}{2}S_{p}(t) ,\]
+where \(S_{p}(t)\) quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play, across strategies k, as \(h^{k}(t)\):
+\[h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k=o_{\tau})}{t}, \]
+as well as an indicator vector of the most recent opponent play:
+\[r^k(t) = I(o^k=o_{t}), \]
+Where \(I\) is the indicator function as defined above.
+To get the surprise index, we simply sum all the squared deviations between the cumulative history vector \(h^{k}(t)\) and the immediate history \(r^k(t)\):
 
@@
 
-For more details on the self-tuning EWA model, we refer the reader to (Ho et al., 2004).As in the models above, actions are chosen based on a softmax decision rule:
+\textbf{MS: why is there a superscript in \(h^k\) and \(r^k\)? }
+\textbf{IG : Because they depend on strategy k}
+
+\textbf{MS: And is the indicator variable \(I(o^k = o_{t})\)?}
+\textbf{IG: Yes, corrected}
+
+\textbf{And is \(\delta_a(t)\) always 0 or 1?}
+\textbf{IG: yes. Pls refer to: Camerer, C. F., \& Ho, T. H. (2015). Behavioral game theory experiments and modeling. Handbook of game theory with economic applications, 4, 517-573.}
+
+For more details on the self-tuning EWA model, we refer the reader to (Ho et al., 2004). As in the RL model above, actions are chosen based on a softmax decision rule:
 
@@
 
-\textbf{MS: Please present the models in the figures in the order mentioned in text (i.e., Nash, RL, EWA, BCH), and when providing versions of each, do so in the same order as well, i.e.~x\_NT, x\_WT, x\_BT.
-IG : DONE }
-
 Figure~\ref{fig:exp1-comp-models} shows the results for Experiment 1.
@@
 Only a few participants were best described by one of the BCH models or the EWA model.
-We have also estimated BIC weights for each model and we confirm that .
-RL models have high BIC weights when they best fit the participants, and very few instances have high BIC weights for models other then RL, which fits the picture drawn by the histogram.
-\textbf{IG: mentioned we looked at BIC weights and removed BIC wgt plot }
 
@@
 
-\caption{Experiment 2 Histogram of best fitting computational models by condition}\label{fig:exp2-comp-models}
+\caption{Experiment 2 histogram of best fitting computational models by condition.}\label{fig:exp2-comp-models}
 \end{figure}
@@
 The results of our first experiment show that the majority of participants learnt to adapt to their opponent's strategy over multiple interactions, and generalised this learning to a similar game.
-\textbf{Performance in early rounds indicated that learning transfer was moderated by the degree of similarity between games.
-There was not enough evidence for a difference in learning transfer between the two opponents.} In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
+Performance in early rounds indicated that learning transfer was moderated by the degree of similarity between games.
+In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
 In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
-\textbf{There was clear evidence of transfer in the early rounds of the later games.
-On top of the moderation of the transfer by degree of similarity between games, we also found that learning transfer is moderated by the type of opponent faced: Transfer was harder when facing the level-2 opponent as compared to the level-1 opponent.} That evidence for transfer was weaker when facing the more sophisticated level-2 opponent may be due to a higher difficulty of learning that opponent's strategy.
+In Experiment 2, we again found clear evidence of transfer in the early rounds of the later games.
+In addition to the moderation of transfer by the similarity between games, we also found that learning transfer was moderated by the type of opponent faced: Transfer was harder when facing the level-2 opponent as compared to the level-1 opponent.
+That evidence for transfer was weaker when facing the more sophisticated level-2 opponent may be due to a higher difficulty of learning that opponent's strategy.
 If it is more difficult to establish a model of the level-2 opponent, there is likely less knowledge to transfer to the new game.

### 2021-09-30 CBB/CBB.Rmd
CBB manuscript

--- 2021-09-22 Report/paper_draft_2021.Rmd
@@
 ---
-title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-shorttitle        : "Upgrade Report"
-
-author: 
-  - name          : "Ismail Guennouni"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
-    email         : "i.guennouni.17@ucl.ac.uk"
-  - name          : "Maarten Speekenbrink"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Experimental Psychology, University College London"
-
-# author_note: |
-  #<!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->
-
-  #Enter author note here.
+title: Transfer of Learned Opponent Models in Zero Sum Games
+subtitle: 
+titlerunning: 
+authorrunning: 
+thanks: | 
+    Grants or other notes about the article that should go on the front 
+    page should be placed here. General acknowledgments should be placed at the
+    end of the article.
+
+authors: 
+- name: Ismail Guennouni
+  address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
+  email: i.guennouni.17@ucl.ac.uk
+
+- name: Maarten Speekenbrink
+  address: Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom
+  email: m.speekenbrink@ucl.ac.uk
+
+keywords:
+- Learning Transfer
+- Opponent Modelling
+- Hidden Markov Models
+- Bayesian Cognitive Hierarchy
+
+#PACS: 
+#- PAC1
+#- superPAC
+
+# MSC:
+# - MSC code 1
+# - MSC code 2
 
 abstract: |
-  Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and 
-  causal models of the environment. One way to build abstract representations of the environment when the task involves interactions with others is to build 
-  a model of the opponent that may inform what actions they are likely to take next. In this study, we explore opponent modelling and its transfer with the use of
-  computer agents with human-like limited degrees of iterated reasoning. In two experiments, we find that participants
-  deviate from Nash equilibrium play and learn to adapt to their opponent's strategy to exploit it. **Moreover, we show that participants transfer their learning to new games and that
-  this transfer is moderated by the level of sophistication of the opponent (second experiment), as well as the similarity between games**.
-Computational modelling shows that players start each game with a model-based
-  learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
-
-# keywords          : "keywords"
-# wordcount         : "X"
-
-bibliography      : ["Mendeley2.bib"]
-csl               : "apa-6th-edition.csl"
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : no
-linkcolor         : "blue"
-mask              : no
-draft             : no
-fig_caption       : yes
-
-documentclass     : "apa6"
-# classoption       : a4paper
-classoption       : man
-output            : papaja::apa6_pdf
-header-includes:
-  - \shorttitle{}
+  Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and causal models of the environment.
+One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the opponent that may inform what actions they are likely to take next.
+In this study, we explore opponent modelling and its transfer with the use of computer agents with human-like limited degrees of iterated reasoning.
+In two experiments, we find that participants deviate from Nash equilibrium play and learn to adapt to their opponent's strategy to exploit it.
+Moreover, we show that participants transfer their learning to new games and that this transfer is moderated by the level of sophistication of the opponent (second experiment), as well as the similarity between games.
+Computational modelling shows that players start each game with a model-based learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
+
+bibliography: Mendeley2.bib
+biblio-style: spphys
+# bibstyle options spbasic(default), spphys, spmpsci
+output: rticles::springer_article
 ---
+```{r setup, include=FALSE}
+knitr::opts_knit$set(root.dir = '../Report')
+knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(out.width = "\\textwidth")
+```
 
@@
 library(depmixS4)
+library(flextable)
 
@@
 The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.
-Nash equilibrium play) or use salient actions (e.g.
-risk dominance) in later games, having had experience with a similar game environment previously [@ho1998iterated; @knez2000].
+Nash equilibrium play) or use salient (e.g.
+risk dominance) actions in later games, having had experience with a similar game environment previously [@ho1998iterated; @knez2000].
 As is well-known, a Nash equilibrium means that all players in a game act such that no-one can unilaterally improve their performance by deviating from their strategy.
@@
 Studies that focused on whether people can learn to exploit deviations from Nash-equilibrium play have mostly looked at the ability of players to detect and exploit action-based learning rules [@spiliopoulos2013strategic; @shachat2004we].
-These studies used computer opponents that don't adapt play to their human opponent, mostly consisting of playing each action with a fixed probability (a mixed strategy).
+These studies used computer opponents that don't adapt play to their human opponent, mostly consisting of playing each action with a fixed probability (a mixed strategy) or using a pre-determined sequence.
 Findings showed that humans are capable of adapting to non-Nash-equilibrium play and detect patterns in an opponent's history of play.
 However, the use of mixed strategies may have limited people's ability to form accurate opponent models.
+
 Instead of thinking of their opponents as drawing random actions from a (non-uniform) probability distribution, people may rather think of their opponents as applying a form of iterated reasoning to determine their next action.
@@
 Iterative reasoning strategies can explain non-equilibrium play in a range of games, such as the $p$-beauty contest game [@nagel1995unraveling], dominance solvable games [@camerer2004cognitive], and various standard normal form games [@costa2001cognition].
-In the present study, we endow our computer opponents with limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
+In the present study, we endow our computer opponents with a limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
 In two experiments, participants face the same opponent (Experiment 1) or the same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, the structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
@@
 # Experiment 1
-
 In the first experiment, we aim to test learning transfer by making participants face the same computer opponent with a limited level of iterative reasoning in three sequential games that vary in similarity.
@@
 ### Tasks
-
 Participants played the three games against their computer opponent.
@@
 The choice of this type of strategy is consistent with evidence that humans strategically use information from last round play of their opponents in zero-sum games [@batzilis; @wang2014social].
-Table \@ref(table:1) shows an example of the computer opponent's actions in response to the previous round play.
-
-\begin{table}[bth!]
-\caption{Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round.}
-\centering
-\label{table:1}
-\begin{tabular}{||c c | c c||} 
- \hline
- Human action $t-1$ & Computer action $t-1$  & Computer level-1 action $t$ & Computer level-2 action $t$ \\ [0.5ex] 
- \hline\hline
- Paper & Rock & Scissors & Scissors \\ 
- Scissors  & Scissors & Rock & Paper \\
- Rock & Paper & Paper & Rock \\
- ... & ... & ... & ... \\ [1ex] 
- \hline
-\end{tabular}
-\end{table}
+Table \ref{tab:table-actions} shows an example of the computer opponent's actions in response to the previous round play.
+
+```{r table-actions, warning = FALSE, ft.align="center", tab.id='table-actions', label='table-actions'}
+library(flextable)
+df <- data.frame( c("Paper","Scissors","Rock","..."),
+                  c("Rock","Scissors","Paper","..."),
+                  c("Scissors","Rock","Paper","..."),
+                  c("Scissors","Paper","Rock","..."))
+colnames(df) <- c("Human action t-1","Computer action t-1","Computer level-1 action t", "Computer level-2 action t")
+
+knitr::kable(df,booktabs = TRUE,
+  caption = 'Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round', ) %>% kable_styling(latex_options="scale_down")
+# df <- flextable(df)
+# df <- set_caption(df, "Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round")
+#   autonum = run_autonum(seq_id = "tab", bkm = "actions"))
+
+# df <- autofit(df)
+# df
+```
+
+<!-- \begin{table}[bth!] -->
+<!-- \caption{Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round.} -->
+<!-- \centering -->
+<!-- \label{table:1} -->
+<!-- \begin{tabular}{||c c | c c||} -->
+<!--  \hline -->
+<!--  Human action $t-1$ & Computer action $t-1$  & Computer level-1 action $t$ & Computer level-2 action $t$ \\ [0.5ex] -->
+<!--  \hline\hline -->
+<!--  Paper & Rock & Scissors & Scissors \\ -->
+<!--  Scissors  & Scissors & Rock & Paper \\ -->
+<!--  Rock & Paper & Paper & Rock \\ -->
+<!--  ... & ... & ... & ... \\ [1ex] -->
+<!--  \hline -->
+<!-- \end{tabular} -->
+<!-- \end{table} -->
 
@@
 They then played the three games against their opponent in the order RPS, FGW, and Numbers.
-An example of the interface for the RPS game is provided in Figure\ \@ref(fig:feedback-rps-exp2).
-On each round, the human player chooses an action, and after a random delay (between 0.5 and 3 seconds) is shown the action chosen by the computer opponent and the outcome of that round.A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
+An example of the interface for the RPS game is provided in Figure \ref{fig:feedback-rps-exp2}.
+On each round, the human player chooses an action, and after a random delay (between 0.5 and 3 seconds) is shown the action chosen by the computer opponent and the outcome of that round.
+A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
 The score was calculated as the number of wins minus the number of losses.
@@
 
-```{r feedback-rps-exp2, fig.cap = "Screenshot of the Rock-Paper-Scissors game in Experiment 2.
+```{r feedback-rps-exp2,fig.cap = "Screenshot of the Rock-Paper-Scissors game in Experiment 2.
 Shown here is the feedback stage, after both the human (left) and computer (right) players have chosen their action.
@@
 
-knitr::include_graphics("images/feedback_rps.png")
-
-```
-
-### Results
+knitr::include_graphics("../Report/images/feedback_rps.png")
+
+```
 
@@
 ```
+
+## Results
+
 First, we focus on participants scores in each game (see Figure \ref{fig:exp1-avg-scores-game}).
@@
 
-lsmeans(mod1, pairwise~game.f*condition, adjust="tukey")
-
-library(emmeans)
-emm = emmeans(mod1, ~ game.f*condition)
-pairs(emm)
+mod.lsm <- lsmeans(mod1, ~ game.f*condition, adjust="holm")
+
+#contrast(mod.lsm, "consec",simple = "each",combine = TRUE, adjust = "tukey")
+#contrast(mod.lsm, interaction = c("game.f", "condition"))
 
@@
 The model included random intercepts for participants.
-The results show a main effect of Game ($F(2,250) = 12.90$, $\eta^{2}  = 0.09$,  $p < .001$) indicating that performance differs between the games.
+The results show a main effect of Game ($F(2,250) = 12.90$, $\eta^{2}  = 0.09$,  $p < .001$).
 Post-hoc pairwise comparisons show that performance in the FWG game was significantly higher than in the RPS game ($t(100) =3.78$, $p < .001$) and the Numbers game ($t(100) = 3.32$ , $p = .002$).
@@
 There was also an interaction between Game and Condition ($F(2,250) = 4.52$ ,  $\eta^{2} = 0.03$, $p = .01$).
-**Post-hoc pairwise comparisons show that, for participants facing level-1 opponents, scores on the FWG game were significantly higher than RPS ($t(250) = 3.85$ , $p = .002$), and also significantly higher than Numbers ($t(250) = 3.79$ , $p = .002$).
-For participants facing level-2 opponents however, there was no significant difference between scores on the three games.**
+Post-hoc pairwise comparisons ($p$-values adjusted using Holm method for multiple comparisons) show that, for participants facing level-1 opponents, scores on the FWG game were significantly higher than those for both RPS ($t(250) = 3.85$ , $p = .002$), and Numbers ($t(250) = 3.79$ , $p = .002$).
+For participants facing level-2 opponents however, there was no significant difference between scores on the three games.
 
@@
 
-### Learning transfer
+## Learning transfer
 
@@
 Scores in this game were indeed not significantly different from 0 ($t(148.85) = 1.04$ , $p = .89$).
-
 ```{r exp1-early-rounds, include=FALSE}
@@
 
-<!-- To delve deeper into the differences between participants learning transfer by opponent,--> We next ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
+We next ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
 For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ($t(150) = 3.96$, $p < .001$) and Numbers ($t(150) = 3.74$, $p < .001$).
@@
 
-### Discussion
+## Discussion
 
@@
 To perform well against both opponents, participants would need to learn distinct strategies against these opponents.
-To reduce effects of increased memory load due to facing distinct opponents, we provided participants access to the history of play against an opponent within each game (see Figure \@ref(fig:feedback-rps-exp2)).
+To reduce effects of increased memory load due to facing distinct opponents, we provided participants access to the history of play against an opponent within each game (see Figure \ref{fig:feedback-rps-exp2}).
 Finally, we changed the third game to a penalty Shootout game, with participants aiming to score a goal and opponents playing the role of goal keepers.
@@
 ## Methods 
-
 ### Participants & Design 
-
 A total of 48 participants (21 females, 28 males, 1 unknown) were recruited via the Prolific platform, none of which took part in Experiment 1.
@@
 ### Tasks
-
 Participants played three games: Rock-Paper-Scissors (RPS), Fire-Water-Grass (FWG), and the penalty Shootout game.
@@
 There is no possibility of ties in this game.
-Figure\ \@ref(fig:screenshot-shootout) shows a snapshot of play in the Shootout game.
+Figure \ref{fig:screenshot-shootout} shows a snapshot of play in the Shootout game.
 What makes this game different to the other games is that there are now two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend "right" in the next round, they can win by either choosing to shoot "left" or "center".
@@
 
-knitr::include_graphics("images/shootout.jpg")
+knitr::include_graphics("../Report/images/shootout.jpg")
 ```
@@
 ### Procedure 
-
 Participants played 3 games sequentially against both level-1 and level-2 computer opponents.
@@
 
-## Results
-
 ```{r load_exp2_data , include=FALSE}
@@
 ```
-
+## Results
 Participants' scores are depicted in Figure \ref{fig:exp2-score-by-opp}.
@@
 
-### Learning transfer
-
+## Learning transfer
+To measure transfer between games, we again focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
+We estimated a linear mixed-effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables, including all main effects and interactions.
+The model also included random intercepts for participants.
+We found a main effect of Game ($F(2,240) = 6.57$, $p = .002$).
+The effect of game reflects early scores on FWG being significantly higher than on RPS ($t(240) = 3.01$, $p = .005$) as well as scores on shootout being significantly higher than RPS ($t(240) = 3.25$, $p = .003$).
+We also found an interaction effect between Game and Opponent type ($F(2,240) = 3.34$,  $p = .037$).
+Post-hoc pairwise comparisons (p-values adjusted using Holm method for multiple comparisons) show that the difference between early scores in RPS and shootout was mostly driven by participants facing level-1 players (($t(240) = 4.12$, $p < .001$)).
+No signifcant differences were found between participants facing different opponents in the same game, or between games when facing the same opponent.
 ```{r, include=FALSE}
@@
 
-To measure transfer between games, we again focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
-We estimated a linear mixed-effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables, including all main effects and interactions.
-The model also included random intercepts for participants.
-We found a main effect of Game ($F(2,240) = 6.57$, $p = .002$).
-**The effect of game reflects early scores on FWG being significantly higher than on RPS ($t(240) = 3.01$, $p = .005$) as well as scores on shootout being significantly higher than RPS ($t(240) = 3.25$, $p = .003$).
-We also found an interaction effect between Game and Opponent type ($F(2,240) = 3.34$,  $p = .037$).
-Post-hoc pairwise comparisons (p-values adjusted using Holm method for multiple comparisons) show that the difference between early scores in RPS and shootout was mostly driven by participants facing level-1 players (($t(240) = 4.12$, $p < .001$)).
-No signifcant differences were found between participants facing different opponents in the same game, or between games when facing the same opponent.**
-
-**MS: What do these effects indicate?
-Report post-hoc comparisons between games, and e.g.
-differences between opponents for each game, here.
-The later tests against 0 are not adequate to understand the effects here.**
-
 ```{r, include = FALSE}
@@
 
-### Discussion
-
+## Discussion
 The results of Experiment 2 confirm earlier findings from Experiment 1 on learning transfer in a situation where participants need to learn about two distinct opponents.
@@
 ## Reinforcement learning (RL) model
-
 We first consider a model-free reinforcement learning algorithm, where actions that have led to positive rewards are reinforced, and the likelihood of actions that led to a negative reward is lowered.
@@
 $$P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}, $$ 
-where the inverse temperature parameter $\lambda$ determines the consistency of the strategy (the higher $\lambda$, the more often the action with the highest $Q$-value is chosen.
+where the inverse temperature parameter $\lambda$ determines the consistency of the strategy (the higher $\lambda$, the more often the action with the highest $Q$-value is chosen).
 While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different state space $\mathcal{S}_g$ and action space $\mathcal{A}_g$, and there is no simple way to map states and actions across games.
-
 The RL model has two free parameters: the learning rate ($\alpha$) and the inverse temperature ($\lambda$).
-<!-- We've assumed $\gamma = 0$ as changes in this parameter didn't affect the other parameter estimations or ultimately the value of the likelihoods.
--->
 
 ## Experience-weighted attraction (EWA) model
-
 The self-tuning Experience Weighted Attraction (EWA) model [@ho2004economics] combines two seemingly different approaches, namely reinforcement learning and belief learning.
@@
 $$ A_{t+1}(a,s) =  \frac{\phi(t) \ N(t) \ A_{t}(a,s) + [ \delta_{a}(t) + (1-\delta_{a}(t)) \ I(a_t = a )] \ R(a,o_t) } {\phi(t)N(t) + 1} $$
-where $I(x)$ is an indicator function which takes the value 1 is its argument is true and 0 otherwise, and $R(a,o_t)$ is the reward that would be obtained from playing action $a$ against opponent action $o_t$.
+where $I(x)$ is an indicator function which takes the value 1 if its argument is true and 0 otherwise, and $R(a,o_t)$ is the reward that would be obtained from playing action $a$ against opponent action $o_t$.
 $R(a,o_t)$ equals the actual obtained reward when $a = a_t$, and otherwise is a counterfactual reward that would have been obtained if a different action were taken.
@@
 where $S_{p}(t)$ quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play, across opponent possible actions k, as $h^{k}(t)$:
-$$h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k=o_{\tau})}{t}, $$ 
+$$h^{k}(t)= \frac{ \sum_{\tau = 1}^t  I( o_{\tau} = o^k )} {t}, $$ 
 as well as an indicator vector of the most recent opponent play:
@@
 
-**MS: why is there a superscript in $h^k$ and $r^k$? ** 
-**IG : Because they depend on opponent action k**
-
-**MS: And is the indicator variable $I(o^k = o_{t})$?**
-**IG: Yes, corrected**
-
-**And is $\delta_a(t)$ always 0 or 1?**
-**IG: yes. Pls refer to: Camerer, C. F., & Ho, T. H. (2015). Behavioral game theory experiments and modeling. Handbook of game theory with economic applications, 4, 517-573.**
-
 For more details on the self-tuning EWA model, we refer the reader to [@ho2004economics]. As in the RL model above, actions are chosen based on a softmax decision rule:
@@
 
-\subsection{Bayesian Cognitive Hierarchy (BCH) model}
+## Bayesian Cognitive Hierarchy (BCH) model
 
@@
 P_t(a) &= \frac{\exp\{\lambda B_t(a) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{ \lambda B_t(a')\}} \end{aligned}$$
-where $b(a,o) = 1$ if action $a$ is a best response to opponent's action $o$ (i.e.
-it leads to a win).
-<!-- and $P_k(o|a_{t-1},o_{t-1}) = \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o|a_{t-1},o_{t-1})$ is the probability that a level $k$ agent takes action $o$, as also used in the likelihood above.-->
+where $b(a,o) = 1$ if action $a$ is a best response to opponent's action $o$ (i.e. it leads to a win).
 
@@
 ## Estimation and model comparison
-
 For both experiments, we fitted all models to individual participant data by maximum likelihood estimation using the DEoptim R package [@R-DEoptim].
 We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
-<!--, the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
--->
-
 For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NT), as well as a reinforcement learning (RL), and finally a self-tuning EWA model with the same state space (EWA).
-
 In Experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two types of opponent model transfer.
@@
 
-Figure\ \@ref(fig:exp1-comp-models)  shows the results for Experiment 1.
+Figure \ref{fig:exp1-comp-models}  shows the results for Experiment 1.
 We can see that the RL model clearly described most participants' behaviour best, followed by the random (Nash) model.
@@
 
-(ref:figure9-caption) Model BIC weights for participants in Experiment 1.
+<!-- (ref:figure9-caption) Model BIC weights for participants in Experiment 1. -->
 ```{r, include = FALSE, xp1-BIC-weigths, fig.cap="(ref:figure9-caption)", fig.align="center"}
@@
 
-In Experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that the RL model was again more successful than the Bayesian Cognitive Hierarchy models (with or without transfer) and the EWA model in fitting participants' action choices.
+In Experiment 2, we can see from Figure \ref{fig:exp2-comp-models} that the RL model was again more successful than the Bayesian Cognitive Hierarchy models (with or without transfer) and the EWA model in fitting participants' action choices.
 <!--  In Experiment 2 when participants faced both level-1 and level-2 agents sequentially, the Bayesian models (with or without transfer) did not fit players observed data as well.
@@
 
-```{r exp2-comp-models, fig.cap = "Experiment 2 histogram of best fitting computational models by condition.", out.width="\\textwidth", fig.align='center'}
+```{r exp2-comp-models, fig.cap = "Experiment 2 - Histogram of best fitting computational models by condition.", out.width="\\textwidth", fig.align='center'}
 
@@
 
-(ref:my-table2-caption) Experiment 2 BIC weights and number of participants best fit by model.
+<!-- (ref:my-table2-caption) Experiment 2 BIC weights and number of participants best fit by model. -->
 ```{r exp2-weights-table, results="asis", echo=FALSE, include =FALSE}
@@
 
-(ref:figure11-caption) BIC weights for each model and participant in Experiment 2.
+<!-- (ref:figure11-caption) BIC weights for each model and participant in Experiment 2. -->
 ```{r, include = FALSE, xp2-BIC-weigths, fig.cap="(ref:figure11-caption)", fig.align="center", out.width="\\textwidth"}
@@
 ## Using Hidden Markov Model to explore strategy switching
-
 The computational modelling indicates that most players are best fit by a reinforcement learning which learns good actions conditional upon the last round play.
@@
 In order to investigate this discrepancy further, we plot the likelihood by trial for each game and three strategies: reinforcement learning (RL), Bayesian Cognitive Hierarchy with between-game transfer (BCH\_BT), and the random (Nash) strategy.
-Figure\ \@ref(fig:exp1-lik-by-tr) shows that in the initial rounds of the the later games in Experiment 1, the likelihood for the BCH models is higher than that of the other models.
-However, over time, the likelihood of the RL model increases and exceeds that of BCH model.
+Figure \ref{fig:exp1-lik-by-tr} shows that in the initial rounds of the the later games in Experiment 1, the likelihood for the BCH models is higher than that of the other models.
+However, over time, the likelihood of the RL model increases and exceeds that of the BCH model.
 ```{r, include= FALSE}
@@
 ```
-The same pattern holds for Experiment 2 (Figure\ \@ref(fig:exp2-lik-by-tr)).
+The same pattern holds for Experiment 2 (Figure \ref{fig:exp2-lik-by-tr}).
 Again, the BCH\_BT model with between-game transfer has the highest likelihood in the early stages of the later games (apart from stage 1 of the shootout game, where the RL model is better).
@@
 
-```{r exp1-posteriors-plot, fig.cap = "Experiment1 posterior probability of strategies by game and opponent faced", fig.align ='center'}
+```{r exp1-posteriors-plot, fig.cap = "Experiment 1 posterior probability of strategies by game and opponent faced", fig.align ='center'}
 
@@
 <!-- **MS: we should really use a bootstrapped Likelihood Ratio test here ** --> This provides further statistical evidence in favour of the hypothesis that participants switch between strategies.
-Figure\ \@ref(fig:exp1-posteriors-plot) depicts the average (across participants) posterior probabilities of each state (strategy), as a function of trial and opponent faced.
+Figure \ref{fig:exp1-posteriors-plot} depicts the average (across participants) posterior probabilities of each state (strategy), as a function of trial and opponent faced.
 As can be seen, there is evidence of strategy switching in the FWG and Numbers games: Initially, participants appear to use a random strategy (in the first round of a game, there is no way to predict the opponent's action), after which the BCH strategy becomes dominant.
@@
 
-```{r exp2-posteriors-plot, fig.cap = "Experiment2 likelihood by trial by game and opponent faced", fig.align ='center'}
+```{r exp2-posteriors-plot, fig.cap = "Experiment 2 posterior probability of strategies by game and opponent faced", fig.align ='center'}
 
@@
 In Experiment 2, the switching model (AIC = `r round(-2*as.numeric(logLik(fmod2)) + 2*8,2)`, BIC = `r round(-2*as.numeric(logLik(fmod2)) + 8*log(nrow(fmod2@dens)),2)`) again fits better than the restricted non-switching model (AIC = `r round(-2*as.numeric(logLik(fmod2_noswitch)) + 2*2,2)`, BIC = `r round(-2*as.numeric(logLik(fmod2_noswitch)) + 2*log(nrow(fmod2_noswitch@dens)),2)`), $\chi^2(6) = `r round(-2*as.numeric(logLik(fmod2_noswitch)) - (-2*as.numeric(logLik(fmod2))),2)`$, $p < .001$.
-The posterior probabilities of the strategies (Figure\ \@ref(fig:exp2-posteriors-plot)) show very clear evidence of strategy switching across games and stages, from using a BCH model in the initial rounds to an RL strategy later on.
+The posterior probabilities of the strategies (Figure \ref{fig:exp2-posteriors-plot}) show very clear evidence of strategy switching across games and stages, from using a BCH model in the initial rounds to an RL strategy later on.
 
@@
 What exactly did the players learn in the first game (RPS) that allowed them to beat their opponent in the later games (FWG, and Numbers or Shootout)?
-what did the players learn specifically about their opponent's strategy and what form did this learning take?
+What did the players learn specifically about their opponent's strategy and what form did this learning take?
 One possible answer is that participants learned simple rules based on last round play.
@@
 Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl [@stahl2000rule; @stahl2003sophisticated].
+
 We admit that our implementation in the BCH models does not predict a performance difference between the types of opponents.
@@
 
-```{r create_r-references}
-#r_refs(file = "Mendeley2.bib")
-```
-
-<!-- \begingroup -->
-<!-- \setlength{\parindent}{-0.5in} -->
-<!-- \setlength{\leftskip}{0.5in} -->
-<!-- <div id = "refs"></div> -->
-<!-- \endgroup -->
+```{r create_r-references, warning= FALSE}
+r_refs(file = "Mendeley2.bib")
+```

### 2021-09-30 CBB/CBB.tex
CBB manuscript

--- 2021-09-22 Report/paper_draft_2021.tex
@@
-\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
+% !TeX program = pdfLaTeX
+\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
 %
-\documentclass[english,man,floatsintext]{apa6}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
+\smartqed  % flush right qed marks, e.g. at end of proof
+%
+\usepackage{amsmath}
+\usepackage{graphicx}
 \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provides euro and other symbols
-\else % if luatex or xelatex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage[]{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\usepackage{xcolor}
+
+\usepackage[hyphens]{url} % not crucial - just used below for the URL
 \usepackage{hyperref}
-\hypersetup{
-            pdftitle={Transfer of Learned Opponent Models in Zero Sum Games},
-            pdfauthor={Ismail Guennouni1 \& Maarten Speekenbrink1},
-            colorlinks=true,
-            linkcolor=blue,
-            filecolor=Maroon,
-            citecolor=Blue,
-            urlcolor=Blue,
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
-
-% Table formatting
+
+%
+% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
+%
+% insert here the call for the packages your document requires
+%\usepackage{latexsym}
+% etc.
+%
+% please place your own definitions here and don't use \def but
+% \newcommand{}{}
+%
+% Insert the name of "your journal" with
+% \journalname{myjournal}
+%
+
+%% load any required packages here
+
+% Pandoc citation processing
+
+\usepackage{booktabs}
 \usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
-
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
-\shorttitle{Upgrade Report}
-\usepackage{csquotes}
-\shorttitle{}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[shorthands=off,main=english]{babel}
-\else
-  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\fi
-
-\title{Transfer of Learned Opponent Models in Zero Sum Games}
-\author{Ismail Guennouni\textsuperscript{1} \& Maarten Speekenbrink\textsuperscript{1}}
-\date{}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Experimental Psychology, University College London}
-
-\abstract{
-Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and
-causal models of the environment. One way to build abstract representations of the environment when the task involves interactions with others is to build
-a model of the opponent that may inform what actions they are likely to take next. In this study, we explore opponent modelling and its transfer with the use of
-computer agents with human-like limited degrees of iterated reasoning. In two experiments, we find that participants
-deviate from Nash equilibrium play and learn to adapt to their opponent's strategy to exploit it. Moreover, we show that participants transfer their learning to new games and that
-this transfer is moderated by the level of sophistication of the opponent, as well as the similarity between games. Computational modelling shows that players start each game with a model-based
-learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+
+\begin{document}
+
+\title{Transfer of Learned Opponent Models in Zero Sum Games \thanks{Grants or other notes about the article that should go on the front page
+should be placed here. General acknowledgments should be placed at the
+end of the article.} }
+
+\author{  Ismail Guennouni \and  Maarten Speekenbrink \and  }
+
+\institute{
+        Ismail Guennouni \at
+     Department of Experimental Psychology, University College London, 26
+ Bedford Way, London WC1H 0AP, United Kingdom \\
+     \email{\href{mailto:i.guennouni.17@ucl.ac.uk}{\nolinkurl{i.guennouni.17@ucl.ac.uk}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
+        Maarten Speekenbrink \at
+     Department of Experimental Psychology, University College London, 26
+ Bedford Way, London WC1H 0AP, United Kingdom \\
+     \email{\href{mailto:m.speekenbrink@ucl.ac.uk}{\nolinkurl{m.speekenbrink@ucl.ac.uk}}}  %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+    \and
     }
 
-\begin{document}
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
+
 \maketitle
+
+\begin{abstract}
+Human learning transfer abilities take advantage of important cognitive
+building blocks such as an abstract representation of concepts
+underlying tasks and causal models of the environment. One way to build
+abstract representations of the environment when the task involves
+interactions with others is to build a model of the opponent that may
+inform what actions they are likely to take next. In this study, we
+explore opponent modelling and its transfer with the use of computer
+agents with human-like limited degrees of iterated reasoning. In two
+experiments, we find that participants deviate from Nash equilibrium
+play and learn to adapt to their opponent's strategy to exploit it.
+Moreover, we show that participants transfer their learning to new games
+and that this transfer is moderated by the level of sophistication of
+the opponent (second experiment), as well as the similarity between
+games. Computational modelling shows that players start each game with a
+model-based learning strategy that facilitates between-game transfer of
+their opponent's strategy, but then switch to behaviour that is
+consistent with a model-free learning strategy in the latter stages of
+the interaction.
+\\
+\keywords{
+        Learning Transfer \and
+        Opponent Modelling \and
+        Hidden Markov Models \and
+        Bayesian Cognitive Hierarchy \and
+    }
+
+\end{abstract}
+
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
 
@@
 
-Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
-This ability relies on important cognitive building blocks, such as an abstract representation of concepts underlying tasks (Lake, Ullman, Tenenbaum, \& Gershman, 2017).
-One way to form these representations when the task involves interactions with others, is to build a model of the person we are interacting with that offers predictions of the actions they are likely to take next.
-There is evidence that people learn such models of their opponents when playing repeated economic games (Stahl \& Wilson, 1995).
-
-A model of the opponent can help increase performance in a particular game, but learning more general characteristics of an opponent may also help increase performance in other games.
-In this paper, we are specifically interested in the latter: How do people build and use models of their opponent to facilitate learning transfer?
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about their opponent's strategies and preferences (Mertens, 1990) are particularly useful to address this question.
-The early literature on learning transfer in repeated games has mostly focused on the proportion of people who play normatively optimal (e.g.~Nash equilibrium play) or use salient actions (e.g.~risk dominance) in later games, having had experience with a similar game environment previously (Camerer \& Knez, 2000; Ho, Camerer, \& Weigelt, 1998).
-As is well-known, a Nash equilibrium means that all players in a game act such that no-one can unilaterally improve their performance by deviating from their strategy.
-When playing against an opponent with a Nash-optimal strategy, I can do no better than play according to the Nash-equilibrium strategy as well.
-However, when faced with a player who deviates from the Nash-optimal strategy, I may be able to exploit this and also deviate from this strategy, increasing my performance beyond what is expected at Nash equilibrium.
-Of course, this comes with some risk, as my own deviation from Nash-optimal play may leave me open to similar exploitation.
-
-Studies that focused on whether people can learn to exploit deviations from Nash-equilibrium play have mostly looked at the ability of players to detect and exploit action-based learning rules (Shachat \& Swarthout, 2004; Spiliopoulos, 2013).
-These studies used computer opponents that don't adapt play to their human opponent, mostly consisting of playing each action with a fixed probability (a mixed strategy).
-Findings showed that humans are capable of adapting to non-Nash-equilibrium play and detect patterns in an opponent's history of play.
-However, the use of mixed strategies may have limited people's ability to form accurate opponent models.
-Instead of thinking of their opponents as drawing random actions from a (non-uniform) probability distribution, people may rather think of their opponents as applying a form of iterated reasoning to determine their next action.
-The type of reasoning we refer to takes the form of \enquote{I believe that you believe that I believe \ldots{}} and has been shown to underlie people's decisions in economic games (Camerer, 2003; Costa-Gomes, Crawford, \& Broseta, 2001).
-It also underlies successful models in behavioural economics, such as Level-\(k\) and Cognitive Hierarchy models (Camerer, Ho, \& Chong, 2004), which posit that people assume their opponent applies a limited level of iterative reasoning, taking actions that are best responses to those of their (modelled) opponent.
-
-In Level-\(k\) theory, a level-0 player uses a fixed strategy without explicitly considering the strategy of their opponent.
-A level-1 player assumes their opponent is a level-0 player, and chooses actions to best respond to the strategy of their opponent, without considering what their opponent might believe that they will play.
-A level-2 player, on the other hand, takes their opponent's belief about their actions into account, assuming they face a level-1 player, and choosing actions to best respond to the actions of that player.
-Cognitive Hierarchy theory is based on similar principles, but rather than assuming an opponent always adopts a particular level-\(k\) strategy, they are assumed to adopt each of the level-\(k\) strategies with a particular probability (i.e., the opponent's strategy is a mixture over pure level-\(k\) strategies).
-
-Iterative reasoning strategies can explain non-equilibrium play in a range of games, such as the \(p\)-beauty contest game (Nagel, 1995), dominance solvable games (Camerer et al., 2004), and various standard normal form games (Costa-Gomes et al., 2001).
-In the present study, we endow our computer opponents with limited ability for iterative reasoning and assess whether (1) human players adapt their strategy to exploit this limited reasoning of their opponent, and (2) whether they are able to generalize a learned opponent model to other games.
-In two experiments, participants face the same opponent (Experiment 1) or the same two opponents (Experiment 2) in three consecutive games: the well-known Rock-Paper-Scissors game, the structurally similar Fire-Water-Grass game, and a less similar Numbers (Experiment 1) or Shootout (Experiment 2) game.
-To foreshadow our results, we find evidence that participants transfer the learned strategy of their opponent to other games, and that this transfer is moderated by the sophistication of their opponent and the similarity between the games.
-Moreover, using computational modelling, we find evidence that participants switch from relying on an opponent model in the early stages of the games, to a more habitual and cognitively less demanding strategy in the later stages of the games.
+Being able to transfer previously acquired knowledge to a new domain is
+one of the hallmarks of human intelligence. This ability relies on
+important cognitive building blocks, such as an abstract representation
+of concepts underlying tasks (Lake et al. 2017). One way to form these
+representations when the task involves interactions with others, is to
+build a model of the person we are interacting with that offers
+predictions of the actions they are likely to take next. There is
+evidence that people learn such models of their opponents when playing
+repeated economic games (Stahl and Wilson 1995).
+
+A model of the opponent can help increase performance in a particular
+game, but learning more general characteristics of an opponent may also
+help increase performance in other games. In this paper, we are
+specifically interested in the latter: How do people build and use
+models of their opponent to facilitate learning transfer? Repeated
+games, in which players interact repeatedly with the same opponent and
+have the ability to learn about their opponent's strategies and
+preferences (Mertens 1990) are particularly useful to address this
+question. The early literature on learning transfer in repeated games
+has mostly focused on the proportion of people who play normatively
+optimal (e.g.~Nash equilibrium play) or use salient (e.g.~risk
+dominance) actions in later games, having had experience with a similar
+game environment previously (Ho, Camerer, and Weigelt 1998; Camerer and
+Knez 2000). As is well-known, a Nash equilibrium means that all players
+in a game act such that no-one can unilaterally improve their
+performance by deviating from their strategy. When playing against an
+opponent with a Nash-optimal strategy, I can do no better than play
+according to the Nash-equilibrium strategy as well. However, when faced
+with a player who deviates from the Nash-optimal strategy, I may be able
+to exploit this and also deviate from this strategy, increasing my
+performance beyond what is expected at Nash equilibrium. Of course, this
+comes with some risk, as my own deviation from Nash-optimal play may
+leave me open to similar exploitation.
+
+Studies that focused on whether people can learn to exploit deviations
+from Nash-equilibrium play have mostly looked at the ability of players
+to detect and exploit action-based learning rules (Spiliopoulos 2013;
+Shachat and Swarthout 2004). These studies used computer opponents that
+don't adapt play to their human opponent, mostly consisting of playing
+each action with a fixed probability (a mixed strategy) or using a
+pre-determined sequence. Findings showed that humans are capable of
+adapting to non-Nash-equilibrium play and detect patterns in an
+opponent's history of play. However, the use of mixed strategies may
+have limited people's ability to form accurate opponent models.
+
+Instead of thinking of their opponents as drawing random actions from a
+(non-uniform) probability distribution, people may rather think of their
+opponents as applying a form of iterated reasoning to determine their
+next action. The type of reasoning we refer to takes the form of ``I
+believe that you believe that I believe \ldots{}'' and has been shown to
+underlie people's decisions in economic games (Camerer 2003;
+Costa-Gomes, Crawford, and Broseta 2001). It also underlies successful
+models in behavioural economics, such as Level-\(k\) and Cognitive
+Hierarchy models (Camerer, Ho, and Chong 2004), which posit that people
+assume their opponent applies a limited level of iterative reasoning,
+taking actions that are best responses to those of their (modelled)
+opponent.
+
+In Level-\(k\) theory, a level-0 player uses a fixed strategy without
+explicitly considering the strategy of their opponent. A level-1 player
+assumes their opponent is a level-0 player, and chooses actions to best
+respond to the strategy of their opponent, without considering what
+their opponent might believe that they will play. A level-2 player, on
+the other hand, takes their opponent's belief about their actions into
+account, assuming they face a level-1 player, and choosing actions to
+best respond to the actions of that player. Cognitive Hierarchy theory
+is based on similar principles, but rather than assuming an opponent
+always adopts a particular level-\(k\) strategy, they are assumed to
+adopt each of the level-\(k\) strategies with a particular probability
+(i.e., the opponent's strategy is a mixture over pure level-\(k\)
+strategies).
+
+Iterative reasoning strategies can explain non-equilibrium play in a
+range of games, such as the \(p\)-beauty contest game (Nagel 1995),
+dominance solvable games (Camerer, Ho, and Chong 2004), and various
+standard normal form games (Costa-Gomes, Crawford, and Broseta 2001). In
+the present study, we endow our computer opponents with a limited
+ability for iterative reasoning and assess whether (1) human players
+adapt their strategy to exploit this limited reasoning of their
+opponent, and (2) whether they are able to generalize a learned opponent
+model to other games. In two experiments, participants face the same
+opponent (Experiment 1) or the same two opponents (Experiment 2) in
+three consecutive games: the well-known Rock-Paper-Scissors game, the
+structurally similar Fire-Water-Grass game, and a less similar Numbers
+(Experiment 1) or Shootout (Experiment 2) game. To foreshadow our
+results, we find evidence that participants transfer the learned
+strategy of their opponent to other games, and that this transfer is
+moderated by the sophistication of their opponent and the similarity
+between the games. Moreover, using computational modelling, we find
+evidence that participants switch from relying on an opponent model in
+the early stages of the games, to a more habitual and cognitively less
+demanding strategy in the later stages of the games.
 
@@
 
-In the first experiment, we aim to test learning transfer by making participants face the same computer opponent with a limited level of iterative reasoning in three sequential games that vary in similarity.
-If participants are able to learn the limitations of their opponent's iterative reasoning and generalize this to new games, their performance in (the early stages of) later games should be higher than expected if they were to completely learn a new strategy in each game.
+In the first experiment, we aim to test learning transfer by making
+participants face the same computer opponent with a limited level of
+iterative reasoning in three sequential games that vary in similarity.
+If participants are able to learn the limitations of their opponent's
+iterative reasoning and generalize this to new games, their performance
+in (the early stages of) later games should be higher than expected if
+they were to completely learn a new strategy in each game.
 
@@
 
-A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
-The mean age of participants was 31.2 years.
-Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance (£1.06 on average).
-The experiment had a 2 (computer opponent: level 1 or level 2) by 3 (games: rock-paper-scissors, fire-water-grass, numbers) design, with repeated measures on the second factor.
-Participants were randomly assigned to one of the two levels of the first factor.
+A total of 52 (28 female, 24 male) participants were recruited on the
+Prolific Academic platform. The mean age of participants was 31.2 years.
+Participants were paid a fixed fee of £2.5 plus a bonus dependent on
+their performance (£1.06 on average). The experiment had a 2 (computer
+opponent: level 1 or level 2) by 3 (games: rock-paper-scissors,
+fire-water-grass, numbers) design, with repeated measures on the second
+factor. Participants were randomly assigned to one of the two levels of
+the first factor.
 
@@
 Participants played the three games against their computer opponent.
-These games were Rock-Paper-Scissors, Fire-Water-Grass, and the Numbers game.
-A typical Rock-Paper-Scissors game (hereafter RPS) is a 3x3 zero-sum game, with a cyclical hierarchy between the two player's actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
-If one player chooses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
-Otherwise it is a draw and both players receive a reward of 0.
-RPS has a unique mixed-strategy Nash equilibrium, which consists of each player in each round randomly selecting from the three options with uniform probability.
-
-The Fire-Water-Grass (FWG) game is identical to RPS in all but action labels: Fire burns grass, water extinguishes fire, and grass absorbs water.
-We use this game as we are interested in whether learning is transferred in a fundamentally similar game where the only difference is in the label of the possible actions.
-This should make it relatively easy to generalize knowledge of the opponent's strategy, provided this knowledge is on a sufficiently abstract level, such as knowing the opponent is a level-1 or level-2 player.
-Crucially, learning simple contingencies such as \enquote{If I played rock on the previous round, playing scissors next will likely result in a win}, is not generalizable to this similar game, as these contingencies are tied to the labels of the actions.
-
-The Numbers game is a generalization of RPS.
-In the variant we use, 2 participants concurrently pick a number between 1 and 5.
-To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by their opponent.
-For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
-To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
-This game has a structure similar to RPS in which every action is dominated by exactly one other action.
-All other possible combinations of choices are considered ties.
-Similar to RPS and FWG, the mixed-strategy Nash equilibrium is to randomly play each action with equal probability.
-
-The computer opponent was programmed to use either a level-1 or level-2 strategy in all the games.
-A level-1 player is defined as a player who best responds to a level-0 player.
-A level-0 player plays in a non-strategic way and does not consider their opponent's actions.
-Here, we assume a level-0 player simply repeats their previous action.
-There are other ways to define a level-0 player.
-For instance, as repeating their action if it resulted in a win and choosing randomly from the remaining actions otherwise, or choosing randomly from all actions.
-As a best response to a uniformly random action is itself a random action, defining a level-0 player in such a way would make a level-1 opponent's strategy much harder to discern.
-Because we are mainly interested in generalization of knowledge of an opponent's strategy to other games, which requires good knowledge of this strategy, we opted for this more deterministic formulation of a level-0 player.
-The level-2 computer opponent assumes in turn that the participant is a level-1 opponent, playing according to the strategy just described.
-To make the computer opponent's strategy not too obvious, we introduced some randomness in actions of computer opponent, making them play randomly in 10\% of all trials.
-Note that at all levels, the strategies are contingent on the actions taken in the previous round.
-The choice of this type of strategy is consistent with evidence that humans strategically use information from last round play of their opponents in zero-sum games (Batzilis, Jaffe, Levitt, List, \& Picel, 2016; Wang, Xu, \& Zhou, 2014).
-Table \ref{table:1} shows an example of the computer opponent's actions in response to the previous round play.
-
-\begin{table}[bth!]
-\caption{Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round.}
+These games were Rock-Paper-Scissors, Fire-Water-Grass, and the Numbers
+game. A typical Rock-Paper-Scissors game (hereafter RPS) is a 3x3
+zero-sum game, with a cyclical hierarchy between the two player's
+actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
+If one player chooses an action which dominates their opponent's action,
+the player wins (receives a reward of 1) and the other player loses
+(receives a reward of -1). Otherwise it is a draw and both players
+receive a reward of 0. RPS has a unique mixed-strategy Nash equilibrium,
+which consists of each player in each round randomly selecting from the
+three options with uniform probability.
+
+The Fire-Water-Grass (FWG) game is identical to RPS in all but action
+labels: Fire burns grass, water extinguishes fire, and grass absorbs
+water. We use this game as we are interested in whether learning is
+transferred in a fundamentally similar game where the only difference is
+in the label of the possible actions. This should make it relatively
+easy to generalize knowledge of the opponent's strategy, provided this
+knowledge is on a sufficiently abstract level, such as knowing the
+opponent is a level-1 or level-2 player. Crucially, learning simple
+contingencies such as ``If I played rock on the previous round, playing
+scissors next will likely result in a win'', is not generalizable to
+this similar game, as these contingencies are tied to the labels of the
+actions.
+
+The Numbers game is a generalization of RPS. In the variant we use, 2
+participants concurrently pick a number between 1 and 5. To win in this
+game, a participant needs to pick a number exactly 1 higher than the
+number chosen by their opponent. For example, if a participant thinks
+their opponent will pick 3, they ought to choose 4 to win the round. To
+make the strategies cyclical as in RPS, the game stipulates that the
+lowest number (1) beats the highest number (5), so if the participant
+thinks the opponent will play 5, then the winning choice is to pick 1.
+This game has a structure similar to RPS in which every action is
+dominated by exactly one other action. All other possible combinations
+of choices are considered ties. Similar to RPS and FWG, the
+mixed-strategy Nash equilibrium is to randomly play each action with
+equal probability.
+
+The computer opponent was programmed to use either a level-1 or level-2
+strategy in all the games. A level-1 player is defined as a player who
+best responds to a level-0 player. A level-0 player plays in a
+non-strategic way and does not consider their opponent's actions. Here,
+we assume a level-0 player simply repeats their previous action. There
+are other ways to define a level-0 player. For instance, as repeating
+their action if it resulted in a win and choosing randomly from the
+remaining actions otherwise, or choosing randomly from all actions. As a
+best response to a uniformly random action is itself a random action,
+defining a level-0 player in such a way would make a level-1 opponent's
+strategy much harder to discern. Because we are mainly interested in
+generalization of knowledge of an opponent's strategy to other games,
+which requires good knowledge of this strategy, we opted for this more
+deterministic formulation of a level-0 player. The level-2 computer
+opponent assumes in turn that the participant is a level-1 opponent,
+playing according to the strategy just described. To make the computer
+opponent's strategy not too obvious, we introduced some randomness in
+actions of computer opponent, making them play randomly in 10\% of all
+trials. Note that at all levels, the strategies are contingent on the
+actions taken in the previous round. The choice of this type of strategy
+is consistent with evidence that humans strategically use information
+from last round play of their opponents in zero-sum games (Batzilis et
+al. 2016; Wang, Xu, and Zhou 2014). Table \ref{tab:table-actions} shows
+an example of the computer opponent's actions in response to the
+previous round play.
+
+\begin{table}
+
+\caption{\label{tab:table-actions}Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round}
 \centering
-\label{table:1}
-\begin{tabular}{||c c | c c||} 
- \hline
- Human action $t-1$ & Computer action $t-1$  & Computer level-1 action $t$ & Computer level-2 action $t$ \\ [0.5ex] 
- \hline\hline
- Paper & Rock & Scissors & Scissors \\ 
- Scissors  & Scissors & Rock & Paper \\
- Rock & Paper & Paper & Rock \\
- ... & ... & ... & ... \\ [1ex] 
- \hline
-\end{tabular}
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{llll}
+\toprule
+Human action t-1 & Computer action t-1 & Computer level-1 action t & Computer level-2 action t\\
+\midrule
+Paper & Rock & Scissors & Scissors\\
+Scissors & Scissors & Rock & Paper\\
+Rock & Paper & Paper & Rock\\
+... & ... & ... & ...\\
+\bottomrule
+\end{tabular}}
 \end{table}
@@
 
-Participants were informed they would play three different games against the same computer opponent.
-Participants were told that the opponent cannot cheat and will choose its actions simultaneously with them, without prior knowledge of the participant's choice.
-After providing informed consent and reading the instructions, participants answered a number of comprehension questions.
-They then played the three games against their opponent in the order RPS, FGW, and Numbers.
-An example of the interface for the RPS game is provided in Figure~\ref{fig:feedback-rps-exp2}.
-On each round, the human player chooses an action, and after a random delay (between 0.5 and 3 seconds) is shown the action chosen by the computer opponent and the outcome of that round.A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
-The score was calculated as the number of wins minus the number of losses.
-Ties did not affect the score.
-In order to incentivise the participants to maximise the number of wins against their opponent, players were paid a bonus at the end of the experiment proportional to their final score (each point was worth £0.02).
-After playing all the games, participants were asked questions about their beliefs about the computer opponent, related to whether they thought they learned their opponent's strategy, and how difficult they found playing against their opponent.
-They were then debriefed and thanked for their participation.
+Participants were informed they would play three different games against
+the same computer opponent. Participants were told that the opponent
+cannot cheat and will choose its actions simultaneously with them,
+without prior knowledge of the participant's choice. After providing
+informed consent and reading the instructions, participants answered a
+number of comprehension questions. They then played the three games
+against their opponent in the order RPS, FGW, and Numbers. An example of
+the interface for the RPS game is provided in Figure
+\ref{fig:feedback-rps-exp2}. On each round, the human player chooses an
+action, and after a random delay (between 0.5 and 3 seconds) is shown
+the action chosen by the computer opponent and the outcome of that
+round. A total of 50 rounds of each game was played with the player's
+score displayed at the end of each game. The score was calculated as the
+number of wins minus the number of losses. Ties did not affect the
+score. In order to incentivise the participants to maximise the number
+of wins against their opponent, players were paid a bonus at the end of
+the experiment proportional to their final score (each point was worth
+£0.02). After playing all the games, participants were asked questions
+about their beliefs about the computer opponent, related to whether they
+thought they learned their opponent's strategy, and how difficult they
+found playing against their opponent. They were then debriefed and
+thanked for their participation.
 
@@
 
-{\centering \includegraphics{images/feedback_rps}
+{\centering \includegraphics[width=\textwidth]{../Report/images/feedback_rps}
 
@@
 
-\hypertarget{results}{%
-\subsubsection{Results}\label{results}}
-
 \begin{figure}
 
-{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp1-avg-scores-game-1}
+{\centering \includegraphics[width=\textwidth]{CBB_files/figure-latex/exp1-avg-scores-game-1}
 
@@
 
-First, we focus on participants scores in each game (see Figure \ref{fig:exp1-avg-scores-game}).
-On average, participants obtained the lowest score in the RPS game (\(M = 0.289\), \(SD = 0.348\)), followed by Numbers (\(M = 0.31\), \(SD = 0.347\)).
-Participants' performance was highest in the FWG game (\(M = 0.454\), \(SD = 0.354\)).
-Scores in each game were significantly different from 0, the expected score of uniformly random play (RPS: \(t(51) = 7.26\), \(p < .001\); FWG: \(t(51) = 10.04\) , \(p < .001\); Numbers: \(t(51) = 7.17\), \(p < .001\)).
-As uniformly random play is the Nash equilibrium, this indicates successful deviation from a Nash-optimal strategy.
-
-To assess learning within and between games, we estimate a linear mixed-effects model with score as the dependent variable, and Condition (Level 1 or Level 2), Game (RPS, FWG, Numbers) and Block (first-half , second-half) as independent variables, including all main effects and interactions.
-The model included random intercepts for participants.
-The results show a main effect of Game (\(F(2,250) = 12.90\), \(\eta^{2} = 0.09\), \(p < .001\)) indicating that performance differs between the games.
-Post-hoc pairwise comparisons show that performance in the FWG game was significantly higher than in the RPS game (\(t(100) =3.78\), \(p < .001\)) and the Numbers game (\(t(100) = 3.32\) , \(p = .002\)).
-The score in RPS was not significantly different from the score in Numbers (\(t(100) = 0.45\) , \(p = .65\)).
-The main effect of Block (\(F(2,250) = 15.16\) , \(\eta^{2} = 0.06\), \(p < .001\)) shows that the score in the first half of each game (\(M = 0.29\)) was significantly lower than in the second half (\(M = 0.40\)), which indicates within-game learning.
-The main effect of Condition (\(F(1,50) = 5.44\), \(\eta^{2} = 0.10\), \(p = .024\)) indicates that scores were higher against the level-1 player (\(M = 0.43\)) than against the level-2 player (\(M = 0.27\)).
-Thus, it appears that is was harder for participants to exploit the strategy of the more sophisticated level-2 opponent than the comparatively less sophisticated level-1 opponent.
-There was also an interaction between Game and Condition (\(F(2,250) = 4.52\) , \(\eta^{2} = 0.03\), \(p = .01\)).
-\textbf{Post-hoc pairwise comparisons show that, for participants facing level-1 opponents, scores on the FWG game were significantly higher than RPS (\(t(250) = 3.85\) , \(p = .002\)), and also significantly higher than Numbers (\(t(250) = 3.79\) , \(p = .002\)).
-For participants facing level-2 opponents however, there was no significant difference between scores on the three games.}
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
+
+First, we focus on participants scores in each game (see Figure
+\ref{fig:exp1-avg-scores-game}). On average, participants obtained the
+lowest score in the RPS game (\(M = 0.289\), \(SD = 0.348\)), followed
+by Numbers (\(M = 0.31\), \(SD = 0.347\)). Participants' performance was
+highest in the FWG game (\(M = 0.454\), \(SD = 0.354\)). Scores in each
+game were significantly different from 0, the expected score of
+uniformly random play (RPS: \(t(51) = 7.26\), \(p < .001\); FWG:
+\(t(51) = 10.04\) , \(p < .001\); Numbers: \(t(51) = 7.17\),
+\(p < .001\)). As uniformly random play is the Nash equilibrium, this
+indicates successful deviation from a Nash-optimal strategy.
+
+To assess learning within and between games, we estimate a linear
+mixed-effects model with score as the dependent variable, and Condition
+(Level 1 or Level 2), Game (RPS, FWG, Numbers) and Block (first-half ,
+second-half) as independent variables, including all main effects and
+interactions. The model included random intercepts for participants. The
+results show a main effect of Game (\(F(2,250) = 12.90\),
+\(\eta^{2} = 0.09\), \(p < .001\)). Post-hoc pairwise comparisons show
+that performance in the FWG game was significantly higher than in the
+RPS game (\(t(100) =3.78\), \(p < .001\)) and the Numbers game
+(\(t(100) = 3.32\) , \(p = .002\)). The score in RPS was not
+significantly different from the score in Numbers (\(t(100) = 0.45\) ,
+\(p = .65\)). The main effect of Block (\(F(2,250) = 15.16\) ,
+\(\eta^{2} = 0.06\), \(p < .001\)) shows that the score in the first
+half of each game (\(M = 0.29\)) was significantly lower than in the
+second half (\(M = 0.40\)), which indicates within-game learning. The
+main effect of Condition (\(F(1,50) = 5.44\), \(\eta^{2} = 0.10\),
+\(p = .024\)) indicates that scores were higher against the level-1
+player (\(M = 0.43\)) than against the level-2 player (\(M = 0.27\)).
+Thus, it appears that is was harder for participants to exploit the
+strategy of the more sophisticated level-2 opponent than the
+comparatively less sophisticated level-1 opponent. There was also an
+interaction between Game and Condition (\(F(2,250) = 4.52\) ,
+\(\eta^{2} = 0.03\), \(p = .01\)). Post-hoc pairwise comparisons
+(\(p\)-values adjusted using Holm method for multiple comparisons) show
+that, for participants facing level-1 opponents, scores on the FWG game
+were significantly higher than those for both RPS (\(t(250) = 3.85\) ,
+\(p = .002\)), and Numbers (\(t(250) = 3.79\) , \(p = .002\)). For
+participants facing level-2 opponents however, there was no significant
+difference between scores on the three games.
 
 \hypertarget{learning-transfer}{%
-\subsubsection{Learning transfer}\label{learning-transfer}}
-
-As a measure for learning transfer, we focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game (see Figure \ref{fig:exp1-early-score-by-opp}).
-We exclude the very first round as the computer opponent plays randomly here and there is no opportunity yet for the human player to exploit their opponent's strategy.
-Players with no knowledge of their opponent's strategy are expected to perform at chance level in these early rounds.
-Positive scores in rounds 2-6 reflect generalization of prior experience.
-The FWG early score score is significantly higher than 0 (\(t(148.85) = 4.584\), \(p < .001\)).
-This is also the case for the Numbers game (\(t(148.85) = 3.00\), \(p = .009\)).
-We did not expect positive scores for the RPS game, as it was the first game played and there was no opportunity for learning about the opponent's strategy.
-Scores in this game were indeed not significantly different from 0 (\(t(148.85) = 1.04\) , \(p = .89\)).
+\subsection{Learning transfer}\label{learning-transfer}}
+
+As a measure for learning transfer, we focus on participants' scores in
+the initial 5 rounds after the first round (rounds 2-6) of each game
+(see Figure \ref{fig:exp1-early-score-by-opp}). We exclude the very
+first round as the computer opponent plays randomly here and there is no
+opportunity yet for the human player to exploit their opponent's
+strategy. Players with no knowledge of their opponent's strategy are
+expected to perform at chance level in these early rounds. Positive
+scores in rounds 2-6 reflect generalization of prior experience. The FWG
+early score score is significantly higher than 0 (\(t(148.85) = 4.584\),
+\(p < .001\)). This is also the case for the Numbers game
+(\(t(148.85) = 3.00\), \(p = .009\)). We did not expect positive scores
+for the RPS game, as it was the first game played and there was no
+opportunity for learning about the opponent's strategy. Scores in this
+game were indeed not significantly different from 0
+(\(t(148.85) = 1.04\) , \(p = .89\)).
 
@@
 
-{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp1-early-score-by-opp-1}
+{\centering \includegraphics[width=\textwidth]{CBB_files/figure-latex/exp1-early-score-by-opp-1}
 
@@
 
-Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-We expected better transfer between more similar games (i.e.~better transfer from RPS to FWG than from RPS/FWG to Numbers), and worse transfer for the more sophisticated level-2 agent.
-Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over the games is indeed dissimilar between level-1 and level-2 opponents.
-We estimates a linear mixed-effects model with the early round score as the dependent variable, and Condition (Level 1 or Level 2) and Game (RPS, FWG, Numbers), as well as their interaction, as independent variables.
-The model included random intercepts for participants.
-The results indicated a main effect of Game (\(F(2,100) = 3.35\), \(p = .04\)), but no effect for condition.
-Further investigation of the effects of game on early score using planned contrasts revealed that early scores in the FWG games are significantly higher than in the RPS ( \(t(99.99) = -2.32\), \(p = 0.02\)).
-
-We next ran statistical tests on early round scores by game and opponent, against the null hypothesis of 0 (no transfer).
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG (\(t(150) = 3.96\), \(p < .001\)) and Numbers (\(t(150) = 3.74\), \(p < .001\)).
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player (\(t(150) = 2.48\), \(p = .01\)) but not to the dissimilar game of Numbers.
+Next, we explore whether learning transfer is moderated by the type of
+opponent and game similarity. We expected better transfer between more
+similar games (i.e.~better transfer from RPS to FWG than from RPS/FWG to
+Numbers), and worse transfer for the more sophisticated level-2 agent.
+Figure \ref{fig:exp1-early-score-by-opp} indicates that the pattern over
+the games is indeed dissimilar between level-1 and level-2 opponents. We
+estimates a linear mixed-effects model with the early round score as the
+dependent variable, and Condition (Level 1 or Level 2) and Game (RPS,
+FWG, Numbers), as well as their interaction, as independent variables.
+The model included random intercepts for participants. The results
+indicated a main effect of Game (\(F(2,100) = 3.35\), \(p = .04\)), but
+no effect for condition. Further investigation of the effects of game on
+early score using planned contrasts revealed that early scores in the
+FWG games are significantly higher than in the RPS (
+\(t(99.99) = -2.32\), \(p = 0.02\)).
+
+We next ran statistical tests on early round scores by game and
+opponent, against the null hypothesis of 0 (no transfer). For level-1
+facing players, there is evidence of learning transfer from RPS to both
+FWG (\(t(150) = 3.96\), \(p < .001\)) and Numbers (\(t(150) = 3.74\),
+\(p < .001\)). For level-2 facing players, there is evidence for
+transfer from RPS to the similar game FWG, albeit scores are lower than
+for level-1 player (\(t(150) = 2.48\), \(p = .01\)) but not to the
+dissimilar game of Numbers.
 
 \hypertarget{discussion}{%
-\subsubsection{Discussion}\label{discussion}}
-
-The results of Experiment 1 indicate that participants were able to learn successful strategies which exploited the deviation from Nash-optimal play of their opponents.
-Moreover, they were able to transfer knowledge about their opponent to other games, but this was moderated by the type of game.
-There was evidence of transfer from the RPS game to the similar FWG game for both opponents.
-However, transfer to the dissimilar Numbers game was only evident for participants facing a level-1 opponent.
+\subsection{Discussion}\label{discussion}}
+
+The results of Experiment 1 indicate that participants were able to
+learn successful strategies which exploited the deviation from
+Nash-optimal play of their opponents. Moreover, they were able to
+transfer knowledge about their opponent to other games, but this was
+moderated by the type of game. There was evidence of transfer from the
+RPS game to the similar FWG game for both opponents. However, transfer
+to the dissimilar Numbers game was only evident for participants facing
+a level-1 opponent.
 
@@
 
-In Experiment 2, we aimed to obtain a stronger test of learning transfer.
-Instead of facing a single level-1 or level-2 opponent throughout all games, participants now faced both types of opponent.
-To perform well against both opponents, participants would need to learn distinct strategies against these opponents.
-To reduce effects of increased memory load due to facing distinct opponents, we provided participants access to the history of play against an opponent within each game (see Figure \ref{fig:feedback-rps-exp2}).
-Finally, we changed the third game to a penalty Shootout game, with participants aiming to score a goal and opponents playing the role of goal keepers.
-Whilst this game has the same number of actions as the first two (aim left, center, or right), it is strategically dissimilar.
-Unlike the Numbers game in Experiment 1, the Shootout game does not have a cyclical hierarchy between actions, making it harder to win through a heuristic based on this cyclicity.
+In Experiment 2, we aimed to obtain a stronger test of learning
+transfer. Instead of facing a single level-1 or level-2 opponent
+throughout all games, participants now faced both types of opponent. To
+perform well against both opponents, participants would need to learn
+distinct strategies against these opponents. To reduce effects of
+increased memory load due to facing distinct opponents, we provided
+participants access to the history of play against an opponent within
+each game (see Figure \ref{fig:feedback-rps-exp2}). Finally, we changed
+the third game to a penalty Shootout game, with participants aiming to
+score a goal and opponents playing the role of goal keepers. Whilst this
+game has the same number of actions as the first two (aim left, center,
+or right), it is strategically dissimilar. Unlike the Numbers game in
+Experiment 1, the Shootout game does not have a cyclical hierarchy
+between actions, making it harder to win through a heuristic based on
+this cyclicity.
 
@@
 
-A total of 48 participants (21 females, 28 males, 1 unknown) were recruited via the Prolific platform, none of which took part in Experiment 1.
-The average age was 30.2 years, and the mean duration to complete the task was 39 minutes.
-Participants received a fixed fee of £2.5 for completing the experiment and a performance dependent bonus (£1.32 on average).
+A total of 48 participants (21 females, 28 males, 1 unknown) were
+recruited via the Prolific platform, none of which took part in
+Experiment 1. The average age was 30.2 years, and the mean duration to
+complete the task was 39 minutes. Participants received a fixed fee of
+£2.5 for completing the experiment and a performance dependent bonus
+(£1.32 on average).
 
@@
 
-Participants played three games: Rock-Paper-Scissors (RPS), Fire-Water-Grass (FWG), and the penalty Shootout game.
-The first two games were identical to the ones used in Experiment 1.
-In the Shootout game, participants took the role of the a football (soccer) player in a penalty situation, with the computer opponent taking the role of the goalkeeper.
-Players had the choice between three actions: shooting the football to the left, right, or centre of the goal.
-Similarly, the goalkeeper chooses between defending the left, right, or centre of the goal.
-If participants shoot in a different direction than where the goalkeeper defends, they win the round and the goalkeeper loses.
-Otherwise, the goalkeeper catches the ball and the player loses the round.
-There is no possibility of ties in this game.
-Figure~\ref{fig:screenshot-shootout} shows a snapshot of play in the Shootout game.
-What makes this game different to the other games is that there are now two ways to beat the opponent: if the shooter thinks their opponent is going to choose to defend \enquote{right} in the next round, they can win by either choosing to shoot \enquote{left} or \enquote{center}.
-A level-1 shooter who thinks that their goalkeeper opponent will repeat their last action has thus two possible best responses.
-A level-1 goalkeeper, however, has only a single best response (defending where their opponent aimed in the last round).
-A level-2 goalkeeper, who believes their opponent is a level-1 shooter, will have two best responses however.
-We programmed the level-2 computer player to choose randomly between these two best responses.
-
-As in Experiment 1, all the games have a unique mixed-strategy Nash equilibrium consisting of uniformly random actions.
-If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
-Evidence of sustained wins would indicate that participants have learned to exploit patterns in their opponents' play.
+Participants played three games: Rock-Paper-Scissors (RPS),
+Fire-Water-Grass (FWG), and the penalty Shootout game. The first two
+games were identical to the ones used in Experiment 1. In the Shootout
+game, participants took the role of the a football (soccer) player in a
+penalty situation, with the computer opponent taking the role of the
+goalkeeper. Players had the choice between three actions: shooting the
+football to the left, right, or centre of the goal. Similarly, the
+goalkeeper chooses between defending the left, right, or centre of the
+goal. If participants shoot in a different direction than where the
+goalkeeper defends, they win the round and the goalkeeper loses.
+Otherwise, the goalkeeper catches the ball and the player loses the
+round. There is no possibility of ties in this game. Figure
+\ref{fig:screenshot-shootout} shows a snapshot of play in the Shootout
+game. What makes this game different to the other games is that there
+are now two ways to beat the opponent: if the shooter thinks their
+opponent is going to choose to defend ``right'' in the next round, they
+can win by either choosing to shoot ``left'' or ``center''. A level-1
+shooter who thinks that their goalkeeper opponent will repeat their last
+action has thus two possible best responses. A level-1 goalkeeper,
+however, has only a single best response (defending where their opponent
+aimed in the last round). A level-2 goalkeeper, who believes their
+opponent is a level-1 shooter, will have two best responses however. We
+programmed the level-2 computer player to choose randomly between these
+two best responses.
+
+As in Experiment 1, all the games have a unique mixed-strategy Nash
+equilibrium consisting of uniformly random actions. If participants
+follow this strategy, or simply don't engage in learning how the
+opponent plays, they would score 0 on average against both level-1 and
+level-2 players. Evidence of sustained wins would indicate that
+participants have learned to exploit patterns in their opponents' play.
 
@@
 
-{\centering \includegraphics{images/shootout}
+{\centering \includegraphics[width=\textwidth]{../Report/images/shootout}
 
@@
 
-Participants played 3 games sequentially against both level-1 and level-2 computer opponents.
-As in Experiment 1, the computer opponents retained the same strategy throughout the 3 games.
-Participants faced each opponent twice in each game.
-Each game was divided into 4 stages, numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
-Participants started by facing one of the opponents in stage one, then the other in stage two.
-This was repeated in the same order in stages 3 and 4.
-Which opponent they faced first was counterbalanced.
-All participants engaged in the three games (RPS, FWG and Shootout) in this exact order, and were aware that their opponent could not cheat and chose their action simultaneously with the player, without knowing their choices beforehand.
-In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
-During those 3 seconds, participants could not choose an action and had to wait for the timer to run out.
-A random delay between 0.5 and 3 seconds was again introduced before the choice of the computer agent was revealed, as a way of simulating a real human opponent's decision time.
-After each round, participants were given detailed feedback about their opponent's action and whether they won or lost the round.
-Further information about the history of play in previous rounds was also provided and participants could scroll down to recall the full history of each interaction against an opponent in a particular stage of a game.
-The number of wins, losses and ties in each game were displayed at the top of the screen, and this scoreboard was reinitialised to zero at the onset of a new stage game.
+Participants played 3 games sequentially against both level-1 and
+level-2 computer opponents. As in Experiment 1, the computer opponents
+retained the same strategy throughout the 3 games. Participants faced
+each opponent twice in each game. Each game was divided into 4 stages,
+numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively
+for a total of 60 rounds per game. Participants started by facing one of
+the opponents in stage one, then the other in stage two. This was
+repeated in the same order in stages 3 and 4. Which opponent they faced
+first was counterbalanced. All participants engaged in the three games
+(RPS, FWG and Shootout) in this exact order, and were aware that their
+opponent could not cheat and chose their action simultaneously with the
+player, without knowing their choices beforehand. In order to encourage
+participants to think about their next choice, a countdown timer of 3
+seconds was introduced at the beginning of each round. During those 3
+seconds, participants could not choose an action and had to wait for the
+timer to run out. A random delay between 0.5 and 3 seconds was again
+introduced before the choice of the computer agent was revealed, as a
+way of simulating a real human opponent's decision time. After each
+round, participants were given detailed feedback about their opponent's
+action and whether they won or lost the round. Further information about
+the history of play in previous rounds was also provided and
+participants could scroll down to recall the full history of each
+interaction against an opponent in a particular stage of a game. The
+number of wins, losses and ties in each game were displayed at the top
+of the screen, and this scoreboard was reinitialised to zero at the
+onset of a new stage game.
 
@@
 Participants' scores are depicted in Figure \ref{fig:exp2-score-by-opp}.
-The RPS game had the lowest average score per round (\(M = 0.194\), SD = 0.345) followed by FWG (\(M = 0.27\), SD = 0.394) and finally the Shootout game (\(M = 0.289\), SD = 0.326).\footnote{A higher score in the Shootout game is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
-Indeed, a player not aiming to uncover the opponent's strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will adjust all scores in the Shootout game by subtracting the average score per round of a random strategy (0.33).} Using one-sample t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: \(t(49) = 6.26\), \(p < .001\); FWG: \(t(49) = 7.25\), \(p < .001\); Shootout: \(t(49) = 13.61\), \(p < .001\)).
+The RPS game had the lowest average score per round (\(M = 0.194\), SD =
+0.345) followed by FWG (\(M = 0.27\), SD = 0.394) and finally the
+Shootout game (\(M = 0.289\), SD = 0.326).\footnote{A higher score in
+  the Shootout game is expected as there are 2 out of three possible
+  winning actions, compared to one out of three in RPS and FWG. Indeed,
+  a player not aiming to uncover the opponent's strategy and thus
+  choosing to play randomly should be expected to have on average score
+  per round of 0 in both RPS and FWG, and 0.33 in the Shootout game. To
+  make the scores more comparable, and because we are interested in
+  player's performance that is not due to chance, we will adjust all
+  scores in the Shootout game by subtracting the average score per round
+  of a random strategy (0.33).} Using one-sample t-tests on adjusted
+scores, we reject the null hypothesis of random play in all three games
+(RPS: \(t(49) = 6.26\), \(p < .001\); FWG: \(t(49) = 7.25\),
+\(p < .001\); Shootout: \(t(49) = 13.61\), \(p < .001\)).
 
@@
 
-{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-score-by-opp-1}
+{\centering \includegraphics[width=\textwidth]{CBB_files/figure-latex/exp2-score-by-opp-1}
 
@@
 
-To explore whether learning occurred within and between games, we estimated a linear mixed-effects model, with score as the dependent variable and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2), Game (RPS, FWG, Shootout) and Encounter (first or second) as the independent variables, including all main effects and interactions.
-The model included random intercepts for participants.
-We found a main effect of Game (\(F(2,528) = 15.32\), \(\eta^{2} = 0.04\), \(p < .001\)).
-Post-hoc pairwise comparisons between games (\(p\)-values adjusted using Holm method for multiple comparisons) indicate performance in the games increased steadily throughout the experiment, with FWG performance significantly higher than RPS (\(t(96) =2.53\), \(p = .025\)), and performance in the Shootout game significantly higher than in FWG (\(t(96) = 2.32\), \(p = .025\)).
-Whilst the model shows no main effect of Condition, Opponent type, or Encounter, there was a significant interaction between Game and Opponent type (\(F(2, 528) = 5.78\) ,\(\eta^{2} = 0.02\), \(p = .003\)).
-Follow-up analysis differentiating performance by type of opponent faced shows that when facing level-1 agents, scores increased steadily after each game, with FWG score significantly higher than RPS (\(t(191) = 2.70\), \(p = .03\)) and Shootout scores in turn significantly higher than FWG (\(t(191) = 3.05\), \(p = .01\)).
-There was no significant difference between scores on games when facing level-2 agents however.
+To explore whether learning occurred within and between games, we
+estimated a linear mixed-effects model, with score as the dependent
+variable and Condition (level-1 first, level-2 first), Opponent type
+(level-1 or level-2), Game (RPS, FWG, Shootout) and Encounter (first or
+second) as the independent variables, including all main effects and
+interactions. The model included random intercepts for participants. We
+found a main effect of Game (\(F(2,528) = 15.32\), \(\eta^{2} = 0.04\),
+\(p < .001\)). Post-hoc pairwise comparisons between games (\(p\)-values
+adjusted using Holm method for multiple comparisons) indicate
+performance in the games increased steadily throughout the experiment,
+with FWG performance significantly higher than RPS (\(t(96) =2.53\),
+\(p = .025\)), and performance in the Shootout game significantly higher
+than in FWG (\(t(96) = 2.32\), \(p = .025\)). Whilst the model shows no
+main effect of Condition, Opponent type, or Encounter, there was a
+significant interaction between Game and Opponent type
+(\(F(2, 528) = 5.78\) ,\(\eta^{2} = 0.02\), \(p = .003\)). Follow-up
+analysis differentiating performance by type of opponent faced shows
+that when facing level-1 agents, scores increased steadily after each
+game, with FWG score significantly higher than RPS (\(t(191) = 2.70\),
+\(p = .03\)) and Shootout scores in turn significantly higher than FWG
+(\(t(191) = 3.05\), \(p = .01\)). There was no significant difference
+between scores on games when facing level-2 agents however.
 
 \hypertarget{learning-transfer-1}{%
-\subsubsection{Learning transfer}\label{learning-transfer-1}}
+\subsection{Learning transfer}\label{learning-transfer-1}}
+
+To measure transfer between games, we again focus on participants'
+scores in the initial 5 rounds after the first round (rounds 2-6) of
+each game and only during the first time they interact with an opponent
+in a game (see Figure \ref{fig:exp2-early-score-by-opp}). We estimated a
+linear mixed-effects model with the early round scores as the dependent
+variable, and Condition (level-1 first, level-2 first), Opponent type
+(level-1 or level-2) and Game (RPS, FWG, Shootout) as independent
+variables, including all main effects and interactions. The model also
+included random intercepts for participants. We found a main effect of
+Game (\(F(2,240) = 6.57\), \(p = .002\)). The effect of game reflects
+early scores on FWG being significantly higher than on RPS
+(\(t(240) = 3.01\), \(p = .005\)) as well as scores on shootout being
+significantly higher than RPS (\(t(240) = 3.25\), \(p = .003\)). We also
+found an interaction effect between Game and Opponent type
+(\(F(2,240) = 3.34\), \(p = .037\)). Post-hoc pairwise comparisons
+(p-values adjusted using Holm method for multiple comparisons) show that
+the difference between early scores in RPS and shootout was mostly
+driven by participants facing level-1 players ((\(t(240) = 4.12\),
+\(p < .001\))). No signifcant differences were found between
+participants facing different opponents in the same game, or between
+games when facing the same opponent.
 
@@
 
-{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-early-score-by-opp-1}
+{\centering \includegraphics[width=\textwidth]{CBB_files/figure-latex/exp2-early-score-by-opp-1}
 
@@
 
-To measure transfer between games, we again focus on participants' scores in the initial 5 rounds after the first round (rounds 2-6) of each game and only during the first time they interact with an opponent in a game (see Figure \ref{fig:exp2-early-score-by-opp}).
-We estimated a linear mixed-effects model with the early round scores as the dependent variable, and Condition (level-1 first, level-2 first), Opponent type (level-1 or level-2) and Game (RPS, FWG, Shootout) as independent variables, including all main effects and interactions.
-The model also included random intercepts for participants.
-We found a main effect of Game (\(F(2,240) = 6.57\), \(p = .002\)).
-\textbf{The effect of game reflects early scores on FWG being significantly higher than on RPS (\(t(240) = 3.01\), \(p = .005\)) as well as scores on shootout being significantly higher than RPS (\(t(240) = 3.25\), \(p = .003\)).
-We also found an interaction effect between Game and Opponent type (\(F(2,240) = 3.34\), \(p = .037\)).
-Post-hoc pairwise comparisons (applying Holm correction for multiple comparisons) show that the difference between early scores in RPS and shootout was mostly driven by participants facing level-1 players ((\(t(240) = 4.12\), \(p < .001\))).
-No signifcant differences were found between opponents for other games, or between games when facing the same opponent.}
-
-\textbf{MS: What do these effects indicate?
-Report post-hoc comparisons between games, and e.g.~differences between opponents for each game, here.
-The later tests against 0 are not adequate to understand the effects here.}
-
-We then ran statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG (\(t(271) = 4.99\), \(p < .001\)) and Shootout (\(t(271) = 6.66\), \(p < .001\)).
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player (\(t(271) = 4.41\), \(p < .001\)).
-Unlike in Experiment 1, there is also evidence of transfer to the dissimilar Shootout game (\(t(271) = 3.22\), \(p = .004\)).
-The early round scores in the similar FWG games for level-1 and level-2 facing players are not significantly different from each other.
-However, the score of the players facing the level-1 opponent in Shootout is higher than that of players facing level-2 opponents (\(t(144) = 2.45\), \(p = 0.01\)).
+We then ran statistical tests on early round scores by game and opponent
+against the null hypothesis of 0 (no transfer). For level-1 facing
+players, there is evidence of learning transfer from RPS to both FWG
+(\(t(271) = 4.99\), \(p < .001\)) and Shootout (\(t(271) = 6.66\),
+\(p < .001\)). For level-2 facing players, there is evidence for
+transfer from RPS to the similar game FWG, albeit scores are lower than
+for level-1 player (\(t(271) = 4.41\), \(p < .001\)). Unlike in
+Experiment 1, there is also evidence of transfer to the dissimilar
+Shootout game (\(t(271) = 3.22\), \(p = .004\)). The early round scores
+in the similar FWG games for level-1 and level-2 facing players are not
+significantly different from each other. However, the score of the
+players facing the level-1 opponent in Shootout is higher than that of
+players facing level-2 opponents (\(t(144) = 2.45\), \(p = 0.01\)).
 
 \hypertarget{discussion-1}{%
-\subsubsection{Discussion}\label{discussion-1}}
-
-The results of Experiment 2 confirm earlier findings from Experiment 1 on learning transfer in a situation where participants need to learn about two distinct opponents.
-As in Experiment 1, participants adapted their strategies to both level-1 and level-2 opponents to exploit deviations from Nash-optimal play.
-Knowledge about both types of opponents were transferred to both the similar and dissimilar game.
-This transfer was moderated by the degree of similarity between games, as well as opponent type.
-The interaction effect showed that transfer to the dissimilar game was easier when facing the less sophisticated agent.
+\subsection{Discussion}\label{discussion-1}}
+
+The results of Experiment 2 confirm earlier findings from Experiment 1
+on learning transfer in a situation where participants need to learn
+about two distinct opponents. As in Experiment 1, participants adapted
+their strategies to both level-1 and level-2 opponents to exploit
+deviations from Nash-optimal play. Knowledge about both types of
+opponents were transferred to both the similar and dissimilar game. This
+transfer was moderated by the degree of similarity between games, as
+well as opponent type. The interaction effect showed that transfer to
+the dissimilar game was easier when facing the less sophisticated agent.
 
@@
 
-To gain more insight into participants' strategies against their computer opponents, we constructed and tested several computational models of strategy learning.
-The baseline model assumes play is random, and each potential action is chosen with equal probability.
-Note that this corresponds to the Nash equilibrium strategy.
-The other models adapted their play to the opponent, either by reinforcing successful actions in each game (reinforcement learning), or by determining the type of opponent through Bayesian learning (Bayesian Cognitive Hierarchy models).
-We also include the (self-tuning) Expected Weighted Attraction (EWA) model, which is a popular model in behavioural economics.
-
-In the following, we will describe the models in more detail, and provide some intuition into how they implement learning about the game and/or the opponent.
-Throughout, we use the following notation: In each game \(g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}\), on each trial \(t\), the participant chooses an action \(a_t \in \mathcal{A}_g\), and the opponent chooses action \(o_t \in \mathcal{A}_g\), where \(\mathcal{A}_g\) is the set of allowed actions in game \(g\), e.g.
-\(\mathcal{A}_\text{RPS} = \{R,P,S\}\).
-The participant then receives reward \(r_t \in \{1,0,-1\}\), and the opponent receives \(-r_t\).
-We use the state variable \(s_t = \{a_{t-1},o_{t-1}\}\) to denote the actions taken in the previous round \(t-1\) by the participant and opponent.
-The initial state is empty, and we assume that the action at a first encounter of an opponent in a game is chosen at random.
+To gain more insight into participants' strategies against their
+computer opponents, we constructed and tested several computational
+models of strategy learning. The baseline model assumes play is random,
+and each potential action is chosen with equal probability. Note that
+this corresponds to the Nash equilibrium strategy. The other models
+adapted their play to the opponent, either by reinforcing successful
+actions in each game (reinforcement learning), or by determining the
+type of opponent through Bayesian learning (Bayesian Cognitive Hierarchy
+models). We also include the (self-tuning) Expected Weighted Attraction
+(EWA) model, which is a popular model in behavioural economics.
+
+In the following, we will describe the models in more detail, and
+provide some intuition into how they implement learning about the game
+and/or the opponent. Throughout, we use the following notation: In each
+game
+\(g \in \{\text{RPS},\text{FWG}, \text{Numbers}, \text{Shootout} \}\),
+on each trial \(t\), the participant chooses an action
+\(a_t \in \mathcal{A}_g\), and the opponent chooses action
+\(o_t \in \mathcal{A}_g\), where \(\mathcal{A}_g\) is the set of allowed
+actions in game \(g\), e.g. \(\mathcal{A}_\text{RPS} = \{R,P,S\}\). The
+participant then receives reward \(r_t \in \{1,0,-1\}\), and the
+opponent receives \(-r_t\). We use the state variable
+\(s_t = \{a_{t-1},o_{t-1}\}\) to denote the actions taken in the
+previous round \(t-1\) by the participant and opponent. The initial
+state is empty, and we assume that the action at a first encounter of an
+opponent in a game is chosen at random.
 
 \hypertarget{reinforcement-learning-rl-model}{%
-\subsection{Reinforcement learning (RL) model}\label{reinforcement-learning-rl-model}}
-
-We first consider a model-free reinforcement learning algorithm, where actions that have led to positive rewards are reinforced, and the likelihood of actions that led to a negative reward is lowered.
-Since the computer players in this experiment based their play on the actions in the previous round, a suitable RL model for this situation is one which learns the value of actions contingent on plays in the previous round, i.e.~by defining the state \(s_{t}\) as above.
-The resulting RL model learns a \(Q\)-value (Watkins \& Dayan, 1992) for each state-action pair:
+\subsection{Reinforcement learning (RL)
+model}\label{reinforcement-learning-rl-model}}
+
+We first consider a model-free reinforcement learning algorithm, where
+actions that have led to positive rewards are reinforced, and the
+likelihood of actions that led to a negative reward is lowered. Since
+the computer players in this experiment based their play on the actions
+in the previous round, a suitable RL model for this situation is one
+which learns the value of actions contingent on plays in the previous
+round, i.e.~by defining the state \(s_{t}\) as above. The resulting RL
+model learns a \(Q\)-value (Watkins and Dayan 1992) for each
+state-action pair:
 \[Q_{t+1}(s_{t},a_{t}) = Q_{t}(s_{t},a_{t}) + \alpha \left( r_{t}  - Q(s_{t},a_{t}) \right) ,\]
-where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), and \(\alpha \in [0,1]\) the learning rate.
-For instance, \(Q_t(\{R,S\},P)\) denotes the value of taking action \enquote{Paper} this round if the player's last action was \enquote{Rock} and the opponent played \enquote{Scissors}.
-Actions are taken according to a softmax rule:
+where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in
+state \(s\) at time \(t\), and \(\alpha \in [0,1]\) the learning rate.
+For instance, \(Q_t(\{R,S\},P)\) denotes the value of taking action
+``Paper'' this round if the player's last action was ``Rock'' and the
+opponent played ``Scissors''. Actions are taken according to a softmax
+rule:
 \[P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}, \]
-where the inverse temperature parameter \(\lambda\) determines the consistency of the strategy (the higher \(\lambda\), the more often the action with the highest \(Q\)-value is chosen.
-While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different state space \(\mathcal{S}_g\) and action space \(\mathcal{A}_g\), and there is no simple way to map states and actions across games.
-
-The RL model has two free parameters: the learning rate (\(\alpha\)) and the inverse temperature (\(\lambda\)).
+where the inverse temperature parameter \(\lambda\) determines the
+consistency of the strategy (the higher \(\lambda\), the more often the
+action with the highest \(Q\)-value is chosen). While this RL model
+allows the players to compute the values of actions conditional on past
+play, crucially, it will not be able to transfer learning between games,
+as each game has a different state space \(\mathcal{S}_g\) and action
+space \(\mathcal{A}_g\), and there is no simple way to map states and
+actions across games. The RL model has two free parameters: the learning
+rate (\(\alpha\)) and the inverse temperature (\(\lambda\)).
 
 \hypertarget{experience-weighted-attraction-ewa-model}{%
-\subsection{Experience-weighted attraction (EWA) model}\label{experience-weighted-attraction-ewa-model}}
-
-The self-tuning Experience Weighted Attraction (EWA) model (Ho, Camerer, \& Chong, 2004) combines two seemingly different approaches, namely reinforcement learning and belief learning.
-Belief learning models are based on the assumption that players keep track of their opponent's frequency of past actions, and best respond to that.
-By contrast, reinforcement learning does not explicitly take into account beliefs about other players, but simply increases the probability of repeating a more rewarding action.
-The self-tuning EWA model has been shown to perform better than either RL or belief learning alone in various repeated games and has the advantage of having only one free parameter, the inverse temperature of the softmax choice function.
-The EWA model is based on updating ``Attractions'' for each action over time given a particular state.
-The attraction of action \(a\) at time \(t\) given state \(s\) is denoted as \(A_{t}(a, s)\) and updated as
+\subsection{Experience-weighted attraction (EWA)
+model}\label{experience-weighted-attraction-ewa-model}}
+
+The self-tuning Experience Weighted Attraction (EWA) model (Ho, Camerer,
+and Chong 2004) combines two seemingly different approaches, namely
+reinforcement learning and belief learning. Belief learning models are
+based on the assumption that players keep track of their opponent's
+frequency of past actions, and best respond to that. By contrast,
+reinforcement learning does not explicitly take into account beliefs
+about other players, but simply increases the probability of repeating a
+more rewarding action. The self-tuning EWA model has been shown to
+perform better than either RL or belief learning alone in various
+repeated games and has the advantage of having only one free parameter,
+the inverse temperature of the softmax choice function. The EWA model is
+based on updating ``Attractions'' for each action over time given a
+particular state. The attraction of action \(a\) at time \(t\) given
+state \(s\) is denoted as \(A_{t}(a, s)\) and updated as
 \[ A_{t+1}(a,s) =  \frac{\phi(t) \ N(t) \ A_{t}(a,s) + [ \delta_{a}(t) + (1-\delta_{a}(t)) \ I(a_t = a )] \ R(a,o_t) } {\phi(t)N(t) + 1} \]
-where \(I(x)\) is an indicator function which takes the value 1 is its argument is true and 0 otherwise, and \(R(a,o_t)\) is the reward that would be obtained from playing action \(a\) against opponent action \(o_t\).
-\(R(a,o_t)\) equals the actual obtained reward when \(a = a_t\), and otherwise is a counterfactual reward that would have been obtained if a different action were taken.
-Unlike reinforcement learning, this uses knowledge of the rules of the game to allow reinforcing actions that were not actually taken by the rewards they would have provided.
-The parameter \(\delta\) reflects the weight given to such counterfactual rewards.
-Setting \(\delta = 0\) leads to reinforcement only of actions taken, while positive values of \(\delta\) makes the update rule take into account foregone payoffs, which is similar to weighted fictitious play (Cheung \& Friedman, 1994).
-\(N(t)\) represents an experience weight and can be interpreted as the number of \enquote{observation-equivalents} of past experience.
-We initialise it to 1 so initial attractions and reinforcement from payoffs are weighted equally.
-
-In the earlier version of the EWA model (Camerer, Ho, \& Others, 1997), \(\phi\) and \(\delta\) were time-invariant free parameters.
-In the self-tuning EWA model (Ho et al., 2004), the values of \(\delta\) and \(\phi\) are learnt from experience.
-Over time, \(\delta\) is updated as
+where \(I(x)\) is an indicator function which takes the value 1 if its
+argument is true and 0 otherwise, and \(R(a,o_t)\) is the reward that
+would be obtained from playing action \(a\) against opponent action
+\(o_t\). \(R(a,o_t)\) equals the actual obtained reward when
+\(a = a_t\), and otherwise is a counterfactual reward that would have
+been obtained if a different action were taken. Unlike reinforcement
+learning, this uses knowledge of the rules of the game to allow
+reinforcing actions that were not actually taken by the rewards they
+would have provided. The parameter \(\delta\) reflects the weight given
+to such counterfactual rewards. Setting \(\delta = 0\) leads to
+reinforcement only of actions taken, while positive values of \(\delta\)
+makes the update rule take into account foregone payoffs, which is
+similar to weighted fictitious play (Cheung and Friedman 1994). \(N(t)\)
+represents an experience weight and can be interpreted as the number of
+``observation-equivalents'' of past experience. We initialise it to 1 so
+initial attractions and reinforcement from payoffs are weighted equally.
+
+In the earlier version of the EWA model (Camerer, Ho, and Others 1997),
+\(\phi\) and \(\delta\) were time-invariant free parameters. In the
+self-tuning EWA model (Ho, Camerer, and Chong 2004), the values of
+\(\delta\) and \(\phi\) are learnt from experience. Over time,
+\(\delta\) is updated as
 \[\delta_{a}(t) = \begin{cases} 1 & \text{if }  R(a,o_{t}) \geq r_{t}  \\
-0 & \text{otherwise} \end{cases}\]
-The \(\phi_{t}\) parameter can be interpreted as a discount of prior experience, modelling either limited agent memory or changes in the game conditions.
-At the core, \(\phi(t)\) depends on a surprise index \(S_{p}(t)\):
-\[\phi(t) = 1 - \frac{1}{2}S_{p}(t) ,\]
-where \(S_{p}(t)\) quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play, across strategies k, as \(h^{k}(t)\):
-\[h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k=o_{\tau})}{t}, \]
-as well as an indicator vector of the most recent opponent play:
-\[r^k(t) = I(o^k=o_{t}), \]
-Where \(I\) is the indicator function as defined above.
-To get the surprise index, we simply sum all the squared deviations between the cumulative history vector \(h^{k}(t)\) and the immediate history \(r^k(t)\):
+0 & \text{otherwise} \end{cases}\] The \(\phi_{t}\) parameter can be
+interpreted as a discount of prior experience, modelling either limited
+agent memory or changes in the game conditions. At the core, \(\phi(t)\)
+depends on a surprise index \(S_{p}(t)\):
+\[\phi(t) = 1 - \frac{1}{2}S_{p}(t) ,\] where \(S_{p}(t)\) quantifies
+how the opponent deviates from past play. It is calculated in turn
+through the cumulative history of play, across opponent possible actions
+k, as \(h^{k}(t)\):
+\[h^{k}(t)= \frac{ \sum_{\tau = 1}^t  I( o_{\tau} = o^k )} {t}, \] as
+well as an indicator vector of the most recent opponent play:
+\[r^k(t) = I(o^k=o_{t}), \] Where \(I\) is the indicator function as
+defined above. To get the surprise index, we simply sum all the squared
+deviations between the cumulative history vector \(h^{k}(t)\) and the
+immediate history \(r^k(t)\):
 
@@
 
-\textbf{MS: why is there a superscript in \(h^k\) and \(r^k\)? }
-\textbf{IG : Because they depend on strategy k}
-
-\textbf{MS: And is the indicator variable \(I(o^k = o_{t})\)?}
-\textbf{IG: Yes, corrected}
-
-\textbf{And is \(\delta_a(t)\) always 0 or 1?}
-\textbf{IG: yes. Pls refer to: Camerer, C. F., \& Ho, T. H. (2015). Behavioral game theory experiments and modeling. Handbook of game theory with economic applications, 4, 517-573.}
-
-For more details on the self-tuning EWA model, we refer the reader to (Ho et al., 2004). As in the RL model above, actions are chosen based on a softmax decision rule:
+For more details on the self-tuning EWA model, we refer the reader to
+(Ho, Camerer, and Chong 2004). As in the RL model above, actions are
+chosen based on a softmax decision rule:
 
 \[P_t(a,s) = \frac{\exp \{\lambda  A_{t}(a,s) \} }{\sum_{a' \in \mathcal{A}_t} \exp \{ \lambda A_{t}(a',s) \} } \]
-The self-tuning EWA has one free parameter: the inverse temperature of the softmax decision rule (\(\lambda\)).
-
-\subsection{Bayesian Cognitive Hierarchy (BCH) model}
-
-In what we call the Bayesian Cognitive Hierarchy (BCH) model, the participant attempts to learn the type of opponent they are facing through Bayesian learning.
-For present purposes, we assume participants consider the opponent could be either a level 0, level 1, or level 2 player, and start with a prior belief that each of these types is equally likely.
-They then use observations of the opponent's actions to infer a posterior probability of each type:
+The self-tuning EWA has one free parameter: the inverse temperature of
+the softmax decision rule (\(\lambda\)).
+
+\hypertarget{bayesian-cognitive-hierarchy-bch-model}{%
+\subsection{Bayesian Cognitive Hierarchy (BCH)
+model}\label{bayesian-cognitive-hierarchy-bch-model}}
+
+In what we call the Bayesian Cognitive Hierarchy (BCH) model, the
+participant attempts to learn the type of opponent they are facing
+through Bayesian learning. For present purposes, we assume participants
+consider the opponent could be either a level 0, level 1, or level 2
+player, and start with a prior belief that each of these types is
+equally likely. They then use observations of the opponent's actions to
+infer a posterior probability of each type:
 \[P(\text{level}=k | \mathcal{D}_{t})  \propto  P(\mathcal{D}_{t}|\text{level}=k ) \times P(\text{level}=k)\]
-where \(\mathcal{D}_{t} = \{s_1,\ldots,s_t\}\) is the data available at time \(t\). The likelihood is defined as
+where \(\mathcal{D}_{t} = \{s_1,\ldots,s_t\}\) is the data available at
+time \(t\). The likelihood is defined as
 \[P(\mathcal{D}_{t}|\text{level}=k) = \prod_{j=1}^t \left( \theta \frac{1}{|\mathcal{A}_g|} + (1-\theta) f_k(o_j|s_{j})\right)\]
-where \(f_k(o_t|s_{t}) = 1\) if \(o_t\) is the action taken by a level \(k\) player when the previous round play was \(s_t = (a_{t-1}, o_{t-1})\), and 0 otherwise.
-Note that the likelihood assumes (correctly) that there is a probability \(\theta \in [0,1]\) that the opponent takes a random action.
-The posterior at time \(t-1\) forms the prior at time \(t\).
-We assume a participant chooses an action by using the softmax function over the best response to predicted actions:
+where \(f_k(o_t|s_{t}) = 1\) if \(o_t\) is the action taken by a level
+\(k\) player when the previous round play was
+\(s_t = (a_{t-1}, o_{t-1})\), and 0 otherwise. Note that the likelihood
+assumes (correctly) that there is a probability \(\theta \in [0,1]\)
+that the opponent takes a random action. The posterior at time \(t-1\)
+forms the prior at time \(t\). We assume a participant chooses an action
+by using the softmax function over the best response to predicted
+actions:
 \[\begin{aligned} B_t(a) &= \sum_{k = 0}^2 \sum_{o \in \mathcal{A}_g} b(a,o) f_k(o|s_{t})  P(\text{level}=k|\mathcal{D}_{t-1})\\
 P_t(a) &= \frac{\exp\{\lambda B_t(a) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{ \lambda B_t(a')\}} \end{aligned}\]
-where \(b(a,o) = 1\) if action \(a\) is a best response to opponent's action \(o\) (i.e.~it leads to a win).
-
-Unlike the models above, the BCH model allows for between-game transfer, as knowledge of the level of the opponent can be used to generate predictions in games that have not been played before.
-This generalization is done simply by using the posterior \(P(\text{level} = k|\mathcal{D}_T)\) from the previous game as the prior distribution in the next game.
-However, the participant might also assume that the level of reasoning of their opponent does not generalize over games.
-This would mean starting with a \enquote{fresh} prior \(P(\text{level} = k)\) at the start of each game.
-We hence distinguish between two versions of the BCH model.
-In the No-Between-Transfer (BCH\_NBT) variant, participants assume a uniform probability of the different levels at the start of each game (and hence do not transfer knowledge of their opponent between games).
-In the Between-Transfer model (BCH\_BT), participants use the posterior probability over the levels of their opponent as the prior at the start of a new game (i.e.~complete transfer of the knowledge of their opponent).
-Both versions of the BCH model have two free parameters: the assumed probability that the opponent chooses a random action (\(\theta\)), and the temperature parameter of the softmax function (\(\lambda\)).
+where \(b(a,o) = 1\) if action \(a\) is a best response to opponent's
+action \(o\) (i.e.~it leads to a win).
+
+Unlike the models above, the BCH model allows for between-game transfer,
+as knowledge of the level of the opponent can be used to generate
+predictions in games that have not been played before. This
+generalization is done simply by using the posterior
+\(P(\text{level} = k|\mathcal{D}_T)\) from the previous game as the
+prior distribution in the next game. However, the participant might also
+assume that the level of reasoning of their opponent does not generalize
+over games. This would mean starting with a ``fresh'' prior
+\(P(\text{level} = k)\) at the start of each game. We hence distinguish
+between two versions of the BCH model. In the No-Between-Transfer
+(BCH\_NBT) variant, participants assume a uniform probability of the
+different levels at the start of each game (and hence do not transfer
+knowledge of their opponent between games). In the Between-Transfer
+model (BCH\_BT), participants use the posterior probability over the
+levels of their opponent as the prior at the start of a new game
+(i.e.~complete transfer of the knowledge of their opponent). Both
+versions of the BCH model have two free parameters: the assumed
+probability that the opponent chooses a random action (\(\theta\)), and
+the temperature parameter of the softmax function (\(\lambda\)).
 
 \hypertarget{estimation-and-model-comparison}{%
-\subsection{Estimation and model comparison}\label{estimation-and-model-comparison}}
-
-For both experiments, we fitted all models to individual participant data by maximum likelihood estimation using the DEoptim R package (Mullen, Ardia, Gil, Windover, \& Cline, 2011).
-We use the Bayesian Information Criterion (BIC) to determine the best fitting model for each participant.
-
-For Experiment 1, we fitted a total of 5 models: a baseline model assuming random play (Nash), the Bayesian Cognitive Hierarchy model allowing transfer between games (BCH\_BT) and without transfer between games (BCH\_NT), as well as a reinforcement learning (RL), and finally a self-tuning EWA model with the same state space (EWA).
-
-In Experiment 2, because participants were interacting with each opponent twice within each game, we need to distinguish between two types of opponent model transfer.
-We can have transfer \emph{within} games between the first and second interaction with the opponent.
-In addition, we can also have transfer \emph{between} games, as in e.g.~transferring a learned opponent model from RPS to FWG.
-Therefore, we fitted a total of three versions of the Bayesian Cognitive Hierarchy model: BCH\_BT allows for both within and between game transfer (between game transfer without within game transfer is implausible); BCH\_WT allows only for within-game transfer, but not between game transfer; BCH\_NT allows for no transfer within or between games.
-As the RL model can't account for between game transfer due to a change in state and action space, we can only have models that allowing for within game transfer (RL\_WT) or with no transfer within games (RL\_NT).
-Likewise, we fit both a self tuning EWA model with (EWA\_WT) and without (EWA\_NT) within-game transfer.
-Including the baseline model of random play (Nash), we therefore fitted a total of 8 models for Experiment 2.
-
-Figure~\ref{fig:exp1-comp-models} shows the results for Experiment 1.
-We can see that the RL model clearly described most participants' behaviour best, followed by the random (Nash) model.
-Only a few participants were best described by one of the BCH models or the EWA model.
+\subsection{Estimation and model
+comparison}\label{estimation-and-model-comparison}}
+
+For both experiments, we fitted all models to individual participant
+data by maximum likelihood estimation using the DEoptim R package
+(Mullen et al. 2011). We use the Bayesian Information Criterion (BIC) to
+determine the best fitting model for each participant. For Experiment 1,
+we fitted a total of 5 models: a baseline model assuming random play
+(Nash), the Bayesian Cognitive Hierarchy model allowing transfer between
+games (BCH\_BT) and without transfer between games (BCH\_NT), as well as
+a reinforcement learning (RL), and finally a self-tuning EWA model with
+the same state space (EWA). In Experiment 2, because participants were
+interacting with each opponent twice within each game, we need to
+distinguish between two types of opponent model transfer. We can have
+transfer \emph{within} games between the first and second interaction
+with the opponent. In addition, we can also have transfer \emph{between}
+games, as in e.g.~transferring a learned opponent model from RPS to FWG.
+Therefore, we fitted a total of three versions of the Bayesian Cognitive
+Hierarchy model: BCH\_BT allows for both within and between game
+transfer (between game transfer without within game transfer is
+implausible); BCH\_WT allows only for within-game transfer, but not
+between game transfer; BCH\_NT allows for no transfer within or between
+games. As the RL model can't account for between game transfer due to a
+change in state and action space, we can only have models that allowing
+for within game transfer (RL\_WT) or with no transfer within games
+(RL\_NT). Likewise, we fit both a self tuning EWA model with (EWA\_WT)
+and without (EWA\_NT) within-game transfer. Including the baseline model
+of random play (Nash), we therefore fitted a total of 8 models for
+Experiment 2.
+
+Figure \ref{fig:exp1-comp-models} shows the results for Experiment 1. We
+can see that the RL model clearly described most participants' behaviour
+best, followed by the random (Nash) model. Only a few participants were
+best described by one of the BCH models or the EWA model.
 
@@
 
-{\centering \includegraphics[width=\textwidth]{paper_draft_2021_files/figure-latex/exp1-comp-models-1}
+{\centering \includegraphics[width=\textwidth]{CBB_files/figure-latex/exp1-comp-models-1}
 
@@
 
-In Experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that the RL model was again more successful than the Bayesian Cognitive Hierarchy models (with or without transfer) and the EWA model in fitting participants' action choices.
+In Experiment 2, we can see from Figure \ref{fig:exp2-comp-models} that
+the RL model was again more successful than the Bayesian Cognitive
+Hierarchy models (with or without transfer) and the EWA model in fitting
+participants' action choices.
 
@@
 
-{\centering \includegraphics[width=\textwidth]{paper_draft_2021_files/figure-latex/exp2-comp-models-1}
+{\centering \includegraphics[width=\textwidth]{CBB_files/figure-latex/exp2-comp-models-1}
 
@@
 
-\caption{Experiment 2 histogram of best fitting computational models by condition.}\label{fig:exp2-comp-models}
+\caption{Experiment 2 - Histogram of best fitting computational models by condition.}\label{fig:exp2-comp-models}
 \end{figure}
@@
 \hypertarget{using-hidden-markov-model-to-explore-strategy-switching}{%
-\subsection{Using Hidden Markov Model to explore strategy switching}\label{using-hidden-markov-model-to-explore-strategy-switching}}
-
-The computational modelling indicates that most players are best fit by a reinforcement learning which learns good actions conditional upon the last round play.
-This is at odds with the behavioural findings, where we found evidence of transfer in early rounds of each game.
-If indeed most participants adopt a reinforcement learning strategy, they should not be able to transfer their learning to the early rounds of a new game.
-In order to investigate this discrepancy further, we plot the likelihood by trial for each game and three strategies: reinforcement learning (RL), Bayesian Cognitive Hierarchy with between-game transfer (BCH\_BT), and the random (Nash) strategy.
-Figure~\ref{fig:exp1-lik-by-tr} shows that in the initial rounds of the the later games in Experiment 1, the likelihood for the BCH models is higher than that of the other models.
-However, over time, the likelihood of the RL model increases and exceeds that of BCH model.
+\subsection{Using Hidden Markov Model to explore strategy
+switching}\label{using-hidden-markov-model-to-explore-strategy-switching}}
+
+The computational modelling indicates that most players are best fit by
+a reinforcement learning which learns good actions conditional upon the
+last round play. This is at odds with the behavioural findings, where we
+found evidence of transfer in early rounds of each game. If indeed most
+participants adopt a reinforcement learning strategy, they should not be
+able to transfer their learning to the early rounds of a new game. In
+order to investigate this discrepancy further, we plot the likelihood by
+trial for each game and three strategies: reinforcement learning (RL),
+Bayesian Cognitive Hierarchy with between-game transfer (BCH\_BT), and
+the random (Nash) strategy. Figure \ref{fig:exp1-lik-by-tr} shows that
+in the initial rounds of the the later games in Experiment 1, the
+likelihood for the BCH models is higher than that of the other models.
+However, over time, the likelihood of the RL model increases and exceeds
+that of the BCH model.
 
@@
 
-{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp1-lik-by-tr-1}
+{\centering \includegraphics[width=\textwidth]{CBB_files/figure-latex/exp1-lik-by-tr-1}
 
@@
 
-The same pattern holds for Experiment 2 (Figure~\ref{fig:exp2-lik-by-tr}).
-Again, the BCH\_BT model with between-game transfer has the highest likelihood in the early stages of the later games (apart from stage 1 of the shootout game, where the RL model is better).
-In later rounds, the likelihood of the RL model exceeds that of the BCH model.
+The same pattern holds for Experiment 2 (Figure
+\ref{fig:exp2-lik-by-tr}). Again, the BCH\_BT model with between-game
+transfer has the highest likelihood in the early stages of the later
+games (apart from stage 1 of the shootout game, where the RL model is
+better). In later rounds, the likelihood of the RL model exceeds that of
+the BCH model.
 
@@
 
-{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-lik-by-tr-1}
+{\centering \includegraphics[width=\textwidth]{CBB_files/figure-latex/exp2-lik-by-tr-1}
 
@@
 
-The fact that the likelihoods of the main strategies considered cross over in both experiments could be interpreted as indicative that participants switch between strategies as the games progress.
-According to this interpretation, participants base their responses in early rounds on the learned level of their opponents iterative reasoning, switching later to learned actions through reinforcement.
-We use hidden Markov models to more formally test for strategy switching in participants' play.
-In these models, the three strategies (RL, BCH with between-game transfer, and Nash) correspond to latent states which determine the overt responses (actions chosen).
-The models allow for switching between the states over time, and such switches correspond to strategy switches.
-Hidden Markov models assume that an observable action at time \(t\) depends on a latent state at time \(t\).
-Second, it is assumed that the latent state at time \(t\) depends on the latent state at the previous time \(t-1\).
-The model is specified by the state-conditional action distributions (these are provided by the likelihood of the fitted models), an initial state distribution (the distribution over the strategies at the initial round), and the state-transition probabilities (probability of switching from one state/strategy to another).
-Initial state probabilities and the transition probabilities were estimated with the depmixS4 package (Visser \& Speekenbrink, 2010).
-As a statistical test of strategy switching, we compare the hidden Markov model to a constrained version which assumes the probability of switching from one strategy to a different one is 0.
-This model thus assumes that when players start with a particular strategy, they continue using it throughout the experiment.
+The fact that the likelihoods of the main strategies considered cross
+over in both experiments could be interpreted as indicative that
+participants switch between strategies as the games progress. According
+to this interpretation, participants base their responses in early
+rounds on the learned level of their opponents iterative reasoning,
+switching later to learned actions through reinforcement. We use hidden
+Markov models to more formally test for strategy switching in
+participants' play. In these models, the three strategies (RL, BCH with
+between-game transfer, and Nash) correspond to latent states which
+determine the overt responses (actions chosen). The models allow for
+switching between the states over time, and such switches correspond to
+strategy switches. Hidden Markov models assume that an observable action
+at time \(t\) depends on a latent state at time \(t\). Second, it is
+assumed that the latent state at time \(t\) depends on the latent state
+at the previous time \(t-1\). The model is specified by the
+state-conditional action distributions (these are provided by the
+likelihood of the fitted models), an initial state distribution (the
+distribution over the strategies at the initial round), and the
+state-transition probabilities (probability of switching from one
+state/strategy to another). Initial state probabilities and the
+transition probabilities were estimated with the depmixS4 package
+(Visser and Speekenbrink 2010). As a statistical test of strategy
+switching, we compare the hidden Markov model to a constrained version
+which assumes the probability of switching from one strategy to a
+different one is 0. This model thus assumes that when players start with
+a particular strategy, they continue using it throughout the experiment.
 
@@
 
-{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp1-posteriors-plot-1}
+{\centering \includegraphics[width=\textwidth]{CBB_files/figure-latex/exp1-posteriors-plot-1}
 
@@
 
-\caption{Experiment1 posterior probability of strategies by game and opponent faced}\label{fig:exp1-posteriors-plot}
+\caption{Experiment 1 posterior probability of strategies by game and opponent faced}\label{fig:exp1-posteriors-plot}
 \end{figure}
 
-In Experiment 1, a likelihood-ratio test shows that the HMM model with switching fits significantly better than the non-switching one, \(\chi^2(6) = 211.09\), \(p < .001\).
-We should note that as the no switch model involves restricting parameters of the switching model on the bounds of the parameter space, the asymptotic \(p\)-value of this test may not be reliable.
-The switching model (AIC = 14,636.87, BIC = 14,692.56) fits also better than the non-switching model (AIC = 14,835.96, BIC = 14,849.88) according to the AIC and BIC.
-This provides further statistical evidence in favour of the hypothesis that participants switch between strategies.
-Figure~\ref{fig:exp1-posteriors-plot} depicts the average (across participants) posterior probabilities of each state (strategy), as a function of trial and opponent faced.
-As can be seen, there is evidence of strategy switching in the FWG and Numbers games: Initially, participants appear to use a random strategy (in the first round of a game, there is no way to predict the opponent's action), after which the BCH strategy becomes dominant.
-In the later rounds of the games, the RL strategy becomes dominant, however.
+In Experiment 1, a likelihood-ratio test shows that the HMM model with
+switching fits significantly better than the non-switching one,
+\(\chi^2(6) = 211.09\), \(p < .001\). We should note that as the no
+switch model involves restricting parameters of the switching model on
+the bounds of the parameter space, the asymptotic \(p\)-value of this
+test may not be reliable. The switching model (AIC =
+\ensuremath{1.463687\times 10^{4}}, BIC =
+\ensuremath{1.469256\times 10^{4}}) fits also better than the
+non-switching model (AIC = \ensuremath{1.483596\times 10^{4}}, BIC =
+\ensuremath{1.484988\times 10^{4}}) according to the AIC and BIC. This
+provides further statistical evidence in favour of the hypothesis that
+participants switch between strategies. Figure
+\ref{fig:exp1-posteriors-plot} depicts the average (across participants)
+posterior probabilities of each state (strategy), as a function of trial
+and opponent faced. As can be seen, there is evidence of strategy
+switching in the FWG and Numbers games: Initially, participants appear
+to use a random strategy (in the first round of a game, there is no way
+to predict the opponent's action), after which the BCH strategy becomes
+dominant. In the later rounds of the games, the RL strategy becomes
+dominant, however.
 
@@
 
-{\centering \includegraphics{paper_draft_2021_files/figure-latex/exp2-posteriors-plot-1}
+{\centering \includegraphics[width=\textwidth]{CBB_files/figure-latex/exp2-posteriors-plot-1}
 
@@
 
-\caption{Experiment2 likelihood by trial by game and opponent faced}\label{fig:exp2-posteriors-plot}
+\caption{Experiment 2 posterior probability of strategies by game and opponent faced}\label{fig:exp2-posteriors-plot}
 \end{figure}
 
-In Experiment 2, the switching model (AIC = 16,879.97, BIC = 16,936.81) again fits better than the restricted non-switching model (AIC = 16,938.41, BIC = 16,952.62), \(\chi^2(6) = 70.44\), \(p < .001\).
-The posterior probabilities of the strategies (Figure~\ref{fig:exp2-posteriors-plot}) show very clear evidence of strategy switching across games and stages, from using a BCH model in the initial rounds to an RL strategy later on.
+In Experiment 2, the switching model (AIC =
+\ensuremath{1.687997\times 10^{4}}, BIC =
+\ensuremath{1.693681\times 10^{4}}) again fits better than the
+restricted non-switching model (AIC =
+\ensuremath{1.693841\times 10^{4}}, BIC =
+\ensuremath{1.695262\times 10^{4}}), \(\chi^2(6) = 70.44\),
+\(p < .001\). The posterior probabilities of the strategies (Figure
+\ref{fig:exp2-posteriors-plot}) show very clear evidence of strategy
+switching across games and stages, from using a BCH model in the initial
+rounds to an RL strategy later on.
 
@@
 
-In this study, we investigated human learning transfer across games by making human participants play against computer agents with limited levels of iterated reasoning.
-We were interested in whether participants learn about the strategy of their opponent and transfer such knowledge between games, and whether this is modulated by the similarity between games and the sophistication of the agent.
-
-The results of our first experiment show that the majority of participants learnt to adapt to their opponent's strategy over multiple interactions, and generalised this learning to a similar game.
-Performance in early rounds indicated that learning transfer was moderated by the degree of similarity between games.
-In the second experiment, participants faced both types of opponents, allowing for a stronger test of opponent modelling, as participants would need to learn a different strategy for each opponent.
-In Experiment 1, participants could learn a single strategy for each game, making opponent modelling possibly less pertinent.
-In Experiment 2, we again found clear evidence of transfer in the early rounds of the later games.
-In addition to the moderation of transfer by the similarity between games, we also found that learning transfer was moderated by the type of opponent faced: Transfer was harder when facing the level-2 opponent as compared to the level-1 opponent.
-That evidence for transfer was weaker when facing the more sophisticated level-2 opponent may be due to a higher difficulty of learning that opponent's strategy.
-If it is more difficult to establish a model of the level-2 opponent, there is likely less knowledge to transfer to the new game.
-A player cannot transfer what they have not learnt.
-
-What exactly did the players learn in the first game (RPS) that allowed them to beat their opponent in the later games (FWG, and Numbers or Shootout)?
-what did the players learn specifically about their opponent's strategy and what form did this learning take?
-One possible answer is that participants learned simple rules based on last round play.
-For instance, \enquote{play scissors whenever my opponent played rock in last round}, or \enquote{play paper whenever the last round play was either rock or scissors}.
-These are the type of strategies that are learned by the model-free reinforcement learning we used in our computational modelling.
-While this strategy fitted participants' actions the best overall, there are at least two reasons why this account is not satisfactory as a complete description of participants' behaviour.
-Firstly, the learned strategies are not transferable to new games.
-There is no simple way to map \enquote{play scissors whenever my opponent played rock in last round} in the RPS game to \enquote{play grass whenever my opponent played fire in last round}.
-Such a mapping may be possible by translating the rules and structure from RPS to FWG, but model-free reinforcement learning lacks the tools to do this: Model-free reinforcement learning would need to start from scratch in each new game, yet we found evidence that participants could successfully exploit their opponent's strategy in early rounds of new games.
-Secondly, a reinforcement learning strategy would fare equally well against the level-1 and level-2 opponent.
-Whilst choosing different actions, the contingency between the state (last round play) and actions is the same for both opponents.
-Yet, we found that participants performed better against the level-1 opponent compared to the level-2 opponent.
-The difference in performance between the two types of opponent indicates that the actions of the more sophisticated level-2 opponent, or the best response to these, were somehow more difficult to predict.
-
-We are left with two possible explanations: First, it is possible that participants discovered a heuristic that allowed them to beat their opponent without explicitly modelling their strategy, and that this heuristic is transferable to new games.
-Because of the cyclicity in action choices (e.g., rock beats scissors, scissors beats paper, paper beats rock), it is possible to beat a level-2 opponent most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
-This is a rule that wins and is transferable to other games, as it does not depend on action labels.
-In the same vein, a heuristic that beats a level-1 player can be stated as \enquote{Choose the action that would have been beaten by my previous action}.
-Intuitively, it seems that this heuristic for a level-2 player is simpler than that for a level-1 player, which is at odds with the finding that participants performed better against the level-1 opponent.
-
-A second explanation is that participants engaged in iterative reasoning, inferring their opponent's beliefs and countering the resulting actions.
-For instance, this would be reasoning of the form \enquote{My opponent expects me to repeat my last action, choosing an action that would beat my last action.
-Hence, I will choose the action that beats their best response} or \enquote{My opponent thinks I expect them to repeat their action, hence expecting me to choose the action that beats their last action.
-They will therefore choose the action that beats this one, and hence I should choose the action that beats their best response.} Beating a level-1 player, in this account, requires being a level-2 player, and beating a level-2 player requires being a level-3 player.
-Intuitively, the additional step of iterative reasoning involved in beating a level-2 player makes the level-3 strategy more demanding and difficult to implement, which is consistent with the lower performance against the level-2 opponent.
-
-The differences in performance between the two players, coupled with the finding of positive transfer, point to participants engaging in iterative reasoning, and learning something useful about their opponent's limitations in this regard.
-This is the type of learning encapsulated by our Bayesian Cognitive Hierarchy model.
-It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
-Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (Stahl, 2000, 2003).
-We admit that our implementation in the BCH models does not predict a performance difference between the types of opponents.
-Starting with an equal prior belief over the different levels of sophistication, a BCH player would perform equally well against the level-1 and level-2 opponent.
-There are two routes to explain the difference in performance.
-Firstly, prior beliefs might be biased against higher-level opponents (i.e., participants might have believed it is more likely that they would face level-1 opponent than a level-2 opponent).
-Secondly, if the actions of a level-2 opponent are more difficult to predict than those of a level-1 opponent, this might introduce more noise in the likelihood of the opponents actions given their level of sophistication.
-Either of these mechanisms would explain why learning the strategy of the level-2 opponent is more difficult and slower than learning the strategy of the level-1 opponent.
-Using hidden Markov models, we found evidence of strategy switching between the BCH and RL strategies, and such switching seems more consistent with the latter idea.
-If predicting an opponent's actions through iterative reasoning is cognitively demanding and error-prone, it is resource-rational to switch to less costly yet equally successful strategies when these are available (Lieder \& Griffiths, 2020).
-Initially, a model-free reinforcement learning strategy will be less successful than an iterative reasoning one.
-However, given enough experience, it will be on par with an iterative reasoning strategy.
-As it involves simple state-action contingencies, a model-free RL strategy may also be computationally less costly, making it overall more effective to rely on this than iterative reasoning.
-This is similar to the arbitration between model-free and model-based RL (Daw, Niv, \& Dayan, 2005; Simon \& Daw, 2011; Wouter Kool, Joseph T.
-McGuire, Zev B.
-Rosen, Matthew M.
-Bovinick, 2011).
-In repeated and well-practised situations, relying on habits allows one to save cognitive resources for other demands.
-However, when the environment -- or game -- changes, it is prudent to use all available resources to reorient oneself.
+In this study, we investigated human learning transfer across games by
+making human participants play against computer agents with limited
+levels of iterated reasoning. We were interested in whether participants
+learn about the strategy of their opponent and transfer such knowledge
+between games, and whether this is modulated by the similarity between
+games and the sophistication of the agent.
+
+The results of our first experiment show that the majority of
+participants learnt to adapt to their opponent's strategy over multiple
+interactions, and generalised this learning to a similar game.
+Performance in early rounds indicated that learning transfer was
+moderated by the degree of similarity between games. In the second
+experiment, participants faced both types of opponents, allowing for a
+stronger test of opponent modelling, as participants would need to learn
+a different strategy for each opponent. In Experiment 1, participants
+could learn a single strategy for each game, making opponent modelling
+possibly less pertinent. In Experiment 2, we again found clear evidence
+of transfer in the early rounds of the later games. In addition to the
+moderation of transfer by the similarity between games, we also found
+that learning transfer was moderated by the type of opponent faced:
+Transfer was harder when facing the level-2 opponent as compared to the
+level-1 opponent. That evidence for transfer was weaker when facing the
+more sophisticated level-2 opponent may be due to a higher difficulty of
+learning that opponent's strategy. If it is more difficult to establish
+a model of the level-2 opponent, there is likely less knowledge to
+transfer to the new game. A player cannot transfer what they have not
+learnt.
+
+What exactly did the players learn in the first game (RPS) that allowed
+them to beat their opponent in the later games (FWG, and Numbers or
+Shootout)? What did the players learn specifically about their
+opponent's strategy and what form did this learning take? One possible
+answer is that participants learned simple rules based on last round
+play. For instance, ``play scissors whenever my opponent played rock in
+last round'', or ``play paper whenever the last round play was either
+rock or scissors''. These are the type of strategies that are learned by
+the model-free reinforcement learning we used in our computational
+modelling. While this strategy fitted participants' actions the best
+overall, there are at least two reasons why this account is not
+satisfactory as a complete description of participants' behaviour.
+Firstly, the learned strategies are not transferable to new games. There
+is no simple way to map ``play scissors whenever my opponent played rock
+in last round'' in the RPS game to ``play grass whenever my opponent
+played fire in last round''. Such a mapping may be possible by
+translating the rules and structure from RPS to FWG, but model-free
+reinforcement learning lacks the tools to do this: Model-free
+reinforcement learning would need to start from scratch in each new
+game, yet we found evidence that participants could successfully exploit
+their opponent's strategy in early rounds of new games. Secondly, a
+reinforcement learning strategy would fare equally well against the
+level-1 and level-2 opponent. Whilst choosing different actions, the
+contingency between the state (last round play) and actions is the same
+for both opponents. Yet, we found that participants performed better
+against the level-1 opponent compared to the level-2 opponent. The
+difference in performance between the two types of opponent indicates
+that the actions of the more sophisticated level-2 opponent, or the best
+response to these, were somehow more difficult to predict.
+
+We are left with two possible explanations: First, it is possible that
+participants discovered a heuristic that allowed them to beat their
+opponent without explicitly modelling their strategy, and that this
+heuristic is transferable to new games. Because of the cyclicity in
+action choices (e.g., rock beats scissors, scissors beats paper, paper
+beats rock), it is possible to beat a level-2 opponent most of the time
+by following a simple rule: Play in the next round whatever the opponent
+played in the last round. This is a rule that wins and is transferable
+to other games, as it does not depend on action labels. In the same
+vein, a heuristic that beats a level-1 player can be stated as ``Choose
+the action that would have been beaten by my previous action''.
+Intuitively, it seems that this heuristic for a level-2 player is
+simpler than that for a level-1 player, which is at odds with the
+finding that participants performed better against the level-1 opponent.
+
+A second explanation is that participants engaged in iterative
+reasoning, inferring their opponent's beliefs and countering the
+resulting actions. For instance, this would be reasoning of the form
+``My opponent expects me to repeat my last action, choosing an action
+that would beat my last action. Hence, I will choose the action that
+beats their best response'' or ``My opponent thinks I expect them to
+repeat their action, hence expecting me to choose the action that beats
+their last action. They will therefore choose the action that beats this
+one, and hence I should choose the action that beats their best
+response.'' Beating a level-1 player, in this account, requires being a
+level-2 player, and beating a level-2 player requires being a level-3
+player. Intuitively, the additional step of iterative reasoning involved
+in beating a level-2 player makes the level-3 strategy more demanding
+and difficult to implement, which is consistent with the lower
+performance against the level-2 opponent.
+
+The differences in performance between the two players, coupled with the
+finding of positive transfer, point to participants engaging in
+iterative reasoning, and learning something useful about their
+opponent's limitations in this regard. This is the type of learning
+encapsulated by our Bayesian Cognitive Hierarchy model. It involves the
+evaluation of explicit hypotheses and results in better problem-solving
+skills (Mandler 2004). Since it is less context dependent, this type of
+learning is generalizable to new situations, akin to the more general
+framework of rule-based learning explored by Stahl (Stahl 2000, 2003).
+
+We admit that our implementation in the BCH models does not predict a
+performance difference between the types of opponents. Starting with an
+equal prior belief over the different levels of sophistication, a BCH
+player would perform equally well against the level-1 and level-2
+opponent. There are two routes to explain the difference in performance.
+Firstly, prior beliefs might be biased against higher-level opponents
+(i.e., participants might have believed it is more likely that they
+would face level-1 opponent than a level-2 opponent). Secondly, if the
+actions of a level-2 opponent are more difficult to predict than those
+of a level-1 opponent, this might introduce more noise in the likelihood
+of the opponents actions given their level of sophistication. Either of
+these mechanisms would explain why learning the strategy of the level-2
+opponent is more difficult and slower than learning the strategy of the
+level-1 opponent. Using hidden Markov models, we found evidence of
+strategy switching between the BCH and RL strategies, and such switching
+seems more consistent with the latter idea. If predicting an opponent's
+actions through iterative reasoning is cognitively demanding and
+error-prone, it is resource-rational to switch to less costly yet
+equally successful strategies when these are available (Lieder and
+Griffiths 2020). Initially, a model-free reinforcement learning strategy
+will be less successful than an iterative reasoning one. However, given
+enough experience, it will be on par with an iterative reasoning
+strategy. As it involves simple state-action contingencies, a model-free
+RL strategy may also be computationally less costly, making it overall
+more effective to rely on this than iterative reasoning. This is similar
+to the arbitration between model-free and model-based RL (Daw, Niv, and
+Dayan 2005; Simon and Daw 2011; Wouter Kool, Joseph T. McGuire, Zev B.
+Rosen, Matthew M. Bovinick 2011). In repeated and well-practised
+situations, relying on habits allows one to save cognitive resources for
+other demands. However, when the environment -- or game -- changes, it
+is prudent to use all available resources to reorient oneself.
 
@@
 
-Our results show that people can successfully deviate from Nash equilibrium play to exploit deviations from such play by their opponents.
-Moreover, people can transfer knowledge about the limitations of their opponents to new situations.
-This transfer of a model of the opponent depends on the similarity between the prior and new game, as well as the sophistication of the opponent.
-Transfer is better to similar games, and for less sophisticated agents.
-Within games, we found evidence for a switch from a more reasoning-based strategy which allows for between-game transfer, to a more habitual strategy which does not.
-This is consistent with a rational trade-off between the goal of maximising performance and minimizing the cost of computing the best possible actions.
+Our results show that people can successfully deviate from Nash
+equilibrium play to exploit deviations from such play by their
+opponents. Moreover, people can transfer knowledge about the limitations
+of their opponents to new situations. This transfer of a model of the
+opponent depends on the similarity between the prior and new game, as
+well as the sophistication of the opponent. Transfer is better to
+similar games, and for less sophisticated agents. Within games, we found
+evidence for a switch from a more reasoning-based strategy which allows
+for between-game transfer, to a more habitual strategy which does not.
+This is consistent with a rational trade-off between the goal of
+maximising performance and minimizing the cost of computing the best
+possible actions.
 
 \hypertarget{references}{%
-\section{References}\label{references}}
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
 
@@
 \leavevmode\hypertarget{ref-batzilis}{}%
-Batzilis, D., Jaffe, S., Levitt, S., List, J.
-A., \& Picel, J.
-(2016).
-\emph{How facebook can deepen our understanding of behavior in strategic settings: Evidence from a million rock-paper-scissors games}.
+Batzilis, Dimitris, Sonia Jaffe, Steven Levitt, John A List, and Jeffrey
+Picel. 2016. ``How Facebook Can Deepen Our Understanding of Behavior in
+Strategic Settings: Evidence from a Million Rock-Paper-Scissors Games.''
 working paper.
@@
 \leavevmode\hypertarget{ref-camerer2003behavioural}{}%
-Camerer, C. F. (2003). Behavioural studies of strategic thinking in games. \emph{Trends in Cognitive Sciences}, \emph{7}(5), 225--231.
+Camerer, Colin F. 2003. ``Behavioural Studies of Strategic Thinking in
+Games.'' \emph{Trends in Cognitive Sciences} 7 (5). Elsevier: 225--31.
 
 \leavevmode\hypertarget{ref-camerer2004cognitive}{}%
-Camerer, C. F., Ho, T.-H., \& Chong, J.-K. (2004). A cognitive hierarchy model of games. \emph{The Quarterly Journal of Economics}, \emph{119}(3), 861--898.
+Camerer, Colin F, Teck-Hua Ho, and Juin-Kuan Chong. 2004. ``A Cognitive
+Hierarchy Model of Games.'' \emph{The Quarterly Journal of Economics}
+119 (3). MIT Press: 861--98.
 
 \leavevmode\hypertarget{ref-camerer1997experience}{}%
-Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
+Camerer, Colin, Teck-Hua Ho, and Others. 1997. ``Experience-weighted
+attraction learning in games: A unifying approach.''
 
 \leavevmode\hypertarget{ref-knez2000}{}%
-Camerer, C., \& Knez, M. (2000). \emph{Increasing Cooperation in Prisoner's Dilemmas by Establishing a Precedent of Efficiency in Coordination Games}.
+Camerer, Colin, and Marc Knez. 2000. ``Increasing Cooperation in
+Prisoner's Dilemmas by Establishing a Precedent of Efficiency in
+Coordination Games.''
 
 \leavevmode\hypertarget{ref-cheung1994learning}{}%
-Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
+Cheung, Yin-Wong, and Daniel Friedman. 1994. \emph{Learning in
+evolutionary games: some laboratory results}. University of California,
+Santa Cruz.
 
 \leavevmode\hypertarget{ref-costa2001cognition}{}%
-Costa-Gomes, M., Crawford, V. P., \& Broseta, B. (2001). Cognition and behavior in normal-form games: An experimental study. \emph{Econometrica}, \emph{69}(5), 1193--1235.
+Costa-Gomes, Miguel, Vincent P Crawford, and Bruno Broseta. 2001.
+``Cognition and Behavior in Normal-Form Games: An Experimental Study.''
+\emph{Econometrica} 69 (5). Wiley Online Library: 1193--1235.
 
 \leavevmode\hypertarget{ref-daw2005uncertainty}{}%
-Daw, N.
-D., Niv, Y., \& Dayan, P.
-(2005).
-Uncertainty-based competition between prefrontal and dorsolateral striatal systems for behavioral control.
-\emph{Nature Neuroscience}, \emph{8}(12), 1704--1711.
+Daw, Nathaniel D, Yael Niv, and Peter Dayan. 2005. ``Uncertainty-Based
+Competition Between Prefrontal and Dorsolateral Striatal Systems for
+Behavioral Control.'' \emph{Nature Neuroscience} 8 (12). Nature
+Publishing Group: 1704--11.
 
 \leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
+Ho, Teck H, Colin F Camerer, and Juin-Kuan Chong. 2004. ``The economics
+of learning models: A self-tuning theory of learning in games.''
+California Institute of Technology.
 
 \leavevmode\hypertarget{ref-ho1998iterated}{}%
-Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
+Ho, Teck-Hua, Colin Camerer, and Keith Weigelt. 1998. ``Iterated
+dominance and iterated best response in experimental" p-beauty
+contests".'' \emph{The American Economic Review} 88 (4). JSTOR: 947--69.
 
 \leavevmode\hypertarget{ref-Lake2017}{}%
-Lake, B.
-M., Ullman, T.
-D., Tenenbaum, J.
-B., \& Gershman, S.
-J.
-(2017).
-Building machines that learn and think like people.
-\emph{Behavioral and Brain Sciences}, \emph{40}.
-\url{https://doi.org/10.1017/S0140525X16001837}
+Lake, Brenden M., Tomer D. Ullman, Joshua B. Tenenbaum, and Samuel J.
+Gershman. 2017. ``Building machines that learn and think like people.''
+\emph{Behavioral and Brain Sciences} 40. Cambridge University Press.
+\url{https://doi.org/10.1017/S0140525X16001837}.
 
 \leavevmode\hypertarget{ref-lieder2020resource}{}%
-Lieder, F., \& Griffiths, T.
-L.
-(2020).
-Resource-rational analysis: Understanding human cognition as the optimal use of limited computational resources.
-\emph{Behavioral and Brain Sciences}, \emph{43}.
+Lieder, Falk, and Thomas L Griffiths. 2020. ``Resource-Rational
+Analysis: Understanding Human Cognition as the Optimal Use of Limited
+Computational Resources.'' \emph{Behavioral and Brain Sciences} 43.
+Cambridge University Press.
 
 \leavevmode\hypertarget{ref-mandler2004foundations}{}%
-Mandler, J. M. (2004). \emph{The foundations of mind: Origins of conceptual thought}. Oxford University Press.
+Mandler, Jean Matter. 2004. \emph{The Foundations of Mind: Origins of
+Conceptual Thought}. Oxford University Press.
 
 \leavevmode\hypertarget{ref-mertens1990repeated}{}%
-Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+Mertens, Jean-François. 1990. ``Repeated games.'' In \emph{Game Theory
+and Applications}, 77--130. Elsevier.
 
 \leavevmode\hypertarget{ref-R-DEoptim}{}%
-Mullen, K., Ardia, D., Gil, D., Windover, D., \& Cline, J.
-(2011).
-DEoptim: An R package for global optimization by Differential Evolution.
-\emph{Journal of Statistical Software}, \emph{40}(6), 1--26.
-\url{https://doi.org/10.18637/jss.v040.i06}
+Mullen, Katharine, David Ardia, David Gil, Donald Windover, and James
+Cline. 2011. ``DEoptim: An R Package for Global Optimization by
+Differential Evolution.'' \emph{Journal of Statistical Software} 40 (6):
+1--26. \url{https://doi.org/10.18637/jss.v040.i06}.
 
 \leavevmode\hypertarget{ref-nagel1995unraveling}{}%
-Nagel, R. (1995). Unraveling in guessing games: An experimental study. \emph{The American Economic Review}, \emph{85}(5), 1313--1326.
+Nagel, Rosemarie. 1995. ``Unraveling in Guessing Games: An Experimental
+Study.'' \emph{The American Economic Review} 85 (5). JSTOR: 1313--26.
 
 \leavevmode\hypertarget{ref-shachat2004we}{}%
-Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
+Shachat, Jason, and J Todd Swarthout. 2004. ``Do we detect and exploit
+mixed strategy play by opponents?'' \emph{Mathematical Methods of
+Operations Research} 59 (3). Springer: 359--73.
 
 \leavevmode\hypertarget{ref-Simon_Daw_11}{}%
-Simon, D.
-A., \& Daw, N.
-D.
-(2011).
-Environmental statistics and the trade-off between model-based and TD learning in humans.
-\emph{Advances in Neural Information Processing Systems 24: 25th Annual Conference on Neural Information Processing Systems 2011, NIPS 2011}, 1--9.
+Simon, Dylan A., and Nathaniel D. Daw. 2011. ``Environmental statistics
+and the trade-off between model-based and TD learning in humans.''
+\emph{Advances in Neural Information Processing Systems 24: 25th Annual
+Conference on Neural Information Processing Systems 2011, NIPS 2011},
+1--9.
 
 \leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
-Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
+Spiliopoulos, Leonidas. 2013. ``Strategic adaptation of humans playing
+computer algorithms in a repeated constant-sum game.'' \emph{Autonomous
+Agents and Multi-Agent Systems} 27 (1). Springer: 131--60.
 
 \leavevmode\hypertarget{ref-stahl2000rule}{}%
-Stahl, D. O. (2000). Rule learning in symmetric normal-form games: Theory and evidence. \emph{Games and Economic Behavior}, \emph{32}(1), 105--138.
+Stahl, Dale O. 2000. ``Rule Learning in Symmetric Normal-Form Games:
+Theory and Evidence.'' \emph{Games and Economic Behavior} 32 (1).
+Elsevier: 105--38.
 
 \leavevmode\hypertarget{ref-stahl2003sophisticated}{}%
-Stahl, D. O. (2003). Sophisticated learning and learning sophistication. \emph{Available at SSRN 410921}.
+---------. 2003. ``Sophisticated Learning and Learning Sophistication.''
+\emph{Available at SSRN 410921}.
 
 \leavevmode\hypertarget{ref-stahl1995players}{}%
-Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
+Stahl, Dale O, and Paul W Wilson. 1995. ``On players models of other
+players: Theory and experimental evidence.'' \emph{Games and Economic
+Behavior} 10 (1). Elsevier: 218--54.
 
 \leavevmode\hypertarget{ref-R-depmixS4}{}%
-Visser, I., \& Speekenbrink, M.
-(2010).
-depmixS4: An R package for hidden markov models.
-\emph{Journal of Statistical Software}, \emph{36}(7), 1--21.
-Retrieved from \url{http://www.jstatsoft.org/v36/i07/}
+Visser, Ingmar, and Maarten Speekenbrink. 2010. ``depmixS4: An R Package
+for Hidden Markov Models.'' \emph{Journal of Statistical Software} 36
+(7): 1--21. \url{http://www.jstatsoft.org/v36/i07/}.
 
 \leavevmode\hypertarget{ref-wang2014social}{}%
-Wang, Z., Xu, B., \& Zhou, H.-J. (2014). Social cycling and conditional responses in the rock-paper-scissors game. \emph{Scientific Reports}, \emph{4}(1), 1--7.
+Wang, Zhijian, Bin Xu, and Hai-Jun Zhou. 2014. ``Social Cycling and
+Conditional Responses in the Rock-Paper-Scissors Game.''
+\emph{Scientific Reports} 4 (1). Nature Publishing Group: 1--7.
 
 \leavevmode\hypertarget{ref-watkins1992q}{}%
-Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
+Watkins, Christopher J C H, and Peter Dayan. 1992. ``Q-learning.''
+\emph{Machine Learning} 8 (3-4). Springer: 279--92.
 
 \leavevmode\hypertarget{ref-Kool_2011}{}%
-Wouter Kool, Joseph T.
-McGuire, Zev B.
-Rosen, Matthew M.
-Bovinick.
-(2011).
-Decision Making and the Avoidance of Cognitive Demand.
+Wouter Kool, Joseph T. McGuire, Zev B. Rosen, Matthew M. Bovinick. 2011.
+``Decision Making and the Avoidance of Cognitive Demand.''
 \emph{Experimental Psychology}.
-\url{https://doi.org/10.2996/kmj/1138846322}
+\url{https://doi.org/10.2996/kmj/1138846322}.
+
+\bibliographystyle{spphys}
+\bibliography{Mendeley2.bib}
 

### 2021-09-30 Report/paper_draft_2021.Rmd
CBB manuscript

@@
 title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-shorttitle        : "Upgrade Report"
+shorttitle        :
 
@@
 abstract: |
-  Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and 
-  causal models of the environment. One way to build abstract representations of the environment when the task involves interactions with others is to build 
-  a model of the opponent that may inform what actions they are likely to take next. In this study, we explore opponent modelling and its transfer with the use of
-  computer agents with human-like limited degrees of iterated reasoning. In two experiments, we find that participants
-  deviate from Nash equilibrium play and learn to adapt to their opponent's strategy to exploit it. **Moreover, we show that participants transfer their learning to new games and that
-  this transfer is moderated by the level of sophistication of the opponent (second experiment), as well as the similarity between games**.
-Computational modelling shows that players start each game with a model-based
-  learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
-
-# keywords          : "keywords"
+ Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and causal models of the environment.
+One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the opponent that may inform what actions they are likely to take next.
+In this study, we explore opponent modelling and its transfer with the use of computer agents with human-like limited degrees of iterated reasoning.
+In two experiments, we find that participants deviate from Nash equilibrium play and learn to adapt to their opponent's strategy to exploit it.
+Moreover, we show that participants transfer their learning to new games and that this transfer is moderated by the level of sophistication of the opponent (second experiment), as well as the similarity between games.
+Computational modelling shows that players start each game with a model-based learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
+keywords          : "Learning Transfer, Opponent Modelling, Hidden Markov Models, Cognitive Hierarchy Models "
 # wordcount         : "X"
-
 bibliography      : ["Mendeley2.bib"]
@@
 fig_caption       : yes
+always_allow_html : true
+indent            : false
 
@@
 # classoption       : a4paper
-classoption       : man
-output            : papaja::apa6_pdf
+# classoption       : man
+output            : papaja::apa6_docx
+
 header-includes:
@@
 ```
+
+\clearpage\mbox{}\thispagestyle{empty}\clearpage
 
@@
 The choice of this type of strategy is consistent with evidence that humans strategically use information from last round play of their opponents in zero-sum games [@batzilis; @wang2014social].
-Table \@ref(table:1) shows an example of the computer opponent's actions in response to the previous round play.
-
-\begin{table}[bth!]
-\caption{Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round.}
-\centering
-\label{table:1}
-\begin{tabular}{||c c | c c||} 
- \hline
- Human action $t-1$ & Computer action $t-1$  & Computer level-1 action $t$ & Computer level-2 action $t$ \\ [0.5ex] 
- \hline\hline
- Paper & Rock & Scissors & Scissors \\ 
- Scissors  & Scissors & Rock & Paper \\
- Rock & Paper & Paper & Rock \\
- ... & ... & ... & ... \\ [1ex] 
- \hline
-\end{tabular}
-\end{table}
+Table \@ref(tab:tab1) shows an example of the computer opponent's actions in response to the previous round play.
+
+```{r table, warning = FALSE, ft.align="center", tab.cap='Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round', tab.id='tab1', label='tab1'}
+library(flextable)
+df <- data.frame( c("Paper","Scissors","Rock","..."),
+                  c("Rock","Scissors","Paper","..."),
+                  c("Scissors","Rock","Paper","..."),
+                  c("Scissors","Paper","Rock","..."))
+colnames(df) <- c("Human action t-1","Computer action t-1","Computer level-1 action t", "Human level-1 action t")
+
+df <- flextable(df)
+df <- autofit(df)
+df
+```
+
+<!-- \begin{table}[bth!] -->
+<!-- \caption{Example of how a level-1 and level-2 computer agent plays in response to actions taken in the previous round.} -->
+<!-- \centering -->
+<!-- \label{table:1} -->
+<!-- \begin{tabular}{||c c | c c||} -->
+<!--  \hline -->
+<!--  Human action $t-1$ & Computer action $t-1$  & Computer level-1 action $t$ & Computer level-2 action $t$ \\ [0.5ex] -->
+<!--  \hline\hline -->
+<!--  Paper & Rock & Scissors & Scissors \\ -->
+<!--  Scissors  & Scissors & Rock & Paper \\ -->
+<!--  Rock & Paper & Paper & Rock \\ -->
+<!--  ... & ... & ... & ... \\ [1ex] -->
+<!--  \hline -->
+<!-- \end{tabular} -->
+<!-- \end{table} -->
 
 ### Procedure
-
 Participants were informed they would play three different games against the same computer opponent.
@@
 
-### Results
-
 ```{r load-exp1-data, include=FALSE}
@@
 
-### Learning transfer
-
+## Learning transfer
 As a measure for learning transfer, we focus on participants’ scores in the initial 5 rounds after the first round (rounds 2-6) of each game (see Figure \ref{fig:exp1-early-score-by-opp}).
@@
 
-### Discussion
-
+## Discussion
 The results of Experiment 1 indicate that participants were able to learn successful strategies which exploited the deviation from Nash-optimal play of their opponents.
@@
 # Experiment 2
-
 In Experiment 2, we aimed to obtain a stronger test of learning transfer.
@@
 $$P_{t}(a|s_t) = \frac{\exp \{ \lambda Q_{t}(a,s_t) \}}{\sum_{a' \in \mathcal{A}_g} \exp \{\lambda  Q_{t}(a',s_t) \}}, $$ 
-where the inverse temperature parameter $\lambda$ determines the consistency of the strategy (the higher $\lambda$, the more often the action with the highest $Q$-value is chosen.
-While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different state space $\mathcal{S}_g$ and action space $\mathcal{A}_g$, and there is no simple way to map states and actions across games.
-
-The RL model has two free parameters: the learning rate ($\alpha$) and the inverse temperature ($\lambda$).
-<!-- We've assumed $\gamma = 0$ as changes in this parameter didn't affect the other parameter estimations or ultimately the value of the likelihoods.
--->
+where the inverse temperature parameter $\lambda$ determines the consistency of the strategy (the higher $\lambda$, the more often the action with the highest $Q$-value is chosen).
+While this RL model allows the players to compute the values of actions conditional on past play, crucially, it will not be able to transfer learning between games, as each game has a different state space $\mathcal{S}_g$ and action space $\mathcal{A}_g$, and there is no simple way to map states and actions across games.The RL model has two free parameters: the learning rate ($\alpha$) and the inverse temperature ($\lambda$).
 
 ## Experience-weighted attraction (EWA) model
-
 The self-tuning Experience Weighted Attraction (EWA) model [@ho2004economics] combines two seemingly different approaches, namely reinforcement learning and belief learning.
@@
 \subsection{Bayesian Cognitive Hierarchy (BCH) model}
-
 In what we call the Bayesian Cognitive Hierarchy (BCH) model, the participant attempts to learn the type of opponent they are facing through Bayesian learning.
@@
 # Discussion
-
 In this study, we investigated human learning transfer across games by making human participants play against computer agents with limited levels of iterated reasoning.

### 2021-09-30 Report/paper_draft_2021.tex
CBB manuscript

@@
             pdfauthor={Ismail Guennouni1 \& Maarten Speekenbrink1},
+            pdfkeywords={Learning Transfer, Opponent modelling, Hidden Markov Models, Cognitive Hierarchy Models},
             colorlinks=true,
@@
 \makeatother
-\shorttitle{Upgrade Report}
+\shorttitle{SHORTTITLE}
+\keywords{Learning Transfer, Opponent modelling, Hidden Markov Models, Cognitive Hierarchy Models }
 \usepackage{csquotes}
@@
 \abstract{
-Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and
-causal models of the environment. One way to build abstract representations of the environment when the task involves interactions with others is to build
-a model of the opponent that may inform what actions they are likely to take next. In this study, we explore opponent modelling and its transfer with the use of
-computer agents with human-like limited degrees of iterated reasoning. In two experiments, we find that participants
-deviate from Nash equilibrium play and learn to adapt to their opponent's strategy to exploit it. Moreover, we show that participants transfer their learning to new games and that
-this transfer is moderated by the level of sophistication of the opponent, as well as the similarity between games. Computational modelling shows that players start each game with a model-based
-learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
+Human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and causal models of the environment.
+One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the opponent that may inform what actions they are likely to take next.
+In this study, we explore opponent modelling and its transfer with the use of computer agents with human-like limited degrees of iterated reasoning.
+In two experiments, we find that participants deviate from Nash equilibrium play and learn to adapt to their opponent's strategy to exploit it.
+Moreover, we show that participants transfer their learning to new games and that this transfer is moderated by the level of sophistication of the opponent (second experiment), as well as the similarity between games.
+Computational modelling shows that players start each game with a model-based learning strategy that facilitates between-game transfer of their opponent's strategy, but then switch to behaviour that is consistent with a model-free learning strategy in the latter stages of the interaction.
 }
@@
 There was also an interaction between Game and Condition (\(F(2,250) = 4.52\) , \(\eta^{2} = 0.03\), \(p = .01\)).
-\textbf{Post-hoc pairwise comparisons show that, for participants facing level-1 opponents, scores on the FWG game were significantly higher than RPS (\(t(250) = 3.85\) , \(p = .002\)), and also significantly higher than Numbers (\(t(250) = 3.79\) , \(p = .002\)).
-For participants facing level-2 opponents however, there was no significant difference between scores on the three games.}
+Post-hoc pairwise comparisons (\(p\)-values adjusted using Holm method for multiple comparisons) show that, for participants facing level-1 opponents, scores on the FWG game were significantly higher than those for both RPS (\(t(250) = 3.85\) , \(p = .002\)), and Numbers (\(t(250) = 3.79\) , \(p = .002\)).
+For participants facing level-2 opponents however, there was no significant difference between scores on the three games.
 
@@
 We found a main effect of Game (\(F(2,240) = 6.57\), \(p = .002\)).
-\textbf{The effect of game reflects early scores on FWG being significantly higher than on RPS (\(t(240) = 3.01\), \(p = .005\)) as well as scores on shootout being significantly higher than RPS (\(t(240) = 3.25\), \(p = .003\)).
+The effect of game reflects early scores on FWG being significantly higher than on RPS (\(t(240) = 3.01\), \(p = .005\)) as well as scores on shootout being significantly higher than RPS (\(t(240) = 3.25\), \(p = .003\)).
 We also found an interaction effect between Game and Opponent type (\(F(2,240) = 3.34\), \(p = .037\)).
-Post-hoc pairwise comparisons (applying Holm correction for multiple comparisons) show that the difference between early scores in RPS and shootout was mostly driven by participants facing level-1 players ((\(t(240) = 4.12\), \(p < .001\))).
-No signifcant differences were found between opponents for other games, or between games when facing the same opponent.}
-
-\textbf{MS: What do these effects indicate?
-Report post-hoc comparisons between games, and e.g.~differences between opponents for each game, here.
-The later tests against 0 are not adequate to understand the effects here.}
+Post-hoc pairwise comparisons (p-values adjusted using Holm method for multiple comparisons) show that the difference between early scores in RPS and shootout was mostly driven by participants facing level-1 players ((\(t(240) = 4.12\), \(p < .001\))).
+No signifcant differences were found between participants facing different opponents in the same game, or between games when facing the same opponent.
 
@@
 \[\phi(t) = 1 - \frac{1}{2}S_{p}(t) ,\]
-where \(S_{p}(t)\) quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play, across strategies k, as \(h^{k}(t)\):
+where \(S_{p}(t)\) quantifies how the opponent deviates from past play. It is calculated in turn through the cumulative history of play, across opponent possible actions k, as \(h^{k}(t)\):
 \[h^{k}(t)= \frac{\sum_{\tau =1}^t I(o^k=o_{\tau})}{t}, \]
@@
 \[S_{p}(t) = \sum_{k=1}^{|\mathcal{A}_g|} (h^{k}(t) - r^k(t))^2 \]
-
-\textbf{MS: why is there a superscript in \(h^k\) and \(r^k\)? }
-\textbf{IG : Because they depend on strategy k}
-
-\textbf{MS: And is the indicator variable \(I(o^k = o_{t})\)?}
-\textbf{IG: Yes, corrected}
-
-\textbf{And is \(\delta_a(t)\) always 0 or 1?}
-\textbf{IG: yes. Pls refer to: Camerer, C. F., \& Ho, T. H. (2015). Behavioral game theory experiments and modeling. Handbook of game theory with economic applications, 4, 517-573.}
 
